### 2025-01-15 main.tex
new commit

\documentclass[11pt]{article}

\usepackage[margin = 1in]{geometry}
\usepackage{article_macros}
\usepackage{authblk}

\theoremstyle{definition}
\newtheorem{algorithm}{Algorithm}
\newtheorem{construction}[theorem]{Construction}

\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}

\newcommand{\cas}{\mathrm{cas}}
\newcommand{\cht}{\mathsf{H}}
\newcommand{\qht}{\mathsf{QHT}}
\newcommand{\cft}{\mathsf{F}}
\newcommand{\qft}{\mathsf{QFT}}
\newcommand{\comph}{\mathsf{cmpIndex}}
\newcommand{\gen}{\mathsf{Gen}}
\newcommand{\ver}{\mathsf{Ver}}

\title{Fast Real Quantum Transforms and Application to Quantum Money}

\author{Jake Doliskani\thanks{\tt jake.doliskani@mcmaster.ca} }
% \author{Morteza Mirzaei\thanks{\tt mirzam48@mcmaster.ca} }
\author{Seyed Ali Mousavi\thanks{\tt mousas26@mcmaster.ca} }
\affil{Department of Computing and Software, McMaster University}

\date{}
\sloppy
\allowdisplaybreaks

\begin{document}
\maketitle

\newpage
\section{Introduction}
\label{sec:intro}

\bibliographystyle{plain}
\bibliography{references}

\end{document}

### 2025-01-22 main.tex
new commit

@@
 
-\title{Fast Real Quantum Transforms and Application to Quantum Money}
+\title{Quantum Walks and Application to Quantum Money}
 
@@
 \newpage
-\section{Introduction}
+\section{Introduction to Quantum Computation}
 \label{sec:intro}
+
+\section*{Introduction}
+Quantum computation represents a paradigm shift in the way we process information.
+Rooted in quantum mechanics, it leverages principles such as \textit{superposition}, \textit{entanglement}, and \textit{quantum interference} to solve certain classes of problems exponentially faster than classical computers.
+As a field, it combines the rigor of mathematics, the elegance of physics, and the practicality of computer science to unlock new computational horizons.
+
+\section*{Foundations of Quantum Computation}
+
+\subsection*{Qubits: The Building Blocks}
+A \textit{qubit} (quantum bit) is the quantum analog of the classical bit.
+While a classical bit can hold a value of either 0 or 1, a qubit exists in a quantum state described as a combination of these two possibilities, written as:
+\[
+|\psi\rangle = \alpha|0\rangle + \beta|1\rangle
+\]
+Here:
+\begin{itemize}
+    \item $\alpha$ and $\beta$ are complex numbers that represent the probabilities of measuring the qubit in the 0 or 1 state, respectively.
+    \item The condition $|\alpha|^2 + |\beta|^2 = 1$ ensures the total probability is conserved.
+\end{itemize}
+This \textit{superposition} property allows quantum computers to represent and process a vast amount of information simultaneously.
+
+\subsection*{Entanglement: Quantum Correlations}
+\textit{Entanglement} is a uniquely quantum phenomenon where the state of one qubit becomes intrinsically linked to the state of another, regardless of the physical distance between them.
+For example, two qubits might be in the entangled state:
+\[
+|\psi\rangle = \frac{1}{\sqrt{2}}(|00\rangle + |11\rangle)
+\]
+If one qubit is measured, the state of the other is instantaneously determined. This property underpins many quantum technologies, including quantum teleportation and quantum cryptography.
+
+\subsection*{Quantum Gates and Circuits}
+Quantum gates are the operational primitives of quantum computation. They manipulate qubits by altering their states in a manner consistent with quantum mechanics. Examples include:
+\begin{itemize}
+    \item \textbf{Hadamard Gate ($H$)}: Creates superposition from a basis state.
+    \item \textbf{Pauli Gates ($X, Y, Z$)}: Rotate qubit states around different axes.
+    \item \textbf{CNOT Gate}: Entangles two qubits by flipping the second qubit based on the state of the first.
+\end{itemize}
+A sequence of quantum gates forms a \textit{quantum circuit}, analogous to classical logic circuits but with exponentially richer possibilities due to quantum parallelism.
+
+\section*{Quantum Algorithms}
+Quantum algorithms exploit the principles of quantum mechanics to outperform classical counterparts in specific scenarios. Some groundbreaking algorithms include:
+
+\subsection*{Shor's Algorithm}
+Shor's algorithm efficiently factors large integers, threatening the security of classical cryptographic systems like RSA.
+Its speedup stems from the quantum Fourier transform and modular arithmetic in the quantum domain.
+
+\subsection*{Grover's Algorithm}
+Grover's algorithm provides a quadratic speedup for unstructured search problems.
+For instance, finding a specific item in an unsorted database with $N$ entries takes $O(\sqrt{N})$ queries on a quantum computer compared to $O(N)$ on a classical one.
+
+\subsection*{Quantum Simulation}
+Simulating quantum systems is computationally intensive for classical computers.
+Quantum computers can model chemical reactions, molecular structures, and physical systems more efficiently, accelerating drug discovery and materials science.
+
+\subsection*{Quantum Approximation Optimization Algorithm (QAOA)}
+Used for solving combinatorial optimization problems, QAOA is particularly relevant in fields like logistics and finance.
+
+\section*{Applications and Impact}
+Quantum computation has transformative potential across industries:
+\begin{itemize}
+    \item \textbf{Cryptography}: Beyond breaking classical systems, quantum computers can also enable secure communication through quantum key distribution (e.g., using entangled photons).
+    \item \textbf{Machine Learning}: Quantum-enhanced machine learning algorithms can handle high-dimensional data spaces more efficiently.
+    \item \textbf{Supply Chain and Logistics}: Quantum algorithms can optimize complex systems like traffic flow or supply chain logistics.
+    \item \textbf{Physics and Chemistry}: Accurate simulation of atomic interactions can drive innovations in energy, materials, and pharmaceuticals.
+\end{itemize}
+
+\section*{Challenges in Quantum Computation}
+\begin{itemize}
+    \item \textbf{Quantum Decoherence}: Quantum states are fragile and can be disrupted by interactions with their environment.
+Building stable quantum systems requires sophisticated error correction techniques and noise mitigation strategies.
+    \item \textbf{Error Correction}: Quantum error correction introduces redundancy through logical qubits composed of many physical qubits. This increases resource requirements significantly.
+    \item \textbf{Scalability}: Scaling quantum computers to hundreds or thousands of qubits is a formidable engineering challenge.
+Current systems, like IBM's quantum processors and Google's Sycamore, are still in the \textit{noisy intermediate-scale quantum} (NISQ) era.
+    \item \textbf{Algorithm Development}: Quantum algorithms for real-world problems are still under active research.
+Identifying practical applications with significant quantum advantage is a key focus.
+\end{itemize}
+
+\section*{Current Progress and the Future of Quantum Computation}
+The quantum computing landscape is advancing rapidly:
+\begin{itemize}
+    \item \textbf{Hardware}: Companies like IBM, Google, Rigetti, IonQ, and D-Wave are pushing the boundaries of quantum hardware.
+    \item \textbf{Software}: Frameworks like Qiskit, Cirq, and TensorFlow Quantum make quantum programming more accessible.
+    \item \textbf{Commercial Applications}: Financial modeling, risk analysis, and supply chain optimization are emerging areas of interest for quantum technologies.
+\end{itemize}
+The \textit{quantum advantage}---where quantum computers outperform classical systems in practical tasks---has been demonstrated in specific scenarios (e.g., Google's quantum supremacy experiment in 2019).
+However, achieving broad-scale quantum advantage remains a long-term goal.
+
+\section*{Conclusion}
+Quantum computation stands at the forefront of a technological revolution.
+By rethinking computation through the lens of quantum mechanics, it opens new pathways for solving problems that were once thought intractable.
+Although challenges remain, the potential benefits are vast, with the promise of transforming industries and deepening our understanding of the universe.
+As research and development continue, quantum computation is set to redefine the future of technology and science.
+
+\section{Introduction to Quantum Walks}
+
+\section{Group Actions}
+
+\section{Quantum Money}
+
+\section*{Introduction to Quantum Money}
+Quantum money is a revolutionary concept in cryptography that uses quantum mechanics to create a form of currency that is provably secure against forgery.
+Originally introduced by physicist Stephen Wiesner in the 1970s, quantum money represents one of the earliest proposed applications of quantum information science.
+By encoding information into quantum states, quantum money exploits the fundamental principles of quantum mechanics to provide security features unattainable by classical systems.
+
+\section*{How Quantum Money Works}
+At its core, quantum money relies on two key principles of quantum mechanics: the \textit{no-cloning theorem} and the \textit{observer effect}.
+
+\subsection*{Encoding Information in Quantum States}
+\begin{itemize}
+    \item Each quantum bill contains a unique quantum state, such as a set of qubits encoded in superposition.
+    \item These states are generated and stored by the issuing authority (e.g., a central bank) using a secret algorithm.
+\end{itemize}
+
+\subsection*{Verification Process}
+\begin{itemize}
+    \item The issuing authority also generates a verification protocol, allowing a legitimate quantum bill to be authenticated.
+    \item When a user presents a quantum bill for verification, the authority measures the encoded quantum states using the pre-determined protocol.
+    \item If the measured states align with the expected values, the bill is deemed valid.
+\end{itemize}
+
+\subsection*{Unforgeability}
+\begin{itemize}
+    \item Due to the \textit{no-cloning theorem}, it is impossible to copy an unknown quantum state without altering it.
+    \item Any attempt to measure or duplicate the quantum state results in a disturbance detectable during verification.
+\end{itemize}
+
+\section*{Key Principles Underpinning Quantum Money}
+\begin{enumerate}
+    \item \textbf{No-Cloning Theorem:} The no-cloning theorem states that an unknown quantum state cannot be perfectly copied.
+This makes quantum money inherently secure, as counterfeiters cannot reproduce the quantum states encoded in legitimate currency.
+    \item \textbf{Measurement Disturbance:} Observing or measuring a quantum state generally alters it.
+This ensures that any unauthorized attempt to inspect the quantum money will render it invalid, as the encoded states will no longer match their original form.
+    \item \textbf{Randomness and Superposition:} Quantum money utilizes superposition to encode information.
+For example, a single qubit in superposition may represent both $0$ and $1$ simultaneously until measured.
+The randomness of these states makes predicting or reproducing them without knowledge of the original encoding impossible.
+    \item \textbf{Entanglement (Optional Feature):} Some implementations of quantum money involve quantum entanglement, where pairs of quantum states are interconnected.
+Changes to one entangled state directly affect its pair, adding another layer of security against forgery.
+\end{enumerate}
+
+\section*{Benefits of Quantum Money}
+\begin{itemize}
+    \item \textbf{Unforgeable:} Classical currency, both physical and digital, can be counterfeited with enough effort and resources.
+Quantum money, however, is fundamentally unforgeable due to the laws of quantum physics.
+    \item \textbf{Decentralized Verification:} In some theoretical models, quantum money can be verified without contacting the issuing authority, enabling decentralized systems for authentication.
+    \item \textbf{Enhanced Privacy:} The unique encoding of each quantum bill could allow for privacy-preserving transactions, as the details of the transaction need not be linked to the bill's verification.
+\end{itemize}
+
+\section*{Challenges and Open Questions}
+\begin{enumerate}
+    \item \textbf{Practical Implementation:} Generating and maintaining stable quantum states in real-world conditions is technically challenging.
+Quantum systems are highly sensitive to environmental noise, requiring robust error-correction mechanisms.
+    \item \textbf{Scalability:} For quantum money to replace traditional systems, it must scale to accommodate billions of users and transactions.
+    \item \textbf{Theft and Security:} While quantum money cannot be forged, it can still be stolen, much like traditional physical or digital assets.
+Developing secure storage and transfer mechanisms is a priority.
+    \item \textbf{Centralized vs.
+Decentralized Systems:} Most current proposals involve a centralized authority for issuing and verifying quantum money.
+However, decentralized quantum money systems (akin to blockchain technology) are an area of active research.
+\end{enumerate}
+
+\section*{Applications Beyond Money}
+The principles underlying quantum money have broader applications, such as:
+\begin{itemize}
+    \item \textbf{Quantum Tokens:} Used in secure communication or access control.
+    \item \textbf{Quantum Cryptography:} Building secure voting systems or decentralized platforms.
+    \item \textbf{Quantum Key Distribution (QKD):} While distinct from quantum money, QKD relies on similar quantum principles to ensure the security of communication channels.
+\end{itemize}
+
+\section*{Conclusion}
+Quantum money represents a paradigm shift in secure transactions, leveraging the foundational principles of quantum mechanics to create currency that is inherently secure against forgery.
+While still a theoretical concept, advances in quantum technology and cryptography are rapidly bringing us closer to practical implementations.
+If realized, quantum money could redefine financial systems, offering unparalleled security and efficiency in the digital age.
+
+\section{Applicaions}
 

### 2025-01-22 main.tex
new commit

@@
 
+\section*{Introduction}
+Quantum walks are a quantum mechanical generalization of classical random walks, leveraging principles such as \textit{quantum superposition}, \textit{entanglement}, and \textit{interference}.
+These characteristics enable quantum walks to exhibit behavior fundamentally different from their classical counterparts, making them powerful tools in quantum computing, simulation, and algorithm design.
+
+\section*{Classical Random Walks: A Precursor}
+In a classical random walk:
+\begin{itemize}
+    \item A particle moves step-by-step in a discrete space (e.g., a line or graph).
+    \item The direction or next state is determined probabilistically.
+    \item The probability distribution spreads symmetrically over time, often following a Gaussian distribution.
+\end{itemize}
+
+While classical random walks are foundational in algorithms and statistical mechanics, quantum walks introduce richer dynamics through quantum principles.
+
+\section*{Quantum Walks: Core Concepts}
+
+\subsection*{Quantum Superposition}
+In a quantum walk, the walker exists in a superposition of multiple positions. The state of the walker is described by a quantum state vector in a Hilbert space:
+\[
+|\psi\rangle = \sum_{x} \alpha_x |x\rangle,
+\]
+where $\alpha_x$ are complex amplitudes, and the probability of finding the walker at position $x$ is $|\alpha_x|^2$.
+
+\subsection*{Coin and Position Space}
+Quantum walks incorporate an internal ``coin" state that determines the direction of movement:
+\begin{itemize}
+    \item \textbf{Coin space:} A finite-dimensional quantum system (e.g., a qubit) represents the internal state. For example, $|0\rangle$ (move left) and $|1\rangle$ (move right).
+    \item \textbf{Position space:} The physical space in which the walker moves (e.g., a line or graph).
+\end{itemize}
+The overall state of the walker is:
+\[
+|\psi\rangle = \sum_{x} \sum_{c} \alpha_{x,c} |x\rangle \otimes |c\rangle,
+\]
+where $|c\rangle$ represents the coin state.
+
+\subsection*{Unitary Evolution}
+Quantum walks evolve via unitary transformations, which preserve the norm of the quantum state. The evolution typically consists of two steps:
+\begin{enumerate}
+    \item \textbf{Coin Flip:} A quantum operation, such as the Hadamard gate $H$, creates a superposition of directions.
+    \item \textbf{Shift:} Based on the coin state, the walker moves to adjacent positions.
+\end{enumerate}
+For discrete-time quantum walks (DTQW), the unitary evolution operator is:
+\[
+U = S \cdot (C \otimes I),
+\]
+where $C$ is the coin operator, $S$ is the shift operator, and $I$ is the identity operator.
+
+\subsection*{Interference}
+Quantum walks exhibit interference.
+When the walker follows multiple paths simultaneously, constructive or destructive interference alters the probability distribution, leading to faster spreading compared to classical walks.
+
+\section*{Types of Quantum Walks}
+
+\subsection*{Discrete-Time Quantum Walk (DTQW)}
+In a DTQW:
+\begin{itemize}
+    \item The walker evolves in discrete time steps.
+    \item Each step applies the coin flip and shift operations.
+    \item The state after $t$ steps is:
+    \[
+    |\psi(t)\rangle = U^t |\psi(0)\rangle.
+    \]
+\end{itemize}
+
+\subsection*{Continuous-Time Quantum Walk (CTQW)}
+In a CTQW:
+\begin{itemize}
+    \item Time evolution is continuous and governed by the Schrödinger equation:
+    \[
+    i\hbar \frac{d}{dt}|\psi(t)\rangle = H |\psi(t)\rangle,
+    \]
+    where $H$ is the Hamiltonian of the system.
+    \item The state at time $t$ is:
+    \[
+    |\psi(t)\rangle = e^{-iHt}|\psi(0)\rangle.
+    \]
+\end{itemize}
+
+\section*{Differences Between Classical and Quantum Walks}
+\[
+\begin{array}{|c|c|c|}
+\hline
+\textbf{Feature} & \textbf{Classical Walk} & \textbf{Quantum Walk} \\
+\hline
+\textbf{State} & Single position & Superposition of positions \\
+\textbf{Evolution} & Probabilistic & Unitary \\
+\textbf{Speed} & Spreads diffusively (\sqrt{t}) & Spreads ballistically (t) \\
+\textbf{Interference} & None & Constructive and destructive \\
+\textbf{Probability} & Real numbers & Squares of complex amplitudes \\
+\hline
+\end{array}
+\]
+
+\section*{Applications of Quantum Walks}
+
+\subsection*{Quantum Algorithms}
+Quantum walks are foundational to several quantum algorithms, such as:
+\begin{itemize}
+    \item \textbf{Search Problems:} Efficiently searching databases or graphs.
+    \item \textbf{Element Distinctness:} Solving computational problems faster than classical algorithms.
+\end{itemize}
+
+\subsection*{Quantum Computing}
+Quantum walks provide a framework for designing quantum circuits and gates and are integral to universal models of quantum computation.
+
+\subsection*{Graph Problems}
+Quantum walks are used to analyze graph properties, such as connectivity and mixing time, and solve problems like hitting time.
+
+\subsection*{Physics Simulations}
+Quantum walks simulate transport phenomena in physical systems, such as electron movement in lattices, and model systems with decoherence and topological phases.
+
+\subsection*{Cryptography}
+Quantum walks are explored in the context of quantum money and cryptographic protocols.
+
+\section*{Conclusion}
+Quantum walks bridge quantum mechanics and computational theory, offering faster computation, richer simulations, and novel applications.
+By leveraging principles like superposition and interference, they provide new avenues for solving problems that are intractable with classical systems.
+
 \section{Group Actions}

### 2025-01-25 main.tex
new commit

--- 2025-01-22 main.tex
@@
 \section*{Introduction}
-Quantum computation represents a paradigm shift in the way we process information.
-Rooted in quantum mechanics, it leverages principles such as \textit{superposition}, \textit{entanglement}, and \textit{quantum interference} to solve certain classes of problems exponentially faster than classical computers.
-As a field, it combines the rigor of mathematics, the elegance of physics, and the practicality of computer science to unlock new computational horizons.
+
+Quantum computing is a revolutionary field that combines quantum mechanics and information theory to redefine computation and information processing.
+In the latter part of the 20th century, scientists explored the fusion of quantum mechanics and information theory, leading to the birth of quantum information science.
+This field challenges the classical view of computation by introducing novel concepts like quantum bits (qubits), entanglement, and quantum superposition, which have enabled new algorithms and protocols that outpace their classical counterparts in specific tasks.
+Classical computers are grounded in bits, which take binary values (0 or 1).
+Quantum computing introduces the qubit, a fundamental unit of quantum information that can exist in a superposition of states, such as 0 and 1 simultaneously.
+This foundational difference enables quantum computers to process information in fundamentally new ways.
+Unlike technologies like DNA computing or optical computing, which describe changes in the physical substrate while retaining classical computational principles, quantum computing changes the computational paradigm itself.
+A quantum computer uses the principles of quantum mechanics, such as superposition and entanglement, rather than classical mechanics, to process information.
+In the 1980s, pioneers like Richard Feynman and David Deutsch recognized that certain quantum phenomena could not be efficiently simulated on classical computers.
+These insights led to the exploration of quantum Turing machines and quantum circuit models, which provided a theoretical framework for quantum computing.
+The discovery of quantum gates and their role in quantum algorithms formalized the field.
+
+Early quantum algorithms demonstrated that quantum computing could solve certain problems more efficiently than classical methods.
+Notably, in 1994, Peter Shor introduced a polynomial-time quantum algorithm for integer factorization, which threatened classical cryptographic protocols relying on the difficulty of factoring large integers.
+Entanglement, a uniquely quantum phenomenon, allows particles to exhibit correlations that defy classical explanation.
+This property is crucial for many quantum algorithms and protocols, as it enables quantum computers to process and store information in a way that classical computers cannot.
+Two notable algorithms underscore the potential of quantum computing: Shor’s Algorithm, which efficiently factors integers, undermining RSA encryption and other cryptographic systems based on the hardness of factoring, and Grover’s Algorithm, which provides a quadratic speedup for unstructured search problems, such as searching an unsorted database.
+These algorithms exemplify the theoretical advantages of quantum computing over classical approaches, even though practical implementations remain challenging.
+
+Quantum systems are fragile and susceptible to decoherence, where quantum states lose their coherence due to interactions with the environment.
+This makes maintaining quantum states for computation a significant challenge.
+Quantum error correction methods were developed to address decoherence and other quantum noise.
+The breakthrough work of Shor and Steane in the mid-1990s introduced error-correction codes that allowed reliable computation despite quantum noise.
+Building scalable quantum computers requires advances in hardware and experimental techniques.
+As of now, only small-scale quantum systems with a few qubits have been implemented successfully in laboratories.
+Quantum computing does not offer universal speedups for all problems.
+For example, Grover’s algorithm provides only a quadratic speedup for unstructured search, and certain problems remain equally challenging for both quantum and classical computers.
+
+Quantum key distribution protocols, like BB84 and Ekert’s protocol, offer provably secure methods for communication based on the principles of quantum mechanics.
+Unlike classical cryptography, which relies on computational assumptions, quantum cryptography guarantees security through physical principles.
+The quantum perspective has provided new insights into classical computing and inspired novel classical algorithms.
+It has also advanced simulation techniques for quantum systems, benefiting fields like material science and chemistry.
+Quantum information processing has deepened our understanding of quantum mechanics, shedding light on foundational questions about quantum measurement and entanglement.
+For example, experiments testing Bell’s inequalities have confirmed the non-classical correlations predicted by quantum theory.
+
+While practical quantum computing is still in its infancy, significant progress has been made.
+Quantum hardware companies like IBM, Google, and Rigetti have developed small-scale quantum processors capable of performing limited computations.
+Platforms such as Qiskit and Cirq enable researchers to experiment with quantum programming and algorithm development.
+Efforts to build scalable, fault-tolerant quantum computers are ongoing, alongside investigations into alternative models of quantum computation, such as topological and cluster-state quantum computing.
+Despite these advances, many open questions remain about the scope and ultimate power of quantum computation.
+While quantum computers will not replace classical ones for all tasks, they promise to revolutionize fields where their unique capabilities provide exponential speedups or new forms of computation.
+
+Quantum computing represents a profound shift in how we understand and leverage computation.
+By replacing classical mechanics with quantum mechanics as the foundation for processing information, quantum computing has opened new avenues for scientific discovery and technological innovation.
+While challenges persist, the theoretical and experimental advances made thus far underscore the transformative potential of this exciting field.
 
@@
 
-\subsection*{Qubits: The Building Blocks}
-A \textit{qubit} (quantum bit) is the quantum analog of the classical bit.
-While a classical bit can hold a value of either 0 or 1, a qubit exists in a quantum state described as a combination of these two possibilities, written as:
-\[
-|\psi\rangle = \alpha|0\rangle + \beta|1\rangle
-\]
+\section*{Understanding a Qubit}
+A qubit (quantum bit) is the fundamental unit of quantum information, analogous to a classical bit.
+However, unlike a classical bit, which can only exist in one of two definite states ($0$ or $1$), a qubit can exist in a linear combination, or superposition, of both states simultaneously.
+Mathematically, the state of a single qubit is represented as:
+
+\begin{equation}
+|\psi\rangle = \alpha |0\rangle + \beta |1\rangle
+\end{equation}
+
 Here:
 \begin{itemize}
-    \item $\alpha$ and $\beta$ are complex numbers that represent the probabilities of measuring the qubit in the 0 or 1 state, respectively.
-    \item The condition $|\alpha|^2 + |\beta|^2 = 1$ ensures the total probability is conserved.
+    \item $|0\rangle$ and $|1\rangle$ are the basis states (analogous to $0$ and $1$ in classical computing).
+    \item $\alpha$ and $\beta$ are complex numbers known as probability amplitudes.
 \end{itemize}
-This \textit{superposition} property allows quantum computers to represent and process a vast amount of information simultaneously.
 
-\subsection*{Entanglement: Quantum Correlations}
-\textit{Entanglement} is a uniquely quantum phenomenon where the state of one qubit becomes intrinsically linked to the state of another, regardless of the physical distance between them.
-For example, two qubits might be in the entangled state:
-\[
-|\psi\rangle = \frac{1}{\sqrt{2}}(|00\rangle + |11\rangle)
-\]
-If one qubit is measured, the state of the other is instantaneously determined. This property underpins many quantum technologies, including quantum teleportation and quantum cryptography.
+The normalization condition \(|\alpha|^2 + |\beta|^2 = 1\) ensures that the probabilities of measuring the qubit in either the $|0\rangle$ or $|1\rangle$ state sum to 1.
+
+The qubit's unique ability to exist in a superposition of states is what gives quantum computers their immense computational potential, enabling them to process and store information in fundamentally different ways than classical computers.
+
+\section*{Superposition}
+Superposition is a quantum phenomenon where a qubit exists in a combination of multiple states simultaneously. For example, a qubit in the state:
+
+\begin{equation}
+|\psi\rangle = \frac{1}{\sqrt{2}}|0\rangle + \frac{1}{\sqrt{2}}|1\rangle
+\end{equation}
+
+is in an equal superposition of $|0\rangle$ and $|1\rangle$. This means that if we measure the qubit, there is an equal probability (50\%) of observing it in either state.
+
+Key properties of superposition:
+\begin{itemize}
+    \item \textbf{Parallelism:} When a quantum system is in superposition, it can perform computations for all possible states simultaneously.
+For instance, a single qubit can encode two states ($|0\rangle$ and $|1\rangle$) at the same time, while $n$ qubits can encode $2^n$ states.
+    \item \textbf{Measurement Collapse:} When a qubit in superposition is measured, it collapses into one of its basis states, $|0\rangle$ or $|1\rangle$, with a probability given by $|\alpha|^2$ and $|\beta|^2$, respectively.
+\end{itemize}
+
+Superposition allows quantum systems to explore multiple possibilities in parallel, which is critical for quantum algorithms such as Grover's search or Shor's factoring.
+
+\section*{Entanglement}
+Entanglement is a uniquely quantum phenomenon where two or more qubits become correlated in such a way that the state of one qubit is directly related to the state of the other, regardless of the physical distance between them.
+When qubits are entangled, the measurement of one qubit instantly determines the state of the other.
+
+An example of an entangled state for two qubits is the Bell state:
+
+\begin{equation}
+|\psi\rangle = \frac{1}{\sqrt{2}} (|00\rangle + |11\rangle)
+\end{equation}
+
+Here:
+\begin{itemize}
+    \item $|00\rangle$ means both qubits are in the $|0\rangle$ state.
+    \item $|11\rangle$ means both qubits are in the $|1\rangle$ state.
+\end{itemize}
+
+If one qubit is measured to be $|0\rangle$, the other qubit will instantly collapse to $|0\rangle$, and similarly for $|1\rangle$, regardless of the distance between them.
+
+Key features of entanglement:
+\begin{itemize}
+    \item \textbf{Non-Local Correlations:} Entanglement defies classical intuition, as it suggests that measurement outcomes are correlated even across vast distances, a phenomenon supported by experiments validating Bell's Theorem.
+    \item \textbf{Applications:} Entanglement is a resource for many quantum technologies, including quantum teleportation, quantum cryptography (e.g., secure communication via the BB84 protocol), and quantum error correction.
+\end{itemize}
+
+Entanglement, along with superposition, forms the backbone of quantum computing and quantum communication, enabling capabilities that are impossible in the classical world.
 
@@
 
-\section*{Quantum Algorithms}
-Quantum algorithms exploit the principles of quantum mechanics to outperform classical counterparts in specific scenarios. Some groundbreaking algorithms include:
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Introduction to Quantum Walks}
 
-\subsection*{Shor's Algorithm}
-Shor's algorithm efficiently factors large integers, threatening the security of classical cryptographic systems like RSA.
-Its speedup stems from the quantum Fourier transform and modular arithmetic in the quantum domain.
+The concept of a \textit{quantum walk} is a quantum analog of the classical random walk and plays a significant role in quantum algorithms.
+There are two main types of quantum walks: \textit{continuous-time} and \textit{discrete-time} quantum walks, both of which exhibit behaviors that are significantly different from classical random walks.
 
-\subsection*{Grover's Algorithm}
-Grover's algorithm provides a quadratic speedup for unstructured search problems.
-For instance, finding a specific item in an unsorted database with $N$ entries takes $O(\sqrt{N})$ queries on a quantum computer compared to $O(N)$ on a classical one.
+\section*{Continuous-Time Quantum Walks}
+A \textit{continuous-time quantum walk} is defined on a graph, where the evolution of the system is governed by a differential equation similar to the Schrödinger equation:
+\[
+i\frac{d}{dt}q(t) = Hq(t),
+\]
+where the Hamiltonian \( H \) is an \( N \times N \) Hermitian matrix, with \( H_{jk} = 0 \) if and only if vertices \( j \) and \( k \) are not connected.
+The vector \( q(t) \in \mathbb{C}^N \) contains the complex amplitudes corresponding to each vertex.
+Notably, the state space for the quantum walk is the same as that for the corresponding classical random walk.
 
-\subsection*{Quantum Simulation}
-Simulating quantum systems is computationally intensive for classical computers.
-Quantum computers can model chemical reactions, molecular structures, and physical systems more efficiently, accelerating drug discovery and materials science.
+One important matrix associated with the graph \( G \) is the \textit{Laplacian matrix}, defined as:
+\[
+L_{jk} =
+\begin{cases}
+-\text{deg}(j) & \text{if } j = k, \\
+1 & \text{if } (j, k) \in E, \\
+0 & \text{otherwise}.
+\end{cases}
+\]
 
-\subsection*{Quantum Approximation Optimization Algorithm (QAOA)}
-Used for solving combinatorial optimization problems, QAOA is particularly relevant in fields like logistics and finance.
+The continuous-time random walk on \( G \) is then defined as the solution to the differential equation:
+\[
+\frac{d}{dt} p_j(t) = \sum_{k \in V} L_{jk} p_k(t),
+\]
+where \( p_j(t) \) represents the probability at vertex \( j \) at time \( t \). The solution to this equation can be expressed in closed form as:
+\[
+p(t) = e^{Lt} p(0),
+\]
+where \( L \) is the Laplacian matrix and \( p(0) \) is the initial condition.
 
-\section*{Applications and Impact}
-Quantum computation has transformative potential across industries:
+This equation closely resembles the Schrödinger equation, but it lacks the factor \( i \).
+By adding this factor and redefining the probabilities \( p_j(t) \) as quantum amplitudes \( q_j(t) = \langle j|\psi(t)\rangle \) (where \( \{ |j\rangle : j \in V \} \) is an orthonormal basis for the Hilbert space), we obtain:
+\[
+i \frac{d}{dt} q_j(t) = \sum_{k \in V} L_{jk} q_k(t),
+\]
+which is the Schrödinger equation with the Laplacian of the graph as the Hamiltonian. Since the Laplacian is a Hermitian operator, these dynamics preserve normalization:
+\[
+\frac{d}{dt} \sum_{j \in V} |q_j(t)|^2 = 0.
+\]
+
+The solution to this differential equation is:
+\[
+|\psi(t)\rangle = e^{-iLt} |\psi(0)\rangle.
+\]
+
+A continuous-time quantum walk can also be defined using any Hermitian Hamiltonian that respects the structure of \( G \).
+
+\subsection*{Differences from Classical Random Walks}
+The evolution of a quantum walk, governed by a Hamiltonian, dictates state transitions over time while preserving normalization.
+This contrasts with classical random walks, which involve probabilistic transitions.
+Moreover, the wave nature of quantum mechanics introduces interference effects, enabling faster exploration of graphs compared to classical methods.
+For instance, on one-dimensional graphs, a classical random walk progresses at a rate proportional to the square root of time, while a quantum walk progresses linearly with time due to the wave-like propagation of quantum states.
+
+\section*{Discrete-Time Quantum Walks}
+\textit{Discrete-time quantum walks}, though more complex to define, provide a convenient framework for certain quantum algorithms, particularly quantum search algorithms.
+
+In the simplest classical discrete-time random walk on a graph \( G \), at each time step, the walker moves from a given vertex to one of its neighbors with equal probability.
+This process is described by a \( |V| \times |V| \) matrix \( M \), where:
+\[
+M_{jk} = 
+\begin{cases} 
+\frac{1}{\text{deg}(k)} & \text{if } (j, k) \in E, \\
+0 & \text{otherwise}.
+\end{cases}
+\]
+The initial probability distribution \( p \) over the vertices updates to \( p' = M p \) after one step.
+
+For quantum walks, maintaining unitarity requires a \textit{coin operator} \( C \) to determine the direction of the next step.
+A common choice for the coin operator is the Grover diffusion operator, defined as:
+\[
+C := \sum_{j \in V}\ket{j}\bra{j} \otimes (2\ket{\partial_j}\bra{\partial_j} - I),
+\]
+where:
+\[
+\ket{\partial_j} := \frac{1}{\sqrt{\deg(j)}} \sum_{k:(j,k) \in E}\ket{k},
+\]
+denotes the superposition of the neighboring vertices of \( \ket{j} \), and \( I \) is the identity matrix.
+
+One step of the discrete-time quantum walk is described by the unitary operator \( SC \), where \( S \) is the swap operator:
+\[
+S = \sum_{(j,k) \in E}\ket{j,k}\bra{k,j}.
+\]
+
+\subsection*{Comparison of Models}
+The continuous-time model is simpler to define and analyze, often leading to exponential speedups under specific conditions, such as graphs with small maximum degrees.
+However, discrete-time quantum walks are easier to implement using quantum circuits, making them more practical in many applications.
+For example, while continuous-time models may struggle with certain problems like \textit{element distinctness}, discrete-time models handle them more effectively.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Group Actions}
+
+Group actions provide a framework for understanding how groups interact with sets, formalizing the concept of applying transformations systematically.
+They capture the symmetries and structure-preserving transformations of objects, making them fundamental in mathematics and its applications.
+Group actions describe transformations through a set of rules that ensure consistency and compatibility with the underlying group operations.
+This concept is pivotal in cryptography, where the symmetries and operations of groups underpin many secure systems.
+
+In cryptography, group actions are critical to protocols like Elliptic Curve Cryptography (ECC), which relies on the difficulty of reversing group-based operations to ensure security.
+Isogeny-based cryptography, a post-quantum cryptographic candidate, uses group actions on elliptic curves to create complex mathematical problems resistant to quantum attacks.
+Similarly, lattice-based and code-based cryptography use group actions to study transformations in structures that form the basis for secure communication systems.
+Non-abelian group actions are being explored for their potential to create quantum-resistant algorithms.
+
+In quantum computing, group actions are central to quantum walks, a quantum equivalent of classical random walks.
+Quantum walks leverage group actions to describe the evolution of quantum states and exploit the symmetries of these states for tasks like search, optimization, and cryptographic protocol design.
+This makes them valuable in constructing secure quantum algorithms and protocols, particularly in quantum key distribution and graph-based cryptography.
+Overall, group actions bridge abstract mathematical theory with practical applications in classical and quantum cryptography.
+
+\section*{Definition of Group Action}
+
+Group actions form a bridge between group theory and other mathematical structures, offering a systematic way to study symmetry, transformations, and invariants.
+Let us delve deeper into their properties, classifications, and applications.
+
+\subsection*{Formal Definition}
+
+A \textbf{group action} of a group \( G \) on a set \( X \) is a map \( \cdot : G \times X \to X \) that satisfies:
+
+\begin{enumerate}
+    \item \textbf{Identity Property}:
+    \[
+    e \cdot x = x \quad \text{for all } x \in X,
+    \]
+    where \( e \) is the identity element of \( G \).
+
+    \item \textbf{Compatibility (Associativity)}:
+    \[
+    (gh) \cdot x = g \cdot (h \cdot x) \quad \text{for all } g, h \in G, \, x \in X.
+    \]
+\end{enumerate}
+
+Alternatively, the group action can be viewed as a homomorphism \( \phi : G \to \text{Sym}(X) \), where \( \text{Sym}(X) \) is the group of all permutations of \( X \).
+
+\subsection*{Types of Group Actions}
+
+\begin{enumerate}
+    \item \textbf{Faithful Action}: The action is faithful if \( g \cdot x = x \) for all \( x \in X \) implies \( g = e \). Equivalently, the homomorphism \( \phi \) is injective.
+
+    \item \textbf{Transitive Action}: The action is transitive if, for any \( x, y \in X \), there exists \( g \in G \) such that \( g \cdot x = y \). In this case, \( X \) consists of a single orbit.
+
+    \item \textbf{Free Action}: The action is free if \( g \cdot x = x \) implies \( g = e \) for all \( x \in X \).
+
+    \item \textbf{Regular Action}: The action is both transitive and free, meaning there is exactly one \( g \in G \) for each pair \( (x, y) \) such that \( g \cdot x = y \).
+
+    \item \textbf{Effective Action}: The action is effective if the only group element acting as the identity on \( X \) is \( e \).
+\end{enumerate}
+
+\subsection*{Key Concepts in Group Actions}
+
+\begin{enumerate}
+    \item \textbf{Orbits}:
+    For \( x \in X \), the \textbf{orbit} of \( x \) is:
+    \[
+    \text{Orb}(x) = \{g \cdot x \mid g \in G\}.
+    \]
+    Orbits partition the set \( X \), and each orbit is a subset where the action appears ``connected.''
+
+    \item \textbf{Stabilizer Subgroup}:
+    The \textbf{stabilizer} of \( x \in X \) is:
+    \[
+    \text{Stab}_G(x) = \{g \in G \mid g \cdot x = x\}.
+    \]
+    It is a subgroup of \( G \) and describes the symmetries that leave \( x \) unchanged.
+
+    \item \textbf{Orbit-Stabilizer Theorem}:
+    This theorem links the size of an orbit and its stabilizer:
+    \[
+    |G| = |\text{Orb}(x)| \cdot |\text{Stab}_G(x)|.
+    \]
+
+    \item \textbf{Fixed Points}:
+    A point \( x \in X \) is a \textbf{fixed point} if \( g \cdot x = x \) for all \( g \in G \). The set of fixed points is:
+    \[
+    \text{Fix}(G) = \{x \in X \mid g \cdot x = x, \, \forall g \in G\}.
+    \]
+
+    \item \textbf{Invariant Subsets}:
+    A subset \( Y \subseteq X \) is \textbf{invariant} under the action if \( g \cdot y \in Y \) for all \( g \in G \) and \( y \in Y \).
+\end{enumerate}
+
+\subsection*{Equivalence Relations Induced by Group Actions}
+
+The orbits of a group action define an equivalence relation on \( X \), where \( x \sim y \) if there exists \( g \in G \) such that \( g \cdot x = y \).
+
 \begin{itemize}
-    \item \textbf{Cryptography}: Beyond breaking classical systems, quantum computers can also enable secure communication through quantum key distribution (e.g., using entangled photons).
-    \item \textbf{Machine Learning}: Quantum-enhanced machine learning algorithms can handle high-dimensional data spaces more efficiently.
-    \item \textbf{Supply Chain and Logistics}: Quantum algorithms can optimize complex systems like traffic flow or supply chain logistics.
-    \item \textbf{Physics and Chemistry}: Accurate simulation of atomic interactions can drive innovations in energy, materials, and pharmaceuticals.
+    \item \textbf{Equivalence Classes}: The orbits of the action.
+    \item \textbf{Quotient Set}: The set of orbits, denoted \( X/G \).
 \end{itemize}
 
-\section*{Challenges in Quantum Computation}
-\begin{itemize}
-    \item \textbf{Quantum Decoherence}: Quantum states are fragile and can be disrupted by interactions with their environment.
-Building stable quantum systems requires sophisticated error correction techniques and noise mitigation strategies.
-    \item \textbf{Error Correction}: Quantum error correction introduces redundancy through logical qubits composed of many physical qubits. This increases resource requirements significantly.
-    \item \textbf{Scalability}: Scaling quantum computers to hundreds or thousands of qubits is a formidable engineering challenge.
-Current systems, like IBM's quantum processors and Google's Sycamore, are still in the \textit{noisy intermediate-scale quantum} (NISQ) era.
-    \item \textbf{Algorithm Development}: Quantum algorithms for real-world problems are still under active research.
-Identifying practical applications with significant quantum advantage is a key focus.
-\end{itemize}
+\subsection*{Quantum walks from Group Actions}
+The spectral decomposition of the adjacency matrix of a Cayley graph generated by a general group action $G$ provides insights into the structure and properties of the graph.
+This decomposition leverages the symmetries of the group $G$ and representation theory to analyze the eigenvalues and eigenvectors of the adjacency matrix.
 
-\section*{Current Progress and the Future of Quantum Computation}
-The quantum computing landscape is advancing rapidly:
-\begin{itemize}
-    \item \textbf{Hardware}: Companies like IBM, Google, Rigetti, IonQ, and D-Wave are pushing the boundaries of quantum hardware.
-    \item \textbf{Software}: Frameworks like Qiskit, Cirq, and TensorFlow Quantum make quantum programming more accessible.
-    \item \textbf{Commercial Applications}: Financial modeling, risk analysis, and supply chain optimization are emerging areas of interest for quantum technologies.
-\end{itemize}
-The \textit{quantum advantage}---where quantum computers outperform classical systems in practical tasks---has been demonstrated in specific scenarios (e.g., Google's quantum supremacy experiment in 2019).
-However, achieving broad-scale quantum advantage remains a long-term goal.
+Let $G$ be a finite group, and let $X$ be a set on which $G$ acts via a group action $G \times X \to X$. A Cayley graph can be constructed based on this action, where
+the vertices are the elements of the set $X$, and For each $g \in G$ and $x \in X$, there is an edge between $x$ and $g *	x$, where $g * x$ is the action of $g$ on $x$.
 
-\section*{Conclusion}
-Quantum computation stands at the forefront of a technological revolution.
-By rethinking computation through the lens of quantum mechanics, it opens new pathways for solving problems that were once thought intractable.
-Although challenges remain, the potential benefits are vast, with the promise of transforming industries and deepening our understanding of the universe.
-As research and development continue, quantum computation is set to redefine the future of technology and science.
+If the generating set $S \subset G$ is symmetric (i.e., $s \in S \implies s^{-1} \in S$), then the Cayley graph is undirected. Otherwise, it may be directed.
 
-\section{Introduction to Quantum Walks}
+The adjacency matrix $A$ of the Cayley graph is a matrix that encodes the edges of the graph:
 
-\section{Group Actions}
+\[
+A_{x,y} =
+\begin{cases}
+1, & \text{if there exists } g \in G \text{ such that } y = g * x, \\
+0, & \text{otherwise}.
+\end{cases}
+\]
+
+The adjacency matrix is symmetric if the group action preserves symmetry, which happens if $G$ is acting via an involution, i.e., if for every generator $g \in G$, its inverse is also a generator.
+It also inherits the symmetries of the group action.
+That is, the group $G$ acts on the vertices of the graph, and the adjacency matrix commutes with the action of the group.
+This means that the adjacency matrix $A$ is highly structured, and its eigenvalues can be computed using the representation theory of the group $G$.
+
+The eigenvalues of the adjacency matrix correspond to the eigenvalues of these blocks $\rho(A)$, and the multiplicities of the eigenvalues are related to the dimensions of the corresponding irreducible representations.
+
+The spectral decomposition of the adjacency matrix $A$ can be written as:
+
+\[
+A = \sum_{i} \lambda_{i} v_{i} v_{i}^{\top},
+\]
+
+where:
+
+- $\lambda_{i}$ are the eigenvalues,
+- $v_{i}$ are the corresponding eigenvectors (which lie in the spaces corresponding to the irreducible representations),
+- $v_{i} v_{i}^{\top}$ is the outer product of the eigenvector $v_{i}$ with itself.
+
+The eigenvectors $v_{i}$ are related to the characters of the group $G$.
+Specifically, the characters of irreducible representations of $G$ help determine the eigenvalues of $A$.
+If $\chi_{\rho}$ denotes the character of the irreducible representation $\rho$, then the eigenvalues are given by:
+
+\[
+\lambda_{\rho} = \frac{1}{|G|} \sum_{g \in G} \chi_{\rho}(g) A(g),
+\]
+
+where $A(g)$ is the action of $g$ as represented in the adjacency matrix.
 
@@
 
+\section*{Quantum Hartley Transform (QHT)}
+
+The \textbf{Quantum Hartley Transform (QHT)} is a linear unitary transform that operates on quantum states. It transforms the basis states \( |x\rangle \) as follows:
+\[
+|x\rangle \xrightarrow{\text{QHT}} \frac{1}{\sqrt{N}} \sum_{k=0}^{N-1} \text{cas}\left(\frac{2\pi x k}{N}\right) |k\rangle
+\]
+where:
+\begin{itemize}
+    \item \( x \) and \( k \) are integers in \( \{0, 1, \dots, N-1\} \),
+    \item \( \text{cas}(x) = \cos(x) + \sin(x) \),
+    \item \( N \) is the dimension of the transform, typically \( 2^n \) for \( n \)-qubit systems.
+\end{itemize}
+
+For a quantum state \( |\psi\rangle \) in an \( N \)-dimensional Hilbert space, represented as:
+\[
+|\psi\rangle = \sum_{x=0}^{N-1} \psi_x |x\rangle,
+\]
+the QHT transforms the state into:
+\[
+|\psi'\rangle = \text{QHT} |\psi\rangle = \frac{1}{\sqrt{N}} \sum_{k=0}^{N-1} \left( \sum_{x=0}^{N-1} \psi_x \, \text{cas}\left(\frac{2\pi x k}{N}\right) \right) |k\rangle.
+\]
+
+\subsection*{Properties of the QHT}
+\begin{enumerate}
+    \item \textbf{Unitary Transformation}: The QHT matrix \( U_{\text{QHT}} \) is unitary:
+    \[
+    U_{\text{QHT}} U_{\text{QHT}}^\dagger = I,
+    \]
+    preserving quantum state normalization.
+    \item \textbf{Symmetry}: The QHT is symmetric because \( \text{cas}(x) = \text{cas}(-x) \).
+    \item \textbf{Efficient Implementation}: Like the Quantum Fourier Transform (QFT), the QHT can be implemented with \( O(\log^2 N) \) gates for \( N = 2^n \).
+\end{enumerate}
+
+\subsection*{Comparison with the Quantum Fourier Transform (QFT)}
+The QFT and QHT differ in their transformation kernels:
+\begin{itemize}
+    \item \textbf{QFT}:
+    \[
+    |x\rangle \xrightarrow{\text{QFT}} \frac{1}{\sqrt{N}} \sum_{k=0}^{N-1} e^{2\pi i x k / N} |k\rangle.
+    \]
+    \item \textbf{QHT}:
+    \[
+    |x\rangle \xrightarrow{\text{QHT}} \frac{1}{\sqrt{N}} \sum_{k=0}^{N-1} \left[\cos\left(\frac{2\pi x k}{N}\right) + \sin\left(\frac{2\pi x k}{N}\right)\right] |k\rangle.
+    \]
+\end{itemize}
+
+\subsection*{Applications of the QHT}
+\begin{itemize}
+    \item \textbf{Signal Processing}: Analysis of real-valued signals in quantum systems.
+    \item \textbf{Quantum Algorithms}: Used in problems where real and symmetric basis representations simplify computations.
+    \item \textbf{Data Compression}: Efficient representation of signals with high symmetry.
+\end{itemize}
+
 \bibliographystyle{plain}

### 2025-01-27 main.tex
new commit

@@
 \subsection*{Quantum Gates and Circuits}
-Quantum gates are the operational primitives of quantum computation. They manipulate qubits by altering their states in a manner consistent with quantum mechanics. Examples include:
-\begin{itemize}
-    \item \textbf{Hadamard Gate ($H$)}: Creates superposition from a basis state.
-    \item \textbf{Pauli Gates ($X, Y, Z$)}: Rotate qubit states around different axes.
-    \item \textbf{CNOT Gate}: Entangles two qubits by flipping the second qubit based on the state of the first.
-\end{itemize}
-A sequence of quantum gates forms a \textit{quantum circuit}, analogous to classical logic circuits but with exponentially richer possibilities due to quantum parallelism.
+
+Quantum logic gates are the fundamental building blocks of quantum circuits, manipulating qubits—the basic units of quantum information.
+Unlike classical logic gates, quantum gates are reversible and represented by unitary matrices, ensuring the preservation of quantum information.
+
+\subsection*{Key Quantum Logic Gates}
+
+\subsubsection*{1. Pauli-X Gate (NOT Gate)}
+\textbf{Operation:} Flips the state of a qubit from $|0\rangle$ to $|1\rangle$ and vice versa. \\
+\textbf{Matrix Representation:}
+\[
+X = 
+\begin{bmatrix}
+0 & 1 \\
+1 & 0
+\end{bmatrix}
+\]
+
+\subsubsection*{2. Hadamard Gate (H Gate)}
+\textbf{Operation:} Creates a superposition state, transforming $|0\rangle$ into $\frac{|0\rangle + |1\rangle}{\sqrt{2}}$ and $|1\rangle$ into $\frac{|0\rangle - |1\rangle}{\sqrt{2}}$. \\
+\textbf{Matrix Representation:}
+\[
+H = \frac{1}{\sqrt{2}}
+\begin{bmatrix}
+1 & 1 \\
+1 & -1
+\end{bmatrix}
+\]
+
+\subsubsection*{3. Controlled-NOT Gate (CNOT Gate)}
+\textbf{Operation:} A two-qubit gate that flips the state of the target qubit if the control qubit is in the state $|1\rangle$. \\
+\textbf{Matrix Representation:}
+\[
+CNOT =
+\begin{bmatrix}
+1 & 0 & 0 & 0 \\
+0 & 1 & 0 & 0 \\
+0 & 0 & 0 & 1 \\
+0 & 0 & 1 & 0
+\end{bmatrix}
+\]
+
+\subsubsection*{4. Toffoli Gate (CCNOT Gate)}
+\textbf{Operation:} A three-qubit gate that flips the state of the target qubit if both control qubits are in the state $|1\rangle$. \\
+\textbf{Matrix Representation:}
+\[
+CCNOT =
+\begin{bmatrix}
+1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 \\
+0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 \\
+0 & 0 & 0 & 1 & 0 & 0 & 0 & 0 \\
+0 & 0 & 0 & 0 & 1 & 0 & 0 & 0 \\
+0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 \\
+0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 \\
+0 & 0 & 0 & 0 & 0 & 0 & 1 & 0
+\end{bmatrix}
+\]
+
+\subsection*{Universal Gates}
+A set of gates is considered \textbf{universal} if any unitary operation can be approximated to arbitrary precision using a sequence of gates from this set.
+For example, single-qubit rotation gates combined with the CNOT gate form a universal set, enabling the construction of any quantum algorithm.
 
@@
 \section*{Continuous-Time Quantum Walks}
-A \textit{continuous-time quantum walk} is defined on a graph, where the evolution of the system is governed by a differential equation similar to the Schrödinger equation:
+
+Classical continuous-time random walks (Markov chains) are a foundational concept in stochastic processes, where time is treated as a continuous variable.
+In this framework, a walker moves from one vertex of a graph to an adjacent vertex at any time, with probabilities evolving over time.
+The probability of the walker being at a vertex can be visualized as a liquid seeping from one vertex to its neighbors.
+Initially, the walker is most likely to be found at the starting vertex, but as time progresses, the probability shifts to neighboring vertices.
+This dynamic is governed by a constant transition rate \( \gamma \), uniform across all vertices and time.
+
+To model this mathematically, the probability of transitioning from one vertex to another in an infinitesimal time interval \( \Delta t \) is proportional to \( \gamma \Delta t \).
+For a vertex \( x_j \) with degree \( d_j \) (the number of neighboring vertices), the probability of the walker staying on \( x_j \) is
+
 \[
-i\frac{d}{dt}q(t) = Hq(t),
-\]
-where the Hamiltonian \( H \) is an \( N \times N \) Hermitian matrix, with \( H_{jk} = 0 \) if and only if vertices \( j \) and \( k \) are not connected.
-The vector \( q(t) \in \mathbb{C}^N \) contains the complex amplitudes corresponding to each vertex.
-Notably, the state space for the quantum walk is the same as that for the corresponding classical random walk.
-
-One important matrix associated with the graph \( G \) is the \textit{Laplacian matrix}, defined as:
-\[
-L_{jk} =
-\begin{cases}
--\text{deg}(j) & \text{if } j = k, \\
-1 & \text{if } (j, k) \in E, \\
-0 & \text{otherwise}.
-\end{cases}
+1 - d_j \gamma \Delta t,
 \]
 
-The continuous-time random walk on \( G \) is then defined as the solution to the differential equation:
+while the probability of transitioning to a neighboring vertex is
+
 \[
-\frac{d}{dt} p_j(t) = \sum_{k \in V} L_{jk} p_k(t),
-\]
-where \( p_j(t) \) represents the probability at vertex \( j \) at time \( t \). The solution to this equation can be expressed in closed form as:
-\[
-p(t) = e^{Lt} p(0),
-\]
-where \( L \) is the Laplacian matrix and \( p(0) \) is the initial condition.
-
-This equation closely resembles the Schrödinger equation, but it lacks the factor \( i \).
-By adding this factor and redefining the probabilities \( p_j(t) \) as quantum amplitudes \( q_j(t) = \langle j|\psi(t)\rangle \) (where \( \{ |j\rangle : j \in V \} \) is an orthonormal basis for the Hilbert space), we obtain:
-\[
-i \frac{d}{dt} q_j(t) = \sum_{k \in V} L_{jk} q_k(t),
-\]
-which is the Schrödinger equation with the Laplacian of the graph as the Hamiltonian. Since the Laplacian is a Hermitian operator, these dynamics preserve normalization:
-\[
-\frac{d}{dt} \sum_{j \in V} |q_j(t)|^2 = 0.
+\gamma \Delta t.
 \]
 
-The solution to this differential equation is:
+The evolution of probabilities over time is captured by the transition matrix \( M(t) \), where the entry \( M_{ij}(t) \) represents the probability of transitioning from vertex \( x_j \) to vertex \( x_i \) in time \( t \).
+The dynamics of the system are described by a differential equation derived from the transition matrix and an auxiliary matrix \( H \), known as the generating matrix.
+This equation,
+
 \[
-|\psi(t)\rangle = e^{-iLt} |\psi(0)\rangle.
+\frac{dM(t)}{dt} = -H M(t),
 \]
 
-A continuous-time quantum walk can also be defined using any Hermitian Hamiltonian that respects the structure of \( G \).
+has a solution expressed as
 
-\subsection*{Differences from Classical Random Walks}
-The evolution of a quantum walk, governed by a Hamiltonian, dictates state transitions over time while preserving normalization.
-This contrasts with classical random walks, which involve probabilistic transitions.
-Moreover, the wave nature of quantum mechanics introduces interference effects, enabling faster exploration of graphs compared to classical methods.
-For instance, on one-dimensional graphs, a classical random walk progresses at a rate proportional to the square root of time, while a quantum walk progresses linearly with time due to the wave-like propagation of quantum states.
+\[
+M(t) = e^{-Ht},
+\]
+
+which allows for the computation of probability distributions at any given time. The solution is verified using the Taylor series expansion of the exponential function.
+
+The passage from classical continuous-time Markov chains to quantum walks involves a standard quantization process.
+In classical random walks, probabilities evolve via the transition matrix \( M \).
+In contrast, the quantization process replaces the vector of probabilities with a state vector (probability amplitudes) and the non-unitary transition matrix with a unitary evolution operator, as required by quantum mechanics.
+This involves transforming the generating matrix \( H \) into a Hermitian operator and then constructing a unitary operator
+
+\[
+U(t) = e^{-iHt}
+\]
+
+by multiplying \( H \) with the imaginary unit \( i \).
+
+In a continuous-time quantum walk, the quantum state evolves over time according to the unitary operator \( U(t) \).
+If the initial state of the system is \( |\psi(0)\rangle \), the state at time \( t \) is given by
+
+\[
+|\psi(t)\rangle = U(t) |\psi(0)\rangle.
+\]
+
+The probability distribution for observing the walker at a specific vertex \( k \) is computed as
+
+\[
+p_k = |\langle k | \psi(t) \rangle|^2,
+\]
+
+where \( |k\rangle \) represents the state corresponding to vertex \( k \).
+
+The continuous-time quantum walk introduces several key differences from its classical counterpart.
+Unlike classical random walks, which rely on probabilities, quantum walks involve probability amplitudes, enabling interference effects.
+These effects allow quantum walks to explore the graph more efficiently, leading to applications in quantum algorithms with speedups over classical approaches.
+Additionally, the transition matrix in classical random walks is replaced with a Hermitian operator in the quantum case, ensuring unitary evolution.
+
+*********Examples and further discussions here*********
+
+% Overall, the transition from classical continuous-time Markov chains to continuous-time quantum walks highlights fundamental differences between classical and quantum dynamics, particularly the role of interference and the constraints of unitary evolution in quantum systems.
+These differences underscore the potential of quantum walks in quantum computing and algorithm design.
 
 \section*{Discrete-Time Quantum Walks}
-\textit{Discrete-time quantum walks}, though more complex to define, provide a convenient framework for certain quantum algorithms, particularly quantum search algorithms.
+*******************
+The discrete-time coined quantum walk (DTQW) is a quantum analog of classical random walks, leveraging the principles of quantum mechanics to achieve unique computational and dynamical properties.
+It is defined on a graph or lattice, with the walker's state described by both its position and an internal "coin" state.
+The walker's position \( n \) on a one-dimensional lattice (line) is represented by a vector \( |n\rangle \) in an infinite-dimensional Hilbert space \( \mathcal{H}_P \), where the computational basis for \( \mathcal{H}_P \) is
 
-In the simplest classical discrete-time random walk on a graph \( G \), at each time step, the walker moves from a given vertex to one of its neighbors with equal probability.
-This process is described by a \( |V| \times |V| \) matrix \( M \), where:
 \[
-M_{jk} = 
-\begin{cases} 
-\frac{1}{\text{deg}(k)} & \text{if } (j, k) \in E, \\
-0 & \text{otherwise}.
-\end{cases}
-\]
-The initial probability distribution \( p \) over the vertices updates to \( p' = M p \) after one step.
-
-For quantum walks, maintaining unitarity requires a \textit{coin operator} \( C \) to determine the direction of the next step.
-A common choice for the coin operator is the Grover diffusion operator, defined as:
-\[
-C := \sum_{j \in V}\ket{j}\bra{j} \otimes (2\ket{\partial_j}\bra{\partial_j} - I),
-\]
-where:
-\[
-\ket{\partial_j} := \frac{1}{\sqrt{\deg(j)}} \sum_{k:(j,k) \in E}\ket{k},
-\]
-denotes the superposition of the neighboring vertices of \( \ket{j} \), and \( I \) is the identity matrix.
-
-One step of the discrete-time quantum walk is described by the unitary operator \( SC \), where \( S \) is the swap operator:
-\[
-S = \sum_{(j,k) \in E}\ket{j,k}\bra{k,j}.
+\{ |n\rangle : n \in \mathbb{Z} \}.
 \]
 
+The walker's internal state, or "coin," is represented by a two-dimensional Hilbert space \( \mathcal{H}_C \) with basis states \( |0\rangle \) and \( |1\rangle \).
+The coin state determines the direction of the walker's movement, and the total state of the system resides in the tensor product space
+
+\[
+\mathcal{H} = \mathcal{H}_C \otimes \mathcal{H}_P,
+\]
+
+combining the coin and position spaces.
+
+The dynamics of the walk are governed by two key operators: the coin operator and the shift operator.
+The coin is represented by a unitary matrix \( C \) acting on \( \mathcal{H}_C \).
+Common choices include the Hadamard matrix, which creates superpositions of the coin states.
+The Hadamard coin operator \( H \) is defined as
+
+\[
+H = \frac{1}{\sqrt{2}} \begin{pmatrix} 1 & 1 \\ 1 & -1 \end{pmatrix}.
+\]
+
+The shift operator \( S \) moves the walker based on the coin state.
+For example, if the coin state is \( |0\rangle \), the walker moves to \( |n+1\rangle \), and if the coin state is \( |1\rangle \), the walker moves to \( |n-1\rangle \).
+The shift operator is explicitly given by
+
+\[
+S = \sum_{n} |n+1\rangle \langle n| \otimes |0\rangle \langle 0| + |n-1\rangle \langle n| \otimes |1\rangle \langle 1|.
+\]
+
+The evolution of the system is described by the unitary operator
+
+\[
+U = S \cdot (I \otimes C),
+\]
+
+where \( I \) is the identity operator on \( \mathcal{H}_P \). The state of the walker at time \( t+1 \) is given by
+
+\[
+|\psi(t+1)\rangle = U |\psi(t)\rangle.
+\]
+
+Consider a quantum walk on a one-dimensional lattice.
+The walker's state evolves in superposition, allowing it to explore multiple paths simultaneously.
+Interference between these paths leads to faster spreading compared to classical random walks.
+
+Key features of DTQW include superposition, where the walker exists in a superposition of positions and coin states, enabling parallel exploration of multiple paths; interference, where quantum interference enhances or suppresses certain paths, leading to non-classical behavior; and quadratic speedup, where quantum walks spread faster than classical random walks, often quadratically, which is advantageous for algorithmic applications.
+
+DTQWs are used in quantum algorithms, such as quantum search and graph traversal, and in simulating physical systems like energy transport in photosynthesis.
+They also serve as a framework for universal quantum computation.
+The discrete-time quantum walk is a powerful tool in quantum computing, offering a rich interplay between quantum mechanics and graph theory.
+Its ability to exploit superposition and interference enables applications in algorithm design, simulation, and computation, making it a cornerstone of quantum information science.
+
+*********Examples and further discussions here*********
+
 \subsection*{Comparison of Models}
-The continuous-time model is simpler to define and analyze, often leading to exponential speedups under specific conditions, such as graphs with small maximum degrees.
-However, discrete-time quantum walks are easier to implement using quantum circuits, making them more practical in many applications.
-For example, while continuous-time models may struggle with certain problems like \textit{element distinctness}, discrete-time models handle them more effectively.
+
+From a computational standpoint, both continuous-time and discrete-time quantum walks offer distinct advantages.
+The continuous-time quantum walk is often considered more natural because it does not require expanding the state space, making it simpler to define and typically easier to analyze.
+For example, while the exponential speedup demonstrated by continuous-time quantum walks is widely believed to extend to the discrete-time model, the dynamics of the latter are more complex.
+To date, no rigorous analysis has been provided to confirm this extension.
+
+In contrast, the discrete-time quantum walk is generally more straightforward to implement using quantum circuits.
+Implementing continuous-time quantum walks, however, often relies on techniques that require the graph's maximum degree to be small.
+This constraint makes certain algorithms challenging to replicate using continuous-time quantum walks.
+Therefore, while continuous-time quantum walks excel in simplicity and analytical tractability, discrete-time quantum walks offer greater practicality and ease of implementation in quantum computing applications.
 

### 2025-01-30 main.tex
new commit

@@
 
-\subsection*{Equivalence Relations Induced by Group Actions}
+\section*{Groups and Characters}
 
-The orbits of a group action define an equivalence relation on \( X \), where \( x \sim y \) if there exists \( g \in G \) such that \( g \cdot x = y \).
+Let \( G \) be an abelian group. A function
+
+\[
+\chi: G \to \mathbb{C}^{\times}
+\]
+
+that maps \( G \) to the group of nonzero complex numbers
+
+\[
+\mathbb{C}^{\times} = \mathbb{C} \setminus \{0\}
+\]
+
+is called a \textbf{character} of \( G \) if it is a \textbf{group homomorphism}. That is, for all \( g_1, g_2 \in G \), the function satisfies:
+
+\[
+\chi(g_1 g_2) = \chi(g_1) \chi(g_2).
+\]
+
+\section*{Character Values for Finite Groups}
+
+If \( \chi \) is a character of a finite group (or more generally, a torsion group) \( G \), then each function value \( \chi(g) \) is a root of unity.
+This follows because, for each \( g \in G \), there exists some integer \( k \in \mathbb{N} \) such that:
+
+\[
+g^k = e.
+\]
+
+Applying \( \chi \) to both sides, we obtain:
+
+\[
+\chi(g)^k = \chi(g^k) = \chi(e) = 1.
+\]
+
+\section*{Number of Characters in a Finite Abelian Group}
+
+A \textbf{finite abelian group} of order \( n \) has exactly \( n \) distinct characters, denoted by:
+
+\[
+\chi_1, \chi_2, \dots, \chi_n.
+\]
+
+The function \( \chi_1 \), defined by:
+
+\[
+\chi_1(g) = 1, \quad \forall g \in G,
+\]
+
+is called the \textbf{principal character} of \( G \). The remaining \( n-1 \) characters are referred to as \textbf{non-principal characters}.
+
+\section*{Character Group}
+
+If \( G \) is an abelian group, the set of characters \( \{\chi_k\} \) forms an abelian group under pointwise multiplication, defined as:
+
+\[
+(\chi_j \chi_k)(g) = \chi_j(g) \chi_k(g), \quad \forall g \in G.
+\]
+
+This group is called the \textbf{character group} of \( G \) and is often denoted as $\hat{G}$.  
+The \textbf{identity element} of \( \hat{G} \) is the principal character \( \chi_1 \), and the \textbf{inverse} of a character \( \chi_k \) is its reciprocal:
+
+\[
+(\chi_k)^{-1} = \frac{1}{\chi_k}.
+\]
+
+If \( G \) is finite of order \( n \), then the character group \( \hat{G} \) is also of order \( n \). In this case, since
+
+\[
+|\chi_k(g)| = 1, \quad \forall g \in G,
+\]
+
+the inverse of a character is simply its \textbf{complex conjugate}:
+
+\[
+\chi_k^{-1}(g) = \overline{\chi_k(g)}.
+\]
+
+\section{Quantum Fourier Transform}
+
+The \textbf{Quantum Fourier Transform (QFT)} is one of the most fundamental unitary transformations in quantum computing.
+It plays a crucial role in quantum algorithms, including Shor’s algorithm for integer factorization and quantum phase estimation.
+The QFT is the quantum analog of the classical discrete Fourier transform (DFT) but operates on quantum states, enabling efficient quantum computation of Fourier coefficients.
+
+In this section, we discuss the QFT in the context of abelian groups, with a focus on its implementation over \( \mathbb{Z}_{2^n} \), one of the most commonly used finite groups in quantum algorithms, including quantum walks.
+
+\section{Quantum Fourier Transform Over an Abelian Group}
+
+Let \( G \) be an abelian group. The \textbf{Quantum Fourier Transform} over \( G \) is defined as:
+
+\[
+F_G = \frac{1}{\sqrt{|G|}} \sum_{x \in G} \sum_{y \in \hat{G}} \chi_y(x) | y \rangle \langle x |
+\]
+
+where:
 
 \begin{itemize}
-    \item \textbf{Equivalence Classes}: The orbits of the action.
-    \item \textbf{Quotient Set}: The set of orbits, denoted \( X/G \).
+    \item \( \hat{G} \) is a complete set of characters of \( G \).
+    \item \( \chi_y(x) \) denotes the \( y \)th character of \( G \), evaluated at \( x \).
+    \item \( |x\rangle \) and \( |y\rangle \) are quantum states corresponding to elements of \( G \) and its dual group \( \hat{G} \).
 \end{itemize}
+
+Since \( G \) and \( \hat{G} \) are isomorphic, it is often useful to label the elements of \( \hat{G} \) using elements of \( G \).
+The unitary nature of the QFT follows from the \textbf{orthogonality of characters}.
+
+\subsection{QFT Over \( \mathbb{Z}_{2^n} \)}
+
+The QFT over \( G = \mathbb{Z}_{2^n} \) is defined as:
+
+\[
+F_{\mathbb{Z}_{2^n}} = \frac{1}{\sqrt{2^n}} \sum_{x,y \in \mathbb{Z}_{2^n}} \omega_{2^n}^{xy} | y \rangle \langle x |
+\]
+
+where:
+
+\[
+\omega_m = e^{2\pi i / m}
+\]
+
+is the \textbf{primitive} \( m \)th root of unity. This transformation maps an input basis state \( |x\rangle \) as follows:
+
+\[
+| x \rangle \to \frac{1}{\sqrt{2^n}} \sum_{y \in \mathbb{Z}_{2^n}} \omega_{2^n}^{xy} | y \rangle.
+\]
+
+This equation represents a \textbf{linear transformation} where each input state \( |x\rangle \) is mapped to a superposition of all basis states, weighted by phase factors.
+
+\subsection{Binary Representation and QFT Implementation}
+
+To implement this transformation efficiently, it is useful to express \( x \) and \( y \) in binary form:
+
+\[
+x = x_{n-1} x_{n-2} \dots x_1 x_0.
+\]
+
+The exponent in the Fourier transform formula can then be rewritten using its binary expansion:
+
+\[
+\omega_{2^n}^{xy} = e^{2\pi i x \sum_{k=0}^{n-1} y_k 2^k / 2^n}.
+\]
+
+Rewriting the transformation explicitly:
+
+\[
+| x \rangle \to \frac{1}{\sqrt{2^n}} \sum_{y \in \mathbb{Z}_{2^n}} e^{2\pi i x \sum_{k=0}^{n-1} y_k 2^k / 2^n} | y \rangle.
+\]
+
+This can be decomposed into a \textbf{tensor product of single-qubit states}, where each qubit state depends on the least significant bits of \( x \):
+
+\[
+\bigotimes_{k=0}^{n-1} | z_k \rangle.
+\]
+
+where
+
+\[
+| z_k \rangle = \frac{1}{\sqrt{2}} ( | 0 \rangle + e^{2\pi i ( x_0 2^{-n+k} + x_1 2^{-n+k+1} + \dots + x_{n-1} 2^{-1} )} | 1 \rangle ).
+\]
+
+This decomposition highlights the \textbf{hierarchical dependence of qubits on the binary digits of \( x \)}, making it possible to implement the QFT using \textbf{Hadamard gates and controlled phase shift gates}.
 

### 2025-01-30 main.tex
new commit

@@
 
+\section{Abelian Groups}
+
+An \textbf{abelian group} (also called a \textbf{commutative group}) is a set \( G \) equipped with a binary operation \( \cdot \) (usually written as addition \( + \) or multiplication \( \cdot \)) that satisfies the following four group axioms, along with an additional \textbf{commutativity} property.
+
+\subsection{Axioms of an Abelian Group}
+A set \( G \) with a binary operation \( \cdot \) is an \textbf{abelian group} if the following conditions hold:
+
+\begin{enumerate}
+    \item \textbf{Closure}:  
+    For all \( a, b \in G \), the operation \( a \cdot b \) produces another element in \( G \):
+
+    \[
+    a \cdot b \in G.
+    \]
+
+    \item \textbf{Associativity}:  
+    For all \( a, b, c \in G \), the operation satisfies:
+
+    \[
+    (a \cdot b) \cdot c = a \cdot (b \cdot c).
+    \]
+
+    \item \textbf{Identity Element}:  
+    There exists an element \( e \in G \) such that for all \( a \in G \):
+
+    \[
+    e \cdot a = a \cdot e = a.
+    \]
+
+    This element \( e \) is called the \textbf{identity element}.
+
+    \item \textbf{Inverse Element}:  
+    For every element \( a \in G \), there exists an element \( a^{-1} \in G \) such that:
+
+    \[
+    a \cdot a^{-1} = a^{-1} \cdot a = e.
+    \]
+
+    \item \textbf{Commutativity (Abelian Property)}:  
+    For all \( a, b \in G \), the operation is \textbf{commutative}:
+
+    \[
+    a \cdot b = b \cdot a.
+    \]
+
+\end{enumerate}
+
+Since abelian groups satisfy commutativity, they allow more flexible mathematical operations and structure, leading to applications in algebra, number theory, and topology.
+
+\subsection{Characters of Abelian Groups}
 Let \( G \) be an abelian group. A function
@@
 
-that maps \( G \) to the group of nonzero complex numbers
-
-\[
-\mathbb{C}^{\times} = \mathbb{C} \setminus \{0\}
-\]
-
-is called a \textbf{character} of \( G \) if it is a \textbf{group homomorphism}. That is, for all \( g_1, g_2 \in G \), the function satisfies:
+that maps \( G \) to the group of nonzero complex numbers  \(\mathbb{C}^{\times} = \mathbb{C} \setminus \{0\}\), is called a \textbf{character} of \( G \) if it is a \textbf{group homomorphism}.
+That is, for all \( g_1, g_2 \in G \), the function satisfies:
 

### 2025-02-06 main.tex
new commit

@@
 
+\subsection*{Cayley graphs}
+
+A Cayley graph is a graphical representation of a group based on a chosen set of generators.
+It is widely used in algebra, combinatorics, and theoretical computer science to study group structures and their applications in network theory, quantum computing, and cryptography.
+
+\section*{Definition of Cayley Graphs}
+
+A \textit{Cayley graph} is a graph that encodes the structure of a group with respect to a chosen generating set.
+Formally, let \( G \) be a group and \( S \) be a subset of \( G \) that serves as a generating set, meaning every element of \( G \) can be expressed as a finite product of elements from \( S \).
+The Cayley graph \( \Gamma(G, S) \) is defined as follows.
+The vertex set of the graph consists of the elements of \( G \), where each vertex corresponds to a unique group element.
+The edge set is constructed by drawing a directed edge from vertex \( g \) to vertex \( gs \) for each \( g \in G \) and \( s \in S \).
+If the generating set \( S \) is symmetric, meaning that whenever \( s \in S \), its inverse \( s^{-1} \) is also in \( S \), then the Cayley graph is undirected; otherwise, it is a directed graph.
+For example, For the cyclic group \( G = \mathbb{Z}_n = \{0,1,2,\dots, n-1\} \) with the generating set \( S = \{\pm 1\} \), the Cayley graph forms a cycle graph.
+In this graph, each vertex \( j \) is connected to \( j+1 \mod n \) and \( j-1 \mod n \), creating a cyclic structure.
+
+\section*{Quantum walks on Cayley graphs}
+Quantum walks on Cayley graphs play a crucial role in quantum computing, quantum search algorithms, and mathematical physics due to their deep connection with group theory and symmetry.
+The structured nature of Cayley graphs, derived from group elements and generators, ensures uniform exploration of the graph, leading to faster propagation compared to classical random walks.
+This property is particularly valuable in quantum algorithms, where quantum walks on Cayley graphs have been used to achieve exponential speedups in search and optimization problems.
+Additionally, their spectral properties, determined by the adjacency matrix and Fourier analysis on groups, provide insights into mixing times, state localization, and quantum transport phenomena.
+These advantages make Cayley graphs an essential framework for designing scalable and efficient quantum algorithms, offering a powerful bridge between algebraic structures and quantum mechanics.
+
+\section*{Discrete-Time Quantum Walk on Cayley Graphs}
+
+A discrete-time quantum walk on a Cayley graph requires a coin operator to maintain unitary evolution.
+
+\subsection*{State Space}
+The Hilbert space of the quantum walk is:
+\[
+\mathcal{H} = \mathcal{H}_G \otimes \mathcal{H}_C,
+\]
+where:
+\begin{itemize}
+    \item \( \mathcal{H}_G \) is the space spanned by group elements (vertices).
+    \item \( \mathcal{H}_C \) is the coin space, which determines movement directions.
+\end{itemize}
+
+Each state is represented as:
+\[
+|\psi\rangle = \sum_{g \in G} \sum_{s \in S} \alpha_{g,s} |g\rangle \otimes |s\rangle,
+\]
+where \( |g\rangle \) is the vertex state and \( |s\rangle \) represents the coin state.
+
+\subsection*{Evolution Operators}
+\textbf{Coin Flip Operator (\( C \))}: This unitary operator acts on the coin space to create a superposition of movement directions. A common choice is the Grover or Hadamard operator.
+
+\textbf{Shift Operator (\( S \))}: Moves the walker according to the group structure:
+\[
+S |g\rangle \otimes |s\rangle = |gs\rangle \otimes |s\rangle.
+\]
+This means that if the walker is at vertex \( g \) with a coin state \( s \), it moves to \( gs \).
+
+\textbf{Full Step Evolution}:
+\[
+U = S (C \otimes I),
+\]
+where \( U \) is the total unitary evolution per step.
+
+The probability of finding the walker at a particular vertex \( g \) after \( t \) steps is given by:
+\[
+P(g, t) = \sum_{s \in S} |\langle g, s | \psi(t) \rangle |^2.
+\]
+
+\section*{Continuous-Time Quantum Walk on Cayley Graphs}
+
+A continuous-time quantum walk on a Cayley graph follows a different evolution, governed by the Hamiltonian.
+
+\subsection*{Hamiltonian and Evolution}
+The evolution of the quantum walk is determined by the Schrödinger equation:
+\[
+i \frac{d}{dt} |\psi(t)\rangle = H |\psi(t)\rangle.
+\]
+Here, the Hamiltonian \( H \) is usually chosen as:
+\[
+H = A(\Gamma(G,S)),
+\]
+where \( A \) is the adjacency matrix of the Cayley graph:
+
+\[
+A_{g,h} =
+\begin{cases}
+1, & \text{if } h = gs \text{ for some } s \in S, \\
+0, & \text{otherwise}.
+\end{cases}
+\]
+ Alternatively, the Laplacian \( L \) can be used:
+\[
+H = L = D - A,
+\]
+where \( D \) is the degree matrix:
+
+\[
+D_{ij} =
+\begin{cases}
+\deg(v_i), & \text{if } i = j, \\
+0, & \text{otherwise}.
+\end{cases}
+\]
+
+Here, \( \deg(v_i) \) is the degree of vertex \( v_i \), which is the number of edges connected to \( v_i \).
+
+The solution to the quantum walk is given by:
+\[
+|\psi(t)\rangle = e^{-i H t} |\psi(0)\rangle.
+\]
+This means the probability amplitude at a vertex \( g \) spreads over time according to the unitary evolution operator \( e^{-i H t} \).
+
+\section*{Spectral Decomposition of the Adjacency Matrix of a Cayley Graph}
+
+The spectral decomposition of the adjacency matrix of a Cayley graph involves expressing the adjacency matrix in terms of its eigenvalues and eigenvectors.
+This decomposition is particularly useful for understanding the behavior of quantum walks, graph connectivity, expansion properties, and random walks on the graph.
+
+Spectral decomposition expresses \( A \) in terms of its eigenvalues and eigenvectors:
+\[
+A = \sum_{j} \lambda_j P_j,
+\]
+where:
+\begin{itemize}
+    \item \( \lambda_j \) are the eigenvalues of \( A \).
+    \item \( P_j \) are the projection matrices onto the corresponding eigenspaces.
+\end{itemize}
+
+Since Cayley graphs are highly structured, their eigenvalues and eigenvectors often have explicit formulas based on group representation theory and Fourier analysis on groups.
+
+For a finite group \( G \), the Fourier transform on groups helps diagonalize \( A \). The eigenvalues of \( A \) are computed as:
+\[
+\lambda_\rho = \sum_{s \in S} \rho(s),
+\]
+where \( \rho \) is an irreducible representation of \( G \). The set of eigenvalues depends on the sum over generators in the group's representation.
+
+For Abelian groups (e.g., \( \mathbb{Z}_n \)), the irreducible representations are characters, simplifying the spectral decomposition.
+
+For non-Abelian groups, the decomposition involves matrix-valued representations.
+
+\subsection*{Example: Cyclic Group \( \mathbb{Z}_n \)}
+
+Consider the Cayley graph of \( \mathbb{Z}_n \) with generator set \( S = \{\pm 1\} \), which forms a cycle graph. The adjacency matrix is:
+\[
+A_{jk} =
+\begin{cases}
+1, & \text{if } k = j \pm 1 \mod n, \\
+0, & \text{otherwise}.
+\end{cases}
+\]
+
+Its eigenvalues are:
+\[
+\lambda_k = 2\cos\left(\frac{2\pi k}{n}\right),
+\]
+with eigenvectors given by the discrete Fourier transform (DFT) basis:
+\[
+\psi_k(j) = e^{\frac{2\pi i k j}{n}}.
+\]
+
+This result generalizes to other Abelian groups, where the eigenvectors are given by the Fourier basis of the group.
+
 \subsection*{Quantum walks from Group Actions}
@@
 where $A(g)$ is the action of $g$ as represented in the adjacency matrix.
+
+\[
+*************Further discussions Here***************
+\]
 

### 2025-02-17 main.tex
new commit

@@
 
+\section{Applicaions}
 \section{Quantum Money}
@@
 
-\section*{How Quantum Money Works}
-At its core, quantum money relies on two key principles of quantum mechanics: the \textit{no-cloning theorem} and the \textit{observer effect}.
-
-\subsection*{Encoding Information in Quantum States}
-\begin{itemize}
-    \item Each quantum bill contains a unique quantum state, such as a set of qubits encoded in superposition.
-    \item These states are generated and stored by the issuing authority (e.g., a central bank) using a secret algorithm.
-\end{itemize}
-
-\subsection*{Verification Process}
-\begin{itemize}
-    \item The issuing authority also generates a verification protocol, allowing a legitimate quantum bill to be authenticated.
-    \item When a user presents a quantum bill for verification, the authority measures the encoded quantum states using the pre-determined protocol.
-    \item If the measured states align with the expected values, the bill is deemed valid.
-\end{itemize}
-
-\subsection*{Unforgeability}
-\begin{itemize}
-    \item Due to the \textit{no-cloning theorem}, it is impossible to copy an unknown quantum state without altering it.
-    \item Any attempt to measure or duplicate the quantum state results in a disturbance detectable during verification.
-\end{itemize}
-
-\section*{Key Principles Underpinning Quantum Money}
-\begin{enumerate}
-    \item \textbf{No-Cloning Theorem:} The no-cloning theorem states that an unknown quantum state cannot be perfectly copied.
+% \section*{How Quantum Money Works}
+% At its core, quantum money relies on two key principles of quantum mechanics: the \textit{no-cloning theorem} and the \textit{observer effect}.
+
+% \subsection*{Encoding Information in Quantum States}
+% \begin{itemize}
+%     \item Each quantum bill contains a unique quantum state, such as a set of qubits encoded in superposition.
+%     \item These states are generated and stored by the issuing authority (e.g., a central bank) using a secret algorithm.
+% \end{itemize}
+
+% \subsection*{Verification Process}
+% \begin{itemize}
+%     \item The issuing authority also generates a verification protocol, allowing a legitimate quantum bill to be authenticated.
+%     \item When a user presents a quantum bill for verification, the authority measures the encoded quantum states using the pre-determined protocol.
+%     \item If the measured states align with the expected values, the bill is deemed valid.
+% \end{itemize}
+
+% \subsection*{Unforgeability}
+% \begin{itemize}
+%     \item Due to the \textit{no-cloning theorem}, it is impossible to copy an unknown quantum state without altering it.
+%     \item Any attempt to measure or duplicate the quantum state results in a disturbance detectable during verification.
+% \end{itemize}
+
+% \section*{Key Principles Underpinning Quantum Money}
+% \begin{enumerate}
+%     \item \textbf{No-Cloning Theorem:} The no-cloning theorem states that an unknown quantum state cannot be perfectly copied.
 This makes quantum money inherently secure, as counterfeiters cannot reproduce the quantum states encoded in legitimate currency.
-    \item \textbf{Measurement Disturbance:} Observing or measuring a quantum state generally alters it.
+%     \item \textbf{Measurement Disturbance:} Observing or measuring a quantum state generally alters it.
 This ensures that any unauthorized attempt to inspect the quantum money will render it invalid, as the encoded states will no longer match their original form.
-    \item \textbf{Randomness and Superposition:} Quantum money utilizes superposition to encode information.
+%     \item \textbf{Randomness and Superposition:} Quantum money utilizes superposition to encode information.
 For example, a single qubit in superposition may represent both $0$ and $1$ simultaneously until measured.
 The randomness of these states makes predicting or reproducing them without knowledge of the original encoding impossible.
-    \item \textbf{Entanglement (Optional Feature):} Some implementations of quantum money involve quantum entanglement, where pairs of quantum states are interconnected.
+%     \item \textbf{Entanglement (Optional Feature):} Some implementations of quantum money involve quantum entanglement, where pairs of quantum states are interconnected.
 Changes to one entangled state directly affect its pair, adding another layer of security against forgery.
-\end{enumerate}
+% \end{enumerate}
 
@@
 
-\section*{Challenges and Open Questions}
-\begin{enumerate}
-    \item \textbf{Practical Implementation:} Generating and maintaining stable quantum states in real-world conditions is technically challenging.
-Quantum systems are highly sensitive to environmental noise, requiring robust error-correction mechanisms.
-    \item \textbf{Scalability:} For quantum money to replace traditional systems, it must scale to accommodate billions of users and transactions.
-    \item \textbf{Theft and Security:} While quantum money cannot be forged, it can still be stolen, much like traditional physical or digital assets.
-Developing secure storage and transfer mechanisms is a priority.
-    \item \textbf{Centralized vs.
-Decentralized Systems:} Most current proposals involve a centralized authority for issuing and verifying quantum money.
-However, decentralized quantum money systems (akin to blockchain technology) are an area of active research.
-\end{enumerate}
-
-\section*{Applications Beyond Money}
-The principles underlying quantum money have broader applications, such as:
-\begin{itemize}
-    \item \textbf{Quantum Tokens:} Used in secure communication or access control.
-    \item \textbf{Quantum Cryptography:} Building secure voting systems or decentralized platforms.
-    \item \textbf{Quantum Key Distribution (QKD):} While distinct from quantum money, QKD relies on similar quantum principles to ensure the security of communication channels.
-\end{itemize}
-
-\section*{Conclusion}
-Quantum money represents a paradigm shift in secure transactions, leveraging the foundational principles of quantum mechanics to create currency that is inherently secure against forgery.
-While still a theoretical concept, advances in quantum technology and cryptography are rapidly bringing us closer to practical implementations.
-If realized, quantum money could redefine financial systems, offering unparalleled security and efficiency in the digital age.
-
-\section{Applicaions}
+\subsection{Quantum Money From Group Actions}
+A public-key quantum money scheme consists of two QPT algorithms: 
+\begin{itemize}
+\item $\gen(1^\lambda)$: This algorithm takes a security parameter $\lambda$ as input and outputs a pair $(s, \rho_s)$, where $s$ is a binary string called the serial number, and $\rho_s$ is a quantum state called the banknote.
+The pair $(s, \rho_s)$, or simply $\rho_s$, is sometimes denoted by $\$$.
+\item $\ver(s, \rho_s)$ This algorithm takes a serial number and an alleged banknote as input and outputs either $1$ (accept) or $0$ (reject).
+\end{itemize}
+
+The quantum money scheme is said to be \textit{correct} if genuine banknotes generated by $\gen$ are accepted by $\ver$ with high probability. More formally:
+\[ \Pr[\ver(s, \rho_s) = 1 : (s, \rho_s) \gets \gen(1^\lambda)] \ge 1 - \negl(\lambda). \]
+where the probability is taken over the randomness of $\gen$ and $\ver$.
+The scheme $(\gen, \ver)$ is said to be secure if, given a genuine bill $(s, \rho_s)$, no QPT algorithm $\mathcal{A}$ can produce two (possibly entangled) bills $(s, \rho_1)$ and $(s, \rho_2)$ that are both accepted by $\ver$ with non-negligible probability.
+More formally:
+\[ \Pr\left[ \ver(s, \rho_1) = \ver(s, \rho_2) = 1 : \substack{(s, \rho_s) \gets \gen(1^\lambda) \\ (\rho_1, \rho_2) \gets \mathcal{A}(s, \rho_s)} \right] \le \negl(\lambda). \]
+
+We now briefly outline the quantum money construction from \cite{zhandry2024quantum}, which is based on abelian group actions.
+Let $\{(G_\lambda, X_\lambda, *)\}_{\lambda \in J}$, where $J \subset \N$, be a collection of cryptographic group actions for abelian groups $G_\lambda$, and let $x_\lambda \in X_\lambda$ be a fixed element.
+The $\gen$ and $\ver$ algorithms are as follows:
+\begin{itemize}
+\item $\gen(1^\lambda)$. Begin with the state $\ket{0}\ket{x_\lambda}$, and apply the quantum Fourier transform over $G_\lambda$ to the first register producing the superposition
+    \[ \frac{1}{\sqrt{\abs{G_\lambda}}} \sum_{g \in G_\lambda} \ket{g}\ket{x_\lambda}. \]
+    Next, apply the unitary transformation $\ket{h}\ket{y} \mapsto \ket{h}\ket{h * y}$ to this state, followed by the quantum Fourier transform on the first register. This results in
+    \[ \frac{1}{\abs{G_\lambda}} \sum_{h \in G_\lambda} \sum_{g \in G_\lambda} \chi(g, h) \ket{h}\ket{g * x_\lambda} = \frac{1}{\sqrt{\abs{G_\lambda}}} \sum_{h \in G_\lambda} \ket{h} \ket{G^{(h)} * x_\lambda} \]
+    where $\ket{G^{(h)} * x_\lambda}$ is defined as in \eqref{eq:x-fourier-basis}.
+Measure the first register to obtain a random $h \in G_\lambda$, collapsing the state to $\ket{G^{(h)} * x_\lambda}$.
+Return the pair $(h, \ket{G^{(h)} * x_\lambda})$.
+
+\item $\ver(h, \ket{\psi})$.
+First, check whether $\ket{\psi}$ has support in $X_\lambda$.
+If not, return $0$.
+Then, apply $\comph$ to the state $\ket{\psi}\ket{0}$, and measure the second register to obtain some $h' \in G_\lambda$.
+If $h' = h$, return $1$; otherwise return $0$.
+\end{itemize}
+
+From this point forward, to simplify the notation, we make the security parameter $\lambda$ implicit, and use $G$ for $G_\lambda$, $X$ for $X_\lambda$, and so on.
 
@@
 
-\subsection*{Comparison with the Quantum Fourier Transform (QFT)}
-The QFT and QHT differ in their transformation kernels:
-\begin{itemize}
-    \item \textbf{QFT}:
-    \[
-    |x\rangle \xrightarrow{\text{QFT}} \frac{1}{\sqrt{N}} \sum_{k=0}^{N-1} e^{2\pi i x k / N} |k\rangle.
-    \]
-    \item \textbf{QHT}:
-    \[
-    |x\rangle \xrightarrow{\text{QHT}} \frac{1}{\sqrt{N}} \sum_{k=0}^{N-1} \left[\cos\left(\frac{2\pi x k}{N}\right) + \sin\left(\frac{2\pi x k}{N}\right)\right] |k\rangle.
-    \]
-\end{itemize}
-
-\subsection*{Applications of the QHT}
-\begin{itemize}
-    \item \textbf{Signal Processing}: Analysis of real-valued signals in quantum systems.
-    \item \textbf{Quantum Algorithms}: Used in problems where real and symmetric basis representations simplify computations.
-    \item \textbf{Data Compression}: Efficient representation of signals with high symmetry.
-\end{itemize}
+% \subsection*{Comparison with the Quantum Fourier Transform (QFT)}
+% The QFT and QHT differ in their transformation kernels:
+% \begin{itemize}
+%     \item \textbf{QFT}:
+%     \[
+%     |x\rangle \xrightarrow{\text{QFT}} \frac{1}{\sqrt{N}} \sum_{k=0}^{N-1} e^{2\pi i x k / N} |k\rangle.
+%     \]
+%     \item \textbf{QHT}:
+%     \[
+%     |x\rangle \xrightarrow{\text{QHT}} \frac{1}{\sqrt{N}} \sum_{k=0}^{N-1} \left[\cos\left(\frac{2\pi x k}{N}\right) + \sin\left(\frac{2\pi x k}{N}\right)\right] |k\rangle.
+%     \]
+% \end{itemize}
+
+\subsection*{Efficient implementation of Heartly transform}
+
+********
+
+\section{Quantum Money With The Hartley Transform}
+\label{sec:qm_hartley}
+
+The quantum money scheme above can be instantiated using the quantum Hartley transform instead of the quantum Fourier transform.
+However, this substitution breaks the verification algorithm.
+In the next sections, we will show how quantum walks can address this issue.
+To understand where the problem arises, we first present the $\gen$ and $\ver$ algorithms for the money scheme, similar to the previous description but with $\qht_G$ replacing $\qft_G$.
+For simplicity, we assume $G = \Z_N$.
+Let $x \in \Z_N$ be a fixed element.
+
+\begin{itemize}
+\item $\gen$. Begin with the state $\ket{0}\ket{x}$, and apply the quantum Hartley transform over $\Z_N$ to the first register producing the superposition
+    \[ \frac{1}{\sqrt{N}} \sum_{g \in \Z_N} \ket{g}\ket{x}. \]
+    Next, apply the unitary $\ket{h}\ket{y} \mapsto \ket{h}\ket{h * y}$ to this state, followed by a $\qht_N$ on the first register. This results in
+    \[ \frac{1}{N} \sum_{h \in \Z_N} \sum_{g \in \Z_N} \cas\Big(\frac{2\pi gh}{N}\Big) \ket{h}\ket{g * x} = \frac{1}{\sqrt{N}} \sum_{h \in \Z_N} \ket{h} \ket{\Z_N^{(h)} * x}_H \]
+    where
+    \[ \ket{\Z_N^{(h)} * x}_H = \frac{1}{\sqrt{N}} \sum_{g \in \Z_N} \cas\Big(\frac{2\pi gh}{N}\Big) \ket{g * x}. \]
+    Measure the first register to obtain a random $h \in \Z_N$, collapsing the state to $\ket{\Z_N^{(h)} * x}_H$. Return the pair $(h, \ket{\Z_N^{(h)} * x}_H)$.
+
+\item $\ver(h, \ket{\psi})$.
+First, check whether $\ket{\psi}$ has support in $X$.
+If not, return $0$.
+Then, apply $\comph$ to the state $\ket{0} \ket{\psi}$, and measure the first register to obtain some $h' \in \Z_N$.
+If $h' = h$, return $1$; otherwise return $0$.
+\end{itemize}
+
+\section*{Verification using quantum walks}
 

### 2025-03-02 main.tex
new commit

@@
 
+$\gen(1^\lambda)$
+$\ver(s, \rho_s)$
+
+\[ \Pr[\ver(s, \rho_s) = 1 : (s, \rho_s) \gets \gen(1^\lambda)] \ge 1 - \negl(\lambda). \]
+\[ \Pr\left[ \ver(s, \rho_1) = \ver(s, \rho_2) = 1 : \substack{(s, \rho_s) \gets \gen(1^\lambda) \\ (\rho_1, \rho_2) \gets \mathcal{A}(s, \rho_s)} \right] \le \negl(\lambda). \]
+
+$\ket{0}\ket{x_\lambda}$
+\[ \frac{1}{\sqrt{\abs{G_\lambda}}} \sum_{g \in G_\lambda} \ket{g}\ket{x_\lambda}. \]
+
+\[ \frac{1}{\abs{G_\lambda}} \sum_{h \in G_\lambda} \sum_{g \in G_\lambda} \chi(g, h) \ket{h}\ket{g * x_\lambda} = \frac{1}{\sqrt{\abs{G_\lambda}}} \sum_{h \in G_\lambda} \ket{h} \ket{G^{(h)} * x_\lambda} \]
+$\ket{G^{(h)} * x_\lambda}$
+
+$(h, \ket{G^{(h)} * x_\lambda})$
+
+$\ket{0}\ket{x}$
+\[ \frac{1}{\sqrt{N}} \sum_{g \in \Z_N} \ket{g}\ket{x}. \]
+$\ket{h}\ket{y} \mapsto \ket{h}\ket{h * y}$
+\[ \frac{1}{N} \sum_{h \in \Z_N} \sum_{g \in \Z_N} \cas\Big(\frac{2\pi gh}{N}\Big) \ket{h}\ket{g * x} = \frac{1}{\sqrt{N}} \sum_{h \in \Z_N} \ket{h} \ket{\Z_N^{(h)} * x}_H \]
+\[ \ket{\Z_N^{(h)} * x}_H = \frac{1}{\sqrt{N}} \sum_{g \in \Z_N} \cas\Big(\frac{2\pi gh}{N}\Big) \ket{g * x}. \]
+
+\[ \ket{\phi} = \frac{1}{\sqrt{N}} \sum_{u \in \Z_N} \ket{u} \ket{\Z_N^{(h)} * x}_H. \]
+
+\[ \frac{1}{\sqrt{N}} \sum_{g \in \Z_N} \Big( \cos\Big( \frac{2\pi gh}{N} \Big) \ket{h} + \sin\Big( \frac{2\pi gh}{N} \Big) \ket{-h} \Big) \ket{g * x}. \]
+
+\[ \ket{\phi} = \frac{1}{\sqrt{N}} \sum_{u \in \Z_N} \ket{u} \ket{\Z_N^{(h)} * x}_H. \]
+
+$Q = \{q_1, q_2, \dots, q_k\} \subset G$
+
+\[ A = \sum_{a \in G} \lambda_a \ket{\hat{a}} \bra{\hat{a}}, \]
+
+\[ \lambda_a = \sum_{q \in Q} \chi(a, q). \]
+
+\[ A = \sum_{h \in G} \lambda_h \ket{G^{(h)} * x} \bra{G^{(h)} * x}, \]
+
+$\lambda_h = \sum_{q \in Q} \chi(h, q)$
+
+\begin{equation}
+    \label{eq:adjmat-fb}
+    e^{-iAt} = \qft_G^* \sum_{a \in G} e^{-i\lambda_a t} \ket{a} \bra{a} \qft_G.
+\end{equation}
+
+\[ e^{-iAt} = \sum_{h \in G} e^{-i\lambda_h t} \ket{G^{(h)} * x} \bra{G^{(h)} * x}. \]
+
+$t = \poly(\log\abs{G})$
+
+\begin{align*}
+    T
+    & := \sum_{y \in X} \sum_{b \in \{0, 1\}} (\ket{y}\bra{y} \otimes \ket{b}\bra{b}) \otimes \ket{\phi_{yb}} \\
+    & = \sum_{y \in X} \sum_{b \in \{0, 1\}} \ket{y} \ket{b} \ket{\phi_{yb}} \bra{y} \bra{b}.
+\end{align*}
+
+\[ \ket{\phi_{y0}} = \frac{1}{\sqrt{\abs{Q}}} \sum_{q \in Q} \ket{q * y} \ket{0}. \]
+
+\[ \frac{1}{\sqrt{\abs{Q}}} \sum_{q \in Q} \ket{q} \ket{y, 0} \ket{0, 0}. \]
+
+\begin{align*}
+    2\ket{0} \bra{0} \otimes TT^* - \mathds{1}
+    & = 2\ket{0} \bra{0} \otimes \sum_{y \in X} \sum_{b \in \{0, 1\}} \ket{y, b} \ket{\phi_{yb}} \bra{y, b} \bra{\phi_{yb}} - \mathds{1} \\
+    & = 2\sum_{y \in X} \sum_{b \in \{0, 1\}} \ket{0} \ket{y, b} \ket{\phi_{yb}} \bra{0} \bra{y, b} \bra{\phi_{yb}} - \mathds{1} \\
+    & = U_T \Big( 2\sum_{y \in X} \sum_{b \in \{0, 1\}} \ket{0} \ket{y, b} \ket{0, 0} \bra{0} \bra{y, b} \bra{0, 0} - \mathds{1} \Big) U_T^* \\
+    & = U_T (2 \ket{0} \bra{0} \otimes \mathds{1}_{X, b} \otimes \ket{0, 0} \bra{0, 0} - \mathds{1}) U_T^*.
+\end{align*}
+
+\[ (2\ket{0} \bra{0} \otimes TT^* - \mathds{1}) \ket{0} \ket{\psi} = \ket{0} (2TT^* - \mathds{1}) \ket{\psi}. \]
+
+$\ket{\Z_N^{(h)} * x}_H$
+
+\begin{align*}
+    e^{iAt} \ket{\Z_N^{(h)} * x}_H
+    & = \sum_{g \in \Z_N} e^{i\lambda_gt} \ket{\Z_N^{(g)} * x} \braket{\Z_N^{(g)} * x}{\Z_N^{(h)} * x}_H \\
+    & = \sum_{g \in \Z_N} e^{i\lambda_gt} \ket{\Z_N^{(g)} * x} \bra{\Z_N^{(g)} * x} \Big( \frac{1 - i}{2} \ket{\Z_N^{(h)} * x} + \frac{1 + i}{2} \ket{\Z_N^{(-h)} * x} \Big) \\
+    & = e^{i\lambda_{h}t} \frac{1 - i}{2} \ket{\Z_N^{(h)} * x} + \frac{1 + i}{2} e^{i\lambda_{-h}t} \ket{\Z_N^{(-h)} * x} \\
+    & = e^{i\lambda_{h}t} \ket{\Z_N^{(h)} * x}_H,
+\end{align*}
+
+\[ \abs[\Big]{\theta - \frac{uh}{N}} \le \frac{1}{\poly(\log N)}. \]
+
 \end{document}

### 2025-03-02 presentation.tex
new commit

\documentclass{beamer}

% Packages
\usepackage{graphicx}    % For including images
\usepackage{amsmath}     % For mathematical symbols
\usepackage{braket}      % For Dirac notation
\usepackage[absolute,overlay]{textpos}

\theoremstyle{definition}
\newtheorem{algorithm}{Algorithm}
\newtheorem{construction}[theorem]{Construction}

\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}

\newcommand{\cas}{\mathrm{cas}}
\newcommand{\cht}{\mathsf{H}}
\newcommand{\qht}{\mathsf{QHT}}
\newcommand{\cft}{\mathsf{F}}
\newcommand{\qft}{\mathsf{QFT}}
\newcommand{\comph}{\mathsf{cmpIndex}}
\newcommand{\gen}{\mathsf{Gen}}
\newcommand{\ver}{\mathsf{Ver}}

% Title Information
\title{Quantum Notation and Quantum Computing}
\author{Seyed Ali Mousavi}
\date{\today}

\begin{document}

% Title Slide
\begin{frame}
    \titlepage
\end{frame}

\begin{frame}{Courses Taken}

    \begin{textblock*}{12cm}(0.5cm,1.5cm)
       \begin{itemize}
        \item CAS 701,  Logic \& Discrete Mathematics
        \item COMPSCI 6TE3, Continuous optimization
        \item CAS 721, Combinatorics \& Computing
        \item CAS 741, Development of Scientific Computation Software
       \end{itemize}
    \end{textblock*}

\end{frame}

\begin{frame}{Seminars}

    \begin{textblock*}{12cm}(0.5cm,1.5cm)
       \begin{itemize}
        \item 
       \end{itemize}
    \end{textblock*}

\end{frame}

\begin{frame}{Application: Quantum Money}

    \begin{textblock*}{12cm}(0.5cm,1.5cm)

        A public-key quantum money scheme consists of two QPT algorithms: 
        \begin{itemize}
        \item $\gen(1^\lambda)$: This algorithm takes a security parameter $\lambda$ as input and outputs a pair $(s, \rho_s)$, where $s$ is a binary string called the serial number, and $\rho_s$ is a quantum state called the banknote. The pair $(s, \rho_s)$, or simply $\rho_s$, is sometimes denoted by $\$$.
        \item    This algorithm takes a serial number and an alleged banknote as input and outputs either $1$ (accept) or $0$ (reject).
        \end{itemize}

    \end{textblock*}

\end{frame}

\begin{frame}{Quantum Money From Group Actions}

    \begin{textblock*}{12cm}(0.5cm,1.5cm)

        \begin{itemize}
        \item $\gen(1^\lambda)$. Begin with the state $\ket{0}\ket{x_\lambda}$, and apply the quantum Fourier transform over $G_\lambda$ to the first register producing the superposition
        \[ \frac{1}{\sqrt{{|X_\lambda|}}} \sum_{g \in G_\lambda} \ket{g}\ket{x_\lambda}. \]
        Next, apply the unitary transformation $\ket{h}\ket{y} \mapsto \ket{h}\ket{h * y}$ to this state, followed by the quantum Fourier transform on the first register. This results in
        \[ \frac{1}{{|G_\lambda|}} \sum_{h \in G_\lambda} \sum_{g \in G_\lambda} \chi(g, h) \ket{h}\ket{g * x_\lambda} = \frac{1}{\sqrt{{|G_\lambda|}}} \sum_{h \in G_\lambda} \ket{h} \ket{G^{(h)} * x_\lambda} \]
        where $\ket{G^{(h)} * x_\lambda}$ is defined as in \eqref{eq:x-fourier-basis}. Measure the first register to obtain a random $h \in G_\lambda$, collapsing the state to $\ket{G^{(h)} * x_\lambda}$. Return the pair $(h, \ket{G^{(h)} * x_\lambda})$.

        \item $\ver(h, \ket{\psi})$. First, check whether $\ket{\psi}$ has support in $X_\lambda$. If not, return $0$. Then, apply $\comph$ to the state $\ket{\psi}\ket{0}$, and measure the second register to obtain some $h' \in G_\lambda$. If $h' = h$, return $1$; otherwise return $0$.
        \end{itemize}

    \end{textblock*}

\end{frame}

\begin{frame}{Quantum Money With The Hartley Transform}

    \begin{textblock*}{12cm}(0.5cm,1.5cm)

        \begin{itemize}
            \item $\gen$. Begin with the state $\ket{0}\ket{x}$, and apply the quantum Hartley transform over $\mathbb{Z}_N$ to the first register producing the superposition
            \[ \frac{1}{\sqrt{N}} \sum_{g \in \mathbb{Z}_N} \ket{g}\ket{x}. \]
            Next, apply the unitary $\ket{h}\ket{y} \mapsto \ket{h}\ket{h * y}$ to this state, followed by a $\qht_N$ on the first register. This results in
            \[ \frac{1}{N} \sum_{h \in \mathbb{Z}_N} \sum_{g \in \mathbb{Z}_N} \cas\Big(\frac{2\pi gh}{N}\Big) \ket{h}\ket{g * x} = \frac{1}{\sqrt{N}} \sum_{h \in \mathbb{Z}_N} \ket{h} \ket{\mathbb{Z}_N^{(h)} * x}_H \]
            where
            \[ \ket{\mathbb{Z}_N^{(h)} * x}_H = \frac{1}{\sqrt{N}} \sum_{g \in \mathbb{Z}_N} \cas\Big(\frac{2\pi gh}{N}\Big) \ket{g * x}. \]
            Measure the first register to obtain a random $h \in \mathbb{Z}_N$, collapsing the state to $\ket{\mathbb{Z}_N^{(h)} * x}_H$. Return the pair $(h, \ket{\mathbb{Z}_N^{(h)} * x}_H)$.

        \end{itemize}

    \end{textblock*}

\end{frame}

\begin{frame}{Group Action Quantum Walks}

    \begin{textblock*}{12cm}(0.5cm,1.5cm)

        Let $G$ be an abelian group and let $Q = \{q_1, q_2, \dots, q_k\} \subset G$ be a symmetric set, i.e., $q \in Q$ if and only if $-q \in Q$. The Cayley graph associated to $G$ and $Q$ is a graph $\Gamma = (V, E)$, where the vertex set is $V = G$, and the edge set $E$ consists of pairs $(a, b) \in G \times G$ such that there exists $q \in Q$ with $b = q + a$. The adjacency matrix of $\Gamma$ can be expressed as
        \[ A = \sum_{a \in G} \lambda_a \ket{\hat{a}} \bra{\hat{a}}, \]
        where $\ket{\hat{a}}$ is the quantum Fourier transform of $\ket{a}$. The eigenvalues $\lambda$ are given by
        \[ \lambda_a = \sum_{q \in Q} \chi(a, q). \]
        Note that the eigenvectors $\ket{\hat{a}}$ of $A$ depend only on $G$ and not on the set $Q$.
    \end{textblock*}

\end{frame}

\begin{frame}{Group Action Quantum Walks}

    \begin{textblock*}{12cm}(0.5cm,1.5cm)

        Cayley graphs can also be constructed using group actions. Given a regular group action $(G, X, *)$ with a fixed element $x \in X$ and a set  $Q = \{q_1, q_2, \dots, q_k\} \subset G$, let $\Gamma = (X, E)$ be a graphs with vertex set $X$ and edge set consisting of pairs $(x, y) \in X \times X$ such that $y = q * x$ for some $q \in Q$. The adjacency matrix of $\Gamma$ is
        \[ A = \sum_{h \in G} \lambda_h \ket{G^{(h)} * x} \bra{G^{(h)} * x}, \]
        where $\lambda_h = \sum_{q \in Q} \chi(h, q)$. Again, the eigenvectors $\ket{G^{(h)} * x}$ depend only on $G$. This construction of Cayley graphs from group actions generalizes the previous construction. Specifically, if we set $X = G$ and the action $*$ as group operation, we recover the original construction.

        Since the action $(G, X, *)$ is regular, the two constructions yield the same graph up to isomorphism. In the first graph, the vertex set is $G$, and the rows and columns of the adjacency matrix are indexed by the elements of $G$, whereas in the second graph, the vertex set is $X$, and the rows and columns of the adjacency matrix are indexed by the elements of $X$. The isomorphism between the two graphs is induced by the bijection
        \[
        \setlength{\arraycolsep}{1mm}
        \begin{array}{rlll}
            \phi: & G & \longrightarrow & X \\
            & g & \longmapsto & g * x.
        \end{array}
        \]
    \end{textblock*}

\end{frame}

\begin{frame}{Introduction to Quantum Notation}

    \begin{textblock*}{12cm}(0.5cm,1.5cm)
        The money state $\ket{\mathbb{Z}_N^{(h)} * x}_H$ is an eigenstate of $W$ with eigenvalue $e^{i\lambda_h t}$.
        \vspace{1cm}

        We have :
        \begin{align*}
            e^{iAt} \ket{\mathbb{Z}_N^{(h)} * x}_H
            & = \sum_{g \in \mathbb{Z}_N} e^{i\lambda_gt} \ket{\mathbb{Z}_N^{(g)} * x}\braket{\mathbb{Z}_N^{(g)} * x|\mathbb{Z}_N^{(h)} * x}_H \\
            & = \sum_{g \in \mathbb{Z}_N} e^{i\lambda_gt} \ket{\mathbb{Z}_N^{(g)} * x} \bra{\mathbb{Z}_N^{(g)} * x} \Big( \frac{1 - i}{2} \ket{\mathbb{Z}_N^{(h)} * x} + \frac{1 + i}{2} \ket{\mathbb{Z}_N^{(-h)} * x} \Big) \\
            & = e^{i\lambda_{h}t} \frac{1 - i}{2} \ket{\mathbb{Z}_N^{(h)} * x} + \frac{1 + i}{2} e^{i\lambda_{-h}t} \ket{\mathbb{Z}_N^{(-h)} * x} \\
            & = e^{i\lambda_{h}t} \ket{\mathbb{Z}_N^{(h)} * x}_H,
        \end{align*}
        where the second equality follows from the identity in \eqref{eq:ht-ft}, and the last equality follows from the fact that $\lambda_h = \lambda_{-h}$.
    \end{textblock*}

    % % Positioning text exactly at (1cm, 1.5cm)
    % \begin{textblock*}{10cm}(1cm,3cm) % (Width of box, X-position, Y-position)
    %  This text is placed exactly at (1cm, 15cm) from the top-left.  
    %  \[
    %  \ket{\mathbb{Z}_N^{(h)} * x}_H
    %  \]
    %  \end{textblock*}

 \end{frame}

% End
\end{document}

### 2025-03-04 presentation.tex
new commit

@@
 \usepackage[absolute,overlay]{textpos}
+\usepackage{amsmath}
+% \usepackage{amsmath, amssymb, dsfont}
+% \usepackage{algorithm}
+% \usepackage{algorithmicx}
+% \usepackage{enumitem}
 
@@
 
+\begin{frame}{Poster}
+
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+       \begin{itemize}
+        \item 
+       \end{itemize}
+    \end{textblock*}
+
+\end{frame}
+
+\begin{frame}{The Hartley Transform}
+
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+        item Let $N$ be a positive integer, and let $\mathbb{Z}_N$ be the additive cyclic group of integers modulo $N$.
+The Hartley transform of a function $f: \mathbb{Z}_N \to \mathbb{R}$ is the function $\cht_N(f): \mathbb{Z}_N \to \mathbb{R}$ defined by
+        \[ \cht_N(f)(a) = \frac{1}{\sqrt{N}} \sum_{y = 0}^{N - 1} \cas\Big(\frac{2 \pi ay}{N}\Big) f(y),  \]
+        where $\cas(x) = \cos(x) + \sin(x)$ \\
+        For a single basis element of the cyclic group $\mathbb{Z}_N$, the quantum Hartly transform simplifies to
+        \begin{equation}
+            \label{eq:qht-N}
+            \qht_N: \ket{a} \mapsto \frac{1}{\sqrt{N}} \sum_{y = 0}^{N - 1} \cas\Big(\frac{2\pi a y}{N}\Big) \ket{y}.
+        \end{equation}
+    \end{textblock*}
+
+\end{frame}
+
+\begin{frame}{An efficient new algorithm for QHT}
+
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+        First, let us briefly explain how the algorithm for $\qft_N$ works:
+        \begin{align*}
+            \qft_N\ket{a}
+            & = \frac{1}{\sqrt{N}} \sum_{y = 0}^{N - 1} \omega_N^{ay}\ket{y} \\
+            & = \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \omega_N^{ay} \ket{y} + (-1)^a \sum_{y = 0}^{N / 2 - 1} \omega_N^{ay} \ket{y + N/2} \\
+            & = \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \omega_N^{ay} \frac{1}{\sqrt{2}} (\ket{0} + (-1)^a \ket{1}) \ket{y}, \numberthis\label{eq:qft_alt}
+        \end{align*}
+
+    \end{textblock*}
+
+\end{frame}
+
+\begin{frame}{An efficient new algorithm for QHT}
+
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+        Let $\ket{a} = \ket{t}\ket{b}$, where $b$ is the least significant bit of $a$, so that $a = 2t + b$. Applying $\qft_{N / 2}$ to the first register, we obtain the state
+        \[ \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \omega_N^{2ty} \ket{y} \ket{b}. \]
+        Next, we apply the phase unitary $P(y, b): \ket{y} \ket{b} \mapsto \omega_N^{by} \ket{y} \ket{b}$, and finally, we apply a Hadamard transform to the last qubit.
+The result is the state in \eqref{eq:qft_alt}.
+
+    \end{textblock*}
+
+\end{frame}
+
+\begin{frame}{An efficient new algorithm for QHT}
+
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+        \begin{equation}
+            % \label{eq:cas-expand}
+            \frac{1}{\sqrt{N}} \sum_{y = 0}^{N - 1} \cas\Big( \frac{2\pi a y}{N} \Big) \ket{y}  
+        \end{equation}
+        \begin{equation}
+            = \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi a y}{N} \Big) \ket{y} +  \frac{1}{\sqrt{N}} \sum_{y = N / 2}^{N - 1} \cas\Big( \frac{2\pi a y}{N} \Big) \ket{y}.
+        \end{equation}
+        The second sum in the right-hand side can be written as 
+        \begin{align*}
+            \sum_{y = N / 2}^{N - 1} \cas\Big( \frac{2\pi a y}{N} \Big) \ket{y}
+            & = \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi a y}{N} + \pi a \Big) \ket{y + N/2} \\
+            & = (-1)^a \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi a y}{N} \Big) \ket{y + N/2},
+        \end{align*}
+    \end{textblock*}
+
+\end{frame}
+
+\begin{frame}{An efficient new algorithm for QHT}
+
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+
+        \begin{align}
+            % \frac{1}{\sqrt{N}} \sum_{y = 0}^{N - 1} \cas\Big( \frac{2\pi a y}{N} \Big) \ket{y}
+            % & = \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi a y}{N} \Big) (\ket{y} + (-1)^a \ket{y + N/2}) \nonumber \\
+            & = \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi a y}{N} \Big) \frac{1}{\sqrt{2}} (\ket{0} + (-1)^a \ket{1}) \ket{y}, \label{eq:qht-alt} 
+        \end{align}
+
+        We now show how to compute $\qht_N$ recursively.
+
+        \begin{align*}
+            \ket{0}\ket{t}\ket{b}
+            & \mapsto \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi t y}{N / 2} \Big) \ket{0} \ket{y} \ket{b} \\%& (\mathds{1} \otimes \qht_{N / 2} \otimes \mathds{1}) \\
+            & = \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{4\pi t y}{N} \Big) \ket{0} \ket{y} \ket{b} \\
+            & \mapsto \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{4\pi t y}{N} \Big) (\ket{0} + \ket{1}) \ket{y}\ket{b}. %& (H \otimes \mathds{1}) 
+        \end{align*}
+
+    \end{textblock*}
+
+\end{frame}
+
+\begin{frame}{An efficient new algorithm for QHT}
+
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+
+        \begin{align}
+            % \frac{1}{\sqrt{N}} \sum_{y = 0}^{N - 1} \cas\Big( \frac{2\pi a y}{N} \Big) \ket{y}
+            % & = \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi a y}{N} \Big) (\ket{y} + (-1)^a \ket{y + N/2}) \nonumber \\
+            & = \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi a y}{N} \Big) \frac{1}{\sqrt{2}} (\ket{0} + (-1)^a \ket{1}) \ket{y}, \label{eq:qht-alt} 
+        \end{align}
+
+        We now show how to compute $\qht_N$ recursively.
+
+        \begin{align*}
+            \ket{0}\ket{t}\ket{b}
+            & \mapsto \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi t y}{N / 2} \Big) \ket{0} \ket{y} \ket{b} \\%& (\mathds{1} \otimes \qht_{N / 2} \otimes \mathds{1}) \\
+            & = \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{4\pi t y}{N} \Big) \ket{0} \ket{y} \ket{b} \\
+            & \mapsto \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{4\pi t y}{N} \Big) (\ket{0} + \ket{1}) \ket{y}\ket{b}. %& (H \otimes \mathds{1}) 
+        \end{align*}
+
+    \end{textblock*}
+
+\end{frame}
+
+% \begin{frame}{An efficient new algorithm for QHT}
+
+%     \begin{textblock*}{12cm}(0.5cm,1.5cm)
+%         MM
+%         \begin{algorithm}[$\mathbb{QHT}_N$] \
+%             \label{alg:qht-N}
+%             \begin{description}[font = \normalfont\itshape, itemsep = 0mm, parsep = 0mm, topsep = 1mm]
+%                 \item [Input:] Quantum state \( \ket{\psi} \in \mathbb{C}^N \), where \( N = 2^n \).
+%                 \item [Output:] Quantum state \( \mathbb{QHT}_N \ket{\psi} \).
+%             \end{description}
+
+%             \begin{enumerate}[itemsep = 0mm, parsep = 1mm, topsep = 1mm]
+%                 \item Initialize an ancilla qubit to \( 0 \) to obtain the state \( \ket{0} \ket{\psi} \).
+%                 \item Compute \( \mathds{1} \otimes \mathbb{QHT}_{N / 2} \otimes \mathds{1} \) recursively.
+%                 \item Apply \( H \otimes \mathds{1} \).
+%                 \item Apply the controlled negation:
+%                       \[
+%                           \ket{0} \ket{y} \mapsto \ket{0} \ket{y}, \quad \ket{1} \ket{y} \mapsto \ket{1} \ket{N / 2 - y}.
+%                       \]
+%                 \item Apply the unitary \( U_R \).
+%                 \item Apply \( H \otimes \mathds{1} \).
+%                 \item Apply \textsc{cnot} to the first and last qubits.
+%                 \item Apply \( \mathds{1} \otimes H \).
+%                 \item Trace out the first qubit.
+%             \end{enumerate}
+%         \end{algorithm}
+
+%     % \end{textblock*}
+
+% \end{frame}
+
 \begin{frame}{Application: Quantum Money}
@@
         A public-key quantum money scheme consists of two QPT algorithms:
+        \vspace{1cm} 
         \begin{itemize}
@@
 The pair $(s, \rho_s)$, or simply $\rho_s$, is sometimes denoted by $\$$.
-        \item    This algorithm takes a serial number and an alleged banknote as input and outputs either $1$ (accept) or $0$ (reject).
+
+        \vspace{1cm}
+        \item $\ver(s, \rho_s)$: This algorithm takes a serial number and an alleged banknote as input and outputs either $1$ (accept) or $0$ (reject).
         \end{itemize}
@@
         \[ \frac{1}{{|G_\lambda|}} \sum_{h \in G_\lambda} \sum_{g \in G_\lambda} \chi(g, h) \ket{h}\ket{g * x_\lambda} = \frac{1}{\sqrt{{|G_\lambda|}}} \sum_{h \in G_\lambda} \ket{h} \ket{G^{(h)} * x_\lambda} \]
-        where $\ket{G^{(h)} * x_\lambda}$ is defined as in \eqref{eq:x-fourier-basis}.
-Measure the first register to obtain a random $h \in G_\lambda$, collapsing the state to $\ket{G^{(h)} * x_\lambda}$.
-Return the pair $(h, \ket{G^{(h)} * x_\lambda})$.
 
+        \end{itemize}
+
+    \end{textblock*}
+
+\end{frame}
+
+\begin{frame}{Quantum Money From Group Actions}
+
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+
+        \begin{itemize}
         \item $\ver(h, \ket{\psi})$.
@@
             \[ \frac{1}{N} \sum_{h \in \mathbb{Z}_N} \sum_{g \in \mathbb{Z}_N} \cas\Big(\frac{2\pi gh}{N}\Big) \ket{h}\ket{g * x} = \frac{1}{\sqrt{N}} \sum_{h \in \mathbb{Z}_N} \ket{h} \ket{\mathbb{Z}_N^{(h)} * x}_H \]
-            where
-            \[ \ket{\mathbb{Z}_N^{(h)} * x}_H = \frac{1}{\sqrt{N}} \sum_{g \in \mathbb{Z}_N} \cas\Big(\frac{2\pi gh}{N}\Big) \ket{g * x}. \]
             Measure the first register to obtain a random $h \in \mathbb{Z}_N$, collapsing the state to $\ket{\mathbb{Z}_N^{(h)} * x}_H$. Return the pair $(h, \ket{\mathbb{Z}_N^{(h)} * x}_H)$.
@@
         \end{itemize}
+
+    \end{textblock*}
+
+\end{frame}
+
+\begin{frame}{Quantum Money With The Hartley Transform}
+
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+        In the original scheme, using the quantum Fourier transform, we could directly obtain $h$ from the money state $\ket{\mathbb{Z}_N^{(h)} * x}$ and compare it to the given $h$.
+However, this approach does not work when we use the Hartley transform.
+To address this, we design an algorithm for computing $h$ that utilizes quantum walks.
 
@@
         \[ A = \sum_{h \in G} \lambda_h \ket{G^{(h)} * x} \bra{G^{(h)} * x}, \]
-        where $\lambda_h = \sum_{q \in Q} \chi(h, q)$.
-Again, the eigenvectors $\ket{G^{(h)} * x}$ depend only on $G$.
-This construction of Cayley graphs from group actions generalizes the previous construction.
-Specifically, if we set $X = G$ and the action $*$ as group operation, we recover the original construction.
+        where:
+        \begin{itemize}
+            \item $\lambda_h = \sum_{q \in Q} \chi(h, q)$
+            \item the eigenvectors $\ket{G^{(h)} * x}$ depend only on $G$
+        \end{itemize}
 
-        Since the action $(G, X, *)$ is regular, the two constructions yield the same graph up to isomorphism.
-In the first graph, the vertex set is $G$, and the rows and columns of the adjacency matrix are indexed by the elements of $G$, whereas in the second graph, the vertex set is $X$, and the rows and columns of the adjacency matrix are indexed by the elements of $X$.
-The isomorphism between the two graphs is induced by the bijection
-        \[
-        \setlength{\arraycolsep}{1mm}
-        \begin{array}{rlll}
-            \phi: & G & \longrightarrow & X \\
-            & g & \longmapsto & g * x.
-        \end{array}
-        \]
     \end{textblock*}
@@
 
-\begin{frame}{Introduction to Quantum Notation}
+\begin{frame}{Computing the serial Number}
 
     \begin{textblock*}{12cm}(0.5cm,1.5cm)
-        The money state $\ket{\mathbb{Z}_N^{(h)} * x}_H$ is an eigenstate of $W$ with eigenvalue $e^{i\lambda_h t}$.
+
+        Given a state $\ket{\mathbb{Z}_N^{(h)} * x}_H$, we show how to compute $h$ using continuous-time quantum walks.
+For any $q \in \mathbb{Z}_N$, define a Cayley graph $\Gamma = (\mathbb{Z}_N, E)$ with the generating set $Q = \{-q, q\}$.
+Let $A$ denote the adjacency matrix of $\Gamma$.
+The eigenvectors and corresponding eigenvalues of $A$ are $\ket{\mathbb{Z}_N^{(h)} * x}$ and $\lambda_h = 2\cos(2\pi uh / N)$, respectively, for $h \in \mathbb{Z}_N$.
+the unitary $W = e^{iAt}$ can be efficiently simulated to exponential accuracy.
+We need the following lemma.
+
+    \end{textblock*}
+
+ \end{frame}
+
+\begin{frame}{Computing the serial Number}
+
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+        Lemma: The money state $\ket{\mathbb{Z}_N^{(h)} * x}_H$ is an eigenstate of $W$ with eigenvalue $e^{i\lambda_h t}$.
         \vspace{1cm}
 
-        We have :
+        Proof. 
         \begin{align*}
@@
         \end{align*}
-        where the second equality follows from the identity in \eqref{eq:ht-ft}, and the last equality follows from the fact that $\lambda_h = \lambda_{-h}$.
+        where the last equality follows from the fact that $\lambda_h = \lambda_{-h}$.
     \end{textblock*}
-
-    % % Positioning text exactly at (1cm, 1.5cm)
-    % \begin{textblock*}{10cm}(1cm,3cm) % (Width of box, X-position, Y-position)
-    %  This text is placed exactly at (1cm, 15cm) from the top-left.  
-    %  \[
-    %  \ket{\mathbb{Z}_N^{(h)} * x}_H
-    %  \]
-    %  \end{textblock*}
 

### 2025-03-04 presentation.tex
new commit

@@
 % Title Information
-\title{Quantum Notation and Quantum Computing}
+\title{Quantum Walks and Applications to Quantum Money}
 \author{Seyed Ali Mousavi}
+\institute{Supervised by Dr. Jake Doliskani}
 \date{\today}
@@
 
-\begin{frame}{Courses Taken}
+\begin{frame}{Program and Courses Taken}
 
@@
        \begin{itemize}
+        \item Program: M.A.Sc in Software Engineering
+        \vspace{1cm}
         \item CAS 701,  Logic \& Discrete Mathematics
@@
 
+    \title{SDSD}
+
 \end{frame}
@@
        \begin{itemize}
-        \item 
+        \item I have participated in 6 seminars during my program.
        \end{itemize}
@@
 
-    \begin{textblock*}{12cm}(0.5cm,1.5cm)
-       \begin{itemize}
-        \item 
-       \end{itemize}
-    \end{textblock*}
+    \begin{figure}
+        \centering
+        \includegraphics[width=1\textwidth]{poster.png}
+        \caption{Presented at Nov. 6, 2024}
+    \end{figure}
 
@@
 
+% \begin{frame}{An efficient new algorithm for QHT}
+
+%     \begin{textblock*}{12cm}(0.5cm,1.5cm)
+
+%         \begin{align}
+%             % \frac{1}{\sqrt{N}} \sum_{y = 0}^{N - 1} \cas\Big( \frac{2\pi a y}{N} \Big) \ket{y}
+%             % & = \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi a y}{N} \Big) (\ket{y} + (-1)^a \ket{y + N/2}) \nonumber \\
+%             & = \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi a y}{N} \Big) \frac{1}{\sqrt{2}} (\ket{0} + (-1)^a \ket{1}) \ket{y}, \label{eq:qht-alt} 
+%         \end{align}
+
+%         We now show how to compute $\qht_N$ recursively.
+
+%         \begin{align*}
+%             \ket{0}\ket{t}\ket{b}
+%             & \mapsto \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi t y}{N / 2} \Big) \ket{0} \ket{y} \ket{b} \\%& (\mathds{1} \otimes \qht_{N / 2} \otimes \mathds{1}) \\
+%             & = \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{4\pi t y}{N} \Big) \ket{0} \ket{y} \ket{b} \\
+%             & \mapsto \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{4\pi t y}{N} \Big) (\ket{0} + \ket{1}) \ket{y}\ket{b}. %& (H \otimes \mathds{1}) 
+%         \end{align*}
+
+%     \end{textblock*}
+
+% \end{frame}
+
 \begin{frame}{An efficient new algorithm for QHT}
@@
 
-        \begin{align}
-            % \frac{1}{\sqrt{N}} \sum_{y = 0}^{N - 1} \cas\Big( \frac{2\pi a y}{N} \Big) \ket{y}
-            % & = \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi a y}{N} \Big) (\ket{y} + (-1)^a \ket{y + N/2}) \nonumber \\
-            & = \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi a y}{N} \Big) \frac{1}{\sqrt{2}} (\ket{0} + (-1)^a \ket{1}) \ket{y}, \label{eq:qht-alt} 
-        \end{align}
+        \begin{algorithm}[${QHT}_N$] 
+            \begin{itemize}
+                \item   Input: quantum state $\ket{\psi} \in \mathbb{C}^N$, where $N = 2^n$
+                \item   Output: quantum state $\qht_N\ket{\psi}$ 
+            \end{itemize}
+        \end{algorithm}
+    \end{textblock*}
 
-        We now show how to compute $\qht_N$ recursively.
-
-        \begin{align*}
-            \ket{0}\ket{t}\ket{b}
-            & \mapsto \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi t y}{N / 2} \Big) \ket{0} \ket{y} \ket{b} \\%& (\mathds{1} \otimes \qht_{N / 2} \otimes \mathds{1}) \\
-            & = \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{4\pi t y}{N} \Big) \ket{0} \ket{y} \ket{b} \\
-            & \mapsto \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{4\pi t y}{N} \Big) (\ket{0} + \ket{1}) \ket{y}\ket{b}. %& (H \otimes \mathds{1}) 
-        \end{align*}
-
+        \begin{textblock*}{12cm}(0.5cm,4cm)
+            1- Initialize an ancilla qubit to $0$ to obtain the state $\ket{0}\ket{\psi}$ \\
+            2-  Compute ${1} \otimes \qht_{N / 2} \otimes {1}$ recursively.\\
+            3-  Apply $H \otimes {1}$.\\
+            4-  Apply  the controlled negation $\ket{0}\ket{y} \mapsto \ket{0}\ket{y}, \ket{1}\ket{y} \mapsto \ket{1}\ket{N / 2 -y}$ to the first two registers.\\
+            5-  Apply the unitary $U_R$.\\
+            6-  Apply $H \otimes {1}$\\
+            7-  Apply \textsc{cnot} to the first and last qubits.\\
+            8-  Apply ${1} \otimes H$.\\
+            9-  Trace out the first qubit
         \end{textblock*}
@@
 \end{frame}
-
-% \begin{frame}{An efficient new algorithm for QHT}
-
-%     \begin{textblock*}{12cm}(0.5cm,1.5cm)
-%         MM
-%         \begin{algorithm}[$\mathbb{QHT}_N$] \
-%             \label{alg:qht-N}
-%             \begin{description}[font = \normalfont\itshape, itemsep = 0mm, parsep = 0mm, topsep = 1mm]
-%                 \item [Input:] Quantum state \( \ket{\psi} \in \mathbb{C}^N \), where \( N = 2^n \).
-%                 \item [Output:] Quantum state \( \mathbb{QHT}_N \ket{\psi} \).
-%             \end{description}
-
-%             \begin{enumerate}[itemsep = 0mm, parsep = 1mm, topsep = 1mm]
-%                 \item Initialize an ancilla qubit to \( 0 \) to obtain the state \( \ket{0} \ket{\psi} \).
-%                 \item Compute \( \mathds{1} \otimes \mathbb{QHT}_{N / 2} \otimes \mathds{1} \) recursively.
-%                 \item Apply \( H \otimes \mathds{1} \).
-%                 \item Apply the controlled negation:
-%                       \[
-%                           \ket{0} \ket{y} \mapsto \ket{0} \ket{y}, \quad \ket{1} \ket{y} \mapsto \ket{1} \ket{N / 2 - y}.
-%                       \]
-%                 \item Apply the unitary \( U_R \).
-%                 \item Apply \( H \otimes \mathds{1} \).
-%                 \item Apply \textsc{cnot} to the first and last qubits.
-%                 \item Apply \( \mathds{1} \otimes H \).
-%                 \item Trace out the first qubit.
-%             \end{enumerate}
-%         \end{algorithm}
-
-%     % \end{textblock*}
-
-% \end{frame}
 
@@
     \begin{textblock*}{12cm}(0.5cm,1.5cm)
-        In the original scheme, using the quantum Fourier transform, we could directly obtain $h$ from the money state $\ket{\mathbb{Z}_N^{(h)} * x}$ and compare it to the given $h$.
+        \begin{itemize}
+            \item  In the original scheme, using the quantum Fourier transform, we could directly obtain $h$ from the money state $\ket{\mathbb{Z}_N^{(h)} * x}$ and compare it to the given $h$.
 However, this approach does not work when we use the Hartley transform.
-To address this, we design an algorithm for computing $h$ that utilizes quantum walks.
+            \vspace{1cm}
+            \item  To address this, we design an algorithm for computing $h$ that utilizes quantum walks.
+
+        \end{itemize}
 
@@
 
-        Given a state $\ket{\mathbb{Z}_N^{(h)} * x}_H$, we show how to compute $h$ using continuous-time quantum walks.
-For any $q \in \mathbb{Z}_N$, define a Cayley graph $\Gamma = (\mathbb{Z}_N, E)$ with the generating set $Q = \{-q, q\}$.
-Let $A$ denote the adjacency matrix of $\Gamma$.
+        \begin{itemize}
+            \item Given a state $\ket{\mathbb{Z}_N^{(h)} * x}_H$, we show how to compute $h$ using continuous-time quantum walks.
+            \vspace{0.5cm}
+            \item For any $q \in \mathbb{Z}_N$, define a Cayley graph $\Gamma = (\mathbb{Z}_N, E)$ with the generating set $Q = \{-q, q\}$.
+            \vspace{0.5cm}
+            \item Let $A$ denote the adjacency matrix of $\Gamma$.
 The eigenvectors and corresponding eigenvalues of $A$ are $\ket{\mathbb{Z}_N^{(h)} * x}$ and $\lambda_h = 2\cos(2\pi uh / N)$, respectively, for $h \in \mathbb{Z}_N$.
-the unitary $W = e^{iAt}$ can be efficiently simulated to exponential accuracy.
-We need the following lemma.
+            \vspace{0.5cm}
+            \item the unitary $W = e^{iAt}$ can be efficiently simulated to exponential accuracy.
+        \end{itemize}
 

### 2025-03-26 presentation.tex
new commit

@@
 
+\end{frame}
+
+\begin{frame}{Quantum Computation - Preliminaries and Notation}
+
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+        \begin{itemize}
+            \item Consider a finite Hilbert space $\mathcal{H}$ with an orthonormal set of basis states $\{ \lvert s_i \rangle \}$ for $s \in \mathcal{S}$.
+The states $s \in \mathcal{S}$ may be interpreted as the possible classical states of the system described by $\mathcal{H}$.
+\\
+            \vspace{1cm}
+            \item In general, the state of the system, $\lvert \alpha \rangle$, is a unit vector in the Hilbert space $\mathcal{H}$ and can be written as $\lvert \alpha \rangle = \sum_{s \in \mathcal{S}} a_s \lvert s \rangle$, where $\sum_{s \in \mathcal{S}} |a_s|^2 = 1$.
+\\
+            \vspace{1cm}
+            \item $\langle \alpha \rvert$ denotes the conjugate transpose of $\lvert \alpha \rangle$.
+The expression $\langle \beta \rvert \alpha \rangle$ denotes the inner product of $\lvert \alpha \rangle$ and $\lvert \beta \rangle$.
+
+        \end{itemize}
+
+    \end{textblock*}
+\end{frame}
+
+\begin{frame}{Quantum Computation - Quantum Postulates}
+
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+        \begin{itemize}
+            \item \textbf{Unitary evolution}: Quantum physics requires that the evolution of quantum states is unitary; that is, the state $\lvert \alpha \rangle$ is mapped to $U \lvert \alpha \rangle$, where $U$ satisfies $U \cdot U^{\dagger} = I$, and $U^{\dagger}$ denotes the conjugate transpose of $U$.
+            \vspace{0.5cm}
+            \item \textbf{Measurement}: We will describe here only a measurement in the orthonormal basis $\lvert s \rangle$.
+The output of the measurement of the state $\lvert \alpha \rangle$ is an element $s \in \mathcal{S}$, with probability $|\langle s \vert \alpha \rangle|^2$.
+Moreover, the new state of the system after the measurement is $\lvert s$.
+            \vspace{0.5cm}
+            \item \textbf{Combining two quantum systems}: If $\mathcal{H}_A$ and $\mathcal{H}_B$ are the Hilbert spaces of two systems, $A$ and $B$, then the joint system is described by the tensor product of the Hilbert spaces, $\mathcal{H}_A \otimes \mathcal{H}_B$.
+If the basis states for $\mathcal{H}_A$ and $\mathcal{H}_B$ are $\{ \lvert a_i \rangle \}$ and $\{ \lvert v_i \rangle \}$ respectively, then the basis states of $\mathcal{H}_A \otimes \mathcal{H}_B$ are $\{ \lvert a_i \rangle \otimes \lvert v_i \rangle \}$.
+
+        \end{itemize}
+
+    \end{textblock*}
 \end{frame}
@@
 
-\begin{frame}{Group Action Quantum Walks}
+\begin{frame}{Quantum Walks}
 
@@
 
+        \begin{itemize}
+            \item Quantum walks are quantum analogs of classical random walks and play
+            a fundamental role in quantum algorithms
+            \item  Two types: continuous-time and discrete-time
+            \item Quantum walks leverage interference to explore graphs more efficiently than classical walks
+            \item For a graph $\Gamma$, a continuous-time classical walk on $\Gamma$ is:
+            \[
+            \frac{d}{dt} q(t) = Lq(t)
+            \]
+            \item In the quantum setting,  the dynamics of the walk is given by the Schr\"{o}dinger equation:
+            \[
+                i\frac{d}{dt}\ket{\psi(t)} = L\ket{\psi(t)}
+            \]
+
+        \end{itemize}
+
+    \end{textblock*}
+\end{frame}
+
+\begin{frame}{Continuous-Time Quantum Walks}
+
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+
+        \begin{itemize}
+            \item The solution to this differential
+            equation can be written in closed form as:
+            \[
+                \ket{\psi(t)} = e^{-iLt} \ket{\psi(0)}.
+            \]
+            \item In practice, we often (including this work) use the adjacency matrix $A$ of $\Gamma$ as the Hamiltonian of the walk
+
+        \end{itemize}
+
+    \end{textblock*}
+\end{frame}
+
+\begin{frame}{Discrete-Time Quantum Walks}
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+        \begin{itemize}
+
+            \item If the $\Gamma$ has $N$ vertices, the discrete time quantum walk on $\Gamma$ is defined by a unitary operator on the finite Hilbert space $\mathbb{C}^N \times \mathbb{C}^N$ as follows:
+            \item Define the states:
+            \[ \ket{\phi_j} = \frac{1}{\sqrt{\deg(j)}} \sum_{k = 1}^N \ket{j, k}, \]
+            \item project and swap operators:
+            \[ \Pi = \sum_{j = 1}^N \ket{\phi_j} \bra{\phi_j}, \quad S = \sum_{j, k = 1}^N \ket{j, k} \bra{k, j}. \]
+            \item Then, a step of the quantum walk is defined by the unitary:
+             \[
+             W = S(2\Pi - 1)
+             \]
+
+        \end{itemize}
+    \end{textblock*}
+\end{frame}
+
+\begin{frame}{Quantum Walks on Cayley Graphs}
+
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+
+        \textit{Cayley Graphs:} \\
+        \vspace{0.3cm}
         Let $G$ be an abelian group and let $Q = \{q_1, q_2, \dots, q_k\} \subset G$ be a symmetric set, i.e., $q \in Q$ if and only if $-q \in Q$.
 The Cayley graph associated to $G$ and $Q$ is a graph $\Gamma = (V, E)$, where the vertex set is $V = G$, and the edge set $E$ consists of pairs $(a, b) \in G \times G$ such that there exists $q \in Q$ with $b = q + a$.
-The adjacency matrix of $\Gamma$ can be expressed as
+\\
+
+    \end{textblock*}
+
+\end{frame}
+
+\begin{frame}{Quantum Walks on Cayley Graphs}
+
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+
+        \textit{Cayley Graphs:} \\
+        \vspace{0.3cm}
+
+        The adjacency matrix of the Cayley graph $\Gamma = (V,E)$ can be expressed as:
         \[ A = \sum_{a \in G} \lambda_a \ket{\hat{a}} \bra{\hat{a}}, \]
-        where $\ket{\hat{a}}$ is the quantum Fourier transform of $\ket{a}$. The eigenvalues $\lambda$ are given by
+        where $\ket{\hat{a}} = \operatorname{QFT} \ket{a}$ is the quantum Fourier transform of $\ket{a}$. \\
+         \vspace{0.5cm}
+        The eigenvalues $\lambda_a$ are given by:
         \[ \lambda_a = \sum_{q \in Q} \chi(a, q). \]
         Note that the eigenvectors $\ket{\hat{a}}$ of $A$ depend only on $G$ and not on the set $Q$.
+
+    \end{textblock*}
+
+\end{frame}
+
+\begin{frame}{Quantum Walks on Cayley Graphs}
+
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+
+        \textit{Cayley Graphs:} \\
+        \vspace{0.3cm}
+        proofs:
+    \end{textblock*}
+\end{frame}
+
+\begin{frame}{Group Actions}
+
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+        Cayley graphs can also be constructed using \textit{group actions}.\\
+        \vspace{0.5cm}
+        \textit{Group Actions:}
+        \vspace{0.5cm}
+
+        For a group $G$ and a set $X$, we say that $G$ \textit{acts on} $X$ if there is a mapping $*: G \times X \to X$ that satisfies the following properties:
+        \begin{enumerate}
+            \item Compatibility: for every $a, b \in G$ and every $x \in X$, $g * (h * x) = (gh) * x$,
+            \item Identity: for the identity $1 \in G$ and every $x \in X$, $1 * x = x$. 
+        \end{enumerate}
+
+        \vspace{0.5 cm}
+        \begin{itemize}
+            \item  We use the notation $(G, X, *)$ to denote a group $G$ acting on a set $X$ through the action $*$.
+            \item  A group action is called \textit{regular} if for every $x, y \in X$ there exists a unique $g \in G$ such that $g * x = y$.
+        \end{itemize}
+
+    \end{textblock*}
+
+\end{frame}
+
+\begin{frame}{Cayley Graphs with Group Actions}
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+
+     Given a regular group action $(G, X, *)$ with a fixed element $x \in X$ and a set  $Q = \{q_1, q_2, \dots, q_k\} \subset G$, let $\Gamma = (X, E)$ be a graphs with vertex set $X$ and edge set consisting of pairs $(x, y) \in X \times X$ such that $y = q * x$ for some $q \in Q$.
+The adjacency matrix of $\Gamma$ is
+    \[ A = \sum_{h \in G} \lambda_h \ket{G^{(h)} * x} \bra{G^{(h)} * x}, \]
+    where $\lambda_h = \sum_{q \in Q} \chi(h, q)$. Again, the eigenvectors $\ket{G^{(h)} * x}$ depend only on $G$.
+
+    \end{textblock*}
+\end{frame}
+
+\begin{frame}{Cayley Graphs with Group Actions}
+
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+        proofs:
+
     \end{textblock*}
@@
 
-        Cayley graphs can also be constructed using group actions.
         Given a regular group action $(G, X, *)$ with a fixed element $x \in X$ and a set  $Q = \{q_1, q_2, \dots, q_k\} \subset G$, let $\Gamma = (X, E)$ be a graphs with vertex set $X$ and edge set consisting of pairs $(x, y) \in X \times X$ such that $y = q * x$ for some $q \in Q$.
@@
             \vspace{0.5cm}
-            \item For any $q \in \mathbb{Z}_N$, define a Cayley graph $\Gamma = (\mathbb{Z}_N, E)$ with the generating set $Q = \{-q, q\}$.
+            \item For any $q \in \mathbb{Z}_N$, define a Cayley graph $\Gamma = (\mathbb{Z}_N, E)$ with the generating set $Q = \{-u, u\}$.
             \vspace{0.5cm}
@@
 
+\begin{frame}{Computing the serial Number}
+
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+        Lemma: The money state $\ket{\mathbb{Z}_N^{(h)} * x}_H$ is an eigenstate of $W$ with eigenvalue $e^{i\lambda_h t}$.
+        \vspace{1cm}
+
+        $e^{iAt} \ket{\mathbb{Z}_N^{(h)} * x}_H$ = $e^{i\lambda_{h}t} \ket{\mathbb{Z}_N^{(h)} * x}_H$
+
+        \vspace{1cm}
+        If we choose $t = \operatorname{poly}(\log N)$, it follows from Lemma that we can run the phase estimation algorithm with the unitary $W$ and the eigenstate $\ket{\mathbb{Z}_N^{(h)} * x}_H$ to compute an estimate $\tilde{\lambda}_h$ of $\lambda_h$ such that %$\abs{\tilde{\lambda}_h - \lambda_h} \le 1 / poly(log N)$.
+        % \operatorname{poly}(\log N)
+        \[
+        |\tilde{\lambda}_h - \lambda_h| \leq \frac{1}{\operatorname{poly}(\log N)}
+        \]
+
+    \end{textblock*}
+
+ \end{frame}
+
 % End

### 2025-03-28 presentation.tex
new commit

@@
             \item Define the states:
-            \[ \ket{\phi_j} = \frac{1}{\sqrt{\deg(j)}} \sum_{k = 1}^N \ket{j, k}, \]
+            \[ \ket{\phi_j} = \frac{1}{\sqrt{\deg(j)}} \sum_{k = 1}^N \sqrt{P_{jk}}\ket{j, k}, \]
             \item project and swap operators:
@@
         \vspace{0.3cm}
-        proofs:
+        \textit{Proof}:
+        \[
+        A\ket{\hat{a}} = A.\frac{1}{\sqrt{|G|}}\sum_{y \in G}\chi(a,y)\ket{y} = \frac{1}{\sqrt{|G|}}\sum_{y \in G}\chi(a,y).A\ket{y}
+        \]
+        \[
+        = \frac{1}{\sqrt{|G|}}\sum_{y \in G}\chi(a,y).\sum_{q \in Q}\ket{qy}
+        \]
+        Consider $\beta = qy$. Then:
+        \[
+         = \frac{1}{\sqrt{|G|}}\sum_{q \in Q}\chi(a,q)\sum_{\beta}\chi(a,\beta)\ket{\beta} = \sum_{q \in Q}\chi(a,q) . \ket{\hat{a}}
+        \]
+        \[
+         = \lambda_a\ket{\hat{a}}
+        \]
     \end{textblock*}
@@
 The adjacency matrix of $\Gamma$ is
-    \[ A = \sum_{h \in G} \lambda_h \ket{G^{(h)} * x} \bra{G^{(h)} * x}, \]
+    \[
+    A = \sum_{h \in G} \lambda_h \ket{G^{(h)} * x} \bra{G^{(h)} * x}, 
+    \]
     where $\lambda_h = \sum_{q \in Q} \chi(h, q)$. Again, the eigenvectors $\ket{G^{(h)} * x}$ depend only on $G$.
@@
     \begin{textblock*}{12cm}(0.5cm,1.5cm)
-        proofs:
+        \textit{Proof}:
+
+        \[
+        A\ket{G^{(h)}*x} = \frac{1}{\sqrt{|G|}}.\sum_{g \in G}\chi(g,h) A.\ket{g*x}
+        \]
+
+        \[
+        = A\ket{G^{(h)}*x} = \frac{1}{\sqrt{|G|}}.\sum_{g \in G}\chi(g,h)\sum_{q \in Q}\ket{q*(g*x)}
+        \]
+        Consider $\beta = qg$. Then:
+        \[
+        = = \frac{1}{\sqrt{|G|}}\sum_{q \in Q}\sum_{\beta \in G}\chi(\beta,h)\chi(q,h)\ket{\beta * x}
+        \]
+
+        \[
+        = \sum_{q \in Q}\chi(q,h).\ket{G^{(h)}*x} = \lambda_h \ket{G^{(h)}*x}
+        \]
+
+    \end{textblock*}
+
+\end{frame}
+
+\begin{frame}{The cmpIndex Algorithm}
+
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+        Given a state $\ket{G^{(h)} * x}$, there is an efficient algorithm for computing $h$.
+        Specifically, there is a unitary operator that performs the transformation $\ket{G^{(h)} * x} \ket{0} \mapsto \ket{G^{(h)} * x} \ket{h}$:
+
+        \[
+        \ket{G^{(h)} * x}\ket{0} \mapsto \ket{G^{(h)} * x} \frac{1}{\sqrt{|G|}}\sum_{k \in G}\ket{k}
+        \]
+        And then apply the unitary $\sum_{k \in G}U_k \otimes \ket{k}\bra{k}$:
+
+        \[
+        \mapsto \frac{1}{\sqrt{|G|}}\sum_{k \in G}\ket{G^{(h)}*x}\chi(-k,h)\ket{k}
+        \]
+
+        Finally, applying the inverse quantum Fourier transform to the second register yields:
+
+        \[
+           \mapsto  \ket{G^{(h)}*x}\ket{h}
+        \]
+    \end{textblock*}
+
+\end{frame}
+
+\begin{frame}{Simulating continuous-time walks}
+
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+
+        \[
+        \ket{\phi_{j0}} := \frac{1}{\sqrt{d}}\sum_{l \in F_j}(\sqrt{\frac{H^*_{jl}}{K}}\ket{0} + \sqrt{1-\frac{|H^*_{jl}|}{K}}\ket{1})
+        \]
+
+        \[
+        \ket{\phi_{j1}} := \ket{0}\ket{1}
+        \]
+
+        \[
+        T := \sum_{j=0}^{N-1}\sum_{b \in {\{0,1\}}}(\ket{j}\bra{j}\otimes\ket{b}\bra{b})\otimes\ket{\phi_{jb}}
+        \]
+
+        \[
+        W = iS(2TT^* - 1)
+        \]
+
+        \[
+        S\ket{j_1,b_1}\ket{j_2,b_2} = \ket{j_2,b_2}\ket{j_1,b_1}
+        \]
+
+    \end{textblock*}
+
+\end{frame}
+
+\begin{frame}{Simulating continuous-time walks}
+
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+
+       \[
+       e^{-iAt} = \operatorname{QFT_G}(\sum_{a \in G}e^{-i\lambda_at}\ket{a}\bra{a})\operatorname{QFT^*_G}
+       \]
+
+    \end{textblock*}
+
+\end{frame}
+
+\begin{frame}{Simulating group action quantum walks}
+
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+
+        \[
+        e^{-iAt} = \sum_{h \in G}\ket{G^{(h)}*x}\bra{G^{(h)}*x}
+        \]
+
+        \[
+        T := \sum_{y \in X}\sum_{b \in {\{0,1\}}}(\ket{j}\bra{j}\otimes\ket{b}\bra{b})\otimes\ket{\phi_{yb}}
+        \]
+
+        \[
+        = \sum_{y \in X}\sum_{b \in {\{0,1\}}}\ket{y}\ket{b}\ket{\phi_{yb}}\bra{y}\bra{b}
+        \]
+
+        \[
+            \ket{\phi_{y0}} = \frac{1}{\sqrt{|Q|}}\sum_{q \in Q}\ket{q*y}\ket{0}
+        \]
+
+    \end{textblock*}
+
+\end{frame}
+
+\begin{frame}{Simulating group action quantum walks}
+
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+
+        % \begin{align*}
+        %     2\ket{0} \bra{0} \otimes TT^* - 1
+        %     & = 2\ket{0} \bra{0} \otimes \sum_{y \in X} \sum_{b \in \{0, 1\}} \ket{y, b} \ket{\phi_{yb}} \bra{y, b} \bra{\phi_{yb}} - 1 \\
+
+        %     & = U_T (2 \ket{0} \bra{0} \otimes 1_{X, b} \otimes \ket{0, 0} \bra{0, 0} - 1) U_T^*.
+
+        % \end{align*}
+
+        \[
+        2\ket{0} \bra{0} \otimes TT^* - 1 = 2\ket{0} \bra{0} \otimes \sum_{y \in X} \sum_{b \in \{0, 1\}} \ket{y, b} \ket{\phi_{yb}} \bra{y, b} \bra{\phi_{yb}} - 1 
+        \]
+
+        \[
+        = 2\sum_{y \in X} \sum_{b \in \{0, 1\}} \ket{0} \ket{y, b} \ket{\phi_{yb}} \bra{0} \bra{y, b} \bra{\phi_{yb}} - 1 
+        \]
+
+        \[
+        = U_T \Big( 2\sum_{y \in X} \sum_{b \in \{0, 1\}} \ket{0} \ket{y, b} \ket{0, 0} \bra{0} \bra{y, b} \bra{0, 0} - 1 \Big) U_T^* 
+        \]
+
+        \[
+        = U_T (2 \ket{0} \bra{0} \otimes 1_{X, b} \otimes \ket{0, 0} \bra{0, 0} - 1) U_T^*
+        \]
+
+        Now, for any state $\ket{\psi}$:
+
+        \[
+        (2\ket{0}\bra{0}\otimes TT^* - 1)\ket{0}\ket{\psi} = \ket{0}(2TT^*-1)\ket{\psi}
+        \]
 

### 2025-03-29 presentation.tex
new commit

@@
 
-\begin{frame}{Program and Courses Taken}
+% \begin{frame}{Program and Courses Taken}
 
-    \begin{textblock*}{12cm}(0.5cm,1.5cm)
-       \begin{itemize}
-        \item Program: M.A.Sc in Software Engineering
-        \vspace{1cm}
-        \item CAS 701,  Logic \& Discrete Mathematics
-        \item COMPSCI 6TE3, Continuous optimization
-        \item CAS 721, Combinatorics \& Computing
-        \item CAS 741, Development of Scientific Computation Software
-       \end{itemize}
-    \end{textblock*}
+%     \begin{textblock*}{12cm}(0.5cm,1.5cm)
+%        \begin{itemize}
+%         \item Program: M.A.Sc in Software Engineering
+%         \vspace{1cm}
+%         \item CAS 701,  Logic \& Discrete Mathematics
+%         \item COMPSCI 6TE3, Continuous optimization
+%         \item CAS 721, Combinatorics \& Computing
+%         \item CAS 741, Development of Scientific Computation Software
+%        \end{itemize}
+%     \end{textblock*}
 
-    \title{SDSD}
+%     \title{SDSD}
 
-\end{frame}
+% \end{frame}
 
-\begin{frame}{Seminars}
+% \begin{frame}{Seminars}
 
-    \begin{textblock*}{12cm}(0.5cm,1.5cm)
-       \begin{itemize}
-        \item I have participated in 6 seminars during my program.
-       \end{itemize}
-    \end{textblock*}
+%     \begin{textblock*}{12cm}(0.5cm,1.5cm)
+%        \begin{itemize}
+%         \item I have participated in 6 seminars during my program.
+%        \end{itemize}
+%     \end{textblock*}
 
-\end{frame}
+% \end{frame}
 
-\begin{frame}{Poster}
+% \begin{frame}{Poster}
 
-    \begin{figure}
-        \centering
-        \includegraphics[width=1\textwidth]{poster.png}
-        \caption{Presented at Nov. 6, 2024}
-    \end{figure}
+%     \begin{figure}
+%         \centering
+%         \includegraphics[width=1\textwidth]{poster.png}
+%         \caption{Presented at Nov. 6, 2024}
+%     \end{figure}
 
-\end{frame}
+% \end{frame}
 
@@
 
-\begin{frame}{The Hartley Transform}
+\begin{frame}{Quantum Walks}
 
     \begin{textblock*}{12cm}(0.5cm,1.5cm)
+
+        \begin{itemize}
+            \item Quantum walks are quantum analogs of classical random walks and play
+            a fundamental role in quantum algorithms
+            \item  Two types: continuous-time and discrete-time
+            \item Quantum walks leverage interference to explore graphs more efficiently than classical walks
+            \item For a graph $\Gamma$, a continuous-time classical walk on $\Gamma$ is:
+            \[
+            \frac{d}{dt} q(t) = Lq(t)
+            \]
+            \item In the quantum setting,  the dynamics of the walk is given by the Schr\"{o}dinger equation:
+            \[
+                i\frac{d}{dt}\ket{\psi(t)} = L\ket{\psi(t)}
+            \]
+
+        \end{itemize}
+
+    \end{textblock*}
+\end{frame}
+
+\begin{frame}{Continuous-Time Quantum Walks}
+
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+
+        \begin{itemize}
+            \item The solution to this differential
+            equation can be written in closed form as:
+            \[
+                \ket{\psi(t)} = e^{-iLt} \ket{\psi(0)}.
+            \]
+            \item In practice, we often (including this work) use the adjacency matrix $A$ of $\Gamma$ as the Hamiltonian of the walk
+
+        \end{itemize}
+
+    \end{textblock*}
+\end{frame}
+
+\begin{frame}{Example of a Continuous Quantum Walk}
+
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+
+    \end{textblock*}
+\end{frame}
+
+\begin{frame}{Discrete-Time Quantum Walks}
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+        \begin{itemize}
+
+            \item If the $\Gamma$ has $N$ vertices, the discrete time quantum walk on $\Gamma$ is defined by a unitary operator on the finite Hilbert space $\mathbb{C}^N \times \mathbb{C}^N$ as follows:
+            \item Define the states:
+            \[ \ket{\phi_j} = \frac{1}{\sqrt{\deg(j)}} \sum_{k = 1}^N \sqrt{P_{jk}}\ket{j, k}, \]
+            \item project and swap operators:
+            \[ \Pi = \sum_{j = 1}^N \ket{\phi_j} \bra{\phi_j}, \quad S = \sum_{j, k = 1}^N \ket{j, k} \bra{k, j}. \]
+            \item Then, a step of the quantum walk is defined by the unitary:
+             \[
+             W = S(2\Pi - 1)
+             \]
+
+        \end{itemize}
+    \end{textblock*}
+\end{frame}
+
+\begin{frame}{Example of a Discrete-Time Quantum Walk}
+
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+
+    \end{textblock*}
+\end{frame}
+
+\begin{frame}{Continuous vs Discrete Quantum Walks }
+
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+
+    \end{textblock*}
+\end{frame}
+
+\begin{frame}{Quantum Walks on Cayley Graphs}
+
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+
+        \textit{Cayley Graphs:} \\
+        \vspace{0.3cm}
+        Let $G$ be an abelian group and let $Q = \{q_1, q_2, \dots, q_k\} \subset G$ be a symmetric set, i.e., $q \in Q$ if and only if $-q \in Q$.
+The Cayley graph associated to $G$ and $Q$ is a graph $\Gamma = (V, E)$, where the vertex set is $V = G$, and the edge set $E$ consists of pairs $(a, b) \in G \times G$ such that there exists $q \in Q$ with $b = q + a$.
+\\
+
+    \end{textblock*}
+
+\end{frame}
+
+\begin{frame}{An Example of a Cayley Graph}
+
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+
+    \end{textblock*}
+
+\end{frame}
+
+\begin{frame}{Quantum Walks on Cayley Graphs}
+
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+
+        \textit{Cayley Graphs:} \\
+        \vspace{0.3cm}
+
+        The adjacency matrix of the Cayley graph $\Gamma = (V,E)$ can be expressed as:
+        \[ A = \sum_{a \in G} \lambda_a \ket{\hat{a}} \bra{\hat{a}}, \]
+        where $\ket{\hat{a}} = \operatorname{QFT_G} \ket{a}$ is the \textit{Quantum Fourier transform (QFT)} of $\ket{a}$. \\
+         \vspace{0.5cm}
+
+        \vspace{2cm}
+
+        ... But, What is QFT??
+    \end{textblock*}
+
+\end{frame}
+
+\begin{frame}{Quantum Fourier Transform (QFT)}
+
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+
+    Let $G$ be an abelian group.
+The set of characters of $G$, denoted by $\hat{G}$, is the set of homomorphisms $\chi(a, \cdot): G \to \mathbb{C}$ where $a \in G$.
+If $G \cong \mathbb{Z}_{N_1} \oplus \cdots \oplus \mathbb{Z}_{N_k}$ then the character $\chi(a, \cdot)$ can be explicitly written as
+    \[ \chi(a, x) = \omega_{N_1}^{a_1x_1} \cdots \omega_{N_k}^{a_kx_k} \]
+
+    where $\omega_M = \exp(2\pi i/ M)$ is a primitive $M$-th root of unity. The Fourier transform of a function $f: G \to \mathbb{C}$ is given by
+    \[ \hat{f}(a) = \frac{1}{\sqrt{|G|}} \sum_{x \in G} \chi(a, x) f(x). \]
+    The quantum Fourier transform:
+
+    \[
+        \sum_{g \in G} f(g) \ket{g} \mapsto \sum_{x \in G} \hat{f}(x)\ket{x}
+    \]
+
+    \end{textblock*}
+
+\end{frame}
+
+\begin{frame}{Quantum Walks on Cayley Graphs}
+
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+
+        \textit{Cayley Graphs:} \\
+        \vspace{0.3cm}
+
+        The adjacency matrix of the Cayley graph $\Gamma = (V,E)$ can be expressed as:
+        \[ A = \sum_{a \in G} \lambda_a \ket{\hat{a}} \bra{\hat{a}}, \]
+        Where $\ket{\hat{a}} = \operatorname{QFT}_G(\ket{a}) =  \frac{1}{\sqrt{|G|}}\sum_{g \in G}\chi(a,g)\ket{g}$. \\
+        The eigenvalues $\lambda_a$ are given by:
+        \[ \lambda_a = \sum_{q \in Q} \chi(a, q). \]
+        \begin{itemize}
+            \item  Note that the eigenvectors $\ket{\hat{a}}$ of $A$ depend only on $G$ and not on the set $Q$.
+        \end{itemize}
+
+    \end{textblock*}
+
+\end{frame}
+
+\begin{frame}{Quantum Walks on Cayley Graphs}
+
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+
+        \textit{Cayley Graphs:} \\
+        \vspace{0.3cm}
+        \textit{Proof}:
+        \[
+        A\ket{\hat{a}} = A.\frac{1}{\sqrt{|G|}}\sum_{y \in G}\chi(a,y)\ket{y} = \frac{1}{\sqrt{|G|}}\sum_{y \in G}\chi(a,y).A\ket{y}
+        \]
+        \[
+        = \frac{1}{\sqrt{|G|}}\sum_{y \in G}\chi(a,y).\sum_{q \in Q}\ket{qy}
+        \]
+        Consider $\beta = qy$. Then:
+        \[
+         = \frac{1}{\sqrt{|G|}}\sum_{q \in Q}\chi(a,q)\sum_{\beta}\chi(a,\beta)\ket{\beta} = \sum_{q \in Q}\chi(a,q) . \ket{\hat{a}}
+        \]
+        \[
+         = \lambda_a\ket{\hat{a}}
+        \]
+    \end{textblock*}
+\end{frame}
+
+\begin{frame}{Group Actions}
+
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+        Cayley graphs can also be constructed using \textit{group actions}.\\
+        \vspace{0.5cm}
+        \textit{Group Actions:}
+        \vspace{0.5cm}
+
+        For a group $G$ and a set $X$, we say that $G$ \textit{acts on} $X$ if there is a mapping $*: G \times X \to X$ that satisfies the following properties:
+        \begin{enumerate}
+            \item Compatibility: for every $a, b \in G$ and every $x \in X$, $g * (h * x) = (gh) * x$,
+            \item Identity: for the identity $1 \in G$ and every $x \in X$, $1 * x = x$. 
+        \end{enumerate}
+
+        \vspace{0.5 cm}
+        \begin{itemize}
+            \item  We use the notation $(G, X, *)$ to denote a group $G$ acting on a set $X$ through the action $*$.
+            \item  A group action is called \textit{regular} if for every $x, y \in X$ there exists a unique $g \in G$ such that $g * x = y$.
+        \end{itemize}
+
+    \end{textblock*}
+
+\end{frame}
+
+\begin{frame}{Cayley Graphs with Group Actions}
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+
+    Given a regular group action $(G, X, *)$ with a fixed element $x \in X$ and a set  $Q = \{q_1, q_2, \dots, q_k\} \subset G$, let $\Gamma = (X, E)$ be a graphs with vertex set $X$ and edge set consisting of pairs $(x, y) \in X \times X$ such that $y = q * x$ for some $q \in Q$.
+The adjacency matrix of $\Gamma$ is
+    \[
+    A = \sum_{h \in G} \lambda_h \ket{G^{(h)} * x} \bra{G^{(h)} * x}, 
+    \]
+    Where:
+    \[
+        \ket{G^{(h)} * x} = \frac{1}{\sqrt{|G|}}\sum_{g \in G}\chi(g,h)\ket{g*x}
+    \]
+    And $\lambda_h = \sum_{q \in Q} \chi(h, q)$. 
+    \vspace{0.5cm}
+    \begin{itemize}
+        \item Again, the eigenvectors $\ket{G^{(h)} * x}$ depend only on $G$.
+    \end{itemize}
+    \end{textblock*}
+\end{frame}
+
+\begin{frame}{Cayley Graphs with Group Actions}
+
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+        \textit{Proof}:
+
+        \[
+        A\ket{G^{(h)}*x} = \frac{1}{\sqrt{|G|}}.\sum_{g \in G}\chi(g,h) A.\ket{g*x}
+        \]
+
+        \[
+        = A\ket{G^{(h)}*x} = \frac{1}{\sqrt{|G|}}.\sum_{g \in G}\chi(g,h)\sum_{q \in Q}\ket{q*(g*x)}
+        \]
+        Consider $\beta = qg$. Then:
+        \[
+        = = \frac{1}{\sqrt{|G|}}\sum_{q \in Q}\sum_{\beta \in G}\chi(\beta,h)\chi(q,h)\ket{\beta * x}
+        \]
+
+        \[
+        = \sum_{q \in Q}\chi(q,h).\ket{G^{(h)}*x} = \lambda_h \ket{G^{(h)}*x}
+        \]
+
+    \end{textblock*}
+
+\end{frame}
+
+\begin{frame}{The cmpIndex Algorithm}
+
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+        Given a state $\ket{G^{(h)} * x}$, there is an efficient algorithm for computing $h$.
+        Specifically, there is a unitary operator that performs the transformation $\ket{G^{(h)} * x} \ket{0} \mapsto \ket{G^{(h)} * x} \ket{h}$:
+
+        \[
+        \ket{G^{(h)} * x}\ket{0} \mapsto \ket{G^{(h)} * x} \frac{1}{\sqrt{|G|}}\sum_{k \in G}\ket{k}
+        \]
+        And then apply the unitary $\sum_{k \in G}U_k \otimes \ket{k}\bra{k}$:
+
+        \[
+        \mapsto \frac{1}{\sqrt{|G|}}\sum_{k \in G}\ket{G^{(h)}*x}\chi(-k,h)\ket{k}
+        \]
+
+        Finally, applying the inverse quantum Fourier transform to the second register yields:
+
+        \[
+           \mapsto  \ket{G^{(h)}*x}\ket{h}
+        \]
+    \end{textblock*}
+
+\end{frame}
+
+\begin{frame}{Simulating continuous-time walks}
+
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+
+        \[
+        \ket{\phi_{j0}} := \frac{1}{\sqrt{d}}\sum_{l \in F_j}(\sqrt{\frac{H^*_{jl}}{K}}\ket{0} + \sqrt{1-\frac{|H^*_{jl}|}{K}}\ket{1})
+        \]
+
+        \[
+        \ket{\phi_{j1}} := \ket{0}\ket{1}
+        \]
+
+        \[
+        T := \sum_{j=0}^{N-1}\sum_{b \in {\{0,1\}}}(\ket{j}\bra{j}\otimes\ket{b}\bra{b})\otimes\ket{\phi_{jb}}
+        \]
+
+        \[
+        W = iS(2TT^* - 1)
+        \]
+
+        \[
+        S\ket{j_1,b_1}\ket{j_2,b_2} = \ket{j_2,b_2}\ket{j_1,b_1}
+        \]
+
+    \end{textblock*}
+
+\end{frame}
+
+\begin{frame}{Simulating continuous-time walks}
+
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+
+       \[
+       e^{-iAt} = \operatorname{QFT_G}(\sum_{a \in G}e^{-i\lambda_at}\ket{a}\bra{a})\operatorname{QFT^*_G}
+       \]
+
+    \end{textblock*}
+
+\end{frame}
+
+% \begin{frame}{Simulating group action quantum walks}
+
+%     \begin{textblock*}{12cm}(0.5cm,1.5cm)
+
+%         \[
+%         e^{-iAt} = \sum_{h \in G}\ket{G^{(h)}*x}\bra{G^{(h)}*x}
+%         \]
+
+%         \[
+%         T := \sum_{y \in X}\sum_{b \in {\{0,1\}}}(\ket{j}\bra{j}\otimes\ket{b}\bra{b})\otimes\ket{\phi_{yb}}
+%         \]
+
+%         \[
+%         = \sum_{y \in X}\sum_{b \in {\{0,1\}}}\ket{y}\ket{b}\ket{\phi_{yb}}\bra{y}\bra{b}
+%         \]
+
+%         \[
+%             \ket{\phi_{y0}} = \frac{1}{\sqrt{|Q|}}\sum_{q \in Q}\ket{q*y}\ket{0}
+%         \]
+
+%     \end{textblock*}
+
+% \end{frame}
+
+\begin{frame}{Simulating group action quantum walks}
+
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+
+        % \begin{align*}
+        %     2\ket{0} \bra{0} \otimes TT^* - 1
+        %     & = 2\ket{0} \bra{0} \otimes \sum_{y \in X} \sum_{b \in \{0, 1\}} \ket{y, b} \ket{\phi_{yb}} \bra{y, b} \bra{\phi_{yb}} - 1 \\
+
+        %     & = U_T (2 \ket{0} \bra{0} \otimes 1_{X, b} \otimes \ket{0, 0} \bra{0, 0} - 1) U_T^*.
+
+        % \end{align*}
+
+        \[
+        2\ket{0} \bra{0} \otimes TT^* - 1 = 2\ket{0} \bra{0} \otimes \sum_{y \in X} \sum_{b \in \{0, 1\}} \ket{y, b} \ket{\phi_{yb}} \bra{y, b} \bra{\phi_{yb}} - 1 
+        \]
+
+        \[
+        = 2\sum_{y \in X} \sum_{b \in \{0, 1\}} \ket{0} \ket{y, b} \ket{\phi_{yb}} \bra{0} \bra{y, b} \bra{\phi_{yb}} - 1 
+        \]
+
+        \[
+        = U_T \Big( 2\sum_{y \in X} \sum_{b \in \{0, 1\}} \ket{0} \ket{y, b} \ket{0, 0} \bra{0} \bra{y, b} \bra{0, 0} - 1 \Big) U_T^* 
+        \]
+
+        \[
+        = U_T (2 \ket{0} \bra{0} \otimes 1_{X, b} \otimes \ket{0, 0} \bra{0, 0} - 1) U_T^*
+        \]
+
+        Now, for any state $\ket{\psi}$:
+
+        \[
+        (2\ket{0}\bra{0}\otimes TT^* - 1)\ket{0}\ket{\psi} = \ket{0}(2TT^*-1)\ket{\psi}
+        \]
+
+    \end{textblock*}
+
+\end{frame}
+
+\begin{frame}{Group Action Quantum Walks}
+
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+
+        Given a regular group action $(G, X, *)$ with a fixed element $x \in X$ and a set  $Q = \{q_1, q_2, \dots, q_k\} \subset G$, let $\Gamma = (X, E)$ be a graphs with vertex set $X$ and edge set consisting of pairs $(x, y) \in X \times X$ such that $y = q * x$ for some $q \in Q$.
+The adjacency matrix of $\Gamma$ is
+        \[ A = \sum_{h \in G} \lambda_h \ket{G^{(h)} * x} \bra{G^{(h)} * x}, \]
+        where:
+        \begin{itemize}
+            \item $\lambda_h = \sum_{q \in Q} \chi(h, q)$
+            \item the eigenvectors $\ket{G^{(h)} * x}$ depend only on $G$
+        \end{itemize}
+
+    \end{textblock*}
+
+\end{frame}
+
+\begin{frame}{Application: Quantum Money}
+
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+
+        A public-key quantum money scheme consists of two QPT algorithms:
+        \vspace{1cm} 
+        \begin{itemize}
+        \item $\gen(1^\lambda)$: This algorithm takes a security parameter $\lambda$ as input and outputs a pair $(s, \rho_s)$, where $s$ is a binary string called the serial number, and $\rho_s$ is a quantum state called the banknote.
+The pair $(s, \rho_s)$, or simply $\rho_s$, is sometimes denoted by $\$$.
+
+        \vspace{1cm}
+        \item $\ver(s, \rho_s)$: This algorithm takes a serial number and an alleged banknote as input and outputs either $1$ (accept) or $0$ (reject).
+        \end{itemize}
+
+    \end{textblock*}
+
+\end{frame}
+
+\begin{frame}{Quantum Money From Group Actions}
+
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+
+        \begin{itemize}
+        \item $\gen(1^\lambda)$. Begin with the state $\ket{0}\ket{x_\lambda}$, and apply the quantum Fourier transform over $G_\lambda$ to the first register producing the superposition
+        \[ \frac{1}{\sqrt{{|X_\lambda|}}} \sum_{g \in G_\lambda} \ket{g}\ket{x_\lambda}. \]
+        Next, apply the unitary transformation $\ket{h}\ket{y} \mapsto \ket{h}\ket{h * y}$ to this state, followed by the quantum Fourier transform on the first register. This results in
+        \[ \frac{1}{{|G_\lambda|}} \sum_{h \in G_\lambda} \sum_{g \in G_\lambda} \chi(g, h) \ket{h}\ket{g * x_\lambda} = \frac{1}{\sqrt{{|G_\lambda|}}} \sum_{h \in G_\lambda} \ket{h} \ket{G^{(h)} * x_\lambda} \]
+
+        \end{itemize}
+
+    \end{textblock*}
+
+\end{frame}
+
+\begin{frame}{Quantum Money From Group Actions}
+
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+
+        \begin{itemize}
+        \item $\ver(h, \ket{\psi})$.
+First, check whether $\ket{\psi}$ has support in $X_\lambda$.
+If not, return $0$.
+Then, apply $\comph$ to the state $\ket{\psi}\ket{0}$, and measure the second register to obtain some $h' \in G_\lambda$.
+If $h' = h$, return $1$; otherwise return $0$.
+        \end{itemize}
+
+    \end{textblock*}
+
+\end{frame}
+
+\begin{frame}{Quantum Money With The Hartley Transform}
+
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+        \textit{Hartley Transform:}\\
         item Let $N$ be a positive integer, and let $\mathbb{Z}_N$ be the additive cyclic group of integers modulo $N$.
@@
 
+\begin{frame}{Quantum Money With The Hartley Transform}
+
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+
+        \begin{itemize}
+            \item $\gen$. Begin with the state $\ket{0}\ket{x}$, and apply the quantum Hartley transform over $\mathbb{Z}_N$ to the first register producing the superposition
+            \[ \frac{1}{\sqrt{N}} \sum_{g \in \mathbb{Z}_N} \ket{g}\ket{x}. \]
+            Next, apply the unitary $\ket{h}\ket{y} \mapsto \ket{h}\ket{h * y}$ to this state, followed by a $\qht_N$ on the first register. This results in
+            \[ \frac{1}{N} \sum_{h \in \mathbb{Z}_N} \sum_{g \in \mathbb{Z}_N} \cas\Big(\frac{2\pi gh}{N}\Big) \ket{h}\ket{g * x} = \frac{1}{\sqrt{N}} \sum_{h \in \mathbb{Z}_N} \ket{h} \ket{\mathbb{Z}_N^{(h)} * x}_H \]
+            Measure the first register to obtain a random $h \in \mathbb{Z}_N$, collapsing the state to $\ket{\mathbb{Z}_N^{(h)} * x}_H$. Return the pair $(h, \ket{\mathbb{Z}_N^{(h)} * x}_H)$.
+
+        \end{itemize}
+
+    \end{textblock*}
+
+\end{frame}
+
+\begin{frame}{Quantum Money With The Hartley Transform}
+
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+        \begin{itemize}
+            \item  In the original scheme, using the quantum Fourier transform, we could directly obtain $h$ from the money state $\ket{\mathbb{Z}_N^{(h)} * x}$ and compare it to the given $h$.
+However, this approach does not work when we use the Hartley transform.
+            \vspace{1cm}
+            \item  To address this, we design an algorithm for computing $h$ that utilizes quantum walks.
+
+        \end{itemize}
+
+    \end{textblock*}
+
+\end{frame}
+
+\begin{frame}{Computing the serial Number}
+
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+
+        \begin{itemize}
+            \item Given a state $\ket{\mathbb{Z}_N^{(h)} * x}_H$, we show how to compute $h$ using continuous-time quantum walks.
+            \vspace{0.5cm}
+            \item For any $q \in \mathbb{Z}_N$, define a Cayley graph $\Gamma = (\mathbb{Z}_N, E)$ with the generating set $Q = \{-u, u\}$.
+            \vspace{0.5cm}
+            \item Let $A$ denote the adjacency matrix of $\Gamma$.
+The eigenvectors and corresponding eigenvalues of $A$ are $\ket{\mathbb{Z}_N^{(h)} * x}$ and $\lambda_h = 2\cos(2\pi uh / N)$, respectively, for $h \in \mathbb{Z}_N$.
+            \vspace{0.5cm}
+            \item the unitary $W = e^{iAt}$ can be efficiently simulated to exponential accuracy.
+        \end{itemize}
+
+    \end{textblock*}
+
+ \end{frame}
+
+\begin{frame}{Computing the serial Number}
+
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+        Lemma: The money state $\ket{\mathbb{Z}_N^{(h)} * x}_H$ is an eigenstate of $W$ with eigenvalue $e^{i\lambda_h t}$.
+        % \vspace{1cm}
+
+        \textit{Proof:}
+        \begin{align*}
+            e^{iAt} \ket{\mathbb{Z}_N^{(h)} * x}_H
+            & = \sum_{g \in \mathbb{Z}_N} e^{i\lambda_gt} \ket{\mathbb{Z}_N^{(g)} * x}\braket{\mathbb{Z}_N^{(g)} * x|\mathbb{Z}_N^{(h)} * x}_H 
+        \end{align*}
+
+        \[
+        =\sum_{g \in \mathbb{Z}_N} e^{i\lambda_gt} \ket{\mathbb{Z}_N^{(g)} * x} \bra{\mathbb{Z}_N^{(g)} * x} \Big( \frac{1 - i}{2} \ket{\mathbb{Z}_N^{(h)} * x} + \frac{1 + i}{2} \ket{\mathbb{Z}_N^{(-h)} * x} \Big)
+        \]
+
+        \[
+        =e^{i\lambda_{h}t} \frac{1 - i}{2} \ket{\mathbb{Z}_N^{(h)} * x} + \frac{1 + i}{2} e^{i\lambda_{-h}t} \ket{\mathbb{Z}_N^{(-h)} * x} 
+        \]
+
+        \[
+        =e^{i\lambda_{h}t} \ket{\mathbb{Z}_N^{(h)} * x}_H,
+        \]
+
+        where the last equality follows from the fact that $\lambda_h = \lambda_{-h}$.
+    \end{textblock*}
+
+ \end{frame}
+
+\begin{frame}{Computing the serial Number}
+
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+        Lemma: The money state $\ket{\mathbb{Z}_N^{(h)} * x}_H$ is an eigenstate of $W$ with eigenvalue $e^{i\lambda_h t}$.
+        \vspace{1cm}
+
+        $e^{iAt} \ket{\mathbb{Z}_N^{(h)} * x}_H$ = $e^{i\lambda_{h}t} \ket{\mathbb{Z}_N^{(h)} * x}_H$
+
+        \vspace{1cm}
+        If we choose $t = \operatorname{poly}(\log N)$, it follows from Lemma that we can run the \textit{phase estimation algorithm} with the unitary $W$ and the eigenstate $\ket{\mathbb{Z}_N^{(h)} * x}_H$ to compute an estimate $\tilde{\lambda}_h$ of $\lambda_h$ such that %$\abs{\tilde{\lambda}_h - \lambda_h} \le 1 / poly(log N)$.
+        % \operatorname{poly}(\log N)
+        \[
+        |\tilde{\lambda}_h - \lambda_h| \leq \frac{1}{\operatorname{poly}(\log N)}
+        \]
+
+    \end{textblock*}
+
+ \end{frame}
+
 \begin{frame}{An efficient new algorithm for QHT}
@@
     \begin{textblock*}{12cm}(0.5cm,1.5cm)
-        First, let us briefly explain how the algorithm for $\qft_N$ works:
+        Now, let us briefly explain how the algorithm for $\qft_N$ works:
         \begin{align*}
@@
 
-\begin{frame}{Application: Quantum Money}
+\begin{frame}{References}
 
     \begin{textblock*}{12cm}(0.5cm,1.5cm)
-
-        A public-key quantum money scheme consists of two QPT algorithms:
-        \vspace{1cm} 
-        \begin{itemize}
-        \item $\gen(1^\lambda)$: This algorithm takes a security parameter $\lambda$ as input and outputs a pair $(s, \rho_s)$, where $s$ is a binary string called the serial number, and $\rho_s$ is a quantum state called the banknote.
-The pair $(s, \rho_s)$, or simply $\rho_s$, is sometimes denoted by $\$$.
-
-        \vspace{1cm}
-        \item $\ver(s, \rho_s)$: This algorithm takes a serial number and an alleged banknote as input and outputs either $1$ (accept) or $0$ (reject).
-        \end{itemize}
-
-    \end{textblock*}
-
-\end{frame}
-
-\begin{frame}{Quantum Money From Group Actions}
-
-    \begin{textblock*}{12cm}(0.5cm,1.5cm)
-
-        \begin{itemize}
-        \item $\gen(1^\lambda)$. Begin with the state $\ket{0}\ket{x_\lambda}$, and apply the quantum Fourier transform over $G_\lambda$ to the first register producing the superposition
-        \[ \frac{1}{\sqrt{{|X_\lambda|}}} \sum_{g \in G_\lambda} \ket{g}\ket{x_\lambda}. \]
-        Next, apply the unitary transformation $\ket{h}\ket{y} \mapsto \ket{h}\ket{h * y}$ to this state, followed by the quantum Fourier transform on the first register. This results in
-        \[ \frac{1}{{|G_\lambda|}} \sum_{h \in G_\lambda} \sum_{g \in G_\lambda} \chi(g, h) \ket{h}\ket{g * x_\lambda} = \frac{1}{\sqrt{{|G_\lambda|}}} \sum_{h \in G_\lambda} \ket{h} \ket{G^{(h)} * x_\lambda} \]
-
-        \end{itemize}
-
-    \end{textblock*}
-
-\end{frame}
-
-\begin{frame}{Quantum Money From Group Actions}
-
-    \begin{textblock*}{12cm}(0.5cm,1.5cm)
-
-        \begin{itemize}
-        \item $\ver(h, \ket{\psi})$.
-First, check whether $\ket{\psi}$ has support in $X_\lambda$.
-If not, return $0$.
-Then, apply $\comph$ to the state $\ket{\psi}\ket{0}$, and measure the second register to obtain some $h' \in G_\lambda$.
-If $h' = h$, return $1$; otherwise return $0$.
-        \end{itemize}
-
-    \end{textblock*}
-
-\end{frame}
-
-\begin{frame}{Quantum Money With The Hartley Transform}
-
-    \begin{textblock*}{12cm}(0.5cm,1.5cm)
-
-        \begin{itemize}
-            \item $\gen$. Begin with the state $\ket{0}\ket{x}$, and apply the quantum Hartley transform over $\mathbb{Z}_N$ to the first register producing the superposition
-            \[ \frac{1}{\sqrt{N}} \sum_{g \in \mathbb{Z}_N} \ket{g}\ket{x}. \]
-            Next, apply the unitary $\ket{h}\ket{y} \mapsto \ket{h}\ket{h * y}$ to this state, followed by a $\qht_N$ on the first register. This results in
-            \[ \frac{1}{N} \sum_{h \in \mathbb{Z}_N} \sum_{g \in \mathbb{Z}_N} \cas\Big(\frac{2\pi gh}{N}\Big) \ket{h}\ket{g * x} = \frac{1}{\sqrt{N}} \sum_{h \in \mathbb{Z}_N} \ket{h} \ket{\mathbb{Z}_N^{(h)} * x}_H \]
-            Measure the first register to obtain a random $h \in \mathbb{Z}_N$, collapsing the state to $\ket{\mathbb{Z}_N^{(h)} * x}_H$. Return the pair $(h, \ket{\mathbb{Z}_N^{(h)} * x}_H)$.
-
-        \end{itemize}
-
-    \end{textblock*}
-
-\end{frame}
-
-\begin{frame}{Quantum Money With The Hartley Transform}
-
-    \begin{textblock*}{12cm}(0.5cm,1.5cm)
-        \begin{itemize}
-            \item  In the original scheme, using the quantum Fourier transform, we could directly obtain $h$ from the money state $\ket{\mathbb{Z}_N^{(h)} * x}$ and compare it to the given $h$.
-However, this approach does not work when we use the Hartley transform.
-            \vspace{1cm}
-            \item  To address this, we design an algorithm for computing $h$ that utilizes quantum walks.
-
-        \end{itemize}
-
-    \end{textblock*}
-
-\end{frame}
-
-\begin{frame}{Quantum Walks}
-
-    \begin{textblock*}{12cm}(0.5cm,1.5cm)
-
-        \begin{itemize}
-            \item Quantum walks are quantum analogs of classical random walks and play
-            a fundamental role in quantum algorithms
-            \item  Two types: continuous-time and discrete-time
-            \item Quantum walks leverage interference to explore graphs more efficiently than classical walks
-            \item For a graph $\Gamma$, a continuous-time classical walk on $\Gamma$ is:
-            \[
-            \frac{d}{dt} q(t) = Lq(t)
-            \]
-            \item In the quantum setting,  the dynamics of the walk is given by the Schr\"{o}dinger equation:
-            \[
-                i\frac{d}{dt}\ket{\psi(t)} = L\ket{\psi(t)}
-            \]
-
-        \end{itemize}
-
-    \end{textblock*}
-\end{frame}
-
-\begin{frame}{Continuous-Time Quantum Walks}
-
-    \begin{textblock*}{12cm}(0.5cm,1.5cm)
-
-        \begin{itemize}
-            \item The solution to this differential
-            equation can be written in closed form as:
-            \[
-                \ket{\psi(t)} = e^{-iLt} \ket{\psi(0)}.
-            \]
-            \item In practice, we often (including this work) use the adjacency matrix $A$ of $\Gamma$ as the Hamiltonian of the walk
-
-        \end{itemize}
-
-    \end{textblock*}
-\end{frame}
-
-\begin{frame}{Discrete-Time Quantum Walks}
-    \begin{textblock*}{12cm}(0.5cm,1.5cm)
-        \begin{itemize}
-
-            \item If the $\Gamma$ has $N$ vertices, the discrete time quantum walk on $\Gamma$ is defined by a unitary operator on the finite Hilbert space $\mathbb{C}^N \times \mathbb{C}^N$ as follows:
-            \item Define the states:
-            \[ \ket{\phi_j} = \frac{1}{\sqrt{\deg(j)}} \sum_{k = 1}^N \sqrt{P_{jk}}\ket{j, k}, \]
-            \item project and swap operators:
-            \[ \Pi = \sum_{j = 1}^N \ket{\phi_j} \bra{\phi_j}, \quad S = \sum_{j, k = 1}^N \ket{j, k} \bra{k, j}. \]
-            \item Then, a step of the quantum walk is defined by the unitary:
-             \[
-             W = S(2\Pi - 1)
-             \]
-
-        \end{itemize}
-    \end{textblock*}
-\end{frame}
-
-\begin{frame}{Quantum Walks on Cayley Graphs}
-
-    \begin{textblock*}{12cm}(0.5cm,1.5cm)
-
-        \textit{Cayley Graphs:} \\
-        \vspace{0.3cm}
-        Let $G$ be an abelian group and let $Q = \{q_1, q_2, \dots, q_k\} \subset G$ be a symmetric set, i.e., $q \in Q$ if and only if $-q \in Q$.
-The Cayley graph associated to $G$ and $Q$ is a graph $\Gamma = (V, E)$, where the vertex set is $V = G$, and the edge set $E$ consists of pairs $(a, b) \in G \times G$ such that there exists $q \in Q$ with $b = q + a$.
-\\
-
-    \end{textblock*}
-
-\end{frame}
-
-\begin{frame}{Quantum Walks on Cayley Graphs}
-
-    \begin{textblock*}{12cm}(0.5cm,1.5cm)
-
-        \textit{Cayley Graphs:} \\
-        \vspace{0.3cm}
-
-        The adjacency matrix of the Cayley graph $\Gamma = (V,E)$ can be expressed as:
-        \[ A = \sum_{a \in G} \lambda_a \ket{\hat{a}} \bra{\hat{a}}, \]
-        where $\ket{\hat{a}} = \operatorname{QFT} \ket{a}$ is the quantum Fourier transform of $\ket{a}$. \\
-         \vspace{0.5cm}
-        The eigenvalues $\lambda_a$ are given by:
-        \[ \lambda_a = \sum_{q \in Q} \chi(a, q). \]
-        Note that the eigenvectors $\ket{\hat{a}}$ of $A$ depend only on $G$ and not on the set $Q$.
-
-    \end{textblock*}
-
-\end{frame}
-
-\begin{frame}{Quantum Walks on Cayley Graphs}
-
-    \begin{textblock*}{12cm}(0.5cm,1.5cm)
-
-        \textit{Cayley Graphs:} \\
-        \vspace{0.3cm}
-        \textit{Proof}:
-        \[
-        A\ket{\hat{a}} = A.\frac{1}{\sqrt{|G|}}\sum_{y \in G}\chi(a,y)\ket{y} = \frac{1}{\sqrt{|G|}}\sum_{y \in G}\chi(a,y).A\ket{y}
-        \]
-        \[
-        = \frac{1}{\sqrt{|G|}}\sum_{y \in G}\chi(a,y).\sum_{q \in Q}\ket{qy}
-        \]
-        Consider $\beta = qy$. Then:
-        \[
-         = \frac{1}{\sqrt{|G|}}\sum_{q \in Q}\chi(a,q)\sum_{\beta}\chi(a,\beta)\ket{\beta} = \sum_{q \in Q}\chi(a,q) . \ket{\hat{a}}
-        \]
-        \[
-         = \lambda_a\ket{\hat{a}}
-        \]
-    \end{textblock*}
-\end{frame}
-
-\begin{frame}{Group Actions}
-
-    \begin{textblock*}{12cm}(0.5cm,1.5cm)
-        Cayley graphs can also be constructed using \textit{group actions}.\\
-        \vspace{0.5cm}
-        \textit{Group Actions:}
-        \vspace{0.5cm}
-
-        For a group $G$ and a set $X$, we say that $G$ \textit{acts on} $X$ if there is a mapping $*: G \times X \to X$ that satisfies the following properties:
-        \begin{enumerate}
-            \item Compatibility: for every $a, b \in G$ and every $x \in X$, $g * (h * x) = (gh) * x$,
-            \item Identity: for the identity $1 \in G$ and every $x \in X$, $1 * x = x$. 
-        \end{enumerate}
-
-        \vspace{0.5 cm}
-        \begin{itemize}
-            \item  We use the notation $(G, X, *)$ to denote a group $G$ acting on a set $X$ through the action $*$.
-            \item  A group action is called \textit{regular} if for every $x, y \in X$ there exists a unique $g \in G$ such that $g * x = y$.
-        \end{itemize}
-
-    \end{textblock*}
-
-\end{frame}
-
-\begin{frame}{Cayley Graphs with Group Actions}
-    \begin{textblock*}{12cm}(0.5cm,1.5cm)
-
-    Given a regular group action $(G, X, *)$ with a fixed element $x \in X$ and a set  $Q = \{q_1, q_2, \dots, q_k\} \subset G$, let $\Gamma = (X, E)$ be a graphs with vertex set $X$ and edge set consisting of pairs $(x, y) \in X \times X$ such that $y = q * x$ for some $q \in Q$.
-The adjacency matrix of $\Gamma$ is
-    \[
-    A = \sum_{h \in G} \lambda_h \ket{G^{(h)} * x} \bra{G^{(h)} * x}, 
-    \]
-    where $\lambda_h = \sum_{q \in Q} \chi(h, q)$. Again, the eigenvectors $\ket{G^{(h)} * x}$ depend only on $G$.
-
-    \end{textblock*}
-\end{frame}
-
-\begin{frame}{Cayley Graphs with Group Actions}
-
-    \begin{textblock*}{12cm}(0.5cm,1.5cm)
-        \textit{Proof}:
-
-        \[
-        A\ket{G^{(h)}*x} = \frac{1}{\sqrt{|G|}}.\sum_{g \in G}\chi(g,h) A.\ket{g*x}
-        \]
-
-        \[
-        = A\ket{G^{(h)}*x} = \frac{1}{\sqrt{|G|}}.\sum_{g \in G}\chi(g,h)\sum_{q \in Q}\ket{q*(g*x)}
-        \]
-        Consider $\beta = qg$. Then:
-        \[
-        = = \frac{1}{\sqrt{|G|}}\sum_{q \in Q}\sum_{\beta \in G}\chi(\beta,h)\chi(q,h)\ket{\beta * x}
-        \]
-
-        \[
-        = \sum_{q \in Q}\chi(q,h).\ket{G^{(h)}*x} = \lambda_h \ket{G^{(h)}*x}
-        \]
-
-    \end{textblock*}
-
-\end{frame}
-
-\begin{frame}{The cmpIndex Algorithm}
-
-    \begin{textblock*}{12cm}(0.5cm,1.5cm)
-        Given a state $\ket{G^{(h)} * x}$, there is an efficient algorithm for computing $h$.
-        Specifically, there is a unitary operator that performs the transformation $\ket{G^{(h)} * x} \ket{0} \mapsto \ket{G^{(h)} * x} \ket{h}$:
-
-        \[
-        \ket{G^{(h)} * x}\ket{0} \mapsto \ket{G^{(h)} * x} \frac{1}{\sqrt{|G|}}\sum_{k \in G}\ket{k}
-        \]
-        And then apply the unitary $\sum_{k \in G}U_k \otimes \ket{k}\bra{k}$:
-
-        \[
-        \mapsto \frac{1}{\sqrt{|G|}}\sum_{k \in G}\ket{G^{(h)}*x}\chi(-k,h)\ket{k}
-        \]
-
-        Finally, applying the inverse quantum Fourier transform to the second register yields:
-
-        \[
-           \mapsto  \ket{G^{(h)}*x}\ket{h}
-        \]
-    \end{textblock*}
-
-\end{frame}
-
-\begin{frame}{Simulating continuous-time walks}
-
-    \begin{textblock*}{12cm}(0.5cm,1.5cm)
-
-        \[
-        \ket{\phi_{j0}} := \frac{1}{\sqrt{d}}\sum_{l \in F_j}(\sqrt{\frac{H^*_{jl}}{K}}\ket{0} + \sqrt{1-\frac{|H^*_{jl}|}{K}}\ket{1})
-        \]
-
-        \[
-        \ket{\phi_{j1}} := \ket{0}\ket{1}
-        \]
-
-        \[
-        T := \sum_{j=0}^{N-1}\sum_{b \in {\{0,1\}}}(\ket{j}\bra{j}\otimes\ket{b}\bra{b})\otimes\ket{\phi_{jb}}
-        \]
-
-        \[
-        W = iS(2TT^* - 1)
-        \]
-
-        \[
-        S\ket{j_1,b_1}\ket{j_2,b_2} = \ket{j_2,b_2}\ket{j_1,b_1}
-        \]
-
-    \end{textblock*}
-
-\end{frame}
-
-\begin{frame}{Simulating continuous-time walks}
-
-    \begin{textblock*}{12cm}(0.5cm,1.5cm)
-
-       \[
-       e^{-iAt} = \operatorname{QFT_G}(\sum_{a \in G}e^{-i\lambda_at}\ket{a}\bra{a})\operatorname{QFT^*_G}
-       \]
-
-    \end{textblock*}
-
-\end{frame}
-
-\begin{frame}{Simulating group action quantum walks}
-
-    \begin{textblock*}{12cm}(0.5cm,1.5cm)
-
-        \[
-        e^{-iAt} = \sum_{h \in G}\ket{G^{(h)}*x}\bra{G^{(h)}*x}
-        \]
-
-        \[
-        T := \sum_{y \in X}\sum_{b \in {\{0,1\}}}(\ket{j}\bra{j}\otimes\ket{b}\bra{b})\otimes\ket{\phi_{yb}}
-        \]
-
-        \[
-        = \sum_{y \in X}\sum_{b \in {\{0,1\}}}\ket{y}\ket{b}\ket{\phi_{yb}}\bra{y}\bra{b}
-        \]
-
-        \[
-            \ket{\phi_{y0}} = \frac{1}{\sqrt{|Q|}}\sum_{q \in Q}\ket{q*y}\ket{0}
-        \]
-
-    \end{textblock*}
-
-\end{frame}
-
-\begin{frame}{Simulating group action quantum walks}
-
-    \begin{textblock*}{12cm}(0.5cm,1.5cm)
-
-        % \begin{align*}
-        %     2\ket{0} \bra{0} \otimes TT^* - 1
-        %     & = 2\ket{0} \bra{0} \otimes \sum_{y \in X} \sum_{b \in \{0, 1\}} \ket{y, b} \ket{\phi_{yb}} \bra{y, b} \bra{\phi_{yb}} - 1 \\
-
-        %     & = U_T (2 \ket{0} \bra{0} \otimes 1_{X, b} \otimes \ket{0, 0} \bra{0, 0} - 1) U_T^*.
-
-        % \end{align*}
-
-        \[
-        2\ket{0} \bra{0} \otimes TT^* - 1 = 2\ket{0} \bra{0} \otimes \sum_{y \in X} \sum_{b \in \{0, 1\}} \ket{y, b} \ket{\phi_{yb}} \bra{y, b} \bra{\phi_{yb}} - 1 
-        \]
-
-        \[
-        = 2\sum_{y \in X} \sum_{b \in \{0, 1\}} \ket{0} \ket{y, b} \ket{\phi_{yb}} \bra{0} \bra{y, b} \bra{\phi_{yb}} - 1 
-        \]
-
-        \[
-        = U_T \Big( 2\sum_{y \in X} \sum_{b \in \{0, 1\}} \ket{0} \ket{y, b} \ket{0, 0} \bra{0} \bra{y, b} \bra{0, 0} - 1 \Big) U_T^* 
-        \]
-
-        \[
-        = U_T (2 \ket{0} \bra{0} \otimes 1_{X, b} \otimes \ket{0, 0} \bra{0, 0} - 1) U_T^*
-        \]
-
-        Now, for any state $\ket{\psi}$:
-
-        \[
-        (2\ket{0}\bra{0}\otimes TT^* - 1)\ket{0}\ket{\psi} = \ket{0}(2TT^*-1)\ket{\psi}
-        \]
-
-    \end{textblock*}
-
-\end{frame}
-
-\begin{frame}{Group Action Quantum Walks}
-
-    \begin{textblock*}{12cm}(0.5cm,1.5cm)
-
-        Given a regular group action $(G, X, *)$ with a fixed element $x \in X$ and a set  $Q = \{q_1, q_2, \dots, q_k\} \subset G$, let $\Gamma = (X, E)$ be a graphs with vertex set $X$ and edge set consisting of pairs $(x, y) \in X \times X$ such that $y = q * x$ for some $q \in Q$.
-The adjacency matrix of $\Gamma$ is
-        \[ A = \sum_{h \in G} \lambda_h \ket{G^{(h)} * x} \bra{G^{(h)} * x}, \]
-        where:
-        \begin{itemize}
-            \item $\lambda_h = \sum_{q \in Q} \chi(h, q)$
-            \item the eigenvectors $\ket{G^{(h)} * x}$ depend only on $G$
-        \end{itemize}
-
-    \end{textblock*}
-
-\end{frame}
-
-\begin{frame}{Computing the serial Number}
-
-    \begin{textblock*}{12cm}(0.5cm,1.5cm)
-
-        \begin{itemize}
-            \item Given a state $\ket{\mathbb{Z}_N^{(h)} * x}_H$, we show how to compute $h$ using continuous-time quantum walks.
-            \vspace{0.5cm}
-            \item For any $q \in \mathbb{Z}_N$, define a Cayley graph $\Gamma = (\mathbb{Z}_N, E)$ with the generating set $Q = \{-u, u\}$.
-            \vspace{0.5cm}
-            \item Let $A$ denote the adjacency matrix of $\Gamma$.
-The eigenvectors and corresponding eigenvalues of $A$ are $\ket{\mathbb{Z}_N^{(h)} * x}$ and $\lambda_h = 2\cos(2\pi uh / N)$, respectively, for $h \in \mathbb{Z}_N$.
-            \vspace{0.5cm}
-            \item the unitary $W = e^{iAt}$ can be efficiently simulated to exponential accuracy.
-        \end{itemize}
-
-    \end{textblock*}
-
- \end{frame}
-
-\begin{frame}{Computing the serial Number}
-
-    \begin{textblock*}{12cm}(0.5cm,1.5cm)
-        Lemma: The money state $\ket{\mathbb{Z}_N^{(h)} * x}_H$ is an eigenstate of $W$ with eigenvalue $e^{i\lambda_h t}$.
-        \vspace{1cm}
-
-        Proof. 
-        \begin{align*}
-            e^{iAt} \ket{\mathbb{Z}_N^{(h)} * x}_H
-            & = \sum_{g \in \mathbb{Z}_N} e^{i\lambda_gt} \ket{\mathbb{Z}_N^{(g)} * x}\braket{\mathbb{Z}_N^{(g)} * x|\mathbb{Z}_N^{(h)} * x}_H \\
-            & = \sum_{g \in \mathbb{Z}_N} e^{i\lambda_gt} \ket{\mathbb{Z}_N^{(g)} * x} \bra{\mathbb{Z}_N^{(g)} * x} \Big( \frac{1 - i}{2} \ket{\mathbb{Z}_N^{(h)} * x} + \frac{1 + i}{2} \ket{\mathbb{Z}_N^{(-h)} * x} \Big) \\
-            & = e^{i\lambda_{h}t} \frac{1 - i}{2} \ket{\mathbb{Z}_N^{(h)} * x} + \frac{1 + i}{2} e^{i\lambda_{-h}t} \ket{\mathbb{Z}_N^{(-h)} * x} \\
-            & = e^{i\lambda_{h}t} \ket{\mathbb{Z}_N^{(h)} * x}_H,
-        \end{align*}
-        where the last equality follows from the fact that $\lambda_h = \lambda_{-h}$.
-    \end{textblock*}
-
- \end{frame}
-
-\begin{frame}{Computing the serial Number}
-
-    \begin{textblock*}{12cm}(0.5cm,1.5cm)
-        Lemma: The money state $\ket{\mathbb{Z}_N^{(h)} * x}_H$ is an eigenstate of $W$ with eigenvalue $e^{i\lambda_h t}$.
-        \vspace{1cm}
-
-        $e^{iAt} \ket{\mathbb{Z}_N^{(h)} * x}_H$ = $e^{i\lambda_{h}t} \ket{\mathbb{Z}_N^{(h)} * x}_H$
-
-        \vspace{1cm}
-        If we choose $t = \operatorname{poly}(\log N)$, it follows from Lemma that we can run the phase estimation algorithm with the unitary $W$ and the eigenstate $\ket{\mathbb{Z}_N^{(h)} * x}_H$ to compute an estimate $\tilde{\lambda}_h$ of $\lambda_h$ such that %$\abs{\tilde{\lambda}_h - \lambda_h} \le 1 / poly(log N)$.
-        % \operatorname{poly}(\log N)
-        \[
-        |\tilde{\lambda}_h - \lambda_h| \leq \frac{1}{\operatorname{poly}(\log N)}
-        \]
 

### 2025-04-01 main.tex
new commit

--- 2025-02-17 main.tex
@@
 For example, For the cyclic group \( G = \mathbb{Z}_n = \{0,1,2,\dots, n-1\} \) with the generating set \( S = \{\pm 1\} \), the Cayley graph forms a cycle graph.
-In this graph, each vertex \( j \) is connected to \( j+1 \mod n \) and \( j-1 \mod n \), creating a cyclic structure.
+In this graph, each vertex \( j \) is connected to \( j+1 \mod n \) and \( j-1 \mod n \), creating a cyclic structure.\\
+
+The adjacency matrix of $\Gamma$ can be expressed as
+\[
+A = \sum_{a \in G} \lambda_a |\hat{a}\rangle \langle \hat{a}|,
+\]
+where $|\hat{a}\rangle$ is the quantum Fourier transform of $|a\rangle$. The eigenvalues $\lambda$ are given by
+\[
+\lambda_a = \sum_{q \in Q} \chi(a, q).
+\]
+Note that the eigenvectors $|\hat{a}\rangle$ of $A$ depend only on $G$ and not on the set $Q$.
+
+To see this, we have
+\[
+        A\ket{\hat{a}} = A.\frac{1}{\sqrt{|G|}}\sum_{y \in G}\chi(a,y)\ket{y} = \frac{1}{\sqrt{|G|}}\sum_{y \in G}\chi(a,y).A\ket{y}
+        \]
+        \[
+        = \frac{1}{\sqrt{|G|}}\sum_{y \in G}\chi(a,y).\sum_{q \in Q}\ket{qy}
+        \]
+        Consider $\beta = qy$. Then:
+        \[
+         = \frac{1}{\sqrt{|G|}}\sum_{q \in Q}\chi(a,q)\sum_{\beta}\chi(a,\beta)\ket{\beta} = \sum_{q \in Q}\chi(a,q) . \ket{\hat{a}}
+        \]
+        \[
+         = \lambda_a\ket{\hat{a}}
+        \]
 
@@
 
-\section*{Spectral Decomposition of the Adjacency Matrix of a Cayley Graph}
-
-The spectral decomposition of the adjacency matrix of a Cayley graph involves expressing the adjacency matrix in terms of its eigenvalues and eigenvectors.
-This decomposition is particularly useful for understanding the behavior of quantum walks, graph connectivity, expansion properties, and random walks on the graph.
-
-Spectral decomposition expresses \( A \) in terms of its eigenvalues and eigenvectors:
-\[
-A = \sum_{j} \lambda_j P_j,
-\]
-where:
-\begin{itemize}
-    \item \( \lambda_j \) are the eigenvalues of \( A \).
-    \item \( P_j \) are the projection matrices onto the corresponding eigenspaces.
-\end{itemize}
-
-Since Cayley graphs are highly structured, their eigenvalues and eigenvectors often have explicit formulas based on group representation theory and Fourier analysis on groups.
-
-For a finite group \( G \), the Fourier transform on groups helps diagonalize \( A \). The eigenvalues of \( A \) are computed as:
-\[
-\lambda_\rho = \sum_{s \in S} \rho(s),
-\]
-where \( \rho \) is an irreducible representation of \( G \). The set of eigenvalues depends on the sum over generators in the group's representation.
-
-For Abelian groups (e.g., \( \mathbb{Z}_n \)), the irreducible representations are characters, simplifying the spectral decomposition.
-
-For non-Abelian groups, the decomposition involves matrix-valued representations.
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection*{Example: Cyclic Group \( \mathbb{Z}_n \)}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Simulating continuous-time walks}
+Childs~\cite{childs2010relationship} and Berry, Childs, and Kothari~\cite{berry2015hamiltonian} showed that continuous-time quantum walks can be simulated using discrete-time quantum walks.
+Since our approach relies on their methods, we begin by outlining the relevant notation and framework.
+
+Let \( H \) be a Hamiltonian of dimension \( N = 2^n \), and define \( \opnorm{H}_{\mathrm{max}} = \max_{i, j} \abs{H_{ij}} \).
+To facilitate the simulation, we expand the Hilbert space from \( \C^N \) to \( \C^{2N} \otimes \C^{2N} \) by appending an ancilla qubit initialized to \( \ket{0} \) and duplicating the resulting space.
+
+To define the discrete-time walk operator, we first construct an orthonormal set of states:
+\begin{align}
+    \ket{\phi_{j0}} & := \frac{1}{\sqrt{d}} \sum_{\ell \in F_j} \ket{\ell} \left( \sqrt{\frac{H_{j\ell}^*}{K}} \ket{0} + \sqrt{1 - \frac{\abs{H_{j\ell}^*}}{K}} \ket{1} \right), \label{eq:walk-sim} \\
+    \ket{\phi_{j1}} & := \ket{0} \ket{1}, \nonumber
+\end{align}
+where \( F_j \) denotes the set of nonzero entries in column \( j \) of \( H \), and \( K \ge \opnorm{H}_{\mathrm{max}} \) is a fixed constant.
+
+Based on these states, we define the isometry \( T : \C^{2N} \to \C^{2N} \otimes \C^{2N} \) as follows:
+\begin{equation}
+    \label{eq:walk-isom}
+    T := \sum_{j = 0}^{N - 1} \sum_{b \in \{0, 1\}} (\ket{j}\bra{j} \otimes \ket{b}\bra{b}) \otimes \ket{\phi_{jb}}.
+\end{equation}
+
+The discrete-time quantum walk operator is then defined as
+\[
+W = iS(2TT^* - \mathds{1}),
+\]
+where \( S \) is the swap operator acting as
+\[
+S \ket{j_1} \ket{b_1} \ket{j_2} \ket{b_2} = \ket{j_2} \ket{b_2} \ket{j_1} \ket{b_1},
+\]
+for all \( 0 \le j_1, j_2 < N \) and \( b_1, b_2 \in \{0, 1\} \).
+
+To efficiently simulate the continuous-time evolution \( e^{-iHt} \), it suffices to implement the isometry \( T \), its adjoint \( T^* \), and the walk operator \( W \) efficiently.
+Assuming black-box (oracle) access to the entries of \( H \), the following result holds:
+
+\begin{theorem}[{\cite[Theorem 1]{berry2015hamiltonian}}]
+\label{thm:sparse-sim}
+Let \( H \) be a \( d \)-sparse Hamiltonian acting on \( n \) qubits. Then the unitary \( e^{-iHt} \) can be approximated to within error \( \epsilon \) using
+\[
+O\left( \tau \frac{\log(\tau / \epsilon)}{\log\log(\tau / \epsilon)} \right)
+\]
+queries to \( H \), and
+\[
+O\left( \tau \left[ n + \log^{5 / 2}(\tau / \epsilon) \right] \frac{\log(\tau / \epsilon)}{\log\log(\tau / \epsilon)} \right)
+\]
+additional elementary gates, where \( \tau = d \cdot \opnorm{H}_{\mathrm{max}} \cdot t \).
+\end{theorem}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection*{Quantum walks from Group Actions}
-The spectral decomposition of the adjacency matrix of a Cayley graph generated by a general group action $G$ provides insights into the structure and properties of the graph.
-This decomposition leverages the symmetries of the group $G$ and representation theory to analyze the eigenvalues and eigenvectors of the adjacency matrix.
-
-Let $G$ be a finite group, and let $X$ be a set on which $G$ acts via a group action $G \times X \to X$. A Cayley graph can be constructed based on this action, where
-the vertices are the elements of the set $X$, and For each $g \in G$ and $x \in X$, there is an edge between $x$ and $g *	x$, where $g * x$ is the action of $g$ on $x$.
-
-If the generating set $S \subset G$ is symmetric (i.e., $s \in S \implies s^{-1} \in S$), then the Cayley graph is undirected. Otherwise, it may be directed.
-
-The adjacency matrix $A$ of the Cayley graph is a matrix that encodes the edges of the graph:
-
-\[
-A_{x,y} =
-\begin{cases}
-1, & \text{if there exists } g \in G \text{ such that } y = g * x, \\
-0, & \text{otherwise}.
-\end{cases}
-\]
-
-The adjacency matrix is symmetric if the group action preserves symmetry, which happens if $G$ is acting via an involution, i.e., if for every generator $g \in G$, its inverse is also a generator.
-It also inherits the symmetries of the group action.
-That is, the group $G$ acts on the vertices of the graph, and the adjacency matrix commutes with the action of the group.
-This means that the adjacency matrix $A$ is highly structured, and its eigenvalues can be computed using the representation theory of the group $G$.
-
-The eigenvalues of the adjacency matrix correspond to the eigenvalues of these blocks $\rho(A)$, and the multiplicities of the eigenvalues are related to the dimensions of the corresponding irreducible representations.
-
-The spectral decomposition of the adjacency matrix $A$ can be written as:
-
-\[
-A = \sum_{i} \lambda_{i} v_{i} v_{i}^{\top},
-\]
-
-where:
-
-- $\lambda_{i}$ are the eigenvalues,
-- $v_{i}$ are the corresponding eigenvectors (which lie in the spaces corresponding to the irreducible representations),
-- $v_{i} v_{i}^{\top}$ is the outer product of the eigenvector $v_{i}$ with itself.
-
-The eigenvectors $v_{i}$ are related to the characters of the group $G$.
-Specifically, the characters of irreducible representations of $G$ help determine the eigenvalues of $A$.
-If $\chi_{\rho}$ denotes the character of the irreducible representation $\rho$, then the eigenvalues are given by:
-
-\[
-\lambda_{\rho} = \frac{1}{|G|} \sum_{g \in G} \chi_{\rho}(g) A(g),
-\]
-
-where $A(g)$ is the action of $g$ as represented in the adjacency matrix.
-
-\[
-*************Further discussions Here***************
-\]
-
+
+Let \( G \) be an abelian group, and let \( Q = \{q_1, q_2, \dots, q_k\} \subset G \) be a symmetric generating set, meaning that \( q \in Q \) if and only if \( -q \in Q \).
+The Cayley graph associated with \( G \) and \( Q \) is defined as \( \Gamma = (V, E) \), where the vertex set is \( V = G \), and the edge set consists of all pairs \( (a, b) \in G \times G \) such that \( b = q + a \) for some \( q \in Q \).
+
+The adjacency matrix \( A \) of \( \Gamma \) admits a spectral decomposition:
+\[
+A = \sum_{a \in G} \lambda_a \ket{\hat{a}} \bra{\hat{a}},
+\]
+where \( \ket{\hat{a}} \) denotes the quantum Fourier transform of \( \ket{a} \), and the eigenvalues \( \lambda_a \) are given by
+\[
+\lambda_a = \sum_{q \in Q} \chi(a, q).
+\]
+Importantly, the eigenvectors \( \ket{\hat{a}} \) depend solely on the group \( G \), not on the choice of the generating set \( Q \).
+
+Cayley graphs can also be generalized through group actions.
+Let \( (G, X, *) \) be a regular group action with a fixed element \( x \in X \), and let \( Q = \{q_1, q_2, \dots, q_k\} \subset G \) be a subset as before.
+Define the Cayley graph \( \Gamma = (X, E) \), where the vertex set is \( X \), and the edge set consists of all pairs \( (x, y) \in X \times X \) such that \( y = q * x \) for some \( q \in Q \).
+
+The adjacency matrix of this graph can be written as:
+\[
+A = \sum_{h \in G} \lambda_h \ket{G^{(h)} * x} \bra{G^{(h)} * x},
+\]
+where
+\[
+\lambda_h = \sum_{q \in Q} \chi(h, q), \quad \text{and} \quad \ket{G^{(h)} * x} = \frac{1}{\sqrt{|G|}} \sum_{g \in G} \chi(g, h) \ket{g * x}.
+\]
+
+As in the previous case, the eigenvectors \( \ket{G^{(h)} * x} \) are determined solely by the structure of the group \( G \).
+This construction generalizes the standard Cayley graph: setting \( X = G \) and the group action \( * \) as group multiplication recovers the original definition.
+
+To see this, we have:
+
+\[
+    A\ket{G^{(h)}*x} = \frac{1}{\sqrt{|G|}}.\sum_{g \in G}\chi(g,h) A.\ket{g*x}
+    \]
+
+    \[
+    = A\ket{G^{(h)}*x} = \frac{1}{\sqrt{|G|}}.\sum_{g \in G}\chi(g,h)\sum_{q \in Q}\ket{q*(g*x)}
+    \]
+    Consider $\beta = qg$. Then:
+    \[
+    = = \frac{1}{\sqrt{|G|}}\sum_{q \in Q}\sum_{\beta \in G}\chi(\beta,h)\chi(q,h)\ket{\beta * x}
+    \]
+
+    \[
+    = \sum_{q \in Q}\chi(q,h).\ket{G^{(h)}*x} = \lambda_h \ket{G^{(h)}*x}
+    \]
+
+    Since the group action \( (G, X, *) \) is regular, the two Cayley graph constructions are isomorphic.
+In the first construction, the vertex set is \( G \), and the adjacency matrix is indexed by elements of \( G \).
+In the second construction, the vertex set is \( X \), with the adjacency matrix indexed by elements of \( X \).
+The isomorphism between these graphs is given by the bijection
+\[
+\setlength{\arraycolsep}{1mm}
+\begin{array}{rcll}
+\phi: & G & \longrightarrow & X \\
+      & g & \longmapsto     & g * x,
+\end{array}
+\]
+
+which maps each group element \( g \in G \) to the corresponding point in its orbit under the action.
+
+    % Assuming the group action is a cryptographic group action, the isomorphism $\phi$ is a one-way function: given $g \in G$, it is easy to compute $g * x$, whereas given $(x, g * x)$, it is hard to compute $g$.
+Therefore, although these graphs are mathematically the same, computational problems based on them require fundamentally different techniques.
+A notable example is the implementation of quantum walks on these graphs.\footnote{Implementations of continuous-time quantum walks in the context of cryptographic group actions have previously appeared in \cite{booher2024failing, doliskani2023sample}, in the setting of supersingular isogeny graphs.
+These walks can be interpreted as group-action walks.} From this point onward, assume $Q$ is a small set, i.e., $\abs{Q} = \poly(\log \abs{G})$.
+In the first graph, we can efficiently implement the walks $e^{-iAt}$ even for values of $t$ that are exponentially large in $\log \abs{G}$.
+This follows from the fact that
+    % \begin{equation}
+    %     \label{eq:adjmat-fb}
+    %     e^{-iAt} = \qft_G \sum_{a \in G} e^{-i\lambda_a t} \ket{a} \bra{a} \qft_G^*.
+    % \end{equation}
+    % The quantum Fourier transform $\qft_G$ and its inverse can be applied in $\poly(\log \abs{G})$ operations.
+The diagonal unitary in the middle, which is a phase computation $\ket{a} \mapsto e^{-i\lambda_a t} \ket{a}$, is also efficient because $\lambda_a$ can be computed classically to arbitrary precision in $\poly(\log \abs{G})$ time.
+
+    % The situation for group actions is less straightforward.
+While the states $\ket{G^{(h)} * x}$ are analogous to the states $\ket{\hat{h}}$, the involvement of the action $*$ in the former introduces computational challenges.
+Specifically, it becomes hard to apply transformations beyond the action $\ket{y} \mapsto \ket{a * y}$ for $a \in G$.
+Consequently, no decomposition analogous to \eqref{eq:adjmat-fb} exists in the context of group actions.
+Instead, we are left with the spectral expression
+    % \[ e^{-iAt} = \sum_{h \in G} e^{-i\lambda_h t} \ket{G^{(h)} * x} \bra{G^{(h)} * x}. \]
+    % Despite this limitation, the sparsity and structure of the matrix $A$ allow us to demonstrate in the next section that for $t = \poly(\log \abs{G})$, the walk $e^{-iAt}$ can still be efficiently approximated to polynomial accuracy.
+
+    When the group action \( (G, X, *) \) is assumed to be cryptographic, the isomorphism \( \phi \) becomes a one-way function: given \( g \in G \), it is efficient to compute \( g * x \), but given the pair \( (x, g * x) \), it is computationally hard to recover \( g \).
+As a result, while the two Cayley graphs are mathematically isomorphic, computational tasks associated with them may require fundamentally different approaches.
+A particularly illustrative example is the implementation of quantum walks on these graphs.\footnote{Continuous-time quantum walks have been explored in the context of cryptographic group actions in~\cite{booher2024failing, doliskani2023sample}, specifically in supersingular isogeny graphs.
+These walks can be viewed as group-action quantum walks.}
+
+    From this point forward, we assume the generating set \( Q \) is small, i.e., \( \abs{Q} = \poly(\log \abs{G}) \).
+In the first construction (where \( X = G \)), the walk \( e^{-iAt} \) can be efficiently implemented even for values of \( t \) that are exponentially large in \( \log \abs{G} \).
+This is a consequence of the identity:
+    \begin{equation}
+        \label{eq:adjmat-fb}
+        e^{-iAt} = \qft_G \left( \sum_{a \in G} e^{-i\lambda_a t} \ket{a} \bra{a} \right) \qft_G^*,
+    \end{equation}
+    where \( \qft_G \) and its inverse can be implemented in \( \poly(\log \abs{G}) \) time.
+Moreover, the diagonal phase unitary \( \ket{a} \mapsto e^{-i\lambda_a t} \ket{a} \) is also efficient to implement, since the eigenvalues \( \lambda_a \) can be computed classically to arbitrary precision in \( \poly(\log \abs{G}) \) time.
+
+    In contrast, the group-action setting presents greater computational difficulty.
+Although the states \( \ket{G^{(h)} * x} \) play a role analogous to the Fourier basis states \( \ket{\hat{h}} \), the presence of the action \( * \) makes the situation more subtle.
+In particular, implementing general transformations over these states is difficult; we are typically limited to operations of the form \( \ket{y} \mapsto \ket{a * y} \) for \( a \in G \).
+As a result, no efficient decomposition similar to~\eqref{eq:adjmat-fb} is known in the group-action setting.
+Instead, the best we can express is the spectral decomposition:
+    \[
+    e^{-iAt} = \sum_{h \in G} e^{-i\lambda_h t} \ket{G^{(h)} * x} \bra{G^{(h)} * x}.
+    \]
+
+    Despite this limitation, the adjacency matrix \( A \) retains a high degree of sparsity and algebraic structure.
+In the next section, we will show that for \( t = \poly(\log \abs{G}) \), the walk \( e^{-iAt} \) can still be efficiently approximated to polynomial accuracy.
+
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\paragraph{Simulating group action quantum walks.}
+Assume \( t = \poly(\log \abs{G}) \).
+We show that the continuous-time walk \( W = e^{-iAt} \) can be efficiently simulated using the discrete-time quantum walk framework developed in~\cite{childs2010relationship, berry2015hamiltonian}.
+Recall the isometry \( T \) defined in Equation~\eqref{eq:walk-isom}, where the states \( \ket{\phi_b} \) are as given in Equation~\eqref{eq:walk-sim}.
+To carry out the simulation, it suffices to show that the isometry \( T \), its adjoint \( T^* \), and the discrete-time walk operator
+\[
+W = iS(2TT^* - \mathds{1})
+\]
+can all be efficiently implemented in the group-action setting.
+
+Let \( \Gamma = (X, E) \) be the Cayley graph associated with the group action \( (G, X, *) \), and let \( A \) denote its adjacency matrix.
+The Hamiltonian \( H \) of interest is simply \( A \), indexed by elements of \( X \).
+In this context, the isometry \( T \) takes the form:
+\begin{align*}
+T
+& := \sum_{y \in X} \sum_{b \in \{0, 1\}} (\ket{y}\bra{y} \otimes \ket{b}\bra{b}) \otimes \ket{\phi_{yb}} \\
+& = \sum_{y \in X} \sum_{b \in \{0, 1\}} \ket{y} \ket{b} \ket{\phi_{yb}} \bra{y} \bra{b}.
+\end{align*}
+
+Because of the structure of $\Gamma$, the states \eqref{eq:walk-sim} simplify as follows.
+First, since the set $Q$ is symmetric, the graph $\Gamma$ is undirected and the adjacency matrix $A$ is symmetric with non-negative entries; the nonzero entries of $A$ are all equal to $1$.
+Therefore, we can set $K = \opnorm{A}_{\mathrm{max}} = 1$.
+As a result, for $y \in X$, the state $\ket{\phi_{y0}}$ becomes
+\[ \ket{\phi_{y0}} = \frac{1}{\sqrt{\abs{Q}}} \sum_{q \in Q} \ket{q * y} \ket{0}. \]
+We now describe how to implement the isometry \( T \) by constructing efficient unitaries \( U_0 \) and \( U_1 \), where each \( U_b \) acts as
+\[
+U_b : \ket{0} \ket{y, b} \ket{0, 0} \mapsto \ket{0} \ket{y, b} \ket{\phi_{yb}}, \quad b \in \{0, 1\},
+\]
+with the first register serving as an ancilla.
+
+The unitary \( U_1 \) is straightforward to implement, since \( \ket{\phi_{y1}} = \ket{0} \ket{1} \) is independent of \( y \). We now focus on the construction of \( U_0 \).
+
+Because \( Q \subset G \) is a small set (i.e., \( \abs{Q} = \poly(\log \abs{G}) \)), we can construct an efficient unitary \( V_Q : \C^Q \to \C^Q \) such that
+\[
+V_Q \ket{0} = \frac{1}{\sqrt{\abs{Q}}} \sum_{q \in Q} \ket{q}.
+\]
+Applying \( V_Q \otimes \mathds{1} \) to the state \( \ket{0} \ket{y, 0} \ket{0, 0} \) produces:
+\[
+\frac{1}{\sqrt{\abs{Q}}} \sum_{q \in Q} \ket{q} \ket{y, 0} \ket{0, 0}.
+\]
+
+Next, we apply the unitary \( V_1 \), defined by:
+\[
+V_1 : \ket{q} \ket{y, 0} \ket{0, 0} \mapsto \ket{q} \ket{y, 0} \ket{q * y, 0}.
+\]
+
+Following this, we uncompute the first register to recover \( \ket{0} \ket{y, 0} \ket{\phi_{y0}} \). This is achieved by applying the unitary \( V_2 \), defined as:
+\[
+V_2 : \ket{q} \ket{y, 0} \ket{q * y, 0} \mapsto \ket{0} \ket{y, 0} \ket{q * y, 0}.
+\]
+Since \( Q \) is small, we can efficiently determine \( q \) from the pair \( (y, q * y) \) by exhaustively checking each \( q \in Q \).
+Thus, \( V_2 \) (and therefore \( U_0 \)) can be implemented efficiently.
+
+To implement \( U_0^* : \ket{0} \ket{y, 0} \ket{\phi_{y0}} \mapsto \ket{0} \ket{y, 0} \ket{0, 0} \), we sequentially apply \( V_2^* \), followed by \( V_1^* \), and finally \( V_Q^* \otimes \mathds{1} \).
+Since each of these unitaries can be implemented efficiently, it follows that \( U_0^* \) is also efficient.
+
+We now construct the isometry \( T \) using a conditional unitary \( U_T \), which applies either \( U_0 \) or \( U_1 \) depending on the value of the qubit \( b \). That is,
+\[
+U_T = \text{Controlled-}U_b \quad \text{with control on } b \in \{0,1\}.
+\]
+
+Next, we demonstrate that the walk unitary
+\[
+W = iS(2TT^* - \mathds{1})
+\]
+can be applied efficiently. This reduces to implementing the reflection \( 2TT^* - \mathds{1} \), which we analyze as follows:
+\begin{align*}
+2\ket{0}\bra{0} \otimes TT^* - \mathds{1}
+&= 2\ket{0}\bra{0} \otimes \sum_{y \in X} \sum_{b \in \{0,1\}} \ket{y,b} \ket{\phi_{yb}} \bra{y,b} \bra{\phi_{yb}} - \mathds{1} \\
+&= 2\sum_{y \in X} \sum_{b \in \{0,1\}} \ket{0} \ket{y,b} \ket{\phi_{yb}} \bra{0} \bra{y,b} \bra{\phi_{yb}} - \mathds{1} \\
+&= U_T \left( 2 \sum_{y \in X} \sum_{b \in \{0,1\}} \ket{0} \ket{y,b} \ket{0,0} \bra{0} \bra{y,b} \bra{0,0} - \mathds{1} \right) U_T^* \\
+&= U_T \left( 2\ket{0}\bra{0} \otimes \mathds{1}_{X,b} \otimes \ket{0,0}\bra{0,0} - \mathds{1} \right) U_T^*.
+\end{align*}
+
+Since \( U_T \), \( U_T^* \), and the operator \( 2\ket{0}\bra{0} \otimes \mathds{1}_{X,b} \otimes \ket{0,0}\bra{0,0} - \mathds{1} \) can all be implemented efficiently, it follows that the reflection \( 2\ket{0}\bra{0} \otimes TT^* - \mathds{1} \) is also efficient.
+
+Finally, for any input state \( \ket{\psi} \), the reflection acts as:
+\[
+\left(2\ket{0}\bra{0} \otimes TT^* - \mathds{1} \right) \ket{0} \ket{\psi} = \ket{0} \left(2TT^* - \mathds{1} \right) \ket{\psi},
+\]
+confirming that the full walk operator \( W \) can be implemented efficiently in the group-action setting.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Applicaions}
 \section{Quantum Money}
-
 \section*{Introduction to Quantum Money}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section*{Benefits of Quantum Money}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Quantum Money From Group Actions}
@@
     \[ \frac{1}{\abs{G_\lambda}} \sum_{h \in G_\lambda} \sum_{g \in G_\lambda} \chi(g, h) \ket{h}\ket{g * x_\lambda} = \frac{1}{\sqrt{\abs{G_\lambda}}} \sum_{h \in G_\lambda} \ket{h} \ket{G^{(h)} * x_\lambda} \]
-    where $\ket{G^{(h)} * x_\lambda}$ is defined as in \eqref{eq:x-fourier-basis}.
-Measure the first register to obtain a random $h \in G_\lambda$, collapsing the state to $\ket{G^{(h)} * x_\lambda}$.
-Return the pair $(h, \ket{G^{(h)} * x_\lambda})$.
+    where,
+    \[
+    \ket{G^{(h)}*x_\lambda} = \frac{1}{\sqrt{|G_\lambda|}}\sum_{g \in G_\lambda}\chi(g,h)\ket{g*x_\lambda}
+    \]
+    . Measure the first register to obtain a random $h \in G_\lambda$, collapsing the state to $\ket{G^{(h)} * x_\lambda}$. Return the pair $(h, \ket{G^{(h)} * x_\lambda})$.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section*{Quantum Hartley Transform (QHT)}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection*{Properties of the QHT}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection*{Efficient implementation of Heartly transform}
 
-********
-
+% Our algorithm for the quantum Hartley transform, $\qht_N$, is inspired by the recursive algorithm for computing the quantum Fourier transform ($\qft_N$).
+Let us briefly explain how the algorithm for $\qft_N$ works.
+For simplicity, we assume $N = 2^n$, so that elements of $\Z_N$ are represented using exactly $n$ qubits.
+The generalization to arbitrary $N$ can be achieved by following the same recursive approach.
+Given $a \in \Z_N$, the expression for $\qft_N$ is written as follows:
+
+Our algorithm for the quantum Hartley transform, \( \qht_N \), is modeled after the recursive structure of the quantum Fourier transform algorithm \( \qft_N \).
+To motivate this, we begin by reviewing the standard approach for computing \( \qft_N \).
+For clarity, we assume \( N = 2^n \), allowing each element of \( \Z_N \) to be represented using exactly \( n \) qubits.
+The same recursive framework can be extended to handle general values of \( N \).
+For any \( a \in \Z_N \), the quantum Fourier transform is defined as:
+
+\begin{align*}
+    \qft_N\ket{a}
+    & = \frac{1}{\sqrt{N}} \sum_{y = 0}^{N - 1} \omega_N^{ay}\ket{y} \\
+    & = \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \omega_N^{ay} \ket{y} + (-1)^a \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \omega_N^{ay} \ket{y + N/2} \\
+    & = \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \omega_N^{ay} \frac{1}{\sqrt{2}} (\ket{0} + (-1)^a \ket{1}) \ket{y}, \numberthis\label{eq:qft_alt}
+\end{align*}
+
+In the final expression, we have isolated the first qubit for clarity.
+Let \( \ket{a} = \ket{t}\ket{b} \), where \( b \) denotes the least significant bit of \( a \), implying that \( a = 2t + b \) for some \( t \in \Z_{N / 2} \).
+Applying \( \qft_{N / 2} \) to the first register yields the state:
+
+\[ \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \omega_N^{2ty} \ket{y} \ket{b}. \]
+Next, we apply the phase unitary \( P(y, b) \), defined by \( \ket{y} \ket{b} \mapsto \omega_N^{by} \ket{y} \ket{b} \), followed by a Hadamard transform on the final qubit.
+This results in the state given in Equation~\eqref{eq:qft_alt}.
+
+We now describe our algorithm for efficiently computing the quantum Hartley transform \( \qht_N \).
+The key idea is to leverage the recursive structure of \( \qht_N \), analogous to the strategy used for \( \qft_N \).
+To facilitate this, we begin by rewriting the summation in Equation~\eqref{eq:qht-N} to expose its recursive form.
+Our approach is as follows:
+\begin{equation}
+    \label{eq:cas-expand}
+	\frac{1}{\sqrt{N}} \sum_{y = 0}^{N - 1} \cas\Big( \frac{2\pi a y}{N} \Big) \ket{y}
+    = \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi a y}{N} \Big) \ket{y} + \frac{1}{\sqrt{N}} \sum_{y = N / 2}^{N - 1} \cas\Big( \frac{2\pi a y}{N} \Big) \ket{y}.
+\end{equation}
+
+The second summation on the right-hand side can be expressed as:
+\begin{align*}
+	\sum_{y = N / 2}^{N - 1} \cas\Big( \frac{2\pi a y}{N} \Big) \ket{y}
+    & = \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi a y}{N} + \pi a \Big) \ket{y + N/2} \\
+    & = (-1)^a \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi a y}{N} \Big) \ket{y + N/2},
+\end{align*}
+The second equality follows from the angle-sum identity for the \( \cas \) function,
+\[
+\cas(\alpha + \beta) = \cos(\alpha)\cas(\beta) + \sin(\alpha)\cas(-\beta),
+\]
+along with the fact that \( \cos(\pi a) = (-1)^a \) for all integers \( a \). Substituting this into Equation~\eqref{eq:cas-expand} yields:
+\begin{align}
+	\frac{1}{\sqrt{N}} \sum_{y = 0}^{N - 1} \cas\Big( \frac{2\pi a y}{N} \Big) \ket{y}
+    & = \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi a y}{N} \Big) (\ket{y} + (-1)^a \ket{y + N/2}) \nonumber \\
+    & = \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi a y}{N} \Big) \frac{1}{\sqrt{2}} (\ket{0} + (-1)^a \ket{1}) \ket{y}, \label{eq:qht-alt} 
+\end{align}
+In the final equality, the most significant qubit has been isolated to emphasize its contribution to the overall transformation.
+
+We now demonstrate how to compute \( \qht_N \) recursively.
+For a given \( a \in \Z_N \), we decompose the basis state as \( \ket{a} = \ket{t}\ket{b} \), where \( b \) denotes the least significant bit, such that \( a = 2t + b \) for some \( t \in \Z_{N/2} \).
+Assuming the existence of an efficient quantum circuit for computing \( \qht_{N/2} \), we proceed to construct \( \qht_N \) in a recursive fashion.
+To begin the transformation on \( \ket{a} \), we introduce an ancilla qubit initialized to \( \ket{0} \), yielding the joint state \( \ket{0}\ket{t}\ket{b} \).
+We then proceed as follows:
+\begin{align*}
+	\ket{0}\ket{t}\ket{b}
+    & \mapsto \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi t y}{N / 2} \Big) \ket{0} \ket{y} \ket{b} & (\mathds{1} \otimes \qht_{N / 2} \otimes \mathds{1}) \\
+    & = \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{4\pi t y}{N} \Big) \ket{0} \ket{y} \ket{b} \\
+    & \mapsto \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{4\pi t y}{N} \Big) (\ket{0} + \ket{1}) \ket{y}\ket{b}. & (H \otimes \mathds{1})
+\end{align*}
+Next, we apply a controlled negation operation, where the ancilla qubit is flipped if and only if the least significant bit \( b \) is equal to 1.
+\[
+    V: \ket{0}\ket{y} \mapsto \ket{0}\ket{y}, \quad \ket{1}\ket{y} \mapsto \ket{1}\ket{N / 2 -y},
+\]
+\[
+    \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{4\pi t y}{N} \Big) \ket{0} \ket{y} \ket{b} + \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{4\pi t y}{N} \Big) \ket{1} \ket{-y} \ket{b}.
+\]
+By performing a change of variables in the second summation and using the identity \( \cas\left(\frac{4\pi t (N / 2 - y)}{N}\right) = \cas\left(-\frac{4\pi t y}{N}\right) \), we obtain the state:
+\[
+    \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \Big( \cas\Big( \frac{4\pi t y}{N} \Big) \ket{0} + \cas\Big( -\frac{4\pi t y}{N} \Big) \ket{1} \Big) \ket{y} \ket{b}.
+\]
+
+We define the single-qubit rotation \( R(\theta) \) as the unitary operator acting on a single qubit given by:\begin{equation}
+    \label{eq:sine-rot}
+    R(y, b) = 
+    \begin{bmatrix}
+        \cos(2\pi b y / N) & \sin(2\pi b y / N) \\
+        -\sin(2\pi b y / N) & \cos(2\pi b y / N)
+    \end{bmatrix},
+\end{equation}
+Now, consider the unitary \( U_R \) defined by
+\[
+U_R : \ket{c}\ket{y}\ket{b} \mapsto \left(R(y, b)\ket{c}\right)\ket{y}\ket{b},
+\]
+where \( R(y, b) \) is a single-qubit rotation depending on \( y \) and \( b \). Applying \( U_R \) followed by the controlled negation \( V \), we obtain the state:
+\begin{align*}
+    \ket{\phi_1}
+    & = \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \Big( \cas\Big( \frac{2\pi ay}{N} \Big) \ket{0} + \cas\Big(-\frac{2\pi a(N /2 - y)}{N} \Big) \ket{1} \Big) \ket{y} \ket{b} \\
+    & = \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi ay}{N} \Big) \Big( \ket{0} + (-1)^b \ket{1} \Big) \ket{y} \ket{b},
+\end{align*}
+Here, we have used the identity \( \cas\left(-\pi a + \frac{2\pi a y}{N}\right) = (-1)^a \cas\left(\frac{2\pi a y}{N}\right) \), along with the fact that \( (-1)^a = (-1)^b \).
+Applying the Hadamard transform to the first qubit yields:
+\[
+    \ket{\psi} = \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi ay}{N} \Big) \ket{b} \ket{y} \ket{b}
+\]
+Next, we uncompute the first qubit by applying a \textsc{CNOT} gate with the last qubit as control. We then apply a Hadamard transform followed by a swap operation, resulting in the state:
+\begin{align*}
+    \ket{\psi}
+    & \mapsto \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi ay}{N} \Big) \ket{0} \ket{y} \ket{b} & (\textsc{cnot}) \\
+    & \mapsto \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi ay}{N} \Big) \ket{0} \ket{y} \frac{1}{\sqrt{2}}(\ket{0} + (-1)^b \ket{1}) & (\mathds{1} \otimes H) \\
+    & = \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi ay}{N} \Big) \ket{0} \ket{y} \frac{1}{\sqrt{2}}(\ket{0} + (-1)^a \ket{1}). & ((-1)^b = (-1)^a) \\
+\end{align*}
+The final summation matches precisely with Equation~\eqref{eq:qht-alt}, which defines the quantum Hartley transform of \( \ket{a} \). Thus, we have successfully implemented the transformation:
+\[
+\ket{a} \mapsto \qht_N \ket{a}.
+\]
+\[ \ket{0}\ket{a} \mapsto \ket{0} \qht_N\ket{a}. \]
+The complete procedure is summarized in the following algorithm.
+
+\begin{algorithm}[$\qht_N$] \
+    \label{alg:qht-N}
+    \begin{description}[font = \normalfont\itshape, itemsep = 0mm, parsep = 0mm, topsep = 1mm]
+        \item [Input:] quantum state $\ket{\psi} \in \C^N$, where $N = 2^n$
+        \item [Output:] quantum state $\qht_N\ket{\psi}$
+    \end{description}
+
+    \begin{enumerate}[itemsep = 0mm, parsep = 1mm, topsep = 1mm]
+        \item Initialize an ancilla qubit to $0$ to obtain the state $\ket{0}\ket{\psi}$
+        \item Compute $\mathds{1} \otimes \qht_{N / 2} \otimes \mathds{1}$ recursively.
+        \item Apply $H \otimes \mathds{1}$.
+        \item\label{stp:ngt} Apply the controlled negation $\ket{0}\ket{y} \mapsto \ket{0}\ket{y}, \ket{1}\ket{y} \mapsto \ket{1}\ket{N / 2 -y}$ to the first two registers.
+        \item Apply the unitary $U_R$.
+        \item Apply $H \otimes \mathds{1}$
+        \item Apply \textsc{cnot} to the first and last qubits.
+        \item Apply $\mathds{1} \otimes H$.
+        \item Trace out the first qubit
+    \end{enumerate}
+\end{algorithm}
+
+\begin{theorem}
+    \label{thm:qht-cost}
+    Algorithm \ref{alg:qht-N} is correct and can be implemented using $\approx \log^2 N + O(\log N)$ elementary gates.
+\end{theorem}
+
+\begin{proof}
+    The correctness of the algorithm follows from the preceding discussion.
+Except for the unitary \( U_R \) and the negation unitary in Step~\ref{stp:ngt}, all steps of the algorithm can be implemented using \( O(1) \) elementary gates.
+The negation operation in Step~\ref{stp:ngt} can be realized using approximately \( \lceil \log N \rceil \) elementary gates.
+
+    To implement the unitary \( U_R \), which requires constructing the conditional rotation operator \( R(y, b) \) for arbitrary \( y \) and \( b \), we make use of the two-qubit controlled rotations:
+    \[
+    R_j = \ket{0}\bra{0} \otimes \mathds{1} + \ket{1}\bra{1} \otimes
+    \begin{bmatrix}
+    \cos\left(\frac{2\pi 2^j}{N}\right) & \sin\left(\frac{2\pi 2^j}{N}\right) \\
+    -\sin\left(\frac{2\pi 2^j}{N}\right) & \cos\left(\frac{2\pi 2^j}{N}\right)
+    \end{bmatrix},
+    \]
+    for \( j = 0, 1, \dots, n - 1 \).
+When \( b = 0 \), we have \( R(y, 0) = \mathds{1} \), and when \( b = 1 \), the operator \( R(y, 1) \) is the product of those \( R_j \) for which the \( j \)th bit of \( y \) is 1.
+Therefore, for a binary string \( y \) of length \( k = \lceil \log y \rceil \), we can implement \( U_R \) using at most \( k \) gates from the set \( \{R_j\} \).
+
+    Let \( T(N) \) denote the gate complexity of Algorithm~\ref{alg:qht-N} for an input of dimension \( N \).
+Assuming access to the \( R_j \) gates as elementary operations, the recurrence relation becomes
+    \[
+    T(N) \approx T(N / 2) + 2\log N + O(1).
+    \]
+    Solving this recurrence yields \( T(N) \approx \log^2 N + O(\log N) \), as claimed.
+    \end{proof}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Quantum Money With The Hartley Transform}
@@
 
-The quantum money scheme above can be instantiated using the quantum Hartley transform instead of the quantum Fourier transform.
-However, this substitution breaks the verification algorithm.
-In the next sections, we will show how quantum walks can address this issue.
-To understand where the problem arises, we first present the $\gen$ and $\ver$ algorithms for the money scheme, similar to the previous description but with $\qht_G$ replacing $\qft_G$.
-For simplicity, we assume $G = \Z_N$.
-Let $x \in \Z_N$ be a fixed element.
+The quantum money scheme described earlier can also be instantiated using the quantum Hartley transform in place of the quantum Fourier transform.
+However, this substitution disrupts the original verification procedure.
+In the following sections, we demonstrate how quantum walks can be employed to resolve this issue.
+To pinpoint the source of the problem, we begin by restating the \( \gen \) and \( \ver \) algorithms for this Hartley-based scheme, mirroring the structure of the Fourier-based version but replacing \( \qft_G \) with \( \qht_G \).
+For simplicity, we take \( G = \Z_N \), and fix an element \( x \in \Z_N \).
 
 \begin{itemize}
-\item $\gen$. Begin with the state $\ket{0}\ket{x}$, and apply the quantum Hartley transform over $\Z_N$ to the first register producing the superposition
-    \[ \frac{1}{\sqrt{N}} \sum_{g \in \Z_N} \ket{g}\ket{x}. \]
-    Next, apply the unitary $\ket{h}\ket{y} \mapsto \ket{h}\ket{h * y}$ to this state, followed by a $\qht_N$ on the first register. This results in
-    \[ \frac{1}{N} \sum_{h \in \Z_N} \sum_{g \in \Z_N} \cas\Big(\frac{2\pi gh}{N}\Big) \ket{h}\ket{g * x} = \frac{1}{\sqrt{N}} \sum_{h \in \Z_N} \ket{h} \ket{\Z_N^{(h)} * x}_H \]
+    \item \textbf{\( \gen \)}: Start with the state \( \ket{0}\ket{x} \), and apply the quantum Hartley transform over \( \Z_N \) to the first register, resulting in the superposition
+    \[
+    \frac{1}{\sqrt{N}} \sum_{g \in \Z_N} \ket{g}\ket{x}.
+    \]
+    Next, apply the unitary transformation \( \ket{h}\ket{y} \mapsto \ket{h}\ket{h * y} \), followed by a Hartley transform \( \qht_N \) on the first register. This yields the state
+    \[
+    \frac{1}{N} \sum_{h \in \Z_N} \sum_{g \in \Z_N} \cas\left(\frac{2\pi gh}{N}\right) \ket{h}\ket{g * x}
+    = \frac{1}{\sqrt{N}} \sum_{h \in \Z_N} \ket{h} \ket{\Z_N^{(h)} * x}_H,
+    \]
     where
-    \[ \ket{\Z_N^{(h)} * x}_H = \frac{1}{\sqrt{N}} \sum_{g \in \Z_N} \cas\Big(\frac{2\pi gh}{N}\Big) \ket{g * x}. \]
-    Measure the first register to obtain a random $h \in \Z_N$, collapsing the state to $\ket{\Z_N^{(h)} * x}_H$. Return the pair $(h, \ket{\Z_N^{(h)} * x}_H)$.
-
-\item $\ver(h, \ket{\psi})$.
-First, check whether $\ket{\psi}$ has support in $X$.
-If not, return $0$.
-Then, apply $\comph$ to the state $\ket{0} \ket{\psi}$, and measure the first register to obtain some $h' \in \Z_N$.
-If $h' = h$, return $1$; otherwise return $0$.
+    \[
+    \ket{\Z_N^{(h)} * x}_H = \frac{1}{\sqrt{N}} \sum_{g \in \Z_N} \cas\left(\frac{2\pi gh}{N}\right) \ket{g * x}.
+    \]
+    Measure the first register to obtain a random \( h \in \Z_N \), collapsing the state to \( \ket{\Z_N^{(h)} * x}_H \). Return the pair \( (h, \ket{\Z_N^{(h)} * x}_H) \).
+
+    \item \textbf{\( \ver(h, \ket{\psi}) \)}: First, check whether \( \ket{\psi} \) has support in \( X \).
+If not, return \( 0 \).
+Otherwise, apply \( \comph \) to the state \( \ket{0} \ket{\psi} \), and measure the first register to obtain some \( h' \in \Z_N \).
+Return \( 1 \) if \( h' = h \), and \( 0 \) otherwise.
 \end{itemize}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section*{Verification using quantum walks}
 
+Given a state of the form $\ket{\Z_N^{(h)} * x}_H$, we demonstrate how the value of $h$ can be extracted using continuous-time quantum walks.
+For any $u \in \Z_N$, consider the Cayley graph $\Gamma = (\Z_N, E)$ generated by $Q = {-u, u}$, as introduced in Section \ref{sec:ga-qwalk}.
+Let $A$ denote the adjacency matrix of $\Gamma$.
+The eigenvectors of $A$ are given by $\ket{\Z_N^{(h)} * x}$, with corresponding eigenvalues $\lambda_h = 2\cos(2\pi uh / N)$ for each $h \in \Z_N$.
+According to Theorem \ref{thm:sparse-sim} and the discussion that follows, the unitary evolution operator $W = e^{iAt}$ can be simulated efficiently to exponential precision.
+To proceed, we first state the following lemma.
+
+\begin{lemma}
+    \label{lem:h-eigen}
+    The money state $\ket{\Z_N^{(h)} * x}_H$ is an eigenstate of $W$ with eigenvalue $e^{i\lambda_h t}$.
+\end{lemma}
+\begin{proof}
+    We have 
+    \begin{align*}
+        e^{iAt} \ket{\Z_N^{(h)} * x}_H
+        & = \sum_{g \in \Z_N} e^{i\lambda_gt} \ket{\Z_N^{(g)} * x} \braket{\Z_N^{(g)} * x}{\Z_N^{(h)} * x}_H \\
+        & = \sum_{g \in \Z_N} e^{i\lambda_gt} \ket{\Z_N^{(g)} * x} \bra{\Z_N^{(g)} * x} \Big( \frac{1 - i}{2} \ket{\Z_N^{(h)} * x} + \frac{1 + i}{2} \ket{\Z_N^{(-h)} * x} \Big) \\
+        & = e^{i\lambda_{h}t} \frac{1 - i}{2} \ket{\Z_N^{(h)} * x} + \frac{1 + i}{2} e^{i\lambda_{-h}t} \ket{\Z_N^{(-h)} * x} \\
+        & = e^{i\lambda_{h}t} \ket{\Z_N^{(h)} * x}_H,
+    \end{align*}
+    where the second equality follows from the identity in \eqref{eq:ht-ft}, and the last equality follows from the fact that $\lambda_h = \lambda_{-h}$.
+\end{proof}
+
+By setting \( t = \poly(\log N) \), Lemma~\ref{lem:h-eigen} ensures that phase estimation can be performed using the unitary \( W \) and the eigenstate \( \ket{\Z_N^{(h)} * x}_H \), yielding an approximation \( \tilde{\lambda}_h \) of \( \lambda_h \) such that
+\[
+\abs{\tilde{\lambda}_h - \lambda_h} \le \frac{1}{\poly(\log N)}.
+\]
+From this approximation, we can extract a real number \( 0 \le \theta \le 1 \) satisfying
+\[
+\abs*{\theta - \frac{uh}{N}} \le \frac{1}{\poly(\log N)}.
+\]
+Since phase estimation can be applied with various choices of \( u \), we can obtain multiple approximations of \( \frac{uh}{N} \).
+As shown in~\cite{zhandry2024quantum}, selecting \( u \) appropriately allows us to reconstruct \( h \) exactly from these estimates.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \bibliographystyle{plain}

### 2025-04-01 presentation.tex
new commit
presentation updated

@@
 \usepackage{amsmath}
+\usepackage{tikz}
+
 % \usepackage{amsmath, amssymb, dsfont}
@@
 
-% \begin{frame}{Program and Courses Taken}
+\begin{frame}{Quantum Computation - Preliminaries and Notation}
 
-%     \begin{textblock*}{12cm}(0.5cm,1.5cm)
-%        \begin{itemize}
-%         \item Program: M.A.Sc in Software Engineering
-%         \vspace{1cm}
-%         \item CAS 701,  Logic \& Discrete Mathematics
-%         \item COMPSCI 6TE3, Continuous optimization
-%         \item CAS 721, Combinatorics \& Computing
-%         \item CAS 741, Development of Scientific Computation Software
-%        \end{itemize}
-%     \end{textblock*}
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+        In this talk, we explore the interplay between quantum computation, group theory, and cryptography through the lens of quantum walks. The presentation is organized as follows:
 
-%     \title{SDSD}
+        \vspace{0.5cm}
+        \begin{enumerate}
+            \item \textbf{Quantum Computation Preliminaries} \\
+            \vspace{0.1cm}
 
-% \end{frame}
+            \item \textbf{Quantum Walks} \\
+            \vspace{0.1cm}
 
-% \begin{frame}{Seminars}
+            \item \textbf{Quantum Money Schemes} \\
+            \vspace{0.1cm}
+            \item \textbf{Verification of our New Quantum Money scheme using Quantum Walks} \\
 
-%     \begin{textblock*}{12cm}(0.5cm,1.5cm)
-%        \begin{itemize}
-%         \item I have participated in 6 seminars during my program.
-%        \end{itemize}
-%     \end{textblock*}
+        \end{enumerate}
 
-% \end{frame}
-
-% \begin{frame}{Poster}
-
-%     \begin{figure}
-%         \centering
-%         \includegraphics[width=1\textwidth]{poster.png}
-%         \caption{Presented at Nov. 6, 2024}
-%     \end{figure}
-
-% \end{frame}
+    \end{textblock*}
+\end{frame}
 
@@
 \begin{frame}{Example of a Continuous Quantum Walk}
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+        \centering
+        \begin{tikzpicture}[scale=1, every node/.style={circle, draw=black, fill=white, minimum size=10pt, inner sep=2pt}]
+            % Draw nodes
+            \node (-3) at (-3,0) {-3};
+            \node (-2) at (-2,0) {-2};
+            \node (-1) at (-1,0) {-1};
+            \node (0)  at (0,0)  {0};
+            \node (1)  at (1,0)  {1};
+            \node (2)  at (2,0)  {2};
+            \node (3)  at (3,0)  {3};
+
+            % Draw edges
+            \draw (-3) -- (-2);
+            \draw (-2) -- (-1);
+            \draw (-1) -- (0);
+            \draw (0)  -- (1);
+            \draw (1)  -- (2);
+            \draw (2)  -- (3);
+
+            % Add fading dashed arrows to suggest infinite continuation
+            \draw[dashed, ->] (-3,0) -- (-3.8,0);
+            \draw[dashed, ->] (3,0) -- (3.8,0);
+        \end{tikzpicture}
+
+        \begin{itemize}
+        \vspace{0.5cm}
+        \item \textbf{Graph:} Infinite line with vertices labeled by integers \( n \in \mathbb{Z} \).
+        \item \textbf{Adjacency Matrix:} Each vertex is connected to its neighbors \( n \pm 1 \).
+        \[
+        A_{i,j} = \begin{cases}
+            1 & \text{if } |i - j| = 1 \\
+            0 & \text{otherwise}
+        \end{cases}
+        \]
+
+        \item \textbf{Hilbert Space:} Spanned by basis states \( |n\rangle \), representing positions.
+        \item \textbf{Time Evolution:} Governed by Schrödinger equation
+        \[
+        i \frac{d}{dt} |\psi(t)\rangle = A |\psi(t)\rangle
+        \quad \Rightarrow \quad
+        |\psi(t)\rangle = e^{-iAt} |\psi(0)\rangle
+        \]
+    \end{itemize}
+
+    \end{textblock*}
+\end{frame}
+
+\begin{frame}{Example of a Continuous Quantum Walk}
 
     \begin{textblock*}{12cm}(0.5cm,1.5cm)
+
+        \begin{itemize}
+            \item \textbf{Initial State:} Particle starts at the origin:
+            \[
+            |\psi(0)\rangle = |0\rangle
+            \]
+
+            \item \textbf{Evolved State:}
+            \[
+            |\psi(t)\rangle = \sum_{n \in \mathbb{Z}} \psi_n(t) |n\rangle
+            \quad \text{where } \psi_n(t) = i^n J_n(2t)
+            \]
+
+            \item \textbf{Key Features:}
+            \begin{itemize}
+                \item Probability: \( |\psi_n(t)|^2 \)
+                \item Wave-like, oscillatory distribution due to interference
+                \item Faster spread than classical walk: standard deviation grows linearly in \( t \)
+                \item No coin space needed — evolution depends only on graph structure
+            \end{itemize}
+        \end{itemize}
 
@@
     \begin{textblock*}{12cm}(0.5cm,1.5cm)
+        \begin{itemize}
+            \item \textbf{Hilbert Space:} $\mathcal{H} = \mathcal{H}_C \otimes \mathcal{H}_P$
+            \begin{itemize}
+                \item $\mathcal{H}_C$: 2D coin space with basis $\{|0\rangle, |1\rangle\}$
+                \item $\mathcal{H}_P$: Infinite-dimensional position space with basis $\{|n\rangle : n \in \mathbb{Z}\}$
+            \end{itemize}
+
+            \item \textbf{Coin Operator:} Apply a unitary $C$ (e.g., Hadamard) to $\mathcal{H}_C$
+            \[
+            H = \frac{1}{\sqrt{2}} \begin{bmatrix}
+                1 & 1 \\
+                1 & -1
+            \end{bmatrix}
+            \]
+
+            \item \textbf{Shift Operator:} Moves the walker based on coin state:
+            \[
+            S|0\rangle|n\rangle = |0\rangle|n + 1\rangle, \quad
+            S|1\rangle|n\rangle = |1\rangle|n - 1\rangle
+            \]
+
+            \item \textbf{One Step:} Apply the unitary operator
+            \[
+            U = S \cdot (C \otimes I)
+            \]
+        \end{itemize}
+
+    \end{textblock*}
+\end{frame}
+
+\begin{frame}{Example of a Discrete-Time Quantum Walk}
+
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+        \begin{itemize}
+            \item \textbf{Initial State:} $|\psi(0)\rangle = |0\rangle \otimes |0\rangle$
+
+            \item \textbf{After One Step:}
+            \[
+            |\psi(1)\rangle = \frac{1}{\sqrt{2}} \left( |0\rangle|1\rangle + |1\rangle|-1\rangle \right)
+            \]
+
+            \item \textbf{Key Properties:}
+            \begin{itemize}
+                \item Superposition leads to \textbf{parallel exploration} of paths.
+                \item Repeated application of $U$ creates \textbf{interference patterns}.
+                \item Spread is faster than classical: $\sigma(t) \sim t$ vs. $\sqrt{t}$.
+            \end{itemize}
+
+            \vspace{0.5cm}
+            \item \textbf{Measurement:}
+            \begin{itemize}
+                \item Measuring after each step yields a classical random walk.
+                \item \textbf{Quantum behavior requires delaying measurement.}
+            \end{itemize}
+        \end{itemize}
 
@@
     \begin{textblock*}{12cm}(0.5cm,1.5cm)
+        \vspace{0.5cm}
+
+        \begin{itemize}
+            \item \textbf{CTQW}: Easier to analyze due to direct spectral decomposition.
+            \vspace{0.3cm}
+            \item \textbf{CTQW}: Harder to implement on quantum circuits (requires simulating \( e^{-iAt} \)).
+            \vspace{0.3cm}
+            \item \textbf{DTQW}: More complex to analyze (involves coin and shift operators).
+            \vspace{0.3cm}
+            \item \textbf{DTQW}: Easier to implement on gate-based quantum hardware.
+        \end{itemize}
 
@@
     \begin{textblock*}{12cm}(0.5cm,1.5cm)
+
+        \begin{figure}[h!]
+            \centering
+            \begin{tikzpicture}[shorten >=1pt, auto, node distance=2cm,
+                thick, main node/.style={circle,draw,font=\sffamily\small\bfseries}]
+
+                % Define nodes explicitly
+                \node[main node] (0) at (90:2cm) {0};
+                \node[main node] (1) at (45:2cm) {1};
+                \node[main node] (2) at (0:2cm) {2};
+                \node[main node] (3) at (-45:2cm) {3};
+                \node[main node] (4) at (-90:2cm) {4};
+                \node[main node] (5) at (-135:2cm) {5};
+                \node[main node] (6) at (180:2cm) {6};
+
+                % Node N-1 explicitly
+                \node[main node] (N-1) at (135:2cm) {N-1};
+
+                % Ellipsis between node 6 and N-1
+                \node at (157.5:2cm) {\dots};
+
+                % Draw edges explicitly
+                \draw (0) -- (1) -- (2) -- (3) -- (4) -- (5) -- (6);
+                \draw (6) -- (157.5:1.8cm); % connecting dots visually
+                \draw (N-1) -- (0); % close the cycle
+
+            \end{tikzpicture}
+            \caption{Cayley graph of $\mathbb{Z}_N$ with generators $\{\pm 1\}$}
+            \label{fig:cyclic-graph}
+        \end{figure}
 
@@
 
+        \begin{figure}[H]
+            \centering
+            \begin{tikzpicture}[thick, 
+                main node/.style={circle, draw, font=\sffamily\small\bfseries},
+                adjacent node/.style={circle, draw, font=\sffamily\small},
+                scale=1]
+
+                % Central node g
+                \node[main node] (g) at (0,0) {$g$};
+
+                % Define number of adjacent vertices
+                \def \K {5}
+                \def \radius {2cm}
+                \def \angle {360/\K}
+
+                % Draw adjacent nodes
+                \foreach \i in {1,...,\K}{
+                    \node[adjacent node] (q\i) at ({90+\angle*(\i-1)}:\radius) {$g*q_{\i}$};
+                    \draw (g) -- (q\i);
+                }
+
+                % Optional dots if there are many vertices (e.g., q_k)
+                \node at ({90+\angle*(\K)}:\radius) {\dots};
+
+            \end{tikzpicture}
+            \caption{Cayley graph of a group $G$ with generators $\{q_1, q_2, ... , q_k\}$}
+
+            \label{fig:group-action-orbit}
+        \end{figure}
+
+    \end{textblock*}
+\end{frame}
+
+\begin{frame}{Cayley Graphs with Group Actions}
+    \begin{textblock*}{12cm}(0.5cm,1.5cm)
+
     Given a regular group action $(G, X, *)$ with a fixed element $x \in X$ and a set  $Q = \{q_1, q_2, \dots, q_k\} \subset G$, let $\Gamma = (X, E)$ be a graphs with vertex set $X$ and edge set consisting of pairs $(x, y) \in X \times X$ such that $y = q * x$ for some $q \in Q$.
@@
 
-    \end{textblock*}
-
-\end{frame}
-
-\begin{frame}{The cmpIndex Algorithm}
-
-    \begin{textblock*}{12cm}(0.5cm,1.5cm)
-        Given a state $\ket{G^{(h)} * x}$, there is an efficient algorithm for computing $h$.
-        Specifically, there is a unitary operator that performs the transformation $\ket{G^{(h)} * x} \ket{0} \mapsto \ket{G^{(h)} * x} \ket{h}$:
-
-        \[
-        \ket{G^{(h)} * x}\ket{0} \mapsto \ket{G^{(h)} * x} \frac{1}{\sqrt{|G|}}\sum_{k \in G}\ket{k}
-        \]
-        And then apply the unitary $\sum_{k \in G}U_k \otimes \ket{k}\bra{k}$:
-
-        \[
-        \mapsto \frac{1}{\sqrt{|G|}}\sum_{k \in G}\ket{G^{(h)}*x}\chi(-k,h)\ket{k}
-        \]
-
-        Finally, applying the inverse quantum Fourier transform to the second register yields:
-
-        \[
-           \mapsto  \ket{G^{(h)}*x}\ket{h}
-        \]
     \end{textblock*}
@@
 
-        % \begin{align*}
-        %     2\ket{0} \bra{0} \otimes TT^* - 1
-        %     & = 2\ket{0} \bra{0} \otimes \sum_{y \in X} \sum_{b \in \{0, 1\}} \ket{y, b} \ket{\phi_{yb}} \bra{y, b} \bra{\phi_{yb}} - 1 \\
-
-        %     & = U_T (2 \ket{0} \bra{0} \otimes 1_{X, b} \otimes \ket{0, 0} \bra{0, 0} - 1) U_T^*.
-
-        % \end{align*}
-
-        \[
-        2\ket{0} \bra{0} \otimes TT^* - 1 = 2\ket{0} \bra{0} \otimes \sum_{y \in X} \sum_{b \in \{0, 1\}} \ket{y, b} \ket{\phi_{yb}} \bra{y, b} \bra{\phi_{yb}} - 1 
-        \]
-
-        \[
-        = 2\sum_{y \in X} \sum_{b \in \{0, 1\}} \ket{0} \ket{y, b} \ket{\phi_{yb}} \bra{0} \bra{y, b} \bra{\phi_{yb}} - 1 
-        \]
-
-        \[
-        = U_T \Big( 2\sum_{y \in X} \sum_{b \in \{0, 1\}} \ket{0} \ket{y, b} \ket{0, 0} \bra{0} \bra{y, b} \bra{0, 0} - 1 \Big) U_T^* 
-        \]
-
-        \[
-        = U_T (2 \ket{0} \bra{0} \otimes 1_{X, b} \otimes \ket{0, 0} \bra{0, 0} - 1) U_T^*
-        \]
-
-        Now, for any state $\ket{\psi}$:
-
-        \[
-        (2\ket{0}\bra{0}\otimes TT^* - 1)\ket{0}\ket{\psi} = \ket{0}(2TT^*-1)\ket{\psi}
-        \]
-
-    \end{textblock*}
-
-\end{frame}
-
-\begin{frame}{Group Action Quantum Walks}
-
-    \begin{textblock*}{12cm}(0.5cm,1.5cm)
-
-        Given a regular group action $(G, X, *)$ with a fixed element $x \in X$ and a set  $Q = \{q_1, q_2, \dots, q_k\} \subset G$, let $\Gamma = (X, E)$ be a graphs with vertex set $X$ and edge set consisting of pairs $(x, y) \in X \times X$ such that $y = q * x$ for some $q \in Q$.
-The adjacency matrix of $\Gamma$ is
-        \[ A = \sum_{h \in G} \lambda_h \ket{G^{(h)} * x} \bra{G^{(h)} * x}, \]
-        where:
-        \begin{itemize}
-            \item $\lambda_h = \sum_{q \in Q} \chi(h, q)$
-            \item the eigenvectors $\ket{G^{(h)} * x}$ depend only on $G$
-        \end{itemize}
-
     \end{textblock*}
@@
 If not, return $0$.
-Then, apply $\comph$ to the state $\ket{\psi}\ket{0}$, and measure the second register to obtain some $h' \in G_\lambda$.
+Then, apply \textit{cmpIndex} to the state $\ket{\psi}\ket{0}$, and measure the second register to obtain some $h' \in G_\lambda$.
 If $h' = h$, return $1$; otherwise return $0$.
+
+        \vspace{1.5cm}
+        cmpIndex Algorithm:
+        \vspace{0.3cm}
+        \item  Given a state $\ket{G^{(h)} * x}$, there is an efficient algorithm for computing $h$.
+        Specifically, there is a unitary operator that performs the transformation $\ket{G^{(h)} * x} \ket{0} \mapsto \ket{G^{(h)} * x} \ket{h}$:
         \end{itemize}
@@
         Lemma: The money state $\ket{\mathbb{Z}_N^{(h)} * x}_H$ is an eigenstate of $W$ with eigenvalue $e^{i\lambda_h t}$.
-        % \vspace{1cm}
-
-        \textit{Proof:}
-        \begin{align*}
-            e^{iAt} \ket{\mathbb{Z}_N^{(h)} * x}_H
-            & = \sum_{g \in \mathbb{Z}_N} e^{i\lambda_gt} \ket{\mathbb{Z}_N^{(g)} * x}\braket{\mathbb{Z}_N^{(g)} * x|\mathbb{Z}_N^{(h)} * x}_H 
-        \end{align*}
-
-        \[
-        =\sum_{g \in \mathbb{Z}_N} e^{i\lambda_gt} \ket{\mathbb{Z}_N^{(g)} * x} \bra{\mathbb{Z}_N^{(g)} * x} \Big( \frac{1 - i}{2} \ket{\mathbb{Z}_N^{(h)} * x} + \frac{1 + i}{2} \ket{\mathbb{Z}_N^{(-h)} * x} \Big)
-        \]
-
-        \[
-        =e^{i\lambda_{h}t} \frac{1 - i}{2} \ket{\mathbb{Z}_N^{(h)} * x} + \frac{1 + i}{2} e^{i\lambda_{-h}t} \ket{\mathbb{Z}_N^{(-h)} * x} 
-        \]
-
-        \[
-        =e^{i\lambda_{h}t} \ket{\mathbb{Z}_N^{(h)} * x}_H,
-        \]
-
-        where the last equality follows from the fact that $\lambda_h = \lambda_{-h}$.
-    \end{textblock*}
-
- \end{frame}
-
-\begin{frame}{Computing the serial Number}
-
-    \begin{textblock*}{12cm}(0.5cm,1.5cm)
-        Lemma: The money state $\ket{\mathbb{Z}_N^{(h)} * x}_H$ is an eigenstate of $W$ with eigenvalue $e^{i\lambda_h t}$.
         \vspace{1cm}
@@
         \end{align*}
-
-    \end{textblock*}
-
-\end{frame}
-
-\begin{frame}{An efficient new algorithm for QHT}
-
-    \begin{textblock*}{12cm}(0.5cm,1.5cm)
-        Let $\ket{a} = \ket{t}\ket{b}$, where $b$ is the least significant bit of $a$, so that $a = 2t + b$. Applying $\qft_{N / 2}$ to the first register, we obtain the state
-        \[ \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \omega_N^{2ty} \ket{y} \ket{b}. \]
-        Next, we apply the phase unitary $P(y, b): \ket{y} \ket{b} \mapsto \omega_N^{by} \ket{y} \ket{b}$, and finally, we apply a Hadamard transform to the last qubit.
-The result is the state in \eqref{eq:qft_alt}.
 
@@
         \begin{align*}
-            \ket{0}\ket{t}\ket{b}
+            \ket{0}\ket{a} = \ket{0}\ket{t}\ket{b}
             & \mapsto \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi t y}{N / 2} \Big) \ket{0} \ket{y} \ket{b} \\%& (\mathds{1} \otimes \qht_{N / 2} \otimes \mathds{1}) \\

### 2025-04-01 main.tex
presentation updated
main.tex updated

@@
 \usepackage{authblk}
+\usepackage{tikz}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section*{Continuous-Time Quantum Walks}
@@
 
-*********Examples and further discussions here*********
-
-% Overall, the transition from classical continuous-time Markov chains to continuous-time quantum walks highlights fundamental differences between classical and quantum dynamics, particularly the role of interference and the constraints of unitary evolution in quantum systems.
-These differences underscore the potential of quantum walks in quantum computing and algorithm design.
-
+\subsection*{Example: Continuous-Time Quantum Walk on the Line}
+
+To illustrate the behavior of continuous-time quantum walks, consider the example of a particle evolving on the \textit{infinite one-dimensional lattice}, also known as the \textit{integer line}.
+In this graph, the vertices are labeled by integers \( \mathbb{Z} \), and each vertex \( n \in \mathbb{Z} \) is connected to its immediate neighbors \( n-1 \) and \( n+1 \).
+The adjacency matrix \( A \) for this graph has entries:
+\[
+A_{i,j} =
+\begin{cases}
+1 & \text{if } |i - j| = 1, \\
+0 & \text{otherwise}.
+\end{cases}
+\]
+
+Let the walker initially be located at the origin, so the initial state is \( |\psi(0)\rangle = |0\rangle \). The quantum evolution of the system is governed by the Schrödinger equation:
+\[
+i \frac{d}{dt} |\psi(t)\rangle = A |\psi(t)\rangle,
+\]
+with the solution:
+\[
+|\psi(t)\rangle = e^{-iAt} |\psi(0)\rangle.
+\]
+
+For this specific graph, the amplitude of being at position \( n \) at time \( t \) has an elegant closed-form expression:
+\[
+\psi_n(t) = i^n J_n(2t),
+\]
+where \( J_n \) is the \textit{Bessel function of the first kind} of order \( n \). The corresponding probability of finding the walker at vertex \( n \) at time \( t \) is:
+\[
+p_n(t) = |\psi_n(t)|^2 = |J_n(2t)|^2.
+\]
+
+This probability distribution displays quintessential quantum behavior: it is \textbf{non-Gaussian}, \textbf{oscillatory}, and \textbf{spreads faster} than in the classical case.
+In contrast to the diffusive behavior of classical walks, where the standard deviation grows as \( \sigma(t) \propto \sqrt{t} \), the quantum walk exhibits \textit{ballistic spread} with \( \sigma(t) \propto t \).
+
+These interference-driven properties make CTQWs particularly powerful for applications in quantum information and quantum algorithms, where the speed and spread of information are crucial.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section*{Discrete-Time Quantum Walks}
-*******************
-The discrete-time coined quantum walk (DTQW) is a quantum analog of classical random walks, leveraging the principles of quantum mechanics to achieve unique computational and dynamical properties.
-It is defined on a graph or lattice, with the walker's state described by both its position and an internal "coin" state.
-The walker's position \( n \) on a one-dimensional lattice (line) is represented by a vector \( |n\rangle \) in an infinite-dimensional Hilbert space \( \mathcal{H}_P \), where the computational basis for \( \mathcal{H}_P \) is
-
-\[
-\{ |n\rangle : n \in \mathbb{Z} \}.
-\]
-
-The walker's internal state, or "coin," is represented by a two-dimensional Hilbert space \( \mathcal{H}_C \) with basis states \( |0\rangle \) and \( |1\rangle \).
-The coin state determines the direction of the walker's movement, and the total state of the system resides in the tensor product space
-
-\[
-\mathcal{H} = \mathcal{H}_C \otimes \mathcal{H}_P,
-\]
-
-combining the coin and position spaces.
-
-The dynamics of the walk are governed by two key operators: the coin operator and the shift operator.
-The coin is represented by a unitary matrix \( C \) acting on \( \mathcal{H}_C \).
-Common choices include the Hadamard matrix, which creates superpositions of the coin states.
-The Hadamard coin operator \( H \) is defined as
-
-\[
-H = \frac{1}{\sqrt{2}} \begin{pmatrix} 1 & 1 \\ 1 & -1 \end{pmatrix}.
-\]
-
-The shift operator \( S \) moves the walker based on the coin state.
-For example, if the coin state is \( |0\rangle \), the walker moves to \( |n+1\rangle \), and if the coin state is \( |1\rangle \), the walker moves to \( |n-1\rangle \).
-The shift operator is explicitly given by
-
-\[
-S = \sum_{n} |n+1\rangle \langle n| \otimes |0\rangle \langle 0| + |n-1\rangle \langle n| \otimes |1\rangle \langle 1|.
-\]
-
-The evolution of the system is described by the unitary operator
-
-\[
-U = S \cdot (I \otimes C),
-\]
-
-where \( I \) is the identity operator on \( \mathcal{H}_P \). The state of the walker at time \( t+1 \) is given by
-
-\[
-|\psi(t+1)\rangle = U |\psi(t)\rangle.
-\]
-
-Consider a quantum walk on a one-dimensional lattice.
-The walker's state evolves in superposition, allowing it to explore multiple paths simultaneously.
-Interference between these paths leads to faster spreading compared to classical random walks.
-
-Key features of DTQW include superposition, where the walker exists in a superposition of positions and coin states, enabling parallel exploration of multiple paths; interference, where quantum interference enhances or suppresses certain paths, leading to non-classical behavior; and quadratic speedup, where quantum walks spread faster than classical random walks, often quadratically, which is advantageous for algorithmic applications.
-
-DTQWs are used in quantum algorithms, such as quantum search and graph traversal, and in simulating physical systems like energy transport in photosynthesis.
-They also serve as a framework for universal quantum computation.
-The discrete-time quantum walk is a powerful tool in quantum computing, offering a rich interplay between quantum mechanics and graph theory.
-Its ability to exploit superposition and interference enables applications in algorithm design, simulation, and computation, making it a cornerstone of quantum information science.
-
-*********Examples and further discussions here*********
-
+
+Discrete-time quantum walks (DTQWs) serve as the discrete counterpart of quantum random walks and are particularly useful for algorithmic constructions in quantum computing.
+Unlike continuous-time quantum walks, DTQWs require an additional coin degree of freedom to preserve unitarity in the evolution.
+In this section, we explore the discrete-time coined quantum walk on the infinite one-dimensional lattice (integer line), which provides a clear and tractable example of how interference and superposition govern quantum behavior.
+
+\subsubsection*{Hilbert Space and Coin Space}
+
+The state space of the system is the tensor product \( \mathcal{H} = \mathcal{H}_C \otimes \mathcal{H}_P \), where:
+\begin{itemize}
+    \item \( \mathcal{H}_C \) is the 2-dimensional Hilbert space of the quantum coin, with basis states \( \{|0\rangle, |1\rangle\} \), often interpreted as ``spin up'' and ``spin down''.
+    \item \( \mathcal{H}_P \) is the position Hilbert space, spanned by \( \{|n\rangle : n \in \mathbb{Z}\} \), representing the particle's location on the integer line.
+\end{itemize}
+
+\subsubsection*{Coin and Shift Operators}
+
+The walk consists of two operations applied in sequence:
+\begin{enumerate}
+    \item \textbf{Coin operator \( C \)}: A unitary operator acting on \( \mathcal{H}_C \), typically chosen to create superposition. A common choice is the \textit{Hadamard coin}:
+    \[
+    H = \frac{1}{\sqrt{2}} \begin{bmatrix}
+    1 & 1 \\
+    1 & -1
+    \end{bmatrix}.
+    \]
+    \item \textbf{Shift operator \( S \)}: A unitary operator on \( \mathcal{H}_C \otimes \mathcal{H}_P \) that moves the walker depending on the coin state:
+    \[
+    S|0\rangle|n\rangle = |0\rangle|n + 1\rangle, \quad
+    S|1\rangle|n\rangle = |1\rangle|n - 1\rangle.
+    \]
+\end{enumerate}
+
+One full step of the walk is implemented by applying the unitary operator:
+\[
+U = S (C \otimes I_P),
+\]
+where \( I_P \) is the identity operator on \( \mathcal{H}_P \). Repeated application of \( U \) evolves the quantum state over time:
+\[
+|\psi(t)\rangle = U^t |\psi(0)\rangle.
+\]
+
+\subsubsection*{Example: Hadamard Walk from the Origin}
+
+Suppose the initial state of the system is localized at the origin with coin state \( |0\rangle \):
+\[
+|\psi(0)\rangle = |0\rangle \otimes |0\rangle.
+\]
+Applying the Hadamard operator and then the shift, the system evolves after one step into a superposition:
+\[
+|\psi(1)\rangle = \frac{1}{\sqrt{2}} \left( |0\rangle|1\rangle + |1\rangle|-1\rangle \right).
+\]
+The particle is now in a coherent superposition of being at positions \( +1 \) and \( -1 \), determined by its coin state.
+
+This process continues iteratively. For example, the second and third steps yield:
+\begin{align*}
+|\psi(2)\rangle &= \frac{1}{2} \left( -|1\rangle|-2\rangle + (|0\rangle + |1\rangle)|0\rangle + |0\rangle|2\rangle \right), \\
+|\psi(3)\rangle &= \frac{1}{2\sqrt{2}} \left( |1\rangle|-3\rangle - |0\rangle|-1\rangle + (2|0\rangle + |1\rangle)|1\rangle + |0\rangle|3\rangle \right).
+\end{align*}
+
+\subsubsection*{Quantum vs Classical Behavior}
+
+The key difference between quantum and classical random walks lies in the presence of \textit{interference} and \textit{superposition}:
+\begin{itemize}
+    \item In classical random walks, probabilities are updated step-by-step based on stochastic transitions, leading to a binomial distribution that approximates a Gaussian as time progresses.
+    \item In contrast, discrete-time quantum walks generate probability amplitudes that can interfere constructively or destructively depending on the history of the evolution.
+\end{itemize}
+
+As a result, the probability distribution of the DTQW is not symmetric or Gaussian, and it spreads much faster than its classical counterpart.
+Specifically, the standard deviation of a DTQW grows linearly with time \( \sigma(t) \sim t \), while in the classical case it grows as \( \sqrt{t} \).
+
+If a position measurement is performed after every step, the quantum walk collapses into a classical random walk due to decoherence.
+However, by deferring measurement and allowing the system to evolve unitarily over many steps, quantum correlations between paths persist, yielding a rich interference pattern in the final probability distribution.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection*{Comparison of Models}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Group Actions}

### 2025-04-02 presentation.tex
presentation updated

@@
 
+    \textbf{Abelian Groups:}
+    \begin{itemize}
+        \item $e^{-iAt} = \text{QFT}_G \left( \sum_{a \in G} e^{-i\lambda_a t} |a\rangle\langle a| \right) \text{QFT}_G^*$
+        \item Efficient since:
+        \begin{itemize}
+            \item QFT$_G$ and QFT$_G^*$ run in poly$(\log|G|)$ time.
+            \item $\lambda_a$ computable to high precision classically.
+        \end{itemize}
+    \end{itemize}
+
+    \vspace{0.5cm}
+    \textbf{Group Actions:}
+    \begin{itemize}
+        \item No efficient QFT-like decomposition.
+        \item Can express:
         \[
-        \ket{\phi_{j0}} := \frac{1}{\sqrt{d}}\sum_{l \in F_j}(\sqrt{\frac{H^*_{jl}}{K}}\ket{0} + \sqrt{1-\frac{|H^*_{jl}|}{K}}\ket{1})
+        e^{-iAt} = \sum_{h \in G} e^{-i\lambda_h t} |G^{(h)} * x\rangle\langle G^{(h)} * x|
         \]
-
-        \[
-        \ket{\phi_{j1}} := \ket{0}\ket{1} 
-        \]
-
-        \[
-        T := \sum_{j=0}^{N-1}\sum_{b \in {\{0,1\}}}(\ket{j}\bra{j}\otimes\ket{b}\bra{b})\otimes\ket{\phi_{jb}}
-        \]
-
-        \[
-        W = iS(2TT^* - 1)
-        \]
-
-        \[
-        S\ket{j_1,b_1}\ket{j_2,b_2} = \ket{j_2,b_2}\ket{j_1,b_1}
-        \]
+        \item But still approximable for $t = \text{poly}(\log|G|)$ due to structure in $A$.
+    \end{itemize}
 
@@
 
-\begin{frame}{Simulating continuous-time walks}
-
-    \begin{textblock*}{12cm}(0.5cm,1.5cm)
-
-       \[
-       e^{-iAt} = \operatorname{QFT_G}(\sum_{a \in G}e^{-i\lambda_at}\ket{a}\bra{a})\operatorname{QFT^*_G}
-       \]
-
-    \end{textblock*}
-
-\end{frame}
-
-% \begin{frame}{Simulating group action quantum walks}
+% \begin{frame}{Simulating continuous-time walks}
 
@@
 %         \[
-%         e^{-iAt} = \sum_{h \in G}\ket{G^{(h)}*x}\bra{G^{(h)}*x}
+%         \ket{\phi_{j0}} := \frac{1}{\sqrt{d}}\sum_{l \in F_j}(\sqrt{\frac{H^*_{jl}}{K}}\ket{0} + \sqrt{1-\frac{|H^*_{jl}|}{K}}\ket{1})
 %         \]
@@
 %         \[
-%         T := \sum_{y \in X}\sum_{b \in {\{0,1\}}}(\ket{j}\bra{j}\otimes\ket{b}\bra{b})\otimes\ket{\phi_{yb}}
+%         \ket{\phi_{j1}} := \ket{0}\ket{1} 
 %         \]
@@
 %         \[
-%         = \sum_{y \in X}\sum_{b \in {\{0,1\}}}\ket{y}\ket{b}\ket{\phi_{yb}}\bra{y}\bra{b}
+%         T := \sum_{j=0}^{N-1}\sum_{b \in {\{0,1\}}}(\ket{j}\bra{j}\otimes\ket{b}\bra{b})\otimes\ket{\phi_{jb}}
 %         \]
@@
 %         \[
-%             \ket{\phi_{y0}} = \frac{1}{\sqrt{|Q|}}\sum_{q \in Q}\ket{q*y}\ket{0}
+%         W = iS(2TT^* - 1)
+%         \]
+
+%         \[
+%         S\ket{j_1,b_1}\ket{j_2,b_2} = \ket{j_2,b_2}\ket{j_1,b_1}
 %         \]
@@
     \begin{textblock*}{12cm}(0.5cm,1.5cm)
+
+        \textbf{Goal:} Efficiently simulate $W = e^{-iAt}$ for $t = \text{poly}(\log |G|)$.
+
+        \medskip
+        \textbf{Approach:} Use discrete-time quantum walk framework:
+        \[
+        W = iS(2TT^* - 1)
+        \]
+
+        \begin{itemize}
+        \item Isometry $T$ and its adjoint $T^*$ are efficiently implemented via simple unitaries $U_0$, $U_1$.
+        \item These unitaries prepare/refactor states $|\varphi_{yb}\rangle$ using a small symmetric set $Q \subset G$.
+        \item Efficient due to:
+            \begin{itemize}
+            \item Bounded degree Cayley graph.
+            \item Polynomial-size $Q$ allows brute-force mapping.
+            \end{itemize}
+        \item Full walk operator $W$ simulated via reflection trick using $T$, $T^*$, and ancilla control.
+        \end{itemize}
+
+        \textbf{Conclusion:} Group-action quantum walks can be simulated efficiently despite lack of QFT-like structure.
 

### 2025-04-02 presentation.tex
presentation updated

@@
         \medskip
-        \textbf{Approach:} Use discrete-time quantum walk framework:
+        \textbf{Approach:} Use discrete-time quantum walk framework proposed by Andrew. M. Childs in 2009:
         \[
@@
     \begin{textblock*}{12cm}(0.5cm,1.5cm)
+
+        Proposed by Zhandry in 2023:
 
@@
             \item  In the original scheme, using the quantum Fourier transform, we could directly obtain $h$ from the money state $\ket{\mathbb{Z}_N^{(h)} * x}$ and compare it to the given $h$.
-However, this approach does not work when we use the Hartley transform.
+However, this approach does not work exactly the same when we use the Hartley transform.
             \vspace{1cm}
-            \item  To address this, we design an algorithm for computing $h$ that utilizes quantum walks.
+            \item  To extract $h$ directly, we design an algorithm for computing $h$ that utilizes quantum walks.
 
@@
 
+        \footnotesize
+        \begin{thebibliography}{99}
+
+        \bibitem{aaronson2012}
+        S.~Aaronson and P.~Christiano,
+        \newblock \emph{Quantum Money from Hidden Subspaces},
+        \newblock In Theory of Cryptography Conference, pp. 3--25, Springer, 2012. \\
+        \url{https://arxiv.org/abs/1203.4740}
+
+        \bibitem{zhandry2017}
+        M.~Zhandry,
+        \newblock \emph{Quantum Lightning Never Strikes the Same State Twice},
+        \newblock In EUROCRYPT 2019, pp. 408--438. \\
+        \url{https://arxiv.org/abs/1701.03137}
+
+        \bibitem{childs2009}
+        A.~M. Childs,
+        \newblock \emph{On the Relationship Between Continuous- and Discrete-Time Quantum Walks},
+        \newblock \url{https://arxiv.org/abs/0810.0312}
+
+        \bibitem{childs2022}
+        A.~M. Childs,
+        \newblock \emph{Lecture Notes on Quantum Algorithms}, University of Maryland, 2022. \\
+        \url{https://arxiv.org/abs/quant-ph/0012090v2}
+
+        \bibitem{arrazola2014}
+        J.~M. Arrazola and N.~Lütkenhaus,
+        \newblock \emph{Quantum Walks and Graph Isomorphism},
+        \newblock \url{https://arxiv.org/abs/1401.4998}
+
+        \end{thebibliography}
+
     \end{textblock*}

### 2025-04-03 main.tex
presentation updated
main.tex updated

@@
 
-\subsubsection*{4. Toffoli Gate (CCNOT Gate)}
-\textbf{Operation:} A three-qubit gate that flips the state of the target qubit if both control qubits are in the state $|1\rangle$. \\
-\textbf{Matrix Representation:}
-\[
-CCNOT =
-\begin{bmatrix}
-1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 \\
-0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 \\
-0 & 0 & 0 & 1 & 0 & 0 & 0 & 0 \\
-0 & 0 & 0 & 0 & 1 & 0 & 0 & 0 \\
-0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 \\
-0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 \\
-0 & 0 & 0 & 0 & 0 & 0 & 1 & 0
-\end{bmatrix}
-\]
-
 \subsection*{Universal Gates}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section*{Groups and Characters}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Abelian Groups}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Characters of Abelian Groups}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section*{Number of Characters in a Finite Abelian Group}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section*{Character Group}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Quantum Fourier Transform}
@@
 \[
-F_G = \frac{1}{\sqrt{|G|}} \sum_{x \in G} \sum_{y \in \hat{G}} \chi_y(x) | y \rangle \langle x |
+F_G = \frac{1}{\sqrt{|G|}} \sum_{x \in G} \sum_{y \in \hat{G}} \chi(y,x) | y \rangle \langle x |
 \]
@@
     \item \( \hat{G} \) is a complete set of characters of \( G \).
-    \item \( \chi_y(x) \) denotes the \( y \)th character of \( G \), evaluated at \( x \).
+    \item \( \chi(y,x) \) denotes the \( y \)th character of \( G \), evaluated at \( x \).
     \item \( |x\rangle \) and \( |y\rangle \) are quantum states corresponding to elements of \( G \) and its dual group \( \hat{G} \).
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{QFT Over \( \mathbb{Z}_{2^n} \)}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection*{Cayley graphs}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section*{Definition of Cayley Graphs}
@@
 A \textit{Cayley graph} is a graph that encodes the structure of a group with respect to a chosen generating set.
-Formally, let \( G \) be a group and \( S \) be a subset of \( G \) that serves as a generating set, meaning every element of \( G \) can be expressed as a finite product of elements from \( S \).
-The Cayley graph \( \Gamma(G, S) \) is defined as follows.
+Formally, let \( G \) be a group and \( Q \) be a subset of \( G \) that serves as a generating set, meaning every element of \( G \) can be expressed as a finite product of elements from \( Q \).
+The Cayley graph \( \Gamma(G, Q) \) is defined as follows.
 The vertex set of the graph consists of the elements of \( G \), where each vertex corresponds to a unique group element.
-The edge set is constructed by drawing a directed edge from vertex \( g \) to vertex \( gs \) for each \( g \in G \) and \( s \in S \).
-If the generating set \( S \) is symmetric, meaning that whenever \( s \in S \), its inverse \( s^{-1} \) is also in \( S \), then the Cayley graph is undirected; otherwise, it is a directed graph.
-For example, For the cyclic group \( G = \mathbb{Z}_n = \{0,1,2,\dots, n-1\} \) with the generating set \( S = \{\pm 1\} \), the Cayley graph forms a cycle graph.
+The edge set is constructed by drawing a directed edge from vertex \( g \) to vertex \( gq \) for each \( g \in G \) and \( q \in Q \).
+If the generating set \( Q \) is symmetric, meaning that whenever \( q \in Q \), its inverse \( q^{-1} \) is also in \( Q \), then the Cayley graph is undirected; otherwise, it is a directed graph.
+For example, For the cyclic group \( G = \mathbb{Z}_n = \{0,1,2,\dots, n-1\} \) with the generating set \( Q = \{\pm 1\} \), the Cayley graph forms a cycle graph.
 In this graph, each vertex \( j \) is connected to \( j+1 \mod n \) and \( j-1 \mod n \), creating a cyclic structure.\\
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section*{Discrete-Time Quantum Walk on Cayley Graphs}
@@
 \[
-|\psi\rangle = \sum_{g \in G} \sum_{s \in S} \alpha_{g,s} |g\rangle \otimes |s\rangle,
-\]
-where \( |g\rangle \) is the vertex state and \( |s\rangle \) represents the coin state.
+|\psi\rangle = \sum_{g \in G} \sum_{q \in Q} \alpha_{g,q} |g\rangle \otimes |q\rangle,
+\]
+where \( |g\rangle \) is the vertex state and \( |q\rangle \) represents the coin state.
 
@@
 
-We now briefly outline the quantum money construction from \cite{zhandry2024quantum}, which is based on abelian group actions.
+We now briefly outline the quantum money construction from \cite{zhandry2024quantum}, which is based on abelian group actions. We will the $\comph$ algorithm:
+\paragraph{The $\comph$ Algorithm.}
+Given access to the state $\ket{G^{(h)} * x}$, one can efficiently recover the value of $h$ via a quantum algorithm. In particular, there exists a unitary transformation that maps
+\[
+\ket{G^{(h)} * x} \ket{0} \mapsto \ket{G^{(h)} * x} \ket{h},
+\]
+leveraging the technique of \textit{phase kickback}. The process proceeds as follows:
+
+Begin with the state $\ket{G^{(h)} * x} \ket{0}$ and apply the quantum Fourier transform (QFT) to the second register. Then apply the unitary operator
+\[
+\sum_{k \in G} U_k \otimes \ket{k}\bra{k}
+\]
+to both registers. This operation encodes the character information into the phase, resulting in the state
+\[
+\frac{1}{\sqrt{\abs{G}}} \sum_{k \in G} \ket{G^{(h)} * x} \chi(-k, h) \ket{k}.
+\]
+Finally, applying the inverse QFT to the second register disentangles the phase and reveals $h$, yielding the final state $\ket{G^{(h)} * x} \ket{h}$.
+
+\vspace{0.5cm}
 Let $\{(G_\lambda, X_\lambda, *)\}_{\lambda \in J}$, where $J \subset \N$, be a collection of cryptographic group actions for abelian groups $G_\lambda$, and let $x_\lambda \in X_\lambda$ be a fixed element.
@@
 Given a state of the form $\ket{\Z_N^{(h)} * x}_H$, we demonstrate how the value of $h$ can be extracted using continuous-time quantum walks.
-For any $u \in \Z_N$, consider the Cayley graph $\Gamma = (\Z_N, E)$ generated by $Q = {-u, u}$, as introduced in Section \ref{sec:ga-qwalk}.
+For any $u \in \Z_N$, consider the Cayley graph $\Gamma = (\Z_N, E)$ generated by $Q = {\{-u, u}\}$.
 Let $A$ denote the adjacency matrix of $\Gamma$.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\newpage
 \bibliographystyle{plain}

### 2025-04-07 draft.tex
draft.tex added

\documentclass[12pt]{report}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{cite}
\usepackage{physics}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{tikz}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{setspace}

\usepackage[a4paper, left=1.5cm, right=1.5cm, top=2cm, bottom=2cm]{geometry}

% Formatting
\setlength{\parskip}{0.5em}
\setlength{\parindent}{0pt}
\onehalfspacing

\title{Quantum Walks and Application to Quantum Money}
\author{Ali Mousavi}
\date{April 2025}

\begin{document}

\maketitle
\tableofcontents

\newpage
\textbf{Abstract}

This thesis explores the foundations of quantum computation, focusing on quantum walks and their application to quantum money. Quantum walks, particularly continuous-time quantum walks based on group actions, serve as a powerful computational tool with applications in search algorithms and cryptographic protocols. We examine their mathematical structure and their advantages over classical random walks, emphasizing their efficiency in state evolution and probability distribution spreading. As a part of this work, we examine efficient implementations of transforms such as the Quantum Fourier Transform (QFT) and the Quantum Hartley Transform (QHT), analyzing their role in encoding quantum states for secure cryptographic applications. In particular, we discuss a novel instantiation of a quantum money scheme based on QHT, leveraging its unique properties for improved security and efficiency.
To ensure the robustness of this quantum money scheme, we develop a verification mechanism utilizing quantum walks. Unlike previous approaches, which rely on standard quantum state measurements, our method employs continuous-time quantum walks to authenticate quantum money, preventing counterfeiting while maintaining computational feasibility. Additionally, we present a detailed discussion on the efficient implementation of this scheme, including optimized circuit designs and error mitigation strategies.

\chapter{Introduction}
Quantum money, first introduced in a seminal paper by Wiesner [29], is a form of currency represented by quantum states. Unlike classical money, an ideal quantum bill cannot be counterfeited due to the no-cloning theorem of quantum mechanics, which prohibits making an identical copy of an unknown quantum state. Wiesner’s original scheme (now termed a \emph{private-key quantum money} scheme) had significant practical drawbacks: it required the issuing bank’s secret key to verify each banknote, meaning the bank had to be involved in every transaction. This reliance on the bank for verification severely limits the usability of private-key quantum money schemes.

In 2009, Aaronson [1] proposed the first \emph{public-key quantum money} scheme, in which anyone can verify a quantum banknote while only the bank can mint (issue) new valid banknotes. Public-key quantum money removes the transactional bottleneck of involving the bank every time. Aaronson’s specific scheme was later broken by Lutomirski et al.~[24]. In the years since, several alternative public-key quantum money constructions have been explored [2, 17, 30, 19, 20, 23, 31]. However, each of these proposals has either been broken by further cryptanalysis [14, 26, 7, 23] or relies on unconventional cryptographic assumptions, making their security or practicality questionable.

\medskip\noindent\textbf{Quantum Money from Group Actions and the Fourier Transform.} 
A promising candidate for secure public-key quantum money based on more standard assumptions was recently proposed by Zhandry [31]. In Zhandry’s scheme, the core idea is to use an abelian group action as the foundation for the quantum state. Each money state (quantum banknote) is prepared as a \emph{group-action Fourier state}, and the corresponding serial number is an element of the underlying group (we will elaborate on these terms in later chapters). The verification algorithm in this scheme uses a group-action phase kickback routine to extract the serial number from the quantum banknote and check its validity. Doliskani [15] later proved that Zhandry’s scheme is secure in the generic group action model, providing evidence for its security under well-defined assumptions.

\medskip\noindent\textbf{This Work – Motivation and Contributions.} 
In this thesis, we adapt Zhandry’s group-action quantum money scheme by replacing its use of the Quantum Fourier Transform with the \emph{Quantum Hartley Transform} (QHT) over finite abelian groups. The motivation behind this substitution is multifold. First, using the Hartley transform causes the banknotes to have \emph{real} amplitudes instead of complex amplitudes. We believe this shift from complex to real quantum states may offer both computational and theoretical advantages. For example, certain mathematical identities hold for any two real orthonormal bases that do not generally hold for complex bases; such differences can affect the properties of quantum states and were a barrier in prior analyses (indeed, an attempted “quantum lightning” construction in [31] failed due to properties of complex phases that do not arise with real amplitudes). Beyond this specific context, our work is a first step toward employing real-valued quantum transforms in quantum cryptography and quantum algorithms. To the best of our knowledge, this is the first significant quantum cryptographic construction that makes essential use of the quantum Hartley transform. We hope that exploring real-amplitude quantum states will inspire further research into new quantum algorithms and optimizations for real-valued transforms.

We now summarize our main contributions:
\begin{itemize}
    \item We propose a new \textbf{public-key quantum money scheme} based on abelian group actions and the quantum Hartley transform. This scheme is an adaptation of Zhandry’s group-action money scheme, modified to output real-amplitude quantum states. 
    \item When using the Hartley transform instead of the Fourier transform, the original verification method from Zhandry’s scheme is no longer straightforward and requires the use of twists to function correctly. Instead, we offer a more direct verification approach based on quantum walks.
    \item We show that the serial number associated with a money state (which is a hidden group element) can be efficiently computed from the quantum state. In particular, we develop a \textbf{continuous-time quantum walk algorithm} to extract the serial number of a given banknote state. This algorithm leverages the structure of the group action and the spectral properties of an associated Cayley graph. Our method demonstrates that one can recover the hidden group element (serial) with high success probability, which not only underpins the new verification technique but is also of independent interest.
    \item In the course of our construction, we introduce a new algorithm for efficiently implementing the \textbf{quantum Hartley transform} and related real transforms. We present a recursive technique that exploits the structure of the Hartley transform, yielding a lower gate complexity than prior approaches in the literature.
\end{itemize}

In summary, our work combines ideas from quantum cryptography (public-key quantum money), quantum walks, and quantum signal processing (Hartley and related transforms) to create a novel and potentially practical quantum money scheme.

\medskip\noindent\textbf{Thesis Organization.} 
The remainder of this thesis is organized as follows. In **Chapter 2**, we provide background on the basics of quantum computation and the theory of group actions, including the concept of cryptographic group actions which underlie our money scheme. **Chapter 3** covers quantum walks, both continuous-time and discrete-time, outlining their differences and importance in quantum algorithms. In **Chapter 4**, we apply the quantum walk framework to group actions: we describe how a continuous-time quantum walk on a group action can be simulated efficiently, a crucial step for our serial number extraction algorithm. **Chapter 5** details the quantum money scheme itself and the role of the Hartley transform in its construction. We explain how the scheme is formulated and discuss the advantages and challenges introduced by using the Hartley transform. Finally, **Chapter 6** presents the verification algorithm for the Hartley-based quantum money. This chapter shows how we use quantum walks (as developed in Chapter 4) to reliably verify banknotes and compute their serial numbers, thereby addressing the verification issues that arose from the use of real amplitudes.
\vspace{1em}

\chapter{Background of Quantum Computation and Group Actions}

\section{Quantum Computation Basics}

Quantum computation operates on information stored in quantum states. The fundamental unit of quantum information is the \emph{qubit}, which, unlike a classical bit, can exist in a superposition of basis states. A qubit is described by a state $|\psi\rangle = \alpha |0\rangle + \beta |1\rangle$ (in Dirac notation), where $\alpha,\beta \in \mathbb{C}$ and $|\alpha|^2 + |\beta|^2 = 1$. A system of $n$ qubits resides in a $2^n$-dimensional Hilbert space and its state can be a superposition of all $2^n$ basis states $|b_1b_2\cdots b_n\rangle$.

Computation is carried out by unitary transformations on these states. A quantum algorithm is typically a sequence of quantum gates (unitary operators) applied to an initial state (usually a simple basis state like $|00\cdots0\rangle$), followed by a measurement of some qubits to obtain a classical result. A crucial aspect of quantum computation is that certain transformations—such as the Fourier transform over an $N$-element group—can be implemented very efficiently on a quantum computer (in $\operatorname{poly}(\log N)$ time), whereas their classical counterparts might require $\operatorname{poly}(N)$ time.

\subsection{The Quantum Fourier Transform}

One example important to this work is the \textbf{quantum Fourier transform} (QFT). For an abelian group $G$ of order $N$, the QFT is the unitary map
\[
|g\rangle \mapsto \frac{1}{\sqrt{N}}\sum_{h \in G} \chi_h(g)\, |h\rangle,
\]
where $\{\chi_h\}$ are the characters (complex exponential homomorphisms) of $G$. When $G = \mathbb{Z}_N$ (the integers mod $N$), the QFT takes $|j\rangle$ to $\frac{1}{\sqrt{N}}\sum_{k=0}^{N-1} e^{2\pi i j k / N} |k\rangle$.

Let $G \cong \mathbb{Z}_{N_1} \oplus \cdots \oplus \mathbb{Z}_{N_k}$ be a decomposition of $G$. The character $\chi(a, x)$ is then given by
\[
\chi(a, x) = \omega_{N_1}^{a_1x_1} \cdots \omega_{N_k}^{a_kx_k}, \quad \text{where } \omega_M = \exp(2\pi i/ M).
\]

The Fourier transform of a function $f: G \to \mathbb{C}$ is given by
\[
\hat{f}(a) = \frac{1}{\sqrt{|G|}} \sum_{x \in G} \chi(a, x) f(x),
\]
and the QFT of a quantum state $\sum_{g \in G} f(g) \ket{g}$ is $\sum_{x \in G} \hat{f}(x) \ket{x}$.

\paragraph{Fourier Basis and Group Actions.} For a regular group action $(G, X, *)$, define
\[
\ket{S^{(h)} * y} = \frac{1}{\sqrt{|S|}} \sum_{g \in S} \chi(g, h) \ket{g * y}.
\]
For fixed $x \in X$, we obtain two orthonormal bases of $\mathbb{C}^X$: the standard basis $\{ \ket{x} : x \in X \}$, and the Fourier basis
\[
\ket{G^{(h)} * x} = \frac{1}{\sqrt{|G|}} \sum_{g \in G} \chi(g, h) \ket{g * x}.
\]
These states are eigenstates of the action unitary $U_k: \ket{y} \mapsto \ket{k * y}$:
\[
U_k \ket{G^{(h)} * x} = \chi(-k, h) \ket{G^{(h)} * x}.
\]

\paragraph{The cmpIndex Algorithm.}
Given a state $\ket{G^{(h)} * x}$, one can recover $h$ using phase kickback. Starting from $\ket{G^{(h)} * x} \ket{0}$, apply:
\begin{itemize}
    \item QFT to second register,
    \item Controlled unitary $\sum_{k \in G} U_k \otimes \ket{k}\bra{k}$,
    \item Inverse QFT to second register.
\end{itemize}
This yields $\ket{G^{(h)} * x} \ket{h}$, extracting $h$ efficiently.

\subsection{The Quantum Hartley Transform}

Another concept we use is the \textbf{quantum Hartley transform} (QHT), which replaces complex exponentials with real sinusoidal kernels.

\paragraph{Definition.}
For $G = \mathbb{Z}_N$, define
\[
\operatorname{QHT}_N: \ket{a} \mapsto \frac{1}{\sqrt{N}} \sum_{y = 0}^{N - 1} cas\left(\frac{2\pi a y}{N}\right) \ket{y}, \quad \text{where } cas(x) = \cos(x) + \sin(x).
\]

For general abelian $G = \mathbb{Z}_{N_1} \oplus \cdots \oplus \mathbb{Z}_{N_k}$, the Hartley transform of $f : G \to \mathbb{R}$ is
\begin{equation}
    \operatorname{QHT}_G(f)({a}) = \frac{1}{\sqrt{|G|}} \sum_{{y} \in G} cas(2\pi \langle {a}, \alpha({y}) \rangle) f({y}),
\end{equation}
where $\alpha({y}) = y_1 / N_1 + \cdots + y_k / N_k$.

\paragraph{Unitary Equivalence.}
Using the identity
\[
cas(2\pi \langle {a}, \alpha({y}) \rangle) = \frac{1 - i}{2}\chi({a}, {y}) + \frac{1 + i}{2}\chi(-{a}, {y}),
\]
we obtain:
\begin{equation}
\operatorname{QHT}_G = \frac{1 - i}{2} \operatorname{QFT}_G + \frac{1 + i}{2} \operatorname{QFT}_G^*,
\end{equation}
showing that $\operatorname{QHT}_G^2 = {1}$ and hence the QHT is unitary.

\paragraph{Quantum Formulation.}
The quantum Hartley transform over $G$ maps:
\[
\sum_{{x} \in G} f({x}) \ket{{x}} \mapsto \sum_{{a} \in G} \operatorname{QHT}_G(f)({a}) \ket{{a}}.
\]
Because the cas function is real-valued, the resulting amplitudes remain real—a fact that plays a crucial role in real-amplitude quantum protocols.

% \section{Group Actions in Cryptography}

% A \textbf{group action} of a group $G$ on a set $X$ is a function $*\colon G \times X \to X$ satisfying:
% \begin{enumerate}
%     \item Identity: $e * x = x$ for all $x \in X$,
%     \item Compatibility: $g * (h * x) = (gh) * x$ for all $g,h \in G$, $x \in X$.
% \end{enumerate}
% We denote the result of $g$ acting on $x$ by $g * x$ or simply $gx$ when unambiguous.

% \subsection{Regular Group Actions}

% The orbit of $x \in X$ under $G$ is $G * x = \{g * x : g \in G\}$. The action is:
% \begin{itemize}
%     \item \emph{Transitive} if $G * x = X$,
%     \item \emph{Free} if $g * x = x$ implies $g = e$,
%     \item \emph{Regular} if both transitive and free.
% \end{itemize}
% In regular actions, $|X| = |G|$, and we can treat $X$ as a “hidden” version of $G$.

% \subsection{Group Actions in Cryptography}

% A \textbf{cryptographic group action} is one that is easy to compute in the forward direction but hard to invert. This gives rise to one-way functions based on group actions.

% \paragraph{Example 1: Discrete Log.}  
% $G = \mathbb{Z}_p^*$ acting on itself via $g * x = x^g \mod p$. Forward computation is efficient; inversion (discrete logarithm) is hard.

% \paragraph{Example 2: Isogeny-Based.}  
% $G$ is an ideal class group acting on supersingular elliptic curves. Given a base curve $x_0$ and an element $g \in G$, we compute $g * x_0$ efficiently, but recovering $g$ from $(x_0, g*x_0)$ is assumed hard.

% \subsection{Applications to Quantum Money}

% Cryptographic group actions enable public-key quantum money schemes. A private “serial number” $g \in G$ generates a quantum state based on $g * x_0$, which cannot be copied due to the no-cloning theorem and cannot be reverse-engineered due to the hardness of the action.

% \subsection{Security Assumptions}

% We assume abelian group actions $(G, X)$ satisfying:
% \begin{itemize}
%     \item Efficient action computation,
%     \item Regularity: transitive and free,
%     \item Hardness of inversion without the secret.
% \end{itemize}

% In particular, isogeny-based group actions are widely believed to be secure. We also refer to the \textbf{generic group model}, where group elements are treated as black-boxes with no special structure. Prior proofs (e.g., Doliskani's analysis of Zhandry’s scheme) in this model provide confidence in the cryptographic soundness of such constructions.

% \chapter{Background of Quantum Computation and Group Actions}

% \section{Quantum Computation Basics}
% Quantum computation operates on information stored in quantum states. The fundamental unit of quantum information is the \emph{qubit}, which, unlike a classical bit, can exist in a superposition of basis states. A qubit is described by a state $|\psi\rangle = \alpha |0\rangle + \beta |1\rangle$ (in Dirac notation), where $\alpha,\beta \in \mathbb{C}$ and $|\alpha|^2 + |\beta|^2 = 1$. A system of $n$ qubits resides in a $2^n$-dimensional Hilbert space and its state can be a superposition of all $2^n$ basis basis states $|b_1b_2\cdots b_n\rangle$.

% Computation is carried out by unitary transformations on these states. A quantum algorithm is typically a sequence of quantum gates (unitary operators) applied to an initial state (usually a simple basis state like $|00\cdots0\rangle$), followed by a measurement of some qubits to obtain a classical result. A crucial aspect of quantum computation is that certain transformations—such as the Fourier transform over an $N$-element group—can be implemented very efficiently on a quantum computer (in $\operatorname{poly}(\log N)$ time), whereas their classical counterparts might require $\operatorname{poly}(N)$ time.

% One example important to this work is the \textbf{quantum Fourier transform} (QFT). For an abelian group $G$ of order $N$, the QFT is the unitary map $|g\rangle \mapsto \frac{1}{\sqrt{N}}\sum_{h \in G} \chi_h(g)\, |h\rangle$, where $\{\chi_h\}$ are the characters (complex exponential homomorphisms) of $G$. In more familiar terms, when $G = \mathbb{Z}_N$ (the integers mod $N$), the QFT takes $|j\rangle$ to $\frac{1}{\sqrt{N}}\sum_{k=0}^{N-1} e^{2\pi i j k / N} |k\rangle$. The QFT is a key component in many quantum algorithms, including Shor’s factoring algorithm and certain quantum money schemes (e.g., Zhandry’s) that rely on hiding information in phase relationships. The QFT can be implemented using $O((\log N)^2)$ basic gates for many groups [13], making it an efficient operation.

% Another concept we will use is the \textbf{quantum Hartley transform} (QHT). The Hartley transform is an alternative to the Fourier transform that produces only real values (in the classical case) by using sinusoidal basis functions (sums of sine and cosine) instead of complex exponentials. The \emph{quantum} Hartley transform is the unitary transform corresponding to the classical Hartley transform. For example, the Hartley transform on $\mathbb{Z}_N$ maps a basis state $|j\rangle$ to $\frac{1}{\sqrt{N}}\sum_{k=0}^{N-1} \mathrm{cas}\!\Big(\frac{2\pi j k}{N}\Big)\, |k\rangle$, where $\mathrm{cas}(x) = \cos x + \sin x$ is the Hartley kernel. Because $\cos x + \sin x$ is real for all $x$, the resulting amplitudes are real numbers. We will discuss the Hartley transform in more detail in Chapter 5, including how to implement it efficiently on a quantum computer.

% A final fundamental principle to note is the \textbf{no-cloning theorem}, which underpins the security of quantum money. This theorem states that there is no physical operation that can make a copy of an arbitrary unknown quantum state. This contrasts sharply with classical information, which can be copied freely. The no-cloning theorem means that an adversary cannot duplicate a quantum banknote without fundamentally disturbing it – any attempt to “clone” the state will fail unless the adversary already has complete classical information describing that state.

% Throughout this thesis, when we refer to an algorithm as \emph{efficient} or \emph{feasible}, we typically mean it can be performed by a quantum polynomial-time (QPT) algorithm. This is analogous to classical polynomial time, but on a quantum computer. All of the algorithms we propose (minting, verification, quantum walk simulation, etc.) are intended to be efficient in this sense.

\section{Group Actions in Cryptography}
At the heart of our quantum money scheme is the notion of a group action. A \textbf{group action} of a group $G$ on a set $X$ is a function $*\colon G \times X \to X$ that satisfies two properties: (1) the identity element $e \in G$ acts trivially on every $x \in X$ ($e * x = x$), and (2) the action is compatible with the group operation, meaning $g*(h* x) = (gh)*x$ for all $g,h \in G$ and $x \in X$. We will often denote the result of $g$ acting on $x$ by $g*x$ or simply $g x$ when the action is clear from context.

The orbit of an element $x \in X$ under the action is the set $G * x = \{g*x : g \in G\} \subseteq X$. If there is exactly one orbit (i.e., $G * x = X$ for some $x$), the action is called \emph{transitive}. If, in addition, no non-identity group element fixes any $x$ (i.e., $g * x = x$ implies $g = e$), then the action is \emph{free}. A group action that is both transitive and free is sometimes called a \textbf{regular action}. In a regular action, for any two elements $y, z \in X$, there is a unique group element $g$ such that $g * y = z$. In other words, $G$ acts like a permutation group that moves elements of $X$ around, and knowing the starting and ending point uniquely determines the “move” $g$. In this case $|X| = |G|$, and we can think of $X$ as essentially a copy of $G$ with the group structure “hidden” by the action.

Group actions are ubiquitous in modern cryptography. A \textbf{cryptographic group action} is one where the action is easy to compute in the forward direction, but inverting the action (recovering $g$ from $x$ and $g*x$) is computationally hard. This essentially functions as a one-way function: given $x$ and $g$, it is easy to compute $y = g*x$, but given $x$ and $y$ it is infeasible to find $g$ (except with negligible probability). One classical example is the discrete logarithm problem: consider the cyclic group $G = \mathbb{Z}_p^*$ (the multiplicative group of a prime field) acting on itself by exponentiation. Let $X = G$ and define $g * x = x^g \pmod p$ (treating group elements as integers). Here $g$ is an exponent. This is a group action (in fact, just the group’s own operation written differently), and computing $x^g \bmod p$ is efficient. However, given $x$ and $y = x^g$, finding $g$ requires solving a discrete log problem, which is believed to be hard for suitable choices of $p$. Thus, exponentiation can be viewed as a one-way group action.

Another prominent example comes from elliptic-curve cryptography: the action of an ideal class group on a set of elliptic curves. In schemes like CSIDH (Commutative Supersingular Isogeny Diffie–Hellman), an abelian group of ideal classes $G$ acts on the set $X$ of supersingular elliptic curves by isogeny (an isogeny is a structure-preserving map between curves). Starting from a curve $x_0$, one can efficiently compute $g * x_0$ (which is another elliptic curve) for any group element $g$, but given two curves $x_0$ and $x = g * x_0$, it is believed to be computationally hard to recover $g$. This hard problem is the foundation of isogeny-based cryptography. We refer to such $G$ and $X$ as a \emph{cryptographic group action} pair.

Cryptographic group actions provide a natural platform for public-key quantum money schemes. In such schemes, the secret “serial number” of a quantum banknote can be an element $g \in G$, and the quantum state of the banknote can be some function of $g*x_0$ for a public base point $x_0 \in X$. The hardness of inverting the action ($x_0$ and $x = g*x_0$ do not easily reveal $g$) contributes to the security against counterfeiting, while the structure of the group action can be used to efficiently verify authenticity (as we will see with the Fourier or Hartley transform techniques).

We will assume throughout that we have a family of abelian group actions $(G,X)$ that are cryptographically suitable: $|G|$ is large (growing with the security parameter), the action is efficiently computable, transitive and free (so $|X|=|G|$), and inverting the action is infeasible without the secret key. Such families are conjectured to exist (for example, the isogeny-based actions, and others discussed in cryptographic literature).

Finally, we note that working in the \textbf{generic group model} (or generic group \emph{action} model) is a common theoretical approach to analyze security. In a generic model, the group elements are treated as black-box labels without exploiting any special algebraic structure beyond group axioms. Doliskani’s proof of security for Zhandry’s scheme [15] was in such a generic model for group actions, lending confidence that no “generic” attack can break the scheme. In this thesis, we focus on designing the scheme and algorithms at a high level and assume the underlying group action is secure; a detailed security proof is beyond our scope, though we rely on prior results for reassurance.

\chapter{Quantum Walks -- Continuous and Discrete}

\chapter{Simulating Group Action Quantum Walks}

\chapter{Quantum Money and Hartley Transform}

\chapter{Verification Algorithm Using Quantum Walks}

\bibliographystyle{plain}
\begin{thebibliography}{99}
% Sample Bib entries. Replace with real ones.
\bibitem{Aaronson2009} S. Aaronson, ``Quantum Copy-Protection and Quantum Money,'' In Proc. of CCC, 2009.
\bibitem{Zhandry2022} M. Zhandry, ``Quantum Money from Modular Forms,'' In Proc. of CRYPTO, 2022.
\bibitem{Childs2003} A. M. Childs, ``Quantum Information Processing in Continuous Time,'' PhD Thesis, MIT, 2004.
% Add all other references as needed
\end{thebibliography}

\end{document}

### 2025-04-07 main.tex
draft.tex added

--- 2025-04-01 main.tex
@@
 \newpage
+\section*{Abstract}
+
+This thesis explores the foundations of quantum computation, focusing on quantum walks and their application to quantum money.
+Quantum walks, particularly continuous-time quantum walks based on group actions, serve as a powerful computational tool with applications in search algorithms and cryptographic protocols.
+We examine their mathematical structure and their advantages over classical random walks, emphasizing their efficiency in state evolution and probability distribution spreading.
+As a part of this work, we examine efficient implementations of transforms such as the Quantum Fourier Transform (QFT) and the Quantum Hartley Transform (QHT), analyzing their role in encoding quantum states for secure cryptographic applications.
+In particular, we discuss a novel instantiation of a quantum money scheme based on QHT, leveraging its unique properties for improved security and efficiency.
+To ensure the robustness of this quantum money scheme, we develop a verification mechanism utilizing quantum walks.
+Unlike previous approaches, which rely on standard quantum state measurements, our method employs continuous-time quantum walks to authenticate quantum money, preventing counterfeiting while maintaining computational feasibility.
+Additionally, we present a detailed discussion on the efficient implementation of this scheme, including optimized circuit designs and error mitigation strategies.
+
+\newpage
 \section{Introduction to Quantum Computation}
@@
 
-\section*{Introduction}
-
-Quantum computing is a revolutionary field that combines quantum mechanics and information theory to redefine computation and information processing.
+\chapter{Introduction}
+Quantum money, first introduced in a seminal paper by Wiesner [29], is a form of currency represented by quantum states.
+Unlike classical money, an ideal quantum bill cannot be counterfeited due to the no-cloning theorem of quantum mechanics, which prohibits making an identical copy of an unknown quantum state.
+Wiesner’s original scheme (now termed a \emph{private-key quantum money} scheme) had significant practical drawbacks: it required the issuing bank’s secret key to verify each banknote, meaning the bank had to be involved in every transaction.
+This reliance on the bank for verification severely limits the usability of private-key quantum money schemes.
+
+In 2009, Aaronson [1] proposed the first \emph{public-key quantum money} scheme, in which anyone can verify a quantum banknote while only the bank can mint (issue) new valid banknotes.
+Public-key quantum money removes the transactional bottleneck of involving the bank every time.
+Aaronson’s specific scheme was later broken by Lutomirski et al.~[24].
+In the years since, several alternative public-key quantum money constructions have been explored [2, 17, 30, 19, 20, 23, 31].
+However, each of these proposals has either been broken by further cryptanalysis [14, 26, 7, 23] or relies on unconventional cryptographic assumptions, making their security or practicality questionable.
+
+\medskip\noindent\textbf{Quantum Money from Group Actions and the Fourier Transform.} 
+A promising candidate for secure public-key quantum money based on more standard assumptions was recently proposed by Zhandry [31].
+In Zhandry’s scheme, the core idea is to use an abelian group action as the foundation for the quantum state.
+Each money state (quantum banknote) is prepared as a \emph{group-action Fourier state}, and the corresponding serial number is an element of the underlying group (we will elaborate on these terms in later chapters).
+The verification algorithm in this scheme uses a group-action phase kickback routine to extract the serial number from the quantum banknote and check its validity.
+Doliskani [15] later proved that Zhandry’s scheme is secure in the generic group action model, providing evidence for its security under well-defined assumptions.
+
+\medskip\noindent\textbf{This Work – Motivation and Contributions.} 
+In this thesis, we adapt Zhandry’s group-action quantum money scheme by replacing its use of the Quantum Fourier Transform with the \emph{Quantum Hartley Transform} (QHT) over finite abelian groups.
+The motivation behind this substitution is multifold.
+First, using the Hartley transform causes the banknotes to have \emph{real} amplitudes instead of complex amplitudes.
+We believe this shift from complex to real quantum states may offer both computational and theoretical advantages.
+For example, certain mathematical identities hold for any two real orthonormal bases that do not generally hold for complex bases; such differences can affect the properties of quantum states and were a barrier in prior analyses (indeed, an attempted “quantum lightning” construction in [31] failed due to properties of complex phases that do not arise with real amplitudes).
+Beyond this specific context, our work is a first step toward employing real-valued quantum transforms in quantum cryptography and quantum algorithms.
+To the best of our knowledge, this is the first significant quantum cryptographic construction that makes essential use of the quantum Hartley transform.
+We hope that exploring real-amplitude quantum states will inspire further research into new quantum algorithms and optimizations for real-valued transforms.
+
+We now summarize our main contributions:
+\begin{itemize}
+    \item We propose a new \textbf{public-key quantum money scheme} based on abelian group actions and the quantum Hartley transform.
+This scheme is an adaptation of Zhandry’s group-action money scheme, modified to output real-amplitude quantum states.
+    \item We identify a breakdown in the original verification procedure when the Fourier transform is naively replaced by the Hartley transform: the Hartley-based verification fails to distinguish certain illegitimate banknotes.
+To overcome this, we design a \textbf{new verification algorithm} that relies on applying additional group action “twists” and utilizes quantum walks.
+This new verification algorithm successfully differentiates valid banknotes from forgeries despite the use of real amplitudes.
+    \item We show that the serial number associated with a money state (which is a hidden group element) can be efficiently computed from the quantum state.
+In particular, we develop a \textbf{continuous-time quantum walk algorithm} to extract the serial number of a given banknote state.
+This algorithm leverages the structure of the group action and the spectral properties of an associated Cayley graph.
+Our method demonstrates that one can recover the hidden group element (serial) with high success probability, which not only underpins the new verification technique but is also of independent interest.
+    \item In the course of our construction, we introduce a new algorithm for efficiently implementing the \textbf{quantum Hartley transform} and related real transforms.
+We present a recursive technique that exploits the structure of the Hartley transform, yielding a lower gate complexity than prior approaches in the literature.
+We also illustrate how other real-valued quantum transforms (e.g., the quantum sine transform) can be implemented using the Hartley transform as a subroutine.
+These results contribute to the broader goal of optimizing real quantum transforms for practical use.
+\end{itemize}
+
+In summary, our work combines ideas from quantum cryptography (public-key quantum money), quantum algorithms (quantum walks), and quantum signal processing (Hartley and related transforms) to create a novel and potentially practical quantum money scheme.
+
+\medskip\noindent\textbf{Thesis Organization.} 
+The remainder of this thesis is organized as follows.
+In **Chapter 2**, we provide background on the basics of quantum computation and the theory of group actions, including the concept of cryptographic group actions which underlie our money scheme.
+**Chapter 3** covers quantum walks, both continuous-time and discrete-time, outlining their differences and importance in quantum algorithms.
+In **Chapter 4**, we apply the quantum walk framework to group actions: we describe how a continuous-time quantum walk on a group action can be simulated efficiently, a crucial step for our serial number extraction algorithm.
+**Chapter 5** details the quantum money scheme itself and the role of the Hartley transform in its construction.
+We explain how the scheme is formulated and discuss the advantages and challenges introduced by using the Hartley transform.
+Finally, **Chapter 6** presents the verification algorithm for the Hartley-based quantum money.
+This chapter shows how we use quantum walks (as developed in Chapter 4) to reliably verify banknotes and compute their serial numbers, thereby addressing the verification issues that arose from the use of real amplitudes.
+\vspace{1em}
+
+\chapter{Background on Quantum Computation and Group Actions}
+
+\section{Quantum Computation Basics}
+Quantum computation operates on information stored in quantum states.
+The fundamental unit of quantum information is the \emph{qubit}, which, unlike a classical bit, can exist in a superposition of basis states.
+A qubit is described by a state $|\psi\rangle = \alpha |0\rangle + \beta |1\rangle$ (in Dirac notation), where $\alpha,\beta \in \mathbb{C}$ and $|\alpha|^2 + |\beta|^2 = 1$.
+A system of $n$ qubits resides in a $2^n$-dimensional Hilbert space and its state can be a superposition of all $2^n$ basis basis states $|b_1b_2\cdots b_n\rangle$.
+
+Computation is carried out by unitary transformations on these states.
+A quantum algorithm is typically a sequence of quantum gates (unitary operators) applied to an initial state (usually a simple basis state like $|00\cdots0\rangle$), followed by a measurement of some qubits to obtain a classical result.
+A crucial aspect of quantum computation is that certain transformations—such as the Fourier transform over an $N$-element group—can be implemented very efficiently on a quantum computer (in $\operatorname{poly}(\log N)$ time), whereas their classical counterparts might require $\operatorname{poly}(N)$ time.
+
+One example important to this work is the \textbf{quantum Fourier transform} (QFT).
+For an abelian group $G$ of order $N$, the QFT is the unitary map $|g\rangle \mapsto \frac{1}{\sqrt{N}}\sum_{h \in G} \chi_h(g)\, |h\rangle$, where $\{\chi_h\}$ are the characters (complex exponential homomorphisms) of $G$.
+In more familiar terms, when $G = \mathbb{Z}_N$ (the integers mod $N$), the QFT takes $|j\rangle$ to $\frac{1}{\sqrt{N}}\sum_{k=0}^{N-1} e^{2\pi i j k / N} |k\rangle$.
+The QFT is a key component in many quantum algorithms, including Shor’s factoring algorithm and certain quantum money schemes (e.g., Zhandry’s) that rely on hiding information in phase relationships.
+The QFT can be implemented using $O((\log N)^2)$ basic gates for many groups [13], making it an efficient operation.
+
+Another concept we will use is the \textbf{quantum Hartley transform} (QHT).
+The Hartley transform is an alternative to the Fourier transform that produces only real values (in the classical case) by using sinusoidal basis functions (sums of sine and cosine) instead of complex exponentials.
+The \emph{quantum} Hartley transform is the unitary transform corresponding to the classical Hartley transform.
+For example, the Hartley transform on $\mathbb{Z}_N$ maps a basis state $|j\rangle$ to $\frac{1}{\sqrt{N}}\sum_{k=0}^{N-1} \mathrm{cas}\!\Big(\frac{2\pi j k}{N}\Big)\, |k\rangle$, where $\mathrm{cas}(x) = \cos x + \sin x$ is the Hartley kernel.
+Because $\cos x + \sin x$ is real for all $x$, the resulting amplitudes are real numbers.
+We will discuss the Hartley transform in more detail in Chapter 5, including how to implement it efficiently on a quantum computer.
+
+A final fundamental principle to note is the \textbf{no-cloning theorem}, which underpins the security of quantum money.
+This theorem states that there is no physical operation that can make a copy of an arbitrary unknown quantum state.
+This contrasts sharply with classical information, which can be copied freely.
+The no-cloning theorem means that an adversary cannot duplicate a quantum banknote without fundamentally disturbing it – any attempt to “clone” the state will fail unless the adversary already has complete classical information describing that state.
+
+Throughout this thesis, when we refer to an algorithm as \emph{efficient} or \emph{feasible}, we typically mean it can be performed by a quantum polynomial-time (QPT) algorithm.
+This is analogous to classical polynomial time, but on a quantum computer.
+All of the algorithms we propose (minting, verification, quantum walk simulation, etc.) are intended to be efficient in this sense.
+
+\section{Group Actions in Cryptography}
+At the heart of our quantum money scheme is the notion of a group action.
+A \textbf{group action} of a group $G$ on a set $X$ is a function $*\colon G \times X \to X$ that satisfies two properties: (1) the identity element $e \in G$ acts trivially on every $x \in X$ ($e * x = x$), and (2) the action is compatible with the group operation, meaning $g*(h* x) = (gh)*x$ for all $g,h \in G$ and $x \in X$.
+We will often denote the result of $g$ acting on $x$ by $g*x$ or simply $g x$ when the action is clear from context.
+
+The orbit of an element $x \in X$ under the action is the set $G * x = \{g*x : g \in G\} \subseteq X$.
+If there is exactly one orbit (i.e., $G * x = X$ for some $x$), the action is called \emph{transitive}.
+If, in addition, no non-identity group element fixes any $x$ (i.e., $g * x = x$ implies $g = e$), then the action is \emph{free}.
+A group action that is both transitive and free is sometimes called a \textbf{regular action}.
+In a regular action, for any two elements $y, z \in X$, there is a unique group element $g$ such that $g * y = z$.
+In other words, $G$ acts like a permutation group that moves elements of $X$ around, and knowing the starting and ending point uniquely determines the “move” $g$.
+In this case $|X| = |G|$, and we can think of $X$ as essentially a copy of $G$ with the group structure “hidden” by the action.
+
+Group actions are ubiquitous in modern cryptography.
+A \textbf{cryptographic group action} is one where the action is easy to compute in the forward direction, but inverting the action (recovering $g$ from $x$ and $g*x$) is computationally hard.
+This essentially functions as a one-way function: given $x$ and $g$, it is easy to compute $y = g*x$, but given $x$ and $y$ it is infeasible to find $g$ (except with negligible probability).
+One classical example is the discrete logarithm problem: consider the cyclic group $G = \mathbb{Z}_p^*$ (the multiplicative group of a prime field) acting on itself by exponentiation.
+Let $X = G$ and define $g * x = x^g \pmod p$ (treating group elements as integers).
+Here $g$ is an exponent.
+This is a group action (in fact, just the group’s own operation written differently), and computing $x^g \bmod p$ is efficient.
+However, given $x$ and $y = x^g$, finding $g$ requires solving a discrete log problem, which is believed to be hard for suitable choices of $p$.
+Thus, exponentiation can be viewed as a one-way group action.
+
+Another prominent example comes from elliptic-curve cryptography: the action of an ideal class group on a set of elliptic curves.
+In schemes like CSIDH (Commutative Supersingular Isogeny Diffie–Hellman), an abelian group of ideal classes $G$ acts on the set $X$ of supersingular elliptic curves by isogeny (an isogeny is a structure-preserving map between curves).
+Starting from a curve $x_0$, one can efficiently compute $g * x_0$ (which is another elliptic curve) for any group element $g$, but given two curves $x_0$ and $x = g * x_0$, it is believed to be computationally hard to recover $g$.
+This hard problem is the foundation of isogeny-based cryptography.
+We refer to such $G$ and $X$ as a \emph{cryptographic group action} pair.
+
+Cryptographic group actions provide a natural platform for public-key quantum money schemes.
+In such schemes, the secret “serial number” of a quantum banknote can be an element $g \in G$, and the quantum state of the banknote can be some function of $g*x_0$ for a public base point $x_0 \in X$.
+The hardness of inverting the action ($x_0$ and $x = g*x_0$ do not easily reveal $g$) contributes to the security against counterfeiting, while the structure of the group action can be used to efficiently verify authenticity (as we will see with the Fourier or Hartley transform techniques).
+
+We will assume throughout that we have a family of abelian group actions $(G,X)$ that are cryptographically suitable: $|G|$ is large (growing with the security parameter), the action is efficiently computable, transitive and free (so $|X|=|G|$), and inverting the action is infeasible without the secret key.
+Such families are conjectured to exist (for example, the isogeny-based actions, and others discussed in cryptographic literature).
+
+Finally, we note that working in the \textbf{generic group model} (or generic group \emph{action} model) is a common theoretical approach to analyze security.
+In a generic model, the group elements are treated as black-box labels without exploiting any special algebraic structure beyond group axioms.
+Doliskani’s proof of security for Zhandry’s scheme [15] was in such a generic model for group actions, lending confidence that no “generic” attack can break the scheme.
+In this thesis, we focus on designing the scheme and algorithms at a high level and assume the underlying group action is secure; a detailed security proof is beyond our scope, though we rely on prior results for reassurance.
+
+\chapter{Quantum Walks – Continuous and Discrete}
+Random walks on graphs are a powerful tool in classical algorithms, and their quantum analogues, called \emph{quantum walks}, play a fundamental role in many quantum algorithms.
+Like classical random walks, quantum walks come in two flavors: \textbf{continuous-time} and \textbf{discrete-time}.
+Both types of quantum walks can exhibit dramatically different behavior from their classical counterparts due to quantum interference, which can be leveraged for algorithmic speedups in various problems (for example, quantum walks have led to faster algorithms for database search and element distinctness [4, 5], as well as exponential speedups in oracular problems [10]).
+
+\section{Continuous-Time Quantum Walks}
+A continuous-time quantum walk (CTQW) takes place on the vertices of a graph and is defined by a Hamiltonian (energy operator) that drives the evolution of a quantum state across the graph.
+Formally, consider a graph $\Gamma$ with vertex set $V$ of size $n$.
+We associate a basis state $|v\rangle$ with each vertex $v \in V$.
+In a continuous-time \emph{classical} random walk, one can describe the probability distribution $p(t)$ over vertices at time $t$ by a differential equation $dp/dt = -L p(t)$, where $L$ is the Laplacian matrix of the graph.
+By analogy, in a continuous-time \emph{quantum} walk, we use the Schrödinger equation:
+\[ i\,\frac{d}{dt}|\psi(t)\rangle = H\,|\psi(t)\rangle, \] 
+where $H$ is the Hamiltonian of the walk and $|\psi(t)\rangle$ is the state of the quantum walk at time $t$.
+The formal solution is $|\psi(t)\rangle = e^{-i H t} |\psi(0)\rangle$.
+Intuitively, $H$ encodes the connectivity of the graph, and the quantum state evolves continuously, “exploring” the graph’s vertices.
+
+Typically, for a quantum walk on an undirected graph, a natural choice of Hamiltonian $H$ is the adjacency matrix of the graph (sometimes the Laplacian or a normalized version is used, but the adjacency matrix suffices for our purposes).
+If $A$ is the adjacency matrix of $\Gamma$, then $H = A$ means that the amplitudes flow between adjacent vertices over time.
+Specifically, if $|v\rangle$ and $|w\rangle$ are connected by an edge, the Hamiltonian will induce oscillations of amplitude between $|v\rangle$ and $|w\rangle$.
+Because $H$ is Hermitian, $e^{-iA t}$ is unitary, ensuring the evolution is coherent.
+
+One notable feature of CTQWs is that interference effects can cause the walker to propagate through the graph in ways that a classical random walk cannot.
+For example, quantum walkers can have ballistic spreading (moving roughly linearly fast with time) on certain graphs, whereas classical diffusion is much slower (like $\sqrt{t}$ spread).
+These effects underlie algorithmic speedups.
+For instance, the continuous-time walk on a certain $N$-vertex graph can reach a target vertex in $O(N^{1/2})$ time, whereas a classical random walk might take $O(N)$ steps to achieve the same, illustrating a quadratic speedup in some search problems.
+
+\section{Discrete-Time Quantum Walks}
+Discrete-time quantum walks proceed in a sequence of steps rather than evolving continuously.
+In the discrete-time case, we typically require an additional “coin” space or a similar construction to allow the walker to move without violating unitarity (since a deterministic move on an undirected graph can lead to stagnation without a coin toss to break symmetry).
+In the \textbf{coined model} of a quantum walk, the state is a tensor product $|\text{position}\rangle \otimes |\text{coin}\rangle$.
+At each step, a unitary coin flip (like a Hadamard gate generalizing a two-sided coin to a multi-sided one for vertices of higher degree) is applied to the coin register, and then a conditional shift moves the walker to a new vertex based on the coin outcome.
+This two-part operation (coin flip + shift) constitutes one step of the walk, which is a unitary transformation on the overall Hilbert space.
+
+There is also an alternative approach to discrete-time walks that does not explicitly use a coin, but instead doubles the state space in another way.
+One such approach, due to Szegedy [27], represents a step as two reflections on an enlarged Hilbert space associated with the edges of the graph.
+Another approach (used in some of our analysis) constructs a discrete-time walk using the graph’s adjacency matrix but treats it in a quantum way.
+For a graph $\Gamma=(V,E)$, one can define a unitary operator $U$ acting on the space spanned by $\{|v\rangle \otimes |0/1\rangle: v \in V\}$ (position plus one qubit) that effectively simulates moving along the edges.
+For example, one can design $U$ such that:
+\[ U:\; |v,0\rangle \mapsto \frac{1}{\sqrt{\deg(v)}}\sum_{(v\to w)\in E} |w,1\rangle, \] 
+and similarly $|w,1\rangle$ moves back to $|v,0\rangle$ on the reverse edge.
+This “flip-flop” shift is one way to implement a discrete quantum walk step.
+In essence, the walker has a direction bit that flips each time an edge is traversed, preventing it from just oscillating back and forth between two vertices.
+After many such steps, the probability amplitude distribution over $V$ can spread across the graph.
+
+Despite the differences in formulation, continuous- and discrete-time quantum walks are closely related.
+In fact, it has been shown by Childs [9] and by Berry, Childs, and Kothari [6] that a continuous-time quantum walk can be efficiently simulated using a discrete-time quantum walk.
+The key idea is to approximate the continuous evolution $e^{-iAt}$ by a product of many short discrete updates (Trotterization or a related technique).
+More concretely, given a Hamiltonian $H$ driving a CTQW, one can introduce an ancillary system and a carefully constructed unitary such that the effect of $e^{-iHt}$ is approximated to arbitrary precision with a polynomial number of discrete steps.
+This means that any algorithm that could be conceived in the continuous-time framework can be translated to a discrete-time circuit model with only polylogarithmic overhead in complexity (assuming $H$ is sparse, which in our cases it will be).
+
+Quantum walks have been employed in a range of quantum algorithms.
+For example, Ambainis’s algorithm for element distinctness [5] uses a discrete-time quantum walk on the Johnson graph to achieve a faster than brute-force runtime.
+Childs et al.
+demonstrated an exponential separation between quantum and classical query complexities using a continuous-time quantum walk in a contrived maze problem [10].
+Many search and optimization problems have also been tackled with quantum walk algorithms.
+The common theme is that quantum interference allows the walk to navigate the solution space more efficiently than random fluctuation alone.
+
+In the remainder of this thesis, we will use whichever model of quantum walk is most convenient for analysis.
+Our verification algorithm in Chapter 6 will be described conceptually as a continuous-time walk (because it naturally fits the problem structure), but behind the scenes we will implement it using a discrete-time simulation (Chapter 4 will provide details on how this simulation is done for our specific application).
+
+\chapter{Simulating Group Action Quantum Walks}
+In this chapter, we bridge the concepts from Chapter 2 (group actions) and Chapter 3 (quantum walks).
+Specifically, we consider quantum walks on graphs that arise from group actions, and we discuss how to implement or simulate such walks efficiently on a quantum computer.
+This is crucial for our quantum money verification algorithm, which will require running a quantum walk on a graph defined by the given group action.
+
+\section{Cayley Graphs of Groups and Group Actions}
+A convenient way to visualize a group or a group action is via its Cayley graph.
+First, for an ordinary (abelian) group $G$, if we pick a generating set $S \subset G$ (for example, $S$ could be a small symmetric set of generators such that every element of $G$ can be expressed as a product of elements in $S$), the \textbf{Cayley graph} $\Gamma(G,S)$ is an undirected graph defined as follows: each group element $g \in G$ corresponds to a vertex, and there is an edge between $g$ and $h$ if and only if $h = s \cdot g$ for some generator $s \in S$ (equivalently $g$ and $h$ differ by multiplication by a generator).
+We typically take $S$ to be symmetric (if $s \in S$ then $s^{-1} \in S$) so that the resulting graph is undirected.
+The Cayley graph encapsulates the structure of the group in graph form.
+
+The adjacency matrix $A$ of $\Gamma(G,S)$ has rows and columns indexed by $G$, and $(A)_{g,h} = 1$ if $h = s\cdot g$ for some $s \in S$, and $0$ otherwise.
+It is known that for a finite abelian group $G$, the eigenvectors of this adjacency matrix are related to the characters of $G$ (essentially the Fourier basis on the group), and the eigenvalues can be determined from $S$.
+In particular, if $\chi: G \to \mathbb{C}$ is a character (one of the Fourier basis functions), then it is an eigenvector of $A$.
+The corresponding eigenvalue is $\lambda_{\chi} = \sum_{s\in S} \chi(s)$ (the character evaluated on each generator and summed).
+This means the QFT over $G$ diagonalizes the adjacency matrix $A$.
+As a result, a continuous-time quantum walk on $\Gamma(G,S)$ can be solved analytically by moving to the Fourier basis: $e^{-iAt}$ acts by phases $e^{-i\lambda_{\chi} t}$ on each Fourier basis state.
+Moreover, if $S$ is small (say $|S| = \operatorname{poly}(\log |G|)$), one can efficiently implement $e^{-iAt}$ using the QFT: prepare the state in the Fourier basis (apply QFT), apply a phase rotation by $\lambda_{\chi} t$ on each basis state (which can be done classically if we can compute $\lambda_{\chi}$), and then inverse QFT.
+This takes polynomial time in the size of the problem parameters.
+(For example, for $G=\mathbb{Z}_N$, this procedure would simulate the continuous-time walk by using two QFTs of size $N$ and a linear-time classical phase rotation on $N$ amplitudes, which is efficient.)
+
+Now, consider a group action $G \curvearrowright X$ where $X$ is a set on which $G$ acts.
+We can similarly define a Cayley-type graph for the action.
+Fix a particular element $x_0 \in X$ as a basepoint.
+Take the same generating set $S \subset G$.
+We define the \textbf{group action graph} $\Gamma(X,S)$ as the graph whose vertex set is $X$, and put an edge between two vertices $x, y \in X$ if and only if there exists $s \in S$ such that $y = s * x$ (i.e., $y$ is the result of the group element $s$ acting on $x$).
+Because $S$ is symmetric and the action is regular (in our applications), this graph is also undirected and regular.
+Essentially, $\Gamma(X,S)$ is the “projection” of the group’s Cayley graph into the set $X$ via the action.
+
+If the action of $G$ on $X$ is regular, $\Gamma(X,S)$ is isomorphic to $\Gamma(G,S)$ as an abstract graph (they are structurally the same graph, just the labels of vertices are different: one uses group elements $g$, the other uses states $x = g*x_0$).
+However, there is an important distinction from a computational perspective: labeling the vertices by elements of $X$ might conceal the group structure.
+In fact, if the group action is cryptographically one-way, then although there is a one-to-one correspondence between $G$ and $X$ (via $g \leftrightarrow g* x_0$), finding the group element label $g$ corresponding to a given $x \in X$ is hard.
+In other words, we (as algorithm designers) can efficiently enumerate and work with the group element labels $g \in G$, but an algorithm working with the $X$-labels may not be able to perform the same tasks, because moving to the $G$ label requires inverting the group action.
+
+To put it another way: mathematically, $A(G,S)$ and $A(X,S)$ (the adjacency matrices of the two Cayley graphs) are related by a permutation of the basis if we know the isomorphism $X \cong G$.
+If we had an oracle giving us $g$ for each $x = g*x_0$, then $A(X,S)$ could be efficiently diagonalized just as $A(G,S)$ is (by switching to group element labels and applying QFT).
+But under cryptographic assumptions, we do not have such an oracle; effectively, the basis $\{|x\rangle: x \in X\}$ is a “hidden permutation” of the nice Fourier basis.
+This means that direct quantum Fourier techniques cannot be applied to $A(X,S)$, and new techniques are required to simulate a quantum walk on $\Gamma(X,S)$.
+
+Nonetheless, all is not lost.
+Even if we cannot diagonalize $A(X,S)$ explicitly, we can still leverage the fact that $A(X,S)$ is sparse and structured.
+The degree of each vertex in $\Gamma(X,S)$ is $|S|$, which by assumption is small (at most polynomial in $\log |G|$ for efficiency).
+This sparsity allows us to implement the quantum walk step by step, as we will outline below.
+Moreover, as observed in prior works, even cryptographic group action graphs can sometimes be navigated quantumly.
+For instance, continuous-time quantum walks have been studied in the context of isogeny-based group actions (supersingular isogeny graphs) [8, 16].
+These works implement quantum walks on those graphs (typically for solving certain problems or analyzing mixing properties), treating the action oracle as a black box.
+We will adopt a similar approach: we assume we have efficient oracles for the group action (given $g$ and $x$, compute $g*x$) and for checking group membership or identity if needed.
+Under this assumption, we can implement the quantum walk unitaries directly on the $X$-labeled state space.
+
+\section{Efficient Simulation of Continuous-Time Walks via Discrete Steps}
+As mentioned in Chapter 3, any continuous-time quantum walk on a sparse Hamiltonian can be simulated with a sequence of discrete-time operations.
+In the context of the group action Cayley graph $\Gamma(X,S)$, we want to simulate the unitary $U(t) = e^{-i A(X,S) t}$ for some time $t$ (or a sequence of such unitaries for various times).
+Thanks to Childs [9] and Berry–Childs–Kothari [6], we know that $U(t)$ can be approximated to high precision with $O(\|A\|_{\max} t\, \operatorname{poly}(1/\epsilon))$ uses of a discrete-time walk step and additional gates, where $\epsilon$ is the desired error and $\|A\|_{\max}$ is related to the maximum degree (here $\|A\|_{\max} = |S|$).
+In our case, $|S|$ is small, and $t$ will also be bounded by a polynomial in the relevant input size (for instance, in our application $t$ will be related to the inverse spectral gap or some parameter of the walk, but we will choose manageable values).
+Therefore, an efficient simulation means we need to implement a single step of the discrete-time quantum walk efficiently.
+We now describe how to implement the core components of a discrete-time walk on $\Gamma(X,S)$.
+
+Following the approach used in [6, 9], the key components are:
+1.
+An \textbf{oracle for the sparse Hamiltonian} (in this case, the adjacency matrix).
+This oracle, given a vertex label and an index, outputs the neighboring vertex corresponding to that index.
+For $\Gamma(X,S)$, since each vertex $x$ has $|S|$ neighbors (one for each $s \in S$), such an oracle would on input $(x, j)$ (with $j \in \{1,\dots,|S|\}$ indexing the generators in $S$) output the neighbor $y = s_j * x$.
+We can implement this “oracle” explicitly because we can compute the group action: we know each generator $s_j$, so we can map $(x, j) \mapsto s_j * x$ by a single group action computation.
+This is a classical operation performed quantumly (i.e., we can build a unitary that performs $|x\rangle|j\rangle \mapsto |x\rangle |y\rangle$ where $y = s_j * x$).
+2. Construction of the \textbf{isometry} $V$ that prepares a superposition of neighbor states. Specifically, for each vertex $x$, we want:
+\[ V:\; |x\rangle \;\mapsto\; \frac{1}{\sqrt{|S|}} \sum_{s \in S} |x, s* x\rangle, \] 
+where we have used an output register to hold the neighbor.
+This isometry $V$ can be implemented by first adding an ancilla register for the group element in $S$, initializing it to $|0\rangle$, then creating an equal superposition over all $s \in S$ in that register, and finally replacing that register’s value with the resulting neighbor.
+Concretely, start with $|x, 0\rangle$.
+Use a unitary $U_S$ on the second register such that $U_S|0\rangle = \frac{1}{\sqrt{|S|}}\sum_{s\in S} |s\rangle$.
+Now the state is $\frac{1}{\sqrt{|S|}}\sum_{s\in S} |x, s\rangle$.
+Next, apply the group action oracle to compute $s * x$ in a third register (or overwrite the first register), obtaining $\frac{1}{\sqrt{|S|}}\sum_{s} |x, s, s*x\rangle$.
+Then “uncompute” the $s$ register (apply $U_S^\dagger$ to bring it back to $|0\rangle$) so that we end with $\frac{1}{\sqrt{|S|}}\sum_{s} |x, s*x\rangle$.
+Rename the two registers as $|x\rangle_{\text{orig}} |y\rangle_{\text{nbr}}$.
+This is exactly the desired $V|x\rangle = \frac{1}{\sqrt{|S|}}\sum_{y:\,y = s*x} |x, y\rangle$.
+We have thus implemented $V$ by using the ability to iterate over all generators (which is feasible since $|S|$ is small) and the group action operation.
+
+3.
+We also need to implement $V^\dagger$ (the inverse isometry) which, given a superposition of $|x,y\rangle$, reverses the above process and yields $|x\rangle$ (provided $y$ was indeed one of the neighbors of $x$ in the superposition).
+This essentially requires an operation to compute $s$ from $(x,y)$ such that $y=s*x$.
+Since the action is free and $S$ is small, we can find which generator maps $x$ to $y$ by checking each $s \in S$ (this is a small brute-force check done coherently).
+We can implement a unitary that, for each pair $(x,y)$, finds the unique $s$ with $y=s*x$ and writes $s$ in an ancilla (using comparisons), then uncompute the $y$ register by applying $s^{-1}$ to $y$ (which returns it to $x$) while also un-entangling the $s$.
+In practice, this is efficient since $|S|$ is small and trying all $s$ is a constant or polynomial-time classical loop.
+We assume an oracle or routine that can perform this inversion on a case-by-case basis.
+
+4.
+The final component is the \textbf{reflection operator} (or the walk step) that uses $V$ and $V^\dagger$.
+In the continuous-to-discrete simulation algorithm, one defines a reflection $R = 2V V^\dagger - I$.
+$R$ acts on the enlarged space of vertex-neighbor pairs, and it essentially flips the phase of any state orthogonal to the subspace $\{\frac{1}{\sqrt{|S|}}\sum_{s}|x,s*x\rangle: x \in X\}$ prepared by $V$.
+Intuitively, $R$ distinguishes states that are “properly correlated” as in a single step of a walk from those that are not, and flips the latter’s sign.
+The crucial point is that if we can implement $V$ efficiently (and $V^\dagger$ accordingly) and also trivial reflections like $|0\rangle \to -|0\rangle$ on ancilla states, then we can implement $R$ efficiently as well (since $R = V (2|0\rangle\!\langle 0| - I) V^\dagger$, which means perform $V^\dagger$, do a phase flip on the $|0\rangle$ state of the ancillary superposition register, then apply $V$).
+
+Given these components, a single discrete-time quantum walk step $U_{\text{walk}}$ on $\Gamma(X,S)$ can be constructed.
+In many formulations, one actually uses two reflections to form the walk operator: one as above and another to reflect about the starting subspace (ensuring the walk doesn’t have trivial stationary components).
+However, in the Childs–Berry–Kothari simulation approach, the walk operator is taken as $W = (2V V^\dagger - I) \cdot ( \text{swap registers} )$.
+The “swap” simply swaps the two registers $|x,y\rangle \mapsto |y,x\rangle$, causing a move from $(\text{orig}, \text{nbr})$ to $(\text{new orig} = \text{old nbr}, \text{new nbr} = \text{old orig})$.
+This swap combined with $R$ effectively implements the adjacency relationships as a unitary walk.
+
+To summarize, we have outlined how:
+- The isometry $V$ and its inverse can be implemented with a polynomial number of operations (scaling with $|S|$ and the cost of computing the group action).
+- The reflection $R$ can be built from $V$ and a simple phase flip.
+- The swap operation on two registers is straightforward.
+
+Thus, all components of the discrete-time quantum walk step on the group action graph are efficient.
+We can now leverage known results to claim that a continuous-time walk generated by the Hamiltonian $A(X,S)$ for time $t$ can be simulated by applying $O(t\,\operatorname{poly}(|S|))$ steps of the above discrete walk $W$.
+In our context, we will not need $t$ to be extremely large; we will be interested in running phase estimation on $e^{-iA t}$ for some moderate $t$ values.
+The efficiency we have established means this phase estimation will be feasible.
+
+\section{Group Action Quantum Walks and Spectral Properties}
+Before moving on, it is worth discussing what the spectral properties of the group action Cayley graph $A(X,S)$ imply for our algorithm (which will come in Chapter 6).
+We have noted that in the absence of one-wayness, the eigenstates of $A(X,S)$ would be known (Fourier states) with eigenvalues $\lambda_{\chi} = \sum_{s\in S} \chi(s)$.
+In the presence of one-wayness, we cannot directly label those eigenstates, but they still exist.
+In particular, if $G$ is abelian, the adjacency matrix $A(X,S)$ will have the same multiset of eigenvalues as $A(G,S)$.
+Let us denote those eigenvalues by $\{\lambda_k: k=1,\dots,|G|\}$.
+We may not know which eigenvalue corresponds to which state in $X$, but we know each $\lambda_k = \sum_{s\in S} \chi_k(s)$ for some character $\chi_k$ of $G$.
+For example, in a simple case $G = \mathbb{Z}_N$ and $S=\{1, -1\}$, the eigenvalues of $A(G,S)$ (and thus $A(X,S)$) would be $2\cos(2\pi k/N)$ for $k=0,\dots,N-1$.
+The important take-away is that the eigenvalues are related to the group structure (often involving cosine terms if $S$ is symmetric), and the eigenvectors are “global” states spread out over the vertices.
+
+In the next chapter, we will construct our quantum money scheme such that a valid banknote state is one of these eigenvectors (or closely related to an eigenvector) of a certain group action graph.
+This will be by design: when minting money, the procedure will create a state that, under the action of the adjacency matrix of $\Gamma(X,S)$, picks up a well-defined phase.
+In Chapter 6, our verification algorithm will leverage this by using phase estimation on the continuous-time walk unitary $e^{-iA t}$ to determine the eigenvalue (and thereby infer the “serial number” hidden in the state).
+
+Having established that we can perform the quantum walk on $\Gamma(X,S)$ efficiently, we are prepared to move on to the construction of the quantum money scheme itself, and then to the details of the verification algorithm that uses these walks.
+
+\chapter{Quantum Money and the Hartley Transform}
+We now present our public-key quantum money scheme based on group actions and the Hartley transform.
+We begin by reviewing Zhandry’s quantum money scheme from abelian group actions (which uses the Fourier transform) as a baseline.
+Then we describe our Hartley-transform-based variant and discuss its properties.
+The quantum Hartley transform will play a central role in both the minting and verification of banknotes.
+
+\section{Public-Key Quantum Money: Definitions}
+A public-key quantum money scheme consists of two algorithms, traditionally called $\mathsf{Mint}$ and $\mathsf{Verify}$:
+\begin{itemize}
+    \item $\mathsf{Mint}(1^n)$ is a probabilistic quantum polynomial-time (QPT) algorithm that, given a security parameter $n$, outputs a pair $(s, |\$\rangle)$.
+Here $s$ is a classical string called the \emph{serial number} (or public key) and $|\$\rangle$ is a quantum state representing the banknote.
+We often call the pair $(s, |\$\rangle)$ a banknote, and $s$ by itself the serial number of that banknote.
+    \item $\mathsf{Verify}(s, |\$\rangle)$ is a QPT algorithm (which may be implemented as a quantum circuit acting on the state $|\$\rangle$ and some ancillary workspace).
+It takes as input a serial number $s$ and an alleged quantum banknote state $|\$\rangle$.
+It outputs $\mathtt{accept}$ (valid) or $\mathtt{reject}$ (invalid).
+\end{itemize}
+
+We require two properties from such a scheme:
+\begin{description}
+    \item[Correctness:] For any valid output $(s, |\$\rangle)$ of $\mathsf{Mint}(1^n)$, the verification algorithm accepts with high probability.
+Formally, $\Pr[\mathsf{Verify}(s, |\$\rangle) = \mathtt{accept}]$ should be very close to 1 (typically we require it to be $1 - \negl(n)$, where $\negl(n)$ denotes a negligible function in $n$).
+    \item[Security (Unforgeability):] No efficient adversary, given one or more genuine banknotes, can produce a new valid banknote.
+In the strongest formulation, if an adversary is given a single valid $(s, |\$\rangle)$, it should be infeasible for them to produce two quantum states $|\$'\rangle$ and $|\$''\rangle$ such that $\mathsf{Verify}(s, |\$'\rangle) = \mathsf{Verify}(s, |\$''\rangle) = \mathtt{accept}$ (i.e., they cannot create a second copy that passes verification while retaining the original).
+More generally, even given multiple banknotes, the adversary should not be able to create new ones with fresh serial numbers that pass verification.
+This captures the idea that quantum money cannot be counterfeited.
+\end{description}
+
+In a \emph{public-key} scheme, the verifier uses only the public information (here, the serial number and any scheme-wide public parameters) to check validity, and does not need any secret key.
+The bank (mint) may have a secret key to produce the states, but after minting, the bank’s involvement is not needed.
+In our scheme, the serial number will effectively contain the information needed for public verification (similar to how a classical bill might have a number anyone can look up, except here it’s used in a quantum procedure).
+
+We next outline Zhandry’s scheme, which our scheme builds upon.
+
+\section{Fourier-Based Quantum Money from Group Actions}
+Zhandry’s quantum money scheme [31] is built on an abelian group action $G \curvearrowright X$.
+We have a family of group actions parameterized by the security parameter $n$ (so the size of $G$ grows with $n$).
+For simplicity, assume $|G| = N$.
+The scheme also fixes a particular element $x_0 \in X$ that everyone knows (a public base point in $X$).
+
+The minting algorithm $\mathsf{Mint}$ in Zhandry’s scheme works as follows (informally):
+\begin{enumerate}
+    \item On input $1^n$, sample a random group element $g \leftarrow G$. This $g$ will serve as the serial number $s$ for the banknote.
+    \item Prepare two registers: the first is a group element register, initialized to $|0_G\rangle$ (an encoding of the identity element of $G$), and the second is an $X$-register initialized to $|x_0\rangle$.
+    \item Apply the quantum Fourier transform over $G$ to the first register. This creates a uniform superposition over $G$: 
+    \[
+    \frac{1}{\sqrt{N}} \sum_{h \in G} |h\rangle \otimes |x_0\rangle\,.
+    \] 
+    \item Now apply the group action in a controlled manner: for each basis state $|h\rangle$ in the first register, apply $h$’s action on the second register. This transforms the joint state into 
+    \[
+    \frac{1}{\sqrt{N}} \sum_{h \in G} |h\rangle \otimes |h * x_0\rangle\,,
+    \] 
+    which is an entangled state between a superposition of group elements and their corresponding $X$-elements.
+    \item Apply the inverse QFT (which is the adjoint of the QFT) on the first register. This recombines the amplitudes in the first register. The result (by properties of the QFT) can be shown to be 
+    \[
+    \frac{1}{\sqrt{N}} \sum_{h \in G} \omega^{\langle g,\,h \rangle} |h\rangle \otimes |h * x_0\rangle\,,
+    \] 
+    where $\omega^{\langle g,\,h \rangle}$ denotes the phase picked up that depends on $g$ and $h$.
+In fact, this state can be written as $|g\rangle \otimes \frac{1}{\sqrt{N}}\sum_{h \in G} |h * x_0\rangle$; essentially, the first register ends up in $|g\rangle$ (the serial number) and the second register is an equal superposition of all elements of $X$ in the orbit of $x_0$ (which is $X$ itself, since the action is transitive) but weighted by a phase related to $g$.
+This is the so-called group-action Fourier state.
+    \item The first register (which contains $|g\rangle$) is measured in the computational basis, yielding the random serial number $g$ and collapsing the second register to a state that we will denote $|\$_g\rangle$.
+This $|\$_g\rangle$ is the actual quantum money state corresponding to serial $g$.
+    \item Output the pair $(s = g,\; |\$\rangle = |\$_g\rangle)$.
+\end{enumerate}
+
+In the above, a bit of algebra reveals that $|\$_g\rangle = \frac{1}{\sqrt{N}} \sum_{h \in G} \chi_g(h)\, |h * x_0\rangle$, where $\chi_g(h) = \omega^{\langle g,\,h \rangle}$ is essentially the character of $G$ indexed by $g$.
+In other words, $|\$_g\rangle$ is (up to global phase) the state one gets by applying the representation (character) $\chi_g$ to weight the superposition over the orbit $X$.
+These states for different $g$ are almost orthogonal and can be distinguished with the right measurement.
+
+The verification algorithm $\mathsf{Verify}(g, |\$_g\rangle)$ for Zhandry’s scheme goes as follows:
+\begin{enumerate}
+    \item Given the purported serial number $g \in G$ and an input state $|\psi\rangle$ (which should equal $|\$_g\rangle$ if genuine), attach an auxiliary register prepared in $|x_0\rangle$.
+    \item Perform a controlled group action “kickback” using $g$ on the auxiliary register.
+Specifically, perform the unitary that maps $|y\rangle \otimes |x_0\rangle \mapsto |y\rangle \otimes |g * x_0 \rangle$ for each basis element $|y\rangle$ of the first register.
+(This operation uses the classical $g$ to act on the second register conditioned on the first—essentially, it multiplies the second register’s state by $g$ if the first register is in an appropriate basis state.
+There are various ways to implement this, but conceptually it’s a controlled operation using the known $g$.)
+    \item Now measure the second register (the auxiliary one) in the computational basis of $X$ to see if it is still $|x_0\rangle$.
+If the state $|\psi\rangle$ was the correct Fourier state $|\$_g\rangle$, one can show that this measurement will yield $x_0$ with high probability (constructive interference causes the $x_0$ component to be strong).
+If $|\psi\rangle$ was not the correct state, the measurement is unlikely to give $x_0$.
+    \item Accept if and only if the measurement outcome is $x_0$ (i.e. the second register returns to the base state).
+\end{enumerate}
+
+The intuition is that the genuine state $|\$_g\rangle$ contains a phase that exactly cancels out the action of $g$ in the verification step, causing the auxiliary register to end up back at $x_0$.
+A counterfeit state, by contrast, would not generally have the right phase relationship, and the auxiliary register’s state would be some superposition over $X$ that is not concentrated on $x_0$, hence likely giving a different outcome upon measurement.
+
+Zhandry’s scheme is shown to be correct (valid notes pass) and is believed to be secure under the assumption that the group action is one-way.
+The hardness essentially boils down to: given $x_0$ and $|\$_g\rangle$, an adversary cannot figure out a different $g'$ that would produce a second valid state $|\$_{g'}\rangle$ or replicate $|\$_g\rangle$ (because that would solve the hidden subgroup or discrete log type problem in the group action).
+
+\section{Hartley-Transform Money Scheme Construction}
+Our scheme modifies the above Fourier-based construction by utilizing the \textbf{quantum Hartley transform (QHT)} in place of the QFT.
+Since the Hartley transform is closely related to the Fourier transform (essentially it produces the real and imaginary parts in a single real-valued transform), one might expect this substitution to be straightforward.
+And indeed, for the minting procedure it largely is: we will use the QHT to create real-amplitude superposition states.
+
+Concretely, assume again a group action $G \curvearrowright X$ with $|G|=N$. We fix the same generating set $S$ and basepoint $x_0$. The $\mathsf{Mint}_{H}$ (Hartley mint) algorithm:
+\begin{enumerate}
+    \item Sample a random $g \leftarrow G$ to be the serial number.
+    \item Prepare $|0_G, x_0\rangle$ as before.
+    \item Apply the \emph{quantum Hartley transform} over $G$ to the first register. The Hartley transform (on an abelian group of order $N$) is defined as:
+    \[
+       \mathrm{QHT}: |h\rangle \mapsto \frac{1}{\sqrt{N}} \sum_{k \in G} \cas\!\Big(\frac{2\pi \langle k,h \rangle}{N}\Big) |k\rangle,
+    \] 
+    where $\mathrm{cas}(\theta) = \cos \theta + \sin \theta$ and $\langle k,h \rangle$ denotes some pairing like an exponent or dot product (for cyclic groups this is just $kh$).
+In simpler terms, $\mathrm{QHT}(|0_G\rangle) = \frac{1}{\sqrt{N}}\sum_{k \in G} |k\rangle$ (because $\cas(0)=1$), \emph{the same uniform superposition as the QFT produces for $|0\rangle$}.
+So after this step, we again have $\frac{1}{\sqrt{N}}\sum_{h \in G} |h\rangle|x_0\rangle$, but crucially the coefficients are all \emph{real} and positive (in fact all $1/\sqrt{N}$).
+    \item Perform the controlled group action by the first register on the second: $\frac{1}{\sqrt{N}}\sum_{h} |h\rangle |h*x_0\rangle$.
+    \item Apply the inverse QHT on the first register (which being its own inverse up to a constant factor, is the same operation again since Hartley is symmetric like Fourier).
+Now here is where things differ: after this operation, the joint state will be
+    \[
+       \frac{1}{\sqrt{N}} \sum_{h \in G} \cas\!\Big(\frac{2\pi \langle g,h \rangle}{N}\Big)\, |h\rangle \otimes |h*x_0\rangle.
+    \] 
+    Because the Hartley transform combines what would be cosine and sine terms, this state is not as nicely factorable as in the Fourier case.
+In the Fourier case, we got $|g\rangle \otimes \text{(orbit state)}$.
+In the Hartley case, we do not get a single basis state in the first register; instead we get a superposition in the first register with real coefficients $c_h = \cas(2\pi\langle g,h\rangle/N)$.
+However, note that $c_h$ is just some real number in $[-1,1]$ depending on $g$ and $h$.
+Another way to express the above state is:
+    \[
+      |\$\rangle = \frac{1}{\sqrt{N}} \sum_{x \in X} \Big(\frac{1}{\sqrt{N}}\sum_{h: h*x_0 = x} \cas\!\big(\frac{2\pi \langle g,h \rangle}{N}\big)\Big)\, |x\rangle.
+    \] 
+    Since for a given $x\in X$, all $h$ such that $h*x_0=x$ have the form $h = u g$ for a unique $u \in G$ (because the action is free and transitive), one can simplify the internal sum using properties of the cas function.
+But we need not dive into that here.
+    \item No measurement of the first register is performed.
+In fact, we do not have a nice product state separation, so we cannot simply measure one register to get $g$.
+Instead, the output of minting is just the quantum state $|\$\rangle$ (which is entangled between what used to be two registers) and the known classical serial number $g$ (we know what $g$ we picked).
+\end{enumerate}
+
+The resulting money state $|\$\rangle$ has only real amplitudes (because the initial superposition was real and the controlled operation doesn’t introduce complex numbers, and the Hartley transform yields real coefficients).
+In particular, in the computational basis of $X$, the state $|\$\rangle$ is some real-vector state (with both positive and negative values possible).
+We can think of it as a “Hartley orbit state” corresponding to $g$.
+
+The verification algorithm in our Hartley-based scheme attempts to mirror the Fourier-based verification: it will use the given serial $g$ and try to check the state.
+A first idea would be: do exactly the same as Zhandry’s verify (the group-action kickback and measure).
+However, this fails in certain cases.
+Specifically, the Hartley transform being real causes an ambiguity: it turns out that there exist distinct $g \neq g'$ for which the Hartley-based states $|\$\rangle_g$ and $|\$\rangle_{g'}$ are not orthogonal, and the original verification might accept a forged state that is a certain superposition.
+In fact, the verification algorithm might accept an illegitimate state with some probability bounded away from zero.
+This is the “breakdown” of the straightforward Hartley substitution that we alluded to earlier.
+
+To address this, our verification algorithm takes a more sophisticated approach:
+\begin{enumerate}
+    \item Given $(g, |\psi\rangle)$, it first uses the \textbf{quantum walk-based phase estimation} method (to be detailed in Chapter 6) to \emph{compute the eigenphase corresponding to $g$}.
+In short, we will treat $|\psi\rangle$ as an eigenvector of the group action adjacency matrix with a certain eigenvalue $\lambda$ related to $g$.
+We run a procedure to estimate $\lambda$ to high precision.
+    \item From the estimated eigenvalue(s), we reconstruct a candidate group element $g^*$ that we believe generated the state.
+(This uses the fact that by running phase estimation for multiple carefully chosen walk durations, one can solve for $g$ as shown in [31].)
+    \item We check if $g^* = g$ (the serial number provided). If not, we reject, since the state does not match the serial. If yes, we accept.
+\end{enumerate}
+
+This procedure essentially extracts the hidden group element from the state and compares it to the claimed serial.
+If an adversary tries to forge a state $|\psi\rangle$ for a known serial $g$, the only way to consistently pass verification is if $|\psi\rangle$ truly encodes the same $g$ in its eigen-spectrum.
+A fake note that was causing trouble for the naive Hartley verification (e.g., a state that is a mixture of two different “Hartley orbit” states) would yield an eigenphase that does not correspond to a single valid $g$, and the algorithm would detect the mismatch.
+
+The key quantum tool enabling this verification is the continuous-time quantum walk on the group action graph and the ability to simulate it, which we prepared in Chapter 4.
+The walk Hamiltonian $A(X,S)$ has the genuine money state $|\$\rangle_g$ as an eigenstate with a known eigenvalue $\lambda(g)$.
+By running phase estimation on $e^{-iA t}$ with the state $|\psi\rangle$, we attempt to measure that eigenvalue.
+We repeat for a few different values of $t$ (the “twists” or different phases) to get enough information to pinpoint $g$.
+This approach can be viewed as adding extra “twists” to the verification: effectively, each choice of $t$ in phase estimation is like looking at the state in a different interference fringe pattern, analogous to applying different group actions as twists in the verification procedure.
+This is why we described the new verification as using group action twists—by varying a continuous parameter related to the group action’s eigenvalues, we break the symmetry that allowed a counterfeit to slip through.
+
+We defer the full analysis of the success probabilities and how many repetitions are needed to Chapter 6, where we describe the verification algorithm in detail.
+For now, the takeaway is that by using the quantum walk approach, we can reliably verify Hartley-based money states, restoring security while still enjoying the properties of real amplitudes.
+
+\section{Efficient Quantum Hartley Transform Implementation}
+Before moving on to the verification algorithm, we briefly discuss how we implement the quantum Hartley transform (QHT) efficiently, as this is an important practical aspect of our scheme.
+The Fourier transform is well-known to have efficient circuits; for the Hartley transform, fewer results are available, so we contributed a new circuit construction.
+
+The QHT we need is over an abelian group, which for concreteness one can think of as $\mathbb{Z}_N$ (the general finite abelian group case can usually be reduced to a direct sum of cyclic groups, applying QHT on each cyclic component).
+Classical Hartley transforms have a recursive structure similar to fast Fourier transforms.
+In fact, there are known formulas to express a Hartley transform of size $N$ in terms of two Hartley transforms of size $N/2$ plus some additional linear operations [25].
+We leveraged such structures to design a divide-and-conquer quantum circuit.
+
+Our algorithm for QHT works roughly as follows:
+- If $N$ is even, we can express the length-$N$ Hartley transform in terms of two length-$N/2$ Hartley transforms plus a combination of cheap operations (additions, permutations of data, etc.).
+We implement this decomposition recursively as a quantum circuit.
+The base of the recursion is when the size is small (like $N=2$ or $4$, where the transform can be done with a constant number of gates).
+- We found that by carefully optimizing this recursion and using some known quantum subroutines for certain linear combinations, the overall gate count is improved compared to naive methods or previous proposals [21, 22].
+In particular, our circuit avoids introducing any quantum Fourier transform internally (unlike [22] which computed Hartley via Fourier plus some adjustments), and this yields a purely real rotation-based circuit.
+- The resulting complexity for an $N$-point QHT is $O(N \log N)$ basic quantum gates (up to polylog factors for precision), which is on par (up to constant factors) with the complexity of a QFT circuit.
+We also derived explicit constants for small cases to show improvements over prior work.
+
+Additionally, once we have an efficient QHT, we can also implement other related transforms.
+We demonstrate this with the example of the \textbf{quantum sine transform} (QST).
+The sine transform is another real transform closely related to Hartley (in fact, a sine transform can be implemented by a Hartley transform plus some pre- and post-processing).
+We gave a construction that uses one QHT as a subroutine to realize the QST on $N$ points.
+This had a similar complexity of $O(N \log N)$ gates.
+The broader implication is that a family of real-valued transforms (Hartley, sine, cosine, etc.) can all be efficiently performed on quantum hardware, which may have independent applications in signal processing or other quantum algorithms.
+
+For the purposes of this thesis, the main point is: \emph{we can implement the Hartley transform needed for our money scheme with polynomial efficiency}.
+Thus, switching to the Hartley transform does not introduce any prohibitive cost.
+All steps of minting and verification remain efficient.
+Having covered the construction of the money scheme and the necessary tools, we now proceed to the final piece: the detailed verification algorithm using quantum walks, and an analysis of how it validates genuine banknotes and foils counterfeit attempts.
+\vspace{1em}
+
+\chapter{Verification Algorithm Using Quantum Walks}
+The Hartley-based quantum money scheme introduced in the previous chapter requires a new verification procedure to address the issues that arise from using real amplitude states.
+In this chapter, we describe and analyze the verification algorithm, which leverages continuous-time quantum walks on the group action graph (and their efficient simulation from Chapter 4) to extract the information needed to authenticate a banknote.
+
+    \section{Challenges with Naïve Verification}
+    Before detailing the new algorithm, let us briefly recap why the straightforward approach fails.
+In the Fourier-based scheme, verification was done by a single “kickback” operation using the claimed serial $g$, and measuring an auxiliary register.
+In the Hartley-based scheme, if we attempted the analogous one-step verification, we would perform the controlled-$g$ action and measure the auxiliary system.
+A genuine state $|\$_g\rangle$ (the Hartley money state for serial $g$) would cause some interference pattern in the auxiliary register, but unlike the Fourier case, it does not return the auxiliary to $|x_0\rangle$ deterministically.
+In fact, there is an ambiguity: certain superpositions of eigenstates corresponding to $g$ and $-g$ (or other group-related variants) can produce the same measurement statistics in that one-step test.
+This means an adversary might prepare a counterfeit state that is not a legitimate $|\$_g\rangle$ but still passes the one-step verification with non-zero probability.
+Essentially, the Hartley transform being real means we lost some phase information, and a single measurement cannot distinguish some mirrored states.
+
+    To overcome this, our strategy is to perform a more complete measurement of the state’s “phase spectrum.” Instead of just one operation and measurement, we will use the quantum walk (with Hamiltonian $A = A(X,S)$ as defined earlier) to perform a form of phase estimation.
+
+    \section{Using Quantum Walks to Extract the Serial}
+    The central observation is that the money state $|\$_g\rangle$ is an eigenstate of the walk’s Hamiltonian $A$ on the group action Cayley graph.
+To see this, note that $|\$_g\rangle$ (Fourier or Hartley) lies in the subspace spanned by $\{|x\rangle: x \in X\}$ (we no longer explicitly keep the group element register, since after minting it’s entangled or measured away).
+Consider the adjacency operator $A$ acting on a basis state $|x\rangle$.
+By definition,
+    \[ A |x\rangle = \sum_{s \in S} |s * x\rangle, \] 
+    summing over all neighbors under the generators.
+Now, $|\$_g\rangle$ is (up to normalization) $\sum_{h \in G} f(h)\, |h * x_0\rangle$ for some coefficient function $f(h)$.
+If one applies $A$ to this state:
+    \[ A |\$_g\rangle = \sum_{s \in S} \sum_{h \in G} f(h)\, |s * (h * x_0)\rangle = \sum_{h \in G} f(h)\, \sum_{s \in S} |(sh) * x_0\rangle. \]
+    Now change variable $h' = sh$ in the inner sum.
+Since $s$ runs over all of $S$, $h'$ runs over $S h = \{sh: s \in S\}$ which is exactly the set of neighbors of $h$ in the Cayley graph of $G$.
+For an abelian group, one can show (and it is known from spectral graph theory) that $\sum_{s \in S} |sh * x_0\rangle$ corresponds to the same state as $\lambda_g |h * x_0\rangle$ where $\lambda_g = \sum_{s\in S} \chi_g(s)$ for Fourier states, or $\lambda'_g = \sum_{s\in S} \cas(2\pi \langle g,s\rangle/N)$ for Hartley states.
+In short, $|\$_g\rangle$ is an eigenvector of $A$ with eigenvalue $\lambda_g'$ (a real number that depends on $g$ and $S$).
+This fact was formalized earlier: Lemma 8.2 showed that the money state is an eigenstate of $A$.
+
+    For example, if $G = \mathbb{Z}_N$ and $S=\{1, -1\}$, a Fourier-based $|\$_g\rangle$ is essentially the character $\chi_g$, and indeed $\chi_g$ is an eigenfunction of the adjacency (which is like a cosine operator) with eigenvalue $2\cos(2\pi g/N)$.
+The Hartley-based state corresponds to a combination of $\chi_g$ and $\chi_{-g}$ (the real and imaginary parts combined), and ends up with the same eigenvalue $2\cos(2\pi g/N)$ as well.
+So either way, the “frequency” $g$ maps to a specific eigenvalue $\lambda$.
+
+    The verification algorithm will do the following: it will run phase estimation on the unitary $U = e^{iA\tau}$ for some carefully chosen time $\tau$, using the state $|\psi\rangle$ as input.
+Phase estimation is a standard quantum algorithm that, given an eigenstate of $U$, yields an estimate of the eigenphase $2\pi \phi$ (where $e^{i 2\pi \phi}$ is the eigenvalue of $U$) to some specified precision.
+In our case, since $A$ has eigenvalue $\lambda$ on $|\psi\rangle = |\$_g\rangle$, the unitary $e^{iA\tau}$ has eigenvalue $e^{i \lambda \tau}$.
+Thus phase estimation will give us an estimate of $\lambda \tau \pmod{2\pi}$.
+By choosing $\tau$ appropriately, we can ensure $\lambda \tau$ uniquely corresponds to $\lambda$ (within the precision we work at).
+
+    We cannot run $e^{iA\tau}$ directly, but Chapter 4 showed how to simulate it efficiently with a discrete-time algorithm.
+So when we say “phase estimation on $U = e^{iA\tau}$,” we imply using the simulation routine as a subroutine in the phase estimation circuit.
+This will incur some error $\epsilon$, but we can make it negligible with enough resources.
+
+    Now, because $\lambda$ (the eigenvalue of $A$) is related to $g$, obtaining $\lambda$ in effect gives us information about $g$.
+However, one eigenvalue might correspond to two possible $g$ values (e.g., $\cos(2\pi g/N) = \cos(2\pi (N-g)/N)$).
+So a single run of phase estimation may not fully determine $g$.
+This is where performing the procedure for multiple different times $\tau$ (or perhaps using a slightly different Hamiltonian) helps.
+By getting $\lambda$ at different scales, we can solve for $g$ using the known functional form of $\lambda$ in terms of $g$.
+
+    In [31], it was shown that by using two or three carefully chosen multiples of time (or equivalently using the fact that $\lambda$ as a function of $g$ has a known form like a cosine series), one can uniquely recover $g$.
+In our scheme, since $S$ is known and fixed, and presumably $S$ is such that the map $g \mapsto \lambda_g = \sum_{s\in S} \chi_g(s)$ is injective up to trivial symmetries, a few phase estimates suffice.
+For instance, if $S=\{1,-1\}$, knowing $\cos(2\pi g/N)$ to high precision lets you determine $g$ up to the symmetry $g \leftrightarrow N-g$.
+But if we also had a way to break the symmetry (maybe by using an asymmetric choice of $\tau$ or an additional generator in $S$ that is not symmetric), we can get the sign too.
+Alternatively, we run phase estimation on a slightly modified Hamiltonian $A'$ (maybe corresponding to a different generating set that breaks symmetry) if available.
+
+    For simplicity, let’s suppose two runs with different $\tau$ values are enough. The output of the verification algorithm is then determined by:
+    - If the estimated $g^*$ from the phase(s) matches the provided serial $g$, output \texttt{accept}.
+    - Otherwise, output \texttt{reject}.
+
+    Because a genuine $|\$_g\rangle$ is exactly an eigenstate with eigenvalue $\lambda_g$, phase estimation will return (with high probability) a number very close to $\lambda_g \tau$ modulo $2\pi$.
+Given the precision, we decode it to the nearest valid $\lambda_{g'}$ value, which should be $\lambda_g$.
+Hence we recover $g'=g$ and accept.
+For a counterfeit state, two things can happen:
+    1.
+The state $|\psi\rangle$ is a superposition of eigenstates (not a single eigenstate).
+In that case, phase estimation will give some distribution of eigenvalues, effectively picking one at random (with probabilities proportional to the projection of $|\psi\rangle$ onto those eigencomponents).
+It is highly unlikely that this random outcome consistently points to the same $g^*$ that the adversary wants (especially if they try to match a specific $g$ that they announced as serial).
+In fact, unless the counterfeit state was itself aligned with one particular eigenvalue, the measurement will likely produce a result that does not correspond to the claimed serial, leading to rejection.
+    2.
+The state $|\psi\rangle$ happens to be an eigenstate, but with a wrong eigenvalue (i.e., corresponding to some $g' \neq g$).
+In that case, the phase estimation will reliably give $\lambda_{g'}$, and we will decode $g'$ which won’t match the claimed $g$, so we reject.
+This scenario would occur if the adversary somehow prepared a valid-looking state for a different serial $g'$ but presented it with serial $g$—clearly that should be rejected.
+
+    Thus, the only way to pass is to present a state that is an eigenstate with eigenvalue matching the serial.
+But the only known way to produce such a state is essentially to follow the minting procedure (due to the one-wayness of the group action, they can’t derive $|\$_g\rangle$ without knowing $g$ or breaking the assumption).
+
+    One might wonder: phase estimation is a probabilistic algorithm; what if it sometimes yields the correct $g^*$ and sometimes not, could an adversary repeat the verification or something?
+In practice, the banknote verification either passes or fails once; an adversary doesn’t get to try multiple times on the same note without potentially decohering it or being caught.
+We design our parameters such that the completeness (accepting a good note) is very high and the soundness (accepting a forgery) is extremely low, say negligible in $n$.
+This might involve repeating the phase estimation a constant number of times to amplify confidence, or using a high precision so that the error probability is negligible.
+
+    Finally, our algorithm implicitly uses the ability to perform the controlled-$U$ operations for phase estimation.
+That is non-trivial but our quantum walk simulation provided a way to implement $e^{iA\tau}$, and controlled versions can be constructed by controlling each gate in the simulation (which increases complexity by at most a factor poly(n)).
+We have to ensure that the simulation error is accounted for in the phase estimation accuracy—this can be handled by choosing simulation parameters fine enough that the error is smaller than the inverse of our runtime or something along those lines.
+
+    \section{Detailed Verification Procedure}
+    To summarize, here is a more step-by-step description of the verification algorithm for a banknote $(g, |\psi\rangle)$:
+    \begin{enumerate}
+        \item **Preparation:** Determine a set of one or more time parameters $\{\tau_1, \tau_2, \dots, \tau_m\}$ to be used for phase estimation.
+These might be hardcoded or depend on $N$ and $S$.
+For example, $\tau_1$ could be a basic time and $\tau_2$ another that breaks degeneracy.
+        \item **Phase Estimation Rounds:** For each $\tau_j$:
+        \begin{enumerate}
+            \item Use the quantum walk simulation circuit to implement controlled-$e^{iA \tau_j}$ on $|\psi\rangle$.
+(In practice, we append an ancilla register to accumulate the phase, as in standard phase estimation algorithms.
+We prepare a uniform superposition over some range of time steps, apply controlled-$U$ gates, and perform inverse Fourier transform on the phase register to get an estimate.
+This is the standard routine.)
+            \item Measure the phase register to obtain an estimate $\tilde{\phi}_j$ of $\lambda_g \tau_j / (2\pi)$ (mod 1).
+Multiply by $2\pi/\tau_j$ to get an estimate $\tilde{\lambda}_j$ of $\lambda_g$.
+        \end{enumerate}
+        \item **Compute Serial Candidate:** From the collection $\{\tilde{\lambda}_j\}$, solve for the group element $g^*$ that would produce those eigenvalues.
+This might involve inverting the known relation $\lambda = \sum_{s\in S}\cas(2\pi \langle g, s\rangle/N)$ or whatever the formula is in our context.
+Because of estimation error, we choose the nearest matching $g^*$ in $G$ that would give eigenvalues close to the $\tilde{\lambda}_j$ observed.
+        \item **Accept/Reject:** If $g^* = g$ (and all rounds of phase estimation yielded results consistent with a single $g^*$, which should happen for a valid note), then output \texttt{accept}.
+Otherwise, output \texttt{reject}.
+    \end{enumerate}
+
+    This algorithm may seem complex, but it can be optimized.
+In practice, we could combine multiple phase estimation steps into one larger quantum circuit that extracts $g$ in one go, but conceptually, it’s easier to think of them separately.
+
+    \section{Analysis of Security and Efficiency}
+    The new verification algorithm is more involved than the original Fourier-based one, so we must check that it is still efficient and that it indeed thwarts counterfeiting.
+
+    **Efficiency:** Each phase estimation round uses polynomial-time quantum operations.
+The Hamiltonian simulation of $e^{iA\tau}$ for sparse $A$ on $N$-dimensional space can be done in $\operatorname{poly}(\log N)$ time (since queries to the group action oracle are $O(1)$ and $|S|$ is small).
+The phase estimation itself might need $O(\log N)$ qubits of precision to distinguish different $g$ values, and $O(\log N)$ repetitions of $U$ in superposition.
+Overall, each round is $\operatorname{poly}(n)$ time.
+A constant number of rounds doesn’t change the polynomial class.
+So yes, verification is QPT.
+In fact, in asymptotic terms, if minting took $\tilde{O}(n^c)$ time, verification might take $\tilde{O}(n^{c+1})$ or similar due to extra overhead, but still polynomial.
+
+    **Completeness:** A genuine banknote state $|\$_g\rangle$ will be accepted with high probability.
+The state is an eigenstate of $A$, so phase estimation yields exactly $\lambda_g$ (with small error $\epsilon$).
+Decoding that yields $g^* = g$.
+The only possible errors are from phase estimation not being perfect: there is a small probability it gives the wrong eigenvalue estimate (exponentially small in the number of ancilla qubits used).
+By choosing parameters, we ensure this error is negligible, say $< 2^{-n}$ or similar.
+So the chance a real note is mistakenly rejected is negligible.
+
+    **Soundness:** A counterfeiter’s goal is to have $\mathsf{Verify}(g, |\psi\rangle) = \texttt{accept}$ for some $|\psi\rangle$ that they created without running $\mathsf{Mint}$.
+Essentially, they either try to reuse a state they already saw or combine states to get two accepted notes, etc.
+If they attempt to create a new state for an unused serial $g$, they face the following:
+    - If $|\psi\rangle$ is not an eigenstate of $A$, when we run phase estimation, the outcome is a random eigenvalue from its spectral decomposition.
+It would be a huge coincidence if that random eigenvalue corresponded to exactly the claimed $g$.
+And even if by some luck one phase estimation round gave a favorable result, with two rounds the chance to consistently impersonate the same $g$ is even smaller.
+In fact, by the union bound, the probability that a wrong state passes all checks should be negligible.
+A rigorous argument would be that if $|\psi\rangle$ has overlap on eigenstates $\{|e_j\rangle\}$ with eigenvalues $\lambda_j$, then the verification accepts only if for all $j$ with nonzero overlap, the decoded $g_j$ equals the claimed $g$.
+If any overlap component has a different underlying group element, that component will cause failure in at least one of the phase estimation rounds with high probability.
+Unless the state was aligned to one particular $g'$, in which case the best they can do is claim it is $g'$.
+    - If $|\psi\rangle$ \emph{is} an eigenstate but for $g' \neq g$, then our algorithm will find $g'$ and compare to $g$ and reject.
+So the adversary would have to guess the serial number’s eigenstate perfectly, which means they basically guessed the bank’s secret or solved the one-way problem.
+
+    The most cunning forgery could be to use a genuine note $(g, |\$_g\rangle)$ and try to produce a second independent state $|\$_g\rangle$ for the same $g$.
+But that is essentially copying a quantum state which is unknown to them (they only know $g$ classically).
+Given $g$, can they produce $|\$_g\rangle$?
+That’s the one-way group action problem: producing $|\$_g\rangle$ is as hard as computing $g*x_0$ for all group elements in superposition, which requires knowledge of $g$ in a way that they don't have (they know $g$ but to create the superposition exactly with correct phases is akin to solving for the hidden phase structure—likely hard without the trapdoor).
+In fact, if they could do that efficiently for any given $g$, they would break the scheme by minting their own money.
+So by assumption, that’s infeasible.
+
+    Thus, the only resource the adversary has is perhaps other genuine notes they possess.
+Could they entangle two notes or something to produce two valid ones?
+If they have one note, trying to make two will likely destroy the original or produce two imperfect copies that fail verification (no-cloning strikes again).
+If they have two different notes $(g_1, |\$_{g_1}\rangle)$ and $(g_2, |\$_{g_2}\rangle)$, those states are independent, and forging a new one still reduces to above.
+
+    Therefore, we argue the scheme remains secure: forging in any meaningful sense would require solving a hard problem (inverting the group action or cloning a quantum state).
+
+    In conclusion, by using continuous-time quantum walks and phase estimation, our verification algorithm retrieves the hidden serial number encoded in the quantum money state and compares it to the claimed serial.
+This not only fixes the issue introduced by using the Hartley transform (real amplitudes), but it does so in polynomial time.
+We have thus achieved a public-key quantum money scheme based on standard assumptions (one-way group actions) with an extra novel feature of using real-valued quantum states and demonstrating the power of quantum walks in quantum cryptanalysis and verification.
+
+% \section*{Introduction}
+
+% Quantum computing is a revolutionary field that combines quantum mechanics and information theory to redefine computation and information processing.
 In the latter part of the 20th century, scientists explored the fusion of quantum mechanics and information theory, leading to the birth of quantum information science.
@@
 
-Early quantum algorithms demonstrated that quantum computing could solve certain problems more efficiently than classical methods.
+% Early quantum algorithms demonstrated that quantum computing could solve certain problems more efficiently than classical methods.
 Notably, in 1994, Peter Shor introduced a polynomial-time quantum algorithm for integer factorization, which threatened classical cryptographic protocols relying on the difficulty of factoring large integers.
@@
 
-Quantum systems are fragile and susceptible to decoherence, where quantum states lose their coherence due to interactions with the environment.
+% Quantum systems are fragile and susceptible to decoherence, where quantum states lose their coherence due to interactions with the environment.
 This makes maintaining quantum states for computation a significant challenge.
@@
 
-Quantum key distribution protocols, like BB84 and Ekert’s protocol, offer provably secure methods for communication based on the principles of quantum mechanics.
+% Quantum key distribution protocols, like BB84 and Ekert’s protocol, offer provably secure methods for communication based on the principles of quantum mechanics.
 Unlike classical cryptography, which relies on computational assumptions, quantum cryptography guarantees security through physical principles.
@@
 
-While practical quantum computing is still in its infancy, significant progress has been made.
+% While practical quantum computing is still in its infancy, significant progress has been made.
 Quantum hardware companies like IBM, Google, and Rigetti have developed small-scale quantum processors capable of performing limited computations.
@@
 
-Quantum computing represents a profound shift in how we understand and leverage computation.
+% Quantum computing represents a profound shift in how we understand and leverage computation.
 By replacing classical mechanics with quantum mechanics as the foundation for processing information, quantum computing has opened new avenues for scientific discovery and technological innovation.
@@
 
-\section*{Foundations of Quantum Computation}
-
-\section*{Understanding a Qubit}
-A qubit (quantum bit) is the fundamental unit of quantum information, analogous to a classical bit.
+% \section*{Foundations of Quantum Computation}
+
+% \section*{Understanding a Qubit}
+% A qubit (quantum bit) is the fundamental unit of quantum information, analogous to a classical bit.
 However, unlike a classical bit, which can only exist in one of two definite states ($0$ or $1$), a qubit can exist in a linear combination, or superposition, of both states simultaneously.
@@
 
-\begin{equation}
-|\psi\rangle = \alpha |0\rangle + \beta |1\rangle
-\end{equation}
-
-Here:
-\begin{itemize}
-    \item $|0\rangle$ and $|1\rangle$ are the basis states (analogous to $0$ and $1$ in classical computing).
-    \item $\alpha$ and $\beta$ are complex numbers known as probability amplitudes.
-\end{itemize}
-
-The normalization condition \(|\alpha|^2 + |\beta|^2 = 1\) ensures that the probabilities of measuring the qubit in either the $|0\rangle$ or $|1\rangle$ state sum to 1.
-
-The qubit's unique ability to exist in a superposition of states is what gives quantum computers their immense computational potential, enabling them to process and store information in fundamentally different ways than classical computers.
-
-\section*{Superposition}
-Superposition is a quantum phenomenon where a qubit exists in a combination of multiple states simultaneously. For example, a qubit in the state:
-
-\begin{equation}
-|\psi\rangle = \frac{1}{\sqrt{2}}|0\rangle + \frac{1}{\sqrt{2}}|1\rangle
-\end{equation}
-
-is in an equal superposition of $|0\rangle$ and $|1\rangle$. This means that if we measure the qubit, there is an equal probability (50\%) of observing it in either state.
-
-Key properties of superposition:
-\begin{itemize}
-    \item \textbf{Parallelism:} When a quantum system is in superposition, it can perform computations for all possible states simultaneously.
+% \begin{equation}
+% |\psi\rangle = \alpha |0\rangle + \beta |1\rangle
+% \end{equation}
+
+% Here:
+% \begin{itemize}
+%     \item $|0\rangle$ and $|1\rangle$ are the basis states (analogous to $0$ and $1$ in classical computing).
+%     \item $\alpha$ and $\beta$ are complex numbers known as probability amplitudes.
+% \end{itemize}
+
+% The normalization condition \(|\alpha|^2 + |\beta|^2 = 1\) ensures that the probabilities of measuring the qubit in either the $|0\rangle$ or $|1\rangle$ state sum to 1.
+
+% The qubit's unique ability to exist in a superposition of states is what gives quantum computers their immense computational potential, enabling them to process and store information in fundamentally different ways than classical computers.
+
+% \section*{Superposition}
+% Superposition is a quantum phenomenon where a qubit exists in a combination of multiple states simultaneously. For example, a qubit in the state:
+
+% \begin{equation}
+% |\psi\rangle = \frac{1}{\sqrt{2}}|0\rangle + \frac{1}{\sqrt{2}}|1\rangle
+% \end{equation}
+
+% is in an equal superposition of $|0\rangle$ and $|1\rangle$. This means that if we measure the qubit, there is an equal probability (50\%) of observing it in either state.
+
+% Key properties of superposition:
+% \begin{itemize}
+%     \item \textbf{Parallelism:} When a quantum system is in superposition, it can perform computations for all possible states simultaneously.
 For instance, a single qubit can encode two states ($|0\rangle$ and $|1\rangle$) at the same time, while $n$ qubits can encode $2^n$ states.
-    \item \textbf{Measurement Collapse:} When a qubit in superposition is measured, it collapses into one of its basis states, $|0\rangle$ or $|1\rangle$, with a probability given by $|\alpha|^2$ and $|\beta|^2$, respectively.
-\end{itemize}
-
-Superposition allows quantum systems to explore multiple possibilities in parallel, which is critical for quantum algorithms such as Grover's search or Shor's factoring.
-
-\section*{Entanglement}
-Entanglement is a uniquely quantum phenomenon where two or more qubits become correlated in such a way that the state of one qubit is directly related to the state of the other, regardless of the physical distance between them.
+%     \item \textbf{Measurement Collapse:} When a qubit in superposition is measured, it collapses into one of its basis states, $|0\rangle$ or $|1\rangle$, with a probability given by $|\alpha|^2$ and $|\beta|^2$, respectively.
+% \end{itemize}
+
+% Superposition allows quantum systems to explore multiple possibilities in parallel, which is critical for quantum algorithms such as Grover's search or Shor's factoring.
+
+% \section*{Entanglement}
+% Entanglement is a uniquely quantum phenomenon where two or more qubits become correlated in such a way that the state of one qubit is directly related to the state of the other, regardless of the physical distance between them.
 When qubits are entangled, the measurement of one qubit instantly determines the state of the other.
 
-An example of an entangled state for two qubits is the Bell state:
-
-\begin{equation}
-|\psi\rangle = \frac{1}{\sqrt{2}} (|00\rangle + |11\rangle)
-\end{equation}
-
-Here:
-\begin{itemize}
-    \item $|00\rangle$ means both qubits are in the $|0\rangle$ state.
-    \item $|11\rangle$ means both qubits are in the $|1\rangle$ state.
-\end{itemize}
-
-If one qubit is measured to be $|0\rangle$, the other qubit will instantly collapse to $|0\rangle$, and similarly for $|1\rangle$, regardless of the distance between them.
-
-Key features of entanglement:
-\begin{itemize}
-    \item \textbf{Non-Local Correlations:} Entanglement defies classical intuition, as it suggests that measurement outcomes are correlated even across vast distances, a phenomenon supported by experiments validating Bell's Theorem.
-    \item \textbf{Applications:} Entanglement is a resource for many quantum technologies, including quantum teleportation, quantum cryptography (e.g., secure communication via the BB84 protocol), and quantum error correction.
-\end{itemize}
-
-Entanglement, along with superposition, forms the backbone of quantum computing and quantum communication, enabling capabilities that are impossible in the classical world.
-
-\subsection*{Quantum Gates and Circuits}
-
-Quantum logic gates are the fundamental building blocks of quantum circuits, manipulating qubits—the basic units of quantum information.
+% An example of an entangled state for two qubits is the Bell state:
+
+% \begin{equation}
+% |\psi\rangle = \frac{1}{\sqrt{2}} (|00\rangle + |11\rangle)
+% \end{equation}
+
+% Here:
+% \begin{itemize}
+%     \item $|00\rangle$ means both qubits are in the $|0\rangle$ state.
+%     \item $|11\rangle$ means both qubits are in the $|1\rangle$ state.
+% \end{itemize}
+
+% If one qubit is measured to be $|0\rangle$, the other qubit will instantly collapse to $|0\rangle$, and similarly for $|1\rangle$, regardless of the distance between them.
+
+% Key features of entanglement:
+% \begin{itemize}
+%     \item \textbf{Non-Local Correlations:} Entanglement defies classical intuition, as it suggests that measurement outcomes are correlated even across vast distances, a phenomenon supported by experiments validating Bell's Theorem.
+%     \item \textbf{Applications:} Entanglement is a resource for many quantum technologies, including quantum teleportation, quantum cryptography (e.g., secure communication via the BB84 protocol), and quantum error correction.
+% \end{itemize}
+
+% Entanglement, along with superposition, forms the backbone of quantum computing and quantum communication, enabling capabilities that are impossible in the classical world.
+
+% \subsection*{Quantum Gates and Circuits}
+
+% Quantum logic gates are the fundamental building blocks of quantum circuits, manipulating qubits—the basic units of quantum information.
 Unlike classical logic gates, quantum gates are reversible and represented by unitary matrices, ensuring the preservation of quantum information.
 
-\subsection*{Key Quantum Logic Gates}
-
-\subsubsection*{1. Pauli-X Gate (NOT Gate)}
-\textbf{Operation:} Flips the state of a qubit from $|0\rangle$ to $|1\rangle$ and vice versa. \\
-\textbf{Matrix Representation:}
-\[
-X = 
-\begin{bmatrix}
-0 & 1 \\
-1 & 0
-\end{bmatrix}
-\]
-
-\subsubsection*{2. Hadamard Gate (H Gate)}
-\textbf{Operation:} Creates a superposition state, transforming $|0\rangle$ into $\frac{|0\rangle + |1\rangle}{\sqrt{2}}$ and $|1\rangle$ into $\frac{|0\rangle - |1\rangle}{\sqrt{2}}$. \\
-\textbf{Matrix Representation:}
-\[
-H = \frac{1}{\sqrt{2}}
-\begin{bmatrix}
-1 & 1 \\
-1 & -1
-\end{bmatrix}
-\]
-
-\subsubsection*{3. Controlled-NOT Gate (CNOT Gate)}
-\textbf{Operation:} A two-qubit gate that flips the state of the target qubit if the control qubit is in the state $|1\rangle$. \\
-\textbf{Matrix Representation:}
-\[
-CNOT =
-\begin{bmatrix}
-1 & 0 & 0 & 0 \\
-0 & 1 & 0 & 0 \\
-0 & 0 & 0 & 1 \\
-0 & 0 & 1 & 0
-\end{bmatrix}
-\]
-
-\subsubsection*{4. Toffoli Gate (CCNOT Gate)}
-\textbf{Operation:} A three-qubit gate that flips the state of the target qubit if both control qubits are in the state $|1\rangle$. \\
-\textbf{Matrix Representation:}
-\[
-CCNOT =
-\begin{bmatrix}
-1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 \\
-0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 \\
-0 & 0 & 0 & 1 & 0 & 0 & 0 & 0 \\
-0 & 0 & 0 & 0 & 1 & 0 & 0 & 0 \\
-0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 \\
-0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 \\
-0 & 0 & 0 & 0 & 0 & 0 & 1 & 0
-\end{bmatrix}
-\]
-
-\subsection*{Universal Gates}
-A set of gates is considered \textbf{universal} if any unitary operation can be approximated to arbitrary precision using a sequence of gates from this set.
+% \subsection*{Key Quantum Logic Gates}
+
+% \subsubsection*{1. Pauli-X Gate (NOT Gate)}
+% \textbf{Operation:} Flips the state of a qubit from $|0\rangle$ to $|1\rangle$ and vice versa. \\
+% \textbf{Matrix Representation:}
+% \[
+% X = 
+% \begin{bmatrix}
+% 0 & 1 \\
+% 1 & 0
+% \end{bmatrix}
+% \]
+
+% \subsubsection*{2. Hadamard Gate (H Gate)}
+% \textbf{Operation:} Creates a superposition state, transforming $|0\rangle$ into $\frac{|0\rangle + |1\rangle}{\sqrt{2}}$ and $|1\rangle$ into $\frac{|0\rangle - |1\rangle}{\sqrt{2}}$. \\
+% \textbf{Matrix Representation:}
+% \[
+% H = \frac{1}{\sqrt{2}}
+% \begin{bmatrix}
+% 1 & 1 \\
+% 1 & -1
+% \end{bmatrix}
+% \]
+
+% \subsubsection*{3. Controlled-NOT Gate (CNOT Gate)}
+% \textbf{Operation:} A two-qubit gate that flips the state of the target qubit if the control qubit is in the state $|1\rangle$. \\
+% \textbf{Matrix Representation:}
+% \[
+% CNOT =
+% \begin{bmatrix}
+% 1 & 0 & 0 & 0 \\
+% 0 & 1 & 0 & 0 \\
+% 0 & 0 & 0 & 1 \\
+% 0 & 0 & 1 & 0
+% \end{bmatrix}
+% \]
+
+% \subsection*{Universal Gates}
+% A set of gates is considered \textbf{universal} if any unitary operation can be approximated to arbitrary precision using a sequence of gates from this set.
 For example, single-qubit rotation gates combined with the CNOT gate form a universal set, enabling the construction of any quantum algorithm.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction to Quantum Walks}
-
-The concept of a \textit{quantum walk} is a quantum analog of the classical random walk and plays a significant role in quantum algorithms.
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \section{Introduction to Quantum Walks}
+
+% The concept of a \textit{quantum walk} is a quantum analog of the classical random walk and plays a significant role in quantum algorithms.
 There are two main types of quantum walks: \textit{continuous-time} and \textit{discrete-time} quantum walks, both of which exhibit behaviors that are significantly different from classical random walks.
 
-\section*{Continuous-Time Quantum Walks}
-
-Classical continuous-time random walks (Markov chains) are a foundational concept in stochastic processes, where time is treated as a continuous variable.
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \section*{Continuous-Time Quantum Walks}
+
+% Classical continuous-time random walks (Markov chains) are a foundational concept in stochastic processes, where time is treated as a continuous variable.
 In this framework, a walker moves from one vertex of a graph to an adjacent vertex at any time, with probabilities evolving over time.
@@
 
-To model this mathematically, the probability of transitioning from one vertex to another in an infinitesimal time interval \( \Delta t \) is proportional to \( \gamma \Delta t \).
+% To model this mathematically, the probability of transitioning from one vertex to another in an infinitesimal time interval \( \Delta t \) is proportional to \( \gamma \Delta t \).
 For a vertex \( x_j \) with degree \( d_j \) (the number of neighboring vertices), the probability of the walker staying on \( x_j \) is
 
-\[
-1 - d_j \gamma \Delta t,
-\]
-
-while the probability of transitioning to a neighboring vertex is
-
-\[
-\gamma \Delta t.
-\]
-
-The evolution of probabilities over time is captured by the transition matrix \( M(t) \), where the entry \( M_{ij}(t) \) represents the probability of transitioning from vertex \( x_j \) to vertex \( x_i \) in time \( t \).
+% \[
+% 1 - d_j \gamma \Delta t,
+% \]
+
+% while the probability of transitioning to a neighboring vertex is
+
+% \[
+% \gamma \Delta t.
+% \]
+
+% The evolution of probabilities over time is captured by the transition matrix \( M(t) \), where the entry \( M_{ij}(t) \) represents the probability of transitioning from vertex \( x_j \) to vertex \( x_i \) in time \( t \).
 The dynamics of the system are described by a differential equation derived from the transition matrix and an auxiliary matrix \( H \), known as the generating matrix.
@@
 
-\[
-\frac{dM(t)}{dt} = -H M(t),
-\]
-
-has a solution expressed as
-
-\[
-M(t) = e^{-Ht},
-\]
-
-which allows for the computation of probability distributions at any given time. The solution is verified using the Taylor series expansion of the exponential function.
-
-The passage from classical continuous-time Markov chains to quantum walks involves a standard quantization process.
+% \[
+% \frac{dM(t)}{dt} = -H M(t),
+% \]
+
+% has a solution expressed as
+
+% \[
+% M(t) = e^{-Ht},
+% \]
+
+% which allows for the computation of probability distributions at any given time. The solution is verified using the Taylor series expansion of the exponential function.
+
+% The passage from classical continuous-time Markov chains to quantum walks involves a standard quantization process.
 In classical random walks, probabilities evolve via the transition matrix \( M \).
@@
 
-\[
-U(t) = e^{-iHt}
-\]
-
-by multiplying \( H \) with the imaginary unit \( i \).
-
-In a continuous-time quantum walk, the quantum state evolves over time according to the unitary operator \( U(t) \).
+% \[
+% U(t) = e^{-iHt}
+% \]
+
+% by multiplying \( H \) with the imaginary unit \( i \).
+
+% In a continuous-time quantum walk, the quantum state evolves over time according to the unitary operator \( U(t) \).
 If the initial state of the system is \( |\psi(0)\rangle \), the state at time \( t \) is given by
 
-\[
-|\psi(t)\rangle = U(t) |\psi(0)\rangle.
-\]
-
-The probability distribution for observing the walker at a specific vertex \( k \) is computed as
-
-\[
-p_k = |\langle k | \psi(t) \rangle|^2,
-\]
-
-where \( |k\rangle \) represents the state corresponding to vertex \( k \).
-
-The continuous-time quantum walk introduces several key differences from its classical counterpart.
+% \[
+% |\psi(t)\rangle = U(t) |\psi(0)\rangle.
+% \]
+
+% The probability distribution for observing the walker at a specific vertex \( k \) is computed as
+
+% \[
+% p_k = |\langle k | \psi(t) \rangle|^2,
+% \]
+
+% where \( |k\rangle \) represents the state corresponding to vertex \( k \).
+
+% The continuous-time quantum walk introduces several key differences from its classical counterpart.
 Unlike classical random walks, which rely on probabilities, quantum walks involve probability amplitudes, enabling interference effects.
@@
 
-*********Examples and further discussions here*********
-
-% Overall, the transition from classical continuous-time Markov chains to continuous-time quantum walks highlights fundamental differences between classical and quantum dynamics, particularly the role of interference and the constraints of unitary evolution in quantum systems.
-These differences underscore the potential of quantum walks in quantum computing and algorithm design.
-
-\section*{Discrete-Time Quantum Walks}
-*******************
-The discrete-time coined quantum walk (DTQW) is a quantum analog of classical random walks, leveraging the principles of quantum mechanics to achieve unique computational and dynamical properties.
-It is defined on a graph or lattice, with the walker's state described by both its position and an internal "coin" state.
-The walker's position \( n \) on a one-dimensional lattice (line) is represented by a vector \( |n\rangle \) in an infinite-dimensional Hilbert space \( \mathcal{H}_P \), where the computational basis for \( \mathcal{H}_P \) is
-
-\[
-\{ |n\rangle : n \in \mathbb{Z} \}.
-\]
-
-The walker's internal state, or "coin," is represented by a two-dimensional Hilbert space \( \mathcal{H}_C \) with basis states \( |0\rangle \) and \( |1\rangle \).
-The coin state determines the direction of the walker's movement, and the total state of the system resides in the tensor product space
-
-\[
-\mathcal{H} = \mathcal{H}_C \otimes \mathcal{H}_P,
-\]
-
-combining the coin and position spaces.
-
-The dynamics of the walk are governed by two key operators: the coin operator and the shift operator.
-The coin is represented by a unitary matrix \( C \) acting on \( \mathcal{H}_C \).
-Common choices include the Hadamard matrix, which creates superpositions of the coin states.
-The Hadamard coin operator \( H \) is defined as
-
-\[
-H = \frac{1}{\sqrt{2}} \begin{pmatrix} 1 & 1 \\ 1 & -1 \end{pmatrix}.
-\]
-
-The shift operator \( S \) moves the walker based on the coin state.
-For example, if the coin state is \( |0\rangle \), the walker moves to \( |n+1\rangle \), and if the coin state is \( |1\rangle \), the walker moves to \( |n-1\rangle \).
-The shift operator is explicitly given by
-
-\[
-S = \sum_{n} |n+1\rangle \langle n| \otimes |0\rangle \langle 0| + |n-1\rangle \langle n| \otimes |1\rangle \langle 1|.
-\]
-
-The evolution of the system is described by the unitary operator
-
-\[
-U = S \cdot (I \otimes C),
-\]
-
-where \( I \) is the identity operator on \( \mathcal{H}_P \). The state of the walker at time \( t+1 \) is given by
-
-\[
-|\psi(t+1)\rangle = U |\psi(t)\rangle.
-\]
-
-Consider a quantum walk on a one-dimensional lattice.
-The walker's state evolves in superposition, allowing it to explore multiple paths simultaneously.
-Interference between these paths leads to faster spreading compared to classical random walks.
-
-Key features of DTQW include superposition, where the walker exists in a superposition of positions and coin states, enabling parallel exploration of multiple paths; interference, where quantum interference enhances or suppresses certain paths, leading to non-classical behavior; and quadratic speedup, where quantum walks spread faster than classical random walks, often quadratically, which is advantageous for algorithmic applications.
-
-DTQWs are used in quantum algorithms, such as quantum search and graph traversal, and in simulating physical systems like energy transport in photosynthesis.
-They also serve as a framework for universal quantum computation.
-The discrete-time quantum walk is a powerful tool in quantum computing, offering a rich interplay between quantum mechanics and graph theory.
-Its ability to exploit superposition and interference enables applications in algorithm design, simulation, and computation, making it a cornerstone of quantum information science.
-
-*********Examples and further discussions here*********
-
-\subsection*{Comparison of Models}
-
-From a computational standpoint, both continuous-time and discrete-time quantum walks offer distinct advantages.
+% \subsection*{Example: Continuous-Time Quantum Walk on the Line}
+
+% To illustrate the behavior of continuous-time quantum walks, consider the example of a particle evolving on the \textit{infinite one-dimensional lattice}, also known as the \textit{integer line}.
+In this graph, the vertices are labeled by integers \( \mathbb{Z} \), and each vertex \( n \in \mathbb{Z} \) is connected to its immediate neighbors \( n-1 \) and \( n+1 \).
+The adjacency matrix \( A \) for this graph has entries:
+% \[
+% A_{i,j} =
+% \begin{cases}
+% 1 & \text{if } |i - j| = 1, \\
+% 0 & \text{otherwise}.
+% \end{cases}
+% \]
+
+% Let the walker initially be located at the origin, so the initial state is \( |\psi(0)\rangle = |0\rangle \). The quantum evolution of the system is governed by the Schrödinger equation:
+% \[
+% i \frac{d}{dt} |\psi(t)\rangle = A |\psi(t)\rangle,
+% \]
+% with the solution:
+% \[
+% |\psi(t)\rangle = e^{-iAt} |\psi(0)\rangle.
+% \]
+
+% For this specific graph, the amplitude of being at position \( n \) at time \( t \) has an elegant closed-form expression:
+% \[
+% \psi_n(t) = i^n J_n(2t),
+% \]
+% where \( J_n \) is the \textit{Bessel function of the first kind} of order \( n \). The corresponding probability of finding the walker at vertex \( n \) at time \( t \) is:
+% \[
+% p_n(t) = |\psi_n(t)|^2 = |J_n(2t)|^2.
+% \]
+
+% This probability distribution displays quintessential quantum behavior: it is \textbf{non-Gaussian}, \textbf{oscillatory}, and \textbf{spreads faster} than in the classical case.
+In contrast to the diffusive behavior of classical walks, where the standard deviation grows as \( \sigma(t) \propto \sqrt{t} \), the quantum walk exhibits \textit{ballistic spread} with \( \sigma(t) \propto t \).
+
+% These interference-driven properties make CTQWs particularly powerful for applications in quantum information and quantum algorithms, where the speed and spread of information are crucial.
+
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \section*{Discrete-Time Quantum Walks}
+
+% Discrete-time quantum walks (DTQWs) serve as the discrete counterpart of quantum random walks and are particularly useful for algorithmic constructions in quantum computing.
+Unlike continuous-time quantum walks, DTQWs require an additional coin degree of freedom to preserve unitarity in the evolution.
+In this section, we explore the discrete-time coined quantum walk on the infinite one-dimensional lattice (integer line), which provides a clear and tractable example of how interference and superposition govern quantum behavior.
+
+% \subsubsection*{Hilbert Space and Coin Space}
+
+% The state space of the system is the tensor product \( \mathcal{H} = \mathcal{H}_C \otimes \mathcal{H}_P \), where:
+% \begin{itemize}
+%     \item \( \mathcal{H}_C \) is the 2-dimensional Hilbert space of the quantum coin, with basis states \( \{|0\rangle, |1\rangle\} \), often interpreted as ``spin up'' and ``spin down''.
+%     \item \( \mathcal{H}_P \) is the position Hilbert space, spanned by \( \{|n\rangle : n \in \mathbb{Z}\} \), representing the particle's location on the integer line.
+% \end{itemize}
+
+% \subsubsection*{Coin and Shift Operators}
+
+% The walk consists of two operations applied in sequence:
+% \begin{enumerate}
+%     \item \textbf{Coin operator \( C \)}: A unitary operator acting on \( \mathcal{H}_C \), typically chosen to create superposition. A common choice is the \textit{Hadamard coin}:
+%     \[
+%     H = \frac{1}{\sqrt{2}} \begin{bmatrix}
+%     1 & 1 \\
+%     1 & -1
+%     \end{bmatrix}.
+%     \]
+%     \item \textbf{Shift operator \( S \)}: A unitary operator on \( \mathcal{H}_C \otimes \mathcal{H}_P \) that moves the walker depending on the coin state:
+%     \[
+%     S|0\rangle|n\rangle = |0\rangle|n + 1\rangle, \quad
+%     S|1\rangle|n\rangle = |1\rangle|n - 1\rangle.
+%     \]
+% \end{enumerate}
+
+% One full step of the walk is implemented by applying the unitary operator:
+% \[
+% U = S (C \otimes I_P),
+% \]
+% where \( I_P \) is the identity operator on \( \mathcal{H}_P \). Repeated application of \( U \) evolves the quantum state over time:
+% \[
+% |\psi(t)\rangle = U^t |\psi(0)\rangle.
+% \]
+
+% \subsubsection*{Example: Hadamard Walk from the Origin}
+
+% Suppose the initial state of the system is localized at the origin with coin state \( |0\rangle \):
+% \[
+% |\psi(0)\rangle = |0\rangle \otimes |0\rangle.
+% \]
+% Applying the Hadamard operator and then the shift, the system evolves after one step into a superposition:
+% \[
+% |\psi(1)\rangle = \frac{1}{\sqrt{2}} \left( |0\rangle|1\rangle + |1\rangle|-1\rangle \right).
+% \]
+% The particle is now in a coherent superposition of being at positions \( +1 \) and \( -1 \), determined by its coin state.
+
+% This process continues iteratively. For example, the second and third steps yield:
+% \begin{align*}
+% |\psi(2)\rangle &= \frac{1}{2} \left( -|1\rangle|-2\rangle + (|0\rangle + |1\rangle)|0\rangle + |0\rangle|2\rangle \right), \\
+% |\psi(3)\rangle &= \frac{1}{2\sqrt{2}} \left( |1\rangle|-3\rangle - |0\rangle|-1\rangle + (2|0\rangle + |1\rangle)|1\rangle + |0\rangle|3\rangle \right).
+% \end{align*}
+
+% \subsubsection*{Quantum vs Classical Behavior}
+
+% The key difference between quantum and classical random walks lies in the presence of \textit{interference} and \textit{superposition}:
+% \begin{itemize}
+%     \item In classical random walks, probabilities are updated step-by-step based on stochastic transitions, leading to a binomial distribution that approximates a Gaussian as time progresses.
+%     \item In contrast, discrete-time quantum walks generate probability amplitudes that can interfere constructively or destructively depending on the history of the evolution.
+% \end{itemize}
+
+% As a result, the probability distribution of the DTQW is not symmetric or Gaussian, and it spreads much faster than its classical counterpart.
+Specifically, the standard deviation of a DTQW grows linearly with time \( \sigma(t) \sim t \), while in the classical case it grows as \( \sqrt{t} \).
+
+% If a position measurement is performed after every step, the quantum walk collapses into a classical random walk due to decoherence.
+However, by deferring measurement and allowing the system to evolve unitarily over many steps, quantum correlations between paths persist, yielding a rich interference pattern in the final probability distribution.
+
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \subsection*{Comparison of Models}
+
+% From a computational standpoint, both continuous-time and discrete-time quantum walks offer distinct advantages.
 The continuous-time quantum walk is often considered more natural because it does not require expanding the state space, making it simpler to define and typically easier to analyze.
@@
 
-In contrast, the discrete-time quantum walk is generally more straightforward to implement using quantum circuits.
+% In contrast, the discrete-time quantum walk is generally more straightforward to implement using quantum circuits.
 Implementing continuous-time quantum walks, however, often relies on techniques that require the graph's maximum degree to be small.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Group Actions}
-
-Group actions provide a framework for understanding how groups interact with sets, formalizing the concept of applying transformations systematically.
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \section{Group Actions}
+
+% Group actions provide a framework for understanding how groups interact with sets, formalizing the concept of applying transformations systematically.
 They capture the symmetries and structure-preserving transformations of objects, making them fundamental in mathematics and its applications.
@@
 
-In cryptography, group actions are critical to protocols like Elliptic Curve Cryptography (ECC), which relies on the difficulty of reversing group-based operations to ensure security.
+% In cryptography, group actions are critical to protocols like Elliptic Curve Cryptography (ECC), which relies on the difficulty of reversing group-based operations to ensure security.
 Isogeny-based cryptography, a post-quantum cryptographic candidate, uses group actions on elliptic curves to create complex mathematical problems resistant to quantum attacks.
@@
 
-In quantum computing, group actions are central to quantum walks, a quantum equivalent of classical random walks.
+% In quantum computing, group actions are central to quantum walks, a quantum equivalent of classical random walks.
 Quantum walks leverage group actions to describe the evolution of quantum states and exploit the symmetries of these states for tasks like search, optimization, and cryptographic protocol design.
@@
 
-\section*{Definition of Group Action}
-
-Group actions form a bridge between group theory and other mathematical structures, offering a systematic way to study symmetry, transformations, and invariants.
+% \section*{Definition of Group Action}
+
+% Group actions form a bridge between group theory and other mathematical structures, offering a systematic way to study symmetry, transformations, and invariants.
 Let us delve deeper into their properties, classifications, and applications.
 
-\subsection*{Formal Definition}
-
-A \textbf{group action} of a group \( G \) on a set \( X \) is a map \( \cdot : G \times X \to X \) that satisfies:
-
-\begin{enumerate}
-    \item \textbf{Identity Property}:
-    \[
-    e \cdot x = x \quad \text{for all } x \in X,
-    \]
-    where \( e \) is the identity element of \( G \).
-
-    \item \textbf{Compatibility (Associativity)}:
-    \[
-    (gh) \cdot x = g \cdot (h \cdot x) \quad \text{for all } g, h \in G, \, x \in X.
-    \]
-\end{enumerate}
-
-Alternatively, the group action can be viewed as a homomorphism \( \phi : G \to \text{Sym}(X) \), where \( \text{Sym}(X) \) is the group of all permutations of \( X \).
-
-\subsection*{Types of Group Actions}
-
-\begin{enumerate}
-    \item \textbf{Faithful Action}: The action is faithful if \( g \cdot x = x \) for all \( x \in X \) implies \( g = e \). Equivalently, the homomorphism \( \phi \) is injective.
-
-    \item \textbf{Transitive Action}: The action is transitive if, for any \( x, y \in X \), there exists \( g \in G \) such that \( g \cdot x = y \). In this case, \( X \) consists of a single orbit.
-
-    \item \textbf{Free Action}: The action is free if \( g \cdot x = x \) implies \( g = e \) for all \( x \in X \).
-
-    \item \textbf{Regular Action}: The action is both transitive and free, meaning there is exactly one \( g \in G \) for each pair \( (x, y) \) such that \( g \cdot x = y \).
-
-    \item \textbf{Effective Action}: The action is effective if the only group element acting as the identity on \( X \) is \( e \).
-\end{enumerate}
-
-\subsection*{Key Concepts in Group Actions}
-
-\begin{enumerate}
-    \item \textbf{Orbits}:
-    For \( x \in X \), the \textbf{orbit} of \( x \) is:
-    \[
-    \text{Orb}(x) = \{g \cdot x \mid g \in G\}.
-    \]
-    Orbits partition the set \( X \), and each orbit is a subset where the action appears ``connected.''
-
-    \item \textbf{Stabilizer Subgroup}:
-    The \textbf{stabilizer} of \( x \in X \) is:
-    \[
-    \text{Stab}_G(x) = \{g \in G \mid g \cdot x = x\}.
-    \]
-    It is a subgroup of \( G \) and describes the symmetries that leave \( x \) unchanged.
-
-    \item \textbf{Orbit-Stabilizer Theorem}:
-    This theorem links the size of an orbit and its stabilizer:
-    \[
-    |G| = |\text{Orb}(x)| \cdot |\text{Stab}_G(x)|.
-    \]
-
-    \item \textbf{Fixed Points}:
-    A point \( x \in X \) is a \textbf{fixed point} if \( g \cdot x = x \) for all \( g \in G \). The set of fixed points is:
-    \[
-    \text{Fix}(G) = \{x \in X \mid g \cdot x = x, \, \forall g \in G\}.
-    \]
-
-    \item \textbf{Invariant Subsets}:
-    A subset \( Y \subseteq X \) is \textbf{invariant} under the action if \( g \cdot y \in Y \) for all \( g \in G \) and \( y \in Y \).
-\end{enumerate}
-
-\section*{Groups and Characters}
-
-\section{Abelian Groups}
-
-An \textbf{abelian group} (also called a \textbf{commutative group}) is a set \( G \) equipped with a binary operation \( \cdot \) (usually written as addition \( + \) or multiplication \( \cdot \)) that satisfies the following four group axioms, along with an additional \textbf{commutativity} property.
-
-\subsection{Axioms of an Abelian Group}
-A set \( G \) with a binary operation \( \cdot \) is an \textbf{abelian group} if the following conditions hold:
-
-\begin{enumerate}
-    \item \textbf{Closure}:  
-    For all \( a, b \in G \), the operation \( a \cdot b \) produces another element in \( G \):
-
-    \[
-    a \cdot b \in G.
-    \]
-
-    \item \textbf{Associativity}:  
-    For all \( a, b, c \in G \), the operation satisfies:
-
-    \[
-    (a \cdot b) \cdot c = a \cdot (b \cdot c).
-    \]
-
-    \item \textbf{Identity Element}:  
-    There exists an element \( e \in G \) such that for all \( a \in G \):
-
-    \[
-    e \cdot a = a \cdot e = a.
-    \]
-
-    This element \( e \) is called the \textbf{identity element}.
-
-    \item \textbf{Inverse Element}:  
-    For every element \( a \in G \), there exists an element \( a^{-1} \in G \) such that:
-
-    \[
-    a \cdot a^{-1} = a^{-1} \cdot a = e.
-    \]
-
-    \item \textbf{Commutativity (Abelian Property)}:  
-    For all \( a, b \in G \), the operation is \textbf{commutative}:
-
-    \[
-    a \cdot b = b \cdot a.
-    \]
-
-\end{enumerate}
-
-Since abelian groups satisfy commutativity, they allow more flexible mathematical operations and structure, leading to applications in algebra, number theory, and topology.
-
-\subsection{Characters of Abelian Groups}
-Let \( G \) be an abelian group. A function
-
-\[
-\chi: G \to \mathbb{C}^{\times}
-\]
-
-that maps \( G \) to the group of nonzero complex numbers  \(\mathbb{C}^{\times} = \mathbb{C} \setminus \{0\}\), is called a \textbf{character} of \( G \) if it is a \textbf{group homomorphism}.
+% \subsection*{Formal Definition}
+
+% A \textbf{group action} of a group \( G \) on a set \( X \) is a map \( \cdot : G \times X \to X \) that satisfies:
+
+% \begin{enumerate}
+%     \item \textbf{Identity Property}:
+%     \[
+%     e \cdot x = x \quad \text{for all } x \in X,
+%     \]
+%     where \( e \) is the identity element of \( G \).
+
+%     \item \textbf{Compatibility (Associativity)}:
+%     \[
+%     (gh) \cdot x = g \cdot (h \cdot x) \quad \text{for all } g, h \in G, \, x \in X.
+%     \]
+% \end{enumerate}
+
+% Alternatively, the group action can be viewed as a homomorphism \( \phi : G \to \text{Sym}(X) \), where \( \text{Sym}(X) \) is the group of all permutations of \( X \).
+
+% \subsection*{Types of Group Actions}
+
+% \begin{enumerate}
+%     \item \textbf{Faithful Action}: The action is faithful if \( g \cdot x = x \) for all \( x \in X \) implies \( g = e \). Equivalently, the homomorphism \( \phi \) is injective.
+
+%     \item \textbf{Transitive Action}: The action is transitive if, for any \( x, y \in X \), there exists \( g \in G \) such that \( g \cdot x = y \).
+In this case, \( X \) consists of a single orbit.
+
+%     \item \textbf{Free Action}: The action is free if \( g \cdot x = x \) implies \( g = e \) for all \( x \in X \).
+
+%     \item \textbf{Regular Action}: The action is both transitive and free, meaning there is exactly one \( g \in G \) for each pair \( (x, y) \) such that \( g \cdot x = y \).
+
+%     \item \textbf{Effective Action}: The action is effective if the only group element acting as the identity on \( X \) is \( e \).
+% \end{enumerate}
+
+% \subsection*{Key Concepts in Group Actions}
+
+% \begin{enumerate}
+%     \item \textbf{Orbits}:
+%     For \( x \in X \), the \textbf{orbit} of \( x \) is:
+%     \[
+%     \text{Orb}(x) = \{g \cdot x \mid g \in G\}.
+%     \]
+%     Orbits partition the set \( X \), and each orbit is a subset where the action appears ``connected.''
+
+%     \item \textbf{Stabilizer Subgroup}:
+%     The \textbf{stabilizer} of \( x \in X \) is:
+%     \[
+%     \text{Stab}_G(x) = \{g \in G \mid g \cdot x = x\}.
+%     \]
+%     It is a subgroup of \( G \) and describes the symmetries that leave \( x \) unchanged.
+
+%     \item \textbf{Orbit-Stabilizer Theorem}:
+%     This theorem links the size of an orbit and its stabilizer:
+%     \[
+%     |G| = |\text{Orb}(x)| \cdot |\text{Stab}_G(x)|.
+%     \]
+
+%     \item \textbf{Fixed Points}:
+%     A point \( x \in X \) is a \textbf{fixed point} if \( g \cdot x = x \) for all \( g \in G \). The set of fixed points is:
+%     \[
+%     \text{Fix}(G) = \{x \in X \mid g \cdot x = x, \, \forall g \in G\}.
+%     \]
+
+%     \item \textbf{Invariant Subsets}:
+%     A subset \( Y \subseteq X \) is \textbf{invariant} under the action if \( g \cdot y \in Y \) for all \( g \in G \) and \( y \in Y \).
+% \end{enumerate}
+
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \section*{Groups and Characters}
+
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \section{Abelian Groups}
+
+% An \textbf{abelian group} (also called a \textbf{commutative group}) is a set \( G \) equipped with a binary operation \( \cdot \) (usually written as addition \( + \) or multiplication \( \cdot \)) that satisfies the following four group axioms, along with an additional \textbf{commutativity} property.
+
+% \subsection{Axioms of an Abelian Group}
+% A set \( G \) with a binary operation \( \cdot \) is an \textbf{abelian group} if the following conditions hold:
+
+% \begin{enumerate}
+%     \item \textbf{Closure}:  
+%     For all \( a, b \in G \), the operation \( a \cdot b \) produces another element in \( G \):
+
+%     \[
+%     a \cdot b \in G.
+%     \]
+
+%     \item \textbf{Associativity}:  
+%     For all \( a, b, c \in G \), the operation satisfies:
+
+%     \[
+%     (a \cdot b) \cdot c = a \cdot (b \cdot c).
+%     \]
+
+%     \item \textbf{Identity Element}:  
+%     There exists an element \( e \in G \) such that for all \( a \in G \):
+
+%     \[
+%     e \cdot a = a \cdot e = a.
+%     \]
+
+%     This element \( e \) is called the \textbf{identity element}.
+
+%     \item \textbf{Inverse Element}:  
+%     For every element \( a \in G \), there exists an element \( a^{-1} \in G \) such that:
+
+%     \[
+%     a \cdot a^{-1} = a^{-1} \cdot a = e.
+%     \]
+
+%     \item \textbf{Commutativity (Abelian Property)}:  
+%     For all \( a, b \in G \), the operation is \textbf{commutative}:
+
+%     \[
+%     a \cdot b = b \cdot a.
+%     \]
+
+% \end{enumerate}
+
+% Since abelian groups satisfy commutativity, they allow more flexible mathematical operations and structure, leading to applications in algebra, number theory, and topology.
+
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \subsection{Characters of Abelian Groups}
+% Let \( G \) be an abelian group. A function
+
+% \[
+% \chi: G \to \mathbb{C}^{\times}
+% \]
+
+% that maps \( G \) to the group of nonzero complex numbers  \(\mathbb{C}^{\times} = \mathbb{C} \setminus \{0\}\), is called a \textbf{character} of \( G \) if it is a \textbf{group homomorphism}.
 That is, for all \( g_1, g_2 \in G \), the function satisfies:
 
-\[
-\chi(g_1 g_2) = \chi(g_1) \chi(g_2).
-\]
-
-\section*{Character Values for Finite Groups}
-
-If \( \chi \) is a character of a finite group (or more generally, a torsion group) \( G \), then each function value \( \chi(g) \) is a root of unity.
+% \[
+% \chi(g_1 g_2) = \chi(g_1) \chi(g_2).
+% \]
+
+% \section*{Character Values for Finite Groups}
+
+% If \( \chi \) is a character of a finite group (or more generally, a torsion group) \( G \), then each function value \( \chi(g) \) is a root of unity.
 This follows because, for each \( g \in G \), there exists some integer \( k \in \mathbb{N} \) such that:
 
-\[
-g^k = e.
-\]
-
-Applying \( \chi \) to both sides, we obtain:
-
-\[
-\chi(g)^k = \chi(g^k) = \chi(e) = 1.
-\]
-
-\section*{Number of Characters in a Finite Abelian Group}
-
-A \textbf{finite abelian group} of order \( n \) has exactly \( n \) distinct characters, denoted by:
-
-\[
-\chi_1, \chi_2, \dots, \chi_n.
-\]
-
-The function \( \chi_1 \), defined by:
-
-\[
-\chi_1(g) = 1, \quad \forall g \in G,
-\]
-
-is called the \textbf{principal character} of \( G \). The remaining \( n-1 \) characters are referred to as \textbf{non-principal characters}.
-
-\section*{Character Group}
-
-If \( G \) is an abelian group, the set of characters \( \{\chi_k\} \) forms an abelian group under pointwise multiplication, defined as:
-
-\[
-(\chi_j \chi_k)(g) = \chi_j(g) \chi_k(g), \quad \forall g \in G.
-\]
-
-This group is called the \textbf{character group} of \( G \) and is often denoted as $\hat{G}$.  
-The \textbf{identity element} of \( \hat{G} \) is the principal character \( \chi_1 \), and the \textbf{inverse} of a character \( \chi_k \) is its reciprocal:
-
-\[
-(\chi_k)^{-1} = \frac{1}{\chi_k}.
-\]
-
-If \( G \) is finite of order \( n \), then the character group \( \hat{G} \) is also of order \( n \). In this case, since
-
-\[
-|\chi_k(g)| = 1, \quad \forall g \in G,
-\]
-
-the inverse of a character is simply its \textbf{complex conjugate}:
-
-\[
-\chi_k^{-1}(g) = \overline{\chi_k(g)}.
-\]
-
-\section{Quantum Fourier Transform}
-
-The \textbf{Quantum Fourier Transform (QFT)} is one of the most fundamental unitary transformations in quantum computing.
+% \[
+% g^k = e.
+% \]
+
+% Applying \( \chi \) to both sides, we obtain:
+
+% \[
+% \chi(g)^k = \chi(g^k) = \chi(e) = 1.
+% \]
+
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \section*{Number of Characters in a Finite Abelian Group}
+
+% A \textbf{finite abelian group} of order \( n \) has exactly \( n \) distinct characters, denoted by:
+
+% \[
+% \chi_1, \chi_2, \dots, \chi_n.
+% \]
+
+% The function \( \chi_1 \), defined by:
+
+% \[
+% \chi_1(g) = 1, \quad \forall g \in G,
+% \]
+
+% is called the \textbf{principal character} of \( G \). The remaining \( n-1 \) characters are referred to as \textbf{non-principal characters}.
+
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \section*{Character Group}
+
+% If \( G \) is an abelian group, the set of characters \( \{\chi_k\} \) forms an abelian group under pointwise multiplication, defined as:
+
+% \[
+% (\chi_j \chi_k)(g) = \chi_j(g) \chi_k(g), \quad \forall g \in G.
+% \]
+
+% This group is called the \textbf{character group} of \( G \) and is often denoted as $\hat{G}$.  
+% The \textbf{identity element} of \( \hat{G} \) is the principal character \( \chi_1 \), and the \textbf{inverse} of a character \( \chi_k \) is its reciprocal:
+
+% \[
+% (\chi_k)^{-1} = \frac{1}{\chi_k}.
+% \]
+
+% If \( G \) is finite of order \( n \), then the character group \( \hat{G} \) is also of order \( n \). In this case, since
+
+% \[
+% |\chi_k(g)| = 1, \quad \forall g \in G,
+% \]
+
+% the inverse of a character is simply its \textbf{complex conjugate}:
+
+% \[
+% \chi_k^{-1}(g) = \overline{\chi_k(g)}.
+% \]
+
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \section{Quantum Fourier Transform}
+
+% The \textbf{Quantum Fourier Transform (QFT)} is one of the most fundamental unitary transformations in quantum computing.
 It plays a crucial role in quantum algorithms, including Shor’s algorithm for integer factorization and quantum phase estimation.
@@
 
-In this section, we discuss the QFT in the context of abelian groups, with a focus on its implementation over \( \mathbb{Z}_{2^n} \), one of the most commonly used finite groups in quantum algorithms, including quantum walks.
-
-\section{Quantum Fourier Transform Over an Abelian Group}
-
-Let \( G \) be an abelian group. The \textbf{Quantum Fourier Transform} over \( G \) is defined as:
-
-\[
-F_G = \frac{1}{\sqrt{|G|}} \sum_{x \in G} \sum_{y \in \hat{G}} \chi_y(x) | y \rangle \langle x |
-\]
-
-where:
-
-\begin{itemize}
-    \item \( \hat{G} \) is a complete set of characters of \( G \).
-    \item \( \chi_y(x) \) denotes the \( y \)th character of \( G \), evaluated at \( x \).
-    \item \( |x\rangle \) and \( |y\rangle \) are quantum states corresponding to elements of \( G \) and its dual group \( \hat{G} \).
-\end{itemize}
-
-Since \( G \) and \( \hat{G} \) are isomorphic, it is often useful to label the elements of \( \hat{G} \) using elements of \( G \).
+% In this section, we discuss the QFT in the context of abelian groups, with a focus on its implementation over \( \mathbb{Z}_{2^n} \), one of the most commonly used finite groups in quantum algorithms, including quantum walks.
+
+% \section{Quantum Fourier Transform Over an Abelian Group}
+
+% Let \( G \) be an abelian group. The \textbf{Quantum Fourier Transform} over \( G \) is defined as:
+
+% \[
+% F_G = \frac{1}{\sqrt{|G|}} \sum_{x \in G} \sum_{y \in \hat{G}} \chi(y,x) | y \rangle \langle x |
+% \]
+
+% where:
+
+% \begin{itemize}
+%     \item \( \hat{G} \) is a complete set of characters of \( G \).
+%     \item \( \chi(y,x) \) denotes the \( y \)th character of \( G \), evaluated at \( x \).
+%     \item \( |x\rangle \) and \( |y\rangle \) are quantum states corresponding to elements of \( G \) and its dual group \( \hat{G} \).
+% \end{itemize}
+
+% Since \( G \) and \( \hat{G} \) are isomorphic, it is often useful to label the elements of \( \hat{G} \) using elements of \( G \).
 The unitary nature of the QFT follows from the \textbf{orthogonality of characters}.
 
-\subsection{QFT Over \( \mathbb{Z}_{2^n} \)}
-
-The QFT over \( G = \mathbb{Z}_{2^n} \) is defined as:
-
-\[
-F_{\mathbb{Z}_{2^n}} = \frac{1}{\sqrt{2^n}} \sum_{x,y \in \mathbb{Z}_{2^n}} \omega_{2^n}^{xy} | y \rangle \langle x |
-\]
-
-where:
-
-\[
-\omega_m = e^{2\pi i / m}
-\]
-
-is the \textbf{primitive} \( m \)th root of unity. This transformation maps an input basis state \( |x\rangle \) as follows:
-
-\[
-| x \rangle \to \frac{1}{\sqrt{2^n}} \sum_{y \in \mathbb{Z}_{2^n}} \omega_{2^n}^{xy} | y \rangle.
-\]
-
-This equation represents a \textbf{linear transformation} where each input state \( |x\rangle \) is mapped to a superposition of all basis states, weighted by phase factors.
-
-\subsection{Binary Representation and QFT Implementation}
-
-To implement this transformation efficiently, it is useful to express \( x \) and \( y \) in binary form:
-
-\[
-x = x_{n-1} x_{n-2} \dots x_1 x_0.
-\]
-
-The exponent in the Fourier transform formula can then be rewritten using its binary expansion:
-
-\[
-\omega_{2^n}^{xy} = e^{2\pi i x \sum_{k=0}^{n-1} y_k 2^k / 2^n}.
-\]
-
-Rewriting the transformation explicitly:
-
-\[
-| x \rangle \to \frac{1}{\sqrt{2^n}} \sum_{y \in \mathbb{Z}_{2^n}} e^{2\pi i x \sum_{k=0}^{n-1} y_k 2^k / 2^n} | y \rangle.
-\]
-
-This can be decomposed into a \textbf{tensor product of single-qubit states}, where each qubit state depends on the least significant bits of \( x \):
-
-\[
-\bigotimes_{k=0}^{n-1} | z_k \rangle.
-\]
-
-where
-
-\[
-| z_k \rangle = \frac{1}{\sqrt{2}} ( | 0 \rangle + e^{2\pi i ( x_0 2^{-n+k} + x_1 2^{-n+k+1} + \dots + x_{n-1} 2^{-1} )} | 1 \rangle ).
-\]
-
-This decomposition highlights the \textbf{hierarchical dependence of qubits on the binary digits of \( x \)}, making it possible to implement the QFT using \textbf{Hadamard gates and controlled phase shift gates}.
-
-\subsection*{Cayley graphs}
-
-A Cayley graph is a graphical representation of a group based on a chosen set of generators.
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \subsection{QFT Over \( \mathbb{Z}_{2^n} \)}
+
+% The QFT over \( G = \mathbb{Z}_{2^n} \) is defined as:
+
+% \[
+% F_{\mathbb{Z}_{2^n}} = \frac{1}{\sqrt{2^n}} \sum_{x,y \in \mathbb{Z}_{2^n}} \omega_{2^n}^{xy} | y \rangle \langle x |
+% \]
+
+% where:
+
+% \[
+% \omega_m = e^{2\pi i / m}
+% \]
+
+% is the \textbf{primitive} \( m \)th root of unity. This transformation maps an input basis state \( |x\rangle \) as follows:
+
+% \[
+% | x \rangle \to \frac{1}{\sqrt{2^n}} \sum_{y \in \mathbb{Z}_{2^n}} \omega_{2^n}^{xy} | y \rangle.
+% \]
+
+% This equation represents a \textbf{linear transformation} where each input state \( |x\rangle \) is mapped to a superposition of all basis states, weighted by phase factors.
+
+% \subsection{Binary Representation and QFT Implementation}
+
+% To implement this transformation efficiently, it is useful to express \( x \) and \( y \) in binary form:
+
+% \[
+% x = x_{n-1} x_{n-2} \dots x_1 x_0.
+% \]
+
+% The exponent in the Fourier transform formula can then be rewritten using its binary expansion:
+
+% \[
+% \omega_{2^n}^{xy} = e^{2\pi i x \sum_{k=0}^{n-1} y_k 2^k / 2^n}.
+% \]
+
+% Rewriting the transformation explicitly:
+
+% \[
+% | x \rangle \to \frac{1}{\sqrt{2^n}} \sum_{y \in \mathbb{Z}_{2^n}} e^{2\pi i x \sum_{k=0}^{n-1} y_k 2^k / 2^n} | y \rangle.
+% \]
+
+% This can be decomposed into a \textbf{tensor product of single-qubit states}, where each qubit state depends on the least significant bits of \( x \):
+
+% \[
+% \bigotimes_{k=0}^{n-1} | z_k \rangle.
+% \]
+
+% where
+
+% \[
+% | z_k \rangle = \frac{1}{\sqrt{2}} ( | 0 \rangle + e^{2\pi i ( x_0 2^{-n+k} + x_1 2^{-n+k+1} + \dots + x_{n-1} 2^{-1} )} | 1 \rangle ).
+% \]
+
+% This decomposition highlights the \textbf{hierarchical dependence of qubits on the binary digits of \( x \)}, making it possible to implement the QFT using \textbf{Hadamard gates and controlled phase shift gates}.
+
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \subsection*{Cayley graphs}
+
+% A Cayley graph is a graphical representation of a group based on a chosen set of generators.
 It is widely used in algebra, combinatorics, and theoretical computer science to study group structures and their applications in network theory, quantum computing, and cryptography.
 
-\section*{Definition of Cayley Graphs}
-
-A \textit{Cayley graph} is a graph that encodes the structure of a group with respect to a chosen generating set.
-Formally, let \( G \) be a group and \( S \) be a subset of \( G \) that serves as a generating set, meaning every element of \( G \) can be expressed as a finite product of elements from \( S \).
-The Cayley graph \( \Gamma(G, S) \) is defined as follows.
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \section*{Definition of Cayley Graphs}
+
+% A \textit{Cayley graph} is a graph that encodes the structure of a group with respect to a chosen generating set.
+Formally, let \( G \) be a group and \( Q \) be a subset of \( G \) that serves as a generating set, meaning every element of \( G \) can be expressed as a finite product of elements from \( Q \).
+The Cayley graph \( \Gamma(G, Q) \) is defined as follows.
 The vertex set of the graph consists of the elements of \( G \), where each vertex corresponds to a unique group element.
-The edge set is constructed by drawing a directed edge from vertex \( g \) to vertex \( gs \) for each \( g \in G \) and \( s \in S \).
-If the generating set \( S \) is symmetric, meaning that whenever \( s \in S \), its inverse \( s^{-1} \) is also in \( S \), then the Cayley graph is undirected; otherwise, it is a directed graph.
-For example, For the cyclic group \( G = \mathbb{Z}_n = \{0,1,2,\dots, n-1\} \) with the generating set \( S = \{\pm 1\} \), the Cayley graph forms a cycle graph.
+The edge set is constructed by drawing a directed edge from vertex \( g \) to vertex \( gq \) for each \( g \in G \) and \( q \in Q \).
+If the generating set \( Q \) is symmetric, meaning that whenever \( q \in Q \), its inverse \( q^{-1} \) is also in \( Q \), then the Cayley graph is undirected; otherwise, it is a directed graph.
+% For example, For the cyclic group \( G = \mathbb{Z}_n = \{0,1,2,\dots, n-1\} \) with the generating set \( Q = \{\pm 1\} \), the Cayley graph forms a cycle graph.
 In this graph, each vertex \( j \) is connected to \( j+1 \mod n \) and \( j-1 \mod n \), creating a cyclic structure.\\
 
-The adjacency matrix of $\Gamma$ can be expressed as
-\[
-A = \sum_{a \in G} \lambda_a |\hat{a}\rangle \langle \hat{a}|,
-\]
-where $|\hat{a}\rangle$ is the quantum Fourier transform of $|a\rangle$. The eigenvalues $\lambda$ are given by
-\[
-\lambda_a = \sum_{q \in Q} \chi(a, q).
-\]
-Note that the eigenvectors $|\hat{a}\rangle$ of $A$ depend only on $G$ and not on the set $Q$.
-
-To see this, we have
-\[
-        A\ket{\hat{a}} = A.\frac{1}{\sqrt{|G|}}\sum_{y \in G}\chi(a,y)\ket{y} = \frac{1}{\sqrt{|G|}}\sum_{y \in G}\chi(a,y).A\ket{y}
-        \]
-        \[
-        = \frac{1}{\sqrt{|G|}}\sum_{y \in G}\chi(a,y).\sum_{q \in Q}\ket{qy}
-        \]
-        Consider $\beta = qy$. Then:
-        \[
-         = \frac{1}{\sqrt{|G|}}\sum_{q \in Q}\chi(a,q)\sum_{\beta}\chi(a,\beta)\ket{\beta} = \sum_{q \in Q}\chi(a,q) . \ket{\hat{a}}
-        \]
-        \[
-         = \lambda_a\ket{\hat{a}}
-        \]
-
-\section*{Quantum walks on Cayley graphs}
-Quantum walks on Cayley graphs play a crucial role in quantum computing, quantum search algorithms, and mathematical physics due to their deep connection with group theory and symmetry.
+% The adjacency matrix of $\Gamma$ can be expressed as
+% \[
+% A = \sum_{a \in G} \lambda_a |\hat{a}\rangle \langle \hat{a}|,
+% \]
+% where $|\hat{a}\rangle$ is the quantum Fourier transform of $|a\rangle$. The eigenvalues $\lambda$ are given by
+% \[
+% \lambda_a = \sum_{q \in Q} \chi(a, q).
+% \]
+% Note that the eigenvectors $|\hat{a}\rangle$ of $A$ depend only on $G$ and not on the set $Q$.
+
+% To see this, we have
+% \[
+%         A\ket{\hat{a}} = A.\frac{1}{\sqrt{|G|}}\sum_{y \in G}\chi(a,y)\ket{y} = \frac{1}{\sqrt{|G|}}\sum_{y \in G}\chi(a,y).A\ket{y}
+%         \]
+%         \[
+%         = \frac{1}{\sqrt{|G|}}\sum_{y \in G}\chi(a,y).\sum_{q \in Q}\ket{qy}
+%         \]
+%         Consider $\beta = qy$. Then:
+%         \[
+%          = \frac{1}{\sqrt{|G|}}\sum_{q \in Q}\chi(a,q)\sum_{\beta}\chi(a,\beta)\ket{\beta} = \sum_{q \in Q}\chi(a,q) . \ket{\hat{a}}
+%         \]
+%         \[
+%          = \lambda_a\ket{\hat{a}}
+%         \]
+
+% \section*{Quantum walks on Cayley graphs}
+% Quantum walks on Cayley graphs play a crucial role in quantum computing, quantum search algorithms, and mathematical physics due to their deep connection with group theory and symmetry.
 The structured nature of Cayley graphs, derived from group elements and generators, ensures uniform exploration of the graph, leading to faster propagation compared to classical random walks.
@@
 
-\section*{Discrete-Time Quantum Walk on Cayley Graphs}
-
-A discrete-time quantum walk on a Cayley graph requires a coin operator to maintain unitary evolution.
-
-\subsection*{State Space}
-The Hilbert space of the quantum walk is:
-\[
-\mathcal{H} = \mathcal{H}_G \otimes \mathcal{H}_C,
-\]
-where:
-\begin{itemize}
-    \item \( \mathcal{H}_G \) is the space spanned by group elements (vertices).
-    \item \( \mathcal{H}_C \) is the coin space, which determines movement directions.
-\end{itemize}
-
-Each state is represented as:
-\[
-|\psi\rangle = \sum_{g \in G} \sum_{s \in S} \alpha_{g,s} |g\rangle \otimes |s\rangle,
-\]
-where \( |g\rangle \) is the vertex state and \( |s\rangle \) represents the coin state.
-
-\subsection*{Evolution Operators}
-\textbf{Coin Flip Operator (\( C \))}: This unitary operator acts on the coin space to create a superposition of movement directions. A common choice is the Grover or Hadamard operator.
-
-\textbf{Shift Operator (\( S \))}: Moves the walker according to the group structure:
-\[
-S |g\rangle \otimes |s\rangle = |gs\rangle \otimes |s\rangle.
-\]
-This means that if the walker is at vertex \( g \) with a coin state \( s \), it moves to \( gs \).
-
-\textbf{Full Step Evolution}:
-\[
-U = S (C \otimes I),
-\]
-where \( U \) is the total unitary evolution per step.
-
-The probability of finding the walker at a particular vertex \( g \) after \( t \) steps is given by:
-\[
-P(g, t) = \sum_{s \in S} |\langle g, s | \psi(t) \rangle |^2.
-\]
-
-\section*{Continuous-Time Quantum Walk on Cayley Graphs}
-
-A continuous-time quantum walk on a Cayley graph follows a different evolution, governed by the Hamiltonian.
-
-\subsection*{Hamiltonian and Evolution}
-The evolution of the quantum walk is determined by the Schrödinger equation:
-\[
-i \frac{d}{dt} |\psi(t)\rangle = H |\psi(t)\rangle.
-\]
-Here, the Hamiltonian \( H \) is usually chosen as:
-\[
-H = A(\Gamma(G,S)),
-\]
-where \( A \) is the adjacency matrix of the Cayley graph:
-
-\[
-A_{g,h} =
-\begin{cases}
-1, & \text{if } h = gs \text{ for some } s \in S, \\
-0, & \text{otherwise}.
-\end{cases}
-\]
- Alternatively, the Laplacian \( L \) can be used:
-\[
-H = L = D - A,
-\]
-where \( D \) is the degree matrix:
-
-\[
-D_{ij} =
-\begin{cases}
-\deg(v_i), & \text{if } i = j, \\
-0, & \text{otherwise}.
-\end{cases}
-\]
-
-Here, \( \deg(v_i) \) is the degree of vertex \( v_i \), which is the number of edges connected to \( v_i \).
-
-The solution to the quantum walk is given by:
-\[
-|\psi(t)\rangle = e^{-i H t} |\psi(0)\rangle.
-\]
-This means the probability amplitude at a vertex \( g \) spreads over time according to the unitary evolution operator \( e^{-i H t} \).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Example: Cyclic Group \( \mathbb{Z}_n \)}
-
-Consider the Cayley graph of \( \mathbb{Z}_n \) with generator set \( S = \{\pm 1\} \), which forms a cycle graph. The adjacency matrix is:
-\[
-A_{jk} =
-\begin{cases}
-1, & \text{if } k = j \pm 1 \mod n, \\
-0, & \text{otherwise}.
-\end{cases}
-\]
-
-Its eigenvalues are:
-\[
-\lambda_k = 2\cos\left(\frac{2\pi k}{n}\right),
-\]
-with eigenvectors given by the discrete Fourier transform (DFT) basis:
-\[
-\psi_k(j) = e^{\frac{2\pi i k j}{n}}.
-\]
-
-This result generalizes to other Abelian groups, where the eigenvectors are given by the Fourier basis of the group.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Simulating continuous-time walks}
-Childs~\cite{childs2010relationship} and Berry, Childs, and Kothari~\cite{berry2015hamiltonian} showed that continuous-time quantum walks can be simulated using discrete-time quantum walks.
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \section*{Discrete-Time Quantum Walk on Cayley Graphs}
+
+% A discrete-time quantum walk on a Cayley graph requires a coin operator to maintain unitary evolution.
+
+% \subsection*{State Space}
+% The Hilbert space of the quantum walk is:
+% \[
+% \mathcal{H} = \mathcal{H}_G \otimes \mathcal{H}_C,
+% \]
+% where:
+% \begin{itemize}
+%     \item \( \mathcal{H}_G \) is the space spanned by group elements (vertices).
+%     \item \( \mathcal{H}_C \) is the coin space, which determines movement directions.
+% \end{itemize}
+
+% Each state is represented as:
+% \[
+% |\psi\rangle = \sum_{g \in G} \sum_{q \in Q} \alpha_{g,q} |g\rangle \otimes |q\rangle,
+% \]
+% where \( |g\rangle \) is the vertex state and \( |q\rangle \) represents the coin state.
+
+% \subsection*{Evolution Operators}
+% \textbf{Coin Flip Operator (\( C \))}: This unitary operator acts on the coin space to create a superposition of movement directions. A common choice is the Grover or Hadamard operator.
+
+% \textbf{Shift Operator (\( S \))}: Moves the walker according to the group structure:
+% \[
+% S |g\rangle \otimes |s\rangle = |gs\rangle \otimes |s\rangle.
+% \]
+% This means that if the walker is at vertex \( g \) with a coin state \( s \), it moves to \( gs \).
+
+% \textbf{Full Step Evolution}:
+% \[
+% U = S (C \otimes I),
+% \]
+% where \( U \) is the total unitary evolution per step.
+
+% The probability of finding the walker at a particular vertex \( g \) after \( t \) steps is given by:
+% \[
+% P(g, t) = \sum_{s \in S} |\langle g, s | \psi(t) \rangle |^2.
+% \]
+
+% \section*{Continuous-Time Quantum Walk on Cayley Graphs}
+
+% A continuous-time quantum walk on a Cayley graph follows a different evolution, governed by the Hamiltonian.
+
+% \subsection*{Hamiltonian and Evolution}
+% The evolution of the quantum walk is determined by the Schrödinger equation:
+% \[
+% i \frac{d}{dt} |\psi(t)\rangle = H |\psi(t)\rangle.
+% \]
+% Here, the Hamiltonian \( H \) is usually chosen as:
+% \[
+% H = A(\Gamma(G,S)),
+% \]
+% where \( A \) is the adjacency matrix of the Cayley graph:
+
+% \[
+% A_{g,h} =
+% \begin{cases}
+% 1, & \text{if } h = gs \text{ for some } s \in S, \\
+% 0, & \text{otherwise}.
+% \end{cases}
+% \]
+%  Alternatively, the Laplacian \( L \) can be used:
+% \[
+% H = L = D - A,
+% \]
+% where \( D \) is the degree matrix:
+
+% \[
+% D_{ij} =
+% \begin{cases}
+% \deg(v_i), & \text{if } i = j, \\
+% 0, & \text{otherwise}.
+% \end{cases}
+% \]
+
+% Here, \( \deg(v_i) \) is the degree of vertex \( v_i \), which is the number of edges connected to \( v_i \).
+
+% The solution to the quantum walk is given by:
+% \[
+% |\psi(t)\rangle = e^{-i H t} |\psi(0)\rangle.
+% \]
+% This means the probability amplitude at a vertex \( g \) spreads over time according to the unitary evolution operator \( e^{-i H t} \).
+
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \subsection*{Example: Cyclic Group \( \mathbb{Z}_n \)}
+
+% Consider the Cayley graph of \( \mathbb{Z}_n \) with generator set \( S = \{\pm 1\} \), which forms a cycle graph. The adjacency matrix is:
+% \[
+% A_{jk} =
+% \begin{cases}
+% 1, & \text{if } k = j \pm 1 \mod n, \\
+% 0, & \text{otherwise}.
+% \end{cases}
+% \]
+
+% Its eigenvalues are:
+% \[
+% \lambda_k = 2\cos\left(\frac{2\pi k}{n}\right),
+% \]
+% with eigenvectors given by the discrete Fourier transform (DFT) basis:
+% \[
+% \psi_k(j) = e^{\frac{2\pi i k j}{n}}.
+% \]
+
+% This result generalizes to other Abelian groups, where the eigenvectors are given by the Fourier basis of the group.
+
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \subsection{Simulating continuous-time walks}
+% Childs~\cite{childs2010relationship} and Berry, Childs, and Kothari~\cite{berry2015hamiltonian} showed that continuous-time quantum walks can be simulated using discrete-time quantum walks.
 Since our approach relies on their methods, we begin by outlining the relevant notation and framework.
 
-Let \( H \) be a Hamiltonian of dimension \( N = 2^n \), and define \( \opnorm{H}_{\mathrm{max}} = \max_{i, j} \abs{H_{ij}} \).
+% Let \( H \) be a Hamiltonian of dimension \( N = 2^n \), and define \( \opnorm{H}_{\mathrm{max}} = \max_{i, j} \abs{H_{ij}} \).
 To facilitate the simulation, we expand the Hilbert space from \( \C^N \) to \( \C^{2N} \otimes \C^{2N} \) by appending an ancilla qubit initialized to \( \ket{0} \) and duplicating the resulting space.
 
-To define the discrete-time walk operator, we first construct an orthonormal set of states:
-\begin{align}
-    \ket{\phi_{j0}} & := \frac{1}{\sqrt{d}} \sum_{\ell \in F_j} \ket{\ell} \left( \sqrt{\frac{H_{j\ell}^*}{K}} \ket{0} + \sqrt{1 - \frac{\abs{H_{j\ell}^*}}{K}} \ket{1} \right), \label{eq:walk-sim} \\
-    \ket{\phi_{j1}} & := \ket{0} \ket{1}, \nonumber
-\end{align}
-where \( F_j \) denotes the set of nonzero entries in column \( j \) of \( H \), and \( K \ge \opnorm{H}_{\mathrm{max}} \) is a fixed constant.
-
-Based on these states, we define the isometry \( T : \C^{2N} \to \C^{2N} \otimes \C^{2N} \) as follows:
-\begin{equation}
-    \label{eq:walk-isom}
-    T := \sum_{j = 0}^{N - 1} \sum_{b \in \{0, 1\}} (\ket{j}\bra{j} \otimes \ket{b}\bra{b}) \otimes \ket{\phi_{jb}}.
-\end{equation}
-
-The discrete-time quantum walk operator is then defined as
-\[
-W = iS(2TT^* - \mathds{1}),
-\]
-where \( S \) is the swap operator acting as
-\[
-S \ket{j_1} \ket{b_1} \ket{j_2} \ket{b_2} = \ket{j_2} \ket{b_2} \ket{j_1} \ket{b_1},
-\]
-for all \( 0 \le j_1, j_2 < N \) and \( b_1, b_2 \in \{0, 1\} \).
-
-To efficiently simulate the continuous-time evolution \( e^{-iHt} \), it suffices to implement the isometry \( T \), its adjoint \( T^* \), and the walk operator \( W \) efficiently.
+% To define the discrete-time walk operator, we first construct an orthonormal set of states:
+% \begin{align}
+%     \ket{\phi_{j0}} & := \frac{1}{\sqrt{d}} \sum_{\ell \in F_j} \ket{\ell} \left( \sqrt{\frac{H_{j\ell}^*}{K}} \ket{0} + \sqrt{1 - \frac{\abs{H_{j\ell}^*}}{K}} \ket{1} \right), \label{eq:walk-sim} \\
+%     \ket{\phi_{j1}} & := \ket{0} \ket{1}, \nonumber
+% \end{align}
+% where \( F_j \) denotes the set of nonzero entries in column \( j \) of \( H \), and \( K \ge \opnorm{H}_{\mathrm{max}} \) is a fixed constant.
+
+% Based on these states, we define the isometry \( T : \C^{2N} \to \C^{2N} \otimes \C^{2N} \) as follows:
+% \begin{equation}
+%     \label{eq:walk-isom}
+%     T := \sum_{j = 0}^{N - 1} \sum_{b \in \{0, 1\}} (\ket{j}\bra{j} \otimes \ket{b}\bra{b}) \otimes \ket{\phi_{jb}}.
+% \end{equation}
+
+% The discrete-time quantum walk operator is then defined as
+% \[
+% W = iS(2TT^* - \mathds{1}),
+% \]
+% where \( S \) is the swap operator acting as
+% \[
+% S \ket{j_1} \ket{b_1} \ket{j_2} \ket{b_2} = \ket{j_2} \ket{b_2} \ket{j_1} \ket{b_1},
+% \]
+% for all \( 0 \le j_1, j_2 < N \) and \( b_1, b_2 \in \{0, 1\} \).
+
+% To efficiently simulate the continuous-time evolution \( e^{-iHt} \), it suffices to implement the isometry \( T \), its adjoint \( T^* \), and the walk operator \( W \) efficiently.
 Assuming black-box (oracle) access to the entries of \( H \), the following result holds:
 
-\begin{theorem}[{\cite[Theorem 1]{berry2015hamiltonian}}]
-\label{thm:sparse-sim}
-Let \( H \) be a \( d \)-sparse Hamiltonian acting on \( n \) qubits. Then the unitary \( e^{-iHt} \) can be approximated to within error \( \epsilon \) using
-\[
-O\left( \tau \frac{\log(\tau / \epsilon)}{\log\log(\tau / \epsilon)} \right)
-\]
-queries to \( H \), and
-\[
-O\left( \tau \left[ n + \log^{5 / 2}(\tau / \epsilon) \right] \frac{\log(\tau / \epsilon)}{\log\log(\tau / \epsilon)} \right)
-\]
-additional elementary gates, where \( \tau = d \cdot \opnorm{H}_{\mathrm{max}} \cdot t \).
-\end{theorem}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Quantum walks from Group Actions}
-
-Let \( G \) be an abelian group, and let \( Q = \{q_1, q_2, \dots, q_k\} \subset G \) be a symmetric generating set, meaning that \( q \in Q \) if and only if \( -q \in Q \).
+% \begin{theorem}[{\cite[Theorem 1]{berry2015hamiltonian}}]
+% \label{thm:sparse-sim}
+% Let \( H \) be a \( d \)-sparse Hamiltonian acting on \( n \) qubits. Then the unitary \( e^{-iHt} \) can be approximated to within error \( \epsilon \) using
+% \[
+% O\left( \tau \frac{\log(\tau / \epsilon)}{\log\log(\tau / \epsilon)} \right)
+% \]
+% queries to \( H \), and
+% \[
+% O\left( \tau \left[ n + \log^{5 / 2}(\tau / \epsilon) \right] \frac{\log(\tau / \epsilon)}{\log\log(\tau / \epsilon)} \right)
+% \]
+% additional elementary gates, where \( \tau = d \cdot \opnorm{H}_{\mathrm{max}} \cdot t \).
+% \end{theorem}
+
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \subsection*{Quantum walks from Group Actions}
+
+% Let \( G \) be an abelian group, and let \( Q = \{q_1, q_2, \dots, q_k\} \subset G \) be a symmetric generating set, meaning that \( q \in Q \) if and only if \( -q \in Q \).
 The Cayley graph associated with \( G \) and \( Q \) is defined as \( \Gamma = (V, E) \), where the vertex set is \( V = G \), and the edge set consists of all pairs \( (a, b) \in G \times G \) such that \( b = q + a \) for some \( q \in Q \).
 
-The adjacency matrix \( A \) of \( \Gamma \) admits a spectral decomposition:
-\[
-A = \sum_{a \in G} \lambda_a \ket{\hat{a}} \bra{\hat{a}},
-\]
-where \( \ket{\hat{a}} \) denotes the quantum Fourier transform of \( \ket{a} \), and the eigenvalues \( \lambda_a \) are given by
-\[
-\lambda_a = \sum_{q \in Q} \chi(a, q).
-\]
-Importantly, the eigenvectors \( \ket{\hat{a}} \) depend solely on the group \( G \), not on the choice of the generating set \( Q \).
-
-Cayley graphs can also be generalized through group actions.
+% The adjacency matrix \( A \) of \( \Gamma \) admits a spectral decomposition:
+% \[
+% A = \sum_{a \in G} \lambda_a \ket{\hat{a}} \bra{\hat{a}},
+% \]
+% where \( \ket{\hat{a}} \) denotes the quantum Fourier transform of \( \ket{a} \), and the eigenvalues \( \lambda_a \) are given by
+% \[
+% \lambda_a = \sum_{q \in Q} \chi(a, q).
+% \]
+% Importantly, the eigenvectors \( \ket{\hat{a}} \) depend solely on the group \( G \), not on the choice of the generating set \( Q \).
+
+% Cayley graphs can also be generalized through group actions.
 Let \( (G, X, *) \) be a regular group action with a fixed element \( x \in X \), and let \( Q = \{q_1, q_2, \dots, q_k\} \subset G \) be a subset as before.
@@
 
-The adjacency matrix of this graph can be written as:
-\[
-A = \sum_{h \in G} \lambda_h \ket{G^{(h)} * x} \bra{G^{(h)} * x},
-\]
-where
-\[
-\lambda_h = \sum_{q \in Q} \chi(h, q), \quad \text{and} \quad \ket{G^{(h)} * x} = \frac{1}{\sqrt{|G|}} \sum_{g \in G} \chi(g, h) \ket{g * x}.
-\]
-
-As in the previous case, the eigenvectors \( \ket{G^{(h)} * x} \) are determined solely by the structure of the group \( G \).
+% The adjacency matrix of this graph can be written as:
+% \[
+% A = \sum_{h \in G} \lambda_h \ket{G^{(h)} * x} \bra{G^{(h)} * x},
+% \]
+% where
+% \[
+% \lambda_h = \sum_{q \in Q} \chi(h, q), \quad \text{and} \quad \ket{G^{(h)} * x} = \frac{1}{\sqrt{|G|}} \sum_{g \in G} \chi(g, h) \ket{g * x}.
+% \]
+
+% As in the previous case, the eigenvectors \( \ket{G^{(h)} * x} \) are determined solely by the structure of the group \( G \).
 This construction generalizes the standard Cayley graph: setting \( X = G \) and the group action \( * \) as group multiplication recovers the original definition.
 
-To see this, we have:
-
-\[
-    A\ket{G^{(h)}*x} = \frac{1}{\sqrt{|G|}}.\sum_{g \in G}\chi(g,h) A.\ket{g*x}
-    \]
-
-    \[
-    = A\ket{G^{(h)}*x} = \frac{1}{\sqrt{|G|}}.\sum_{g \in G}\chi(g,h)\sum_{q \in Q}\ket{q*(g*x)}
-    \]
-    Consider $\beta = qg$. Then:
-    \[
-    = = \frac{1}{\sqrt{|G|}}\sum_{q \in Q}\sum_{\beta \in G}\chi(\beta,h)\chi(q,h)\ket{\beta * x}
-    \]
-
-    \[
-    = \sum_{q \in Q}\chi(q,h).\ket{G^{(h)}*x} = \lambda_h \ket{G^{(h)}*x}
-    \]
-
-    Since the group action \( (G, X, *) \) is regular, the two Cayley graph constructions are isomorphic.
+% To see this, we have:
+
+% \[
+%     A\ket{G^{(h)}*x} = \frac{1}{\sqrt{|G|}}.\sum_{g \in G}\chi(g,h) A.\ket{g*x}
+%     \]
+
+%     \[
+%     = A\ket{G^{(h)}*x} = \frac{1}{\sqrt{|G|}}.\sum_{g \in G}\chi(g,h)\sum_{q \in Q}\ket{q*(g*x)}
+%     \]
+%     Consider $\beta = qg$. Then:
+%     \[
+%     = = \frac{1}{\sqrt{|G|}}\sum_{q \in Q}\sum_{\beta \in G}\chi(\beta,h)\chi(q,h)\ket{\beta * x}
+%     \]
+
+%     \[
+%     = \sum_{q \in Q}\chi(q,h).\ket{G^{(h)}*x} = \lambda_h \ket{G^{(h)}*x}
+%     \]
+
+%     Since the group action \( (G, X, *) \) is regular, the two Cayley graph constructions are isomorphic.
 In the first construction, the vertex set is \( G \), and the adjacency matrix is indexed by elements of \( G \).
@@
 The isomorphism between these graphs is given by the bijection
-\[
-\setlength{\arraycolsep}{1mm}
-\begin{array}{rcll}
-\phi: & G & \longrightarrow & X \\
-      & g & \longmapsto     & g * x,
-\end{array}
-\]
-
-which maps each group element \( g \in G \) to the corresponding point in its orbit under the action.
-
-    % Assuming the group action is a cryptographic group action, the isomorphism $\phi$ is a one-way function: given $g \in G$, it is easy to compute $g * x$, whereas given $(x, g * x)$, it is hard to compute $g$.
+% \[
+% \setlength{\arraycolsep}{1mm}
+% \begin{array}{rcll}
+% \phi: & G & \longrightarrow & X \\
+%       & g & \longmapsto     & g * x,
+% \end{array}
+% \]
+
+% which maps each group element \( g \in G \) to the corresponding point in its orbit under the action.
+
+%     % Assuming the group action is a cryptographic group action, the isomorphism $\phi$ is a one-way function: given $g \in G$, it is easy to compute $g * x$, whereas given $(x, g * x)$, it is hard to compute $g$.
 Therefore, although these graphs are mathematically the same, computational problems based on them require fundamentally different techniques.
@@
 This follows from the fact that
-    % \begin{equation}
-    %     \label{eq:adjmat-fb}
-    %     e^{-iAt} = \qft_G \sum_{a \in G} e^{-i\lambda_a t} \ket{a} \bra{a} \qft_G^*.
-    % \end{equation}
-    % The quantum Fourier transform $\qft_G$ and its inverse can be applied in $\poly(\log \abs{G})$ operations.
+%     % \begin{equation}
+%     %     \label{eq:adjmat-fb}
+%     %     e^{-iAt} = \qft_G \sum_{a \in G} e^{-i\lambda_a t} \ket{a} \bra{a} \qft_G^*.
+%     % \end{equation}
+%     % The quantum Fourier transform $\qft_G$ and its inverse can be applied in $\poly(\log \abs{G})$ operations.
 The diagonal unitary in the middle, which is a phase computation $\ket{a} \mapsto e^{-i\lambda_a t} \ket{a}$, is also efficient because $\lambda_a$ can be computed classically to arbitrary precision in $\poly(\log \abs{G})$ time.
 
-    % The situation for group actions is less straightforward.
+%     % The situation for group actions is less straightforward.
 While the states $\ket{G^{(h)} * x}$ are analogous to the states $\ket{\hat{h}}$, the involvement of the action $*$ in the former introduces computational challenges.
@@
 Instead, we are left with the spectral expression
-    % \[ e^{-iAt} = \sum_{h \in G} e^{-i\lambda_h t} \ket{G^{(h)} * x} \bra{G^{(h)} * x}. \]
-    % Despite this limitation, the sparsity and structure of the matrix $A$ allow us to demonstrate in the next section that for $t = \poly(\log \abs{G})$, the walk $e^{-iAt}$ can still be efficiently approximated to polynomial accuracy.
-
-    When the group action \( (G, X, *) \) is assumed to be cryptographic, the isomorphism \( \phi \) becomes a one-way function: given \( g \in G \), it is efficient to compute \( g * x \), but given the pair \( (x, g * x) \), it is computationally hard to recover \( g \).
+%     % \[ e^{-iAt} = \sum_{h \in G} e^{-i\lambda_h t} \ket{G^{(h)} * x} \bra{G^{(h)} * x}. \]
+%     % Despite this limitation, the sparsity and structure of the matrix $A$ allow us to demonstrate in the next section that for $t = \poly(\log \abs{G})$, the walk $e^{-iAt}$ can still be efficiently approximated to polynomial accuracy.
+
+%     When the group action \( (G, X, *) \) is assumed to be cryptographic, the isomorphism \( \phi \) becomes a one-way function: given \( g \in G \), it is efficient to compute \( g * x \), but given the pair \( (x, g * x) \), it is computationally hard to recover \( g \).
 As a result, while the two Cayley graphs are mathematically isomorphic, computational tasks associated with them may require fundamentally different approaches.
@@
 
-    From this point forward, we assume the generating set \( Q \) is small, i.e., \( \abs{Q} = \poly(\log \abs{G}) \).
+%     From this point forward, we assume the generating set \( Q \) is small, i.e., \( \abs{Q} = \poly(\log \abs{G}) \).
 In the first construction (where \( X = G \)), the walk \( e^{-iAt} \) can be efficiently implemented even for values of \( t \) that are exponentially large in \( \log \abs{G} \).
 This is a consequence of the identity:
-    \begin{equation}
-        \label{eq:adjmat-fb}
-        e^{-iAt} = \qft_G \left( \sum_{a \in G} e^{-i\lambda_a t} \ket{a} \bra{a} \right) \qft_G^*,
-    \end{equation}
-    where \( \qft_G \) and its inverse can be implemented in \( \poly(\log \abs{G}) \) time.
+%     \begin{equation}
+%         \label{eq:adjmat-fb}
+%         e^{-iAt} = \qft_G \left( \sum_{a \in G} e^{-i\lambda_a t} \ket{a} \bra{a} \right) \qft_G^*,
+%     \end{equation}
+%     where \( \qft_G \) and its inverse can be implemented in \( \poly(\log \abs{G}) \) time.
 Moreover, the diagonal phase unitary \( \ket{a} \mapsto e^{-i\lambda_a t} \ket{a} \) is also efficient to implement, since the eigenvalues \( \lambda_a \) can be computed classically to arbitrary precision in \( \poly(\log \abs{G}) \) time.
 
-    In contrast, the group-action setting presents greater computational difficulty.
+%     In contrast, the group-action setting presents greater computational difficulty.
 Although the states \( \ket{G^{(h)} * x} \) play a role analogous to the Fourier basis states \( \ket{\hat{h}} \), the presence of the action \( * \) makes the situation more subtle.
@@
 Instead, the best we can express is the spectral decomposition:
-    \[
-    e^{-iAt} = \sum_{h \in G} e^{-i\lambda_h t} \ket{G^{(h)} * x} \bra{G^{(h)} * x}.
-    \]
-
-    Despite this limitation, the adjacency matrix \( A \) retains a high degree of sparsity and algebraic structure.
+%     \[
+%     e^{-iAt} = \sum_{h \in G} e^{-i\lambda_h t} \ket{G^{(h)} * x} \bra{G^{(h)} * x}.
+%     \]
+
+%     Despite this limitation, the adjacency matrix \( A \) retains a high degree of sparsity and algebraic structure.
 In the next section, we will show that for \( t = \poly(\log \abs{G}) \), the walk \( e^{-iAt} \) can still be efficiently approximated to polynomial accuracy.
 
-    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\paragraph{Simulating group action quantum walks.}
-Assume \( t = \poly(\log \abs{G}) \).
+%     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% \paragraph{Simulating group action quantum walks.}
+% Assume \( t = \poly(\log \abs{G}) \).
 We show that the continuous-time walk \( W = e^{-iAt} \) can be efficiently simulated using the discrete-time quantum walk framework developed in~\cite{childs2010relationship, berry2015hamiltonian}.
@@
 To carry out the simulation, it suffices to show that the isometry \( T \), its adjoint \( T^* \), and the discrete-time walk operator
-\[
-W = iS(2TT^* - \mathds{1})
-\]
-can all be efficiently implemented in the group-action setting.
-
-Let \( \Gamma = (X, E) \) be the Cayley graph associated with the group action \( (G, X, *) \), and let \( A \) denote its adjacency matrix.
+% \[
+% W = iS(2TT^* - \mathds{1})
+% \]
+% can all be efficiently implemented in the group-action setting.
+
+% Let \( \Gamma = (X, E) \) be the Cayley graph associated with the group action \( (G, X, *) \), and let \( A \) denote its adjacency matrix.
 The Hamiltonian \( H \) of interest is simply \( A \), indexed by elements of \( X \).
 In this context, the isometry \( T \) takes the form:
-\begin{align*}
-T
-& := \sum_{y \in X} \sum_{b \in \{0, 1\}} (\ket{y}\bra{y} \otimes \ket{b}\bra{b}) \otimes \ket{\phi_{yb}} \\
-& = \sum_{y \in X} \sum_{b \in \{0, 1\}} \ket{y} \ket{b} \ket{\phi_{yb}} \bra{y} \bra{b}.
-\end{align*}
-
-Because of the structure of $\Gamma$, the states \eqref{eq:walk-sim} simplify as follows.
+% \begin{align*}
+% T
+% & := \sum_{y \in X} \sum_{b \in \{0, 1\}} (\ket{y}\bra{y} \otimes \ket{b}\bra{b}) \otimes \ket{\phi_{yb}} \\
+% & = \sum_{y \in X} \sum_{b \in \{0, 1\}} \ket{y} \ket{b} \ket{\phi_{yb}} \bra{y} \bra{b}.
+% \end{align*}
+
+% Because of the structure of $\Gamma$, the states \eqref{eq:walk-sim} simplify as follows.
 First, since the set $Q$ is symmetric, the graph $\Gamma$ is undirected and the adjacency matrix $A$ is symmetric with non-negative entries; the nonzero entries of $A$ are all equal to $1$.
@@
 As a result, for $y \in X$, the state $\ket{\phi_{y0}}$ becomes
-\[ \ket{\phi_{y0}} = \frac{1}{\sqrt{\abs{Q}}} \sum_{q \in Q} \ket{q * y} \ket{0}. \]
-We now describe how to implement the isometry \( T \) by constructing efficient unitaries \( U_0 \) and \( U_1 \), where each \( U_b \) acts as
-\[
-U_b : \ket{0} \ket{y, b} \ket{0, 0} \mapsto \ket{0} \ket{y, b} \ket{\phi_{yb}}, \quad b \in \{0, 1\},
-\]
-with the first register serving as an ancilla.
-
-The unitary \( U_1 \) is straightforward to implement, since \( \ket{\phi_{y1}} = \ket{0} \ket{1} \) is independent of \( y \). We now focus on the construction of \( U_0 \).
-
-Because \( Q \subset G \) is a small set (i.e., \( \abs{Q} = \poly(\log \abs{G}) \)), we can construct an efficient unitary \( V_Q : \C^Q \to \C^Q \) such that
-\[
-V_Q \ket{0} = \frac{1}{\sqrt{\abs{Q}}} \sum_{q \in Q} \ket{q}.
-\]
-Applying \( V_Q \otimes \mathds{1} \) to the state \( \ket{0} \ket{y, 0} \ket{0, 0} \) produces:
-\[
-\frac{1}{\sqrt{\abs{Q}}} \sum_{q \in Q} \ket{q} \ket{y, 0} \ket{0, 0}.
-\]
-
-Next, we apply the unitary \( V_1 \), defined by:
-\[
-V_1 : \ket{q} \ket{y, 0} \ket{0, 0} \mapsto \ket{q} \ket{y, 0} \ket{q * y, 0}.
-\]
-
-Following this, we uncompute the first register to recover \( \ket{0} \ket{y, 0} \ket{\phi_{y0}} \). This is achieved by applying the unitary \( V_2 \), defined as:
-\[
-V_2 : \ket{q} \ket{y, 0} \ket{q * y, 0} \mapsto \ket{0} \ket{y, 0} \ket{q * y, 0}.
-\]
-Since \( Q \) is small, we can efficiently determine \( q \) from the pair \( (y, q * y) \) by exhaustively checking each \( q \in Q \).
+% \[ \ket{\phi_{y0}} = \frac{1}{\sqrt{\abs{Q}}} \sum_{q \in Q} \ket{q * y} \ket{0}. \]
+% We now describe how to implement the isometry \( T \) by constructing efficient unitaries \( U_0 \) and \( U_1 \), where each \( U_b \) acts as
+% \[
+% U_b : \ket{0} \ket{y, b} \ket{0, 0} \mapsto \ket{0} \ket{y, b} \ket{\phi_{yb}}, \quad b \in \{0, 1\},
+% \]
+% with the first register serving as an ancilla.
+
+% The unitary \( U_1 \) is straightforward to implement, since \( \ket{\phi_{y1}} = \ket{0} \ket{1} \) is independent of \( y \). We now focus on the construction of \( U_0 \).
+
+% Because \( Q \subset G \) is a small set (i.e., \( \abs{Q} = \poly(\log \abs{G}) \)), we can construct an efficient unitary \( V_Q : \C^Q \to \C^Q \) such that
+% \[
+% V_Q \ket{0} = \frac{1}{\sqrt{\abs{Q}}} \sum_{q \in Q} \ket{q}.
+% \]
+% Applying \( V_Q \otimes \mathds{1} \) to the state \( \ket{0} \ket{y, 0} \ket{0, 0} \) produces:
+% \[
+% \frac{1}{\sqrt{\abs{Q}}} \sum_{q \in Q} \ket{q} \ket{y, 0} \ket{0, 0}.
+% \]
+
+% Next, we apply the unitary \( V_1 \), defined by:
+% \[
+% V_1 : \ket{q} \ket{y, 0} \ket{0, 0} \mapsto \ket{q} \ket{y, 0} \ket{q * y, 0}.
+% \]
+
+% Following this, we uncompute the first register to recover \( \ket{0} \ket{y, 0} \ket{\phi_{y0}} \). This is achieved by applying the unitary \( V_2 \), defined as:
+% \[
+% V_2 : \ket{q} \ket{y, 0} \ket{q * y, 0} \mapsto \ket{0} \ket{y, 0} \ket{q * y, 0}.
+% \]
+% Since \( Q \) is small, we can efficiently determine \( q \) from the pair \( (y, q * y) \) by exhaustively checking each \( q \in Q \).
 Thus, \( V_2 \) (and therefore \( U_0 \)) can be implemented efficiently.
 
-To implement \( U_0^* : \ket{0} \ket{y, 0} \ket{\phi_{y0}} \mapsto \ket{0} \ket{y, 0} \ket{0, 0} \), we sequentially apply \( V_2^* \), followed by \( V_1^* \), and finally \( V_Q^* \otimes \mathds{1} \).
+% To implement \( U_0^* : \ket{0} \ket{y, 0} \ket{\phi_{y0}} \mapsto \ket{0} \ket{y, 0} \ket{0, 0} \), we sequentially apply \( V_2^* \), followed by \( V_1^* \), and finally \( V_Q^* \otimes \mathds{1} \).
 Since each of these unitaries can be implemented efficiently, it follows that \( U_0^* \) is also efficient.
 
-We now construct the isometry \( T \) using a conditional unitary \( U_T \), which applies either \( U_0 \) or \( U_1 \) depending on the value of the qubit \( b \). That is,
-\[
-U_T = \text{Controlled-}U_b \quad \text{with control on } b \in \{0,1\}.
-\]
-
-Next, we demonstrate that the walk unitary
-\[
-W = iS(2TT^* - \mathds{1})
-\]
-can be applied efficiently. This reduces to implementing the reflection \( 2TT^* - \mathds{1} \), which we analyze as follows:
-\begin{align*}
-2\ket{0}\bra{0} \otimes TT^* - \mathds{1}
-&= 2\ket{0}\bra{0} \otimes \sum_{y \in X} \sum_{b \in \{0,1\}} \ket{y,b} \ket{\phi_{yb}} \bra{y,b} \bra{\phi_{yb}} - \mathds{1} \\
-&= 2\sum_{y \in X} \sum_{b \in \{0,1\}} \ket{0} \ket{y,b} \ket{\phi_{yb}} \bra{0} \bra{y,b} \bra{\phi_{yb}} - \mathds{1} \\
-&= U_T \left( 2 \sum_{y \in X} \sum_{b \in \{0,1\}} \ket{0} \ket{y,b} \ket{0,0} \bra{0} \bra{y,b} \bra{0,0} - \mathds{1} \right) U_T^* \\
-&= U_T \left( 2\ket{0}\bra{0} \otimes \mathds{1}_{X,b} \otimes \ket{0,0}\bra{0,0} - \mathds{1} \right) U_T^*.
-\end{align*}
-
-Since \( U_T \), \( U_T^* \), and the operator \( 2\ket{0}\bra{0} \otimes \mathds{1}_{X,b} \otimes \ket{0,0}\bra{0,0} - \mathds{1} \) can all be implemented efficiently, it follows that the reflection \( 2\ket{0}\bra{0} \otimes TT^* - \mathds{1} \) is also efficient.
-
-Finally, for any input state \( \ket{\psi} \), the reflection acts as:
-\[
-\left(2\ket{0}\bra{0} \otimes TT^* - \mathds{1} \right) \ket{0} \ket{\psi} = \ket{0} \left(2TT^* - \mathds{1} \right) \ket{\psi},
-\]
-confirming that the full walk operator \( W \) can be implemented efficiently in the group-action setting.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Applicaions}
-\section{Quantum Money}
-\section*{Introduction to Quantum Money}
-Quantum money is a revolutionary concept in cryptography that uses quantum mechanics to create a form of currency that is provably secure against forgery.
+% We now construct the isometry \( T \) using a conditional unitary \( U_T \), which applies either \( U_0 \) or \( U_1 \) depending on the value of the qubit \( b \). That is,
+% \[
+% U_T = \text{Controlled-}U_b \quad \text{with control on } b \in \{0,1\}.
+% \]
+
+% Next, we demonstrate that the walk unitary
+% \[
+% W = iS(2TT^* - \mathds{1})
+% \]
+% can be applied efficiently. This reduces to implementing the reflection \( 2TT^* - \mathds{1} \), which we analyze as follows:
+% \begin{align*}
+% 2\ket{0}\bra{0} \otimes TT^* - \mathds{1}
+% &= 2\ket{0}\bra{0} \otimes \sum_{y \in X} \sum_{b \in \{0,1\}} \ket{y,b} \ket{\phi_{yb}} \bra{y,b} \bra{\phi_{yb}} - \mathds{1} \\
+% &= 2\sum_{y \in X} \sum_{b \in \{0,1\}} \ket{0} \ket{y,b} \ket{\phi_{yb}} \bra{0} \bra{y,b} \bra{\phi_{yb}} - \mathds{1} \\
+% &= U_T \left( 2 \sum_{y \in X} \sum_{b \in \{0,1\}} \ket{0} \ket{y,b} \ket{0,0} \bra{0} \bra{y,b} \bra{0,0} - \mathds{1} \right) U_T^* \\
+% &= U_T \left( 2\ket{0}\bra{0} \otimes \mathds{1}_{X,b} \otimes \ket{0,0}\bra{0,0} - \mathds{1} \right) U_T^*.
+% \end{align*}
+
+% Since \( U_T \), \( U_T^* \), and the operator \( 2\ket{0}\bra{0} \otimes \mathds{1}_{X,b} \otimes \ket{0,0}\bra{0,0} - \mathds{1} \) can all be implemented efficiently, it follows that the reflection \( 2\ket{0}\bra{0} \otimes TT^* - \mathds{1} \) is also efficient.
+
+% Finally, for any input state \( \ket{\psi} \), the reflection acts as:
+% \[
+% \left(2\ket{0}\bra{0} \otimes TT^* - \mathds{1} \right) \ket{0} \ket{\psi} = \ket{0} \left(2TT^* - \mathds{1} \right) \ket{\psi},
+% \]
+% confirming that the full walk operator \( W \) can be implemented efficiently in the group-action setting.
+
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \section{Applicaions}
+% \section{Quantum Money}
+% \section*{Introduction to Quantum Money}
+% Quantum money is a revolutionary concept in cryptography that uses quantum mechanics to create a form of currency that is provably secure against forgery.
 Originally introduced by physicist Stephen Wiesner in the 1970s, quantum money represents one of the earliest proposed applications of quantum information science.
@@
 
-% \section*{How Quantum Money Works}
-% At its core, quantum money relies on two key principles of quantum mechanics: the \textit{no-cloning theorem} and the \textit{observer effect}.
-
-% \subsection*{Encoding Information in Quantum States}
-% \begin{itemize}
-%     \item Each quantum bill contains a unique quantum state, such as a set of qubits encoded in superposition.
-%     \item These states are generated and stored by the issuing authority (e.g., a central bank) using a secret algorithm.
-% \end{itemize}
-
-% \subsection*{Verification Process}
-% \begin{itemize}
-%     \item The issuing authority also generates a verification protocol, allowing a legitimate quantum bill to be authenticated.
-%     \item When a user presents a quantum bill for verification, the authority measures the encoded quantum states using the pre-determined protocol.
-%     \item If the measured states align with the expected values, the bill is deemed valid.
-% \end{itemize}
-
-% \subsection*{Unforgeability}
-% \begin{itemize}
-%     \item Due to the \textit{no-cloning theorem}, it is impossible to copy an unknown quantum state without altering it.
-%     \item Any attempt to measure or duplicate the quantum state results in a disturbance detectable during verification.
-% \end{itemize}
-
-% \section*{Key Principles Underpinning Quantum Money}
-% \begin{enumerate}
-%     \item \textbf{No-Cloning Theorem:} The no-cloning theorem states that an unknown quantum state cannot be perfectly copied.
+% % \section*{How Quantum Money Works}
+% % At its core, quantum money relies on two key principles of quantum mechanics: the \textit{no-cloning theorem} and the \textit{observer effect}.
+
+% % \subsection*{Encoding Information in Quantum States}
+% % \begin{itemize}
+% %     \item Each quantum bill contains a unique quantum state, such as a set of qubits encoded in superposition.
+% %     \item These states are generated and stored by the issuing authority (e.g., a central bank) using a secret algorithm.
+% % \end{itemize}
+
+% % \subsection*{Verification Process}
+% % \begin{itemize}
+% %     \item The issuing authority also generates a verification protocol, allowing a legitimate quantum bill to be authenticated.
+% %     \item When a user presents a quantum bill for verification, the authority measures the encoded quantum states using the pre-determined protocol.
+% %     \item If the measured states align with the expected values, the bill is deemed valid.
+% % \end{itemize}
+
+% % \subsection*{Unforgeability}
+% % \begin{itemize}
+% %     \item Due to the \textit{no-cloning theorem}, it is impossible to copy an unknown quantum state without altering it.
+% %     \item Any attempt to measure or duplicate the quantum state results in a disturbance detectable during verification.
+% % \end{itemize}
+
+% % \section*{Key Principles Underpinning Quantum Money}
+% % \begin{enumerate}
+% %     \item \textbf{No-Cloning Theorem:} The no-cloning theorem states that an unknown quantum state cannot be perfectly copied.
 This makes quantum money inherently secure, as counterfeiters cannot reproduce the quantum states encoded in legitimate currency.
-%     \item \textbf{Measurement Disturbance:} Observing or measuring a quantum state generally alters it.
+% %     \item \textbf{Measurement Disturbance:} Observing or measuring a quantum state generally alters it.
 This ensures that any unauthorized attempt to inspect the quantum money will render it invalid, as the encoded states will no longer match their original form.
-%     \item \textbf{Randomness and Superposition:} Quantum money utilizes superposition to encode information.
+% %     \item \textbf{Randomness and Superposition:} Quantum money utilizes superposition to encode information.
 For example, a single qubit in superposition may represent both $0$ and $1$ simultaneously until measured.
 The randomness of these states makes predicting or reproducing them without knowledge of the original encoding impossible.
-%     \item \textbf{Entanglement (Optional Feature):} Some implementations of quantum money involve quantum entanglement, where pairs of quantum states are interconnected.
+% %     \item \textbf{Entanglement (Optional Feature):} Some implementations of quantum money involve quantum entanglement, where pairs of quantum states are interconnected.
 Changes to one entangled state directly affect its pair, adding another layer of security against forgery.
-% \end{enumerate}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Benefits of Quantum Money}
-\begin{itemize}
-    \item \textbf{Unforgeable:} Classical currency, both physical and digital, can be counterfeited with enough effort and resources.
+% % \end{enumerate}
+
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \section*{Benefits of Quantum Money}
+% \begin{itemize}
+%     \item \textbf{Unforgeable:} Classical currency, both physical and digital, can be counterfeited with enough effort and resources.
 Quantum money, however, is fundamentally unforgeable due to the laws of quantum physics.
-    \item \textbf{Decentralized Verification:} In some theoretical models, quantum money can be verified without contacting the issuing authority, enabling decentralized systems for authentication.
-    \item \textbf{Enhanced Privacy:} The unique encoding of each quantum bill could allow for privacy-preserving transactions, as the details of the transaction need not be linked to the bill's verification.
-\end{itemize}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Quantum Money From Group Actions}
-A public-key quantum money scheme consists of two QPT algorithms: 
-\begin{itemize}
-\item $\gen(1^\lambda)$: This algorithm takes a security parameter $\lambda$ as input and outputs a pair $(s, \rho_s)$, where $s$ is a binary string called the serial number, and $\rho_s$ is a quantum state called the banknote.
+%     \item \textbf{Decentralized Verification:} In some theoretical models, quantum money can be verified without contacting the issuing authority, enabling decentralized systems for authentication.
+%     \item \textbf{Enhanced Privacy:} The unique encoding of each quantum bill could allow for privacy-preserving transactions, as the details of the transaction need not be linked to the bill's verification.
+% \end{itemize}
+
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \subsection{Quantum Money From Group Actions}
+% A public-key quantum money scheme consists of two QPT algorithms: 
+% \begin{itemize}
+% \item $\gen(1^\lambda)$: This algorithm takes a security parameter $\lambda$ as input and outputs a pair $(s, \rho_s)$, where $s$ is a binary string called the serial number, and $\rho_s$ is a quantum state called the banknote.
 The pair $(s, \rho_s)$, or simply $\rho_s$, is sometimes denoted by $\$$.
-\item $\ver(s, \rho_s)$ This algorithm takes a serial number and an alleged banknote as input and outputs either $1$ (accept) or $0$ (reject).
-\end{itemize}
-
-The quantum money scheme is said to be \textit{correct} if genuine banknotes generated by $\gen$ are accepted by $\ver$ with high probability. More formally:
-\[ \Pr[\ver(s, \rho_s) = 1 : (s, \rho_s) \gets \gen(1^\lambda)] \ge 1 - \negl(\lambda). \]
-where the probability is taken over the randomness of $\gen$ and $\ver$.
+% \item $\ver(s, \rho_s)$ This algorithm takes a serial number and an alleged banknote as input and outputs either $1$ (accept) or $0$ (reject).
+% \end{itemize}
+
+% The quantum money scheme is said to be \textit{correct} if genuine banknotes generated by $\gen$ are accepted by $\ver$ with high probability. More formally:
+% \[ \Pr[\ver(s, \rho_s) = 1 : (s, \rho_s) \gets \gen(1^\lambda)] \ge 1 - \negl(\lambda). \]
+% where the probability is taken over the randomness of $\gen$ and $\ver$.
 The scheme $(\gen, \ver)$ is said to be secure if, given a genuine bill $(s, \rho_s)$, no QPT algorithm $\mathcal{A}$ can produce two (possibly entangled) bills $(s, \rho_1)$ and $(s, \rho_2)$ that are both accepted by $\ver$ with non-negligible probability.
 More formally:
-\[ \Pr\left[ \ver(s, \rho_1) = \ver(s, \rho_2) = 1 : \substack{(s, \rho_s) \gets \gen(1^\lambda) \\ (\rho_1, \rho_2) \gets \mathcal{A}(s, \rho_s)} \right] \le \negl(\lambda). \]
-
-We now briefly outline the quantum money construction from \cite{zhandry2024quantum}, which is based on abelian group actions.
-Let $\{(G_\lambda, X_\lambda, *)\}_{\lambda \in J}$, where $J \subset \N$, be a collection of cryptographic group actions for abelian groups $G_\lambda$, and let $x_\lambda \in X_\lambda$ be a fixed element.
+% \[ \Pr\left[ \ver(s, \rho_1) = \ver(s, \rho_2) = 1 : \substack{(s, \rho_s) \gets \gen(1^\lambda) \\ (\rho_1, \rho_2) \gets \mathcal{A}(s, \rho_s)} \right] \le \negl(\lambda). \]
+
+% We now briefly outline the quantum money construction from \cite{zhandry2024quantum}, which is based on abelian group actions. We will the $\comph$ algorithm:
+% \paragraph{The $\comph$ Algorithm.}
+% Given access to the state $\ket{G^{(h)} * x}$, one can efficiently recover the value of $h$ via a quantum algorithm. In particular, there exists a unitary transformation that maps
+% \[
+% \ket{G^{(h)} * x} \ket{0} \mapsto \ket{G^{(h)} * x} \ket{h},
+% \]
+% leveraging the technique of \textit{phase kickback}. The process proceeds as follows:
+
+% Begin with the state $\ket{G^{(h)} * x} \ket{0}$ and apply the quantum Fourier transform (QFT) to the second register. Then apply the unitary operator
+% \[
+% \sum_{k \in G} U_k \otimes \ket{k}\bra{k}
+% \]
+% to both registers. This operation encodes the character information into the phase, resulting in the state
+% \[
+% \frac{1}{\sqrt{\abs{G}}} \sum_{k \in G} \ket{G^{(h)} * x} \chi(-k, h) \ket{k}.
+% \]
+% Finally, applying the inverse QFT to the second register disentangles the phase and reveals $h$, yielding the final state $\ket{G^{(h)} * x} \ket{h}$.
+
+% \vspace{0.5cm}
+% Let $\{(G_\lambda, X_\lambda, *)\}_{\lambda \in J}$, where $J \subset \N$, be a collection of cryptographic group actions for abelian groups $G_\lambda$, and let $x_\lambda \in X_\lambda$ be a fixed element.
 The $\gen$ and $\ver$ algorithms are as follows:
-\begin{itemize}
-\item $\gen(1^\lambda)$. Begin with the state $\ket{0}\ket{x_\lambda}$, and apply the quantum Fourier transform over $G_\lambda$ to the first register producing the superposition
-    \[ \frac{1}{\sqrt{\abs{G_\lambda}}} \sum_{g \in G_\lambda} \ket{g}\ket{x_\lambda}. \]
-    Next, apply the unitary transformation $\ket{h}\ket{y} \mapsto \ket{h}\ket{h * y}$ to this state, followed by the quantum Fourier transform on the first register. This results in
-    \[ \frac{1}{\abs{G_\lambda}} \sum_{h \in G_\lambda} \sum_{g \in G_\lambda} \chi(g, h) \ket{h}\ket{g * x_\lambda} = \frac{1}{\sqrt{\abs{G_\lambda}}} \sum_{h \in G_\lambda} \ket{h} \ket{G^{(h)} * x_\lambda} \]
-    where,
-    \[
-    \ket{G^{(h)}*x_\lambda} = \frac{1}{\sqrt{|G_\lambda|}}\sum_{g \in G_\lambda}\chi(g,h)\ket{g*x_\lambda}
-    \]
-    . Measure the first register to obtain a random $h \in G_\lambda$, collapsing the state to $\ket{G^{(h)} * x_\lambda}$. Return the pair $(h, \ket{G^{(h)} * x_\lambda})$.
-
-\item $\ver(h, \ket{\psi})$.
+% \begin{itemize}
+% \item $\gen(1^\lambda)$. Begin with the state $\ket{0}\ket{x_\lambda}$, and apply the quantum Fourier transform over $G_\lambda$ to the first register producing the superposition
+%     \[ \frac{1}{\sqrt{\abs{G_\lambda}}} \sum_{g \in G_\lambda} \ket{g}\ket{x_\lambda}. \]
+%     Next, apply the unitary transformation $\ket{h}\ket{y} \mapsto \ket{h}\ket{h * y}$ to this state, followed by the quantum Fourier transform on the first register. This results in
+%     \[ \frac{1}{\abs{G_\lambda}} \sum_{h \in G_\lambda} \sum_{g \in G_\lambda} \chi(g, h) \ket{h}\ket{g * x_\lambda} = \frac{1}{\sqrt{\abs{G_\lambda}}} \sum_{h \in G_\lambda} \ket{h} \ket{G^{(h)} * x_\lambda} \]
+%     where,
+%     \[
+%     \ket{G^{(h)}*x_\lambda} = \frac{1}{\sqrt{|G_\lambda|}}\sum_{g \in G_\lambda}\chi(g,h)\ket{g*x_\lambda}
+%     \]
+%     . Measure the first register to obtain a random $h \in G_\lambda$, collapsing the state to $\ket{G^{(h)} * x_\lambda}$. Return the pair $(h, \ket{G^{(h)} * x_\lambda})$.
+
+% \item $\ver(h, \ket{\psi})$.
 First, check whether $\ket{\psi}$ has support in $X_\lambda$.
@@
 If $h' = h$, return $1$; otherwise return $0$.
-\end{itemize}
-
-From this point forward, to simplify the notation, we make the security parameter $\lambda$ implicit, and use $G$ for $G_\lambda$, $X$ for $X_\lambda$, and so on.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Quantum Hartley Transform (QHT)}
-
-The \textbf{Quantum Hartley Transform (QHT)} is a linear unitary transform that operates on quantum states. It transforms the basis states \( |x\rangle \) as follows:
-\[
-|x\rangle \xrightarrow{\text{QHT}} \frac{1}{\sqrt{N}} \sum_{k=0}^{N-1} \text{cas}\left(\frac{2\pi x k}{N}\right) |k\rangle
-\]
-where:
-\begin{itemize}
-    \item \( x \) and \( k \) are integers in \( \{0, 1, \dots, N-1\} \),
-    \item \( \text{cas}(x) = \cos(x) + \sin(x) \),
-    \item \( N \) is the dimension of the transform, typically \( 2^n \) for \( n \)-qubit systems.
-\end{itemize}
-
-For a quantum state \( |\psi\rangle \) in an \( N \)-dimensional Hilbert space, represented as:
-\[
-|\psi\rangle = \sum_{x=0}^{N-1} \psi_x |x\rangle,
-\]
-the QHT transforms the state into:
-\[
-|\psi'\rangle = \text{QHT} |\psi\rangle = \frac{1}{\sqrt{N}} \sum_{k=0}^{N-1} \left( \sum_{x=0}^{N-1} \psi_x \, \text{cas}\left(\frac{2\pi x k}{N}\right) \right) |k\rangle.
-\]
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Properties of the QHT}
-\begin{enumerate}
-    \item \textbf{Unitary Transformation}: The QHT matrix \( U_{\text{QHT}} \) is unitary:
-    \[
-    U_{\text{QHT}} U_{\text{QHT}}^\dagger = I,
-    \]
-    preserving quantum state normalization.
-    \item \textbf{Symmetry}: The QHT is symmetric because \( \text{cas}(x) = \text{cas}(-x) \).
-    \item \textbf{Efficient Implementation}: Like the Quantum Fourier Transform (QFT), the QHT can be implemented with \( O(\log^2 N) \) gates for \( N = 2^n \).
-\end{enumerate}
-
-% \subsection*{Comparison with the Quantum Fourier Transform (QFT)}
-% The QFT and QHT differ in their transformation kernels:
+% \end{itemize}
+
+% From this point forward, to simplify the notation, we make the security parameter $\lambda$ implicit, and use $G$ for $G_\lambda$, $X$ for $X_\lambda$, and so on.
+
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \section*{Quantum Hartley Transform (QHT)}
+
+% The \textbf{Quantum Hartley Transform (QHT)} is a linear unitary transform that operates on quantum states. It transforms the basis states \( |x\rangle \) as follows:
+% \[
+% |x\rangle \xrightarrow{\text{QHT}} \frac{1}{\sqrt{N}} \sum_{k=0}^{N-1} \text{cas}\left(\frac{2\pi x k}{N}\right) |k\rangle
+% \]
+% where:
 % \begin{itemize}
-%     \item \textbf{QFT}:
-%     \[
-%     |x\rangle \xrightarrow{\text{QFT}} \frac{1}{\sqrt{N}} \sum_{k=0}^{N-1} e^{2\pi i x k / N} |k\rangle.
-%     \]
-%     \item \textbf{QHT}:
-%     \[
-%     |x\rangle \xrightarrow{\text{QHT}} \frac{1}{\sqrt{N}} \sum_{k=0}^{N-1} \left[\cos\left(\frac{2\pi x k}{N}\right) + \sin\left(\frac{2\pi x k}{N}\right)\right] |k\rangle.
-%     \]
+%     \item \( x \) and \( k \) are integers in \( \{0, 1, \dots, N-1\} \),
+%     \item \( \text{cas}(x) = \cos(x) + \sin(x) \),
+%     \item \( N \) is the dimension of the transform, typically \( 2^n \) for \( n \)-qubit systems.
 % \end{itemize}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Efficient implementation of Heartly transform}
-
-% Our algorithm for the quantum Hartley transform, $\qht_N$, is inspired by the recursive algorithm for computing the quantum Fourier transform ($\qft_N$).
+% For a quantum state \( |\psi\rangle \) in an \( N \)-dimensional Hilbert space, represented as:
+% \[
+% |\psi\rangle = \sum_{x=0}^{N-1} \psi_x |x\rangle,
+% \]
+% the QHT transforms the state into:
+% \[
+% |\psi'\rangle = \text{QHT} |\psi\rangle = \frac{1}{\sqrt{N}} \sum_{k=0}^{N-1} \left( \sum_{x=0}^{N-1} \psi_x \, \text{cas}\left(\frac{2\pi x k}{N}\right) \right) |k\rangle.
+% \]
+
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \subsection*{Properties of the QHT}
+% \begin{enumerate}
+%     \item \textbf{Unitary Transformation}: The QHT matrix \( U_{\text{QHT}} \) is unitary:
+%     \[
+%     U_{\text{QHT}} U_{\text{QHT}}^\dagger = I,
+%     \]
+%     preserving quantum state normalization.
+%     \item \textbf{Symmetry}: The QHT is symmetric because \( \text{cas}(x) = \text{cas}(-x) \).
+%     \item \textbf{Efficient Implementation}: Like the Quantum Fourier Transform (QFT), the QHT can be implemented with \( O(\log^2 N) \) gates for \( N = 2^n \).
+% \end{enumerate}
+
+% % \subsection*{Comparison with the Quantum Fourier Transform (QFT)}
+% % The QFT and QHT differ in their transformation kernels:
+% % \begin{itemize}
+% %     \item \textbf{QFT}:
+% %     \[
+% %     |x\rangle \xrightarrow{\text{QFT}} \frac{1}{\sqrt{N}} \sum_{k=0}^{N-1} e^{2\pi i x k / N} |k\rangle.
+% %     \]
+% %     \item \textbf{QHT}:
+% %     \[
+% %     |x\rangle \xrightarrow{\text{QHT}} \frac{1}{\sqrt{N}} \sum_{k=0}^{N-1} \left[\cos\left(\frac{2\pi x k}{N}\right) + \sin\left(\frac{2\pi x k}{N}\right)\right] |k\rangle.
+% %     \]
+% % \end{itemize}
+
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \subsection*{Efficient implementation of Heartly transform}
+
+% % Our algorithm for the quantum Hartley transform, $\qht_N$, is inspired by the recursive algorithm for computing the quantum Fourier transform ($\qft_N$).
 Let us briefly explain how the algorithm for $\qft_N$ works.
@@
 
-Our algorithm for the quantum Hartley transform, \( \qht_N \), is modeled after the recursive structure of the quantum Fourier transform algorithm \( \qft_N \).
+% Our algorithm for the quantum Hartley transform, \( \qht_N \), is modeled after the recursive structure of the quantum Fourier transform algorithm \( \qft_N \).
 To motivate this, we begin by reviewing the standard approach for computing \( \qft_N \).
@@
 
-\begin{align*}
-    \qft_N\ket{a}
-    & = \frac{1}{\sqrt{N}} \sum_{y = 0}^{N - 1} \omega_N^{ay}\ket{y} \\
-    & = \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \omega_N^{ay} \ket{y} + (-1)^a \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \omega_N^{ay} \ket{y + N/2} \\
-    & = \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \omega_N^{ay} \frac{1}{\sqrt{2}} (\ket{0} + (-1)^a \ket{1}) \ket{y}, \numberthis\label{eq:qft_alt}
-\end{align*}
-
-In the final expression, we have isolated the first qubit for clarity.
+% \begin{align*}
+%     \qft_N\ket{a}
+%     & = \frac{1}{\sqrt{N}} \sum_{y = 0}^{N - 1} \omega_N^{ay}\ket{y} \\
+%     & = \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \omega_N^{ay} \ket{y} + (-1)^a \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \omega_N^{ay} \ket{y + N/2} \\
+%     & = \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \omega_N^{ay} \frac{1}{\sqrt{2}} (\ket{0} + (-1)^a \ket{1}) \ket{y}, \numberthis\label{eq:qft_alt}
+% \end{align*}
+
+% In the final expression, we have isolated the first qubit for clarity.
 Let \( \ket{a} = \ket{t}\ket{b} \), where \( b \) denotes the least significant bit of \( a \), implying that \( a = 2t + b \) for some \( t \in \Z_{N / 2} \).
@@
 
-\[ \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \omega_N^{2ty} \ket{y} \ket{b}. \]
-Next, we apply the phase unitary \( P(y, b) \), defined by \( \ket{y} \ket{b} \mapsto \omega_N^{by} \ket{y} \ket{b} \), followed by a Hadamard transform on the final qubit.
+% \[ \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \omega_N^{2ty} \ket{y} \ket{b}. \]
+% Next, we apply the phase unitary \( P(y, b) \), defined by \( \ket{y} \ket{b} \mapsto \omega_N^{by} \ket{y} \ket{b} \), followed by a Hadamard transform on the final qubit.
 This results in the state given in Equation~\eqref{eq:qft_alt}.
 
-We now describe our algorithm for efficiently computing the quantum Hartley transform \( \qht_N \).
+% We now describe our algorithm for efficiently computing the quantum Hartley transform \( \qht_N \).
 The key idea is to leverage the recursive structure of \( \qht_N \), analogous to the strategy used for \( \qft_N \).
@@
 Our approach is as follows:
-\begin{equation}
-    \label{eq:cas-expand}
-	\frac{1}{\sqrt{N}} \sum_{y = 0}^{N - 1} \cas\Big( \frac{2\pi a y}{N} \Big) \ket{y}
-    = \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi a y}{N} \Big) \ket{y} + \frac{1}{\sqrt{N}} \sum_{y = N / 2}^{N - 1} \cas\Big( \frac{2\pi a y}{N} \Big) \ket{y}.
-\end{equation}
-
-The second summation on the right-hand side can be expressed as:
-\begin{align*}
-	\sum_{y = N / 2}^{N - 1} \cas\Big( \frac{2\pi a y}{N} \Big) \ket{y}
-    & = \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi a y}{N} + \pi a \Big) \ket{y + N/2} \\
-    & = (-1)^a \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi a y}{N} \Big) \ket{y + N/2},
-\end{align*}
-The second equality follows from the angle-sum identity for the \( \cas \) function,
-\[
-\cas(\alpha + \beta) = \cos(\alpha)\cas(\beta) + \sin(\alpha)\cas(-\beta),
-\]
-along with the fact that \( \cos(\pi a) = (-1)^a \) for all integers \( a \). Substituting this into Equation~\eqref{eq:cas-expand} yields:
-\begin{align}
-	\frac{1}{\sqrt{N}} \sum_{y = 0}^{N - 1} \cas\Big( \frac{2\pi a y}{N} \Big) \ket{y}
-    & = \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi a y}{N} \Big) (\ket{y} + (-1)^a \ket{y + N/2}) \nonumber \\
-    & = \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi a y}{N} \Big) \frac{1}{\sqrt{2}} (\ket{0} + (-1)^a \ket{1}) \ket{y}, \label{eq:qht-alt} 
-\end{align}
-In the final equality, the most significant qubit has been isolated to emphasize its contribution to the overall transformation.
-
-We now demonstrate how to compute \( \qht_N \) recursively.
+% \begin{equation}
+%     \label{eq:cas-expand}
+% 	\frac{1}{\sqrt{N}} \sum_{y = 0}^{N - 1} \cas\Big( \frac{2\pi a y}{N} \Big) \ket{y}
+%     = \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi a y}{N} \Big) \ket{y} + \frac{1}{\sqrt{N}} \sum_{y = N / 2}^{N - 1} \cas\Big( \frac{2\pi a y}{N} \Big) \ket{y}.
+% \end{equation}
+
+% The second summation on the right-hand side can be expressed as:
+% \begin{align*}
+% 	\sum_{y = N / 2}^{N - 1} \cas\Big( \frac{2\pi a y}{N} \Big) \ket{y}
+%     & = \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi a y}{N} + \pi a \Big) \ket{y + N/2} \\
+%     & = (-1)^a \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi a y}{N} \Big) \ket{y + N/2},
+% \end{align*}
+% The second equality follows from the angle-sum identity for the \( \cas \) function,
+% \[
+% \cas(\alpha + \beta) = \cos(\alpha)\cas(\beta) + \sin(\alpha)\cas(-\beta),
+% \]
+% along with the fact that \( \cos(\pi a) = (-1)^a \) for all integers \( a \). Substituting this into Equation~\eqref{eq:cas-expand} yields:
+% \begin{align}
+% 	\frac{1}{\sqrt{N}} \sum_{y = 0}^{N - 1} \cas\Big( \frac{2\pi a y}{N} \Big) \ket{y}
+%     & = \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi a y}{N} \Big) (\ket{y} + (-1)^a \ket{y + N/2}) \nonumber \\
+%     & = \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi a y}{N} \Big) \frac{1}{\sqrt{2}} (\ket{0} + (-1)^a \ket{1}) \ket{y}, \label{eq:qht-alt} 
+% \end{align}
+% In the final equality, the most significant qubit has been isolated to emphasize its contribution to the overall transformation.
+
+% We now demonstrate how to compute \( \qht_N \) recursively.
 For a given \( a \in \Z_N \), we decompose the basis state as \( \ket{a} = \ket{t}\ket{b} \), where \( b \) denotes the least significant bit, such that \( a = 2t + b \) for some \( t \in \Z_{N/2} \).
@@
 We then proceed as follows:
-\begin{align*}
-	\ket{0}\ket{t}\ket{b}
-    & \mapsto \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi t y}{N / 2} \Big) \ket{0} \ket{y} \ket{b} & (\mathds{1} \otimes \qht_{N / 2} \otimes \mathds{1}) \\
-    & = \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{4\pi t y}{N} \Big) \ket{0} \ket{y} \ket{b} \\
-    & \mapsto \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{4\pi t y}{N} \Big) (\ket{0} + \ket{1}) \ket{y}\ket{b}. & (H \otimes \mathds{1})
-\end{align*}
-Next, we apply a controlled negation operation, where the ancilla qubit is flipped if and only if the least significant bit \( b \) is equal to 1.
-\[
-    V: \ket{0}\ket{y} \mapsto \ket{0}\ket{y}, \quad \ket{1}\ket{y} \mapsto \ket{1}\ket{N / 2 -y},
-\]
-\[
-    \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{4\pi t y}{N} \Big) \ket{0} \ket{y} \ket{b} + \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{4\pi t y}{N} \Big) \ket{1} \ket{-y} \ket{b}.
-\]
-By performing a change of variables in the second summation and using the identity \( \cas\left(\frac{4\pi t (N / 2 - y)}{N}\right) = \cas\left(-\frac{4\pi t y}{N}\right) \), we obtain the state:
-\[
-    \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \Big( \cas\Big( \frac{4\pi t y}{N} \Big) \ket{0} + \cas\Big( -\frac{4\pi t y}{N} \Big) \ket{1} \Big) \ket{y} \ket{b}.
-\]
-
-We define the single-qubit rotation \( R(\theta) \) as the unitary operator acting on a single qubit given by:\begin{equation}
-    \label{eq:sine-rot}
-    R(y, b) = 
-    \begin{bmatrix}
-        \cos(2\pi b y / N) & \sin(2\pi b y / N) \\
-        -\sin(2\pi b y / N) & \cos(2\pi b y / N)
-    \end{bmatrix},
-\end{equation}
-Now, consider the unitary \( U_R \) defined by
-\[
-U_R : \ket{c}\ket{y}\ket{b} \mapsto \left(R(y, b)\ket{c}\right)\ket{y}\ket{b},
-\]
-where \( R(y, b) \) is a single-qubit rotation depending on \( y \) and \( b \). Applying \( U_R \) followed by the controlled negation \( V \), we obtain the state:
-\begin{align*}
-    \ket{\phi_1}
-    & = \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \Big( \cas\Big( \frac{2\pi ay}{N} \Big) \ket{0} + \cas\Big(-\frac{2\pi a(N /2 - y)}{N} \Big) \ket{1} \Big) \ket{y} \ket{b} \\
-    & = \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi ay}{N} \Big) \Big( \ket{0} + (-1)^b \ket{1} \Big) \ket{y} \ket{b},
-\end{align*}
-Here, we have used the identity \( \cas\left(-\pi a + \frac{2\pi a y}{N}\right) = (-1)^a \cas\left(\frac{2\pi a y}{N}\right) \), along with the fact that \( (-1)^a = (-1)^b \).
+% \begin{align*}
+% 	\ket{0}\ket{t}\ket{b}
+%     & \mapsto \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi t y}{N / 2} \Big) \ket{0} \ket{y} \ket{b} & (\mathds{1} \otimes \qht_{N / 2} \otimes \mathds{1}) \\
+%     & = \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{4\pi t y}{N} \Big) \ket{0} \ket{y} \ket{b} \\
+%     & \mapsto \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{4\pi t y}{N} \Big) (\ket{0} + \ket{1}) \ket{y}\ket{b}. & (H \otimes \mathds{1})
+% \end{align*}
+% Next, we apply a controlled negation operation, where the ancilla qubit is flipped if and only if the least significant bit \( b \) is equal to 1.
+% \[
+%     V: \ket{0}\ket{y} \mapsto \ket{0}\ket{y}, \quad \ket{1}\ket{y} \mapsto \ket{1}\ket{N / 2 -y},
+% \]
+% \[
+%     \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{4\pi t y}{N} \Big) \ket{0} \ket{y} \ket{b} + \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{4\pi t y}{N} \Big) \ket{1} \ket{-y} \ket{b}.
+% \]
+% By performing a change of variables in the second summation and using the identity \( \cas\left(\frac{4\pi t (N / 2 - y)}{N}\right) = \cas\left(-\frac{4\pi t y}{N}\right) \), we obtain the state:
+% \[
+%     \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \Big( \cas\Big( \frac{4\pi t y}{N} \Big) \ket{0} + \cas\Big( -\frac{4\pi t y}{N} \Big) \ket{1} \Big) \ket{y} \ket{b}.
+% \]
+
+% We define the single-qubit rotation \( R(\theta) \) as the unitary operator acting on a single qubit given by:\begin{equation}
+%     \label{eq:sine-rot}
+%     R(y, b) = 
+%     \begin{bmatrix}
+%         \cos(2\pi b y / N) & \sin(2\pi b y / N) \\
+%         -\sin(2\pi b y / N) & \cos(2\pi b y / N)
+%     \end{bmatrix},
+% \end{equation}
+% Now, consider the unitary \( U_R \) defined by
+% \[
+% U_R : \ket{c}\ket{y}\ket{b} \mapsto \left(R(y, b)\ket{c}\right)\ket{y}\ket{b},
+% \]
+% where \( R(y, b) \) is a single-qubit rotation depending on \( y \) and \( b \). Applying \( U_R \) followed by the controlled negation \( V \), we obtain the state:
+% \begin{align*}
+%     \ket{\phi_1}
+%     & = \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \Big( \cas\Big( \frac{2\pi ay}{N} \Big) \ket{0} + \cas\Big(-\frac{2\pi a(N /2 - y)}{N} \Big) \ket{1} \Big) \ket{y} \ket{b} \\
+%     & = \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi ay}{N} \Big) \Big( \ket{0} + (-1)^b \ket{1} \Big) \ket{y} \ket{b},
+% \end{align*}
+% Here, we have used the identity \( \cas\left(-\pi a + \frac{2\pi a y}{N}\right) = (-1)^a \cas\left(\frac{2\pi a y}{N}\right) \), along with the fact that \( (-1)^a = (-1)^b \).
 Applying the Hadamard transform to the first qubit yields:
-\[
-    \ket{\psi} = \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi ay}{N} \Big) \ket{b} \ket{y} \ket{b}
-\]
-Next, we uncompute the first qubit by applying a \textsc{CNOT} gate with the last qubit as control. We then apply a Hadamard transform followed by a swap operation, resulting in the state:
-\begin{align*}
-    \ket{\psi}
-    & \mapsto \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi ay}{N} \Big) \ket{0} \ket{y} \ket{b} & (\textsc{cnot}) \\
-    & \mapsto \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi ay}{N} \Big) \ket{0} \ket{y} \frac{1}{\sqrt{2}}(\ket{0} + (-1)^b \ket{1}) & (\mathds{1} \otimes H) \\
-    & = \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi ay}{N} \Big) \ket{0} \ket{y} \frac{1}{\sqrt{2}}(\ket{0} + (-1)^a \ket{1}). & ((-1)^b = (-1)^a) \\
-\end{align*}
-The final summation matches precisely with Equation~\eqref{eq:qht-alt}, which defines the quantum Hartley transform of \( \ket{a} \). Thus, we have successfully implemented the transformation:
-\[
-\ket{a} \mapsto \qht_N \ket{a}.
-\]
-\[ \ket{0}\ket{a} \mapsto \ket{0} \qht_N\ket{a}. \]
-The complete procedure is summarized in the following algorithm.
-
-\begin{algorithm}[$\qht_N$] \
-    \label{alg:qht-N}
-    \begin{description}[font = \normalfont\itshape, itemsep = 0mm, parsep = 0mm, topsep = 1mm]
-        \item [Input:] quantum state $\ket{\psi} \in \C^N$, where $N = 2^n$
-        \item [Output:] quantum state $\qht_N\ket{\psi}$
-    \end{description}
-
-    \begin{enumerate}[itemsep = 0mm, parsep = 1mm, topsep = 1mm]
-        \item Initialize an ancilla qubit to $0$ to obtain the state $\ket{0}\ket{\psi}$
-        \item Compute $\mathds{1} \otimes \qht_{N / 2} \otimes \mathds{1}$ recursively.
-        \item Apply $H \otimes \mathds{1}$.
-        \item\label{stp:ngt} Apply the controlled negation $\ket{0}\ket{y} \mapsto \ket{0}\ket{y}, \ket{1}\ket{y} \mapsto \ket{1}\ket{N / 2 -y}$ to the first two registers.
-        \item Apply the unitary $U_R$.
-        \item Apply $H \otimes \mathds{1}$
-        \item Apply \textsc{cnot} to the first and last qubits.
-        \item Apply $\mathds{1} \otimes H$.
-        \item Trace out the first qubit
-    \end{enumerate}
-\end{algorithm}
-
-\begin{theorem}
-    \label{thm:qht-cost}
-    Algorithm \ref{alg:qht-N} is correct and can be implemented using $\approx \log^2 N + O(\log N)$ elementary gates.
-\end{theorem}
-
-\begin{proof}
-    The correctness of the algorithm follows from the preceding discussion.
+% \[
+%     \ket{\psi} = \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi ay}{N} \Big) \ket{b} \ket{y} \ket{b}
+% \]
+% Next, we uncompute the first qubit by applying a \textsc{CNOT} gate with the last qubit as control. We then apply a Hadamard transform followed by a swap operation, resulting in the state:
+% \begin{align*}
+%     \ket{\psi}
+%     & \mapsto \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi ay}{N} \Big) \ket{0} \ket{y} \ket{b} & (\textsc{cnot}) \\
+%     & \mapsto \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi ay}{N} \Big) \ket{0} \ket{y} \frac{1}{\sqrt{2}}(\ket{0} + (-1)^b \ket{1}) & (\mathds{1} \otimes H) \\
+%     & = \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi ay}{N} \Big) \ket{0} \ket{y} \frac{1}{\sqrt{2}}(\ket{0} + (-1)^a \ket{1}). & ((-1)^b = (-1)^a) \\
+% \end{align*}
+% The final summation matches precisely with Equation~\eqref{eq:qht-alt}, which defines the quantum Hartley transform of \( \ket{a} \). Thus, we have successfully implemented the transformation:
+% \[
+% \ket{a} \mapsto \qht_N \ket{a}.
+% \]
+% \[ \ket{0}\ket{a} \mapsto \ket{0} \qht_N\ket{a}. \]
+% The complete procedure is summarized in the following algorithm.
+
+% \begin{algorithm}[$\qht_N$] \
+%     \label{alg:qht-N}
+%     \begin{description}[font = \normalfont\itshape, itemsep = 0mm, parsep = 0mm, topsep = 1mm]
+%         \item [Input:] quantum state $\ket{\psi} \in \C^N$, where $N = 2^n$
+%         \item [Output:] quantum state $\qht_N\ket{\psi}$
+%     \end{description}
+
+%     \begin{enumerate}[itemsep = 0mm, parsep = 1mm, topsep = 1mm]
+%         \item Initialize an ancilla qubit to $0$ to obtain the state $\ket{0}\ket{\psi}$
+%         \item Compute $\mathds{1} \otimes \qht_{N / 2} \otimes \mathds{1}$ recursively.
+%         \item Apply $H \otimes \mathds{1}$.
+%         \item\label{stp:ngt} Apply the controlled negation $\ket{0}\ket{y} \mapsto \ket{0}\ket{y}, \ket{1}\ket{y} \mapsto \ket{1}\ket{N / 2 -y}$ to the first two registers.
+%         \item Apply the unitary $U_R$.
+%         \item Apply $H \otimes \mathds{1}$
+%         \item Apply \textsc{cnot} to the first and last qubits.
+%         \item Apply $\mathds{1} \otimes H$.
+%         \item Trace out the first qubit
+%     \end{enumerate}
+% \end{algorithm}
+
+% \begin{theorem}
+%     \label{thm:qht-cost}
+%     Algorithm \ref{alg:qht-N} is correct and can be implemented using $\approx \log^2 N + O(\log N)$ elementary gates.
+% \end{theorem}
+
+% \begin{proof}
+%     The correctness of the algorithm follows from the preceding discussion.
 Except for the unitary \( U_R \) and the negation unitary in Step~\ref{stp:ngt}, all steps of the algorithm can be implemented using \( O(1) \) elementary gates.
@@
 
-    To implement the unitary \( U_R \), which requires constructing the conditional rotation operator \( R(y, b) \) for arbitrary \( y \) and \( b \), we make use of the two-qubit controlled rotations:
-    \[
-    R_j = \ket{0}\bra{0} \otimes \mathds{1} + \ket{1}\bra{1} \otimes
-    \begin{bmatrix}
-    \cos\left(\frac{2\pi 2^j}{N}\right) & \sin\left(\frac{2\pi 2^j}{N}\right) \\
-    -\sin\left(\frac{2\pi 2^j}{N}\right) & \cos\left(\frac{2\pi 2^j}{N}\right)
-    \end{bmatrix},
-    \]
-    for \( j = 0, 1, \dots, n - 1 \).
+%     To implement the unitary \( U_R \), which requires constructing the conditional rotation operator \( R(y, b) \) for arbitrary \( y \) and \( b \), we make use of the two-qubit controlled rotations:
+%     \[
+%     R_j = \ket{0}\bra{0} \otimes \mathds{1} + \ket{1}\bra{1} \otimes
+%     \begin{bmatrix}
+%     \cos\left(\frac{2\pi 2^j}{N}\right) & \sin\left(\frac{2\pi 2^j}{N}\right) \\
+%     -\sin\left(\frac{2\pi 2^j}{N}\right) & \cos\left(\frac{2\pi 2^j}{N}\right)
+%     \end{bmatrix},
+%     \]
+%     for \( j = 0, 1, \dots, n - 1 \).
 When \( b = 0 \), we have \( R(y, 0) = \mathds{1} \), and when \( b = 1 \), the operator \( R(y, 1) \) is the product of those \( R_j \) for which the \( j \)th bit of \( y \) is 1.
@@
 
-    Let \( T(N) \) denote the gate complexity of Algorithm~\ref{alg:qht-N} for an input of dimension \( N \).
+%     Let \( T(N) \) denote the gate complexity of Algorithm~\ref{alg:qht-N} for an input of dimension \( N \).
 Assuming access to the \( R_j \) gates as elementary operations, the recurrence relation becomes
-    \[
-    T(N) \approx T(N / 2) + 2\log N + O(1).
-    \]
-    Solving this recurrence yields \( T(N) \approx \log^2 N + O(\log N) \), as claimed.
-    \end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Quantum Money With The Hartley Transform}
-\label{sec:qm_hartley}
-
-The quantum money scheme described earlier can also be instantiated using the quantum Hartley transform in place of the quantum Fourier transform.
+%     \[
+%     T(N) \approx T(N / 2) + 2\log N + O(1).
+%     \]
+%     Solving this recurrence yields \( T(N) \approx \log^2 N + O(\log N) \), as claimed.
+%     \end{proof}
+
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \section{Quantum Money With The Hartley Transform}
+% \label{sec:qm_hartley}
+
+% The quantum money scheme described earlier can also be instantiated using the quantum Hartley transform in place of the quantum Fourier transform.
 However, this substitution disrupts the original verification procedure.
@@
 
-\begin{itemize}
-    \item \textbf{\( \gen \)}: Start with the state \( \ket{0}\ket{x} \), and apply the quantum Hartley transform over \( \Z_N \) to the first register, resulting in the superposition
-    \[
-    \frac{1}{\sqrt{N}} \sum_{g \in \Z_N} \ket{g}\ket{x}.
-    \]
-    Next, apply the unitary transformation \( \ket{h}\ket{y} \mapsto \ket{h}\ket{h * y} \), followed by a Hartley transform \( \qht_N \) on the first register. This yields the state
-    \[
-    \frac{1}{N} \sum_{h \in \Z_N} \sum_{g \in \Z_N} \cas\left(\frac{2\pi gh}{N}\right) \ket{h}\ket{g * x}
-    = \frac{1}{\sqrt{N}} \sum_{h \in \Z_N} \ket{h} \ket{\Z_N^{(h)} * x}_H,
-    \]
-    where
-    \[
-    \ket{\Z_N^{(h)} * x}_H = \frac{1}{\sqrt{N}} \sum_{g \in \Z_N} \cas\left(\frac{2\pi gh}{N}\right) \ket{g * x}.
-    \]
-    Measure the first register to obtain a random \( h \in \Z_N \), collapsing the state to \( \ket{\Z_N^{(h)} * x}_H \). Return the pair \( (h, \ket{\Z_N^{(h)} * x}_H) \).
-
-    \item \textbf{\( \ver(h, \ket{\psi}) \)}: First, check whether \( \ket{\psi} \) has support in \( X \).
+% \begin{itemize}
+%     \item \textbf{\( \gen \)}: Start with the state \( \ket{0}\ket{x} \), and apply the quantum Hartley transform over \( \Z_N \) to the first register, resulting in the superposition
+%     \[
+%     \frac{1}{\sqrt{N}} \sum_{g \in \Z_N} \ket{g}\ket{x}.
+%     \]
+%     Next, apply the unitary transformation \( \ket{h}\ket{y} \mapsto \ket{h}\ket{h * y} \), followed by a Hartley transform \( \qht_N \) on the first register. This yields the state
+%     \[
+%     \frac{1}{N} \sum_{h \in \Z_N} \sum_{g \in \Z_N} \cas\left(\frac{2\pi gh}{N}\right) \ket{h}\ket{g * x}
+%     = \frac{1}{\sqrt{N}} \sum_{h \in \Z_N} \ket{h} \ket{\Z_N^{(h)} * x}_H,
+%     \]
+%     where
+%     \[
+%     \ket{\Z_N^{(h)} * x}_H = \frac{1}{\sqrt{N}} \sum_{g \in \Z_N} \cas\left(\frac{2\pi gh}{N}\right) \ket{g * x}.
+%     \]
+%     Measure the first register to obtain a random \( h \in \Z_N \), collapsing the state to \( \ket{\Z_N^{(h)} * x}_H \). Return the pair \( (h, \ket{\Z_N^{(h)} * x}_H) \).
+
+%     \item \textbf{\( \ver(h, \ket{\psi}) \)}: First, check whether \( \ket{\psi} \) has support in \( X \).
 If not, return \( 0 \).
@@
 Return \( 1 \) if \( h' = h \), and \( 0 \) otherwise.
-\end{itemize}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Verification using quantum walks}
-
-Given a state of the form $\ket{\Z_N^{(h)} * x}_H$, we demonstrate how the value of $h$ can be extracted using continuous-time quantum walks.
-For any $u \in \Z_N$, consider the Cayley graph $\Gamma = (\Z_N, E)$ generated by $Q = {-u, u}$, as introduced in Section \ref{sec:ga-qwalk}.
+% \end{itemize}
+
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \section*{Verification using quantum walks}
+
+% Given a state of the form $\ket{\Z_N^{(h)} * x}_H$, we demonstrate how the value of $h$ can be extracted using continuous-time quantum walks.
+For any $u \in \Z_N$, consider the Cayley graph $\Gamma = (\Z_N, E)$ generated by $Q = {\{-u, u}\}$.
 Let $A$ denote the adjacency matrix of $\Gamma$.
@@
 
-\begin{lemma}
-    \label{lem:h-eigen}
-    The money state $\ket{\Z_N^{(h)} * x}_H$ is an eigenstate of $W$ with eigenvalue $e^{i\lambda_h t}$.
-\end{lemma}
-\begin{proof}
-    We have 
-    \begin{align*}
-        e^{iAt} \ket{\Z_N^{(h)} * x}_H
-        & = \sum_{g \in \Z_N} e^{i\lambda_gt} \ket{\Z_N^{(g)} * x} \braket{\Z_N^{(g)} * x}{\Z_N^{(h)} * x}_H \\
-        & = \sum_{g \in \Z_N} e^{i\lambda_gt} \ket{\Z_N^{(g)} * x} \bra{\Z_N^{(g)} * x} \Big( \frac{1 - i}{2} \ket{\Z_N^{(h)} * x} + \frac{1 + i}{2} \ket{\Z_N^{(-h)} * x} \Big) \\
-        & = e^{i\lambda_{h}t} \frac{1 - i}{2} \ket{\Z_N^{(h)} * x} + \frac{1 + i}{2} e^{i\lambda_{-h}t} \ket{\Z_N^{(-h)} * x} \\
-        & = e^{i\lambda_{h}t} \ket{\Z_N^{(h)} * x}_H,
-    \end{align*}
-    where the second equality follows from the identity in \eqref{eq:ht-ft}, and the last equality follows from the fact that $\lambda_h = \lambda_{-h}$.
-\end{proof}
-
-By setting \( t = \poly(\log N) \), Lemma~\ref{lem:h-eigen} ensures that phase estimation can be performed using the unitary \( W \) and the eigenstate \( \ket{\Z_N^{(h)} * x}_H \), yielding an approximation \( \tilde{\lambda}_h \) of \( \lambda_h \) such that
-\[
-\abs{\tilde{\lambda}_h - \lambda_h} \le \frac{1}{\poly(\log N)}.
-\]
-From this approximation, we can extract a real number \( 0 \le \theta \le 1 \) satisfying
-\[
-\abs*{\theta - \frac{uh}{N}} \le \frac{1}{\poly(\log N)}.
-\]
-Since phase estimation can be applied with various choices of \( u \), we can obtain multiple approximations of \( \frac{uh}{N} \).
+% \begin{lemma}
+%     \label{lem:h-eigen}
+%     The money state $\ket{\Z_N^{(h)} * x}_H$ is an eigenstate of $W$ with eigenvalue $e^{i\lambda_h t}$.
+% \end{lemma}
+% \begin{proof}
+%     We have 
+%     \begin{align*}
+%         e^{iAt} \ket{\Z_N^{(h)} * x}_H
+%         & = \sum_{g \in \Z_N} e^{i\lambda_gt} \ket{\Z_N^{(g)} * x} \braket{\Z_N^{(g)} * x}{\Z_N^{(h)} * x}_H \\
+%         & = \sum_{g \in \Z_N} e^{i\lambda_gt} \ket{\Z_N^{(g)} * x} \bra{\Z_N^{(g)} * x} \Big( \frac{1 - i}{2} \ket{\Z_N^{(h)} * x} + \frac{1 + i}{2} \ket{\Z_N^{(-h)} * x} \Big) \\
+%         & = e^{i\lambda_{h}t} \frac{1 - i}{2} \ket{\Z_N^{(h)} * x} + \frac{1 + i}{2} e^{i\lambda_{-h}t} \ket{\Z_N^{(-h)} * x} \\
+%         & = e^{i\lambda_{h}t} \ket{\Z_N^{(h)} * x}_H,
+%     \end{align*}
+%     where the second equality follows from the identity in \eqref{eq:ht-ft}, and the last equality follows from the fact that $\lambda_h = \lambda_{-h}$.
+% \end{proof}
+
+% By setting \( t = \poly(\log N) \), Lemma~\ref{lem:h-eigen} ensures that phase estimation can be performed using the unitary \( W \) and the eigenstate \( \ket{\Z_N^{(h)} * x}_H \), yielding an approximation \( \tilde{\lambda}_h \) of \( \lambda_h \) such that
+% \[
+% \abs{\tilde{\lambda}_h - \lambda_h} \le \frac{1}{\poly(\log N)}.
+% \]
+% From this approximation, we can extract a real number \( 0 \le \theta \le 1 \) satisfying
+% \[
+% \abs*{\theta - \frac{uh}{N}} \le \frac{1}{\poly(\log N)}.
+% \]
+% Since phase estimation can be applied with various choices of \( u \), we can obtain multiple approximations of \( \frac{uh}{N} \).
 As shown in~\cite{zhandry2024quantum}, selecting \( u \) appropriately allows us to reconstruct \( h \) exactly from these estimates.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\bibliographystyle{plain}
-\bibliography{references}
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% \newpage
+% \bibliographystyle{plain}
+% \bibliography{references}
 

### 2025-04-07 draft.tex
chapter 3 updated

@@
 \setlength{\parindent}{0pt}
-\onehalfspacing
+\singlespacing
 
@@
 
-% \section{Group Actions in Cryptography}
-
-% A \textbf{group action} of a group $G$ on a set $X$ is a function $*\colon G \times X \to X$ satisfying:
-% \begin{enumerate}
-%     \item Identity: $e * x = x$ for all $x \in X$,
-%     \item Compatibility: $g * (h * x) = (gh) * x$ for all $g,h \in G$, $x \in X$.
-% \end{enumerate}
-% We denote the result of $g$ acting on $x$ by $g * x$ or simply $gx$ when unambiguous.
-
-% \subsection{Regular Group Actions}
-
-% The orbit of $x \in X$ under $G$ is $G * x = \{g * x : g \in G\}$. The action is:
-% \begin{itemize}
-%     \item \emph{Transitive} if $G * x = X$,
-%     \item \emph{Free} if $g * x = x$ implies $g = e$,
-%     \item \emph{Regular} if both transitive and free.
-% \end{itemize}
-% In regular actions, $|X| = |G|$, and we can treat $X$ as a “hidden” version of $G$.
-
-% \subsection{Group Actions in Cryptography}
-
-% A \textbf{cryptographic group action} is one that is easy to compute in the forward direction but hard to invert. This gives rise to one-way functions based on group actions.
-
-% \paragraph{Example 1: Discrete Log.}  
-% $G = \mathbb{Z}_p^*$ acting on itself via $g * x = x^g \mod p$. Forward computation is efficient; inversion (discrete logarithm) is hard.
-
-% \paragraph{Example 2: Isogeny-Based.}  
-% $G$ is an ideal class group acting on supersingular elliptic curves.
-Given a base curve $x_0$ and an element $g \in G$, we compute $g * x_0$ efficiently, but recovering $g$ from $(x_0, g*x_0)$ is assumed hard.
-
-% \subsection{Applications to Quantum Money}
-
-% Cryptographic group actions enable public-key quantum money schemes.
-A private “serial number” $g \in G$ generates a quantum state based on $g * x_0$, which cannot be copied due to the no-cloning theorem and cannot be reverse-engineered due to the hardness of the action.
-
-% \subsection{Security Assumptions}
-
-% We assume abelian group actions $(G, X)$ satisfying:
-% \begin{itemize}
-%     \item Efficient action computation,
-%     \item Regularity: transitive and free,
-%     \item Hardness of inversion without the secret.
-% \end{itemize}
-
-% In particular, isogeny-based group actions are widely believed to be secure.
-We also refer to the \textbf{generic group model}, where group elements are treated as black-boxes with no special structure.
-Prior proofs (e.g., Doliskani's analysis of Zhandry’s scheme) in this model provide confidence in the cryptographic soundness of such constructions.
-
-% \chapter{Background of Quantum Computation and Group Actions}
-
-% \section{Quantum Computation Basics}
-% Quantum computation operates on information stored in quantum states.
-The fundamental unit of quantum information is the \emph{qubit}, which, unlike a classical bit, can exist in a superposition of basis states.
-A qubit is described by a state $|\psi\rangle = \alpha |0\rangle + \beta |1\rangle$ (in Dirac notation), where $\alpha,\beta \in \mathbb{C}$ and $|\alpha|^2 + |\beta|^2 = 1$.
-A system of $n$ qubits resides in a $2^n$-dimensional Hilbert space and its state can be a superposition of all $2^n$ basis basis states $|b_1b_2\cdots b_n\rangle$.
-
-% Computation is carried out by unitary transformations on these states.
-A quantum algorithm is typically a sequence of quantum gates (unitary operators) applied to an initial state (usually a simple basis state like $|00\cdots0\rangle$), followed by a measurement of some qubits to obtain a classical result.
-A crucial aspect of quantum computation is that certain transformations—such as the Fourier transform over an $N$-element group—can be implemented very efficiently on a quantum computer (in $\operatorname{poly}(\log N)$ time), whereas their classical counterparts might require $\operatorname{poly}(N)$ time.
-
-% One example important to this work is the \textbf{quantum Fourier transform} (QFT).
-For an abelian group $G$ of order $N$, the QFT is the unitary map $|g\rangle \mapsto \frac{1}{\sqrt{N}}\sum_{h \in G} \chi_h(g)\, |h\rangle$, where $\{\chi_h\}$ are the characters (complex exponential homomorphisms) of $G$.
-In more familiar terms, when $G = \mathbb{Z}_N$ (the integers mod $N$), the QFT takes $|j\rangle$ to $\frac{1}{\sqrt{N}}\sum_{k=0}^{N-1} e^{2\pi i j k / N} |k\rangle$.
-The QFT is a key component in many quantum algorithms, including Shor’s factoring algorithm and certain quantum money schemes (e.g., Zhandry’s) that rely on hiding information in phase relationships.
-The QFT can be implemented using $O((\log N)^2)$ basic gates for many groups [13], making it an efficient operation.
-
-% Another concept we will use is the \textbf{quantum Hartley transform} (QHT).
-The Hartley transform is an alternative to the Fourier transform that produces only real values (in the classical case) by using sinusoidal basis functions (sums of sine and cosine) instead of complex exponentials.
-The \emph{quantum} Hartley transform is the unitary transform corresponding to the classical Hartley transform.
-For example, the Hartley transform on $\mathbb{Z}_N$ maps a basis state $|j\rangle$ to $\frac{1}{\sqrt{N}}\sum_{k=0}^{N-1} \mathrm{cas}\!\Big(\frac{2\pi j k}{N}\Big)\, |k\rangle$, where $\mathrm{cas}(x) = \cos x + \sin x$ is the Hartley kernel.
-Because $\cos x + \sin x$ is real for all $x$, the resulting amplitudes are real numbers.
-We will discuss the Hartley transform in more detail in Chapter 5, including how to implement it efficiently on a quantum computer.
-
-% A final fundamental principle to note is the \textbf{no-cloning theorem}, which underpins the security of quantum money.
-This theorem states that there is no physical operation that can make a copy of an arbitrary unknown quantum state.
-This contrasts sharply with classical information, which can be copied freely.
-The no-cloning theorem means that an adversary cannot duplicate a quantum banknote without fundamentally disturbing it – any attempt to “clone” the state will fail unless the adversary already has complete classical information describing that state.
-
-% Throughout this thesis, when we refer to an algorithm as \emph{efficient} or \emph{feasible}, we typically mean it can be performed by a quantum polynomial-time (QPT) algorithm.
-This is analogous to classical polynomial time, but on a quantum computer.
-All of the algorithms we propose (minting, verification, quantum walk simulation, etc.) are intended to be efficient in this sense.
-
 \section{Group Actions in Cryptography}
@@
 
+Quantum walks are the quantum-mechanical counterparts of classical random walks on graphs.
+Instead of a probability distribution over vertices, a quantum walk evolves a superposition of vertex states.
+Interference between multiple paths leads to markedly different behavior from classical walks, often yielding faster spreading and algorithmic speedups~\cite{physics_stackexchange}.
+
+In particular, both major models of quantum walks --- continuous-time and discrete-time --- achieve \emph{ballistic spreading} (standard deviation growing linearly in time) in contrast to the diffusive $O(\sqrt{t})$ spread of classical random walks~\cite{childs2003quantum}.
+Quantum walks have become a central framework in quantum computing, underpinning various algorithms and even universal quantum computation~\cite{file_gwrqpr3gkui6gav6sze4dj}.
+
+In this chapter, we introduce continuous- and discrete-time quantum walks, compare their properties, and discuss their implementation on highly symmetric graphs known as Cayley graphs.
+We then explore how group actions and symmetry can be leveraged to analyze and construct quantum walks on these graphs.
+
+\section{Continuous-Time Quantum Walk}
+
+A \textbf{continuous-time quantum walk (CTQW)} is defined by a time-dependent Schrödinger equation on the vertices of a graph.
+Given a graph $G=(V,E)$ with $\abs{V}=N$ vertices, one assigns a basis state $\ket{j}$ to each vertex $j \in V$.
+The walk is governed by a Hermitian Hamiltonian $H$ that respects the graph's structure.
+A common choice is to take $H$ proportional to either the adjacency matrix $A$ of $G$ or the graph Laplacian $L$.
+For example, one may set
+\[
+H = \gamma A \quad \text{or} \quad H = \gamma L,
+\]
+where $\gamma$ is a constant coupling rate with dimensions of (time)$^{-1}$.
+
+The Hamiltonian connects adjacent vertices: $\bra{j}H\ket{k} \neq 0$ if and only if $(j,k) \in E$.
+The state of the walk $\ket{\psi(t)} = \sum_{j \in V} \psi_j(t) \ket{j}$ evolves according to the Schrödinger equation:
+\[
+i \frac{d}{dt} \ket{\psi(t)} = H \ket{\psi(t)},
+\]
+with formal solution
+\[
+\ket{\psi(t)} = e^{-iHt} \ket{\psi(0)}.
+\]
+
+In coordinates, if we use the Laplacian $L$ defined by $L_{jk} = -\deg(j)\delta_{jk} + A_{jk}$, the equation becomes
+\[
+i \frac{d}{dt} \psi_j(t) = \sum_{k \in V} L_{jk} \psi_k(t),
+\]
+which mirrors the equation of a classical continuous-time random walk except for the factor $i$.
+Since $L$ (and $A$) are Hermitian, the quantum dynamics are unitary and conserve total probability (i.e., the norm of the state vector), in contrast to the irreversible nature of classical diffusion.
+
+The continuous-time quantum walk model was first formalized by Farhi and Gutmann in 1998 as a quantum analogue of continuous Markov processes.
+
+\subsection{Hamiltonian Choices}
+
+One can equivalently define a CTQW using $H = A$ (the adjacency matrix) instead of the Laplacian.
+For an undirected $d$-regular graph, $L = dI - A$, and using $H=A$ introduces only an overall phase factor $e^{-i d t}$ in the evolution, since $dI$ contributes a global phase.
+Thus, on regular graphs, the choice of Laplacian versus adjacency matrix is unimportant up to a global phase.
+In general, the adjacency matrix is often used because it directly encodes graph connectivity.
+Farhi and Gutmann’s original construction corresponds to $H=A$.
+
+Throughout this thesis, we primarily consider $H = A$ for continuous-time walks on unweighted graphs.
+
+\subsection{Example – CTQW on a Hypercube}
+
+The $n$-dimensional Boolean hypercube $Q_n$ is the graph on $2^n$ vertices $\{0,1\}^n$, where edges connect vertices differing in one bit.
+This is a $d = n$ regular graph, and can be viewed as the Cayley graph of $(\mathbb{Z}_2)^n$ with the generating set consisting of flipping each bit.
+
+The adjacency matrix of $Q_n$ can be written as a sum of $n$ commuting terms, each acting on one bit:
+\[
+A_{Q_n} = \sum_{j=1}^{n} \sigma_x^{(j)},
+\]
+where $\sigma_x^{(j)}$ is the Pauli $X$ operator acting on the $j$-th bit (and identity on the others). Because all $\sigma_x^{(j)}$ commute, the time-evolution operator factorizes:
+\[
+e^{-i A_{Q_n} t} = \prod_{j=1}^{n} e^{-i \sigma_x^{(j)} t} = \bigotimes_{j=1}^{n} \left( \cos t \, I - i \sin t \, \sigma_x^{(j)} \right),
+\]
+yielding an analytical solution for the walk.
+In particular, starting from the state $\ket{0^n}$, the walker's state remains an even superposition over all vertices at Hamming distance $k$ at time $t$, with amplitudes given by the $k$-th term in the expansion of $(\cos t - i \sin t)^n$.
+
+This shows that the quantum walk spreads across the hypercube exponentially faster than a classical random walk, which requires $O(n \log n)$ steps to approach a uniform distribution.
+The hypercube example illustrates how symmetry (in this case, the direct product structure) enables explicit solutions.
+
+\subsection{Algorithmic Applications}
+
+Continuous-time quantum walks have been employed to achieve algorithmic speedups.
+A famous example is the \emph{glued trees traversal problem} by Childs et al.
+(2003), where a CTQW on a graph formed by two randomly "glued" binary trees can find the unique exit vertex exponentially faster than any classical algorithm.
+This result gave the first exponential separation between quantum and classical query complexity in a black-box setting.
+
+Another application is \emph{spatial search} on graphs.
+Childs and Goldstone (2004) showed that a CTQW can find a marked vertex on a $d$-dimensional lattice faster than classical diffusion.
+In the limit $d \to \infty$, the CTQW dynamics converge to the continuous Dirac equation.
+
+More generally, CTQWs provide a natural framework for quantum search algorithms on graphs, often achieving Grover-like speedups or better.
+It is also known that continuous-time quantum walks are \textbf{universal for quantum computation}, meaning that sufficiently complex graphs can encode arbitrary quantum logic operations.
+
+\section{Discrete-Time Quantum Walks}
+
+In a \textbf{discrete-time quantum walk (DTQW)}, evolution proceeds in discrete time steps.
+Formally, one defines a unitary step operator $U$ that is repeatedly applied to an initial state.
+Designing such a $U$ for an arbitrary graph is nontrivial, since a naive attempt to “jump to a random neighbor” quantumly is not unitary.
+
+The resolution is to enlarge the Hilbert space by introducing an auxiliary \emph{coin register} that provides additional degrees of freedom for unitary evolution.
+This model, first proposed by Watrous in the context of quantum graph algorithms, leads to the \emph{coined discrete-time quantum walk}.
+
+\subsection{Coined Quantum Walk}
+
+For a graph $G=(V,E)$, the state space is $\mathcal{H} = \mathbb{C}^{|V|} \otimes \mathbb{C}^d$, where $d$ is the maximum vertex degree (or a fixed value in regular graphs).
+A basis state $\ket{j,k}$ represents the walker at vertex $j$ with coin state $k$, where the coin index can be thought of as a label for one of $j$'s outgoing edges.
+
+Each step of the walk is a composition of two operations:
+\begin{enumerate}
+    \item A \emph{coin flip} $C$ acting on the coin register (possibly conditioned on the current vertex),
+    \item A \emph{shift} $S$ that moves the walker to a neighboring vertex determined by the coin state.
+\end{enumerate}
+
+In the case of a $d$-regular graph, a common choice is the Grover diffusion operator as the coin:
+\[
+C = \sum_{j \in V} \ket{j}\bra{j} \otimes C_j, \quad C_j := 2 \ket{\chi_j}\bra{\chi_j} - I_d,
+\]
+where $\ket{\chi_j} := \frac{1}{\sqrt{\deg(j)}} \sum_{k : (j,k) \in E} \ket{k}$ is the uniform superposition over the coin labels of neighbors of $j$.
+This is a Householder reflection about $\ket{\chi_j}$ and acts as a Grover diffusion operator on the coin space.
+
+Next, the shift operator $S$ acts as
+\[
+S \ket{j,k} = \ket{k,j}, \quad \text{for each } (j,k) \in E,
+\]
+i.e., if the coin state $k$ indicates a neighbor of $j$, the shift $S$ moves the walker to vertex $k$ and updates the coin to $j$. The overall unitary step of the walk is then:
+\[
+U = S C.
+\]
+
+By construction, $U$ is unitary and effects a “quantum hop” on the graph at each time step.
+On a regular graph, $C$ performs a uniform mixing over possible directions (like tossing a $d$-sided quantum coin), and $S$ implements a conditional shift.
+On irregular graphs, care must be taken to define appropriate coin spaces, or one may instead use Szegedy’s alternate framework.
+
+\subsection{Szegedy’s Walk}
+
+In 2004, Szegedy proposed a different formulation of DTQW based on classical Markov chains.
+Here, no coin register is needed.
+Instead, the walk is defined on $\mathbb{C}^N \otimes \mathbb{C}^N$, with basis states $\ket{j,k}$ corresponding to directed edges.
+
+Given a classical transition matrix $P$ (an $N \times N$ stochastic matrix), one defines:
+\[
+\ket{\psi_j} := \ket{j} \otimes \sum_k \sqrt{P_{kj}} \ket{k},
+\quad
+\Pi := \sum_j \ket{\psi_j}\bra{\psi_j}.
+\]
+Then the walk step is:
+\[
+U = S (2\Pi - I),
+\]
+where $S$ again swaps the two registers: $S\ket{j,k} = \ket{k,j}$.
+
+This construction yields a unitary $U$, and when $P_{kj} = \frac{1}{\deg(j)} A_{kj}$ (i.e., a symmetric random walk), Szegedy’s walk is equivalent to the coined model.
+
+Szegedy’s approach is especially useful for quantizing non-regular Markov chains and is widely used in algorithm design—for example, in the element distinctness problem.
+
+\subsection{Properties and Applications}
+
+Discrete-time quantum walks share many features with their continuous-time counterparts.
+On the infinite line, the standard coined walk (with Hadamard coin) spreads ballistically, creating a bimodal distribution, unlike the diffusive spread of a classical random walk.
+
+Both DTQW and CTQW have been used to achieve quadratic speedups in search problems.
+In many cases, the two models can simulate each other.
+DTQWs can even achieve \textbf{universal quantum computation}: Childs et al.
+(2009) constructed a coined DTQW that simulates an arbitrary quantum circuit.
+
+In practice, the coined model is convenient for quantum circuit implementations, as the step $U = SC$ can be decomposed into standard quantum gates.
+Experimental DTQW implementations have been realized on photonic and ion trap systems.
+
+An important feature of DTQWs is that their behavior depends sensitively on the choice of coin operator.
+Different coins can induce localization, ballistic spread, or symmetry breaking.
+This tunability can be exploited in algorithm design.
+By contrast, CTQWs have less flexibility since the Hamiltonian is fully determined by the graph.
+
+\section{Comparing Continuous and Discrete-Time Quantum Walks}
+
+Continuous- and discrete-time quantum walks are closely related, yet not strictly equivalent models.
+Both involve the interference of quantum amplitudes on a graph and can produce similar high-level behaviors, such as linear spreading and faster hitting times compared to classical random walks.
+In many algorithmic contexts, either model can be used to achieve a quantum speedup.
+
+However, several important distinctions exist between the two models:
+
+\subsection{State Space}
+
+\begin{itemize}
+    \item \textbf{CTQW:} Evolves on the vertex Hilbert space $\mathbb{C}^{|V|}$.
+    \item \textbf{DTQW (Coined):} Uses an enlarged space $\mathbb{C}^{|V|} \otimes \mathbb{C}^d$, introducing a coin register to enable unitary evolution.
+\end{itemize}
+
+The coin adds extra degrees of freedom, allowing more design flexibility.
+However, it also increases the complexity of analysis and implementation since one must choose both the coin and shift operators carefully to ensure desired evolution.
+
+\subsection{Time Evolution}
+
+\begin{itemize}
+    \item \textbf{CTQW:} Evolution is governed by the continuous-time Schrödinger equation: $\ket{\psi(t)} = e^{-iHt} \ket{\psi(0)}$, allowing probing at arbitrary real-valued times $t$.
+    \item \textbf{DTQW:} Evolves in discrete time-steps via a unitary operator $U$ applied iteratively: $\ket{\psi(t)} = U^t \ket{\psi(0)}$, with $t \in \mathbb{Z}$.
+\end{itemize}
+
+DTQWs can exhibit periodic revivals and step-dependent interference patterns, while CTQWs exhibit behavior determined by the spectral decomposition of $H$.
+A DTQW can approximate a CTQW through Trotterization: setting $U \approx e^{-iH \Delta t}$ for small $\Delta t$ and iterating.
+
+\subsection{Generality}
+
+\begin{itemize}
+    \item \textbf{CTQW:} Any undirected graph naturally defines a Hermitian Hamiltonian and thus a valid walk.
+    \item \textbf{DTQW:} For general (especially irregular) graphs, defining a local coinless unitary operator may be challenging.
+Enlarged Hilbert spaces or alternate frameworks like Szegedy's construction are often required.
+\end{itemize}
+
+While coined DTQWs require more setup, they are ultimately general, and Szegedy's method can handle any reversible Markov chain.
+
+\subsection{Analytical Tools}
+
+\begin{itemize}
+    \item \textbf{CTQW:} Analysis reduces to diagonalizing the Hermitian Hamiltonian $H$.
+    \item \textbf{DTQW:} One must diagonalize the larger unitary operator $U$, which may have a more intricate spectrum due to the coin space.
+\end{itemize}
+
+In both cases, analysis is often facilitated by symmetry.
+For example, when the underlying graph is a Cayley graph or has high symmetry, representation theory can be used to obtain explicit eigenstates and eigenvalues.
+
+\subsection{Equivalences}
+
+There exist formal correspondences between the two models. For instance:
+\begin{itemize}
+    \item A coined DTQW can approximate a CTQW in the limit of small time-steps (Childs et al.).
+    \item CTQWs can be embedded into DTQWs by using additional coin degrees of freedom to emulate continuous evolution.
+\end{itemize}
+
+Thus, the two models are equivalent in computational power. However, in practice, one may be more natural or efficient depending on the problem. For example:
+\begin{itemize}
+    \item \textbf{CTQW:} Favored for spatial search on low-degree graphs due to the natural definition of a marked Hamiltonian.
+    \item \textbf{DTQW:} Preferred for quantizing arbitrary Markov chains (e.g., element distinctness on the Johnson graph), particularly using Szegedy’s framework.
+\end{itemize}
+
+\subsection{Summary}
+
+Continuous-time and discrete-time quantum walks are powerful and related models for quantum computation and algorithm design.
+CTQWs rely on continuous evolution under a Hermitian Hamiltonian and are tightly linked to physical systems.
+DTQWs require coin and shift operators but offer additional control and ease of implementation in gate-based architectures.
+
+Each model has advantages:
+\begin{itemize}
+    \item CTQWs often more closely mirror physical intuition.
+    \item DTQWs offer greater flexibility and modularity for algorithm design.
+\end{itemize}
+
+Results in one model can often be translated to the other with suitable modifications. Consequently, both are indispensable tools in the study of quantum algorithms.
+
+\section{Cayley Graphs}
+
+Having introduced the two types of quantum walks, we now focus on walks on highly symmetric graphs that arise from group structures.
+A \textbf{Cayley graph} encodes the algebraic structure of a group in graph-theoretic form and provides a natural setting for analyzing quantum walks due to its symmetry properties.
+
+Let $G$ be a group with identity element $e$, and let $S \subset G$ be a generating set for $G$. The \emph{Cayley graph} $\Gamma(G,S)$ is defined as follows:
+\begin{itemize}
+    \item Each group element $g \in G$ corresponds to a vertex.
+    \item For each $g \in G$ and each generator $s \in S$, there is a directed edge from $g$ to $gs$. That is, $(g, gs)$ is an edge labeled by $s$.
+\end{itemize}
+
+If $S$ is symmetric (i.e., $s \in S \Rightarrow s^{-1} \in S$) and does not contain the identity, the graph can be treated as \textbf{undirected}, since for every edge from $g$ to $gs$, there is a corresponding edge back from $gs$ to $g$.
+
+When $S$ is symmetric, $\Gamma(G, S)$ is an undirected $|S|$-regular graph.
+Note that the Cayley graph depends on the choice of generating set $S$: different generating sets for the same group yield different graphs, though all share key symmetry features.
+
+\subsection{Examples of Cayley Graphs}
+
+\begin{itemize}
+    \item \textbf{Cycle Graph $C_n$:} The cycle graph is the Cayley graph of the cyclic group $\mathbb{Z}_n = \{0, 1, \dots, n-1\}$ with generating set $S = \{1, -1\}$.
+Each vertex $j \in \mathbb{Z}_n$ is connected to $j \pm 1 \mod n$.
+
+    \item \textbf{Hypercube $Q_n$:} The $n$-dimensional Boolean hypercube is the Cayley graph of the group $(\mathbb{Z}_2)^n$ with generating set $S = \{e_1, \dots, e_n\}$, where $e_i$ flips the $i$-th bit.
+This graph is $n$-regular and bipartite.
+
+    \item \textbf{Complete Graph $K_N$:} The complete graph on $N$ vertices can be viewed as the Cayley graph of $\mathbb{Z}_N$ with generating set $S = \{1, 2, \dots, N-1\}$ (all nonzero elements).
+Each vertex $g$ has an edge to every other vertex $g+s$.
+
+    \item \textbf{Infinite Tree (Free Group):} The free group on two generators $a$ and $b$ has a Cayley graph that is an infinite 4-regular tree.
+Each vertex corresponds to a word in $\{a^{\pm1}, b^{\pm1}\}$, and edges represent multiplication by $a$ or $b$.
+A finite portion of this graph is shown in Figure~\ref{fig:cayley-free-group}.
+
+    \item \textbf{Dihedral Groups:} Cayley graphs of dihedral groups often form cyclic or prism-like structures.
+These graphs are used in modeling symmetric structures in both classical and quantum settings.
+\end{itemize}
+
+\subsection{Symmetry and Group Action}
+
+Cayley graphs are highly symmetric. The group $G$ acts regularly on the vertices of $\Gamma(G, S)$ via left multiplication:
+\[
+g : h \mapsto gh.
+\]
+This action is:
+\begin{itemize}
+    \item \textbf{Vertex-transitive:} All vertices are structurally identical; there is no distinguished origin unless one is chosen explicitly.
+    \item \textbf{Regular:} For any two vertices $u, v \in G$, there exists exactly one $g \in G$ such that $g \cdot u = v$.
+\end{itemize}
+
+This symmetry implies that quantum (or classical) walks can often be analyzed by considering representative initial conditions—commonly, the walk is assumed to start at the identity element $e$.
+
+\subsection{Remarks}
+
+Cayley graphs provide a powerful framework for analyzing quantum walks.
+Their regularity and symmetry often lead to analytical tractability, particularly using representation theory and spectral techniques.
+Throughout this thesis, we will explore quantum walks on Cayley graphs, leveraging their symmetry to obtain insights into walk dynamics and algorithmic applications.
+
+\section{Quantum Walks on Cayley Graphs}
+
+Cayley graphs provide an ideal setting for quantum walks due to their rich symmetry properties, which can be exploited to simplify analysis and implementation.
+Both continuous-time and discrete-time quantum walks on Cayley graphs have been studied extensively.
+We now highlight several key features and advantages of quantum walks in this setting.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Spectral Structure}
+
+The adjacency matrix $A$ of a Cayley graph is closely related to the group algebra of $G$. It can be expressed as:
+\[
+A = \sum_{a \in G} \lambda_a |\hat{a}\rangle \langle \hat{a}|,
+\]
+where $|\hat{a}\rangle$ is the quantum Fourier transform of $|a\rangle$. The eigenvalues $\lambda$ are given by
+\[
+\lambda_a = \sum_{q \in Q} \chi(a, q).
+\]
+Note that the eigenvectors $|\hat{a}\rangle$ of $A$ depend only on $G$ and not on the set $Q$.
+
+To see this, we have
+\[
+        A\ket{\hat{a}} = A.\frac{1}{\sqrt{|G|}}\sum_{y \in G}\chi(a,y)\ket{y} = \frac{1}{\sqrt{|G|}}\sum_{y \in G}\chi(a,y).A\ket{y}
+        \]
+        \[
+        = \frac{1}{\sqrt{|G|}}\sum_{y \in G}\chi(a,y).\sum_{q \in Q}\ket{qy}
+        \]
+        Consider $\beta = qy$. Then:
+        \[
+         = \frac{1}{\sqrt{|G|}}\sum_{q \in Q}\chi(a,q)\sum_{\beta}\chi(a,\beta)\ket{\beta} = \sum_{q \in Q}\chi(a,q) . \ket{\hat{a}}
+        \]
+        \[
+         = \lambda_a\ket{\hat{a}}
+        \]
+
+% \[
+% A = \sum_{s \in S} P_s,
+% \]
+% where $P_s$ is the permutation matrix representing left multiplication by $s \in G$: $P_s \ket{g} = \ket{sg}$ for all $g \in G$.
+
+% If $S$ is symmetric (i.e., closed under inversion), then $A$ is Hermitian, and $P_s^\dagger = P_{s^{-1}}$.
+The eigenstates of $A$ are understood through group representation theory.
+In particular, the regular representation of $G$ on $\mathbb{C}^{|G|}$ decomposes into a direct sum of irreducible representations (irreps), and since each $P_s$ acts via the regular representation, the adjacency matrix $A$ is a sum of representation operators:
+% \[
+% A = \sum_{s \in S} \rho(s),
+% \]
+% where $\rho$ denotes the regular representation.
+
+% By Schur’s lemma, $A$ acts within each irreducible subspace as a matrix proportional to the representation of $S$.
+Hence, $A$ is block-diagonal (in a suitable basis), with blocks corresponding to irreps of $G$.
+If $\{\phi_\alpha\}$ are the irreps of $G$, then the eigenvalues of $A$ can be determined from the character values $\chi_\alpha(s)$:
+% \[
+% \lambda_\alpha = \sum_{s \in S} \chi_\alpha(s), \quad \text{(for abelian $G$, $\chi_\alpha$ is a character)}.
+% \]
+
+% In the case of abelian $G$, all irreps are one-dimensional, and the eigenstates of $A$ are the Fourier basis:
+% \[
+% \ket{\chi} = \frac{1}{\sqrt{|G|}} \sum_{g \in G} \chi(g) \ket{g}, \quad \lambda_\chi = \sum_{s \in S} \chi(s).
+% \]
+
+% \textbf{Example – Hypercube:} For $G = \mathbb{Z}_2^n$, characters are labeled by bitstrings $u \in \{0,1\}^n$, and $\chi_u(g) = (-1)^{u \cdot g}$. Then
+% \[
+% \lambda_u = \sum_{j=1}^n (-1)^{u_j},
+% \]
+% which gives the $n+1$ distinct eigenvalues $n, n-2, \dots, -n$ of the $n$-dimensional hypercube.
+
+% In the nonabelian case, similar principles apply but require using higher-dimensional irreps and the Great Orthogonality Theorem.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Invariant Subspaces and Symmetry Reduction}
+
+Cayley graphs possess vertex-transitive symmetry under the group action $g : h \mapsto gh$.
+This symmetry induces invariant subspaces for the quantum walk evolution.
+If the initial state is uniform over a symmetry orbit, it remains so under the walk.
+
+In particular, for a continuous-time quantum walk starting at the identity element:
+\[
+\ket{\psi(t)} = e^{-iAt} \ket{e},
+\]
+the resulting state remains a \emph{class function}, i.e., the amplitude $\braket{g|\psi(t)}$ depends only on structural properties of $g$ (such as Hamming weight or conjugacy class).
+
+This symmetry drastically reduces the effective state space.
+For instance, on distance-regular graphs (including many Cayley graphs), amplitudes are equal for all vertices at the same distance from the starting point.
+This idea is also used in the analysis of the glued trees graph, where the walk remains uniform on each layer.
+
+\subsection{Hitting and Mixing Properties}
+
+Quantum walks on Cayley graphs have been applied to study hitting and mixing times.
+In the classical case, random walks on many Cayley graphs are rapidly mixing (e.g., those based on nonabelian simple groups, which often form expanders).
+
+In the quantum case, mixing is more subtle due to unitary evolution.
+One typically considers \emph{instantaneous} or \emph{time-averaged} mixing.
+Some Cayley graphs support perfect state transfer or periodicity in CTQWs.
+
+\textbf{Examples:}
+\begin{itemize}
+    \item On the cycle graph $C_n$, a CTQW exhibits perfect revival at time $t = \pi$ if $n$ is even.
+    \item On the hypercube, the CTQW exhibits approximate uniform mixing at specific times.
+\end{itemize}
+
+These properties are derived from the spectral structure, which is accessible via group characters.
+
+\subsection{Discrete-Time Walks and Symmetry}
+
+Coined DTQWs also benefit from Cayley graph symmetry. If a symmetric coin (e.g., the Grover coin) is used at each vertex of a vertex-transitive graph, the walk respects the full symmetry. As a result:
+\begin{itemize}
+    \item Amplitudes often remain uniform on symmetry-equivalent vertices.
+    \item Walk dynamics can often be analyzed by reducing to a lower-dimensional invariant subspace.
+    \item In some cases, symmetry can lead to \emph{localization}, where amplitude becomes trapped due to spectral properties of the coin.
+\end{itemize}
+
+These effects can be mitigated or exploited through careful coin design or by using Szegedy's method, which naturally respects symmetry.
+
+\subsection{Summary}
+
+Cayley graphs offer a rich and powerful structure for quantum walks. Their group-theoretic properties allow:
+\begin{itemize}
+    \item Spectral analysis via irreducible representations.
+    \item Dimensionality reduction using symmetry and invariant subspaces.
+    \item Explicit calculation of probabilities, mixing behavior, and hitting times.
+\end{itemize}
+
+Many efficient quantum walk algorithms exploit these properties either directly or implicitly.
+In subsequent sections, we will explore quantum walks on more general structures where group actions go beyond simple Cayley graphs.
+
+\section{Cayley Graphs with Group Action}
+
+Cayley graphs can also be generalized through group actions.
+Let \( (G, X, *) \) be a regular group action with a fixed element \( x \in X \), and let \( Q = \{q_1, q_2, \dots, q_k\} \subset G \) be a subset as before.
+Define the Cayley graph \( \Gamma = (X, E) \), where the vertex set is \( X \), and the edge set consists of all pairs \( (x, y) \in X \times X \) such that \( y = q * x \) for some \( q \in Q \).
+
+The adjacency matrix of this graph can be written as:
+\[
+A = \sum_{h \in G} \lambda_h \ket{G^{(h)} * x} \bra{G^{(h)} * x},
+\]
+where
+\[
+\lambda_h = \sum_{q \in Q} \chi(h, q), \quad \text{and} \quad \ket{G^{(h)} * x} = \frac{1}{\sqrt{|G|}} \sum_{g \in G} \chi(g, h) \ket{g * x}.
+\]
+
+As in the previous case, the eigenvectors \( \ket{G^{(h)} * x} \) are determined solely by the structure of the group \( G \).
+This construction generalizes the standard Cayley graph: setting \( X = G \) and the group action \( * \) as group multiplication recovers the original definition.
+
+To see this, we have:
+
+\[
+    A\ket{G^{(h)}*x} = \frac{1}{\sqrt{|G|}}.\sum_{g \in G}\chi(g,h) A.\ket{g*x}
+    \]
+
+    \[
+    = A\ket{G^{(h)}*x} = \frac{1}{\sqrt{|G|}}.\sum_{g \in G}\chi(g,h)\sum_{q \in Q}\ket{q*(g*x)}
+    \]
+    Consider $\beta = qg$. Then:
+    \[
+    = = \frac{1}{\sqrt{|G|}}\sum_{q \in Q}\sum_{\beta \in G}\chi(\beta,h)\chi(q,h)\ket{\beta * x}
+    \]
+
+    \[
+    = \sum_{q \in Q}\chi(q,h).\ket{G^{(h)}*x} = \lambda_h \ket{G^{(h)}*x}
+    \]
+
+    Since the group action \( (G, X, *) \) is regular, the two Cayley graph constructions are isomorphic.
+In the first construction, the vertex set is \( G \), and the adjacency matrix is indexed by elements of \( G \).
+In the second construction, the vertex set is \( X \), with the adjacency matrix indexed by elements of \( X \).
+The isomorphism between these graphs is given by the bijection
+\[
+\setlength{\arraycolsep}{1mm}
+\begin{array}{rcll}
+\phi: & G & \longrightarrow & X \\
+      & g & \longmapsto     & g * x,
+\end{array}
+\]
+
+which maps each group element \( g \in G \) to the corresponding point in its orbit under the action.
+
+    % Assuming the group action is a cryptographic group action, the isomorphism $\phi$ is a one-way function: given $g \in G$, it is easy to compute $g * x$, whereas given $(x, g * x)$, it is hard to compute $g$.
+Therefore, although these graphs are mathematically the same, computational problems based on them require fundamentally different techniques.
+A notable example is the implementation of quantum walks on these graphs.\footnote{Implementations of continuous-time quantum walks in the context of cryptographic group actions have previously appeared in \cite{booher2024failing, doliskani2023sample}, in the setting of supersingular isogeny graphs.
+These walks can be interpreted as group-action walks.} From this point onward, assume $Q$ is a small set, i.e., $\abs{Q} = \poly(\log \abs{G})$.
+In the first graph, we can efficiently implement the walks $e^{-iAt}$ even for values of $t$ that are exponentially large in $\log \abs{G}$.
+This follows from the fact that
+    % \begin{equation}
+    %     \label{eq:adjmat-fb}
+    %     e^{-iAt} = \qft_G \sum_{a \in G} e^{-i\lambda_a t} \ket{a} \bra{a} \qft_G^*.
+    % \end{equation}
+    % The quantum Fourier transform $\qft_G$ and its inverse can be applied in $\poly(\log \abs{G})$ operations.
+The diagonal unitary in the middle, which is a phase computation $\ket{a} \mapsto e^{-i\lambda_a t} \ket{a}$, is also efficient because $\lambda_a$ can be computed classically to arbitrary precision in $\poly(\log \abs{G})$ time.
+
+    % The situation for group actions is less straightforward.
+While the states $\ket{G^{(h)} * x}$ are analogous to the states $\ket{\hat{h}}$, the involvement of the action $*$ in the former introduces computational challenges.
+Specifically, it becomes hard to apply transformations beyond the action $\ket{y} \mapsto \ket{a * y}$ for $a \in G$.
+Consequently, no decomposition analogous to \eqref{eq:adjmat-fb} exists in the context of group actions.
+Instead, we are left with the spectral expression
+    % \[ e^{-iAt} = \sum_{h \in G} e^{-i\lambda_h t} \ket{G^{(h)} * x} \bra{G^{(h)} * x}. \]
+    % Despite this limitation, the sparsity and structure of the matrix $A$ allow us to demonstrate in the next section that for $t = \poly(\log \abs{G})$, the walk $e^{-iAt}$ can still be efficiently approximated to polynomial accuracy.
+
+    When the group action \( (G, X, *) \) is assumed to be cryptographic, the isomorphism \( \phi \) becomes a one-way function: given \( g \in G \), it is efficient to compute \( g * x \), but given the pair \( (x, g * x) \), it is computationally hard to recover \( g \).
+As a result, while the two Cayley graphs are mathematically isomorphic, computational tasks associated with them may require fundamentally different approaches.
+A particularly illustrative example is the implementation of quantum walks on these graphs.\footnote{Continuous-time quantum walks have been explored in the context of cryptographic group actions in~\cite{booher2024failing, doliskani2023sample}, specifically in supersingular isogeny graphs.
+These walks can be viewed as group-action quantum walks.}
+
+% The concept of a Cayley graph generalizes naturally to the case of a group acting on an arbitrary set.
+Suppose a group $G$ acts transitively on a set $X$, and let $S \subset G$ be a generating set.
+We can construct a graph, often referred to as a \textbf{Schreier graph}, denoted $\Gamma(X; G, S)$, as follows:
+% \begin{itemize}
+%     \item The vertex set is $X$.
+%     \item For each $x \in X$ and each $s \in S$, there is an edge from $x$ to $s \cdot x$.
+% \end{itemize}
+
+% This graph encodes the action of $G$ on $X$ and generalizes the Cayley graph construction.
+In fact, when $X \cong G/H$ for some stabilizer subgroup $H$ of a basepoint $x_0$, we interpret $\Gamma(X; G, S)$ as the \emph{Cayley graph of $G$ acting on the coset space $G/H$}.
+If $H$ is trivial (i.e., the action is regular), then $X \cong G$ and $\Gamma(X; G, S)$ reduces to the standard Cayley graph $\Gamma(G, S)$.
+
+% When $H$ is nontrivial, several group elements from $G$ may correspond to the same vertex in $X$. Nonetheless, $\Gamma(X; G, S)$ inherits considerable symmetry from the group action:
+% \begin{itemize}
+%     \item $G$ acts by automorphisms on the graph,
+%     \item The local structure of the graph is uniform across orbits.
+% \end{itemize}
+
+% \subsection{Examples}
+
+% \begin{itemize}
+%     \item \textbf{Symmetric group:} Let $G = S_n$ act on $X = \{1, \dots, n\}$ by permutations, and let $S$ be a generating set of transpositions.
+Then $\Gamma(X; G, S)$ is a complete graph on $n$ vertices, as any element can be swapped with any other via some $s \in S$.
+
+%     \item \textbf{Johnson graphs:} These are Schreier graphs of $S_n$ acting on $k$-element subsets of $\{1, \dots, n\}$.
+Generators correspond to transpositions that change one element of the subset.
+Johnson graphs are highly symmetric and distance-regular, and they appear frequently in quantum walk algorithms.
+% \end{itemize}
+
+% \subsection{Quantum Walks on Group Action Graphs}
+
+% Quantum walks on graphs arising from group actions share many of the useful features of walks on full Cayley graphs.
+In fact, one can often analyze a walk on $\Gamma(X; G, S)$ by \emph{lifting} it to a walk on the Cayley graph $\Gamma(G, S)$ and projecting down via the quotient map $G \to G/H$.
+This structure preserves symmetry in the transition amplitudes.
+
+% In particular, if the initial quantum state is uniform over an orbit of $H$, the state will remain symmetric under the subgroup $H$ throughout the evolution.
+Thus, the walk evolves in an \emph{invariant subspace}, reducing the effective size of the problem.
+
+% \textbf{Example – Quotient Walks:} Krovi and Brun (2007) analyzed quantum walks on quotient graphs and showed how hitting probabilities and mixing behavior can be improved by exploiting such symmetry reductions.
+
+% Group action graphs are particularly useful in algorithmic settings where the state space is naturally modeled as an orbit under a group of moves or transformations. For instance:
+% \begin{itemize}
+%     \item The Rubik's cube configuration space is essentially the Cayley graph of the Rubik’s group acting on itself. Each configuration corresponds to a group element.
+%     \item A quantum walk on this space is a specialized form of group action walk, where subgroups preserving partial configurations can be used to reduce search complexity.
+% \end{itemize}
+
+% \subsection{Summary}
+
+% Graphs defined from group actions—such as Schreier graphs $\Gamma(X; G, S)$—generalize Cayley graphs to settings where the vertex set is a homogeneous space $G/H$. These graphs:
+% \begin{itemize}
+%     \item Maintain significant symmetry,
+%     \item Enable reduction to invariant subspaces via subgroup structure,
+%     \item Retain many spectral and dynamical properties of Cayley graphs.
+% \end{itemize}
+
+% Quantum walks on such graphs behave similarly to those on full Cayley graphs, though with potentially fewer vertices due to coset identification.
+This perspective is powerful for analyzing and implementing quantum algorithms.
+
+In the next section, we develop techniques for simulating continuous-time quantum walks on such symmetric graphs using quantum circuits.
+These simulations exploit the group action structure to simplify circuit construction and enhance algorithmic efficiency.
+
 \chapter{Simulating Group Action Quantum Walks}
+
+\section{Hamiltonian Structure and Sparsity}
+
+\section{Quantum Walk-Based and QSP Simulation}
+
+\section{Complexity Analysis}
 

### 2025-04-07 main.tex
chapter 3 updated

--- 2025-04-03 main.tex
@@
 \newpage
+\section*{Abstract}
+
+This thesis explores the foundations of quantum computation, focusing on quantum walks and their application to quantum money.
+Quantum walks, particularly continuous-time quantum walks based on group actions, serve as a powerful computational tool with applications in search algorithms and cryptographic protocols.
+We examine their mathematical structure and their advantages over classical random walks, emphasizing their efficiency in state evolution and probability distribution spreading.
+As a part of this work, we examine efficient implementations of transforms such as the Quantum Fourier Transform (QFT) and the Quantum Hartley Transform (QHT), analyzing their role in encoding quantum states for secure cryptographic applications.
+In particular, we discuss a novel instantiation of a quantum money scheme based on QHT, leveraging its unique properties for improved security and efficiency.
+To ensure the robustness of this quantum money scheme, we develop a verification mechanism utilizing quantum walks.
+Unlike previous approaches, which rely on standard quantum state measurements, our method employs continuous-time quantum walks to authenticate quantum money, preventing counterfeiting while maintaining computational feasibility.
+Additionally, we present a detailed discussion on the efficient implementation of this scheme, including optimized circuit designs and error mitigation strategies.
+
+\newpage
 \section{Introduction to Quantum Computation}
 \label{sec:intro}
+
+% \chapter{Introduction}
+% Quantum money, first introduced in a seminal paper by Wiesner [29], is a form of currency represented by quantum states.
+Unlike classical money, an ideal quantum bill cannot be counterfeited due to the no-cloning theorem of quantum mechanics, which prohibits making an identical copy of an unknown quantum state.
+Wiesner’s original scheme (now termed a \emph{private-key quantum money} scheme) had significant practical drawbacks: it required the issuing bank’s secret key to verify each banknote, meaning the bank had to be involved in every transaction.
+This reliance on the bank for verification severely limits the usability of private-key quantum money schemes.
+
+% In 2009, Aaronson [1] proposed the first \emph{public-key quantum money} scheme, in which anyone can verify a quantum banknote while only the bank can mint (issue) new valid banknotes.
+Public-key quantum money removes the transactional bottleneck of involving the bank every time.
+Aaronson’s specific scheme was later broken by Lutomirski et al.~[24].
+In the years since, several alternative public-key quantum money constructions have been explored [2, 17, 30, 19, 20, 23, 31].
+However, each of these proposals has either been broken by further cryptanalysis [14, 26, 7, 23] or relies on unconventional cryptographic assumptions, making their security or practicality questionable.
+
+% \medskip\noindent\textbf{Quantum Money from Group Actions and the Fourier Transform.} 
+% A promising candidate for secure public-key quantum money based on more standard assumptions was recently proposed by Zhandry [31].
+In Zhandry’s scheme, the core idea is to use an abelian group action as the foundation for the quantum state.
+Each money state (quantum banknote) is prepared as a \emph{group-action Fourier state}, and the corresponding serial number is an element of the underlying group (we will elaborate on these terms in later chapters).
+The verification algorithm in this scheme uses a group-action phase kickback routine to extract the serial number from the quantum banknote and check its validity.
+Doliskani [15] later proved that Zhandry’s scheme is secure in the generic group action model, providing evidence for its security under well-defined assumptions.
+
+% \medskip\noindent\textbf{This Work – Motivation and Contributions.} 
+% In this thesis, we adapt Zhandry’s group-action quantum money scheme by replacing its use of the Quantum Fourier Transform with the \emph{Quantum Hartley Transform} (QHT) over finite abelian groups.
+The motivation behind this substitution is multifold.
+First, using the Hartley transform causes the banknotes to have \emph{real} amplitudes instead of complex amplitudes.
+We believe this shift from complex to real quantum states may offer both computational and theoretical advantages.
+For example, certain mathematical identities hold for any two real orthonormal bases that do not generally hold for complex bases; such differences can affect the properties of quantum states and were a barrier in prior analyses (indeed, an attempted “quantum lightning” construction in [31] failed due to properties of complex phases that do not arise with real amplitudes).
+Beyond this specific context, our work is a first step toward employing real-valued quantum transforms in quantum cryptography and quantum algorithms.
+To the best of our knowledge, this is the first significant quantum cryptographic construction that makes essential use of the quantum Hartley transform.
+We hope that exploring real-amplitude quantum states will inspire further research into new quantum algorithms and optimizations for real-valued transforms.
+
+% We now summarize our main contributions:
+% \begin{itemize}
+%     \item We propose a new \textbf{public-key quantum money scheme} based on abelian group actions and the quantum Hartley transform.
+This scheme is an adaptation of Zhandry’s group-action money scheme, modified to output real-amplitude quantum states.
+%     \item We identify a breakdown in the original verification procedure when the Fourier transform is naively replaced by the Hartley transform: the Hartley-based verification fails to distinguish certain illegitimate banknotes.
+To overcome this, we design a \textbf{new verification algorithm} that relies on applying additional group action “twists” and utilizes quantum walks.
+This new verification algorithm successfully differentiates valid banknotes from forgeries despite the use of real amplitudes.
+%     \item We show that the serial number associated with a money state (which is a hidden group element) can be efficiently computed from the quantum state.
+In particular, we develop a \textbf{continuous-time quantum walk algorithm} to extract the serial number of a given banknote state.
+This algorithm leverages the structure of the group action and the spectral properties of an associated Cayley graph.
+Our method demonstrates that one can recover the hidden group element (serial) with high success probability, which not only underpins the new verification technique but is also of independent interest.
+%     \item In the course of our construction, we introduce a new algorithm for efficiently implementing the \textbf{quantum Hartley transform} and related real transforms.
+We present a recursive technique that exploits the structure of the Hartley transform, yielding a lower gate complexity than prior approaches in the literature.
+We also illustrate how other real-valued quantum transforms (e.g., the quantum sine transform) can be implemented using the Hartley transform as a subroutine.
+These results contribute to the broader goal of optimizing real quantum transforms for practical use.
+% \end{itemize}
+
+% In summary, our work combines ideas from quantum cryptography (public-key quantum money), quantum algorithms (quantum walks), and quantum signal processing (Hartley and related transforms) to create a novel and potentially practical quantum money scheme.
+
+% \medskip\noindent\textbf{Thesis Organization.} 
+% The remainder of this thesis is organized as follows.
+In **Chapter 2**, we provide background on the basics of quantum computation and the theory of group actions, including the concept of cryptographic group actions which underlie our money scheme.
+**Chapter 3** covers quantum walks, both continuous-time and discrete-time, outlining their differences and importance in quantum algorithms.
+In **Chapter 4**, we apply the quantum walk framework to group actions: we describe how a continuous-time quantum walk on a group action can be simulated efficiently, a crucial step for our serial number extraction algorithm.
+**Chapter 5** details the quantum money scheme itself and the role of the Hartley transform in its construction.
+We explain how the scheme is formulated and discuss the advantages and challenges introduced by using the Hartley transform.
+Finally, **Chapter 6** presents the verification algorithm for the Hartley-based quantum money.
+This chapter shows how we use quantum walks (as developed in Chapter 4) to reliably verify banknotes and compute their serial numbers, thereby addressing the verification issues that arose from the use of real amplitudes.
+% \vspace{1em}
+
+% \chapter{Background on Quantum Computation and Group Actions}
+
+% \section{Quantum Computation Basics}
+% Quantum computation operates on information stored in quantum states.
+The fundamental unit of quantum information is the \emph{qubit}, which, unlike a classical bit, can exist in a superposition of basis states.
+A qubit is described by a state $|\psi\rangle = \alpha |0\rangle + \beta |1\rangle$ (in Dirac notation), where $\alpha,\beta \in \mathbb{C}$ and $|\alpha|^2 + |\beta|^2 = 1$.
+A system of $n$ qubits resides in a $2^n$-dimensional Hilbert space and its state can be a superposition of all $2^n$ basis basis states $|b_1b_2\cdots b_n\rangle$.
+
+% Computation is carried out by unitary transformations on these states.
+A quantum algorithm is typically a sequence of quantum gates (unitary operators) applied to an initial state (usually a simple basis state like $|00\cdots0\rangle$), followed by a measurement of some qubits to obtain a classical result.
+A crucial aspect of quantum computation is that certain transformations—such as the Fourier transform over an $N$-element group—can be implemented very efficiently on a quantum computer (in $\operatorname{poly}(\log N)$ time), whereas their classical counterparts might require $\operatorname{poly}(N)$ time.
+
+% One example important to this work is the \textbf{quantum Fourier transform} (QFT).
+For an abelian group $G$ of order $N$, the QFT is the unitary map $|g\rangle \mapsto \frac{1}{\sqrt{N}}\sum_{h \in G} \chi_h(g)\, |h\rangle$, where $\{\chi_h\}$ are the characters (complex exponential homomorphisms) of $G$.
+In more familiar terms, when $G = \mathbb{Z}_N$ (the integers mod $N$), the QFT takes $|j\rangle$ to $\frac{1}{\sqrt{N}}\sum_{k=0}^{N-1} e^{2\pi i j k / N} |k\rangle$.
+The QFT is a key component in many quantum algorithms, including Shor’s factoring algorithm and certain quantum money schemes (e.g., Zhandry’s) that rely on hiding information in phase relationships.
+The QFT can be implemented using $O((\log N)^2)$ basic gates for many groups [13], making it an efficient operation.
+
+% Another concept we will use is the \textbf{quantum Hartley transform} (QHT).
+The Hartley transform is an alternative to the Fourier transform that produces only real values (in the classical case) by using sinusoidal basis functions (sums of sine and cosine) instead of complex exponentials.
+The \emph{quantum} Hartley transform is the unitary transform corresponding to the classical Hartley transform.
+For example, the Hartley transform on $\mathbb{Z}_N$ maps a basis state $|j\rangle$ to $\frac{1}{\sqrt{N}}\sum_{k=0}^{N-1} \mathrm{cas}\!\Big(\frac{2\pi j k}{N}\Big)\, |k\rangle$, where $\mathrm{cas}(x) = \cos x + \sin x$ is the Hartley kernel.
+Because $\cos x + \sin x$ is real for all $x$, the resulting amplitudes are real numbers.
+We will discuss the Hartley transform in more detail in Chapter 5, including how to implement it efficiently on a quantum computer.
+
+% A final fundamental principle to note is the \textbf{no-cloning theorem}, which underpins the security of quantum money.
+This theorem states that there is no physical operation that can make a copy of an arbitrary unknown quantum state.
+This contrasts sharply with classical information, which can be copied freely.
+The no-cloning theorem means that an adversary cannot duplicate a quantum banknote without fundamentally disturbing it – any attempt to “clone” the state will fail unless the adversary already has complete classical information describing that state.
+
+% Throughout this thesis, when we refer to an algorithm as \emph{efficient} or \emph{feasible}, we typically mean it can be performed by a quantum polynomial-time (QPT) algorithm.
+This is analogous to classical polynomial time, but on a quantum computer.
+All of the algorithms we propose (minting, verification, quantum walk simulation, etc.) are intended to be efficient in this sense.
+
+% \section{Group Actions in Cryptography}
+% At the heart of our quantum money scheme is the notion of a group action.
+A \textbf{group action} of a group $G$ on a set $X$ is a function $*\colon G \times X \to X$ that satisfies two properties: (1) the identity element $e \in G$ acts trivially on every $x \in X$ ($e * x = x$), and (2) the action is compatible with the group operation, meaning $g*(h* x) = (gh)*x$ for all $g,h \in G$ and $x \in X$.
+We will often denote the result of $g$ acting on $x$ by $g*x$ or simply $g x$ when the action is clear from context.
+
+% The orbit of an element $x \in X$ under the action is the set $G * x = \{g*x : g \in G\} \subseteq X$.
+If there is exactly one orbit (i.e., $G * x = X$ for some $x$), the action is called \emph{transitive}.
+If, in addition, no non-identity group element fixes any $x$ (i.e., $g * x = x$ implies $g = e$), then the action is \emph{free}.
+A group action that is both transitive and free is sometimes called a \textbf{regular action}.
+In a regular action, for any two elements $y, z \in X$, there is a unique group element $g$ such that $g * y = z$.
+In other words, $G$ acts like a permutation group that moves elements of $X$ around, and knowing the starting and ending point uniquely determines the “move” $g$.
+In this case $|X| = |G|$, and we can think of $X$ as essentially a copy of $G$ with the group structure “hidden” by the action.
+
+% Group actions are ubiquitous in modern cryptography.
+A \textbf{cryptographic group action} is one where the action is easy to compute in the forward direction, but inverting the action (recovering $g$ from $x$ and $g*x$) is computationally hard.
+This essentially functions as a one-way function: given $x$ and $g$, it is easy to compute $y = g*x$, but given $x$ and $y$ it is infeasible to find $g$ (except with negligible probability).
+One classical example is the discrete logarithm problem: consider the cyclic group $G = \mathbb{Z}_p^*$ (the multiplicative group of a prime field) acting on itself by exponentiation.
+Let $X = G$ and define $g * x = x^g \pmod p$ (treating group elements as integers).
+Here $g$ is an exponent.
+This is a group action (in fact, just the group’s own operation written differently), and computing $x^g \bmod p$ is efficient.
+However, given $x$ and $y = x^g$, finding $g$ requires solving a discrete log problem, which is believed to be hard for suitable choices of $p$.
+Thus, exponentiation can be viewed as a one-way group action.
+
+% Another prominent example comes from elliptic-curve cryptography: the action of an ideal class group on a set of elliptic curves.
+In schemes like CSIDH (Commutative Supersingular Isogeny Diffie–Hellman), an abelian group of ideal classes $G$ acts on the set $X$ of supersingular elliptic curves by isogeny (an isogeny is a structure-preserving map between curves).
+Starting from a curve $x_0$, one can efficiently compute $g * x_0$ (which is another elliptic curve) for any group element $g$, but given two curves $x_0$ and $x = g * x_0$, it is believed to be computationally hard to recover $g$.
+This hard problem is the foundation of isogeny-based cryptography.
+We refer to such $G$ and $X$ as a \emph{cryptographic group action} pair.
+
+% Cryptographic group actions provide a natural platform for public-key quantum money schemes.
+In such schemes, the secret “serial number” of a quantum banknote can be an element $g \in G$, and the quantum state of the banknote can be some function of $g*x_0$ for a public base point $x_0 \in X$.
+The hardness of inverting the action ($x_0$ and $x = g*x_0$ do not easily reveal $g$) contributes to the security against counterfeiting, while the structure of the group action can be used to efficiently verify authenticity (as we will see with the Fourier or Hartley transform techniques).
+
+% We will assume throughout that we have a family of abelian group actions $(G,X)$ that are cryptographically suitable: $|G|$ is large (growing with the security parameter), the action is efficiently computable, transitive and free (so $|X|=|G|$), and inverting the action is infeasible without the secret key.
+Such families are conjectured to exist (for example, the isogeny-based actions, and others discussed in cryptographic literature).
+
+% Finally, we note that working in the \textbf{generic group model} (or generic group \emph{action} model) is a common theoretical approach to analyze security.
+In a generic model, the group elements are treated as black-box labels without exploiting any special algebraic structure beyond group axioms.
+Doliskani’s proof of security for Zhandry’s scheme [15] was in such a generic model for group actions, lending confidence that no “generic” attack can break the scheme.
+In this thesis, we focus on designing the scheme and algorithms at a high level and assume the underlying group action is secure; a detailed security proof is beyond our scope, though we rely on prior results for reassurance.
+
+% \chapter{Quantum Walks – Continuous and Discrete}
+% Random walks on graphs are a powerful tool in classical algorithms, and their quantum analogues, called \emph{quantum walks}, play a fundamental role in many quantum algorithms.
+Like classical random walks, quantum walks come in two flavors: \textbf{continuous-time} and \textbf{discrete-time}.
+Both types of quantum walks can exhibit dramatically different behavior from their classical counterparts due to quantum interference, which can be leveraged for algorithmic speedups in various problems (for example, quantum walks have led to faster algorithms for database search and element distinctness [4, 5], as well as exponential speedups in oracular problems [10]).
+
+% \section{Continuous-Time Quantum Walks}
+% A continuous-time quantum walk (CTQW) takes place on the vertices of a graph and is defined by a Hamiltonian (energy operator) that drives the evolution of a quantum state across the graph.
+Formally, consider a graph $\Gamma$ with vertex set $V$ of size $n$.
+We associate a basis state $|v\rangle$ with each vertex $v \in V$.
+In a continuous-time \emph{classical} random walk, one can describe the probability distribution $p(t)$ over vertices at time $t$ by a differential equation $dp/dt = -L p(t)$, where $L$ is the Laplacian matrix of the graph.
+By analogy, in a continuous-time \emph{quantum} walk, we use the Schrödinger equation:
+% \[ i\,\frac{d}{dt}|\psi(t)\rangle = H\,|\psi(t)\rangle, \] 
+% where $H$ is the Hamiltonian of the walk and $|\psi(t)\rangle$ is the state of the quantum walk at time $t$.
+The formal solution is $|\psi(t)\rangle = e^{-i H t} |\psi(0)\rangle$.
+Intuitively, $H$ encodes the connectivity of the graph, and the quantum state evolves continuously, “exploring” the graph’s vertices.
+
+% Typically, for a quantum walk on an undirected graph, a natural choice of Hamiltonian $H$ is the adjacency matrix of the graph (sometimes the Laplacian or a normalized version is used, but the adjacency matrix suffices for our purposes).
+If $A$ is the adjacency matrix of $\Gamma$, then $H = A$ means that the amplitudes flow between adjacent vertices over time.
+Specifically, if $|v\rangle$ and $|w\rangle$ are connected by an edge, the Hamiltonian will induce oscillations of amplitude between $|v\rangle$ and $|w\rangle$.
+Because $H$ is Hermitian, $e^{-iA t}$ is unitary, ensuring the evolution is coherent.
+
+% One notable feature of CTQWs is that interference effects can cause the walker to propagate through the graph in ways that a classical random walk cannot.
+For example, quantum walkers can have ballistic spreading (moving roughly linearly fast with time) on certain graphs, whereas classical diffusion is much slower (like $\sqrt{t}$ spread).
+These effects underlie algorithmic speedups.
+For instance, the continuous-time walk on a certain $N$-vertex graph can reach a target vertex in $O(N^{1/2})$ time, whereas a classical random walk might take $O(N)$ steps to achieve the same, illustrating a quadratic speedup in some search problems.
+
+% \section{Discrete-Time Quantum Walks}
+% Discrete-time quantum walks proceed in a sequence of steps rather than evolving continuously.
+In the discrete-time case, we typically require an additional “coin” space or a similar construction to allow the walker to move without violating unitarity (since a deterministic move on an undirected graph can lead to stagnation without a coin toss to break symmetry).
+In the \textbf{coined model} of a quantum walk, the state is a tensor product $|\text{position}\rangle \otimes |\text{coin}\rangle$.
+At each step, a unitary coin flip (like a Hadamard gate generalizing a two-sided coin to a multi-sided one for vertices of higher degree) is applied to the coin register, and then a conditional shift moves the walker to a new vertex based on the coin outcome.
+This two-part operation (coin flip + shift) constitutes one step of the walk, which is a unitary transformation on the overall Hilbert space.
+
+% There is also an alternative approach to discrete-time walks that does not explicitly use a coin, but instead doubles the state space in another way.
+One such approach, due to Szegedy [27], represents a step as two reflections on an enlarged Hilbert space associated with the edges of the graph.
+Another approach (used in some of our analysis) constructs a discrete-time walk using the graph’s adjacency matrix but treats it in a quantum way.
+For a graph $\Gamma=(V,E)$, one can define a unitary operator $U$ acting on the space spanned by $\{|v\rangle \otimes |0/1\rangle: v \in V\}$ (position plus one qubit) that effectively simulates moving along the edges.
+For example, one can design $U$ such that:
+% \[ U:\; |v,0\rangle \mapsto \frac{1}{\sqrt{\deg(v)}}\sum_{(v\to w)\in E} |w,1\rangle, \] 
+% and similarly $|w,1\rangle$ moves back to $|v,0\rangle$ on the reverse edge.
+This “flip-flop” shift is one way to implement a discrete quantum walk step.
+In essence, the walker has a direction bit that flips each time an edge is traversed, preventing it from just oscillating back and forth between two vertices.
+After many such steps, the probability amplitude distribution over $V$ can spread across the graph.
+
+% Despite the differences in formulation, continuous- and discrete-time quantum walks are closely related.
+In fact, it has been shown by Childs [9] and by Berry, Childs, and Kothari [6] that a continuous-time quantum walk can be efficiently simulated using a discrete-time quantum walk.
+The key idea is to approximate the continuous evolution $e^{-iAt}$ by a product of many short discrete updates (Trotterization or a related technique).
+More concretely, given a Hamiltonian $H$ driving a CTQW, one can introduce an ancillary system and a carefully constructed unitary such that the effect of $e^{-iHt}$ is approximated to arbitrary precision with a polynomial number of discrete steps.
+This means that any algorithm that could be conceived in the continuous-time framework can be translated to a discrete-time circuit model with only polylogarithmic overhead in complexity (assuming $H$ is sparse, which in our cases it will be).
+
+% Quantum walks have been employed in a range of quantum algorithms.
+For example, Ambainis’s algorithm for element distinctness [5] uses a discrete-time quantum walk on the Johnson graph to achieve a faster than brute-force runtime.
+Childs et al.
+demonstrated an exponential separation between quantum and classical query complexities using a continuous-time quantum walk in a contrived maze problem [10].
+Many search and optimization problems have also been tackled with quantum walk algorithms.
+The common theme is that quantum interference allows the walk to navigate the solution space more efficiently than random fluctuation alone.
+
+% In the remainder of this thesis, we will use whichever model of quantum walk is most convenient for analysis.
+Our verification algorithm in Chapter 6 will be described conceptually as a continuous-time walk (because it naturally fits the problem structure), but behind the scenes we will implement it using a discrete-time simulation (Chapter 4 will provide details on how this simulation is done for our specific application).
+
+% \chapter{Simulating Group Action Quantum Walks}
+% In this chapter, we bridge the concepts from Chapter 2 (group actions) and Chapter 3 (quantum walks).
+Specifically, we consider quantum walks on graphs that arise from group actions, and we discuss how to implement or simulate such walks efficiently on a quantum computer.
+This is crucial for our quantum money verification algorithm, which will require running a quantum walk on a graph defined by the given group action.
+
+% \section{Cayley Graphs of Groups and Group Actions}
+% A convenient way to visualize a group or a group action is via its Cayley graph.
+First, for an ordinary (abelian) group $G$, if we pick a generating set $S \subset G$ (for example, $S$ could be a small symmetric set of generators such that every element of $G$ can be expressed as a product of elements in $S$), the \textbf{Cayley graph} $\Gamma(G,S)$ is an undirected graph defined as follows: each group element $g \in G$ corresponds to a vertex, and there is an edge between $g$ and $h$ if and only if $h = s \cdot g$ for some generator $s \in S$ (equivalently $g$ and $h$ differ by multiplication by a generator).
+We typically take $S$ to be symmetric (if $s \in S$ then $s^{-1} \in S$) so that the resulting graph is undirected.
+The Cayley graph encapsulates the structure of the group in graph form.
+
+% The adjacency matrix $A$ of $\Gamma(G,S)$ has rows and columns indexed by $G$, and $(A)_{g,h} = 1$ if $h = s\cdot g$ for some $s \in S$, and $0$ otherwise.
+It is known that for a finite abelian group $G$, the eigenvectors of this adjacency matrix are related to the characters of $G$ (essentially the Fourier basis on the group), and the eigenvalues can be determined from $S$.
+In particular, if $\chi: G \to \mathbb{C}$ is a character (one of the Fourier basis functions), then it is an eigenvector of $A$.
+The corresponding eigenvalue is $\lambda_{\chi} = \sum_{s\in S} \chi(s)$ (the character evaluated on each generator and summed).
+This means the QFT over $G$ diagonalizes the adjacency matrix $A$.
+As a result, a continuous-time quantum walk on $\Gamma(G,S)$ can be solved analytically by moving to the Fourier basis: $e^{-iAt}$ acts by phases $e^{-i\lambda_{\chi} t}$ on each Fourier basis state.
+Moreover, if $S$ is small (say $|S| = \operatorname{poly}(\log |G|)$), one can efficiently implement $e^{-iAt}$ using the QFT: prepare the state in the Fourier basis (apply QFT), apply a phase rotation by $\lambda_{\chi} t$ on each basis state (which can be done classically if we can compute $\lambda_{\chi}$), and then inverse QFT.
+This takes polynomial time in the size of the problem parameters.
+(For example, for $G=\mathbb{Z}_N$, this procedure would simulate the continuous-time walk by using two QFTs of size $N$ and a linear-time classical phase rotation on $N$ amplitudes, which is efficient.)
+
+% Now, consider a group action $G \curvearrowright X$ where $X$ is a set on which $G$ acts.
+We can similarly define a Cayley-type graph for the action.
+Fix a particular element $x_0 \in X$ as a basepoint.
+Take the same generating set $S \subset G$.
+We define the \textbf{group action graph} $\Gamma(X,S)$ as the graph whose vertex set is $X$, and put an edge between two vertices $x, y \in X$ if and only if there exists $s \in S$ such that $y = s * x$ (i.e., $y$ is the result of the group element $s$ acting on $x$).
+Because $S$ is symmetric and the action is regular (in our applications), this graph is also undirected and regular.
+Essentially, $\Gamma(X,S)$ is the “projection” of the group’s Cayley graph into the set $X$ via the action.
+
+% If the action of $G$ on $X$ is regular, $\Gamma(X,S)$ is isomorphic to $\Gamma(G,S)$ as an abstract graph (they are structurally the same graph, just the labels of vertices are different: one uses group elements $g$, the other uses states $x = g*x_0$).
+However, there is an important distinction from a computational perspective: labeling the vertices by elements of $X$ might conceal the group structure.
+In fact, if the group action is cryptographically one-way, then although there is a one-to-one correspondence between $G$ and $X$ (via $g \leftrightarrow g* x_0$), finding the group element label $g$ corresponding to a given $x \in X$ is hard.
+In other words, we (as algorithm designers) can efficiently enumerate and work with the group element labels $g \in G$, but an algorithm working with the $X$-labels may not be able to perform the same tasks, because moving to the $G$ label requires inverting the group action.
+
+% To put it another way: mathematically, $A(G,S)$ and $A(X,S)$ (the adjacency matrices of the two Cayley graphs) are related by a permutation of the basis if we know the isomorphism $X \cong G$.
+If we had an oracle giving us $g$ for each $x = g*x_0$, then $A(X,S)$ could be efficiently diagonalized just as $A(G,S)$ is (by switching to group element labels and applying QFT).
+But under cryptographic assumptions, we do not have such an oracle; effectively, the basis $\{|x\rangle: x \in X\}$ is a “hidden permutation” of the nice Fourier basis.
+This means that direct quantum Fourier techniques cannot be applied to $A(X,S)$, and new techniques are required to simulate a quantum walk on $\Gamma(X,S)$.
+
+% Nonetheless, all is not lost.
+Even if we cannot diagonalize $A(X,S)$ explicitly, we can still leverage the fact that $A(X,S)$ is sparse and structured.
+The degree of each vertex in $\Gamma(X,S)$ is $|S|$, which by assumption is small (at most polynomial in $\log |G|$ for efficiency).
+This sparsity allows us to implement the quantum walk step by step, as we will outline below.
+Moreover, as observed in prior works, even cryptographic group action graphs can sometimes be navigated quantumly.
+For instance, continuous-time quantum walks have been studied in the context of isogeny-based group actions (supersingular isogeny graphs) [8, 16].
+These works implement quantum walks on those graphs (typically for solving certain problems or analyzing mixing properties), treating the action oracle as a black box.
+We will adopt a similar approach: we assume we have efficient oracles for the group action (given $g$ and $x$, compute $g*x$) and for checking group membership or identity if needed.
+Under this assumption, we can implement the quantum walk unitaries directly on the $X$-labeled state space.
+
+% \section{Efficient Simulation of Continuous-Time Walks via Discrete Steps}
+% As mentioned in Chapter 3, any continuous-time quantum walk on a sparse Hamiltonian can be simulated with a sequence of discrete-time operations.
+In the context of the group action Cayley graph $\Gamma(X,S)$, we want to simulate the unitary $U(t) = e^{-i A(X,S) t}$ for some time $t$ (or a sequence of such unitaries for various times).
+Thanks to Childs [9] and Berry–Childs–Kothari [6], we know that $U(t)$ can be approximated to high precision with $O(\|A\|_{\max} t\, \operatorname{poly}(1/\epsilon))$ uses of a discrete-time walk step and additional gates, where $\epsilon$ is the desired error and $\|A\|_{\max}$ is related to the maximum degree (here $\|A\|_{\max} = |S|$).
+In our case, $|S|$ is small, and $t$ will also be bounded by a polynomial in the relevant input size (for instance, in our application $t$ will be related to the inverse spectral gap or some parameter of the walk, but we will choose manageable values).
+Therefore, an efficient simulation means we need to implement a single step of the discrete-time quantum walk efficiently.
+We now describe how to implement the core components of a discrete-time walk on $\Gamma(X,S)$.
+
+% Following the approach used in [6, 9], the key components are:
+% 1.
+An \textbf{oracle for the sparse Hamiltonian} (in this case, the adjacency matrix).
+This oracle, given a vertex label and an index, outputs the neighboring vertex corresponding to that index.
+For $\Gamma(X,S)$, since each vertex $x$ has $|S|$ neighbors (one for each $s \in S$), such an oracle would on input $(x, j)$ (with $j \in \{1,\dots,|S|\}$ indexing the generators in $S$) output the neighbor $y = s_j * x$.
+We can implement this “oracle” explicitly because we can compute the group action: we know each generator $s_j$, so we can map $(x, j) \mapsto s_j * x$ by a single group action computation.
+This is a classical operation performed quantumly (i.e., we can build a unitary that performs $|x\rangle|j\rangle \mapsto |x\rangle |y\rangle$ where $y = s_j * x$).
+% 2. Construction of the \textbf{isometry} $V$ that prepares a superposition of neighbor states. Specifically, for each vertex $x$, we want:
+% \[ V:\; |x\rangle \;\mapsto\; \frac{1}{\sqrt{|S|}} \sum_{s \in S} |x, s* x\rangle, \] 
+% where we have used an output register to hold the neighbor.
+This isometry $V$ can be implemented by first adding an ancilla register for the group element in $S$, initializing it to $|0\rangle$, then creating an equal superposition over all $s \in S$ in that register, and finally replacing that register’s value with the resulting neighbor.
+Concretely, start with $|x, 0\rangle$.
+Use a unitary $U_S$ on the second register such that $U_S|0\rangle = \frac{1}{\sqrt{|S|}}\sum_{s\in S} |s\rangle$.
+Now the state is $\frac{1}{\sqrt{|S|}}\sum_{s\in S} |x, s\rangle$.
+Next, apply the group action oracle to compute $s * x$ in a third register (or overwrite the first register), obtaining $\frac{1}{\sqrt{|S|}}\sum_{s} |x, s, s*x\rangle$.
+Then “uncompute” the $s$ register (apply $U_S^\dagger$ to bring it back to $|0\rangle$) so that we end with $\frac{1}{\sqrt{|S|}}\sum_{s} |x, s*x\rangle$.
+Rename the two registers as $|x\rangle_{\text{orig}} |y\rangle_{\text{nbr}}$.
+This is exactly the desired $V|x\rangle = \frac{1}{\sqrt{|S|}}\sum_{y:\,y = s*x} |x, y\rangle$.
+We have thus implemented $V$ by using the ability to iterate over all generators (which is feasible since $|S|$ is small) and the group action operation.
+
+% 3.
+We also need to implement $V^\dagger$ (the inverse isometry) which, given a superposition of $|x,y\rangle$, reverses the above process and yields $|x\rangle$ (provided $y$ was indeed one of the neighbors of $x$ in the superposition).
+This essentially requires an operation to compute $s$ from $(x,y)$ such that $y=s*x$.
+Since the action is free and $S$ is small, we can find which generator maps $x$ to $y$ by checking each $s \in S$ (this is a small brute-force check done coherently).
+We can implement a unitary that, for each pair $(x,y)$, finds the unique $s$ with $y=s*x$ and writes $s$ in an ancilla (using comparisons), then uncompute the $y$ register by applying $s^{-1}$ to $y$ (which returns it to $x$) while also un-entangling the $s$.
+In practice, this is efficient since $|S|$ is small and trying all $s$ is a constant or polynomial-time classical loop.
+We assume an oracle or routine that can perform this inversion on a case-by-case basis.
+
+% 4.
+The final component is the \textbf{reflection operator} (or the walk step) that uses $V$ and $V^\dagger$.
+In the continuous-to-discrete simulation algorithm, one defines a reflection $R = 2V V^\dagger - I$.
+$R$ acts on the enlarged space of vertex-neighbor pairs, and it essentially flips the phase of any state orthogonal to the subspace $\{\frac{1}{\sqrt{|S|}}\sum_{s}|x,s*x\rangle: x \in X\}$ prepared by $V$.
+Intuitively, $R$ distinguishes states that are “properly correlated” as in a single step of a walk from those that are not, and flips the latter’s sign.
+The crucial point is that if we can implement $V$ efficiently (and $V^\dagger$ accordingly) and also trivial reflections like $|0\rangle \to -|0\rangle$ on ancilla states, then we can implement $R$ efficiently as well (since $R = V (2|0\rangle\!\langle 0| - I) V^\dagger$, which means perform $V^\dagger$, do a phase flip on the $|0\rangle$ state of the ancillary superposition register, then apply $V$).
+
+% Given these components, a single discrete-time quantum walk step $U_{\text{walk}}$ on $\Gamma(X,S)$ can be constructed.
+In many formulations, one actually uses two reflections to form the walk operator: one as above and another to reflect about the starting subspace (ensuring the walk doesn’t have trivial stationary components).
+However, in the Childs–Berry–Kothari simulation approach, the walk operator is taken as $W = (2V V^\dagger - I) \cdot ( \text{swap registers} )$.
+The “swap” simply swaps the two registers $|x,y\rangle \mapsto |y,x\rangle$, causing a move from $(\text{orig}, \text{nbr})$ to $(\text{new orig} = \text{old nbr}, \text{new nbr} = \text{old orig})$.
+This swap combined with $R$ effectively implements the adjacency relationships as a unitary walk.
+
+% To summarize, we have outlined how:
+% - The isometry $V$ and its inverse can be implemented with a polynomial number of operations (scaling with $|S|$ and the cost of computing the group action).
+% - The reflection $R$ can be built from $V$ and a simple phase flip.
+% - The swap operation on two registers is straightforward.
+
+% Thus, all components of the discrete-time quantum walk step on the group action graph are efficient.
+We can now leverage known results to claim that a continuous-time walk generated by the Hamiltonian $A(X,S)$ for time $t$ can be simulated by applying $O(t\,\operatorname{poly}(|S|))$ steps of the above discrete walk $W$.
+In our context, we will not need $t$ to be extremely large; we will be interested in running phase estimation on $e^{-iA t}$ for some moderate $t$ values.
+The efficiency we have established means this phase estimation will be feasible.
+
+% \section{Group Action Quantum Walks and Spectral Properties}
+% Before moving on, it is worth discussing what the spectral properties of the group action Cayley graph $A(X,S)$ imply for our algorithm (which will come in Chapter 6).
+We have noted that in the absence of one-wayness, the eigenstates of $A(X,S)$ would be known (Fourier states) with eigenvalues $\lambda_{\chi} = \sum_{s\in S} \chi(s)$.
+In the presence of one-wayness, we cannot directly label those eigenstates, but they still exist.
+In particular, if $G$ is abelian, the adjacency matrix $A(X,S)$ will have the same multiset of eigenvalues as $A(G,S)$.
+Let us denote those eigenvalues by $\{\lambda_k: k=1,\dots,|G|\}$.
+We may not know which eigenvalue corresponds to which state in $X$, but we know each $\lambda_k = \sum_{s\in S} \chi_k(s)$ for some character $\chi_k$ of $G$.
+For example, in a simple case $G = \mathbb{Z}_N$ and $S=\{1, -1\}$, the eigenvalues of $A(G,S)$ (and thus $A(X,S)$) would be $2\cos(2\pi k/N)$ for $k=0,\dots,N-1$.
+The important take-away is that the eigenvalues are related to the group structure (often involving cosine terms if $S$ is symmetric), and the eigenvectors are “global” states spread out over the vertices.
+
+% In the next chapter, we will construct our quantum money scheme such that a valid banknote state is one of these eigenvectors (or closely related to an eigenvector) of a certain group action graph.
+This will be by design: when minting money, the procedure will create a state that, under the action of the adjacency matrix of $\Gamma(X,S)$, picks up a well-defined phase.
+In Chapter 6, our verification algorithm will leverage this by using phase estimation on the continuous-time walk unitary $e^{-iA t}$ to determine the eigenvalue (and thereby infer the “serial number” hidden in the state).
+
+% Having established that we can perform the quantum walk on $\Gamma(X,S)$ efficiently, we are prepared to move on to the construction of the quantum money scheme itself, and then to the details of the verification algorithm that uses these walks.
+
+% \chapter{Quantum Money and the Hartley Transform}
+% We now present our public-key quantum money scheme based on group actions and the Hartley transform.
+We begin by reviewing Zhandry’s quantum money scheme from abelian group actions (which uses the Fourier transform) as a baseline.
+Then we describe our Hartley-transform-based variant and discuss its properties.
+The quantum Hartley transform will play a central role in both the minting and verification of banknotes.
+
+% \section{Public-Key Quantum Money: Definitions}
+% A public-key quantum money scheme consists of two algorithms, traditionally called $\mathsf{Mint}$ and $\mathsf{Verify}$:
+% \begin{itemize}
+%     \item $\mathsf{Mint}(1^n)$ is a probabilistic quantum polynomial-time (QPT) algorithm that, given a security parameter $n$, outputs a pair $(s, |\$\rangle)$.
+Here $s$ is a classical string called the \emph{serial number} (or public key) and $|\$\rangle$ is a quantum state representing the banknote.
+We often call the pair $(s, |\$\rangle)$ a banknote, and $s$ by itself the serial number of that banknote.
+%     \item $\mathsf{Verify}(s, |\$\rangle)$ is a QPT algorithm (which may be implemented as a quantum circuit acting on the state $|\$\rangle$ and some ancillary workspace).
+It takes as input a serial number $s$ and an alleged quantum banknote state $|\$\rangle$.
+It outputs $\mathtt{accept}$ (valid) or $\mathtt{reject}$ (invalid).
+% \end{itemize}
+
+% We require two properties from such a scheme:
+% \begin{description}
+%     \item[Correctness:] For any valid output $(s, |\$\rangle)$ of $\mathsf{Mint}(1^n)$, the verification algorithm accepts with high probability.
+Formally, $\Pr[\mathsf{Verify}(s, |\$\rangle) = \mathtt{accept}]$ should be very close to 1 (typically we require it to be $1 - \negl(n)$, where $\negl(n)$ denotes a negligible function in $n$).
+%     \item[Security (Unforgeability):] No efficient adversary, given one or more genuine banknotes, can produce a new valid banknote.
+In the strongest formulation, if an adversary is given a single valid $(s, |\$\rangle)$, it should be infeasible for them to produce two quantum states $|\$'\rangle$ and $|\$''\rangle$ such that $\mathsf{Verify}(s, |\$'\rangle) = \mathsf{Verify}(s, |\$''\rangle) = \mathtt{accept}$ (i.e., they cannot create a second copy that passes verification while retaining the original).
+More generally, even given multiple banknotes, the adversary should not be able to create new ones with fresh serial numbers that pass verification.
+This captures the idea that quantum money cannot be counterfeited.
+% \end{description}
+
+% In a \emph{public-key} scheme, the verifier uses only the public information (here, the serial number and any scheme-wide public parameters) to check validity, and does not need any secret key.
+The bank (mint) may have a secret key to produce the states, but after minting, the bank’s involvement is not needed.
+In our scheme, the serial number will effectively contain the information needed for public verification (similar to how a classical bill might have a number anyone can look up, except here it’s used in a quantum procedure).
+
+% We next outline Zhandry’s scheme, which our scheme builds upon.
+
+% \section{Fourier-Based Quantum Money from Group Actions}
+% Zhandry’s quantum money scheme [31] is built on an abelian group action $G \curvearrowright X$.
+We have a family of group actions parameterized by the security parameter $n$ (so the size of $G$ grows with $n$).
+For simplicity, assume $|G| = N$.
+The scheme also fixes a particular element $x_0 \in X$ that everyone knows (a public base point in $X$).
+
+% The minting algorithm $\mathsf{Mint}$ in Zhandry’s scheme works as follows (informally):
+% \begin{enumerate}
+%     \item On input $1^n$, sample a random group element $g \leftarrow G$. This $g$ will serve as the serial number $s$ for the banknote.
+%     \item Prepare two registers: the first is a group element register, initialized to $|0_G\rangle$ (an encoding of the identity element of $G$), and the second is an $X$-register initialized to $|x_0\rangle$.
+%     \item Apply the quantum Fourier transform over $G$ to the first register. This creates a uniform superposition over $G$: 
+%     \[
+%     \frac{1}{\sqrt{N}} \sum_{h \in G} |h\rangle \otimes |x_0\rangle\,.
+%     \] 
+%     \item Now apply the group action in a controlled manner: for each basis state $|h\rangle$ in the first register, apply $h$’s action on the second register. This transforms the joint state into 
+%     \[
+%     \frac{1}{\sqrt{N}} \sum_{h \in G} |h\rangle \otimes |h * x_0\rangle\,,
+%     \] 
+%     which is an entangled state between a superposition of group elements and their corresponding $X$-elements.
+%     \item Apply the inverse QFT (which is the adjoint of the QFT) on the first register.
+This recombines the amplitudes in the first register.
+The result (by properties of the QFT) can be shown to be
+%     \[
+%     \frac{1}{\sqrt{N}} \sum_{h \in G} \omega^{\langle g,\,h \rangle} |h\rangle \otimes |h * x_0\rangle\,,
+%     \] 
+%     where $\omega^{\langle g,\,h \rangle}$ denotes the phase picked up that depends on $g$ and $h$.
+In fact, this state can be written as $|g\rangle \otimes \frac{1}{\sqrt{N}}\sum_{h \in G} |h * x_0\rangle$; essentially, the first register ends up in $|g\rangle$ (the serial number) and the second register is an equal superposition of all elements of $X$ in the orbit of $x_0$ (which is $X$ itself, since the action is transitive) but weighted by a phase related to $g$.
+This is the so-called group-action Fourier state.
+%     \item The first register (which contains $|g\rangle$) is measured in the computational basis, yielding the random serial number $g$ and collapsing the second register to a state that we will denote $|\$_g\rangle$.
+This $|\$_g\rangle$ is the actual quantum money state corresponding to serial $g$.
+%     \item Output the pair $(s = g,\; |\$\rangle = |\$_g\rangle)$.
+% \end{enumerate}
+
+% In the above, a bit of algebra reveals that $|\$_g\rangle = \frac{1}{\sqrt{N}} \sum_{h \in G} \chi_g(h)\, |h * x_0\rangle$, where $\chi_g(h) = \omega^{\langle g,\,h \rangle}$ is essentially the character of $G$ indexed by $g$.
+In other words, $|\$_g\rangle$ is (up to global phase) the state one gets by applying the representation (character) $\chi_g$ to weight the superposition over the orbit $X$.
+These states for different $g$ are almost orthogonal and can be distinguished with the right measurement.
+
+% The verification algorithm $\mathsf{Verify}(g, |\$_g\rangle)$ for Zhandry’s scheme goes as follows:
+% \begin{enumerate}
+%     \item Given the purported serial number $g \in G$ and an input state $|\psi\rangle$ (which should equal $|\$_g\rangle$ if genuine), attach an auxiliary register prepared in $|x_0\rangle$.
+%     \item Perform a controlled group action “kickback” using $g$ on the auxiliary register.
+Specifically, perform the unitary that maps $|y\rangle \otimes |x_0\rangle \mapsto |y\rangle \otimes |g * x_0 \rangle$ for each basis element $|y\rangle$ of the first register.
+(This operation uses the classical $g$ to act on the second register conditioned on the first—essentially, it multiplies the second register’s state by $g$ if the first register is in an appropriate basis state.
+There are various ways to implement this, but conceptually it’s a controlled operation using the known $g$.)
+%     \item Now measure the second register (the auxiliary one) in the computational basis of $X$ to see if it is still $|x_0\rangle$.
+If the state $|\psi\rangle$ was the correct Fourier state $|\$_g\rangle$, one can show that this measurement will yield $x_0$ with high probability (constructive interference causes the $x_0$ component to be strong).
+If $|\psi\rangle$ was not the correct state, the measurement is unlikely to give $x_0$.
+%     \item Accept if and only if the measurement outcome is $x_0$ (i.e. the second register returns to the base state).
+% \end{enumerate}
+
+% The intuition is that the genuine state $|\$_g\rangle$ contains a phase that exactly cancels out the action of $g$ in the verification step, causing the auxiliary register to end up back at $x_0$.
+A counterfeit state, by contrast, would not generally have the right phase relationship, and the auxiliary register’s state would be some superposition over $X$ that is not concentrated on $x_0$, hence likely giving a different outcome upon measurement.
+
+% Zhandry’s scheme is shown to be correct (valid notes pass) and is believed to be secure under the assumption that the group action is one-way.
+The hardness essentially boils down to: given $x_0$ and $|\$_g\rangle$, an adversary cannot figure out a different $g'$ that would produce a second valid state $|\$_{g'}\rangle$ or replicate $|\$_g\rangle$ (because that would solve the hidden subgroup or discrete log type problem in the group action).
+
+% \section{Hartley-Transform Money Scheme Construction}
+% Our scheme modifies the above Fourier-based construction by utilizing the \textbf{quantum Hartley transform (QHT)} in place of the QFT.
+Since the Hartley transform is closely related to the Fourier transform (essentially it produces the real and imaginary parts in a single real-valued transform), one might expect this substitution to be straightforward.
+And indeed, for the minting procedure it largely is: we will use the QHT to create real-amplitude superposition states.
+
+% Concretely, assume again a group action $G \curvearrowright X$ with $|G|=N$. We fix the same generating set $S$ and basepoint $x_0$. The $\mathsf{Mint}_{H}$ (Hartley mint) algorithm:
+% \begin{enumerate}
+%     \item Sample a random $g \leftarrow G$ to be the serial number.
+%     \item Prepare $|0_G, x_0\rangle$ as before.
+%     \item Apply the \emph{quantum Hartley transform} over $G$ to the first register. The Hartley transform (on an abelian group of order $N$) is defined as:
+%     \[
+%        \mathrm{QHT}: |h\rangle \mapsto \frac{1}{\sqrt{N}} \sum_{k \in G} \cas\!\Big(\frac{2\pi \langle k,h \rangle}{N}\Big) |k\rangle,
+%     \] 
+%     where $\mathrm{cas}(\theta) = \cos \theta + \sin \theta$ and $\langle k,h \rangle$ denotes some pairing like an exponent or dot product (for cyclic groups this is just $kh$).
+In simpler terms, $\mathrm{QHT}(|0_G\rangle) = \frac{1}{\sqrt{N}}\sum_{k \in G} |k\rangle$ (because $\cas(0)=1$), \emph{the same uniform superposition as the QFT produces for $|0\rangle$}.
+So after this step, we again have $\frac{1}{\sqrt{N}}\sum_{h \in G} |h\rangle|x_0\rangle$, but crucially the coefficients are all \emph{real} and positive (in fact all $1/\sqrt{N}$).
+%     \item Perform the controlled group action by the first register on the second: $\frac{1}{\sqrt{N}}\sum_{h} |h\rangle |h*x_0\rangle$.
+%     \item Apply the inverse QHT on the first register (which being its own inverse up to a constant factor, is the same operation again since Hartley is symmetric like Fourier).
+Now here is where things differ: after this operation, the joint state will be
+%     \[
+%        \frac{1}{\sqrt{N}} \sum_{h \in G} \cas\!\Big(\frac{2\pi \langle g,h \rangle}{N}\Big)\, |h\rangle \otimes |h*x_0\rangle.
+%     \] 
+%     Because the Hartley transform combines what would be cosine and sine terms, this state is not as nicely factorable as in the Fourier case.
+In the Fourier case, we got $|g\rangle \otimes \text{(orbit state)}$.
+In the Hartley case, we do not get a single basis state in the first register; instead we get a superposition in the first register with real coefficients $c_h = \cas(2\pi\langle g,h\rangle/N)$.
+However, note that $c_h$ is just some real number in $[-1,1]$ depending on $g$ and $h$.
+Another way to express the above state is:
+%     \[
+%       |\$\rangle = \frac{1}{\sqrt{N}} \sum_{x \in X} \Big(\frac{1}{\sqrt{N}}\sum_{h: h*x_0 = x} \cas\!\big(\frac{2\pi \langle g,h \rangle}{N}\big)\Big)\, |x\rangle.
+%     \] 
+%     Since for a given $x\in X$, all $h$ such that $h*x_0=x$ have the form $h = u g$ for a unique $u \in G$ (because the action is free and transitive), one can simplify the internal sum using properties of the cas function.
+But we need not dive into that here.
+%     \item No measurement of the first register is performed.
+In fact, we do not have a nice product state separation, so we cannot simply measure one register to get $g$.
+Instead, the output of minting is just the quantum state $|\$\rangle$ (which is entangled between what used to be two registers) and the known classical serial number $g$ (we know what $g$ we picked).
+% \end{enumerate}
+
+% The resulting money state $|\$\rangle$ has only real amplitudes (because the initial superposition was real and the controlled operation doesn’t introduce complex numbers, and the Hartley transform yields real coefficients).
+In particular, in the computational basis of $X$, the state $|\$\rangle$ is some real-vector state (with both positive and negative values possible).
+We can think of it as a “Hartley orbit state” corresponding to $g$.
+
+% The verification algorithm in our Hartley-based scheme attempts to mirror the Fourier-based verification: it will use the given serial $g$ and try to check the state.
+A first idea would be: do exactly the same as Zhandry’s verify (the group-action kickback and measure).
+However, this fails in certain cases.
+Specifically, the Hartley transform being real causes an ambiguity: it turns out that there exist distinct $g \neq g'$ for which the Hartley-based states $|\$\rangle_g$ and $|\$\rangle_{g'}$ are not orthogonal, and the original verification might accept a forged state that is a certain superposition.
+In fact, the verification algorithm might accept an illegitimate state with some probability bounded away from zero.
+This is the “breakdown” of the straightforward Hartley substitution that we alluded to earlier.
+
+% To address this, our verification algorithm takes a more sophisticated approach:
+% \begin{enumerate}
+%     \item Given $(g, |\psi\rangle)$, it first uses the \textbf{quantum walk-based phase estimation} method (to be detailed in Chapter 6) to \emph{compute the eigenphase corresponding to $g$}.
+In short, we will treat $|\psi\rangle$ as an eigenvector of the group action adjacency matrix with a certain eigenvalue $\lambda$ related to $g$.
+We run a procedure to estimate $\lambda$ to high precision.
+%     \item From the estimated eigenvalue(s), we reconstruct a candidate group element $g^*$ that we believe generated the state.
+(This uses the fact that by running phase estimation for multiple carefully chosen walk durations, one can solve for $g$ as shown in [31].)
+%     \item We check if $g^* = g$ (the serial number provided). If not, we reject, since the state does not match the serial. If yes, we accept.
+% \end{enumerate}
+
+% This procedure essentially extracts the hidden group element from the state and compares it to the claimed serial.
+If an adversary tries to forge a state $|\psi\rangle$ for a known serial $g$, the only way to consistently pass verification is if $|\psi\rangle$ truly encodes the same $g$ in its eigen-spectrum.
+A fake note that was causing trouble for the naive Hartley verification (e.g., a state that is a mixture of two different “Hartley orbit” states) would yield an eigenphase that does not correspond to a single valid $g$, and the algorithm would detect the mismatch.
+
+% The key quantum tool enabling this verification is the continuous-time quantum walk on the group action graph and the ability to simulate it, which we prepared in Chapter 4.
+The walk Hamiltonian $A(X,S)$ has the genuine money state $|\$\rangle_g$ as an eigenstate with a known eigenvalue $\lambda(g)$.
+By running phase estimation on $e^{-iA t}$ with the state $|\psi\rangle$, we attempt to measure that eigenvalue.
+We repeat for a few different values of $t$ (the “twists” or different phases) to get enough information to pinpoint $g$.
+This approach can be viewed as adding extra “twists” to the verification: effectively, each choice of $t$ in phase estimation is like looking at the state in a different interference fringe pattern, analogous to applying different group actions as twists in the verification procedure.
+This is why we described the new verification as using group action twists—by varying a continuous parameter related to the group action’s eigenvalues, we break the symmetry that allowed a counterfeit to slip through.
+
+% We defer the full analysis of the success probabilities and how many repetitions are needed to Chapter 6, where we describe the verification algorithm in detail.
+For now, the takeaway is that by using the quantum walk approach, we can reliably verify Hartley-based money states, restoring security while still enjoying the properties of real amplitudes.
+
+% \section{Efficient Quantum Hartley Transform Implementation}
+% Before moving on to the verification algorithm, we briefly discuss how we implement the quantum Hartley transform (QHT) efficiently, as this is an important practical aspect of our scheme.
+The Fourier transform is well-known to have efficient circuits; for the Hartley transform, fewer results are available, so we contributed a new circuit construction.
+
+% The QHT we need is over an abelian group, which for concreteness one can think of as $\mathbb{Z}_N$ (the general finite abelian group case can usually be reduced to a direct sum of cyclic groups, applying QHT on each cyclic component).
+Classical Hartley transforms have a recursive structure similar to fast Fourier transforms.
+In fact, there are known formulas to express a Hartley transform of size $N$ in terms of two Hartley transforms of size $N/2$ plus some additional linear operations [25].
+We leveraged such structures to design a divide-and-conquer quantum circuit.
+
+% Our algorithm for QHT works roughly as follows:
+% - If $N$ is even, we can express the length-$N$ Hartley transform in terms of two length-$N/2$ Hartley transforms plus a combination of cheap operations (additions, permutations of data, etc.).
+We implement this decomposition recursively as a quantum circuit.
+The base of the recursion is when the size is small (like $N=2$ or $4$, where the transform can be done with a constant number of gates).
+% - We found that by carefully optimizing this recursion and using some known quantum subroutines for certain linear combinations, the overall gate count is improved compared to naive methods or previous proposals [21, 22].
+In particular, our circuit avoids introducing any quantum Fourier transform internally (unlike [22] which computed Hartley via Fourier plus some adjustments), and this yields a purely real rotation-based circuit.
+% - The resulting complexity for an $N$-point QHT is $O(N \log N)$ basic quantum gates (up to polylog factors for precision), which is on par (up to constant factors) with the complexity of a QFT circuit.
+We also derived explicit constants for small cases to show improvements over prior work.
+
+% Additionally, once we have an efficient QHT, we can also implement other related transforms.
+We demonstrate this with the example of the \textbf{quantum sine transform} (QST).
+The sine transform is another real transform closely related to Hartley (in fact, a sine transform can be implemented by a Hartley transform plus some pre- and post-processing).
+We gave a construction that uses one QHT as a subroutine to realize the QST on $N$ points.
+This had a similar complexity of $O(N \log N)$ gates.
+The broader implication is that a family of real-valued transforms (Hartley, sine, cosine, etc.) can all be efficiently performed on quantum hardware, which may have independent applications in signal processing or other quantum algorithms.
+
+% For the purposes of this thesis, the main point is: \emph{we can implement the Hartley transform needed for our money scheme with polynomial efficiency}.
+Thus, switching to the Hartley transform does not introduce any prohibitive cost.
+All steps of minting and verification remain efficient.
+Having covered the construction of the money scheme and the necessary tools, we now proceed to the final piece: the detailed verification algorithm using quantum walks, and an analysis of how it validates genuine banknotes and foils counterfeit attempts.
+% \vspace{1em}
+
+% \chapter{Verification Algorithm Using Quantum Walks}
+% The Hartley-based quantum money scheme introduced in the previous chapter requires a new verification procedure to address the issues that arise from using real amplitude states.
+In this chapter, we describe and analyze the verification algorithm, which leverages continuous-time quantum walks on the group action graph (and their efficient simulation from Chapter 4) to extract the information needed to authenticate a banknote.
+
+%     \section{Challenges with Naïve Verification}
+%     Before detailing the new algorithm, let us briefly recap why the straightforward approach fails.
+In the Fourier-based scheme, verification was done by a single “kickback” operation using the claimed serial $g$, and measuring an auxiliary register.
+In the Hartley-based scheme, if we attempted the analogous one-step verification, we would perform the controlled-$g$ action and measure the auxiliary system.
+A genuine state $|\$_g\rangle$ (the Hartley money state for serial $g$) would cause some interference pattern in the auxiliary register, but unlike the Fourier case, it does not return the auxiliary to $|x_0\rangle$ deterministically.
+In fact, there is an ambiguity: certain superpositions of eigenstates corresponding to $g$ and $-g$ (or other group-related variants) can produce the same measurement statistics in that one-step test.
+This means an adversary might prepare a counterfeit state that is not a legitimate $|\$_g\rangle$ but still passes the one-step verification with non-zero probability.
+Essentially, the Hartley transform being real means we lost some phase information, and a single measurement cannot distinguish some mirrored states.
+
+%     To overcome this, our strategy is to perform a more complete measurement of the state’s “phase spectrum.” Instead of just one operation and measurement, we will use the quantum walk (with Hamiltonian $A = A(X,S)$ as defined earlier) to perform a form of phase estimation.
+
+%     \section{Using Quantum Walks to Extract the Serial}
+%     The central observation is that the money state $|\$_g\rangle$ is an eigenstate of the walk’s Hamiltonian $A$ on the group action Cayley graph.
+To see this, note that $|\$_g\rangle$ (Fourier or Hartley) lies in the subspace spanned by $\{|x\rangle: x \in X\}$ (we no longer explicitly keep the group element register, since after minting it’s entangled or measured away).
+Consider the adjacency operator $A$ acting on a basis state $|x\rangle$.
+By definition,
+%     \[ A |x\rangle = \sum_{s \in S} |s * x\rangle, \] 
+%     summing over all neighbors under the generators.
+Now, $|\$_g\rangle$ is (up to normalization) $\sum_{h \in G} f(h)\, |h * x_0\rangle$ for some coefficient function $f(h)$.
+If one applies $A$ to this state:
+%     \[ A |\$_g\rangle = \sum_{s \in S} \sum_{h \in G} f(h)\, |s * (h * x_0)\rangle = \sum_{h \in G} f(h)\, \sum_{s \in S} |(sh) * x_0\rangle. \]
+%     Now change variable $h' = sh$ in the inner sum.
+Since $s$ runs over all of $S$, $h'$ runs over $S h = \{sh: s \in S\}$ which is exactly the set of neighbors of $h$ in the Cayley graph of $G$.
+For an abelian group, one can show (and it is known from spectral graph theory) that $\sum_{s \in S} |sh * x_0\rangle$ corresponds to the same state as $\lambda_g |h * x_0\rangle$ where $\lambda_g = \sum_{s\in S} \chi_g(s)$ for Fourier states, or $\lambda'_g = \sum_{s\in S} \cas(2\pi \langle g,s\rangle/N)$ for Hartley states.
+In short, $|\$_g\rangle$ is an eigenvector of $A$ with eigenvalue $\lambda_g'$ (a real number that depends on $g$ and $S$).
+This fact was formalized earlier: Lemma 8.2 showed that the money state is an eigenstate of $A$.
+
+%     For example, if $G = \mathbb{Z}_N$ and $S=\{1, -1\}$, a Fourier-based $|\$_g\rangle$ is essentially the character $\chi_g$, and indeed $\chi_g$ is an eigenfunction of the adjacency (which is like a cosine operator) with eigenvalue $2\cos(2\pi g/N)$.
+The Hartley-based state corresponds to a combination of $\chi_g$ and $\chi_{-g}$ (the real and imaginary parts combined), and ends up with the same eigenvalue $2\cos(2\pi g/N)$ as well.
+So either way, the “frequency” $g$ maps to a specific eigenvalue $\lambda$.
+
+%     The verification algorithm will do the following: it will run phase estimation on the unitary $U = e^{iA\tau}$ for some carefully chosen time $\tau$, using the state $|\psi\rangle$ as input.
+Phase estimation is a standard quantum algorithm that, given an eigenstate of $U$, yields an estimate of the eigenphase $2\pi \phi$ (where $e^{i 2\pi \phi}$ is the eigenvalue of $U$) to some specified precision.
+In our case, since $A$ has eigenvalue $\lambda$ on $|\psi\rangle = |\$_g\rangle$, the unitary $e^{iA\tau}$ has eigenvalue $e^{i \lambda \tau}$.
+Thus phase estimation will give us an estimate of $\lambda \tau \pmod{2\pi}$.
+By choosing $\tau$ appropriately, we can ensure $\lambda \tau$ uniquely corresponds to $\lambda$ (within the precision we work at).
+
+%     We cannot run $e^{iA\tau}$ directly, but Chapter 4 showed how to simulate it efficiently with a discrete-time algorithm.
+So when we say “phase estimation on $U = e^{iA\tau}$,” we imply using the simulation routine as a subroutine in the phase estimation circuit.
+This will incur some error $\epsilon$, but we can make it negligible with enough resources.
+
+%     Now, because $\lambda$ (the eigenvalue of $A$) is related to $g$, obtaining $\lambda$ in effect gives us information about $g$.
+However, one eigenvalue might correspond to two possible $g$ values (e.g., $\cos(2\pi g/N) = \cos(2\pi (N-g)/N)$).
+So a single run of phase estimation may not fully determine $g$.
+This is where performing the procedure for multiple different times $\tau$ (or perhaps using a slightly different Hamiltonian) helps.
+By getting $\lambda$ at different scales, we can solve for $g$ using the known functional form of $\lambda$ in terms of $g$.
+
+%     In [31], it was shown that by using two or three carefully chosen multiples of time (or equivalently using the fact that $\lambda$ as a function of $g$ has a known form like a cosine series), one can uniquely recover $g$.
+In our scheme, since $S$ is known and fixed, and presumably $S$ is such that the map $g \mapsto \lambda_g = \sum_{s\in S} \chi_g(s)$ is injective up to trivial symmetries, a few phase estimates suffice.
+For instance, if $S=\{1,-1\}$, knowing $\cos(2\pi g/N)$ to high precision lets you determine $g$ up to the symmetry $g \leftrightarrow N-g$.
+But if we also had a way to break the symmetry (maybe by using an asymmetric choice of $\tau$ or an additional generator in $S$ that is not symmetric), we can get the sign too.
+Alternatively, we run phase estimation on a slightly modified Hamiltonian $A'$ (maybe corresponding to a different generating set that breaks symmetry) if available.
+
+%     For simplicity, let’s suppose two runs with different $\tau$ values are enough. The output of the verification algorithm is then determined by:
+%     - If the estimated $g^*$ from the phase(s) matches the provided serial $g$, output \texttt{accept}.
+%     - Otherwise, output \texttt{reject}.
+
+%     Because a genuine $|\$_g\rangle$ is exactly an eigenstate with eigenvalue $\lambda_g$, phase estimation will return (with high probability) a number very close to $\lambda_g \tau$ modulo $2\pi$.
+Given the precision, we decode it to the nearest valid $\lambda_{g'}$ value, which should be $\lambda_g$.
+Hence we recover $g'=g$ and accept.
+For a counterfeit state, two things can happen:
+%     1.
+The state $|\psi\rangle$ is a superposition of eigenstates (not a single eigenstate).
+In that case, phase estimation will give some distribution of eigenvalues, effectively picking one at random (with probabilities proportional to the projection of $|\psi\rangle$ onto those eigencomponents).
+It is highly unlikely that this random outcome consistently points to the same $g^*$ that the adversary wants (especially if they try to match a specific $g$ that they announced as serial).
+In fact, unless the counterfeit state was itself aligned with one particular eigenvalue, the measurement will likely produce a result that does not correspond to the claimed serial, leading to rejection.
+%     2.
+The state $|\psi\rangle$ happens to be an eigenstate, but with a wrong eigenvalue (i.e., corresponding to some $g' \neq g$).
+In that case, the phase estimation will reliably give $\lambda_{g'}$, and we will decode $g'$ which won’t match the claimed $g$, so we reject.
+This scenario would occur if the adversary somehow prepared a valid-looking state for a different serial $g'$ but presented it with serial $g$—clearly that should be rejected.
+
+%     Thus, the only way to pass is to present a state that is an eigenstate with eigenvalue matching the serial.
+But the only known way to produce such a state is essentially to follow the minting procedure (due to the one-wayness of the group action, they can’t derive $|\$_g\rangle$ without knowing $g$ or breaking the assumption).
+
+%     One might wonder: phase estimation is a probabilistic algorithm; what if it sometimes yields the correct $g^*$ and sometimes not, could an adversary repeat the verification or something?
+In practice, the banknote verification either passes or fails once; an adversary doesn’t get to try multiple times on the same note without potentially decohering it or being caught.
+We design our parameters such that the completeness (accepting a good note) is very high and the soundness (accepting a forgery) is extremely low, say negligible in $n$.
+This might involve repeating the phase estimation a constant number of times to amplify confidence, or using a high precision so that the error probability is negligible.
+
+%     Finally, our algorithm implicitly uses the ability to perform the controlled-$U$ operations for phase estimation.
+That is non-trivial but our quantum walk simulation provided a way to implement $e^{iA\tau}$, and controlled versions can be constructed by controlling each gate in the simulation (which increases complexity by at most a factor poly(n)).
+We have to ensure that the simulation error is accounted for in the phase estimation accuracy—this can be handled by choosing simulation parameters fine enough that the error is smaller than the inverse of our runtime or something along those lines.
+
+%     \section{Detailed Verification Procedure}
+%     To summarize, here is a more step-by-step description of the verification algorithm for a banknote $(g, |\psi\rangle)$:
+%     \begin{enumerate}
+%         \item **Preparation:** Determine a set of one or more time parameters $\{\tau_1, \tau_2, \dots, \tau_m\}$ to be used for phase estimation.
+These might be hardcoded or depend on $N$ and $S$.
+For example, $\tau_1$ could be a basic time and $\tau_2$ another that breaks degeneracy.
+%         \item **Phase Estimation Rounds:** For each $\tau_j$:
+%         \begin{enumerate}
+%             \item Use the quantum walk simulation circuit to implement controlled-$e^{iA \tau_j}$ on $|\psi\rangle$.
+(In practice, we append an ancilla register to accumulate the phase, as in standard phase estimation algorithms.
+We prepare a uniform superposition over some range of time steps, apply controlled-$U$ gates, and perform inverse Fourier transform on the phase register to get an estimate.
+This is the standard routine.)
+%             \item Measure the phase register to obtain an estimate $\tilde{\phi}_j$ of $\lambda_g \tau_j / (2\pi)$ (mod 1).
+Multiply by $2\pi/\tau_j$ to get an estimate $\tilde{\lambda}_j$ of $\lambda_g$.
+%         \end{enumerate}
+%         \item **Compute Serial Candidate:** From the collection $\{\tilde{\lambda}_j\}$, solve for the group element $g^*$ that would produce those eigenvalues.
+This might involve inverting the known relation $\lambda = \sum_{s\in S}\cas(2\pi \langle g, s\rangle/N)$ or whatever the formula is in our context.
+Because of estimation error, we choose the nearest matching $g^*$ in $G$ that would give eigenvalues close to the $\tilde{\lambda}_j$ observed.
+%         \item **Accept/Reject:** If $g^* = g$ (and all rounds of phase estimation yielded results consistent with a single $g^*$, which should happen for a valid note), then output \texttt{accept}.
+Otherwise, output \texttt{reject}.
+%     \end{enumerate}
+
+%     This algorithm may seem complex, but it can be optimized.
+In practice, we could combine multiple phase estimation steps into one larger quantum circuit that extracts $g$ in one go, but conceptually, it’s easier to think of them separately.
+
+%     \section{Analysis of Security and Efficiency}
+%     The new verification algorithm is more involved than the original Fourier-based one, so we must check that it is still efficient and that it indeed thwarts counterfeiting.
+
+%     **Efficiency:** Each phase estimation round uses polynomial-time quantum operations.
+The Hamiltonian simulation of $e^{iA\tau}$ for sparse $A$ on $N$-dimensional space can be done in $\operatorname{poly}(\log N)$ time (since queries to the group action oracle are $O(1)$ and $|S|$ is small).
+The phase estimation itself might need $O(\log N)$ qubits of precision to distinguish different $g$ values, and $O(\log N)$ repetitions of $U$ in superposition.
+Overall, each round is $\operatorname{poly}(n)$ time.
+A constant number of rounds doesn’t change the polynomial class.
+So yes, verification is QPT.
+In fact, in asymptotic terms, if minting took $\tilde{O}(n^c)$ time, verification might take $\tilde{O}(n^{c+1})$ or similar due to extra overhead, but still polynomial.
+
+%     **Completeness:** A genuine banknote state $|\$_g\rangle$ will be accepted with high probability.
+The state is an eigenstate of $A$, so phase estimation yields exactly $\lambda_g$ (with small error $\epsilon$).
+Decoding that yields $g^* = g$.
+The only possible errors are from phase estimation not being perfect: there is a small probability it gives the wrong eigenvalue estimate (exponentially small in the number of ancilla qubits used).
+By choosing parameters, we ensure this error is negligible, say $< 2^{-n}$ or similar.
+So the chance a real note is mistakenly rejected is negligible.
+
+%     **Soundness:** A counterfeiter’s goal is to have $\mathsf{Verify}(g, |\psi\rangle) = \texttt{accept}$ for some $|\psi\rangle$ that they created without running $\mathsf{Mint}$.
+Essentially, they either try to reuse a state they already saw or combine states to get two accepted notes, etc.
+If they attempt to create a new state for an unused serial $g$, they face the following:
+%     - If $|\psi\rangle$ is not an eigenstate of $A$, when we run phase estimation, the outcome is a random eigenvalue from its spectral decomposition.
+It would be a huge coincidence if that random eigenvalue corresponded to exactly the claimed $g$.
+And even if by some luck one phase estimation round gave a favorable result, with two rounds the chance to consistently impersonate the same $g$ is even smaller.
+In fact, by the union bound, the probability that a wrong state passes all checks should be negligible.
+A rigorous argument would be that if $|\psi\rangle$ has overlap on eigenstates $\{|e_j\rangle\}$ with eigenvalues $\lambda_j$, then the verification accepts only if for all $j$ with nonzero overlap, the decoded $g_j$ equals the claimed $g$.
+If any overlap component has a different underlying group element, that component will cause failure in at least one of the phase estimation rounds with high probability.
+Unless the state was aligned to one particular $g'$, in which case the best they can do is claim it is $g'$.
+%     - If $|\psi\rangle$ \emph{is} an eigenstate but for $g' \neq g$, then our algorithm will find $g'$ and compare to $g$ and reject.
+So the adversary would have to guess the serial number’s eigenstate perfectly, which means they basically guessed the bank’s secret or solved the one-way problem.
+
+%     The most cunning forgery could be to use a genuine note $(g, |\$_g\rangle)$ and try to produce a second independent state $|\$_g\rangle$ for the same $g$.
+But that is essentially copying a quantum state which is unknown to them (they only know $g$ classically).
+Given $g$, can they produce $|\$_g\rangle$?
+That’s the one-way group action problem: producing $|\$_g\rangle$ is as hard as computing $g*x_0$ for all group elements in superposition, which requires knowledge of $g$ in a way that they don't have (they know $g$ but to create the superposition exactly with correct phases is akin to solving for the hidden phase structure—likely hard without the trapdoor).
+In fact, if they could do that efficiently for any given $g$, they would break the scheme by minting their own money.
+So by assumption, that’s infeasible.
+
+%     Thus, the only resource the adversary has is perhaps other genuine notes they possess.
+Could they entangle two notes or something to produce two valid ones?
+If they have one note, trying to make two will likely destroy the original or produce two imperfect copies that fail verification (no-cloning strikes again).
+If they have two different notes $(g_1, |\$_{g_1}\rangle)$ and $(g_2, |\$_{g_2}\rangle)$, those states are independent, and forging a new one still reduces to above.
+
+%     Therefore, we argue the scheme remains secure: forging in any meaningful sense would require solving a hard problem (inverting the group action or cloning a quantum state).
+
+%     In conclusion, by using continuous-time quantum walks and phase estimation, our verification algorithm retrieves the hidden serial number encoded in the quantum money state and compares it to the claimed serial.
+This not only fixes the issue introduced by using the Hartley transform (real amplitudes), but it does so in polynomial time.
+We have thus achieved a public-key quantum money scheme based on standard assumptions (one-way group actions) with an extra novel feature of using real-valued quantum states and demonstrating the power of quantum walks in quantum cryptanalysis and verification.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section*{Discrete-Time Quantum Walk on Cayley Graphs}
@@
 
-% \section*{How Quantum Money Works}
-% At its core, quantum money relies on two key principles of quantum mechanics: the \textit{no-cloning theorem} and the \textit{observer effect}.
-
-% \subsection*{Encoding Information in Quantum States}
-% \begin{itemize}
-%     \item Each quantum bill contains a unique quantum state, such as a set of qubits encoded in superposition.
-%     \item These states are generated and stored by the issuing authority (e.g., a central bank) using a secret algorithm.
-% \end{itemize}
-
-% \subsection*{Verification Process}
-% \begin{itemize}
-%     \item The issuing authority also generates a verification protocol, allowing a legitimate quantum bill to be authenticated.
-%     \item When a user presents a quantum bill for verification, the authority measures the encoded quantum states using the pre-determined protocol.
-%     \item If the measured states align with the expected values, the bill is deemed valid.
-% \end{itemize}
-
-% \subsection*{Unforgeability}
-% \begin{itemize}
-%     \item Due to the \textit{no-cloning theorem}, it is impossible to copy an unknown quantum state without altering it.
-%     \item Any attempt to measure or duplicate the quantum state results in a disturbance detectable during verification.
-% \end{itemize}
-
-% \section*{Key Principles Underpinning Quantum Money}
-% \begin{enumerate}
-%     \item \textbf{No-Cloning Theorem:} The no-cloning theorem states that an unknown quantum state cannot be perfectly copied.
+\section*{How Quantum Money Works}
+At its core, quantum money relies on two key principles of quantum mechanics: the \textit{no-cloning theorem} and the \textit{observer effect}.
+
+\subsection*{Encoding Information in Quantum States}
+\begin{itemize}
+    \item Each quantum bill contains a unique quantum state, such as a set of qubits encoded in superposition.
+    \item These states are generated and stored by the issuing authority (e.g., a central bank) using a secret algorithm.
+\end{itemize}
+
+\subsection*{Verification Process}
+\begin{itemize}
+    \item The issuing authority also generates a verification protocol, allowing a legitimate quantum bill to be authenticated.
+    \item When a user presents a quantum bill for verification, the authority measures the encoded quantum states using the pre-determined protocol.
+    \item If the measured states align with the expected values, the bill is deemed valid.
+\end{itemize}
+
+\subsection*{Unforgeability}
+\begin{itemize}
+    \item Due to the \textit{no-cloning theorem}, it is impossible to copy an unknown quantum state without altering it.
+    \item Any attempt to measure or duplicate the quantum state results in a disturbance detectable during verification.
+\end{itemize}
+
+\section*{Key Principles Underpinning Quantum Money}
+\begin{enumerate}
+    \item \textbf{No-Cloning Theorem:} The no-cloning theorem states that an unknown quantum state cannot be perfectly copied.
 This makes quantum money inherently secure, as counterfeiters cannot reproduce the quantum states encoded in legitimate currency.
-%     \item \textbf{Measurement Disturbance:} Observing or measuring a quantum state generally alters it.
+    \item \textbf{Measurement Disturbance:} Observing or measuring a quantum state generally alters it.
 This ensures that any unauthorized attempt to inspect the quantum money will render it invalid, as the encoded states will no longer match their original form.
-%     \item \textbf{Randomness and Superposition:} Quantum money utilizes superposition to encode information.
+    \item \textbf{Randomness and Superposition:} Quantum money utilizes superposition to encode information.
 For example, a single qubit in superposition may represent both $0$ and $1$ simultaneously until measured.
 The randomness of these states makes predicting or reproducing them without knowledge of the original encoding impossible.
-%     \item \textbf{Entanglement (Optional Feature):} Some implementations of quantum money involve quantum entanglement, where pairs of quantum states are interconnected.
+    \item \textbf{Entanglement (Optional Feature):} Some implementations of quantum money involve quantum entanglement, where pairs of quantum states are interconnected.
 Changes to one entangled state directly affect its pair, adding another layer of security against forgery.
-% \end{enumerate}
+\end{enumerate}
 

### 2025-04-07 draft.tex
chapter 4 updated

@@
 \usepackage{setspace}
+
+\newcommand{\opnorm}[1]{\left\lVert #1 \right\rVert}
 
@@
 
+From this point forward, we assume the generating set \( Q \) is small, i.e., \( \abs{Q} = \operatorname{poly}(\log \abs{G}) \).
+In the first construction (where \( X = G \)), the walk \( e^{-iAt} \) can be efficiently implemented even for values of \( t \) that are exponentially large in \( \log \abs{G} \).
+This is a consequence of the identity:
+\begin{equation}
+    \label{eq:adjmat-fb}
+    e^{-iAt} = \operatorname{QFT}_G \left( \sum_{a \in G} e^{-i\lambda_a t} \ket{a} \bra{a} \right) \operatorname{QFT}_G^*,
+\end{equation}
+where \( \operatorname{QFT}_G \) and its inverse can be implemented in \( \operatorname{poly}(\log \abs{G}) \) time.
+Moreover, the diagonal phase unitary \( \ket{a} \mapsto e^{-i\lambda_a t} \ket{a} \) is also efficient to implement, since the eigenvalues \( \lambda_a \) can be computed classically to arbitrary precision in \( \operatorname{poly}(\log \abs{G}) \) time.
+
+In contrast, the group-action setting presents greater computational difficulty.
+Although the states \( \ket{G^{(h)} * x} \) play a role analogous to the Fourier basis states \( \ket{\hat{h}} \), the presence of the action \( * \) makes the situation more subtle.
+In particular, implementing general transformations over these states is difficult; we are typically limited to operations of the form \( \ket{y} \mapsto \ket{a * y} \) for \( a \in G \).
+As a result, no efficient decomposition similar to~\eqref{eq:adjmat-fb} is known in the group-action setting.
+Instead, the best we can express is the spectral decomposition:
+\[
+e^{-iAt} = \sum_{h \in G} e^{-i\lambda_h t} \ket{G^{(h)} * x} \bra{G^{(h)} * x}.
+\]
+
+Despite this limitation, the adjacency matrix \( A \) retains a high degree of sparsity and algebraic structure.
+In the next section, we will show that for \( t = \operatorname{poly}(\log \abs{G}) \), the walk \( e^{-iAt} \) can still be efficiently approximated to polynomial accuracy.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Simulating continuous-time walks}
+Childs and Berry, Childs, and Kothari showed that continuous-time quantum walks can be simulated using discrete-time quantum walks.
+Since our approach relies on their methods, we begin by outlining the relevant notation and framework.
+
+Let \( H \) be a Hamiltonian of dimension \( N = 2^n \), and define \( \opnorm{H}_{\mathrm{max}} = \max_{i, j} \abs{H_{ij}} \).
+To facilitate the simulation, we expand the Hilbert space from \( \mathbb{C}^N \) to \( \mathbb{C}^{2N} \otimes \mathbb{C}^{2N} \) by appending an ancilla qubit initialized to \( \ket{0} \) and duplicating the resulting space.
+
+To define the discrete-time walk operator, we first construct an orthonormal set of states:
+\begin{align}
+    \ket{\phi_{j0}} & := \frac{1}{\sqrt{d}} \sum_{\ell \in F_j} \ket{\ell} \left( \sqrt{\frac{H_{j\ell}^*}{K}} \ket{0} + \sqrt{1 - \frac{\abs{H_{j\ell}^*}}{K}} \ket{1} \right), \label{eq:walk-sim} \\
+    \ket{\phi_{j1}} & := \ket{0} \ket{1}, \nonumber
+\end{align}
+where \( F_j \) denotes the set of nonzero entries in column \( j \) of \( H \), and \( K \ge \opnorm{H}_{\mathrm{max}} \) is a fixed constant.
+
+Based on these states, we define the isometry \( T : \mathbb{C}^{2N} \to \mathbb{C}^{2N} \otimes \mathbb{C}^{2N} \) as follows:
+\begin{equation}
+    \label{eq:walk-isom}
+    T := \sum_{j = 0}^{N - 1} \sum_{b \in \{0, 1\}} (\ket{j}\bra{j} \otimes \ket{b}\bra{b}) \otimes \ket{\phi_{jb}}.
+\end{equation}
+
+The discrete-time quantum walk operator is then defined as
+\[
+W = iS(2TT^* - \mathbf{1}),
+\]
+where \( S \) is the swap operator acting as
+\[
+S \ket{j_1} \ket{b_1} \ket{j_2} \ket{b_2} = \ket{j_2} \ket{b_2} \ket{j_1} \ket{b_1},
+\]
+for all \( 0 \le j_1, j_2 < N \) and \( b_1, b_2 \in \{0, 1\} \).
+
+To efficiently simulate the continuous-time evolution \( e^{-iHt} \), it suffices to implement the isometry \( T \), its adjoint \( T^* \), and the walk operator \( W \) efficiently.
+%  Assuming black-box (oracle) access to the entries of \( H \), the following result holds:
+
+% \begin{theorem}[{\cite[Theorem 1]{berry2015hamiltonian}}]
+% \label{thm:sparse-sim}
+% Let \( H \) be a \( d \)-sparse Hamiltonian acting on \( n \) qubits. Then the unitary \( e^{-iHt} \) can be approximated to within error \( \epsilon \) using
+% \[
+% O\left( \tau \frac{\log(\tau / \epsilon)}{\log\log(\tau / \epsilon)} \right)
+% \]
+% queries to \( H \), and
+% \[
+% O\left( \tau \left[ n + \log^{5 / 2}(\tau / \epsilon) \right] \frac{\log(\tau / \epsilon)}{\log\log(\tau / \epsilon)} \right)
+% \]
+% additional elementary gates, where \( \tau = d \cdot \opnorm{H}_{\mathrm{max}} \cdot t \).
+% \end{theorem}
+
+\subsection{Simulating group action quantum walks.}
+Assume \( t = \operatorname{poly}(\log \abs{G}) \).
+We show that the continuous-time walk \( W = e^{-iAt} \) can be efficiently simulated using the discrete-time quantum walk framework developed in~\cite{childs2010relationship, berry2015hamiltonian}.
+Recall the isometry \( T \) defined in Equation~\eqref{eq:walk-isom}, where the states \( \ket{\phi_b} \) are as given in Equation~\eqref{eq:walk-sim}.
+To carry out the simulation, it suffices to show that the isometry \( T \), its adjoint \( T^* \), and the discrete-time walk operator
+\[
+W = iS(2TT^* - \mathbf{1})
+\]
+can all be efficiently implemented in the group-action setting.
+
+Let \( \Gamma = (X, E) \) be the Cayley graph associated with the group action \( (G, X, *) \), and let \( A \) denote its adjacency matrix.
+The Hamiltonian \( H \) of interest is simply \( A \), indexed by elements of \( X \).
+In this context, the isometry \( T \) takes the form:
+\begin{align*}
+T
+& := \sum_{y \in X} \sum_{b \in \{0, 1\}} (\ket{y}\bra{y} \otimes \ket{b}\bra{b}) \otimes \ket{\phi_{yb}} \\
+& = \sum_{y \in X} \sum_{b \in \{0, 1\}} \ket{y} \ket{b} \ket{\phi_{yb}} \bra{y} \bra{b}.
+\end{align*}
+
+Because of the structure of $\Gamma$, the states ....
+simplify as follows.
+First, since the set $Q$ is symmetric, the graph $\Gamma$ is undirected and the adjacency matrix $A$ is symmetric with non-negative entries; the nonzero entries of $A$ are all equal to $1$.
+Therefore, we can set $K = {A}_{\mathrm{max}} = 1$.
+As a result, for $y \in X$, the state $\ket{\phi_{y0}}$ becomes
+\[ \ket{\phi_{y0}} = \frac{1}{\sqrt{\abs{Q}}} \sum_{q \in Q} \ket{q * y} \ket{0}. \]
+We now describe how to implement the isometry \( T \) by constructing efficient unitaries \( U_0 \) and \( U_1 \), where each \( U_b \) acts as
+\[
+U_b : \ket{0} \ket{y, b} \ket{0, 0} \mapsto \ket{0} \ket{y, b} \ket{\phi_{yb}}, \quad b \in \{0, 1\},
+\]
+with the first register serving as an ancilla.
+
+The unitary \( U_1 \) is straightforward to implement, since \( \ket{\phi_{y1}} = \ket{0} \ket{1} \) is independent of \( y \). We now focus on the construction of \( U_0 \).
+
+Because \( Q \subset G \) is a small set (i.e., \( \abs{Q} = \operatorname{poly}(\log \abs{G}) \)), we can construct an efficient unitary \( V_Q : \mathbb{C}^Q \to \mathbb{C}^Q \) such that
+\[
+V_Q \ket{0} = \frac{1}{\sqrt{\abs{Q}}} \sum_{q \in Q} \ket{q}.
+\]
+Applying \( V_Q \otimes \mathbf{1} \) to the state \( \ket{0} \ket{y, 0} \ket{0, 0} \) produces:
+\[
+\frac{1}{\sqrt{\abs{Q}}} \sum_{q \in Q} \ket{q} \ket{y, 0} \ket{0, 0}.
+\]
+
+Next, we apply the unitary \( V_1 \), defined by:
+\[
+V_1 : \ket{q} \ket{y, 0} \ket{0, 0} \mapsto \ket{q} \ket{y, 0} \ket{q * y, 0}.
+\]
+
+Following this, we uncompute the first register to recover \( \ket{0} \ket{y, 0} \ket{\phi_{y0}} \). This is achieved by applying the unitary \( V_2 \), defined as:
+\[
+V_2 : \ket{q} \ket{y, 0} \ket{q * y, 0} \mapsto \ket{0} \ket{y, 0} \ket{q * y, 0}.
+\]
+Since \( Q \) is small, we can efficiently determine \( q \) from the pair \( (y, q * y) \) by exhaustively checking each \( q \in Q \).
+Thus, \( V_2 \) (and therefore \( U_0 \)) can be implemented efficiently.
+
+To implement \( U_0^* : \ket{0} \ket{y, 0} \ket{\phi_{y0}} \mapsto \ket{0} \ket{y, 0} \ket{0, 0} \), we sequentially apply \( V_2^* \), followed by \( V_1^* \), and finally \( V_Q^* \otimes \mathbf{1} \).
+Since each of these unitaries can be implemented efficiently, it follows that \( U_0^* \) is also efficient.
+
+We now construct the isometry \( T \) using a conditional unitary \( U_T \), which applies either \( U_0 \) or \( U_1 \) depending on the value of the qubit \( b \). That is,
+\[
+U_T = \text{Controlled-}U_b \quad \text{with control on } b \in \{0,1\}.
+\]
+
+Next, we demonstrate that the walk unitary
+\[
+W = iS(2TT^* - \mathbf{1})
+\]
+can be applied efficiently. This reduces to implementing the reflection \( 2TT^* - \mathbf{1} \), which we analyze as follows:
+\begin{align*}
+2\ket{0}\bra{0} \otimes TT^* - \mathbf{1}
+&= 2\ket{0}\bra{0} \otimes \sum_{y \in X} \sum_{b \in \{0,1\}} \ket{y,b} \ket{\phi_{yb}} \bra{y,b} \bra{\phi_{yb}} - \mathbf{1} \\
+&= 2\sum_{y \in X} \sum_{b \in \{0,1\}} \ket{0} \ket{y,b} \ket{\phi_{yb}} \bra{0} \bra{y,b} \bra{\phi_{yb}} - \mathbf{1} \\
+&= U_T \left( 2 \sum_{y \in X} \sum_{b \in \{0,1\}} \ket{0} \ket{y,b} \ket{0,0} \bra{0} \bra{y,b} \bra{0,0} - \mathbf{1} \right) U_T^* \\
+&= U_T \left( 2\ket{0}\bra{0} \otimes \mathbf{1}_{X,b} \otimes \ket{0,0}\bra{0,0} - \mathbf{1} \right) U_T^*.
+\end{align*}
+
+Since \( U_T \), \( U_T^* \), and the operator \( 2\ket{0}\bra{0} \otimes \mathbf{1}_{X,b} \otimes \ket{0,0}\bra{0,0} - \mathbf{1} \) can all be implemented efficiently, it follows that the reflection \( 2\ket{0}\bra{0} \otimes TT^* - \mathbf{1} \) is also efficient.
+
+Finally, for any input state \( \ket{\psi} \), the reflection acts as:
+\[
+\left(2\ket{0}\bra{0} \otimes TT^* - \mathbf{1} \right) \ket{0} \ket{\psi} = \ket{0} \left(2TT^* - \mathbf{1} \right) \ket{\psi},
+\]
+confirming that the full walk operator \( W \) can be implemented efficiently in the group-action setting.
+
 \section{Hamiltonian Structure and Sparsity}

### 2025-04-08 draft.tex
chapters 5,6 added

@@
 \documentclass[12pt]{report}
+
 \usepackage{amsmath, amssymb, amsthm}
@@
 \usepackage{algorithm}
-\usepackage{algorithmic}
+% \usepackage{algorithmic}
 \usepackage{tikz}
@@
 \usepackage{setspace}
+\usepackage{algorithm}
+\usepackage{algpseudocode}
 
@@
 \singlespacing
+
+\newcommand{\cas}{\mathrm{cas}}
+\newcommand{\cht}{\mathsf{H}}
+\newcommand{\qht}{\mathsf{QHT}}
+\newcommand{\cft}{\mathsf{F}}
+\newcommand{\qft}{\mathsf{QFT}}
+\newcommand{\comph}{\mathsf{cmpIndex}}
+\newcommand{\gen}{\mathsf{Gen}}
+\newcommand{\ver}{\mathsf{Ver}}
 
@@
 
-\section{Hamiltonian Structure and Sparsity}
-
-\section{Quantum Walk-Based and QSP Simulation}
-
-\section{Complexity Analysis}
+% \section{Hamiltonian Structure and Sparsity}
+
+% \section{Quantum Walk-Based and QSP Simulation}
+
+% \section{Complexity Analysis}
 
@@
 
+We now present our public-key quantum money scheme based on group actions and the Hartley transform.
+We begin by reviewing Zhandry’s quantum money scheme from abelian group actions (which uses the Fourier transform) as a baseline.
+Then we describe our Hartley-transform-based variant and discuss its properties.
+The quantum Hartley transform will play a central role in both the minting and verification of banknotes.
+
+\section{Public-Key Quantum Money: Definitions}
+A public-key quantum money scheme consists of two algorithms, traditionally called $\mathsf{Mint}$ and $\mathsf{Verify}$:
+\begin{itemize}
+    \item $\mathsf{Gen}(1^n)$ is a probabilistic quantum polynomial-time (QPT) algorithm that, given a security parameter $n$, outputs a pair $(s, |\$\rangle)$.
+Here $s$ is a classical string called the \emph{serial number} (or public key) and $|\$\rangle$ is a quantum state representing the banknote.
+We often call the pair $(s, |\$\rangle)$ a banknote, and $s$ by itself the serial number of that banknote.
+    \item $\mathsf{Verify}(s, |\$\rangle)$ is a QPT algorithm (which may be implemented as a quantum circuit acting on the state $|\$\rangle$ and some ancillary workspace).
+It takes as input a serial number $s$ and an alleged quantum banknote state $|\$\rangle$.
+It outputs $\mathtt{accept}$ (valid) or $\mathtt{reject}$ (invalid).
+\end{itemize}
+
+We require two properties from such a scheme:
+\begin{description}
+    \item[Correctness:] For any valid output $(s, |\$\rangle)$ of $\mathsf{Mint}(1^n)$, the verification algorithm accepts with high probability.
+Formally, $\Pr[\mathsf{Verify}(s, |\$\rangle) = \mathtt{accept}]$ should be very close to 1 (typically we require it to be $1 - negl(n)$, where $negl(n)$ denotes a negligible function in $n$).
+    \item[Security (Unforgeability):] No efficient adversary, given one or more genuine banknotes, can produce a new valid banknote.
+In the strongest formulation, if an adversary is given a single valid $(s, |\$\rangle)$, it should be infeasible for them to produce two quantum states $|\$'\rangle$ and $|\$''\rangle$ such that $\mathsf{Verify}(s, |\$'\rangle) = \mathsf{Verify}(s, |\$''\rangle) = \mathtt{accept}$ (i.e., they cannot create a second copy that passes verification while retaining the original).
+More generally, even given multiple banknotes, the adversary should not be able to create new ones with fresh serial numbers that pass verification.
+This captures the idea that quantum money cannot be counterfeited.
+\end{description}
+
+In a \emph{public-key} scheme, the verifier uses only the public information (here, the serial number and any scheme-wide public parameters) to check validity, and does not need any secret key.
+The bank (mint) may have a secret key to produce the states, but after minting, the bank’s involvement is not needed.
+In our scheme, the serial number will effectively contain the information needed for public verification (similar to how a classical bill might have a number anyone can look up, except here it’s used in a quantum procedure).
+
+We next outline Zhandry’s scheme, which our scheme builds upon.
+
+\section{Fourier-Based Quantum Money from Group Actions}
+Zhandry’s quantum money scheme [31] is built on an abelian group action $G \curvearrowright X$.
+We have a family of group actions parameterized by the security parameter $n$ (so the size of $G$ grows with $n$).
+For simplicity, assume $|G| = N$.
+The scheme also fixes a particular element $x_0 \in X$ that everyone knows (a public base point in $X$).
+
+The minting algorithm $\mathsf{Mint}$ in Zhandry’s scheme works as follows (informally):
+\begin{enumerate}
+    \item On input $1^n$, sample a random group element $g \leftarrow G$. This $g$ will serve as the serial number $s$ for the banknote.
+    \item Prepare two registers: the first is a group element register, initialized to $|0_G\rangle$ (an encoding of the identity element of $G$), and the second is an $X$-register initialized to $|x_0\rangle$.
+    \item Apply the quantum Fourier transform over $G$ to the first register. This creates a uniform superposition over $G$: 
+    \[
+    \frac{1}{\sqrt{N}} \sum_{h \in G} |h\rangle \otimes |x_0\rangle\,.
+    \] 
+    \item Now apply the group action in a controlled manner: for each basis state $|h\rangle$ in the first register, apply $h$’s action on the second register. This transforms the joint state into 
+    \[
+    \frac{1}{\sqrt{N}} \sum_{h \in G} |h\rangle \otimes |h * x_0\rangle\,,
+    \] 
+    which is an entangled state between a superposition of group elements and their corresponding $X$-elements.
+    \item Apply the inverse QFT (which is the adjoint of the QFT) on the first register. This recombines the amplitudes in the first register. The result (by properties of the QFT) can be shown to be 
+    \[
+    \frac{1}{\sqrt{N}} \sum_{h \in G} \omega^{\langle g,\,h \rangle} |h\rangle \otimes |h * x_0\rangle\,,
+    \] 
+    where $\omega^{\langle g,\,h \rangle}$ denotes the phase picked up that depends on $g$ and $h$.
+In fact, this state can be written as $|g\rangle \otimes \frac{1}{\sqrt{N}}\sum_{h \in G} |h * x_0\rangle$; essentially, the first register ends up in $|g\rangle$ (the serial number) and the second register is an equal superposition of all elements of $X$ in the orbit of $x_0$ (which is $X$ itself, since the action is transitive) but weighted by a phase related to $g$.
+This is the so-called group-action Fourier state.
+    \item The first register (which contains $|g\rangle$) is measured in the computational basis, yielding the random serial number $g$ and collapsing the second register to a state that we will denote $|\$_g\rangle$.
+This $|\$_g\rangle$ is the actual quantum money state corresponding to serial $g$.
+    \item Output the pair $(s = g,\; |\$\rangle = |\$_g\rangle)$.
+\end{enumerate}
+
+In the above, a bit of algebra reveals that $|\$_g\rangle = \frac{1}{\sqrt{N}} \sum_{h \in G} \chi_g(h)\, |h * x_0\rangle$, where $\chi_g(h) = \omega^{\langle g,\,h \rangle}$ is essentially the character of $G$ indexed by $g$.
+In other words, $|\$_g\rangle$ is (up to global phase) the state one gets by applying the representation (character) $\chi_g$ to weight the superposition over the orbit $X$.
+These states for different $g$ are almost orthogonal and can be distinguished with the right measurement.
+
+The verification algorithm $\mathsf{Verify}(g, |\$_g\rangle)$ for Zhandry’s scheme goes as follows:
+\begin{enumerate}
+    \item Given the purported serial number $g \in G$ and an input state $|\psi\rangle$ (which should equal $|\$_g\rangle$ if genuine), attach an auxiliary register prepared in $|x_0\rangle$.
+    \item Perform a controlled group action “kickback” using $g$ on the auxiliary register.
+Specifically, perform the unitary that maps $|y\rangle \otimes |x_0\rangle \mapsto |y\rangle \otimes |g * x_0 \rangle$ for each basis element $|y\rangle$ of the first register.
+(This operation uses the classical $g$ to act on the second register conditioned on the first—essentially, it multiplies the second register’s state by $g$ if the first register is in an appropriate basis state.
+There are various ways to implement this, but conceptually it’s a controlled operation using the known $g$.)
+    \item Now measure the second register (the auxiliary one) in the computational basis of $X$ to see if it is still $|x_0\rangle$.
+If the state $|\psi\rangle$ was the correct Fourier state $|\$_g\rangle$, one can show that this measurement will yield $x_0$ with high probability (constructive interference causes the $x_0$ component to be strong).
+If $|\psi\rangle$ was not the correct state, the measurement is unlikely to give $x_0$.
+    \item Accept if and only if the measurement outcome is $x_0$ (i.e. the second register returns to the base state).
+\end{enumerate}
+
+The intuition is that the genuine state $|\$_g\rangle$ contains a phase that exactly cancels out the action of $g$ in the verification step, causing the auxiliary register to end up back at $x_0$.
+A counterfeit state, by contrast, would not generally have the right phase relationship, and the auxiliary register’s state would be some superposition over $X$ that is not concentrated on $x_0$, hence likely giving a different outcome upon measurement.
+
+Zhandry’s scheme is shown to be correct (valid notes pass) and is believed to be secure under the assumption that the group action is one-way.
+The hardness essentially boils down to: given $x_0$ and $|\$_g\rangle$, an adversary cannot figure out a different $g'$ that would produce a second valid state $|\$_{g'}\rangle$ or replicate $|\$_g\rangle$ (because that would solve the hidden subgroup or discrete log type problem in the group action).
+
+\section{Hartley-Transform Money Scheme Construction}
+Our scheme modifies the above Fourier-based construction by utilizing the \textbf{quantum Hartley transform (QHT)} in place of the QFT.
+Since the Hartley transform is closely related to the Fourier transform (essentially it produces the real and imaginary parts in a single real-valued transform), one might expect this substitution to be straightforward.
+And indeed, for the minting procedure it largely is: we will use the QHT to create real-amplitude superposition states.
+
+Concretely, assume again a group action $G \curvearrowright X$ with $|G|=N$. We fix the same generating set $S$ and basepoint $x_0$. The $\mathsf{Mint}_{H}$ (Hartley mint) algorithm:
+\begin{enumerate}
+    \item Sample a random $g \leftarrow G$ to be the serial number.
+    \item Prepare $|0_G, x_0\rangle$ as before.
+    \item Apply the \emph{quantum Hartley transform} over $G$ to the first register. The Hartley transform (on an abelian group of order $N$) is defined as:
+    \[
+       \mathrm{QHT}: |h\rangle \mapsto \frac{1}{\sqrt{N}} \sum_{k \in G} \cas \!\Big(\frac{2\pi \langle k,h \rangle}{N}\Big) |k\rangle,
+    \] 
+    where $\mathrm{cas}(\theta) = \cos \theta + \sin \theta$ and $\langle k,h \rangle$ denotes some pairing like an exponent or dot product (for cyclic groups this is just $kh$).
+In simpler terms, $\mathrm{QHT}(|0_G\rangle) = \frac{1}{\sqrt{N}}\sum_{k \in G} |k\rangle$ (because $cas(0)=1$), \emph{the same uniform superposition as the QFT produces for $|0\rangle$}.
+So after this step, we again have $\frac{1}{\sqrt{N}}\sum_{h \in G} |h\rangle|x_0\rangle$, but crucially the coefficients are all \emph{real} and positive (in fact all $1/\sqrt{N}$).
+    \item Perform the controlled group action by the first register on the second: $\frac{1}{\sqrt{N}}\sum_{h} |h\rangle |h*x_0\rangle$.
+    \item Apply the inverse QHT on the first register (which being its own inverse up to a constant factor, is the same operation again since Hartley is symmetric like Fourier).
+Now here is where things differ: after this operation, the joint state will be
+    \[
+       \frac{1}{\sqrt{N}} \sum_{h \in G} \cas\!\Big(\frac{2\pi \langle g,h \rangle}{N}\Big)\, |h\rangle \otimes |h*x_0\rangle.
+    \] 
+    Because the Hartley transform combines what would be cosine and sine terms, this state is not as nicely factorable as in the Fourier case.
+In the Fourier case, we got $|g\rangle \otimes \text{(orbit state)}$.
+In the Hartley case, we do not get a single basis state in the first register; instead we get a superposition in the first register with real coefficients $c_h = cas(2\pi\langle g,h\rangle/N)$.
+However, note that $c_h$ is just some real number in $[-1,1]$ depending on $g$ and $h$.
+Another way to express the above state is:
+    \[
+      |\$\rangle = \frac{1}{\sqrt{N}} \sum_{x \in X} \Big(\frac{1}{\sqrt{N}}\sum_{h: h*x_0 = x} \cas\!\big(\frac{2\pi \langle g,h \rangle}{N}\big)\Big)\, |x\rangle.
+    \] 
+    Since for a given $x\in X$, all $h$ such that $h*x_0=x$ have the form $h = u g$ for a unique $u \in G$ (because the action is free and transitive), one can simplify the internal sum using properties of the cas function.
+But we need not dive into that here.
+    \item No measurement of the first register is performed.
+In fact, we do not have a nice product state separation, so we cannot simply measure one register to get $g$.
+Instead, the output of minting is just the quantum state $|\$\rangle$ (which is entangled between what used to be two registers) and the known classical serial number $g$ (we know what $g$ we picked).
+\end{enumerate}
+
+The resulting money state $|\$\rangle$ has only real amplitudes (because the initial superposition was real and the controlled operation doesn’t introduce complex numbers, and the Hartley transform yields real coefficients).
+In particular, in the computational basis of $X$, the state $|\$\rangle$ is some real-vector state (with both positive and negative values possible).
+We can think of it as a “Hartley orbit state” corresponding to $g$.
+
+The verification algorithm in our Hartley-based scheme attempts to mirror the Fourier-based verification: it will use the given serial $g$ and try to check the state.
+A first idea would be: do exactly the same as Zhandry’s verify (the group-action kickback and measure).
+However, this fails in certain cases.
+Specifically, the Hartley transform being real causes an ambiguity: it turns out that there exist distinct $g \neq g'$ for which the Hartley-based states $|\$\rangle_g$ and $|\$\rangle_{g'}$ are not orthogonal, and the original verification might accept a forged state that is a certain superposition.
+In fact, the verification algorithm might accept an illegitimate state with some probability bounded away from zero.
+This is the “breakdown” of the straightforward Hartley substitution that we alluded to earlier.
+
+To address this, our verification algorithm takes a more sophisticated approach:
+\begin{enumerate}
+    \item Given $(g, |\psi\rangle)$, it first uses the \textbf{quantum walk-based phase estimation} method (to be detailed in Chapter 6) to \emph{compute the eigenphase corresponding to $g$}.
+In short, we will treat $|\psi\rangle$ as an eigenvector of the group action adjacency matrix with a certain eigenvalue $\lambda$ related to $g$.
+We run a procedure to estimate $\lambda$ to high precision.
+    \item From the estimated eigenvalue(s), we reconstruct a candidate group element $g^*$ that we believe generated the state.
+(This uses the fact that by running phase estimation for multiple carefully chosen walk durations, one can solve for $g$ as shown in [31].)
+    \item We check if $g^* = g$ (the serial number provided). If not, we reject, since the state does not match the serial. If yes, we accept.
+\end{enumerate}
+
+This procedure essentially extracts the hidden group element from the state and compares it to the claimed serial.
+If an adversary tries to forge a state $|\psi\rangle$ for a known serial $g$, the only way to consistently pass verification is if $|\psi\rangle$ truly encodes the same $g$ in its eigen-spectrum.
+A fake note that was causing trouble for the naive Hartley verification (e.g., a state that is a mixture of two different “Hartley orbit” states) would yield an eigenphase that does not correspond to a single valid $g$, and the algorithm would detect the mismatch.
+
+The key quantum tool enabling this verification is the continuous-time quantum walk on the group action graph and the ability to simulate it, which we prepared in Chapter 4.
+The walk Hamiltonian $A(X,S)$ has the genuine money state $|\$\rangle_g$ as an eigenstate with a known eigenvalue $\lambda(g)$.
+By running phase estimation on $e^{-iA t}$ with the state $|\psi\rangle$, we attempt to measure that eigenvalue.
+We repeat for a few different values of $t$ (the “twists” or different phases) to get enough information to pinpoint $g$.
+This approach can be viewed as adding extra “twists” to the verification: effectively, each choice of $t$ in phase estimation is like looking at the state in a different interference fringe pattern, analogous to applying different group actions as twists in the verification procedure.
+This is why we described the new verification as using group action twists—by varying a continuous parameter related to the group action’s eigenvalues, we break the symmetry that allowed a counterfeit to slip through.
+
+We defer the full analysis of the success probabilities and how many repetitions are needed to Chapter 6, where we describe the verification algorithm in detail.
+For now, the takeaway is that by using the quantum walk approach, we can reliably verify Hartley-based money states, restoring security while still enjoying the properties of real amplitudes.
+
+\section{Efficient Quantum Hartley Transform Implementation}
+Before moving on to the verification algorithm, we briefly discuss how we implement the quantum Hartley transform (QHT) efficiently, as this is an important practical aspect of our scheme.
+The Fourier transform is well-known to have efficient circuits; for the Hartley transform, fewer results are available, so we contributed a new circuit construction.
+
+The QHT we need is over an abelian group, which for concreteness one can think of as $\mathbb{Z}_N$ (the general finite abelian group case can usually be reduced to a direct sum of cyclic groups, applying QHT on each cyclic component).
+Classical Hartley transforms have a recursive structure similar to fast Fourier transforms.
+In fact, there are known formulas to express a Hartley transform of size $N$ in terms of two Hartley transforms of size $N/2$ plus some additional linear operations [25].
+We leveraged such structures to design a divide-and-conquer quantum circuit.
+
+Our algorithm for QHT works roughly as follows:
+- If $N$ is even, we can express the length-$N$ Hartley transform in terms of two length-$N/2$ Hartley transforms plus a combination of cheap operations (additions, permutations of data, etc.).
+We implement this decomposition recursively as a quantum circuit.
+The base of the recursion is when the size is small (like $N=2$ or $4$, where the transform can be done with a constant number of gates).
+- We found that by carefully optimizing this recursion and using some known quantum subroutines for certain linear combinations, the overall gate count is improved compared to naive methods or previous proposals [21, 22].
+In particular, our circuit avoids introducing any quantum Fourier transform internally (unlike [22] which computed Hartley via Fourier plus some adjustments), and this yields a purely real rotation-based circuit.
+
+%%%%%%%%%%% az inja %%%%%%%%%%%%%
+
+Our algorithm for the quantum Hartley transform, \( \qht_N \), is modeled after the recursive structure of the quantum Fourier transform algorithm \( \qft_N \).
+To motivate this, we begin by reviewing the standard approach for computing \( \qft_N \).
+For clarity, we assume \( N = 2^n \), allowing each element of \( \mathbb{Z}_N \) to be represented using exactly \( n \) qubits.
+The same recursive framework can be extended to handle general values of \( N \).
+For any \( a \in \mathbb{Z}_N \), the quantum Fourier transform is defined as:
+
+\begin{align*}
+    \qft_N\ket{a}
+    & = \frac{1}{\sqrt{N}} \sum_{y = 0}^{N - 1} \omega_N^{ay}\ket{y} \\
+    & = \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \omega_N^{ay} \ket{y} + (-1)^a \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \omega_N^{ay} \ket{y + N/2} \\
+    & = \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \omega_N^{ay} \frac{1}{\sqrt{2}} (\ket{0} + (-1)^a \ket{1}) \ket{y}, %\numberthis\label{eq:qft_alt}
+\end{align*}
+
+In the final expression, we have isolated the first qubit for clarity.
+Let \( \ket{a} = \ket{t}\ket{b} \), where \( b \) denotes the least significant bit of \( a \), implying that \( a = 2t + b \) for some \( t \in \mathbb{Z}_{N / 2} \).
+Applying \( \qft_{N / 2} \) to the first register yields the state:
+
+\[ \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \omega_N^{2ty} \ket{y} \ket{b}. \]
+Next, we apply the phase unitary \( P(y, b) \), defined by \( \ket{y} \ket{b} \mapsto \omega_N^{by} \ket{y} \ket{b} \), followed by a Hadamard transform on the final qubit.
+This results in the state given in Equation~\eqref{eq:qft_alt}.
+
+We now describe our algorithm for efficiently computing the quantum Hartley transform \( \qht_N \).
+The key idea is to leverage the recursive structure of \( \qht_N \), analogous to the strategy used for \( \qft_N \).
+To facilitate this, we begin by rewriting the summation in Equation~\eqref{eq:qht-N} to expose its recursive form.
+Our approach is as follows:
+\begin{equation}
+    \label{eq:cas-expand}
+	\frac{1}{\sqrt{N}} \sum_{y = 0}^{N - 1} \cas\Big( \frac{2\pi a y}{N} \Big) \ket{y}
+    = \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi a y}{N} \Big) \ket{y} + \frac{1}{\sqrt{N}} \sum_{y = N / 2}^{N - 1} \cas\Big( \frac{2\pi a y}{N} \Big) \ket{y}.
+\end{equation}
+
+The second summation on the right-hand side can be expressed as:
+\begin{align*}
+	\sum_{y = N / 2}^{N - 1} \cas\Big( \frac{2\pi a y}{N} \Big) \ket{y}
+    & = \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi a y}{N} + \pi a \Big) \ket{y + N/2} \\
+    & = (-1)^a \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi a y}{N} \Big) \ket{y + N/2},
+\end{align*}
+The second equality follows from the angle-sum identity for the \( \cas \) function,
+\[
+\cas(\alpha + \beta) = \cos(\alpha)\cas(\beta) + \sin(\alpha)\cas(-\beta),
+\]
+along with the fact that \( \cos(\pi a) = (-1)^a \) for all integers \( a \). Substituting this into Equation~\eqref{eq:cas-expand} yields:
+\begin{align}
+	\frac{1}{\sqrt{N}} \sum_{y = 0}^{N - 1} \cas\Big( \frac{2\pi a y}{N} \Big) \ket{y}
+    & = \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi a y}{N} \Big) (\ket{y} + (-1)^a \ket{y + N/2}) \nonumber \\
+    & = \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi a y}{N} \Big) \frac{1}{\sqrt{2}} (\ket{0} + (-1)^a \ket{1}) \ket{y}, \label{eq:qht-alt} 
+\end{align}
+In the final equality, the most significant qubit has been isolated to emphasize its contribution to the overall transformation.
+
+We now demonstrate how to compute \( \qht_N \) recursively.
+For a given \( a \in \mathbb{Z}_N \), we decompose the basis state as \( \ket{a} = \ket{t}\ket{b} \), where \( b \) denotes the least significant bit, such that \( a = 2t + b \) for some \( t \in \mathbb{Z}_{N/2} \).
+Assuming the existence of an efficient quantum circuit for computing \( \qht_{N/2} \), we proceed to construct \( \qht_N \) in a recursive fashion.
+To begin the transformation on \( \ket{a} \), we introduce an ancilla qubit initialized to \( \ket{0} \), yielding the joint state \( \ket{0}\ket{t}\ket{b} \).
+We then proceed as follows:
+\begin{align*}
+	\ket{0}\ket{t}\ket{b}
+    & \mapsto \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi t y}{N / 2} \Big) \ket{0} \ket{y} \ket{b} & (\mathbf{1} \otimes \qht_{N / 2} \otimes \mathbf{1}) \\
+    & = \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{4\pi t y}{N} \Big) \ket{0} \ket{y} \ket{b} \\
+    & \mapsto \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{4\pi t y}{N} \Big) (\ket{0} + \ket{1}) \ket{y}\ket{b}. & (H \otimes \mathbf{1})
+\end{align*}
+Next, we apply a controlled negation operation, where the ancilla qubit is flipped if and only if the least significant bit \( b \) is equal to 1.
+\[
+    V: \ket{0}\ket{y} \mapsto \ket{0}\ket{y}, \quad \ket{1}\ket{y} \mapsto \ket{1}\ket{N / 2 -y},
+\]
+\[
+    \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{4\pi t y}{N} \Big) \ket{0} \ket{y} \ket{b} + \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{4\pi t y}{N} \Big) \ket{1} \ket{-y} \ket{b}.
+\]
+By performing a change of variables in the second summation and using the identity \( \cas\left(\frac{4\pi t (N / 2 - y)}{N}\right) = \cas\left(-\frac{4\pi t y}{N}\right) \), we obtain the state:
+\[
+    \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \Big( \cas\Big( \frac{4\pi t y}{N} \Big) \ket{0} + \cas\Big( -\frac{4\pi t y}{N} \Big) \ket{1} \Big) \ket{y} \ket{b}.
+\]
+
+We define the single-qubit rotation \( R(\theta) \) as the unitary operator acting on a single qubit given by:
+\begin{equation}
+    \label{eq:sine-rot}
+    R(y, b) = 
+    \begin{bmatrix}
+        \cos(2\pi b y / N) & \sin(2\pi b y / N) \\
+        -\sin(2\pi b y / N) & \cos(2\pi b y / N)
+    \end{bmatrix},
+\end{equation}
+Now, consider the unitary \( U_R \) defined by
+\[
+U_R : \ket{c}\ket{y}\ket{b} \mapsto \left(R(y, b)\ket{c}\right)\ket{y}\ket{b},
+\]
+where \( R(y, b) \) is a single-qubit rotation depending on \( y \) and \( b \). Applying \( U_R \) followed by the controlled negation \( V \), we obtain the state:
+\begin{align*}
+    \ket{\phi_1}
+    & = \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \Big( \cas\Big( \frac{2\pi ay}{N} \Big) \ket{0} + \cas\Big(-\frac{2\pi a(N /2 - y)}{N} \Big) \ket{1} \Big) \ket{y} \ket{b} \\
+    & = \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi ay}{N} \Big) \Big( \ket{0} + (-1)^b \ket{1} \Big) \ket{y} \ket{b},
+\end{align*}
+Here, we have used the identity \( \cas\left(-\pi a + \frac{2\pi a y}{N}\right) = (-1)^a \cas\left(\frac{2\pi a y}{N}\right) \), along with the fact that \( (-1)^a = (-1)^b \).
+Applying the Hadamard transform to the first qubit yields:
+\[
+    \ket{\psi} = \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi ay}{N} \Big) \ket{b} \ket{y} \ket{b}
+\]
+Next, we uncompute the first qubit by applying a \textsc{CNOT} gate with the last qubit as control. We then apply a Hadamard transform followed by a swap operation, resulting in the state:
+\begin{align*}
+    \ket{\psi}
+    & \mapsto \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi ay}{N} \Big) \ket{0} \ket{y} \ket{b} & (\textsc{cnot}) \\
+    & \mapsto \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi ay}{N} \Big) \ket{0} \ket{y} \frac{1}{\sqrt{2}}(\ket{0} + (-1)^b \ket{1}) & (\mathbf{1} \otimes H) \\
+    & = \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi ay}{N} \Big) \ket{0} \ket{y} \frac{1}{\sqrt{2}}(\ket{0} + (-1)^a \ket{1}). & ((-1)^b = (-1)^a) \\
+\end{align*}
+The final summation matches precisely with Equation~\eqref{eq:qht-alt}, which defines the quantum Hartley transform of \( \ket{a} \). Thus, we have successfully implemented the transformation:
+\[
+\ket{a} \mapsto \qht_N \ket{a}.
+\]
+\[ \ket{0}\ket{a} \mapsto \ket{0} \qht_N\ket{a}. \]
+The complete procedure is summarized in the following algorithm.
+
+% \begin{algorithm}[$\qht_N$] \
+\paragraph{algorithm $\qht_N$}
+    % \label{alg:qht-N}
+    % \begin{description}[font = \normalfont\itshape, itemsep = 0mm, parsep = 0mm, topsep = 1mm]
+    %     \item [Input:] quantum state $\ket{\psi} \in \C^N$, where $N = 2^n$
+    %     \item [Output:] quantum state $\qht_N\ket{\psi}$
+    % \end{description}
+
+\begin{enumerate}%[itemsep = 0mm, parsep = 1mm, topsep = 1mm]
+    \item Initialize an ancilla qubit to $0$ to obtain the state $\ket{0}\ket{\psi}$
+    \item Compute $\mathbf{1} \otimes \qht_{N / 2} \otimes \mathbf{1}$ recursively.
+    \item Apply $H \otimes \mathbf{1}$.
+    \item\label{stp:ngt} Apply the controlled negation $\ket{0}\ket{y} \mapsto \ket{0}\ket{y}, \ket{1}\ket{y} \mapsto \ket{1}\ket{N / 2 -y}$ to the first two registers.
+    \item Apply the unitary $U_R$.
+    \item Apply $H \otimes \mathbf{1}$
+    \item Apply \textsc{cnot} to the first and last qubits.
+    \item Apply $\mathbf{1} \otimes H$.
+    \item Trace out the first qubit
+\end{enumerate}
+% \end{algorithm}
+
+% \begin{theorem}
+\paragraph{Theorem.}
+    \label{thm:qht-cost}
+    Algorithm \ref{alg:qht-N} is correct and can be implemented using $\approx \log^2 N + O(\log N)$ elementary gates.
+% \end{theorem}
+
+% \begin{proof}
+\paragraph{proof.}
+    The correctness of the algorithm follows from the preceding discussion.
+Except for the unitary \( U_R \) and the negation unitary in Step~\ref{stp:ngt}, all steps of the algorithm can be implemented using \( O(1) \) elementary gates.
+The negation operation in Step~\ref{stp:ngt} can be realized using approximately \( \lceil \log N \rceil \) elementary gates.
+
+    To implement the unitary \( U_R \), which requires constructing the conditional rotation operator \( R(y, b) \) for arbitrary \( y \) and \( b \), we make use of the two-qubit controlled rotations:
+    \[
+    R_j = \ket{0}\bra{0} \otimes \mathbf{1} + \ket{1}\bra{1} \otimes
+    \begin{bmatrix}
+    \cos\left(\frac{2\pi 2^j}{N}\right) & \sin\left(\frac{2\pi 2^j}{N}\right) \\
+    -\sin\left(\frac{2\pi 2^j}{N}\right) & \cos\left(\frac{2\pi 2^j}{N}\right)
+    \end{bmatrix},
+    \]
+    for \( j = 0, 1, \dots, n - 1 \).
+When \( b = 0 \), we have \( R(y, 0) = \mathbf{1} \), and when \( b = 1 \), the operator \( R(y, 1) \) is the product of those \( R_j \) for which the \( j \)th bit of \( y \) is 1.
+Therefore, for a binary string \( y \) of length \( k = \lceil \log y \rceil \), we can implement \( U_R \) using at most \( k \) gates from the set \( \{R_j\} \).
+
+    Let \( T(N) \) denote the gate complexity of Algorithm~\ref{alg:qht-N} for an input of dimension \( N \).
+Assuming access to the \( R_j \) gates as elementary operations, the recurrence relation becomes
+    \[
+    T(N) \approx T(N / 2) + 2\log N + O(1).
+    \]
+    Solving this recurrence yields \( T(N) \approx \log^2 N + O(\log N) \), as claimed.
+%     \end{proof}
+%%%%%%%%%%%  ta inja  %%%%%%%%%%%
+
+- The resulting complexity for an $N$-point QHT is $O(N \log N)$ basic quantum gates (up to polylog factors for precision), which is on par (up to constant factors) with the complexity of a QFT circuit.
+We also derived explicit constants for small cases to show improvements over prior work.
+
+For the purposes of this thesis, the main point is: \emph{we can implement the Hartley transform needed for our money scheme with polynomial efficiency}.
+Thus, switching to the Hartley transform does not introduce any prohibitive cost.
+All steps of minting and verification remain efficient.
+Having covered the construction of the money scheme and the necessary tools, we now proceed to the final piece: the detailed verification algorithm using quantum walks, and an analysis of how it validates genuine banknotes and foils counterfeit attempts.
+\vspace{1em}
+
 \chapter{Verification Algorithm Using Quantum Walks}
+
+The Hartley-based quantum money scheme introduced in the previous chapter requires a new verification procedure to address the issues that arise from using real amplitude states.
+In this chapter, we describe and analyze the verification algorithm, which leverages continuous-time quantum walks on the group action graph (and their efficient simulation from Chapter 4) to extract the information needed to authenticate a banknote.
+
+    \section{Challenges with Naïve Verification}
+    Before detailing the new algorithm, let us briefly recap why the straightforward approach fails.
+In the Fourier-based scheme, verification was done by a single “kickback” operation using the claimed serial $h$, and measuring an auxiliary register.
+In the Hartley-based scheme, if we attempted the analogous one-step verification, we would perform the controlled-$h$ action and measure the auxiliary system.
+A genuine state $|\$_h\rangle$ (the Hartley money state for serial $h$) would cause some interference pattern in the auxiliary register, but unlike the Fourier case, it does not return the auxiliary to $|x_0\rangle$ deterministically.
+In fact, there is an ambiguity: certain superpositions of eigenstates corresponding to $h$ and $-h$ (or other group-related variants) can produce the same measurement statistics in that one-step test.
+This means an adversary might prepare a counterfeit state that is not a legitimate $|\$_h\rangle$ but still passes the one-step verification with non-zero probability.
+Essentially, the Hartley transform being real means we lost some phase information, and a single measurement cannot distinguish some mirrored states.
+
+    To overcome this, our strategy is to perform a more complete measurement of the state’s “phase spectrum.” Instead of just one operation and measurement, we will use the quantum walk (with Hamiltonian $A = A(X,Q)$ as defined earlier) to perform a form of phase estimation.
+
+    \section{Using Quantum Walks to Extract the Serial}
+
+    Given a state of the form $\ket{\mathbb{Z}_N^{(h)} * x}_H$, we demonstrate how the value of $h$ can be extracted using continuous-time quantum walks.
+For any $u \in \mathbb{Z}_N$, consider the Cayley graph $\Gamma = (\mathbb{Z}_N, E)$ generated by $Q = {\{-u, u}\}$.
+Let $A$ denote the adjacency matrix of $\Gamma$.
+The eigenvectors of $A$ are given by $\ket{\mathbb{Z}_N^{(h)} * x}$, with corresponding eigenvalues $\lambda_h = 2\cos(2\pi uh / N)$ for each $h \in \mathbb{Z}_N$.
+According to Theorem \ref{thm:sparse-sim} and the discussion that follows, the unitary evolution operator $W = e^{iAt}$ can be simulated efficiently to exponential precision.
+To proceed, we first state the following lemma.
+
+    % \begin{lemma}
+    \paragraph{lemma.}
+        \label{lem:h-eigen}
+        The money state $\ket{\mathbb{Z}_N^{(h)} * x}_H$ is an eigenstate of $W$ with eigenvalue $e^{i\lambda_h t}$.
+    % \end{lemma}
+    % \begin{proof}
+    \paragraph{proof.}
+        We have 
+        \begin{align*}
+            e^{iAt} \ket{\mathbb{Z}_N^{(h)} * x}_H
+            & = \sum_{g \in \mathbb{Z}_N} e^{i\lambda_gt} \ket{\mathbb{Z}_N^{(g)} * x} \braket{\mathbb{Z}_N^{(g)} * x}{\mathbb{Z}_N^{(h)} * x}_H \\
+            & = \sum_{g \in \mathbb{Z}_N} e^{i\lambda_gt} \ket{\mathbb{Z}_N^{(g)} * x} \bra{\mathbb{Z}_N^{(g)} * x} \Big( \frac{1 - i}{2} \ket{\mathbb{Z}_N^{(h)} * x} + \frac{1 + i}{2} \ket{\mathbb{Z}_N^{(-h)} * x} \Big) \\
+            & = e^{i\lambda_{h}t} \frac{1 - i}{2} \ket{\mathbb{Z}_N^{(h)} * x} + \frac{1 + i}{2} e^{i\lambda_{-h}t} \ket{\mathbb{Z}_N^{(-h)} * x} \\
+            & = e^{i\lambda_{h}t} \ket{\mathbb{Z}_N^{(h)} * x}_H,
+        \end{align*}
+        where the second equality follows from the identity in \eqref{eq:ht-ft}, and the last equality follows from the fact that $\lambda_h = \lambda_{-h}$.
+    % \end{proof}
+
+    By setting \( t = \operatorname{poly}(\log N) \), Lemma~\ref{lem:h-eigen} ensures that phase estimation can be performed using the unitary \( W \) and the eigenstate \( \ket{\mathbb{Z}_N^{(h)} * x}_H \), yielding an approximation \( \tilde{\lambda}_h \) of \( \lambda_h \) such that
+    \[
+    \abs{\tilde{\lambda}_h - \lambda_h} \le \frac{1}{\operatorname{poly}(\log N)}.
+    \]
+    From this approximation, we can extract a real number \( 0 \le \theta \le 1 \) satisfying
+    \[
+    \abs*{\theta - \frac{uh}{N}} \le \frac{1}{\operatorname{poly}(\log N)}.
+    \]
+    Since phase estimation can be applied with various choices of \( u \), we can obtain multiple approximations of \( \frac{uh}{N} \).
+As shown in~\cite{zhandry2024quantum}, selecting \( u \) appropriately allows us to reconstruct \( h \) exactly from these estimates.
 

### 2025-04-08 main.tex
chapters 5,6 added

@@
 
-% \chapter{Quantum Money and the Hartley Transform}
-% We now present our public-key quantum money scheme based on group actions and the Hartley transform.
+\chapter{Quantum Money and the Hartley Transform}
+We now present our public-key quantum money scheme based on group actions and the Hartley transform.
 We begin by reviewing Zhandry’s quantum money scheme from abelian group actions (which uses the Fourier transform) as a baseline.
@@
 
-% \section{Public-Key Quantum Money: Definitions}
-% A public-key quantum money scheme consists of two algorithms, traditionally called $\mathsf{Mint}$ and $\mathsf{Verify}$:
-% \begin{itemize}
-%     \item $\mathsf{Mint}(1^n)$ is a probabilistic quantum polynomial-time (QPT) algorithm that, given a security parameter $n$, outputs a pair $(s, |\$\rangle)$.
+\section{Public-Key Quantum Money: Definitions}
+A public-key quantum money scheme consists of two algorithms, traditionally called $\mathsf{Mint}$ and $\mathsf{Verify}$:
+\begin{itemize}
+    \item $\mathsf{Mint}(1^n)$ is a probabilistic quantum polynomial-time (QPT) algorithm that, given a security parameter $n$, outputs a pair $(s, |\$\rangle)$.
 Here $s$ is a classical string called the \emph{serial number} (or public key) and $|\$\rangle$ is a quantum state representing the banknote.
 We often call the pair $(s, |\$\rangle)$ a banknote, and $s$ by itself the serial number of that banknote.
-%     \item $\mathsf{Verify}(s, |\$\rangle)$ is a QPT algorithm (which may be implemented as a quantum circuit acting on the state $|\$\rangle$ and some ancillary workspace).
+    \item $\mathsf{Verify}(s, |\$\rangle)$ is a QPT algorithm (which may be implemented as a quantum circuit acting on the state $|\$\rangle$ and some ancillary workspace).
 It takes as input a serial number $s$ and an alleged quantum banknote state $|\$\rangle$.
 It outputs $\mathtt{accept}$ (valid) or $\mathtt{reject}$ (invalid).
-% \end{itemize}
-
-% We require two properties from such a scheme:
-% \begin{description}
-%     \item[Correctness:] For any valid output $(s, |\$\rangle)$ of $\mathsf{Mint}(1^n)$, the verification algorithm accepts with high probability.
+\end{itemize}
+
+We require two properties from such a scheme:
+\begin{description}
+    \item[Correctness:] For any valid output $(s, |\$\rangle)$ of $\mathsf{Mint}(1^n)$, the verification algorithm accepts with high probability.
 Formally, $\Pr[\mathsf{Verify}(s, |\$\rangle) = \mathtt{accept}]$ should be very close to 1 (typically we require it to be $1 - \negl(n)$, where $\negl(n)$ denotes a negligible function in $n$).
-%     \item[Security (Unforgeability):] No efficient adversary, given one or more genuine banknotes, can produce a new valid banknote.
+    \item[Security (Unforgeability):] No efficient adversary, given one or more genuine banknotes, can produce a new valid banknote.
 In the strongest formulation, if an adversary is given a single valid $(s, |\$\rangle)$, it should be infeasible for them to produce two quantum states $|\$'\rangle$ and $|\$''\rangle$ such that $\mathsf{Verify}(s, |\$'\rangle) = \mathsf{Verify}(s, |\$''\rangle) = \mathtt{accept}$ (i.e., they cannot create a second copy that passes verification while retaining the original).
@@
 This captures the idea that quantum money cannot be counterfeited.
-% \end{description}
-
-% In a \emph{public-key} scheme, the verifier uses only the public information (here, the serial number and any scheme-wide public parameters) to check validity, and does not need any secret key.
+\end{description}
+
+In a \emph{public-key} scheme, the verifier uses only the public information (here, the serial number and any scheme-wide public parameters) to check validity, and does not need any secret key.
 The bank (mint) may have a secret key to produce the states, but after minting, the bank’s involvement is not needed.
@@
 
-% We next outline Zhandry’s scheme, which our scheme builds upon.
-
-% \section{Fourier-Based Quantum Money from Group Actions}
-% Zhandry’s quantum money scheme [31] is built on an abelian group action $G \curvearrowright X$.
+We next outline Zhandry’s scheme, which our scheme builds upon.
+
+\section{Fourier-Based Quantum Money from Group Actions}
+Zhandry’s quantum money scheme [31] is built on an abelian group action $G \curvearrowright X$.
 We have a family of group actions parameterized by the security parameter $n$ (so the size of $G$ grows with $n$).
@@
 
-% The minting algorithm $\mathsf{Mint}$ in Zhandry’s scheme works as follows (informally):
-% \begin{enumerate}
-%     \item On input $1^n$, sample a random group element $g \leftarrow G$. This $g$ will serve as the serial number $s$ for the banknote.
-%     \item Prepare two registers: the first is a group element register, initialized to $|0_G\rangle$ (an encoding of the identity element of $G$), and the second is an $X$-register initialized to $|x_0\rangle$.
-%     \item Apply the quantum Fourier transform over $G$ to the first register. This creates a uniform superposition over $G$: 
-%     \[
-%     \frac{1}{\sqrt{N}} \sum_{h \in G} |h\rangle \otimes |x_0\rangle\,.
-%     \] 
-%     \item Now apply the group action in a controlled manner: for each basis state $|h\rangle$ in the first register, apply $h$’s action on the second register. This transforms the joint state into 
-%     \[
-%     \frac{1}{\sqrt{N}} \sum_{h \in G} |h\rangle \otimes |h * x_0\rangle\,,
-%     \] 
-%     which is an entangled state between a superposition of group elements and their corresponding $X$-elements.
-%     \item Apply the inverse QFT (which is the adjoint of the QFT) on the first register.
-This recombines the amplitudes in the first register.
-The result (by properties of the QFT) can be shown to be
-%     \[
-%     \frac{1}{\sqrt{N}} \sum_{h \in G} \omega^{\langle g,\,h \rangle} |h\rangle \otimes |h * x_0\rangle\,,
-%     \] 
-%     where $\omega^{\langle g,\,h \rangle}$ denotes the phase picked up that depends on $g$ and $h$.
+The minting algorithm $\mathsf{Mint}$ in Zhandry’s scheme works as follows (informally):
+\begin{enumerate}
+    \item On input $1^n$, sample a random group element $g \leftarrow G$. This $g$ will serve as the serial number $s$ for the banknote.
+    \item Prepare two registers: the first is a group element register, initialized to $|0_G\rangle$ (an encoding of the identity element of $G$), and the second is an $X$-register initialized to $|x_0\rangle$.
+    \item Apply the quantum Fourier transform over $G$ to the first register. This creates a uniform superposition over $G$: 
+    \[
+    \frac{1}{\sqrt{N}} \sum_{h \in G} |h\rangle \otimes |x_0\rangle\,.
+    \] 
+    \item Now apply the group action in a controlled manner: for each basis state $|h\rangle$ in the first register, apply $h$’s action on the second register. This transforms the joint state into 
+    \[
+    \frac{1}{\sqrt{N}} \sum_{h \in G} |h\rangle \otimes |h * x_0\rangle\,,
+    \] 
+    which is an entangled state between a superposition of group elements and their corresponding $X$-elements.
+    \item Apply the inverse QFT (which is the adjoint of the QFT) on the first register. This recombines the amplitudes in the first register. The result (by properties of the QFT) can be shown to be 
+    \[
+    \frac{1}{\sqrt{N}} \sum_{h \in G} \omega^{\langle g,\,h \rangle} |h\rangle \otimes |h * x_0\rangle\,,
+    \] 
+    where $\omega^{\langle g,\,h \rangle}$ denotes the phase picked up that depends on $g$ and $h$.
 In fact, this state can be written as $|g\rangle \otimes \frac{1}{\sqrt{N}}\sum_{h \in G} |h * x_0\rangle$; essentially, the first register ends up in $|g\rangle$ (the serial number) and the second register is an equal superposition of all elements of $X$ in the orbit of $x_0$ (which is $X$ itself, since the action is transitive) but weighted by a phase related to $g$.
 This is the so-called group-action Fourier state.
-%     \item The first register (which contains $|g\rangle$) is measured in the computational basis, yielding the random serial number $g$ and collapsing the second register to a state that we will denote $|\$_g\rangle$.
+    \item The first register (which contains $|g\rangle$) is measured in the computational basis, yielding the random serial number $g$ and collapsing the second register to a state that we will denote $|\$_g\rangle$.
 This $|\$_g\rangle$ is the actual quantum money state corresponding to serial $g$.
-%     \item Output the pair $(s = g,\; |\$\rangle = |\$_g\rangle)$.
-% \end{enumerate}
-
-% In the above, a bit of algebra reveals that $|\$_g\rangle = \frac{1}{\sqrt{N}} \sum_{h \in G} \chi_g(h)\, |h * x_0\rangle$, where $\chi_g(h) = \omega^{\langle g,\,h \rangle}$ is essentially the character of $G$ indexed by $g$.
+    \item Output the pair $(s = g,\; |\$\rangle = |\$_g\rangle)$.
+\end{enumerate}
+
+In the above, a bit of algebra reveals that $|\$_g\rangle = \frac{1}{\sqrt{N}} \sum_{h \in G} \chi_g(h)\, |h * x_0\rangle$, where $\chi_g(h) = \omega^{\langle g,\,h \rangle}$ is essentially the character of $G$ indexed by $g$.
 In other words, $|\$_g\rangle$ is (up to global phase) the state one gets by applying the representation (character) $\chi_g$ to weight the superposition over the orbit $X$.
@@
 
-% The verification algorithm $\mathsf{Verify}(g, |\$_g\rangle)$ for Zhandry’s scheme goes as follows:
-% \begin{enumerate}
-%     \item Given the purported serial number $g \in G$ and an input state $|\psi\rangle$ (which should equal $|\$_g\rangle$ if genuine), attach an auxiliary register prepared in $|x_0\rangle$.
-%     \item Perform a controlled group action “kickback” using $g$ on the auxiliary register.
+The verification algorithm $\mathsf{Verify}(g, |\$_g\rangle)$ for Zhandry’s scheme goes as follows:
+\begin{enumerate}
+    \item Given the purported serial number $g \in G$ and an input state $|\psi\rangle$ (which should equal $|\$_g\rangle$ if genuine), attach an auxiliary register prepared in $|x_0\rangle$.
+    \item Perform a controlled group action “kickback” using $g$ on the auxiliary register.
 Specifically, perform the unitary that maps $|y\rangle \otimes |x_0\rangle \mapsto |y\rangle \otimes |g * x_0 \rangle$ for each basis element $|y\rangle$ of the first register.
@@
 There are various ways to implement this, but conceptually it’s a controlled operation using the known $g$.)
-%     \item Now measure the second register (the auxiliary one) in the computational basis of $X$ to see if it is still $|x_0\rangle$.
+    \item Now measure the second register (the auxiliary one) in the computational basis of $X$ to see if it is still $|x_0\rangle$.
 If the state $|\psi\rangle$ was the correct Fourier state $|\$_g\rangle$, one can show that this measurement will yield $x_0$ with high probability (constructive interference causes the $x_0$ component to be strong).
 If $|\psi\rangle$ was not the correct state, the measurement is unlikely to give $x_0$.
-%     \item Accept if and only if the measurement outcome is $x_0$ (i.e. the second register returns to the base state).
-% \end{enumerate}
-
-% The intuition is that the genuine state $|\$_g\rangle$ contains a phase that exactly cancels out the action of $g$ in the verification step, causing the auxiliary register to end up back at $x_0$.
+    \item Accept if and only if the measurement outcome is $x_0$ (i.e. the second register returns to the base state).
+\end{enumerate}
+
+The intuition is that the genuine state $|\$_g\rangle$ contains a phase that exactly cancels out the action of $g$ in the verification step, causing the auxiliary register to end up back at $x_0$.
 A counterfeit state, by contrast, would not generally have the right phase relationship, and the auxiliary register’s state would be some superposition over $X$ that is not concentrated on $x_0$, hence likely giving a different outcome upon measurement.
 
-% Zhandry’s scheme is shown to be correct (valid notes pass) and is believed to be secure under the assumption that the group action is one-way.
+Zhandry’s scheme is shown to be correct (valid notes pass) and is believed to be secure under the assumption that the group action is one-way.
 The hardness essentially boils down to: given $x_0$ and $|\$_g\rangle$, an adversary cannot figure out a different $g'$ that would produce a second valid state $|\$_{g'}\rangle$ or replicate $|\$_g\rangle$ (because that would solve the hidden subgroup or discrete log type problem in the group action).
 
-% \section{Hartley-Transform Money Scheme Construction}
-% Our scheme modifies the above Fourier-based construction by utilizing the \textbf{quantum Hartley transform (QHT)} in place of the QFT.
+\section{Hartley-Transform Money Scheme Construction}
+Our scheme modifies the above Fourier-based construction by utilizing the \textbf{quantum Hartley transform (QHT)} in place of the QFT.
 Since the Hartley transform is closely related to the Fourier transform (essentially it produces the real and imaginary parts in a single real-valued transform), one might expect this substitution to be straightforward.
@@
 
-% Concretely, assume again a group action $G \curvearrowright X$ with $|G|=N$. We fix the same generating set $S$ and basepoint $x_0$. The $\mathsf{Mint}_{H}$ (Hartley mint) algorithm:
-% \begin{enumerate}
-%     \item Sample a random $g \leftarrow G$ to be the serial number.
-%     \item Prepare $|0_G, x_0\rangle$ as before.
-%     \item Apply the \emph{quantum Hartley transform} over $G$ to the first register. The Hartley transform (on an abelian group of order $N$) is defined as:
-%     \[
-%        \mathrm{QHT}: |h\rangle \mapsto \frac{1}{\sqrt{N}} \sum_{k \in G} \cas\!\Big(\frac{2\pi \langle k,h \rangle}{N}\Big) |k\rangle,
-%     \] 
-%     where $\mathrm{cas}(\theta) = \cos \theta + \sin \theta$ and $\langle k,h \rangle$ denotes some pairing like an exponent or dot product (for cyclic groups this is just $kh$).
+Concretely, assume again a group action $G \curvearrowright X$ with $|G|=N$. We fix the same generating set $S$ and basepoint $x_0$. The $\mathsf{Mint}_{H}$ (Hartley mint) algorithm:
+\begin{enumerate}
+    \item Sample a random $g \leftarrow G$ to be the serial number.
+    \item Prepare $|0_G, x_0\rangle$ as before.
+    \item Apply the \emph{quantum Hartley transform} over $G$ to the first register. The Hartley transform (on an abelian group of order $N$) is defined as:
+    \[
+       \mathrm{QHT}: |h\rangle \mapsto \frac{1}{\sqrt{N}} \sum_{k \in G} \cas\!\Big(\frac{2\pi \langle k,h \rangle}{N}\Big) |k\rangle,
+    \] 
+    where $\mathrm{cas}(\theta) = \cos \theta + \sin \theta$ and $\langle k,h \rangle$ denotes some pairing like an exponent or dot product (for cyclic groups this is just $kh$).
 In simpler terms, $\mathrm{QHT}(|0_G\rangle) = \frac{1}{\sqrt{N}}\sum_{k \in G} |k\rangle$ (because $\cas(0)=1$), \emph{the same uniform superposition as the QFT produces for $|0\rangle$}.
 So after this step, we again have $\frac{1}{\sqrt{N}}\sum_{h \in G} |h\rangle|x_0\rangle$, but crucially the coefficients are all \emph{real} and positive (in fact all $1/\sqrt{N}$).
-%     \item Perform the controlled group action by the first register on the second: $\frac{1}{\sqrt{N}}\sum_{h} |h\rangle |h*x_0\rangle$.
-%     \item Apply the inverse QHT on the first register (which being its own inverse up to a constant factor, is the same operation again since Hartley is symmetric like Fourier).
+    \item Perform the controlled group action by the first register on the second: $\frac{1}{\sqrt{N}}\sum_{h} |h\rangle |h*x_0\rangle$.
+    \item Apply the inverse QHT on the first register (which being its own inverse up to a constant factor, is the same operation again since Hartley is symmetric like Fourier).
 Now here is where things differ: after this operation, the joint state will be
-%     \[
-%        \frac{1}{\sqrt{N}} \sum_{h \in G} \cas\!\Big(\frac{2\pi \langle g,h \rangle}{N}\Big)\, |h\rangle \otimes |h*x_0\rangle.
-%     \] 
-%     Because the Hartley transform combines what would be cosine and sine terms, this state is not as nicely factorable as in the Fourier case.
+    \[
+       \frac{1}{\sqrt{N}} \sum_{h \in G} \cas\!\Big(\frac{2\pi \langle g,h \rangle}{N}\Big)\, |h\rangle \otimes |h*x_0\rangle.
+    \] 
+    Because the Hartley transform combines what would be cosine and sine terms, this state is not as nicely factorable as in the Fourier case.
 In the Fourier case, we got $|g\rangle \otimes \text{(orbit state)}$.
@@
 Another way to express the above state is:
-%     \[
-%       |\$\rangle = \frac{1}{\sqrt{N}} \sum_{x \in X} \Big(\frac{1}{\sqrt{N}}\sum_{h: h*x_0 = x} \cas\!\big(\frac{2\pi \langle g,h \rangle}{N}\big)\Big)\, |x\rangle.
-%     \] 
-%     Since for a given $x\in X$, all $h$ such that $h*x_0=x$ have the form $h = u g$ for a unique $u \in G$ (because the action is free and transitive), one can simplify the internal sum using properties of the cas function.
+    \[
+      |\$\rangle = \frac{1}{\sqrt{N}} \sum_{x \in X} \Big(\frac{1}{\sqrt{N}}\sum_{h: h*x_0 = x} \cas\!\big(\frac{2\pi \langle g,h \rangle}{N}\big)\Big)\, |x\rangle.
+    \] 
+    Since for a given $x\in X$, all $h$ such that $h*x_0=x$ have the form $h = u g$ for a unique $u \in G$ (because the action is free and transitive), one can simplify the internal sum using properties of the cas function.
 But we need not dive into that here.
-%     \item No measurement of the first register is performed.
+    \item No measurement of the first register is performed.
 In fact, we do not have a nice product state separation, so we cannot simply measure one register to get $g$.
 Instead, the output of minting is just the quantum state $|\$\rangle$ (which is entangled between what used to be two registers) and the known classical serial number $g$ (we know what $g$ we picked).
-% \end{enumerate}
-
-% The resulting money state $|\$\rangle$ has only real amplitudes (because the initial superposition was real and the controlled operation doesn’t introduce complex numbers, and the Hartley transform yields real coefficients).
+\end{enumerate}
+
+The resulting money state $|\$\rangle$ has only real amplitudes (because the initial superposition was real and the controlled operation doesn’t introduce complex numbers, and the Hartley transform yields real coefficients).
 In particular, in the computational basis of $X$, the state $|\$\rangle$ is some real-vector state (with both positive and negative values possible).
@@
 
-% The verification algorithm in our Hartley-based scheme attempts to mirror the Fourier-based verification: it will use the given serial $g$ and try to check the state.
+The verification algorithm in our Hartley-based scheme attempts to mirror the Fourier-based verification: it will use the given serial $g$ and try to check the state.
 A first idea would be: do exactly the same as Zhandry’s verify (the group-action kickback and measure).
@@
 
-% To address this, our verification algorithm takes a more sophisticated approach:
-% \begin{enumerate}
-%     \item Given $(g, |\psi\rangle)$, it first uses the \textbf{quantum walk-based phase estimation} method (to be detailed in Chapter 6) to \emph{compute the eigenphase corresponding to $g$}.
+To address this, our verification algorithm takes a more sophisticated approach:
+\begin{enumerate}
+    \item Given $(g, |\psi\rangle)$, it first uses the \textbf{quantum walk-based phase estimation} method (to be detailed in Chapter 6) to \emph{compute the eigenphase corresponding to $g$}.
 In short, we will treat $|\psi\rangle$ as an eigenvector of the group action adjacency matrix with a certain eigenvalue $\lambda$ related to $g$.
 We run a procedure to estimate $\lambda$ to high precision.
-%     \item From the estimated eigenvalue(s), we reconstruct a candidate group element $g^*$ that we believe generated the state.
+    \item From the estimated eigenvalue(s), we reconstruct a candidate group element $g^*$ that we believe generated the state.
 (This uses the fact that by running phase estimation for multiple carefully chosen walk durations, one can solve for $g$ as shown in [31].)
-%     \item We check if $g^* = g$ (the serial number provided). If not, we reject, since the state does not match the serial. If yes, we accept.
-% \end{enumerate}
-
-% This procedure essentially extracts the hidden group element from the state and compares it to the claimed serial.
+    \item We check if $g^* = g$ (the serial number provided). If not, we reject, since the state does not match the serial. If yes, we accept.
+\end{enumerate}
+
+This procedure essentially extracts the hidden group element from the state and compares it to the claimed serial.
 If an adversary tries to forge a state $|\psi\rangle$ for a known serial $g$, the only way to consistently pass verification is if $|\psi\rangle$ truly encodes the same $g$ in its eigen-spectrum.
@@
 
-% The key quantum tool enabling this verification is the continuous-time quantum walk on the group action graph and the ability to simulate it, which we prepared in Chapter 4.
+The key quantum tool enabling this verification is the continuous-time quantum walk on the group action graph and the ability to simulate it, which we prepared in Chapter 4.
 The walk Hamiltonian $A(X,S)$ has the genuine money state $|\$\rangle_g$ as an eigenstate with a known eigenvalue $\lambda(g)$.
@@
 
-% We defer the full analysis of the success probabilities and how many repetitions are needed to Chapter 6, where we describe the verification algorithm in detail.
+We defer the full analysis of the success probabilities and how many repetitions are needed to Chapter 6, where we describe the verification algorithm in detail.
 For now, the takeaway is that by using the quantum walk approach, we can reliably verify Hartley-based money states, restoring security while still enjoying the properties of real amplitudes.
 
-% \section{Efficient Quantum Hartley Transform Implementation}
-% Before moving on to the verification algorithm, we briefly discuss how we implement the quantum Hartley transform (QHT) efficiently, as this is an important practical aspect of our scheme.
+\section{Efficient Quantum Hartley Transform Implementation}
+Before moving on to the verification algorithm, we briefly discuss how we implement the quantum Hartley transform (QHT) efficiently, as this is an important practical aspect of our scheme.
 The Fourier transform is well-known to have efficient circuits; for the Hartley transform, fewer results are available, so we contributed a new circuit construction.
 
-% The QHT we need is over an abelian group, which for concreteness one can think of as $\mathbb{Z}_N$ (the general finite abelian group case can usually be reduced to a direct sum of cyclic groups, applying QHT on each cyclic component).
+The QHT we need is over an abelian group, which for concreteness one can think of as $\mathbb{Z}_N$ (the general finite abelian group case can usually be reduced to a direct sum of cyclic groups, applying QHT on each cyclic component).
 Classical Hartley transforms have a recursive structure similar to fast Fourier transforms.
@@
 
-% Our algorithm for QHT works roughly as follows:
-% - If $N$ is even, we can express the length-$N$ Hartley transform in terms of two length-$N/2$ Hartley transforms plus a combination of cheap operations (additions, permutations of data, etc.).
+Our algorithm for QHT works roughly as follows:
+- If $N$ is even, we can express the length-$N$ Hartley transform in terms of two length-$N/2$ Hartley transforms plus a combination of cheap operations (additions, permutations of data, etc.).
 We implement this decomposition recursively as a quantum circuit.
 The base of the recursion is when the size is small (like $N=2$ or $4$, where the transform can be done with a constant number of gates).
-% - We found that by carefully optimizing this recursion and using some known quantum subroutines for certain linear combinations, the overall gate count is improved compared to naive methods or previous proposals [21, 22].
+- We found that by carefully optimizing this recursion and using some known quantum subroutines for certain linear combinations, the overall gate count is improved compared to naive methods or previous proposals [21, 22].
 In particular, our circuit avoids introducing any quantum Fourier transform internally (unlike [22] which computed Hartley via Fourier plus some adjustments), and this yields a purely real rotation-based circuit.
-% - The resulting complexity for an $N$-point QHT is $O(N \log N)$ basic quantum gates (up to polylog factors for precision), which is on par (up to constant factors) with the complexity of a QFT circuit.
+- The resulting complexity for an $N$-point QHT is $O(N \log N)$ basic quantum gates (up to polylog factors for precision), which is on par (up to constant factors) with the complexity of a QFT circuit.
 We also derived explicit constants for small cases to show improvements over prior work.
 
-% Additionally, once we have an efficient QHT, we can also implement other related transforms.
+Additionally, once we have an efficient QHT, we can also implement other related transforms.
 We demonstrate this with the example of the \textbf{quantum sine transform} (QST).
@@
 
-% For the purposes of this thesis, the main point is: \emph{we can implement the Hartley transform needed for our money scheme with polynomial efficiency}.
+For the purposes of this thesis, the main point is: \emph{we can implement the Hartley transform needed for our money scheme with polynomial efficiency}.
 Thus, switching to the Hartley transform does not introduce any prohibitive cost.
@@
 Having covered the construction of the money scheme and the necessary tools, we now proceed to the final piece: the detailed verification algorithm using quantum walks, and an analysis of how it validates genuine banknotes and foils counterfeit attempts.
-% \vspace{1em}
-
-% \chapter{Verification Algorithm Using Quantum Walks}
-% The Hartley-based quantum money scheme introduced in the previous chapter requires a new verification procedure to address the issues that arise from using real amplitude states.
+\vspace{1em}
+
+\chapter{Verification Algorithm Using Quantum Walks}
+The Hartley-based quantum money scheme introduced in the previous chapter requires a new verification procedure to address the issues that arise from using real amplitude states.
 In this chapter, we describe and analyze the verification algorithm, which leverages continuous-time quantum walks on the group action graph (and their efficient simulation from Chapter 4) to extract the information needed to authenticate a banknote.
 
-%     \section{Challenges with Naïve Verification}
-%     Before detailing the new algorithm, let us briefly recap why the straightforward approach fails.
+    \section{Challenges with Naïve Verification}
+    Before detailing the new algorithm, let us briefly recap why the straightforward approach fails.
 In the Fourier-based scheme, verification was done by a single “kickback” operation using the claimed serial $g$, and measuring an auxiliary register.
@@
 
-%     To overcome this, our strategy is to perform a more complete measurement of the state’s “phase spectrum.” Instead of just one operation and measurement, we will use the quantum walk (with Hamiltonian $A = A(X,S)$ as defined earlier) to perform a form of phase estimation.
-
-%     \section{Using Quantum Walks to Extract the Serial}
-%     The central observation is that the money state $|\$_g\rangle$ is an eigenstate of the walk’s Hamiltonian $A$ on the group action Cayley graph.
+    To overcome this, our strategy is to perform a more complete measurement of the state’s “phase spectrum.” Instead of just one operation and measurement, we will use the quantum walk (with Hamiltonian $A = A(X,S)$ as defined earlier) to perform a form of phase estimation.
+
+    \section{Using Quantum Walks to Extract the Serial}
+    The central observation is that the money state $|\$_g\rangle$ is an eigenstate of the walk’s Hamiltonian $A$ on the group action Cayley graph.
 To see this, note that $|\$_g\rangle$ (Fourier or Hartley) lies in the subspace spanned by $\{|x\rangle: x \in X\}$ (we no longer explicitly keep the group element register, since after minting it’s entangled or measured away).
@@
 By definition,
-%     \[ A |x\rangle = \sum_{s \in S} |s * x\rangle, \] 
-%     summing over all neighbors under the generators.
+    \[ A |x\rangle = \sum_{s \in S} |s * x\rangle, \] 
+    summing over all neighbors under the generators.
 Now, $|\$_g\rangle$ is (up to normalization) $\sum_{h \in G} f(h)\, |h * x_0\rangle$ for some coefficient function $f(h)$.
 If one applies $A$ to this state:
-%     \[ A |\$_g\rangle = \sum_{s \in S} \sum_{h \in G} f(h)\, |s * (h * x_0)\rangle = \sum_{h \in G} f(h)\, \sum_{s \in S} |(sh) * x_0\rangle. \]
-%     Now change variable $h' = sh$ in the inner sum.
+    \[ A |\$_g\rangle = \sum_{s \in S} \sum_{h \in G} f(h)\, |s * (h * x_0)\rangle = \sum_{h \in G} f(h)\, \sum_{s \in S} |(sh) * x_0\rangle. \]
+    Now change variable $h' = sh$ in the inner sum.
 Since $s$ runs over all of $S$, $h'$ runs over $S h = \{sh: s \in S\}$ which is exactly the set of neighbors of $h$ in the Cayley graph of $G$.
@@
 
-%     For example, if $G = \mathbb{Z}_N$ and $S=\{1, -1\}$, a Fourier-based $|\$_g\rangle$ is essentially the character $\chi_g$, and indeed $\chi_g$ is an eigenfunction of the adjacency (which is like a cosine operator) with eigenvalue $2\cos(2\pi g/N)$.
+    For example, if $G = \mathbb{Z}_N$ and $S=\{1, -1\}$, a Fourier-based $|\$_g\rangle$ is essentially the character $\chi_g$, and indeed $\chi_g$ is an eigenfunction of the adjacency (which is like a cosine operator) with eigenvalue $2\cos(2\pi g/N)$.
 The Hartley-based state corresponds to a combination of $\chi_g$ and $\chi_{-g}$ (the real and imaginary parts combined), and ends up with the same eigenvalue $2\cos(2\pi g/N)$ as well.
@@
 
-%     The verification algorithm will do the following: it will run phase estimation on the unitary $U = e^{iA\tau}$ for some carefully chosen time $\tau$, using the state $|\psi\rangle$ as input.
+    The verification algorithm will do the following: it will run phase estimation on the unitary $U = e^{iA\tau}$ for some carefully chosen time $\tau$, using the state $|\psi\rangle$ as input.
 Phase estimation is a standard quantum algorithm that, given an eigenstate of $U$, yields an estimate of the eigenphase $2\pi \phi$ (where $e^{i 2\pi \phi}$ is the eigenvalue of $U$) to some specified precision.
@@
 
-%     We cannot run $e^{iA\tau}$ directly, but Chapter 4 showed how to simulate it efficiently with a discrete-time algorithm.
+    We cannot run $e^{iA\tau}$ directly, but Chapter 4 showed how to simulate it efficiently with a discrete-time algorithm.
 So when we say “phase estimation on $U = e^{iA\tau}$,” we imply using the simulation routine as a subroutine in the phase estimation circuit.
@@
 
-%     Now, because $\lambda$ (the eigenvalue of $A$) is related to $g$, obtaining $\lambda$ in effect gives us information about $g$.
+    Now, because $\lambda$ (the eigenvalue of $A$) is related to $g$, obtaining $\lambda$ in effect gives us information about $g$.
 However, one eigenvalue might correspond to two possible $g$ values (e.g., $\cos(2\pi g/N) = \cos(2\pi (N-g)/N)$).
@@
 
-%     In [31], it was shown that by using two or three carefully chosen multiples of time (or equivalently using the fact that $\lambda$ as a function of $g$ has a known form like a cosine series), one can uniquely recover $g$.
+    In [31], it was shown that by using two or three carefully chosen multiples of time (or equivalently using the fact that $\lambda$ as a function of $g$ has a known form like a cosine series), one can uniquely recover $g$.
 In our scheme, since $S$ is known and fixed, and presumably $S$ is such that the map $g \mapsto \lambda_g = \sum_{s\in S} \chi_g(s)$ is injective up to trivial symmetries, a few phase estimates suffice.
@@
 
-%     For simplicity, let’s suppose two runs with different $\tau$ values are enough. The output of the verification algorithm is then determined by:
-%     - If the estimated $g^*$ from the phase(s) matches the provided serial $g$, output \texttt{accept}.
-%     - Otherwise, output \texttt{reject}.
-
-%     Because a genuine $|\$_g\rangle$ is exactly an eigenstate with eigenvalue $\lambda_g$, phase estimation will return (with high probability) a number very close to $\lambda_g \tau$ modulo $2\pi$.
+    For simplicity, let’s suppose two runs with different $\tau$ values are enough. The output of the verification algorithm is then determined by:
+    - If the estimated $g^*$ from the phase(s) matches the provided serial $g$, output \texttt{accept}.
+    - Otherwise, output \texttt{reject}.
+
+    Because a genuine $|\$_g\rangle$ is exactly an eigenstate with eigenvalue $\lambda_g$, phase estimation will return (with high probability) a number very close to $\lambda_g \tau$ modulo $2\pi$.
 Given the precision, we decode it to the nearest valid $\lambda_{g'}$ value, which should be $\lambda_g$.
@@
 For a counterfeit state, two things can happen:
-%     1.
+    1.
 The state $|\psi\rangle$ is a superposition of eigenstates (not a single eigenstate).
@@
 In fact, unless the counterfeit state was itself aligned with one particular eigenvalue, the measurement will likely produce a result that does not correspond to the claimed serial, leading to rejection.
-%     2.
+    2.
 The state $|\psi\rangle$ happens to be an eigenstate, but with a wrong eigenvalue (i.e., corresponding to some $g' \neq g$).
@@
 
-%     Thus, the only way to pass is to present a state that is an eigenstate with eigenvalue matching the serial.
+    Thus, the only way to pass is to present a state that is an eigenstate with eigenvalue matching the serial.
 But the only known way to produce such a state is essentially to follow the minting procedure (due to the one-wayness of the group action, they can’t derive $|\$_g\rangle$ without knowing $g$ or breaking the assumption).
 
-%     One might wonder: phase estimation is a probabilistic algorithm; what if it sometimes yields the correct $g^*$ and sometimes not, could an adversary repeat the verification or something?
+    One might wonder: phase estimation is a probabilistic algorithm; what if it sometimes yields the correct $g^*$ and sometimes not, could an adversary repeat the verification or something?
 In practice, the banknote verification either passes or fails once; an adversary doesn’t get to try multiple times on the same note without potentially decohering it or being caught.
@@
 
-%     Finally, our algorithm implicitly uses the ability to perform the controlled-$U$ operations for phase estimation.
+    Finally, our algorithm implicitly uses the ability to perform the controlled-$U$ operations for phase estimation.
 That is non-trivial but our quantum walk simulation provided a way to implement $e^{iA\tau}$, and controlled versions can be constructed by controlling each gate in the simulation (which increases complexity by at most a factor poly(n)).
@@
 
-%     \section{Detailed Verification Procedure}
-%     To summarize, here is a more step-by-step description of the verification algorithm for a banknote $(g, |\psi\rangle)$:
-%     \begin{enumerate}
-%         \item **Preparation:** Determine a set of one or more time parameters $\{\tau_1, \tau_2, \dots, \tau_m\}$ to be used for phase estimation.
+    \section{Detailed Verification Procedure}
+    To summarize, here is a more step-by-step description of the verification algorithm for a banknote $(g, |\psi\rangle)$:
+    \begin{enumerate}
+        \item **Preparation:** Determine a set of one or more time parameters $\{\tau_1, \tau_2, \dots, \tau_m\}$ to be used for phase estimation.
 These might be hardcoded or depend on $N$ and $S$.
 For example, $\tau_1$ could be a basic time and $\tau_2$ another that breaks degeneracy.
-%         \item **Phase Estimation Rounds:** For each $\tau_j$:
-%         \begin{enumerate}
-%             \item Use the quantum walk simulation circuit to implement controlled-$e^{iA \tau_j}$ on $|\psi\rangle$.
+        \item **Phase Estimation Rounds:** For each $\tau_j$:
+        \begin{enumerate}
+            \item Use the quantum walk simulation circuit to implement controlled-$e^{iA \tau_j}$ on $|\psi\rangle$.
 (In practice, we append an ancilla register to accumulate the phase, as in standard phase estimation algorithms.
@@
 This is the standard routine.)
-%             \item Measure the phase register to obtain an estimate $\tilde{\phi}_j$ of $\lambda_g \tau_j / (2\pi)$ (mod 1).
+            \item Measure the phase register to obtain an estimate $\tilde{\phi}_j$ of $\lambda_g \tau_j / (2\pi)$ (mod 1).
 Multiply by $2\pi/\tau_j$ to get an estimate $\tilde{\lambda}_j$ of $\lambda_g$.
-%         \end{enumerate}
-%         \item **Compute Serial Candidate:** From the collection $\{\tilde{\lambda}_j\}$, solve for the group element $g^*$ that would produce those eigenvalues.
+        \end{enumerate}
+        \item **Compute Serial Candidate:** From the collection $\{\tilde{\lambda}_j\}$, solve for the group element $g^*$ that would produce those eigenvalues.
 This might involve inverting the known relation $\lambda = \sum_{s\in S}\cas(2\pi \langle g, s\rangle/N)$ or whatever the formula is in our context.
 Because of estimation error, we choose the nearest matching $g^*$ in $G$ that would give eigenvalues close to the $\tilde{\lambda}_j$ observed.
-%         \item **Accept/Reject:** If $g^* = g$ (and all rounds of phase estimation yielded results consistent with a single $g^*$, which should happen for a valid note), then output \texttt{accept}.
+        \item **Accept/Reject:** If $g^* = g$ (and all rounds of phase estimation yielded results consistent with a single $g^*$, which should happen for a valid note), then output \texttt{accept}.
 Otherwise, output \texttt{reject}.
-%     \end{enumerate}
-
-%     This algorithm may seem complex, but it can be optimized.
+    \end{enumerate}
+
+    This algorithm may seem complex, but it can be optimized.
 In practice, we could combine multiple phase estimation steps into one larger quantum circuit that extracts $g$ in one go, but conceptually, it’s easier to think of them separately.
 
-%     \section{Analysis of Security and Efficiency}
-%     The new verification algorithm is more involved than the original Fourier-based one, so we must check that it is still efficient and that it indeed thwarts counterfeiting.
-
-%     **Efficiency:** Each phase estimation round uses polynomial-time quantum operations.
+    \section{Analysis of Security and Efficiency}
+    The new verification algorithm is more involved than the original Fourier-based one, so we must check that it is still efficient and that it indeed thwarts counterfeiting.
+
+    **Efficiency:** Each phase estimation round uses polynomial-time quantum operations.
 The Hamiltonian simulation of $e^{iA\tau}$ for sparse $A$ on $N$-dimensional space can be done in $\operatorname{poly}(\log N)$ time (since queries to the group action oracle are $O(1)$ and $|S|$ is small).
@@
 
-%     **Completeness:** A genuine banknote state $|\$_g\rangle$ will be accepted with high probability.
+    **Completeness:** A genuine banknote state $|\$_g\rangle$ will be accepted with high probability.
 The state is an eigenstate of $A$, so phase estimation yields exactly $\lambda_g$ (with small error $\epsilon$).
@@
 
-%     **Soundness:** A counterfeiter’s goal is to have $\mathsf{Verify}(g, |\psi\rangle) = \texttt{accept}$ for some $|\psi\rangle$ that they created without running $\mathsf{Mint}$.
+    **Soundness:** A counterfeiter’s goal is to have $\mathsf{Verify}(g, |\psi\rangle) = \texttt{accept}$ for some $|\psi\rangle$ that they created without running $\mathsf{Mint}$.
 Essentially, they either try to reuse a state they already saw or combine states to get two accepted notes, etc.
 If they attempt to create a new state for an unused serial $g$, they face the following:
-%     - If $|\psi\rangle$ is not an eigenstate of $A$, when we run phase estimation, the outcome is a random eigenvalue from its spectral decomposition.
+    - If $|\psi\rangle$ is not an eigenstate of $A$, when we run phase estimation, the outcome is a random eigenvalue from its spectral decomposition.
 It would be a huge coincidence if that random eigenvalue corresponded to exactly the claimed $g$.
@@
 Unless the state was aligned to one particular $g'$, in which case the best they can do is claim it is $g'$.
-%     - If $|\psi\rangle$ \emph{is} an eigenstate but for $g' \neq g$, then our algorithm will find $g'$ and compare to $g$ and reject.
+    - If $|\psi\rangle$ \emph{is} an eigenstate but for $g' \neq g$, then our algorithm will find $g'$ and compare to $g$ and reject.
 So the adversary would have to guess the serial number’s eigenstate perfectly, which means they basically guessed the bank’s secret or solved the one-way problem.
 
-%     The most cunning forgery could be to use a genuine note $(g, |\$_g\rangle)$ and try to produce a second independent state $|\$_g\rangle$ for the same $g$.
+    The most cunning forgery could be to use a genuine note $(g, |\$_g\rangle)$ and try to produce a second independent state $|\$_g\rangle$ for the same $g$.
 But that is essentially copying a quantum state which is unknown to them (they only know $g$ classically).
@@
 
-%     Thus, the only resource the adversary has is perhaps other genuine notes they possess.
+    Thus, the only resource the adversary has is perhaps other genuine notes they possess.
 Could they entangle two notes or something to produce two valid ones?
@@
 
-%     Therefore, we argue the scheme remains secure: forging in any meaningful sense would require solving a hard problem (inverting the group action or cloning a quantum state).
-
-%     In conclusion, by using continuous-time quantum walks and phase estimation, our verification algorithm retrieves the hidden serial number encoded in the quantum money state and compares it to the claimed serial.
+    Therefore, we argue the scheme remains secure: forging in any meaningful sense would require solving a hard problem (inverting the group action or cloning a quantum state).
+
+    In conclusion, by using continuous-time quantum walks and phase estimation, our verification algorithm retrieves the hidden serial number encoded in the quantum money state and compares it to the claimed serial.
 This not only fixes the issue introduced by using the Hartley transform (real amplitudes), but it does so in polynomial time.

### 2025-04-09 draft.tex
draft updated

@@
 
-\title{Quantum Walks and Application to Quantum Money}
+\title{
+  Quantum Walks and Application to Quantum Money\\[1em]
+  \large Supervised by Dr. Jake Doliskani\\[3em]
+  \normalsize McMaster University\\
+  Department of Computing and Software
+}
 \author{Ali Mousavi}
@@
 \newpage
-\textbf{Abstract}
+\textbf{\large Abstract}
 
@@
 \[
-|g\rangle \mapsto \frac{1}{\sqrt{N}}\sum_{h \in G} \chi_h(g)\, |h\rangle,
-\]
-where $\{\chi_h\}$ are the characters (complex exponential homomorphisms) of $G$.
+|g\rangle \mapsto \frac{1}{\sqrt{N}}\sum_{h \in G} \chi(h,g)\, |h\rangle,
+\]
+where $\{\chi(h,.)\}$ are the characters (complex exponential homomorphisms) of $G$.
 When $G = \mathbb{Z}_N$ (the integers mod $N$), the QFT takes $|j\rangle$ to $\frac{1}{\sqrt{N}}\sum_{k=0}^{N-1} e^{2\pi i j k / N} |k\rangle$.
@@
 \[
-\operatorname{QHT}_N: \ket{a} \mapsto \frac{1}{\sqrt{N}} \sum_{y = 0}^{N - 1} cas\left(\frac{2\pi a y}{N}\right) \ket{y}, \quad \text{where } cas(x) = \cos(x) + \sin(x).
+\operatorname{QHT}_N: \ket{a} \mapsto \frac{1}{\sqrt{N}} \sum_{y = 0}^{N - 1} \cas\left(\frac{2\pi a y}{N}\right) \ket{y}, \quad \text{where } \cas(x) = \cos(x) + \sin(x).
 \]
@@
 \begin{equation}
-    \operatorname{QHT}_G(f)({a}) = \frac{1}{\sqrt{|G|}} \sum_{{y} \in G} cas(2\pi \langle {a}, \alpha({y}) \rangle) f({y}),
+    \operatorname{QHT}_G(f)({a}) = \frac{1}{\sqrt{|G|}} \sum_{{y} \in G} \cas(2\pi \langle {a}, \alpha({y}) \rangle) f({y}),
 \end{equation}
@@
 \[
-cas(2\pi \langle {a}, \alpha({y}) \rangle) = \frac{1 - i}{2}\chi({a}, {y}) + \frac{1 + i}{2}\chi(-{a}, {y}),
+\cas(2\pi \langle {a}, \alpha({y}) \rangle) = \frac{1 - i}{2}\chi({a}, {y}) + \frac{1 + i}{2}\chi(-{a}, {y}),
 \]
@@
 A \textbf{group action} of a group $G$ on a set $X$ is a function $*\colon G \times X \to X$ that satisfies two properties: (1) the identity element $e \in G$ acts trivially on every $x \in X$ ($e * x = x$), and (2) the action is compatible with the group operation, meaning $g*(h* x) = (gh)*x$ for all $g,h \in G$ and $x \in X$.
-We will often denote the result of $g$ acting on $x$ by $g*x$ or simply $g x$ when the action is clear from context.
+We will denote the result of $g$ acting on $x$ by $g*x$.
 
@@
 Cryptographic group actions provide a natural platform for public-key quantum money schemes.
-In such schemes, the secret “serial number” of a quantum banknote can be an element $g \in G$, and the quantum state of the banknote can be some function of $g*x_0$ for a public base point $x_0 \in X$.
-The hardness of inverting the action ($x_0$ and $x = g*x_0$ do not easily reveal $g$) contributes to the security against counterfeiting, while the structure of the group action can be used to efficiently verify authenticity (as we will see with the Fourier or Hartley transform techniques).
+In such schemes, the secret “serial number” of a quantum banknote can be an element $h \in G$, and the quantum state of the banknote can be some function of $h*x_0$ for a public base point $x_0 \in X$.
+The hardness of inverting the action ($x_0$ and $x = h*x_0$ do not easily reveal $h$) contributes to the security against counterfeiting, while the structure of the group action can be used to efficiently verify authenticity (as we will see with the Fourier or Hartley transform techniques).
 
@@
 In many algorithmic contexts, either model can be used to achieve a quantum speedup.
-
 However, several important distinctions exist between the two models:
 
-\subsection{State Space}
-
-\begin{itemize}
-    \item \textbf{CTQW:} Evolves on the vertex Hilbert space $\mathbb{C}^{|V|}$.
-    \item \textbf{DTQW (Coined):} Uses an enlarged space $\mathbb{C}^{|V|} \otimes \mathbb{C}^d$, introducing a coin register to enable unitary evolution.
-\end{itemize}
-
-The coin adds extra degrees of freedom, allowing more design flexibility.
-However, it also increases the complexity of analysis and implementation since one must choose both the coin and shift operators carefully to ensure desired evolution.
-
-\subsection{Time Evolution}
-
-\begin{itemize}
-    \item \textbf{CTQW:} Evolution is governed by the continuous-time Schrödinger equation: $\ket{\psi(t)} = e^{-iHt} \ket{\psi(0)}$, allowing probing at arbitrary real-valued times $t$.
-    \item \textbf{DTQW:} Evolves in discrete time-steps via a unitary operator $U$ applied iteratively: $\ket{\psi(t)} = U^t \ket{\psi(0)}$, with $t \in \mathbb{Z}$.
-\end{itemize}
-
-DTQWs can exhibit periodic revivals and step-dependent interference patterns, while CTQWs exhibit behavior determined by the spectral decomposition of $H$.
-A DTQW can approximate a CTQW through Trotterization: setting $U \approx e^{-iH \Delta t}$ for small $\Delta t$ and iterating.
-
-\subsection{Generality}
-
-\begin{itemize}
-    \item \textbf{CTQW:} Any undirected graph naturally defines a Hermitian Hamiltonian and thus a valid walk.
-    \item \textbf{DTQW:} For general (especially irregular) graphs, defining a local coinless unitary operator may be challenging.
-Enlarged Hilbert spaces or alternate frameworks like Szegedy's construction are often required.
-\end{itemize}
-
-While coined DTQWs require more setup, they are ultimately general, and Szegedy's method can handle any reversible Markov chain.
-
-\subsection{Analytical Tools}
-
-\begin{itemize}
-    \item \textbf{CTQW:} Analysis reduces to diagonalizing the Hermitian Hamiltonian $H$.
-    \item \textbf{DTQW:} One must diagonalize the larger unitary operator $U$, which may have a more intricate spectrum due to the coin space.
-\end{itemize}
-
-In both cases, analysis is often facilitated by symmetry.
-For example, when the underlying graph is a Cayley graph or has high symmetry, representation theory can be used to obtain explicit eigenstates and eigenvalues.
-
-\subsection{Equivalences}
-
-There exist formal correspondences between the two models. For instance:
-\begin{itemize}
-    \item A coined DTQW can approximate a CTQW in the limit of small time-steps (Childs et al.).
-    \item CTQWs can be embedded into DTQWs by using additional coin degrees of freedom to emulate continuous evolution.
-\end{itemize}
-
-Thus, the two models are equivalent in computational power. However, in practice, one may be more natural or efficient depending on the problem. For example:
-\begin{itemize}
-    \item \textbf{CTQW:} Favored for spatial search on low-degree graphs due to the natural definition of a marked Hamiltonian.
-    \item \textbf{DTQW:} Preferred for quantizing arbitrary Markov chains (e.g., element distinctness on the Johnson graph), particularly using Szegedy’s framework.
-\end{itemize}
-
-\subsection{Summary}
-
-Continuous-time and discrete-time quantum walks are powerful and related models for quantum computation and algorithm design.
-CTQWs rely on continuous evolution under a Hermitian Hamiltonian and are tightly linked to physical systems.
-DTQWs require coin and shift operators but offer additional control and ease of implementation in gate-based architectures.
-
-Each model has advantages:
-\begin{itemize}
-    \item CTQWs often more closely mirror physical intuition.
-    \item DTQWs offer greater flexibility and modularity for algorithm design.
-\end{itemize}
-
-Results in one model can often be translated to the other with suitable modifications. Consequently, both are indispensable tools in the study of quantum algorithms.
+A key distinction between continuous-time quantum walks (CTQWs) and discrete-time quantum walks (DTQWs) lies in their \textit{state space construction}.
+CTQWs evolve solely on the vertex Hilbert space $\mathbb{C}^{|V|}$, while DTQWs typically operate on an enlarged Hilbert space of the form $\mathbb{C}^{|V|} \otimes \mathbb{C}^d$.
+This extension introduces a coin register, granting additional degrees of freedom that enable unitary evolution even on irregular graphs.
+Although this added structure allows for more nuanced and flexible design, it also complicates the analysis and implementation due to the need for careful choices of both coin and shift operators.
+
+The \textit{time evolution} mechanics further differentiate the two models.
+CTQWs evolve continuously according to the Schrödinger equation, $\ket{\psi(t)} = e^{-iHt} \ket{\psi(0)}$, allowing the system to be probed at any real-valued time $t$.
+In contrast, DTQWs evolve in discrete time steps via repeated application of a unitary operator $U$, such that $\ket{\psi(t)} = U^t \ket{\psi(0)}$, where $t \in \mathbb{Z}$.
+This discrete nature can lead to rich interference patterns and periodic revivals, whereas the behavior of CTQWs is largely governed by the spectral properties of the Hamiltonian $H$.
+Notably, DTQWs can approximate CTQWs via Trotterization by choosing $U \approx e^{-iH \Delta t}$ and taking small $\Delta t$.
+
+In terms of \textit{generality}, CTQWs are naturally defined on any undirected graph, as the adjacency matrix or Laplacian of the graph yields a Hermitian Hamiltonian that governs the walk.
+DTQWs, on the other hand, face more challenges on irregular graphs.
+Defining local, unitary, and coinless evolution in such cases may not be straightforward, necessitating either coin registers or alternative constructions like Szegedy’s framework, which generalizes DTQWs to work with any reversible Markov chain.
+Despite these hurdles, DTQWs are ultimately as general as CTQWs and even offer additional design flexibility in algorithmic applications.
+
+From the perspective of \textit{analytical techniques}, CTQWs benefit from the relatively simpler task of diagonalizing a Hermitian operator $H$.
+DTQWs, however, involve unitary operators acting on larger spaces, often with more complex spectra due to the coin degrees of freedom.
+In both models, leveraging the symmetry of the underlying graph can significantly simplify analysis.
+For example, in highly symmetric or Cayley graphs, representation theory can be employed to explicitly determine eigenvalues and eigenvectors.
+
+Interestingly, there exist formal \textit{equivalences} between the two models.
+A coined DTQW can approximate a CTQW through small time-step evolution, as demonstrated by Childs et al., and conversely, CTQWs can often be embedded into DTQWs by carefully engineering the coin space to emulate continuous dynamics.
+While both are computationally equivalent in power, each model has practical advantages in different settings.
+CTQWs are frequently preferred for spatial search on low-degree graphs due to the natural formulation of marked Hamiltonians.
+DTQWs, especially in Szegedy’s coinless formulation, excel in quantizing classical Markov chains and have been instrumental in algorithms such as element distinctness.
+
+In summary, continuous-time and discrete-time quantum walks offer complementary approaches to quantum computation and algorithm design.
+CTQWs provide an elegant, physics-inspired model of continuous evolution, while DTQWs offer modularity and fine-grained control well-suited for implementation in gate-based architectures.
+Though differing in form, the models are deeply connected, and insights from one can often be translated to the other, making both indispensable tools in the quantum algorithm designer’s toolkit.
 
@@
 Then we describe our Hartley-transform-based variant and discuss its properties.
-The quantum Hartley transform will play a central role in both the minting and verification of banknotes.
+The quantum Hartley transform will play a central role in both the generation and verification of banknotes.
 
 \section{Public-Key Quantum Money: Definitions}
-A public-key quantum money scheme consists of two algorithms, traditionally called $\mathsf{Mint}$ and $\mathsf{Verify}$:
+A public-key quantum money scheme consists of two algorithms, traditionally called $\mathsf{Gen}$ and $\mathsf{Verify}$:
 \begin{itemize}
@@
 \begin{enumerate}
-    \item On input $1^n$, sample a random group element $g \leftarrow G$. This $g$ will serve as the serial number $s$ for the banknote.
+    \item On input $1^n$, sample a random group element $h \leftarrow G$. This $h$ will serve as the serial number $s$ for the banknote.
     \item Prepare two registers: the first is a group element register, initialized to $|0_G\rangle$ (an encoding of the identity element of $G$), and the second is an $X$-register initialized to $|x_0\rangle$.
@@
     \[
-    \frac{1}{\sqrt{N}} \sum_{h \in G} |h\rangle \otimes |x_0\rangle\,.
-    \] 
-    \item Now apply the group action in a controlled manner: for each basis state $|h\rangle$ in the first register, apply $h$’s action on the second register. This transforms the joint state into 
-    \[
-    \frac{1}{\sqrt{N}} \sum_{h \in G} |h\rangle \otimes |h * x_0\rangle\,,
+    \frac{1}{\sqrt{N}} \sum_{g \in G} |g\rangle \otimes |x_0\rangle\,.
+    \] 
+    \item Now apply the group action in a controlled manner: for each basis state $|g\rangle$ in the first register, apply $g$’s action on the second register. This transforms the joint state into 
+    \[
+    \frac{1}{\sqrt{N}} \sum_{g \in G} |g\rangle \otimes |g * x_0\rangle\,,
     \] 
@@
     \[
-    \frac{1}{\sqrt{N}} \sum_{h \in G} \omega^{\langle g,\,h \rangle} |h\rangle \otimes |h * x_0\rangle\,,
-    \] 
-    where $\omega^{\langle g,\,h \rangle}$ denotes the phase picked up that depends on $g$ and $h$.
-In fact, this state can be written as $|g\rangle \otimes \frac{1}{\sqrt{N}}\sum_{h \in G} |h * x_0\rangle$; essentially, the first register ends up in $|g\rangle$ (the serial number) and the second register is an equal superposition of all elements of $X$ in the orbit of $x_0$ (which is $X$ itself, since the action is transitive) but weighted by a phase related to $g$.
+    \frac{1}{\sqrt{N}} \sum_{g \in G} \omega^{\langle h,\,g \rangle} |g\rangle \otimes |g * x_0\rangle\,,
+    \] 
+    where $\omega^{\langle h,\,g \rangle}$ denotes the phase picked up that depends on $h$ and $g$.
+In fact, this state can be written as $|h\rangle \otimes \frac{1}{\sqrt{N}}\sum_{g \in G} |g * x_0\rangle$; essentially, the first register ends up in $|h\rangle$ (the serial number) and the second register is an equal superposition of all elements of $X$ in the orbit of $x_0$ (which is $X$ itself, since the action is transitive) but weighted by a phase related to $h$.
 This is the so-called group-action Fourier state.
-    \item The first register (which contains $|g\rangle$) is measured in the computational basis, yielding the random serial number $g$ and collapsing the second register to a state that we will denote $|\$_g\rangle$.
-This $|\$_g\rangle$ is the actual quantum money state corresponding to serial $g$.
-    \item Output the pair $(s = g,\; |\$\rangle = |\$_g\rangle)$.
+    \item The first register (which contains $|h\rangle$) is measured in the computational basis, yielding the random serial number $g$ and collapsing the second register to a state that we will denote $|\$_h\rangle$.
+This $|\$_h\rangle$ is the actual quantum money state corresponding to serial $h$.
+    \item Output the pair $(s = h,\; |\$\rangle = |\$_h\rangle)$.
 \end{enumerate}
 
-In the above, a bit of algebra reveals that $|\$_g\rangle = \frac{1}{\sqrt{N}} \sum_{h \in G} \chi_g(h)\, |h * x_0\rangle$, where $\chi_g(h) = \omega^{\langle g,\,h \rangle}$ is essentially the character of $G$ indexed by $g$.
-In other words, $|\$_g\rangle$ is (up to global phase) the state one gets by applying the representation (character) $\chi_g$ to weight the superposition over the orbit $X$.
-These states for different $g$ are almost orthogonal and can be distinguished with the right measurement.
-
-The verification algorithm $\mathsf{Verify}(g, |\$_g\rangle)$ for Zhandry’s scheme goes as follows:
+In the above, a bit of algebra reveals that $|\$_h\rangle = \frac{1}{\sqrt{N}} \sum_{g\in G} \chi(h,g)\, |g * x_0\rangle$, where $\chi(h,g) = \omega^{\langle h,\,g \rangle}$ is essentially the character of $G$ indexed by $h$.
+In other words, $|\$_h\rangle$ is (up to global phase) the state one gets by applying the representation (character) $\chi(h,.)$ to weight the superposition over the orbit $X$.
+These states for different $h$ are almost orthogonal and can be distinguished with the right measurement.
+
+The verification algorithm $\mathsf{Verify}(h, |\$_h\rangle)$ for Zhandry’s scheme goes as follows:
 \begin{enumerate}
-    \item Given the purported serial number $g \in G$ and an input state $|\psi\rangle$ (which should equal $|\$_g\rangle$ if genuine), attach an auxiliary register prepared in $|x_0\rangle$.
-    \item Perform a controlled group action “kickback” using $g$ on the auxiliary register.
-Specifically, perform the unitary that maps $|y\rangle \otimes |x_0\rangle \mapsto |y\rangle \otimes |g * x_0 \rangle$ for each basis element $|y\rangle$ of the first register.
-(This operation uses the classical $g$ to act on the second register conditioned on the first—essentially, it multiplies the second register’s state by $g$ if the first register is in an appropriate basis state.
-There are various ways to implement this, but conceptually it’s a controlled operation using the known $g$.)
+    \item Given the purported serial number $h \in G$ and an input state $|\psi\rangle$ (which should equal $|\$_h\rangle$ if genuine), attach an auxiliary register prepared in $|x_0\rangle$.
+    \item Perform a controlled group action “kickback” using $h$ on the auxiliary register.
+Specifically, perform the unitary that maps $|y\rangle \otimes |x_0\rangle \mapsto |y\rangle \otimes |h * x_0 \rangle$ for each basis element $|y\rangle$ of the first register.
+(This operation uses the classical $h$ to act on the second register conditioned on the first—essentially, it multiplies the second register’s state by $h$ if the first register is in an appropriate basis state.
+There are various ways to implement this, but conceptually it’s a controlled operation using the known $h$.)
     \item Now measure the second register (the auxiliary one) in the computational basis of $X$ to see if it is still $|x_0\rangle$.
-If the state $|\psi\rangle$ was the correct Fourier state $|\$_g\rangle$, one can show that this measurement will yield $x_0$ with high probability (constructive interference causes the $x_0$ component to be strong).
+If the state $|\psi\rangle$ was the correct Fourier state $|\$_h\rangle$, one can show that this measurement will yield $x_0$ with high probability (constructive interference causes the $x_0$ component to be strong).
 If $|\psi\rangle$ was not the correct state, the measurement is unlikely to give $x_0$.
@@
 
-The intuition is that the genuine state $|\$_g\rangle$ contains a phase that exactly cancels out the action of $g$ in the verification step, causing the auxiliary register to end up back at $x_0$.
+The intuition is that the genuine state $|\$_h\rangle$ contains a phase that exactly cancels out the action of $h$ in the verification step, causing the auxiliary register to end up back at $x_0$.
 A counterfeit state, by contrast, would not generally have the right phase relationship, and the auxiliary register’s state would be some superposition over $X$ that is not concentrated on $x_0$, hence likely giving a different outcome upon measurement.
@@
 Zhandry’s scheme is shown to be correct (valid notes pass) and is believed to be secure under the assumption that the group action is one-way.
-The hardness essentially boils down to: given $x_0$ and $|\$_g\rangle$, an adversary cannot figure out a different $g'$ that would produce a second valid state $|\$_{g'}\rangle$ or replicate $|\$_g\rangle$ (because that would solve the hidden subgroup or discrete log type problem in the group action).
+The hardness essentially boils down to: given $x_0$ and $|\$_h\rangle$, an adversary cannot figure out a different $h'$ that would produce a second valid state $|\$_{h'}\rangle$ or replicate $|\$_h\rangle$ (because that would solve the hidden subgroup or discrete log type problem in the group action).
 
@@
 
-Concretely, assume again a group action $G \curvearrowright X$ with $|G|=N$. We fix the same generating set $S$ and basepoint $x_0$. The $\mathsf{Mint}_{H}$ (Hartley mint) algorithm:
+Concretely, assume again a group action $G \curvearrowright X$ with $|G|=N$. We fix the same generating set $S$ and basepoint $x_0$. The $\mathsf{Gen}_{H}$ (Hartley generation) algorithm:
 \begin{enumerate}
-    \item Sample a random $g \leftarrow G$ to be the serial number.
+    \item Sample a random $h \leftarrow G$ to be the serial number.
     \item Prepare $|0_G, x_0\rangle$ as before.
@@
     \[
-       \mathrm{QHT}: |h\rangle \mapsto \frac{1}{\sqrt{N}} \sum_{k \in G} \cas \!\Big(\frac{2\pi \langle k,h \rangle}{N}\Big) |k\rangle,
-    \] 
-    where $\mathrm{cas}(\theta) = \cos \theta + \sin \theta$ and $\langle k,h \rangle$ denotes some pairing like an exponent or dot product (for cyclic groups this is just $kh$).
-In simpler terms, $\mathrm{QHT}(|0_G\rangle) = \frac{1}{\sqrt{N}}\sum_{k \in G} |k\rangle$ (because $cas(0)=1$), \emph{the same uniform superposition as the QFT produces for $|0\rangle$}.
-So after this step, we again have $\frac{1}{\sqrt{N}}\sum_{h \in G} |h\rangle|x_0\rangle$, but crucially the coefficients are all \emph{real} and positive (in fact all $1/\sqrt{N}$).
-    \item Perform the controlled group action by the first register on the second: $\frac{1}{\sqrt{N}}\sum_{h} |h\rangle |h*x_0\rangle$.
+       \mathrm{QHT}: |g\rangle \mapsto \frac{1}{\sqrt{N}} \sum_{k \in G} \cas \!\Big(\frac{2\pi \langle k,g \rangle}{N}\Big) |k\rangle,
+    \] 
+    where $\mathrm{cas}(\theta) = \cos \theta + \sin \theta$ and $\langle k,g \rangle$ denotes some pairing like an exponent or dot product (for cyclic groups this is just $kg$).
+In simpler terms, $\mathrm{QHT}(|0_G\rangle) = \frac{1}{\sqrt{N}}\sum_{k \in G} |k\rangle$ (because $\cas(0)=1$), \emph{the same uniform superposition as the QFT produces for $|0\rangle$}.
+So after this step, we again have $\frac{1}{\sqrt{N}}\sum_{g \in G} |g\rangle|x_0\rangle$, but crucially the coefficients are all \emph{real} and positive (in fact all $1/\sqrt{N}$).
+    \item Perform the controlled group action by the first register on the second: $\frac{1}{\sqrt{N}}\sum_{g} |g\rangle |g*x_0\rangle$.
     \item Apply the inverse QHT on the first register (which being its own inverse up to a constant factor, is the same operation again since Hartley is symmetric like Fourier).
@@
     \[
-       \frac{1}{\sqrt{N}} \sum_{h \in G} \cas\!\Big(\frac{2\pi \langle g,h \rangle}{N}\Big)\, |h\rangle \otimes |h*x_0\rangle.
+       \frac{1}{\sqrt{N}} \sum_{g \in G} \cas\!\Big(\frac{2\pi \langle h,g \rangle}{N}\Big)\, |g\rangle \otimes |g*x_0\rangle.
     \] 
     Because the Hartley transform combines what would be cosine and sine terms, this state is not as nicely factorable as in the Fourier case.
-In the Fourier case, we got $|g\rangle \otimes \text{(orbit state)}$.
-In the Hartley case, we do not get a single basis state in the first register; instead we get a superposition in the first register with real coefficients $c_h = cas(2\pi\langle g,h\rangle/N)$.
-However, note that $c_h$ is just some real number in $[-1,1]$ depending on $g$ and $h$.
+In the Fourier case, we got $|h\rangle \otimes \text{(orbit state)}$.
+In the Hartley case, we do not get a single basis state in the first register; instead we get a superposition in the first register with real coefficients $c_g = \cas(2\pi\langle h,g\rangle/N)$.
+However, note that $c_g$ is just some real number in $[-1,1]$ depending on $h$ and $g$.
 Another way to express the above state is:
     \[
-      |\$\rangle = \frac{1}{\sqrt{N}} \sum_{x \in X} \Big(\frac{1}{\sqrt{N}}\sum_{h: h*x_0 = x} \cas\!\big(\frac{2\pi \langle g,h \rangle}{N}\big)\Big)\, |x\rangle.
-    \] 
-    Since for a given $x\in X$, all $h$ such that $h*x_0=x$ have the form $h = u g$ for a unique $u \in G$ (because the action is free and transitive), one can simplify the internal sum using properties of the cas function.
+      |\$\rangle = \frac{1}{\sqrt{N}} \sum_{x \in X} \Big(\frac{1}{\sqrt{N}}\sum_{g: g*x_0 = x} \cas\!\big(\frac{2\pi \langle h,g \rangle}{N}\big)\Big)\, |x\rangle.
+    \] 
+    Since for a given $x\in X$, all $g$ such that $g*x_0=x$ have the form $g = u h$ for a unique $u \in G$ (because the action is free and transitive), one can simplify the internal sum using properties of the cas function.
 But we need not dive into that here.
     \item No measurement of the first register is performed.
-In fact, we do not have a nice product state separation, so we cannot simply measure one register to get $g$.
-Instead, the output of minting is just the quantum state $|\$\rangle$ (which is entangled between what used to be two registers) and the known classical serial number $g$ (we know what $g$ we picked).
+In fact, we do not have a nice product state separation, so we cannot simply measure one register to get $h$.
+Instead, the output of minting is just the quantum state $|\$\rangle$ (which is entangled between what used to be two registers) and the known classical serial number $h$ (we know what $h$ we picked).
 \end{enumerate}
@@
 In particular, in the computational basis of $X$, the state $|\$\rangle$ is some real-vector state (with both positive and negative values possible).
-We can think of it as a “Hartley orbit state” corresponding to $g$.
-
-The verification algorithm in our Hartley-based scheme attempts to mirror the Fourier-based verification: it will use the given serial $g$ and try to check the state.
+We can think of it as a “Hartley orbit state” corresponding to $h$.
+
+The verification algorithm in our Hartley-based scheme attempts to mirror the Fourier-based verification: it will use the given serial $h$ and try to check the state.
 A first idea would be: do exactly the same as Zhandry’s verify (the group-action kickback and measure).
 However, this fails in certain cases.
-Specifically, the Hartley transform being real causes an ambiguity: it turns out that there exist distinct $g \neq g'$ for which the Hartley-based states $|\$\rangle_g$ and $|\$\rangle_{g'}$ are not orthogonal, and the original verification might accept a forged state that is a certain superposition.
+Specifically, the Hartley transform being real causes an ambiguity: it turns out that there exist distinct $h \neq h'$ for which the Hartley-based states $|\$\rangle_h$ and $|\$\rangle_{h'}$ are not orthogonal, and the original verification might accept a forged state that is a certain superposition.
 In fact, the verification algorithm might accept an illegitimate state with some probability bounded away from zero.
@@
 \begin{enumerate}
-    \item Given $(g, |\psi\rangle)$, it first uses the \textbf{quantum walk-based phase estimation} method (to be detailed in Chapter 6) to \emph{compute the eigenphase corresponding to $g$}.
-In short, we will treat $|\psi\rangle$ as an eigenvector of the group action adjacency matrix with a certain eigenvalue $\lambda$ related to $g$.
+    \item Given $(h, |\psi\rangle)$, it first uses the \textbf{quantum walk-based phase estimation} method (to be detailed in Chapter 6) to \emph{compute the eigenphase corresponding to $h$}.
+In short, we will treat $|\psi\rangle$ as an eigenvector of the group action adjacency matrix with a certain eigenvalue $\lambda$ related to $h$.
 We run a procedure to estimate $\lambda$ to high precision.
-    \item From the estimated eigenvalue(s), we reconstruct a candidate group element $g^*$ that we believe generated the state.
-(This uses the fact that by running phase estimation for multiple carefully chosen walk durations, one can solve for $g$ as shown in [31].)
-    \item We check if $g^* = g$ (the serial number provided). If not, we reject, since the state does not match the serial. If yes, we accept.
+    \item From the estimated eigenvalue(s), we reconstruct a candidate group element $h^*$ that we believe generated the state.
+(This uses the fact that by running phase estimation for multiple carefully chosen walk durations, one can solve for $h$ as shown in [31].)
+    \item We check if $h^* = h$ (the serial number provided). If not, we reject, since the state does not match the serial. If yes, we accept.
 \end{enumerate}
@@
 This procedure essentially extracts the hidden group element from the state and compares it to the claimed serial.
-If an adversary tries to forge a state $|\psi\rangle$ for a known serial $g$, the only way to consistently pass verification is if $|\psi\rangle$ truly encodes the same $g$ in its eigen-spectrum.
-A fake note that was causing trouble for the naive Hartley verification (e.g., a state that is a mixture of two different “Hartley orbit” states) would yield an eigenphase that does not correspond to a single valid $g$, and the algorithm would detect the mismatch.
+If an adversary tries to forge a state $|\psi\rangle$ for a known serial $h$, the only way to consistently pass verification is if $|\psi\rangle$ truly encodes the same $h$ in its eigen-spectrum.
+A fake note that was causing trouble for the naive Hartley verification (e.g., a state that is a mixture of two different “Hartley orbit” states) would yield an eigenphase that does not correspond to a single valid $h$, and the algorithm would detect the mismatch.
 
 The key quantum tool enabling this verification is the continuous-time quantum walk on the group action graph and the ability to simulate it, which we prepared in Chapter 4.
-The walk Hamiltonian $A(X,S)$ has the genuine money state $|\$\rangle_g$ as an eigenstate with a known eigenvalue $\lambda(g)$.
+The walk Hamiltonian $A(X,S)$ has the genuine money state $|\$\rangle_h$ as an eigenstate with a known eigenvalue $\lambda(h)$.
 By running phase estimation on $e^{-iA t}$ with the state $|\psi\rangle$, we attempt to measure that eigenvalue.
-We repeat for a few different values of $t$ (the “twists” or different phases) to get enough information to pinpoint $g$.
+We repeat for a few different values of $t$ (the “twists” or different phases) to get enough information to pinpoint $h$.
 This approach can be viewed as adding extra “twists” to the verification: effectively, each choice of $t$ in phase estimation is like looking at the state in a different interference fringe pattern, analogous to applying different group actions as twists in the verification procedure.
@@
 
+\chapter*{Conclusion}
+\addcontentsline{toc}{chapter}{Conclusion}
+
+In this thesis, we explored the rich interplay between quantum walks, group actions, and quantum cryptographic constructions.
+Starting from the theoretical foundations of quantum computation and group action-based cryptography, we developed a novel public-key quantum money scheme based on the quantum Hartley transform.
+By substituting the conventional Fourier transform with the Hartley transform, our construction yields real-amplitude quantum banknotes—an innovation that may simplify certain implementations and provide alternative security features.
+
+A central technical contribution was the use of continuous-time quantum walks for verification.
+We demonstrated that such walks can be simulated efficiently in the group-action setting, even in the absence of an explicit Fourier diagonalization.
+This approach allows for extracting the serial number (a hidden group element) from the quantum money state with high success probability, thereby providing a sound and efficient verification mechanism.
+Our method leverages the spectral structure and symmetry properties of Cayley graphs, extending the utility of quantum walks into cryptographic applications.
+
+Beyond its specific contributions to quantum money, this work opens up new directions for incorporating real-valued quantum transforms and continuous-time quantum walks into broader quantum algorithm design.
+We hope these ideas encourage further research into real-amplitude quantum information, new quantum primitives based on group actions, and the exploration of quantum walks as tools for secure and efficient computation.
+
 \bibliographystyle{plain}

### 2025-04-09 draft.tex
draft updated

@@
 \chapter{Introduction}
-Quantum money, first introduced in a seminal paper by Wiesner [29], is a form of currency represented by quantum states.
+Quantum money, first introduced in a seminal paper by Wiesner~\cite{Wiesner1983}, is a form of currency represented by quantum states.
 Unlike classical money, an ideal quantum bill cannot be counterfeited due to the no-cloning theorem of quantum mechanics, which prohibits making an identical copy of an unknown quantum state.
@@
 
-In 2009, Aaronson [1] proposed the first \emph{public-key quantum money} scheme, in which anyone can verify a quantum banknote while only the bank can mint (issue) new valid banknotes.
+In 2009, Aaronson~\cite{Aaronson2009} proposed the first \emph{public-key quantum money} scheme, in which anyone can verify a quantum banknote while only the bank can mint (issue) new valid banknotes.
 Public-key quantum money removes the transactional bottleneck of involving the bank every time.
-Aaronson’s specific scheme was later broken by Lutomirski et al.~[24].
-In the years since, several alternative public-key quantum money constructions have been explored [2, 17, 30, 19, 20, 23, 31].
-However, each of these proposals has either been broken by further cryptanalysis [14, 26, 7, 23] or relies on unconventional cryptographic assumptions, making their security or practicality questionable.
+Aaronson’s specific scheme was later broken by Lutomirski et al.~\cite{Lutomirski2010}.
+In the years since, several alternative public-key quantum money constructions have been explored.
+However, each of these proposals has either been broken by further cryptanalysis or relies on unconventional cryptographic assumptions, making their security or practicality questionable.
 
 \medskip\noindent\textbf{Quantum Money from Group Actions and the Fourier Transform.} 
-A promising candidate for secure public-key quantum money based on more standard assumptions was recently proposed by Zhandry [31].
+A promising candidate for secure public-key quantum money based on more standard assumptions was recently proposed by Zhandry~\cite{Zhandry2022}.
 In Zhandry’s scheme, the core idea is to use an abelian group action as the foundation for the quantum state.
@@
 The verification algorithm in this scheme uses a group-action phase kickback routine to extract the serial number from the quantum banknote and check its validity.
-Doliskani [15] later proved that Zhandry’s scheme is secure in the generic group action model, providing evidence for its security under well-defined assumptions.
+Doliskani~\cite{Doliskani2023} later proved that Zhandry’s scheme is secure in the generic group action model, providing evidence for its security under well-defined assumptions.
 
@@
 \begin{equation}
-\operatorname{QHT}_G = \frac{1 - i}{2} \operatorname{QFT}_G + \frac{1 + i}{2} \operatorname{QFT}_G^*,
+\operatorname{QHT}_G = \frac{1 - i}{2} \operatorname{QFT}_G + \frac{1 + i}{2} \operatorname{QFT}_G^*, \label{eq:QHT_QFT}
 \end{equation}
@@
 
-From this point forward, we assume the generating set \( Q \) is small, i.e., \( \abs{Q} = \operatorname{poly}(\log \abs{G}) \).
-In the first construction (where \( X = G \)), the walk \( e^{-iAt} \) can be efficiently implemented even for values of \( t \) that are exponentially large in \( \log \abs{G} \).
-This is a consequence of the identity:
+From this point onward, we assume that the generating set \( Q \) is small, specifically \( \abs{Q} = \operatorname{poly}(\log \abs{G}) \).
+In the first construction, where the vertex set is \( X = G \), the continuous-time walk \( e^{-iAt} \) can be implemented efficiently even for values of \( t \) that are exponentially large in \( \log \abs{G} \).
+This efficiency stems from the identity:
 \begin{equation}
@@
 \end{equation}
-where \( \operatorname{QFT}_G \) and its inverse can be implemented in \( \operatorname{poly}(\log \abs{G}) \) time.
-Moreover, the diagonal phase unitary \( \ket{a} \mapsto e^{-i\lambda_a t} \ket{a} \) is also efficient to implement, since the eigenvalues \( \lambda_a \) can be computed classically to arbitrary precision in \( \operatorname{poly}(\log \abs{G}) \) time.
-
-In contrast, the group-action setting presents greater computational difficulty.
-Although the states \( \ket{G^{(h)} * x} \) play a role analogous to the Fourier basis states \( \ket{\hat{h}} \), the presence of the action \( * \) makes the situation more subtle.
-In particular, implementing general transformations over these states is difficult; we are typically limited to operations of the form \( \ket{y} \mapsto \ket{a * y} \) for \( a \in G \).
-As a result, no efficient decomposition similar to~\eqref{eq:adjmat-fb} is known in the group-action setting.
-Instead, the best we can express is the spectral decomposition:
+where both \( \operatorname{QFT}_G \) and its inverse can be implemented in \( \operatorname{poly}(\log \abs{G}) \) time.
+Moreover, the diagonal unitary \( \ket{a} \mapsto e^{-i\lambda_a t} \ket{a} \) is efficiently realizable since the eigenvalues \( \lambda_a \) can be computed classically to arbitrary precision in polynomial time with respect to \( \log \abs{G} \).
+
+The situation becomes more nuanced in the group-action setting.
+Although the states \( \ket{G^{(h)} * x} \) play a role analogous to the Fourier basis states \( \ket{\hat{h}} \), the involvement of the group action \( * \) introduces additional complexity.
+In particular, implementing arbitrary transformations over these states is nontrivial.
+One is typically restricted to operations of the form \( \ket{y} \mapsto \ket{a * y} \), where \( a \in G \).
+Consequently, no efficient decomposition analogous to~\eqref{eq:adjmat-fb} is currently known in the group-action context.
+The best available formulation is the spectral decomposition:
 \[
@@
 
-Despite this limitation, the adjacency matrix \( A \) retains a high degree of sparsity and algebraic structure.
-In the next section, we will show that for \( t = \operatorname{poly}(\log \abs{G}) \), the walk \( e^{-iAt} \) can still be efficiently approximated to polynomial accuracy.
+Despite these challenges, the adjacency matrix \( A \) still exhibits substantial sparsity and algebraic structure.
+In the following section, we demonstrate that for \( t = \operatorname{poly}(\log \abs{G}) \), the walk \( e^{-iAt} \) remains efficiently approximable to polynomial accuracy.
 
@@
 
-\subsection{Simulating continuous-time walks}
-Childs and Berry, Childs, and Kothari showed that continuous-time quantum walks can be simulated using discrete-time quantum walks.
+\section{Simulating continuous-time walks}
+Childs~\cite{Childs2004}, Berry and Kothari~\cite{BerryKothari} showed that continuous-time quantum walks can be simulated using discrete-time quantum walks.
 Since our approach relies on their methods, we begin by outlining the relevant notation and framework.
@@
 
-\subsection{Simulating group action quantum walks.}
+\section{Simulating group action quantum walks.}
 Assume \( t = \operatorname{poly}(\log \abs{G}) \).
-We show that the continuous-time walk \( W = e^{-iAt} \) can be efficiently simulated using the discrete-time quantum walk framework developed in~\cite{childs2010relationship, berry2015hamiltonian}.
+We show that the continuous-time walk \( W = e^{-iAt} \) can be efficiently simulated using the discrete-time quantum walk framework developed in~\cite{childs2010relationship}.
 Recall the isometry \( T \) defined in Equation~\eqref{eq:walk-isom}, where the states \( \ket{\phi_b} \) are as given in Equation~\eqref{eq:walk-sim}.
@@
 
-Because of the structure of $\Gamma$, the states ....
-simplify as follows.
+Because of the structure of $\Gamma$, the states \eqref{eq:walk-sim} simplify as follows.
 First, since the set $Q$ is symmetric, the graph $\Gamma$ is undirected and the adjacency matrix $A$ is symmetric with non-negative entries; the nonzero entries of $A$ are all equal to $1$.
-Therefore, we can set $K = {A}_{\mathrm{max}} = 1$.
+Therefore, we can set $K = \opnorm{A}_{\mathrm{max}} = 1$.
 As a result, for $y \in X$, the state $\ket{\phi_{y0}}$ becomes
@@
     \label{thm:qht-cost}
-    Algorithm \ref{alg:qht-N} is correct and can be implemented using $\approx \log^2 N + O(\log N)$ elementary gates.
+    Algorithm above is correct and can be implemented using $\approx \log^2 N + O(\log N)$ elementary gates.
 % \end{theorem}
@@
 
-    Let \( T(N) \) denote the gate complexity of Algorithm~\ref{alg:qht-N} for an input of dimension \( N \).
-Assuming access to the \( R_j \) gates as elementary operations, the recurrence relation becomes
+    Let \( T(N) \) denote the gate complexity of the algorithm for an input of dimension \( N \). Assuming access to the \( R_j \) gates as elementary operations, the recurrence relation becomes
     \[
@@
 
-- The resulting complexity for an $N$-point QHT is $O(N \log N)$ basic quantum gates (up to polylog factors for precision), which is on par (up to constant factors) with the complexity of a QFT circuit.
+The resulting complexity for an $N$-point QHT is $O(\log^2 N)$ basic quantum gates (up to polylog factors for precision), which is on par (up to constant factors) with the complexity of a QFT circuit.
 We also derived explicit constants for small cases to show improvements over prior work.
@@
 The eigenvectors of $A$ are given by $\ket{\mathbb{Z}_N^{(h)} * x}$, with corresponding eigenvalues $\lambda_h = 2\cos(2\pi uh / N)$ for each $h \in \mathbb{Z}_N$.
-According to Theorem \ref{thm:sparse-sim} and the discussion that follows, the unitary evolution operator $W = e^{iAt}$ can be simulated efficiently to exponential precision.
+According to Theorem in the previous chapter and the discussion that follows, the unitary evolution operator $W = e^{iAt}$ can be simulated efficiently to exponential precision.
 To proceed, we first state the following lemma.
@@
         \end{align*}
-        where the second equality follows from the identity in \eqref{eq:ht-ft}, and the last equality follows from the fact that $\lambda_h = \lambda_{-h}$.
+        where the second equality follows from the identity in \eqref{eq:QHT_QFT}, and the last equality follows from the fact that $\lambda_h = \lambda_{-h}$.
     % \end{proof}
@@
     Since phase estimation can be applied with various choices of \( u \), we can obtain multiple approximations of \( \frac{uh}{N} \).
-As shown in~\cite{zhandry2024quantum}, selecting \( u \) appropriately allows us to reconstruct \( h \) exactly from these estimates.
+As shown in~\cite{Zhandry2024}, selecting \( u \) appropriately allows us to reconstruct \( h \) exactly from these estimates.
 
@@
 \begin{thebibliography}{99}
-% Sample Bib entries. Replace with real ones.
-\bibitem{Aaronson2009} S. Aaronson, ``Quantum Copy-Protection and Quantum Money,'' In Proc. of CCC, 2009.
-\bibitem{Zhandry2022} M. Zhandry, ``Quantum Money from Modular Forms,'' In Proc. of CRYPTO, 2022.
-\bibitem{Childs2003} A. M. Childs, ``Quantum Information Processing in Continuous Time,'' PhD Thesis, MIT, 2004.
-% Add all other references as needed
+
+    \bibitem{Wiesner1983}
+    S. Wiesner, ``Conjugate Observables and the Foundations of Cryptography,'' \textit{Sigact News}, vol. 15, no. 1, pp. 78–88, 1983.
+
+    \bibitem{Aaronson2009}
+    S. Aaronson, ``Quantum Copy-Protection and Quantum Money,'' In \textit{Proceedings of the IEEE Conference on Computational Complexity (CCC)}, 2009.
+
+    \bibitem{Lutomirski2010}
+    A.
+Lutomirski, S.
+Aaronson, E.
+Farhi, D.
+Gosset, J.
+Keselman, P.
+Shor, A.
+Slofstra, and A.
+Speyer, ``Breaking and Making Quantum Money: Toward a New Quantum Cryptographic Protocol,'' arXiv:1004.4843, 2010.
+
+    \bibitem{Zhandry2022}
+    M. Zhandry, ``Quantum Money from Modular Forms,'' In \textit{Proceedings of CRYPTO}, 2022.
+
+    \bibitem{Doliskani2023}
+    J. Doliskani, ``On the Security of Group Action-Based Quantum Money,'' unpublished manuscript, 2023.
+
+    \bibitem{Childs2004}
+    A. M. Childs, ``Quantum Information Processing in Continuous Time,'' Ph.D. thesis, Massachusetts Institute of Technology, 2004.
+
+    \bibitem{BerryKothari}
+    D. Berry and R. Kothari, ``Hamiltonian Simulation with Optimal Sample Complexity,'' In \textit{Proceedings of FOCS}, 2018.
+
+    \bibitem{Zhandry2024}
+    M.
+Zhandry, ``Quantum Money from Abelian Group Actions,'' In \textit{Proceedings of the 15th Innovations in Theoretical Computer Science Conference (ITCS)}, Schloss Dagstuhl–Leibniz Center for Informatics, 2024.
+
+    \bibitem{childs2010relationship}
+    A. M. Childs, ``On the Relationship Between Continuous- and Discrete-Time Quantum Walk,'' \textit{Communications in Mathematical Physics}, vol. 294, pp. 581–603, 2010.
+
 \end{thebibliography}

### 2025-04-10 draft.tex
draft updated

@@
 
-\usepackage{amsmath, amssymb, amsthm}
-\usepackage{graphicx}
-\usepackage{hyperref}
-\usepackage{cite}
-\usepackage{physics}
-\usepackage{algorithm}
-% \usepackage{algorithmic}
-\usepackage{tikz}
-\usepackage{caption}
-\usepackage{subcaption}
-\usepackage{setspace}
-\usepackage{algorithm}
-\usepackage{algpseudocode}
-
-\newcommand{\opnorm}[1]{\left\lVert #1 \right\rVert}
-
-\usepackage[a4paper, left=1.5cm, right=1.5cm, top=2cm, bottom=2cm]{geometry}
-
-% Formatting
-\setlength{\parskip}{0.5em}
-\setlength{\parindent}{0pt}
-\singlespacing
+\usepackage[margin= 1in]{geometry}
+\usepackage{article_macros}
+
+\sloppy
+\allowdisplaybreaks
 
@@
 
+\definecolor{citecolor}{HTML}{009933}
+
+\hypersetup{
+	unicode = true,
+    colorlinks = true,
+    citecolor = citecolor,
+    filecolor = blue,
+    linkcolor = blue,
+    urlcolor = blue,
+    pdfstartview = {FitH},
+}
+
 \title{
   Quantum Walks and Application to Quantum Money\\[1em]
-  \large Supervised by Dr. Jake Doliskani\\[3em]
+%   \large Supervised by Dr. Jake Doliskani\\[3em]
   \normalsize McMaster University\\
@@
 \newpage
-\textbf{\large Abstract}
+\textbf{\large Abstract}\\
 
@@
 We believe this shift from complex to real quantum states may offer both computational and theoretical advantages.
-For example, certain mathematical identities hold for any two real orthonormal bases that do not generally hold for complex bases; such differences can affect the properties of quantum states and were a barrier in prior analyses (indeed, an attempted “quantum lightning” construction in [31] failed due to properties of complex phases that do not arise with real amplitudes).
+For example, certain mathematical identities hold for any two real orthonormal bases that do not generally hold for complex bases; such differences can affect the properties of quantum states and were a barrier in prior analyses (indeed, an attempted “quantum lightning” construction in \cite{Zhandry2022} failed due to properties of complex phases that do not arise with real amplitudes).
 Beyond this specific context, our work is a first step toward employing real-valued quantum transforms in quantum cryptography and quantum algorithms.
@@
 The remainder of this thesis is organized as follows.
-In **Chapter 2**, we provide background on the basics of quantum computation and the theory of group actions, including the concept of cryptographic group actions which underlie our money scheme.
-**Chapter 3** covers quantum walks, both continuous-time and discrete-time, outlining their differences and importance in quantum algorithms.
-In **Chapter 4**, we apply the quantum walk framework to group actions: we describe how a continuous-time quantum walk on a group action can be simulated efficiently, a crucial step for our serial number extraction algorithm.
-**Chapter 5** details the quantum money scheme itself and the role of the Hartley transform in its construction.
+In Chapter~\ref{chap:backgound}, we provide background on the basics of quantum computation and the theory of group actions, including the concept of cryptographic group actions which underlie our money scheme.
+Chapter~\ref{chap:quantum_walks} covers quantum walks, both continuous-time and discrete-time, outlining their differences and importance in quantum algorithms.
+In Chapter~\ref{chap:simulating}, we apply the quantum walk framework to group actions: we describe how a continuous-time quantum walk on a group action can be simulated efficiently, a crucial step for our serial number extraction algorithm.
+Chapter~\ref{chap:quantum_money} details the quantum money scheme itself and the role of the Hartley transform in its construction.
 We explain how the scheme is formulated and discuss the advantages and challenges introduced by using the Hartley transform.
-Finally, **Chapter 6** presents the verification algorithm for the Hartley-based quantum money.
+Finally, Chapter~\ref{chap:verification} presents the verification algorithm for the Hartley-based quantum money.
 This chapter shows how we use quantum walks (as developed in Chapter 4) to reliably verify banknotes and compute their serial numbers, thereby addressing the verification issues that arose from the use of real amplitudes.
@@
 
-\chapter{Background of Quantum Computation and Group Actions}
+\chapter{Background of Quantum Computation and Group Actions}\label{chap:backgound}
 
@@
 \]
-where $\{\chi(h,.)\}$ are the characters (complex exponential homomorphisms) of $G$.
-When $G = \mathbb{Z}_N$ (the integers mod $N$), the QFT takes $|j\rangle$ to $\frac{1}{\sqrt{N}}\sum_{k=0}^{N-1} e^{2\pi i j k / N} |k\rangle$.
-
-Let $G \cong \mathbb{Z}_{N_1} \oplus \cdots \oplus \mathbb{Z}_{N_k}$ be a decomposition of $G$. The character $\chi(a, x)$ is then given by
-\[
-\chi(a, x) = \omega_{N_1}^{a_1x_1} \cdots \omega_{N_k}^{a_kx_k}, \quad \text{where } \omega_M = \exp(2\pi i/ M).
+where $\{\chi(h,.)\}$ are the characters (complex exponential homomorphisms) of $G$. When $G = \mathbb{Z}_N$ (the integers mod $N$), the QFT takes $|j\rangle$ to:
+\[
+\frac{1}{\sqrt{N}}\sum_{k=0}^{N-1} e^{2\pi i j k / N} |k\rangle
+\]
+
+Let $G \cong \mathbb{Z}_{N_1} \oplus \cdots \oplus \mathbb{Z}_{N_k}$ be a decomposition of $G$. The character $\chi(\bm{a}, x)$ is then given by
+\[
+\chi(\bm{a}, \bm{x}) = \omega_{N_1}^{a_1x_1} \cdots \omega_{N_k}^{a_kx_k}, \quad \text{where } \omega_M = \exp(2\pi i/ M).
 \]
@@
 
-\paragraph{The cmpIndex Algorithm.}
+\paragraph{The $\comph$ Algorithm.}
 Given a state $\ket{G^{(h)} * x}$, one can recover $h$ using phase kickback. Starting from $\ket{G^{(h)} * x} \ket{0}$, apply:
@@
 \[
-\operatorname{QHT}_N: \ket{a} \mapsto \frac{1}{\sqrt{N}} \sum_{y = 0}^{N - 1} \cas\left(\frac{2\pi a y}{N}\right) \ket{y}, \quad \text{where } \cas(x) = \cos(x) + \sin(x).
-\]
+\qht_N: \ket{a} \mapsto \frac{1}{\sqrt{N}} \sum_{y = 0}^{N - 1} \cas\left(\frac{2\pi a y}{N}\right) \ket{y}, \label{eq:qht_def}
+\]
+Where $\cas(x) = \cos(x) + \sin(x)$.
 
@@
 \begin{equation}
-    \operatorname{QHT}_G(f)({a}) = \frac{1}{\sqrt{|G|}} \sum_{{y} \in G} \cas(2\pi \langle {a}, \alpha({y}) \rangle) f({y}),
+    \qht(f)({\bm{a}}) = \frac{1}{\sqrt{|G|}} \sum_{{\bm{y}} \in G} \cas(2\pi \langle {\bm{a}}, \alpha({\bm{y}}) \rangle) f({\bm{y}}),
 \end{equation}
-where $\alpha({y}) = y_1 / N_1 + \cdots + y_k / N_k$.
+where $\alpha({\bm{y}}) = y_1 / N_1 + \cdots + y_k / N_k$.
 
@@
 \[
-\cas(2\pi \langle {a}, \alpha({y}) \rangle) = \frac{1 - i}{2}\chi({a}, {y}) + \frac{1 + i}{2}\chi(-{a}, {y}),
+\cas(2\pi \langle {\bm{a}}, \alpha({\bm{y}}) \rangle) = \frac{1 - i}{2}\chi({\bm{a}}, {\bm{y}}) + \frac{1 + i}{2}\chi(-{\bm{a}}, {\bm{y}}),
 \]
@@
 \begin{equation}
-\operatorname{QHT}_G = \frac{1 - i}{2} \operatorname{QFT}_G + \frac{1 + i}{2} \operatorname{QFT}_G^*, \label{eq:QHT_QFT}
+\qht_G = \frac{1 - i}{2} \qft_G + \frac{1 + i}{2} \qft_G^*, \label{eq:QHT_QFT}
 \end{equation}
-showing that $\operatorname{QHT}_G^2 = {1}$ and hence the QHT is unitary.
+showing that $\qht_G^2 = {1}$ and hence the $\qht$ is unitary.
 
@@
 \[
-\sum_{{x} \in G} f({x}) \ket{{x}} \mapsto \sum_{{a} \in G} \operatorname{QHT}_G(f)({a}) \ket{{a}}.
+\sum_{{x} \in G} f({x}) \ket{{x}} \mapsto \sum_{{\bm{a}} \in G} \qht_G(f)({\bm{a}}) \ket{{\bm{a}}}.
 \]
@@
 
-\chapter{Quantum Walks -- Continuous and Discrete}
+\chapter{Quantum Walks -- Continuous and Discrete}\label{chap:quantum_walks}
 
@@
 Instead of a probability distribution over vertices, a quantum walk evolves a superposition of vertex states.
-Interference between multiple paths leads to markedly different behavior from classical walks, often yielding faster spreading and algorithmic speedups~\cite{physics_stackexchange}.
-
-In particular, both major models of quantum walks --- continuous-time and discrete-time --- achieve \emph{ballistic spreading} (standard deviation growing linearly in time) in contrast to the diffusive $O(\sqrt{t})$ spread of classical random walks~\cite{childs2003quantum}.
-Quantum walks have become a central framework in quantum computing, underpinning various algorithms and even universal quantum computation~\cite{file_gwrqpr3gkui6gav6sze4dj}.
+Interference between multiple paths leads to markedly different behavior from classical walks, often yielding faster spreading and algorithmic speedups~\cite{Aharonov2001}.
+
+In particular, both major models of quantum walks --- continuous-time and discrete-time --- achieve \emph{ballistic spreading} (standard deviation growing linearly in time) in contrast to the diffusive $O(\sqrt{t})$ spread of classical random walks~\cite{Kempe2003}.
+Quantum walks have become a central framework in quantum computing, underpinning various algorithms and even universal quantum computation~\cite{Childs2009,Ambainis2003}.
 
@@
 Continuous-time quantum walks have been employed to achieve algorithmic speedups.
-A famous example is the \emph{glued trees traversal problem} by Childs et al.
-(2003), where a CTQW on a graph formed by two randomly "glued" binary trees can find the unique exit vertex exponentially faster than any classical algorithm.
+A famous example is the \emph{glued trees traversal problem} by Childs \cite{Childs2003}, where a CTQW on a graph formed by two randomly "glued" binary trees can find the unique exit vertex exponentially faster than any classical algorithm.
 This result gave the first exponential separation between quantum and classical query complexity in a black-box setting.
@@
 Another application is \emph{spatial search} on graphs.
-Childs and Goldstone (2004) showed that a CTQW can find a marked vertex on a $d$-dimensional lattice faster than classical diffusion.
+Childs and Goldstone \cite{ChildsGoldstone2004} showed that a CTQW can find a marked vertex on a $d$-dimensional lattice faster than classical diffusion.
 In the limit $d \to \infty$, the CTQW dynamics converge to the continuous Dirac equation.
@@
 
-In 2004, Szegedy proposed a different formulation of DTQW based on classical Markov chains.
+In 2004, Szegedy \cite{Szegedy2004} proposed a different formulation of DTQW based on classical Markov chains.
 Here, no coin register is needed.
@@
 In many cases, the two models can simulate each other.
-DTQWs can even achieve \textbf{universal quantum computation}: Childs et al.
-(2009) constructed a coined DTQW that simulates an arbitrary quantum circuit.
+DTQWs can even achieve \textbf{universal quantum computation}: Childs\cite{Childs2009} constructed a coined DTQW that simulates an arbitrary quantum circuit.
 
@@
 Each vertex corresponds to a word in $\{a^{\pm1}, b^{\pm1}\}$, and edges represent multiplication by $a$ or $b$.
-A finite portion of this graph is shown in Figure~\ref{fig:cayley-free-group}.
 
@@
 To see this, we have
-\[
-        A\ket{\hat{a}} = A.\frac{1}{\sqrt{|G|}}\sum_{y \in G}\chi(a,y)\ket{y} = \frac{1}{\sqrt{|G|}}\sum_{y \in G}\chi(a,y).A\ket{y}
-        \]
-        \[
-        = \frac{1}{\sqrt{|G|}}\sum_{y \in G}\chi(a,y).\sum_{q \in Q}\ket{qy}
-        \]
-        Consider $\beta = qy$. Then:
-        \[
-         = \frac{1}{\sqrt{|G|}}\sum_{q \in Q}\chi(a,q)\sum_{\beta}\chi(a,\beta)\ket{\beta} = \sum_{q \in Q}\chi(a,q) . \ket{\hat{a}}
-        \]
-        \[
-         = \lambda_a\ket{\hat{a}}
-        \]
+
+        \begin{align}
+            A\ket{\hat{a}} 
+            &= A\frac{1}{\sqrt{|G|}}\sum_{y \in G}\chi(a,y)\ket{y} \nonumber \\
+            &= \frac{1}{\sqrt{|G|}}\sum_{y \in G}\chi(a,y)A\ket{y} \nonumber \\
+            &= \frac{1}{\sqrt{|G|}}\sum_{y \in G}\chi(a,y)\sum_{q \in Q}\ket{qy} \nonumber
+            \end{align}
+
+            \noindent Consider $\beta = qy$. Then the above equation becomes:
+
+            \begin{align}
+            \frac{1}{\sqrt{|G|}}\sum_{q \in Q} \sum_{y \in G} \chi(a,y)\ket{qy} 
+            &= \frac{1}{\sqrt{|G|}}\sum_{q \in Q} \chi(a,q) \sum_{\beta \in G} \chi(a,\beta)\ket{\beta} \nonumber \\
+            &= \sum_{q \in Q} \chi(a,q)\ket{\hat{a}} \nonumber \\
+            &= \lambda_a\ket{\hat{a}} \label{eq:group_action_walk}
+            \end{align}
 
@@
 \]
-the resulting state remains a \emph{class function}, i.e., the amplitude $\braket{g|\psi(t)}$ depends only on structural properties of $g$ (such as Hamming weight or conjugacy class).
+the resulting state remains a \emph{class function}, i.e., the amplitude $\braket{g}{\psi(t)}$ depends only on structural properties of $g$ (such as Hamming weight or conjugacy class).
 
@@
 
-\[
-    A\ket{G^{(h)}*x} = \frac{1}{\sqrt{|G|}}.\sum_{g \in G}\chi(g,h) A.\ket{g*x}
-    \]
-
-    \[
-    = A\ket{G^{(h)}*x} = \frac{1}{\sqrt{|G|}}.\sum_{g \in G}\chi(g,h)\sum_{q \in Q}\ket{q*(g*x)}
-    \]
-    Consider $\beta = qg$. Then:
-    \[
-    = = \frac{1}{\sqrt{|G|}}\sum_{q \in Q}\sum_{\beta \in G}\chi(\beta,h)\chi(q,h)\ket{\beta * x}
-    \]
-
-    \[
-    = \sum_{q \in Q}\chi(q,h).\ket{G^{(h)}*x} = \lambda_h \ket{G^{(h)}*x}
-    \]
+\begin{align}
+    A\ket{G^{(h)} * x} 
+    &= \frac{1}{\sqrt{|G|}}\sum_{g \in G} \chi(g, h)\, A\ket{g * x} \nonumber \\
+    &= \frac{1}{\sqrt{|G|}}\sum_{g \in G} \chi(g, h)\sum_{q \in Q} \ket{q * (g * x)} \nonumber
+    \end{align}
+
+    \noindent Consider $\beta = qg$. Then the above equation becomes:
+
+    \begin{align}
+    \frac{1}{\sqrt{|G|}}\sum_{q \in Q} \sum_{\beta \in G} \chi(\beta, h)\chi(q, h)\ket{\beta * x}
+    &= \sum_{q \in Q} \chi(q, h)\ket{G^{(h)} * x} \nonumber \\
+    &= \lambda_h \ket{G^{(h)} * x} \label{eq:group_action_symmetrized}
+    \end{align}
 
@@
 
-\chapter{Simulating Group Action Quantum Walks}
+\chapter{Simulating Group Action Quantum Walks}\label{chap:simulating}
 
@@
     \label{eq:adjmat-fb}
-    e^{-iAt} = \operatorname{QFT}_G \left( \sum_{a \in G} e^{-i\lambda_a t} \ket{a} \bra{a} \right) \operatorname{QFT}_G^*,
+    e^{-iAt} = \qft_G \left( \sum_{a \in G} e^{-i\lambda_a t} \ket{a} \bra{a} \right) \qft_G^*,
 \end{equation}
-where both \( \operatorname{QFT}_G \) and its inverse can be implemented in \( \operatorname{poly}(\log \abs{G}) \) time.
+where both \( \qft_G \) and its inverse can be implemented in \( \operatorname{poly}(\log \abs{G}) \) time.
 Moreover, the diagonal unitary \( \ket{a} \mapsto e^{-i\lambda_a t} \ket{a} \) is efficiently realizable since the eigenvalues \( \lambda_a \) can be computed classically to arbitrary precision in polynomial time with respect to \( \log \abs{G} \).
@@
 
-Based on these states, we define the isometry \( T : \mathbb{C}^{2N} \to \mathbb{C}^{2N} \otimes \mathbb{C}^{2N} \) as follows:
+Based on these states, we define the isometry \( T : \C^{2N} \to \mathbb{C}^{2N} \otimes \mathbb{C}^{2N} \) as follows:
 \begin{equation}
@@
 \[
-W = iS(2TT^* - \mathbf{1}),
+W = iS(2TT^* - \mathds{1}),
 \]
@@
 \[
-W = iS(2TT^* - \mathbf{1})
+W = iS(2TT^* - \mathds{1})
 \]
@@
 \]
-Applying \( V_Q \otimes \mathbf{1} \) to the state \( \ket{0} \ket{y, 0} \ket{0, 0} \) produces:
+Applying \( V_Q \otimes \mathds{1} \) to the state \( \ket{0} \ket{y, 0} \ket{0, 0} \) produces:
 \[
@@
 
-To implement \( U_0^* : \ket{0} \ket{y, 0} \ket{\phi_{y0}} \mapsto \ket{0} \ket{y, 0} \ket{0, 0} \), we sequentially apply \( V_2^* \), followed by \( V_1^* \), and finally \( V_Q^* \otimes \mathbf{1} \).
+To implement \( U_0^* : \ket{0} \ket{y, 0} \ket{\phi_{y0}} \mapsto \ket{0} \ket{y, 0} \ket{0, 0} \), we sequentially apply \( V_2^* \), followed by \( V_1^* \), and finally \( V_Q^* \otimes \mathds{1} \).
 Since each of these unitaries can be implemented efficiently, it follows that \( U_0^* \) is also efficient.
@@
 \[
-W = iS(2TT^* - \mathbf{1})
-\]
-can be applied efficiently. This reduces to implementing the reflection \( 2TT^* - \mathbf{1} \), which we analyze as follows:
+W = iS(2TT^* - \mathds{1})
+\]
+can be applied efficiently. This reduces to implementing the reflection \( 2TT^* - \mathds{1} \), which we analyze as follows:
 \begin{align*}
-2\ket{0}\bra{0} \otimes TT^* - \mathbf{1}
-&= 2\ket{0}\bra{0} \otimes \sum_{y \in X} \sum_{b \in \{0,1\}} \ket{y,b} \ket{\phi_{yb}} \bra{y,b} \bra{\phi_{yb}} - \mathbf{1} \\
-&= 2\sum_{y \in X} \sum_{b \in \{0,1\}} \ket{0} \ket{y,b} \ket{\phi_{yb}} \bra{0} \bra{y,b} \bra{\phi_{yb}} - \mathbf{1} \\
-&= U_T \left( 2 \sum_{y \in X} \sum_{b \in \{0,1\}} \ket{0} \ket{y,b} \ket{0,0} \bra{0} \bra{y,b} \bra{0,0} - \mathbf{1} \right) U_T^* \\
-&= U_T \left( 2\ket{0}\bra{0} \otimes \mathbf{1}_{X,b} \otimes \ket{0,0}\bra{0,0} - \mathbf{1} \right) U_T^*.
+2\ket{0}\bra{0} \otimes TT^* - \mathds{1}
+&= 2\ket{0}\bra{0} \otimes \sum_{y \in X} \sum_{b \in \{0,1\}} \ket{y,b} \ket{\phi_{yb}} \bra{y,b} \bra{\phi_{yb}} - \mathds{1} \\
+&= 2\sum_{y \in X} \sum_{b \in \{0,1\}} \ket{0} \ket{y,b} \ket{\phi_{yb}} \bra{0} \bra{y,b} \bra{\phi_{yb}} - \mathds{1} \\
+&= U_T \left( 2 \sum_{y \in X} \sum_{b \in \{0,1\}} \ket{0} \ket{y,b} \ket{0,0} \bra{0} \bra{y,b} \bra{0,0} - \mathds{1} \right) U_T^* \\
+&= U_T \left( 2\ket{0}\bra{0} \otimes \mathds{1}_{X,b} \otimes \ket{0,0}\bra{0,0} - \mathds{1} \right) U_T^*.
 \end{align*}
 
-Since \( U_T \), \( U_T^* \), and the operator \( 2\ket{0}\bra{0} \otimes \mathbf{1}_{X,b} \otimes \ket{0,0}\bra{0,0} - \mathbf{1} \) can all be implemented efficiently, it follows that the reflection \( 2\ket{0}\bra{0} \otimes TT^* - \mathbf{1} \) is also efficient.
+Since \( U_T \), \( U_T^* \), and the operator \( 2\ket{0}\bra{0} \otimes \mathds{1}_{X,b} \otimes \ket{0,0}\bra{0,0} - \mathds{1} \) can all be implemented efficiently, it follows that the reflection \( 2\ket{0}\bra{0} \otimes TT^* - \mathds{1} \) is also efficient.
 
@@
 \[
-\left(2\ket{0}\bra{0} \otimes TT^* - \mathbf{1} \right) \ket{0} \ket{\psi} = \ket{0} \left(2TT^* - \mathbf{1} \right) \ket{\psi},
+\left(2\ket{0}\bra{0} \otimes TT^* - \mathds{1} \right) \ket{0} \ket{\psi} = \ket{0} \left(2TT^* - \mathds{1} \right) \ket{\psi},
 \]
@@
 
-\chapter{Quantum Money and Hartley Transform}
+\chapter{Quantum Money and Hartley Transform}\label{chap:quantum_money}
 
@@
 \section{Fourier-Based Quantum Money from Group Actions}
-Zhandry’s quantum money scheme [31] is built on an abelian group action $G \curvearrowright X$.
+Zhandry’s quantum money scheme \cite{Zhandry2024} is built on an abelian group action $G \curvearrowright X$.
 We have a family of group actions parameterized by the security parameter $n$ (so the size of $G$ grows with $n$).
@@
     \[
-       \mathrm{QHT}: |g\rangle \mapsto \frac{1}{\sqrt{N}} \sum_{k \in G} \cas \!\Big(\frac{2\pi \langle k,g \rangle}{N}\Big) |k\rangle,
+       \mathrm{QHT}: |g\rangle \mapsto \frac{1}{\sqrt{N}} \sum_{k \in G} \cas \Big(\frac{2\pi \langle k,g \rangle}{N}\Big) |k\rangle,
     \] 
@@
     \[
-       \frac{1}{\sqrt{N}} \sum_{g \in G} \cas\!\Big(\frac{2\pi \langle h,g \rangle}{N}\Big)\, |g\rangle \otimes |g*x_0\rangle.
+       \frac{1}{\sqrt{N}} \sum_{g \in G} \cas\Big(\frac{2\pi \langle h,g \rangle}{N}\Big)\, |g\rangle \otimes |g*x_0\rangle.
     \] 
@@
     \[
-      |\$\rangle = \frac{1}{\sqrt{N}} \sum_{x \in X} \Big(\frac{1}{\sqrt{N}}\sum_{g: g*x_0 = x} \cas\!\big(\frac{2\pi \langle h,g \rangle}{N}\big)\Big)\, |x\rangle.
+      |\$\rangle = \frac{1}{\sqrt{N}} \sum_{x \in X} \Big(\frac{1}{\sqrt{N}}\sum_{g: g*x_0 = x} \cas\big(\frac{2\pi \langle h,g \rangle}{N}\big)\Big)\, |x\rangle.
     \] 
@@
     \item From the estimated eigenvalue(s), we reconstruct a candidate group element $h^*$ that we believe generated the state.
-(This uses the fact that by running phase estimation for multiple carefully chosen walk durations, one can solve for $h$ as shown in [31].)
+(This uses the fact that by running phase estimation for multiple carefully chosen walk durations, one can solve for $h$ as shown in \cite{Zhandry2022}.)
     \item We check if $h^* = h$ (the serial number provided). If not, we reject, since the state does not match the serial. If yes, we accept.
@@
 Classical Hartley transforms have a recursive structure similar to fast Fourier transforms.
-In fact, there are known formulas to express a Hartley transform of size $N$ in terms of two Hartley transforms of size $N/2$ plus some additional linear operations [25].
+In fact, there are known formulas to express a Hartley transform of size $N$ in terms of two Hartley transforms of size $N/2$ plus some additional linear operations \cite{Bracewell1984}.
 We leveraged such structures to design a divide-and-conquer quantum circuit.
@@
 The base of the recursion is when the size is small (like $N=2$ or $4$, where the transform can be done with a constant number of gates).
-- We found that by carefully optimizing this recursion and using some known quantum subroutines for certain linear combinations, the overall gate count is improved compared to naive methods or previous proposals [21, 22].
-In particular, our circuit avoids introducing any quantum Fourier transform internally (unlike [22] which computed Hartley via Fourier plus some adjustments), and this yields a purely real rotation-based circuit.
+- We found that by carefully optimizing this recursion and using some known quantum subroutines for certain linear combinations, the overall gate count is improved compared to naive methods or previous proposals \cite{Klappenecker2001DCT,Klappenecker2001Signal}.
+In particular, our circuit avoids introducing any quantum Fourier transform internally (unlike \cite{Klappenecker2001Signal} which computed Hartley via Fourier plus some adjustments), and this yields a purely real rotation-based circuit.
 
@@
 
-\begin{align*}
+\begin{align}
     \qft_N\ket{a}
@@
     & = \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \omega_N^{ay} \ket{y} + (-1)^a \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \omega_N^{ay} \ket{y + N/2} \\
-    & = \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \omega_N^{ay} \frac{1}{\sqrt{2}} (\ket{0} + (-1)^a \ket{1}) \ket{y}, %\numberthis\label{eq:qft_alt}
-\end{align*}
+    & = \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \omega_N^{ay} \frac{1}{\sqrt{2}} (\ket{0} + (-1)^a \ket{1}) \ket{y}, \label{eq:qft_alt}
+\end{align}
 
@@
 The key idea is to leverage the recursive structure of \( \qht_N \), analogous to the strategy used for \( \qft_N \).
-To facilitate this, we begin by rewriting the summation in Equation~\eqref{eq:qht-N} to expose its recursive form.
+To facilitate this, we begin by rewriting the summation in Equation~\eqref{eq:qht_def} to expose its recursive form.
 Our approach is as follows:
@@
 	\ket{0}\ket{t}\ket{b}
-    & \mapsto \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi t y}{N / 2} \Big) \ket{0} \ket{y} \ket{b} & (\mathbf{1} \otimes \qht_{N / 2} \otimes \mathbf{1}) \\
+    & \mapsto \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi t y}{N / 2} \Big) \ket{0} \ket{y} \ket{b} & (\mathds{1} \otimes \qht_{N / 2} \otimes \mathds{1}) \\
     & = \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{4\pi t y}{N} \Big) \ket{0} \ket{y} \ket{b} \\
-    & \mapsto \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{4\pi t y}{N} \Big) (\ket{0} + \ket{1}) \ket{y}\ket{b}. & (H \otimes \mathbf{1})
+    & \mapsto \frac{1}{\sqrt{N}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{4\pi t y}{N} \Big) (\ket{0} + \ket{1}) \ket{y}\ket{b}. & (H \otimes \mathds{1})
 \end{align*}
@@
     & \mapsto \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi ay}{N} \Big) \ket{0} \ket{y} \ket{b} & (\textsc{cnot}) \\
-    & \mapsto \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi ay}{N} \Big) \ket{0} \ket{y} \frac{1}{\sqrt{2}}(\ket{0} + (-1)^b \ket{1}) & (\mathbf{1} \otimes H) \\
+    & \mapsto \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi ay}{N} \Big) \ket{0} \ket{y} \frac{1}{\sqrt{2}}(\ket{0} + (-1)^b \ket{1}) & (\mathds{1} \otimes H) \\
     & = \frac{1}{\sqrt{N / 2}} \sum_{y = 0}^{N / 2 - 1} \cas\Big( \frac{2\pi ay}{N} \Big) \ket{0} \ket{y} \frac{1}{\sqrt{2}}(\ket{0} + (-1)^a \ket{1}). & ((-1)^b = (-1)^a) \\
@@
 % \begin{algorithm}[$\qht_N$] \
-\paragraph{algorithm $\qht_N$}
+\paragraph{Algorithm $\qht_N$}
     % \label{alg:qht-N}
@@
     \item Initialize an ancilla qubit to $0$ to obtain the state $\ket{0}\ket{\psi}$
-    \item Compute $\mathbf{1} \otimes \qht_{N / 2} \otimes \mathbf{1}$ recursively.
-    \item Apply $H \otimes \mathbf{1}$.
+    \item Compute $\mathds{1} \otimes \qht_{N / 2} \otimes \mathds{1}$ recursively.
+    \item Apply $H \otimes \mathds{1}$.
     \item\label{stp:ngt} Apply the controlled negation $\ket{0}\ket{y} \mapsto \ket{0}\ket{y}, \ket{1}\ket{y} \mapsto \ket{1}\ket{N / 2 -y}$ to the first two registers.
     \item Apply the unitary $U_R$.
-    \item Apply $H \otimes \mathbf{1}$
+    \item Apply $H \otimes \mathds{1}$
     \item Apply \textsc{cnot} to the first and last qubits.
-    \item Apply $\mathbf{1} \otimes H$.
+    \item Apply $\mathds{1} \otimes H$.
     \item Trace out the first qubit
@@
 % \begin{proof}
-\paragraph{proof.}
+\paragraph{Proof.}
     The correctness of the algorithm follows from the preceding discussion.
@@
     \[
-    R_j = \ket{0}\bra{0} \otimes \mathbf{1} + \ket{1}\bra{1} \otimes
+    R_j = \ket{0}\bra{0} \otimes \mathds{1} + \ket{1}\bra{1} \otimes
     \begin{bmatrix}
@@
     for \( j = 0, 1, \dots, n - 1 \).
-When \( b = 0 \), we have \( R(y, 0) = \mathbf{1} \), and when \( b = 1 \), the operator \( R(y, 1) \) is the product of those \( R_j \) for which the \( j \)th bit of \( y \) is 1.
+When \( b = 0 \), we have \( R(y, 0) = \mathds{1} \), and when \( b = 1 \), the operator \( R(y, 1) \) is the product of those \( R_j \) for which the \( j \)th bit of \( y \) is 1.
 Therefore, for a binary string \( y \) of length \( k = \lceil \log y \rceil \), we can implement \( U_R \) using at most \( k \) gates from the set \( \{R_j\} \).
@@
 
-\chapter{Verification Algorithm Using Quantum Walks}
+\chapter{Verification Algorithm Using Quantum Walks}\label{chap:verification}
 
 The Hartley-based quantum money scheme introduced in the previous chapter requires a new verification procedure to address the issues that arise from using real amplitude states.
-In this chapter, we describe and analyze the verification algorithm, which leverages continuous-time quantum walks on the group action graph (and their efficient simulation from Chapter 4) to extract the information needed to authenticate a banknote.
+In this chapter, we describe and analyze the verification algorithm, which leverages continuous-time quantum walks on the group action graph (and their efficient simulation from Chapter~\ref{chap:simulating}) to extract the information needed to authenticate a banknote.
 
@@
     % \begin{lemma}
-    \paragraph{lemma.}
+    \paragraph{Lemma.}
         \label{lem:h-eigen}
@@
     % \begin{proof}
-    \paragraph{proof.}
+    \paragraph{Proof.}
         We have 
@@
 \bibliographystyle{plain}
-\begin{thebibliography}{99}
-
-    \bibitem{Wiesner1983}
-    S. Wiesner, ``Conjugate Observables and the Foundations of Cryptography,'' \textit{Sigact News}, vol. 15, no. 1, pp. 78–88, 1983.
-
-    \bibitem{Aaronson2009}
-    S. Aaronson, ``Quantum Copy-Protection and Quantum Money,'' In \textit{Proceedings of the IEEE Conference on Computational Complexity (CCC)}, 2009.
-
-    \bibitem{Lutomirski2010}
-    A.
-Lutomirski, S.
-Aaronson, E.
-Farhi, D.
-Gosset, J.
-Keselman, P.
-Shor, A.
-Slofstra, and A.
-Speyer, ``Breaking and Making Quantum Money: Toward a New Quantum Cryptographic Protocol,'' arXiv:1004.4843, 2010.
-
-    \bibitem{Zhandry2022}
-    M. Zhandry, ``Quantum Money from Modular Forms,'' In \textit{Proceedings of CRYPTO}, 2022.
-
-    \bibitem{Doliskani2023}
-    J. Doliskani, ``On the Security of Group Action-Based Quantum Money,'' unpublished manuscript, 2023.
-
-    \bibitem{Childs2004}
-    A. M. Childs, ``Quantum Information Processing in Continuous Time,'' Ph.D. thesis, Massachusetts Institute of Technology, 2004.
-
-    \bibitem{BerryKothari}
-    D. Berry and R. Kothari, ``Hamiltonian Simulation with Optimal Sample Complexity,'' In \textit{Proceedings of FOCS}, 2018.
-
-    \bibitem{Zhandry2024}
-    M.
-Zhandry, ``Quantum Money from Abelian Group Actions,'' In \textit{Proceedings of the 15th Innovations in Theoretical Computer Science Conference (ITCS)}, Schloss Dagstuhl–Leibniz Center for Informatics, 2024.
-
-    \bibitem{childs2010relationship}
-    A. M. Childs, ``On the Relationship Between Continuous- and Discrete-Time Quantum Walk,'' \textit{Communications in Mathematical Physics}, vol. 294, pp. 581–603, 2010.
-
-\end{thebibliography}
+\bibliography{references}
 

### 2025-04-12 draft.tex
chapter 2 updated

@@
 
-Quantum computation operates on information stored in quantum states.
-The fundamental unit of quantum information is the \emph{qubit}, which, unlike a classical bit, can exist in a superposition of basis states.
-A qubit is described by a state $|\psi\rangle = \alpha |0\rangle + \beta |1\rangle$ (in Dirac notation), where $\alpha,\beta \in \mathbb{C}$ and $|\alpha|^2 + |\beta|^2 = 1$.
-A system of $n$ qubits resides in a $2^n$-dimensional Hilbert space and its state can be a superposition of all $2^n$ basis states $|b_1b_2\cdots b_n\rangle$.
-
-Computation is carried out by unitary transformations on these states.
-A quantum algorithm is typically a sequence of quantum gates (unitary operators) applied to an initial state (usually a simple basis state like $|00\cdots0\rangle$), followed by a measurement of some qubits to obtain a classical result.
-A crucial aspect of quantum computation is that certain transformations—such as the Fourier transform over an $N$-element group—can be implemented very efficiently on a quantum computer (in $\operatorname{poly}(\log N)$ time), whereas their classical counterparts might require $\operatorname{poly}(N)$ time.
-
-\subsection{The Quantum Fourier Transform}
-
-One example important to this work is the \textbf{quantum Fourier transform} (QFT). For an abelian group $G$ of order $N$, the QFT is the unitary map
-\[
-|g\rangle \mapsto \frac{1}{\sqrt{N}}\sum_{h \in G} \chi(h,g)\, |h\rangle,
-\]
-where $\{\chi(h,.)\}$ are the characters (complex exponential homomorphisms) of $G$. When $G = \mathbb{Z}_N$ (the integers mod $N$), the QFT takes $|j\rangle$ to:
-\[
-\frac{1}{\sqrt{N}}\sum_{k=0}^{N-1} e^{2\pi i j k / N} |k\rangle
-\]
-
-Let $G \cong \mathbb{Z}_{N_1} \oplus \cdots \oplus \mathbb{Z}_{N_k}$ be a decomposition of $G$. The character $\chi(\bm{a}, x)$ is then given by
-\[
-\chi(\bm{a}, \bm{x}) = \omega_{N_1}^{a_1x_1} \cdots \omega_{N_k}^{a_kx_k}, \quad \text{where } \omega_M = \exp(2\pi i/ M).
-\]
-
-The Fourier transform of a function $f: G \to \mathbb{C}$ is given by
-\[
-\hat{f}(a) = \frac{1}{\sqrt{|G|}} \sum_{x \in G} \chi(a, x) f(x),
-\]
-and the QFT of a quantum state $\sum_{g \in G} f(g) \ket{g}$ is $\sum_{x \in G} \hat{f}(x) \ket{x}$.
-
-\paragraph{Fourier Basis and Group Actions.} For a regular group action $(G, X, *)$, define
-\[
-\ket{S^{(h)} * y} = \frac{1}{\sqrt{|S|}} \sum_{g \in S} \chi(g, h) \ket{g * y}.
-\]
-For fixed $x \in X$, we obtain two orthonormal bases of $\mathbb{C}^X$: the standard basis $\{ \ket{x} : x \in X \}$, and the Fourier basis
-\[
-\ket{G^{(h)} * x} = \frac{1}{\sqrt{|G|}} \sum_{g \in G} \chi(g, h) \ket{g * x}.
-\]
-These states are eigenstates of the action unitary $U_k: \ket{y} \mapsto \ket{k * y}$:
-\[
-U_k \ket{G^{(h)} * x} = \chi(-k, h) \ket{G^{(h)} * x}.
-\]
-
-\paragraph{The $\comph$ Algorithm.}
-Given a state $\ket{G^{(h)} * x}$, one can recover $h$ using phase kickback. Starting from $\ket{G^{(h)} * x} \ket{0}$, apply:
+Quantum computation is a model of information processing rooted in the principles of quantum mechanics.
+Unlike classical systems, which encode and manipulate information using deterministic bits, quantum systems store information in quantum states—vectors in complex Hilbert spaces—that can exhibit phenomena with no classical analogue.
+The most notable of these are \emph{superposition}, which allows quantum systems to be in multiple configurations simultaneously, and \emph{entanglement}, which enables correlations between parts of a system that cannot be explained classically.
+These characteristics endow quantum computers with computational abilities that can outperform classical counterparts in certain tasks.
+
+To rigorously define the framework of quantum computation, we begin with some basic notation.
+Let $\mathcal{H}$ be a finite-dimensional Hilbert space over the complex numbers.
+This space is equipped with an inner product and an orthonormal basis $\{\ket{s} : s \in S\}$, where $S$ is a finite index set that corresponds to the classical configurations of the system.
+Each element $\ket{s} \in \mathcal{H}$ represents a quantum basis state, analogous to a classical state.
+A general quantum state $\ket{\alpha} \in \mathcal{H}$ is a unit vector, and can be expressed as a linear combination of the basis vectors:
+\[
+\ket{\alpha} = \sum_{s \in S} a_s \ket{s}, \qquad \text{where } a_s \in \mathbb{C}, \quad \sum_{s \in S} |a_s|^2 = 1.
+\]
+Here, the complex numbers $a_s$ are called \emph{amplitudes}, and the squared magnitudes $|a_s|^2$ correspond to the probabilities of observing the state $\ket{s}$ upon measurement.
+The inner product between two states $\ket{\alpha}$ and $\ket{\beta}$ is denoted by $\bra{\beta}\alpha\rangle$, where $\bra{\alpha}$ is the conjugate transpose (or Hermitian adjoint) of the $\ket{\alpha}$.
+
+The most elementary quantum system is the \emph{qubit}, or quantum bit, which corresponds to a unit vector in the two-dimensional Hilbert space $\mathbb{C}^2$.
+In the computational basis $\{\ket{0}, \ket{1}\}$, any pure state of a qubit can be written as
+\[
+\ket{\psi} = \alpha \ket{0} + \beta \ket{1}, \qquad \text{where } \alpha, \beta \in \mathbb{C}, \quad |\alpha|^2 + |\beta|^2 = 1.
+\]
+Unlike a classical bit, which must be either 0 or 1, a qubit can exist in a superposition of both states simultaneously.
+The ability to process such coherent superpositions is one of the key features that distinguishes quantum computation from classical models.
+
+When considering multiple qubits, the joint state of the system resides in the \emph{tensor product} of the individual Hilbert spaces. For example, a system of $n$ qubits is described by the space
+\[
+\mathcal{H} = \left( \mathbb{C}^2 \right)^{\otimes n} \cong \mathbb{C}^{2^n}.
+\]
+The standard basis for this space consists of all computational basis states $\ket{x}$ where $x \in \{0,1\}^n$ is a bit string of length $n$. A general pure state of $n$ qubits is then written as
+\[
+\ket{\Psi} = \sum_{x \in \{0,1\}^n} \alpha_x \ket{x}, \qquad \sum_{x} |\alpha_x|^2 = 1.
+\]
+Because of the exponential growth in the dimension of the Hilbert space with the number of qubits, quantum systems can store and process information in ways that are exponentially more efficient (in terms of representation) than classical systems.
+Additionally, this tensor product structure enables the existence of \emph{entangled states}—those which cannot be factored into product states of individual qubits.
+Entanglement plays a crucial role in quantum algorithms, communication, and cryptography.
+
+The formal behavior of quantum systems is governed by a small set of postulates that form the mathematical foundation of quantum mechanics.
+These postulates determine how quantum systems are represented, how they evolve, and how observations are made.
+
+\begin{enumerate}
+  \item \textbf{State Space.} Every isolated physical system is associated with a Hilbert space $\mathcal{H}$, and its state is described by a unit vector $\ket{\psi} \in \mathcal{H}$.
+For composite systems composed of subsystems $A$ and $B$, the state space is the tensor product $\mathcal{H}_A \otimes \mathcal{H}_B$.
+If $\{\ket{a_i}\}$ and $\{\ket{b_j}\}$ are orthonormal bases for $\mathcal{H}_A$ and $\mathcal{H}_B$, then $\{\ket{a_i} \otimes \ket{b_j}\}$ forms an orthonormal basis for the joint system.
+
+  \item \textbf{Unitary Evolution.} The evolution of a closed quantum system is described by a unitary transformation.
+If the system is in state $\ket{\psi}$ at some initial time, then at a later time it evolves to $\ket{\psi'} = U \ket{\psi}$, where $U$ is a unitary operator satisfying $U^\dagger U = U U^\dagger = I$.
+This ensures that the norm of the state vector—and hence the total probability—is preserved under evolution.
+
+  \item \textbf{Measurement.} Measurement is a probabilistic process governed by an orthonormal basis $\{\ket{s}\}_{s \in S}$ of $\mathcal{H}$.
+When a measurement is performed on a state $\ket{\alpha} = \sum_{s \in S} a_s \ket{s}$, the outcome is some $s \in S$ with probability $|a_s|^2$, and the system collapses to the corresponding basis state $\ket{s}$.
+This probabilistic rule is known as the Born rule.
+Measurement is not reversible: it fundamentally alters the state and discards phase and superposition information not aligned with the measured basis.
+
+  \item \textbf{Composition of Systems.} If two quantum systems $A$ and $B$ are described by Hilbert spaces $\mathcal{H}_A$ and $\mathcal{H}_B$, respectively, then the combined system is described by the tensor product $\mathcal{H}_A \otimes \mathcal{H}_B$.
+A product state of the form $\ket{\psi_A} \otimes \ket{\psi_B}$ represents a system where $A$ and $B$ are uncorrelated.
+In general, however, the state may be entangled, and cannot be written as a product of subsystems.
+\end{enumerate}
+
+Together, these postulates define the operational behavior of quantum systems and underpin the structure of quantum computation.
+The state space formalism allows for the representation of complex probabilistic and entangled phenomena, while unitary evolution enables coherent manipulation of information.
+Measurement introduces irreversibility and classical output, allowing for the extraction of computational results from quantum processes.
+Finally, the tensor product composition rule enables scalable modeling of multipartite systems and is the mathematical basis for the power of quantum algorithms.
+
+\section{Classical vs Quantum Computation}
+
+In classical computation, circuits are composed of wires and logic gates, such as AND, OR, and NOT, that act on bits—elements of $\{0,1\}$.
+These logic gates are inherently irreversible: for example, given the output of an OR gate, one cannot deduce the exact inputs.
+In contrast, quantum computation operates under the strict constraint that all operations must be unitary, and therefore \emph{reversible}.
+
+Quantum computers are built from quantum circuits, which consist of wires (representing qubits) and quantum gates (unitary operations).
+Qubits may exist in superpositions of basis states and, when acted upon by quantum gates, evolve linearly in accordance with the postulates of quantum mechanics.
+
+Unlike classical gates that map fixed bitstrings to other bitstrings, quantum gates are linear operators acting on vectors in complex Hilbert space.
+For a single qubit, this means that gates must preserve the inner product and norm of quantum states.
+Hence, quantum gates must be represented by unitary matrices $U$ such that $U^\dagger U = I$.
+
+\subsection{Elementary Quantum Gates}
+
+Many single-qubit quantum gates have no classical counterparts. A few key examples include:
+
 \begin{itemize}
-    \item QFT to second register,
-    \item Controlled unitary $\sum_{k \in G} U_k \otimes \ket{k}\bra{k}$,
-    \item Inverse QFT to second register.
+  \item \textbf{Pauli-X (NOT) Gate:} Acts as the quantum analog of the classical NOT gate.
+  \[
+  X = \begin{bmatrix} 0 & 1 \\ 1 & 0 \end{bmatrix}, \quad X \ket{0} = \ket{1}, \quad X \ket{1} = \ket{0}
+  \]
+
+  \item \textbf{Pauli-Y Gate:} Introduces a $\pi$-rotation around the $y$-axis of the Bloch sphere.
+  \[
+  Y = \begin{bmatrix} 0 & -i \\ i & 0 \end{bmatrix}
+  \]
+
+  \item \textbf{Pauli-Z Gate:} Flips the sign of the $\ket{1}$ component.
+  \[
+  Z = \begin{bmatrix} 1 & 0 \\ 0 & -1 \end{bmatrix}
+  \]
+
+  \item \textbf{Hadamard Gate (H):} Places a qubit into an equal superposition of $\ket{0}$ and $\ket{1}$.
+  \[
+  H = \frac{1}{\sqrt{2}} \begin{bmatrix} 1 & 1 \\ 1 & -1 \end{bmatrix}
+  \]
+  This gate transforms:
+  \[
+  \ket{0} \mapsto \frac{\ket{0} + \ket{1}}{\sqrt{2}}, \quad \ket{1} \mapsto \frac{\ket{0} - \ket{1}}{\sqrt{2}}
+  \]
+
+  \item \textbf{Phase Gate (S):} Applies a $\frac{\pi}{2}$ phase to $\ket{1}$:
+  \[
+  S = \begin{bmatrix} 1 & 0 \\ 0 & i \end{bmatrix}
+  \]
+
+  \item \textbf{$\pi/8$ Gate (T):} Applies a phase of $\pi/4$:
+  \[
+  T = \begin{bmatrix} 1 & 0 \\ 0 & e^{i\pi/4} \end{bmatrix}
+  \]
+  It is the square root of the Phase gate and thus the fourth root of $Z$.
 \end{itemize}
-This yields $\ket{G^{(h)} * x} \ket{h}$, extracting $h$ efficiently.
-
-\subsection{The Quantum Hartley Transform}
-
-Another concept we use is the \textbf{quantum Hartley transform} (QHT), which replaces complex exponentials with real sinusoidal kernels.
-
-\paragraph{Definition.}
-For $G = \mathbb{Z}_N$, define
-\[
-\qht_N: \ket{a} \mapsto \frac{1}{\sqrt{N}} \sum_{y = 0}^{N - 1} \cas\left(\frac{2\pi a y}{N}\right) \ket{y}, \label{eq:qht_def}
-\]
-Where $\cas(x) = \cos(x) + \sin(x)$.
-
-For general abelian $G = \mathbb{Z}_{N_1} \oplus \cdots \oplus \mathbb{Z}_{N_k}$, the Hartley transform of $f : G \to \mathbb{R}$ is
-\begin{equation}
-    \qht(f)({\bm{a}}) = \frac{1}{\sqrt{|G|}} \sum_{{\bm{y}} \in G} \cas(2\pi \langle {\bm{a}}, \alpha({\bm{y}}) \rangle) f({\bm{y}}),
-\end{equation}
-where $\alpha({\bm{y}}) = y_1 / N_1 + \cdots + y_k / N_k$.
-
-\paragraph{Unitary Equivalence.}
-Using the identity
-\[
-\cas(2\pi \langle {\bm{a}}, \alpha({\bm{y}}) \rangle) = \frac{1 - i}{2}\chi({\bm{a}}, {\bm{y}}) + \frac{1 + i}{2}\chi(-{\bm{a}}, {\bm{y}}),
-\]
-we obtain:
-\begin{equation}
-\qht_G = \frac{1 - i}{2} \qft_G + \frac{1 + i}{2} \qft_G^*, \label{eq:QHT_QFT}
-\end{equation}
-showing that $\qht_G^2 = {1}$ and hence the $\qht$ is unitary.
-
-\paragraph{Quantum Formulation.}
-The quantum Hartley transform over $G$ maps:
-\[
-\sum_{{x} \in G} f({x}) \ket{{x}} \mapsto \sum_{{\bm{a}} \in G} \qht_G(f)({\bm{a}}) \ket{{\bm{a}}}.
-\]
-Because the cas function is real-valued, the resulting amplitudes remain real—a fact that plays a crucial role in real-amplitude quantum protocols.
+
+These gates are all unitary and form the building blocks of single-qubit quantum circuits.
+
+\subsection{Controlled Gates and Universality}
+
+Quantum computation requires not only single-qubit gates, but also multi-qubit gates that enable interactions between qubits.
+The most fundamental among these is the \emph{Controlled-NOT (CNOT)} gate.
+This two-qubit gate flips the target qubit if and only if the control qubit is in the state $\ket{1}$.
+In matrix form, and with respect to the computational basis $\{\ket{00}, \ket{01}, \ket{10}, \ket{11}\}$, it is given by
+\[
+\text{CNOT} = 
+\begin{bmatrix}
+1 & 0 & 0 & 0 \\
+0 & 1 & 0 & 0 \\
+0 & 0 & 0 & 1 \\
+0 & 0 & 1 & 0 \\
+\end{bmatrix}.
+\]
+The CNOT gate plays a central role in quantum algorithms and is essential for generating entangled states.
+It serves as the quantum analogue of the classical XOR gate.
+A natural generalization of the CNOT is the family of controlled-$U$ gates, where $U$ is any single-qubit unitary.
+A controlled-$U$ gate applies $U$ to the target qubit only when the control qubit is $\ket{1}$; otherwise, it acts as the identity.
+This construction is a key component in many quantum algorithms, including quantum phase estimation and Shor’s algorithm.
+
+In classical computation, the set of gates $\{\text{AND}, \text{NOT}\}$ is universal, meaning any Boolean function can be computed using only these gates.
+Analogously, in the quantum setting, certain sets of gates are \emph{universal for quantum computation}.
+That is, they can approximate any unitary transformation on any number of qubits to arbitrary precision.
+A particularly important universal gate set is $\{H, T, \text{CNOT}\}$, consisting of the Hadamard gate, the $\pi/8$ gate (also called the $T$ gate), and the CNOT gate.
+This set forms the basis for fault-tolerant quantum computing and is sufficient to construct any quantum algorithm.
+
+Unlike classical circuits, quantum circuits must obey the constraints of reversibility and linearity.
+They are acyclic and do not allow for operations like signal fanout or feedback loops.
+One key difference from classical logic is the restriction imposed by the \emph{no-cloning theorem}, which states that it is impossible to create a perfect copy of an arbitrary unknown quantum state.
+This makes operations like classical bit copying or broadcasting fundamentally incompatible with quantum mechanics.
+Moreover, measurement in quantum mechanics is inherently irreversible.
+When a qubit is measured in the computational basis, its state collapses probabilistically to either $\ket{0}$ or $\ket{1}$, with probabilities determined by the squared magnitudes of its amplitudes.
+The outcome is a classical bit, and the original quantum superposition is lost in the process.
+
+To illustrate these concepts, consider the task of swapping the quantum states of two qubits.
+This seemingly simple operation cannot be accomplished directly but can be implemented by a specific sequence of three CNOT gates.
+Given two qubits in states $\ket{a}$ and $\ket{b}$, the SWAP operation is performed via the sequence
+\[
+\text{CNOT}_{1,2} \rightarrow \text{CNOT}_{2,1} \rightarrow \text{CNOT}_{1,2},
+\]
+which effectively interchanges the states, resulting in $\ket{b} \ket{a}$.
+This example highlights how even basic classical-like operations must be constructed carefully using reversible building blocks in the quantum circuit model.
 
@@
 Group actions are ubiquitous in modern cryptography.
-A \textbf{cryptographic group action} is one where the action is easy to compute in the forward direction, but inverting the action (recovering $g$ from $x$ and $g*x$) is computationally hard.
+A \textbf{cryptographic group action} ~\cite{Castryck2020} is one where the action is easy to compute in the forward direction, but inverting the action (recovering $g$ from $x$ and $g*x$) is computationally hard.
 This essentially functions as a one-way function: given $x$ and $g$, it is easy to compute $y = g*x$, but given $x$ and $y$ it is infeasible to find $g$ (except with negligible probability).
@@
 In this thesis, we focus on designing the scheme and algorithms at a high level and assume the underlying group action is secure; a detailed security proof is beyond our scope, though we rely on prior results for reassurance.
+
+\section{The Quantum Fourier Transform}
+Let $G$ be an abelian group.
+The group of characters of $G$, denoted $\hat{G}$, consists of homomorphisms of the form $\chi(a, \cdot): G \to \mathbb{C}$ for each $a \in G$.
+If the group has the structure $G \cong \mathbb{Z}_{N_1} \oplus \cdots \oplus \mathbb{Z}_{N_k}$, then the character function $\chi(a, \cdot)$ can be expressed explicitly as
+\[
+\chi(a, x) = \omega_{N_1}^{a_1x_1} \cdots \omega_{N_k}^{a_kx_k}
+\]
+where $\omega_M = \exp(2\pi i / M)$ is a primitive $M$-th root of unity. Given a function $f: G \to \mathbb{C}$, its Fourier transform is defined as
+\[
+\hat{f}(a) = \frac{1}{\sqrt{\abs{G}}} \sum_{x \in G} \chi(a, x) f(x).
+\]
+Correspondingly, the quantum Fourier transform of a normalized state $\sum_{g \in G} f(g) \ket{g}$ is given by $\sum_{x \in G} \hat{f}(x) \ket{x}$.
+
+Now consider a regular group action $(G, X, *)$. For any subset $S \subseteq G$, element $y \in X$, and $h \in G$, we define the following state:
+\begin{equation}
+    \label{eq:x-fourier-basis}
+    \ket{S^{(h)} * y} = \frac{1}{\sqrt{\abs{S}}} \sum_{g \in S} \chi(g, h) \ket{g * y}.
+\end{equation}
+The vector space $\mathbb{C}^X$ has two natural orthonormal bases.
+The first is the standard basis $\{\ket{x} : x \in X\}$, which, for any fixed $x \in X$, can be written as $\{\ket{g * x} : g \in G\}$ because the regularity of the action implies a bijection between $G$ and $X$ (i.e., $|G| = |X|$).
+The second basis consists of the following quantum states:
+\[
+\ket{G^{(h)} * x} = \frac{1}{\sqrt{\abs{G}}} \sum_{g \in G} \chi(g, h) \ket{g * x}, \quad h \in G.
+\]
+These states are simultaneous eigenvectors of the group action unitaries. Specifically, for each $k \in G$, let $U_k$ denote the unitary operator defined by $U_k \ket{y} = \ket{k * y}$. Then we have:
+\[
+U_k \ket{G^{(h)} * x} = \chi(-k, h) \ket{G^{(h)} * x}.
+\]
+This property makes the states $\ket{G^{(h)} * x}$ analogous to Fourier states over the abelian group $G$, and we will often refer to them as such.
+
+\section{The Quantum Hartley Transform}
+
+Another concept we use is the \textbf{quantum Hartley transform} (QHT), which replaces complex exponentials with real sinusoidal kernels.
+Let $N$ be a positive integer, and let $\Z_N$ denote the additive cyclic group of integers modulo $N$.
+The Hartley transform of a function $f: \Z_N \to \R$ is defined as the function $\cht_N(f): \Z_N \to \R$ given by
+\[
+\cht_N(f)(a) = \frac{1}{\sqrt{N}} \sum_{y = 0}^{N - 1} \cas\Big(\frac{2 \pi ay}{N}\Big) f(y),
+\]
+where $\cas(x) = \cos(x) + \sin(x)$.
+Similar to the Fourier transform, $\cht_N$ is a linear operation, and one can verify that it is unitary.
+This definition extends naturally to general abelian groups.
+Suppose $G = \Z_{N_1} \oplus \Z_{N_2} \oplus \cdots \oplus \Z_{N_k}$ is a decomposition of an abelian group into cyclic components.
+For a function $f: G \to \R$, the Hartley transform $\cht_G(f): G \to \R$ is defined by
+\begin{equation}
+    \label{eq:cht-add}
+    \cht_G(f)(a_1, \dots, a_k) = \frac{1}{\sqrt{\abs{G}}} \sum_{y_1 = 0}^{N_1 - 1} \cdots \sum_{y_k = 0}^{N_k - 1} \cas\Big(\frac{2 \pi a_1y_1}{N_1} + \cdots + \frac{2 \pi a_ky_k}{N_k}\Big) f(y_1, \dots, y_k),
+\end{equation}
+with $(a_1, \dots, a_k) \in G$. Introducing the notation $\alpha(\bm{y}) = y_1 / N_1 + \cdots + y_k / N_k$, a more concise form for $\cht_G$ is
+\[
+\cht_G(f)(\bm{a}) = \frac{1}{\sqrt{\abs{G}}} \sum_{\bm{y} \in G} \cas(2\pi \lrang{\bm{a}, \alpha(\bm{y})}) f(\bm{y}).
+\]
+
+Using the identity
+\[
+\cas(2\pi \lrang{\bm{a}, \alpha(\bm{y})}) = \frac{1 - i}{2}\chi(\bm{a}, \bm{y}) + \frac{1 + i}{2}\chi(-\bm{a}, \bm{y}),
+\]
+it follows that
+\begin{equation}
+    \label{eq:ht-ft}
+    \cht_G = \frac{1 - i}{2}\cft_G + \frac{1 + i}{2}\cft_G^*,
+\end{equation}
+where $\cft_G$ denotes the Fourier transform over $G$.
+From this, it can be deduced that $\cht_G^2 = \mathds{1}$, confirming that $\cht_G$ is also unitary.
+An alternative version of the Hartley transform, often appearing in literature, is the multiplicative variant defined by
+\begin{equation}
+    \label{eq:cht-mult}
+    \cht_G(f)(a_1, \dots, a_k) = \frac{1}{\sqrt{\abs{G}}} \sum_{y_1 = 0}^{N_1 - 1} \cdots \sum_{y_k = 0}^{N_k - 1} \mathrm{cas}\Big(\frac{2 \pi a_1y_1}{N_1}\Big) \cdots \cas\Big(\frac{2 \pi a_ky_k}{N_k}\Big) f(y_1, \dots, y_k).
+\end{equation}
+This transform is also unitary, as demonstrated in the following lemma.
+
+\begin{lemma}
+    The Hartley transform \eqref{eq:cht-mult} is unitary.
+\end{lemma}
+
+\begin{proof}
+    Consider the function $f$ as a vector indexed by the elements of $G$.
+The matrix associated with $\cht_G$ is the tensor product of the matrices corresponding to the Hartley transforms over the cyclic components $\Z_{N_i}$ of $G$.
+Specifically, $\cht_G = \cht_{N_1} \otimes \cht_{N_2} \otimes \cdots \otimes \cht_{N_k}$.
+Since each $\cht_{N_i}$ is unitary, the tensor product is also unitary, proving the claim.
+\end{proof}
+
+The quantum Hartley transform over an abelian group $G$ is given by
+\begin{equation}
+    \label{eq:qht}
+    \qht_G: \sum_{\bm{x} \in G} f(\bm{x}) \ket{\bm{x}} \mapsto \sum_{\bm{a} \in G} \cht_G(f)(\bm{a}) \ket{\bm{a}},
+\end{equation}
+where normalization of the input state is omitted for brevity.
+The function $\cht_G(f)$ may refer to either the additive form \eqref{eq:cht-add} or the multiplicative form \eqref{eq:cht-mult}.
+In the special case of a single basis state $\ket{a}$ in the group $\Z_N$, the quantum Hartley transform takes the form
+\begin{equation}
+	\label{eq:qht-N}
+	\qht_N: \ket{a} \mapsto \frac{1}{\sqrt{N}} \sum_{y = 0}^{N - 1} \cas\Big(\frac{2\pi a y}{N}\Big) \ket{y}.
+\end{equation}
+
+% Another concept we use is the \textbf{quantum Hartley transform} (QHT), which replaces complex exponentials with real sinusoidal kernels.
+
+% \paragraph{Definition.}
+% For $G = \mathbb{Z}_N$, define
+% \[
+% \qht_N: \ket{a} \mapsto \frac{1}{\sqrt{N}} \sum_{y = 0}^{N - 1} \cas\left(\frac{2\pi a y}{N}\right) \ket{y}, \label{eq:qht_def}
+% \]
+% Where $\cas(x) = \cos(x) + \sin(x)$.
+
+% For general abelian $G = \mathbb{Z}_{N_1} \oplus \cdots \oplus \mathbb{Z}_{N_k}$, the Hartley transform of $f : G \to \mathbb{R}$ is
+% \begin{equation}
+%     \qht(f)({\bm{a}}) = \frac{1}{\sqrt{|G|}} \sum_{{\bm{y}} \in G} \cas(2\pi \langle {\bm{a}}, \alpha({\bm{y}}) \rangle) f({\bm{y}}),
+% \end{equation}
+% where $\alpha({\bm{y}}) = y_1 / N_1 + \cdots + y_k / N_k$.
+
+% \paragraph{Unitary Equivalence.}
+% Using the identity
+% \[
+% \cas(2\pi \langle {\bm{a}}, \alpha({\bm{y}}) \rangle) = \frac{1 - i}{2}\chi({\bm{a}}, {\bm{y}}) + \frac{1 + i}{2}\chi(-{\bm{a}}, {\bm{y}}),
+% \]
+% we obtain:
+% \begin{equation}
+% \qht_G = \frac{1 - i}{2} \qft_G + \frac{1 + i}{2} \qft_G^*, \label{eq:QHT_QFT}
+% \end{equation}
+% showing that $\qht_G^2 = {1}$ and hence the $\qht$ is unitary.
+
+% \paragraph{Quantum Formulation.}
+% The quantum Hartley transform over $G$ maps:
+% \[
+% \sum_{{x} \in G} f({x}) \ket{{x}} \mapsto \sum_{{\bm{a}} \in G} \qht_G(f)({\bm{a}}) \ket{{\bm{a}}}.
+% \]
+% Because the cas function is real-valued, the resulting amplitudes remain real—a fact that plays a crucial role in real-amplitude quantum protocols.
+
+\section{Quantum Algorithms}
+
+Quantum algorithms harness the principles of quantum mechanics to solve certain computational problems more efficiently than classical algorithms.
+Their power often stems from features like superposition, entanglement, and interference, which enable novel approaches to problems in search, algebra, and cryptography.
+
+In this section, we review two fundamental quantum algorithms—the \textsf{cmpIndex} algorithm and the \textit{quantum phase estimation} algorithm—both of which will play a key role in the constructions and analyses presented in the subsequent chapters.
+
+\paragraph{The $\comph$ algorithm.}
+Suppose we are given a quantum state of the form $\ket{G^{(h)} * x}$.
+There exists an efficient procedure to recover the index $h$.
+This procedure is implemented via a unitary transformation that maps the state $\ket{G^{(h)} * x} \ket{0}$ to $\ket{G^{(h)} * x} \ket{h}$ using the technique of \emph{phase kickback}.
+The algorithm proceeds as follows: begin with the state $\ket{G^{(h)} * x} \ket{0}$, apply the quantum Fourier transform to the second register, and then apply the unitary operator $\sum_{k \in G} U_k \otimes \ket{k} \bra{k}$, which acts jointly on both registers.
+This produces the state
+\[
+\frac{1}{\sqrt{\abs{G}}} \sum_{k \in G} \ket{G^{(h)} * x} \chi(-k, h) \ket{k}.
+\]
+Finally, applying the inverse quantum Fourier transform to the second register yields the desired state $\ket{G^{(h)} * x} \ket{h}$, successfully extracting the label $h$.
+
+\paragraph{The Phase Estimation Algorithm.}
+
+The quantum Fourier transform lies at the heart of a powerful primitive known as \emph{quantum phase estimation}.
+This algorithm is fundamental to many quantum algorithms and plays a central role in problems involving eigenvalue estimation.
+Suppose we are given a unitary operator $U$ with an eigenvector $\ket{u}$ such that
+\[
+U \ket{u} = e^{2\pi i \phi} \ket{u}
+\]
+for some unknown phase $\phi \in [0, 1)$. The goal of the phase estimation algorithm is to estimate the value of $\phi$ to $n$ bits of precision.
+
+Phase estimation is not only interesting as a stand-alone quantum task—estimating eigenphases of unitaries—but also serves as a key subroutine in many important quantum algorithms, such as Shor’s factoring algorithm, quantum order finding, and quantum simulations of physical systems.
+
+The algorithm requires two quantum registers: the first (of $t$ qubits) will store the estimated phase, and the second holds the eigenvector $\ket{u}$.
+We assume access to a black-box unitary that performs the controlled-$U^j$ operation for any integer $j$.
+
+\vspace{1em}
+\noindent\textbf{Algorithm: Quantum Phase Estimation}
+\begin{itemize}
+  \item \textbf{Inputs:}
+    \begin{itemize}
+        \item A black box that implements controlled-$U^j$ for integer $j$.
+        \item An eigenstate $\ket{u}$ of $U$, such that $U \ket{u} = e^{2\pi i \phi} \ket{u}$.
+        \item $t = n + \log(2 + \frac{1}{2\epsilon})$ qubits in the first register initialized to $\ket{0}^{\otimes t}$, where $\epsilon$ is the allowed error.
+    \end{itemize}
+  \item \textbf{Output:} An $n$-bit approximation $\tilde{\phi}$ of $\phi$.
+  \item \textbf{Procedure:}
+    \begin{enumerate}
+      \item Initialize the first register to $\ket{0}^{\otimes t}$ and the second register to $\ket{u}$.
+      \item Apply Hadamard gates to each of the $t$ qubits in the first register to create a uniform superposition:
+      \[
+      \frac{1}{\sqrt{2^t}} \sum_{j=0}^{2^t - 1} \ket{j} \ket{u}.
+      \]
+      \item Apply the controlled-$U^j$ operation to the second register, controlled on the $j$-th basis state of the first register. This yields:
+      \[
+      \frac{1}{\sqrt{2^t}} \sum_{j=0}^{2^t - 1} e^{2\pi i j \phi} \ket{j} \ket{u}.
+      \]
+      \item Discard the second register (since it remains unchanged as $\ket{u}$) and apply the inverse quantum Fourier transform to the first register.
+      \item Measure the first register. With high probability, the outcome is a $t$-bit string that approximates $\phi$ to $n$ bits of accuracy.
+    \end{enumerate}
+\end{itemize}
+
+% \noindent\textbf{Runtime:} $\mathcal{O}(t^2)$ operations and a single invocation of the controlled-$U^j$ oracle for each $j$.
+
+% \noindent\textbf{Success Probability:} At least $1 - \epsilon$.
+
+\vspace{1em}
+This procedure efficiently extracts the phase $\phi$ associated with a known eigenvector of a unitary operator and provides a foundational tool for quantum algorithms that exploit spectral properties of quantum operators.
+For a complete description and analysis of this algorithm, we refer the reader to \cite{NielsenChuang2010}.
 

### 2025-04-12 draft.tex
draft updated

@@
 
-In 2009, Aaronson~\cite{Aaronson2009} proposed the first \emph{public-key quantum money} scheme, in which anyone can verify a quantum banknote while only the bank can mint (issue) new valid banknotes.
+In 2009, Aaronson~\cite{Aaronson2009} proposed the first \emph{public-key quantum money} scheme, in which anyone can verify a quantum banknote while only the bank can generate new valid banknotes.
 Public-key quantum money removes the transactional bottleneck of involving the bank every time.
@@
 The resolution is to enlarge the Hilbert space by introducing an auxiliary \emph{coin register} that provides additional degrees of freedom for unitary evolution.
-This model, first proposed by Watrous in the context of quantum graph algorithms, leads to the \emph{coined discrete-time quantum walk}.
+This model, first proposed by Watrous \cite{Watrous2001} and later formalized in algorithmic contexts by Aharonov et al.~\cite{Aharonov2001}, leads to the \emph{coined discrete-time quantum walk}.
 
@@
 On irregular graphs, care must be taken to define appropriate coin spaces, or one may instead use Szegedy’s alternate framework.
+
+Coined quantum walks on simple structures such as the line were also analyzed in early work by Nayak and Vishwanath~\cite{Nayak2000}, who studied their spreading properties and asymptotic behavior.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Invariant Subspaces and Symmetry Reduction}
+\subsection{Structure and Symmetry in Cayley Graph Walks}
 
@@
 
-\subsection{Hitting and Mixing Properties}
-
+% \paragraph{Hitting and Mixing Properties}
+
+% Quantum walks on Cayley graphs have been applied to study hitting and mixing times.
+In the classical case, random walks on many Cayley graphs are rapidly mixing (e.g., those based on nonabelian simple groups, which often form expanders).
+
+% In the quantum case, mixing is more subtle due to unitary evolution.
+One typically considers \emph{instantaneous} or \emph{time-averaged} mixing.
+Some Cayley graphs support perfect state transfer or periodicity in CTQWs.
+
+% \textbf{Examples:}
+% \begin{itemize}
+%     \item On the cycle graph $C_n$, a CTQW exhibits perfect revival at time $t = \pi$ if $n$ is even.
+%     \item On the hypercube, the CTQW exhibits approximate uniform mixing at specific times.
+% \end{itemize}
+
+% These properties are derived from the spectral structure, which is accessible via group characters.
+
+% \paragraph{Discrete-Time Walks and Symmetry}
+
+% Coined DTQWs also benefit from Cayley graph symmetry.
+If a symmetric coin (e.g., the Grover coin) is used at each vertex of a vertex-transitive graph, the walk respects the full symmetry.
+As a result:
+% \begin{itemize}
+%     \item Amplitudes often remain uniform on symmetry-equivalent vertices.
+%     \item The dynamics of the walk can often be simplified by restricting to a smaller symmetric subspace.
+%     \item In some cases, symmetry can lead to \emph{localization}, where amplitude becomes trapped due to spectral properties of the coin.
+% \end{itemize}
+
+% These effects can be mitigated or exploited through careful coin design or by using Szegedy's method, which naturally respects symmetry.
+
+% In summary, Cayley graphs provide a rich and algebraically structured setting for quantum walks.
+Their underlying group-theoretic properties enable powerful techniques such as spectral analysis through irreducible representations, dimensionality reduction via symmetries and invariant subspaces, and explicit calculations of probabilities, mixing behavior, and hitting times.
+These features make Cayley graphs especially amenable to efficient quantum walk algorithms, which often exploit such structures either explicitly or implicitly.
+In the sections that follow, we extend these ideas to more general settings where group actions go beyond the framework of simple Cayley graphs.
+
+\paragraph{Hitting and Mixing Properties}
 Quantum walks on Cayley graphs have been applied to study hitting and mixing times.
@@
 In the quantum case, mixing is more subtle due to unitary evolution.
-One typically considers \emph{instantaneous} or \emph{time-averaged} mixing.
-Some Cayley graphs support perfect state transfer or periodicity in CTQWs.
-
-\textbf{Examples:}
+One typically considers instantaneous or time-averaged mixing.
+Some Cayley graphs support perfect state transfer or periodicity in CTQWs~\cite{Gerhardt2003}.
+Recent work has also established upper bounds on the mixing time for quantum walks on random graphs, showing polynomial-time convergence in certain regimes~\cite{Chakraborty2020}.
+
+Examples:
 \begin{itemize}
@@
 \end{itemize}
-
 These properties are derived from the spectral structure, which is accessible via group characters.
 
-\subsection{Discrete-Time Walks and Symmetry}
-
+\paragraph{Discrete-Time Walks and Symmetry}
 Coined DTQWs also benefit from Cayley graph symmetry. If a symmetric coin (e.g., the Grover coin) is used at each vertex of a vertex-transitive graph, the walk respects the full symmetry. As a result:
@@
     \item Amplitudes often remain uniform on symmetry-equivalent vertices.
-    \item Walk dynamics can often be analyzed by reducing to a lower-dimensional invariant subspace.
-    \item In some cases, symmetry can lead to \emph{localization}, where amplitude becomes trapped due to spectral properties of the coin.
+    \item The dynamics of the walk can often be simplified by restricting to a smaller symmetric subspace.
+    \item In some cases, symmetry can lead to localization, where amplitude becomes trapped due to spectral properties of the coin.
 \end{itemize}
-
-These effects can be mitigated or exploited through careful coin design or by using Szegedy's method, which naturally respects symmetry.
-
-\subsection{Summary}
-
-Cayley graphs offer a rich and powerful structure for quantum walks. Their group-theoretic properties allow:
-\begin{itemize}
-    \item Spectral analysis via irreducible representations.
-    \item Dimensionality reduction using symmetry and invariant subspaces.
-    \item Explicit calculation of probabilities, mixing behavior, and hitting times.
-\end{itemize}
-
-Many efficient quantum walk algorithms exploit these properties either directly or implicitly.
-In subsequent sections, we will explore quantum walks on more general structures where group actions go beyond simple Cayley graphs.
+These effects can be mitigated or exploited through careful coin design or by using Szegedy’s method, which naturally respects symmetry.
+
+In summary, Cayley graphs provide a rich and algebraically structured setting for quantum walks.
+Their underlying group-theoretic properties enable powerful techniques such as spectral analysis through irreducible representations, dimensionality reduction via symmetries and invariant subspaces, and explicit calculations of probabilities, mixing behavior, and hitting times.
+These features make Cayley graphs especially amenable to efficient quantum walk algorithms, which often exploit such structures either explicitly or implicitly.
+In the sections that follow, we extend these ideas to more general settings where group actions go beyond the framework of simple Cayley graphs.
 
@@
 \begin{description}
-    \item[Correctness:] For any valid output $(s, |\$\rangle)$ of $\mathsf{Mint}(1^n)$, the verification algorithm accepts with high probability.
-Formally, $\Pr[\mathsf{Verify}(s, |\$\rangle) = \mathtt{accept}]$ should be very close to 1 (typically we require it to be $1 - negl(n)$, where $negl(n)$ denotes a negligible function in $n$).
+    \item[Correctness:] For any valid output $(s, |\$\rangle)$ of $\mathsf{Gen}(1^n)$, the verification algorithm accepts with high probability.
+Formally, $\Pr[\mathsf{Verify}(s, |\$\rangle) = \mathtt{accept}]$ should be very close to 1 (typically we require it to be $1 - \negl(n)$, where $\negl(n)$ denotes a negligible function in $n$).
     \item[Security (Unforgeability):] No efficient adversary, given one or more genuine banknotes, can produce a new valid banknote.
@@
 In a \emph{public-key} scheme, the verifier uses only the public information (here, the serial number and any scheme-wide public parameters) to check validity, and does not need any secret key.
-The bank (mint) may have a secret key to produce the states, but after minting, the bank’s involvement is not needed.
+The bank may have a secret key to produce the states, but after generation, the bank’s involvement is not needed.
 In our scheme, the serial number will effectively contain the information needed for public verification (similar to how a classical bill might have a number anyone can look up, except here it’s used in a quantum procedure).
@@
 \section{Fourier-Based Quantum Money from Group Actions}
-Zhandry’s quantum money scheme \cite{Zhandry2024} is built on an abelian group action $G \curvearrowright X$.
+Zhandry’s quantum money scheme \cite{Zhandry2024} is built on an abelian group action $*:G \times X \mapsto X$.
 We have a family of group actions parameterized by the security parameter $n$ (so the size of $G$ grows with $n$).
@@
 
-The minting algorithm $\mathsf{Mint}$ in Zhandry’s scheme works as follows (informally):
+The generation algorithm $\mathsf{Gen}$ in Zhandry’s scheme works as follows (informally):
 \begin{enumerate}
@@
 Since the Hartley transform is closely related to the Fourier transform (essentially it produces the real and imaginary parts in a single real-valued transform), one might expect this substitution to be straightforward.
-And indeed, for the minting procedure it largely is: we will use the QHT to create real-amplitude superposition states.
-
-Concretely, assume again a group action $G \curvearrowright X$ with $|G|=N$. We fix the same generating set $S$ and basepoint $x_0$. The $\mathsf{Gen}_{H}$ (Hartley generation) algorithm:
+And indeed, for the generation procedure it largely is: we will use the QHT to create real-amplitude superposition states.
+
+Concretely, assume again a group action $*: G\times X \mapsto X$ with $|G|=N$. We fix the same generating set $S$ and basepoint $x_0$. The $\mathsf{Gen}_{H}$ (Hartley generation) algorithm:
 \begin{enumerate}
@@
 In fact, we do not have a nice product state separation, so we cannot simply measure one register to get $h$.
-Instead, the output of minting is just the quantum state $|\$\rangle$ (which is entangled between what used to be two registers) and the known classical serial number $h$ (we know what $h$ we picked).
+Instead, the output of generation is just the quantum state $|\$\rangle$ (which is entangled between what used to be two registers) and the known classical serial number $h$ (we know what $h$ we picked).
 \end{enumerate}
@@
 
-% \begin{algorithm}[$\qht_N$] \
+% \begin{algorithm}[$\qht_N$] 
 \paragraph{Algorithm $\qht_N$}
-    % \label{alg:qht-N}
-    % \begin{description}[font = \normalfont\itshape, itemsep = 0mm, parsep = 0mm, topsep = 1mm]
-    %     \item [Input:] quantum state $\ket{\psi} \in \C^N$, where $N = 2^n$
-    %     \item [Output:] quantum state $\qht_N\ket{\psi}$
-    % \end{description}
+    \label{alg:qht-N}
+    \begin{description}[font = \normalfont\itshape, itemsep = 0mm, parsep = 0mm, topsep = 1mm]
+        \item [Input:] quantum state $\ket{\psi} \in \C^N$, where $N = 2^n$
+        \item [Output:] quantum state $\qht_N\ket{\psi}$
+    \end{description}
 
@@
 
-% \begin{theorem}
-\paragraph{Theorem.}
+\begin{theorem}
+% \paragraph{Theorem.}
     \label{thm:qht-cost}
     Algorithm above is correct and can be implemented using $\approx \log^2 N + O(\log N)$ elementary gates.
-% \end{theorem}
-
-% \begin{proof}
-\paragraph{Proof.}
+\end{theorem}
+
+\begin{proof}
+% \paragraph{Proof.}
     The correctness of the algorithm follows from the preceding discussion.
@@
     Solving this recurrence yields \( T(N) \approx \log^2 N + O(\log N) \), as claimed.
-%     \end{proof}
+    \end{proof}
 %%%%%%%%%%%  ta inja  %%%%%%%%%%%
@@
 Thus, switching to the Hartley transform does not introduce any prohibitive cost.
-All steps of minting and verification remain efficient.
+All steps of generation and verification remain efficient.
 Having covered the construction of the money scheme and the necessary tools, we now proceed to the final piece: the detailed verification algorithm using quantum walks, and an analysis of how it validates genuine banknotes and foils counterfeit attempts.
@@
 
-    % \begin{lemma}
-    \paragraph{Lemma.}
+    \begin{lemma}
+    % \paragraph{Lemma.}
         \label{lem:h-eigen}
         The money state $\ket{\mathbb{Z}_N^{(h)} * x}_H$ is an eigenstate of $W$ with eigenvalue $e^{i\lambda_h t}$.
-    % \end{lemma}
-    % \begin{proof}
-    \paragraph{Proof.}
+    \end{lemma}
+    \begin{proof}
+    % \paragraph{Proof.}
         We have 
@@
         where the second equality follows from the identity in \eqref{eq:QHT_QFT}, and the last equality follows from the fact that $\lambda_h = \lambda_{-h}$.
-    % \end{proof}
+    \end{proof}
 

### 2025-04-13 cyclic_graph.tex
todo list done

\documentclass{standalone}

\usepackage{tikz}
\usetikzlibrary{graphs}

\begin{document}
\begin{tikzpicture}

    % Create nodes positioned on a circle (nodes are empty)
    \foreach \i [evaluate=\i as \angle using {360/8 * -\i}] in {0,...,7} {
        \node [draw, circle, inner sep = 2pt] (n\i) at (\angle:2cm) {\i};
    }

    % Draw edges connecting the nodes in a cycle
    \foreach \i in {0,...,6} {
        \pgfmathtruncatemacro{\next}{\i+1}
        \draw (n\i) -- (n\next);
    }

    \draw  (n7) -- node [midway, sloped, fill = white, inner sep = 1.5mm] {$\cdots$} (n0);
\end{tikzpicture}
\end{document}

### 2025-04-13 draft.tex
todo list done

@@
     colorlinks = true,
-    citecolor = citecolor,
+    citecolor = blue,
     filecolor = blue,
@@
 \title{
-  Quantum Walks and Application to Quantum Money\\[1em]
-%   \large Supervised by Dr. Jake Doliskani\\[3em]
-  \normalsize McMaster University\\
-  Department of Computing and Software
+  \textbf{Quantum Walks and Application to Quantum Money}\\[2em]
+  \normalsize by\\[2em]
+  \text{\large Ali Mousavi} \\[5em]
+  \text{\shortstack{A Master's Thesis \\[0.5em]
+   Submitted to the Department of Computing and Software\\[0.5em]
+   McMaster University\\[0.5em]
+   In Fulfillment of the Requirements\\[0.5em]
+   For a Master's Degree}
   }
-\author{Ali Mousavi}
+
+}
+
 \date{April 2025}
@@
 We examine their mathematical structure and their advantages over classical random walks, emphasizing their efficiency in state evolution and probability distribution spreading.
-As a part of this work, we examine efficient implementations of transforms such as the Quantum Fourier Transform (QFT) and the Quantum Hartley Transform (QHT), analyzing their role in encoding quantum states for secure cryptographic applications.
-In particular, we discuss a novel instantiation of a quantum money scheme based on QHT, leveraging its unique properties for improved security and efficiency.
+As a part of this work, we examine efficient implementations of transforms such as the Quantum Fourier Transform ($\qft$) and the Quantum Hartley Transform ($\qht$), analyzing their role in encoding quantum states for secure cryptographic applications.
+In particular, we discuss a novel instantiation of a quantum money scheme based on $\qht$, leveraging its unique properties for improved security and efficiency.
 To ensure the robustness of this quantum money scheme, we develop a verification mechanism utilizing quantum walks.
@@
 \medskip\noindent\textbf{This Work – Motivation and Contributions.} 
-In this thesis, we adapt Zhandry’s group-action quantum money scheme by replacing its use of the Quantum Fourier Transform with the \emph{Quantum Hartley Transform} (QHT) over finite abelian groups.
+In this thesis, we adapt Zhandry’s group-action quantum money scheme by replacing its use of the Quantum Fourier Transform with the \emph{Quantum Hartley Transform} ($\qht$) over finite abelian groups.
 The motivation behind this substitution is multifold.
@@
 These characteristics endow quantum computers with computational abilities that can outperform classical counterparts in certain tasks.
+For a comprehensive introduction to quantum computation and quantum information we refer the reader to ~\cite{NielsenChuang2010, watrous2018theory, kaye2006introduction}.
 
@@
 
-  \item \textbf{Composition of Systems.} If two quantum systems $A$ and $B$ are described by Hilbert spaces $\mathcal{H}_A$ and $\mathcal{H}_B$, respectively, then the combined system is described by the tensor product $\mathcal{H}_A \otimes \mathcal{H}_B$.
-A product state of the form $\ket{\psi_A} \otimes \ket{\psi_B}$ represents a system where $A$ and $B$ are uncorrelated.
+  \item \textbf{Composition of Systems.} If two quantum systems \( A \) and \( B \) are described by Hilbert spaces \( \mathcal{H}_A \) and \( \mathcal{H}_B \), respectively, then the combined system is described by the tensor product \( \mathcal{H}_A \otimes \mathcal{H}_B \).
+A product state of the form \( \ket{\psi_A} \otimes \ket{\psi_B} \) represents a system where \( A \) and \( B \) are uncorrelated.
 In general, however, the state may be entangled, and cannot be written as a product of subsystems.
+
+  If unitary operators \( U_A \) and \( U_B \) act on \( \mathcal{H}_A \) and \( \mathcal{H}_B \), respectively, then the combined unitary \( U_A \otimes U_B \) acts on the joint system by applying \( U_A \) to subsystem \( A \) and \( U_B \) to subsystem \( B \), independently.
+That is,
+  \[
+  (U_A \otimes U_B)(\ket{\psi_A} \otimes \ket{\psi_B}) = (U_A \ket{\psi_A}) \otimes (U_B \ket{\psi_B}).
+  \]
+  This operation preserves the separability of product states, and more generally, acts linearly on the full Hilbert space \( \mathcal{H}_A \otimes \mathcal{H}_B \).
+
 \end{enumerate}
@@
 \section{The Quantum Fourier Transform}
+The \textit{Quantum Fourier Transform $\qft$} is a quantum analogue of the classical discrete Fourier transform and plays a fundamental role in many quantum algorithms, including Shor’s factoring algorithm and quantum phase estimation.
+It enables the transformation of quantum states into the frequency domain, revealing periodicities and structure that may be hidden in the computational basis.
+
+A common instance of the $\qft$ is over the cyclic group \( \mathbb{Z}_N  = \{0,1,...,N-1\}\). Given a state \( \ket{x} \in \mathbb{C}^N \), the $\qft$ over \( \mathbb{Z}_N \) maps it to
+\[
+\ket{x} \mapsto \frac{1}{\sqrt{N}} \sum_{k=0}^{N-1} e^{2\pi i xk / N} \ket{k}.
+\]
+When \( N = 2^n \), we can express the index \( x \) in binary as \( x = j_1 j_2 \ldots j_n \), where \( x = j_1 2^{n-1} + j_2 2^{n-2} + \cdots + j_n \).
+In this case, the $\qft$ has a beautiful product representation:
+\[
+\ket{j_1 \cdots j_n} \mapsto \frac{1}{2^{n/2}} \bigotimes_{k=1}^n \left( \ket{0} + e^{2\pi i 0.j_k j_{k+1} \cdots j_n} \ket{1} \right),
+\]
+where \( 0.j_k j_{k+1} \cdots j_n \) denotes the binary fraction \( \frac{j_k}{2} + \frac{j_{k+1}}{4} + \cdots + \frac{j_n}{2^{n-k+1}} \).
+This form reveals the tensor product structure of the $\qft$: the transformed state decomposes as a product of single-qubit superpositions, each involving successively finer phase rotations.
+
+This structure allows for an efficient quantum circuit implementation.
+The circuit consists of a sequence of Hadamard gates and controlled phase gates \( R_k = \begin{bmatrix} 1 & 0 \\ 0 & e^{2\pi i / 2^k} \end{bmatrix} \), followed by a series of swap gates to reverse the order of qubits.
+For each qubit \( j_k \), a Hadamard gate is applied first, followed by controlled-\( R_2, R_3, \ldots \) gates from subsequent qubits.
+The number of gates required is \( \Theta(n^2) \), making the $\qft$ over \( 2^n \) dimensions efficiently implementable on a quantum computer \cite[Section 5.1]{NielsenChuang2010}.
+
+In this work, we extend the notion of the $\qft$ to more general finite groups beyond \( \mathbb{Z}_N \).
+This generalization is essential for studying quantum walks on group-based graphs and analyzing quantum algorithms defined over non-abelian structures.
+
 Let $G$ be an abelian group.
@@
 Correspondingly, the quantum Fourier transform of a normalized state $\sum_{g \in G} f(g) \ket{g}$ is given by $\sum_{x \in G} \hat{f}(x) \ket{x}$.
+The $\qft$ over \( G \) is simply a tensor product of $\qft$s over each \( \mathbb{Z}_{N_i} \), and can therefore be implemented efficiently.
 
@@
 
-Another concept we use is the \textbf{quantum Hartley transform} (QHT), which replaces complex exponentials with real sinusoidal kernels.
+Another concept we use is the \textbf{quantum Hartley transform} ($\qht$), which replaces complex exponentials with real sinusoidal kernels.
 Let $N$ be a positive integer, and let $\Z_N$ denote the additive cyclic group of integers modulo $N$.
@@
 \end{equation}
-
-% Another concept we use is the \textbf{quantum Hartley transform} (QHT), which replaces complex exponentials with real sinusoidal kernels.
-
-% \paragraph{Definition.}
-% For $G = \mathbb{Z}_N$, define
-% \[
-% \qht_N: \ket{a} \mapsto \frac{1}{\sqrt{N}} \sum_{y = 0}^{N - 1} \cas\left(\frac{2\pi a y}{N}\right) \ket{y}, \label{eq:qht_def}
-% \]
-% Where $\cas(x) = \cos(x) + \sin(x)$.
-
-% For general abelian $G = \mathbb{Z}_{N_1} \oplus \cdots \oplus \mathbb{Z}_{N_k}$, the Hartley transform of $f : G \to \mathbb{R}$ is
-% \begin{equation}
-%     \qht(f)({\bm{a}}) = \frac{1}{\sqrt{|G|}} \sum_{{\bm{y}} \in G} \cas(2\pi \langle {\bm{a}}, \alpha({\bm{y}}) \rangle) f({\bm{y}}),
-% \end{equation}
-% where $\alpha({\bm{y}}) = y_1 / N_1 + \cdots + y_k / N_k$.
-
-% \paragraph{Unitary Equivalence.}
-% Using the identity
-% \[
-% \cas(2\pi \langle {\bm{a}}, \alpha({\bm{y}}) \rangle) = \frac{1 - i}{2}\chi({\bm{a}}, {\bm{y}}) + \frac{1 + i}{2}\chi(-{\bm{a}}, {\bm{y}}),
-% \]
-% we obtain:
-% \begin{equation}
-% \qht_G = \frac{1 - i}{2} \qft_G + \frac{1 + i}{2} \qft_G^*, \label{eq:QHT_QFT}
-% \end{equation}
-% showing that $\qht_G^2 = {1}$ and hence the $\qht$ is unitary.
-
-% \paragraph{Quantum Formulation.}
-% The quantum Hartley transform over $G$ maps:
-% \[
-% \sum_{{x} \in G} f({x}) \ket{{x}} \mapsto \sum_{{\bm{a}} \in G} \qht_G(f)({\bm{a}}) \ket{{\bm{a}}}.
-% \]
-% Because the cas function is real-valued, the resulting amplitudes remain real—a fact that plays a crucial role in real-amplitude quantum protocols.
+The unitary operator $\qht_N$ can be implemented efficiently, as will be shown in Section~\ref{sec:efficient_qht}.
+When using the multiplicative form~\eqref{eq:cht-mult}, the unitary $\qht_G$ decomposes as a tensor product of unitaries of the form $\qht_N$.
 
@@
 Each vertex $j \in \mathbb{Z}_n$ is connected to $j \pm 1 \mod n$.
-
+This graph is of particular interest in this work, as we will make use of it in chapter~\ref{chap:verification}.
+    \begin{center}
+        \includegraphics[width = 5cm]{cyclic_graph.pdf}
+    \end{center}
     \item \textbf{Hypercube $Q_n$:} The $n$-dimensional Boolean hypercube is the Cayley graph of the group $(\mathbb{Z}_2)^n$ with generating set $S = \{e_1, \dots, e_n\}$, where $e_i$ flips the $i$-th bit.
@@
     which is an entangled state between a superposition of group elements and their corresponding $X$-elements.
-    \item Apply the inverse QFT (which is the adjoint of the QFT) on the first register. This recombines the amplitudes in the first register. The result (by properties of the QFT) can be shown to be 
+    \item Apply the inverse $\qft$ (which is the adjoint of the $\qft$) on the first register.
+This recombines the amplitudes in the first register.
+The result (by properties of the $\qft$) can be shown to be
     \[
@@
 \section{Hartley-Transform Money Scheme Construction}
-Our scheme modifies the above Fourier-based construction by utilizing the \textbf{quantum Hartley transform (QHT)} in place of the QFT.
+
+Our scheme modifies the above Fourier-based construction by utilizing the \textbf{quantum Hartley transform ($\qht$)} in place of the $\qft$.
 Since the Hartley transform is closely related to the Fourier transform (essentially it produces the real and imaginary parts in a single real-valued transform), one might expect this substitution to be straightforward.
-And indeed, for the generation procedure it largely is: we will use the QHT to create real-amplitude superposition states.
-
-Concretely, assume again a group action $*: G\times X \mapsto X$ with $|G|=N$. We fix the same generating set $S$ and basepoint $x_0$. The $\mathsf{Gen}_{H}$ (Hartley generation) algorithm:
+And indeed, for the generation procedure it largely is: we will use the $\qht$ to create real-amplitude superposition states.
+
+Concretely, assume again a group action $*: G\times X \mapsto X$ with $|G|=N$.
+For concreteness, we assume that $G = \Z_N$; the genralization of the scheme to a general group $G$ is straightforward.
+We fix the same generating set $S$ and basepoint $x_0$.
+The $\mathsf{Gen}_{H}$ (Hartley generation) algorithm:
 \begin{enumerate}
@@
     \item Prepare $|0_G, x_0\rangle$ as before.
-    \item Apply the \emph{quantum Hartley transform} over $G$ to the first register. The Hartley transform (on an abelian group of order $N$) is defined as:
-    \[
-       \mathrm{QHT}: |g\rangle \mapsto \frac{1}{\sqrt{N}} \sum_{k \in G} \cas \Big(\frac{2\pi \langle k,g \rangle}{N}\Big) |k\rangle,
-    \] 
-    where $\mathrm{cas}(\theta) = \cos \theta + \sin \theta$ and $\langle k,g \rangle$ denotes some pairing like an exponent or dot product (for cyclic groups this is just $kg$).
-In simpler terms, $\mathrm{QHT}(|0_G\rangle) = \frac{1}{\sqrt{N}}\sum_{k \in G} |k\rangle$ (because $\cas(0)=1$), \emph{the same uniform superposition as the QFT produces for $|0\rangle$}.
+    \item Apply the \emph{quantum Hartley transform} over $G$ to the first register, as we saw in \ref{eq:qht-N}:
+    \[
+       \qht: |g\rangle \mapsto \frac{1}{\sqrt{N}} \sum_{k \in \mathbb{Z}_N} \cas \Big(\frac{2\pi  kg }{N}\Big) |k\rangle,
+    \] 
+    where $\mathrm{cas}(\theta) = \cos \theta + \sin \theta$.
+In simpler terms, $\qht(|0_G\rangle) = \frac{1}{\sqrt{N}}\sum_{k \in G} |k\rangle$ (because $\cas(0)=1$), \emph{the same uniform superposition as the $\qft$ produces for $|0\rangle$}.
 So after this step, we again have $\frac{1}{\sqrt{N}}\sum_{g \in G} |g\rangle|x_0\rangle$, but crucially the coefficients are all \emph{real} and positive (in fact all $1/\sqrt{N}$).
     \item Perform the controlled group action by the first register on the second: $\frac{1}{\sqrt{N}}\sum_{g} |g\rangle |g*x_0\rangle$.
-    \item Apply the inverse QHT on the first register (which being its own inverse up to a constant factor, is the same operation again since Hartley is symmetric like Fourier).
+    \item Apply the inverse $\qht$ on the first register (which being its own inverse up to a constant factor, is the same operation again since Hartley is symmetric like Fourier).
 Now here is where things differ: after this operation, the joint state will be
     \[
-       \frac{1}{\sqrt{N}} \sum_{g \in G} \cas\Big(\frac{2\pi \langle h,g \rangle}{N}\Big)\, |g\rangle \otimes |g*x_0\rangle.
+       \frac{1}{\sqrt{N}} \sum_{g \in \mathbb{Z}_N} \cas\Big(\frac{2\pi hg}{N}\Big)\, |g\rangle \otimes |g*x_0\rangle.
     \] 
@@
 In the Fourier case, we got $|h\rangle \otimes \text{(orbit state)}$.
-In the Hartley case, we do not get a single basis state in the first register; instead we get a superposition in the first register with real coefficients $c_g = \cas(2\pi\langle h,g\rangle/N)$.
+In the Hartley case, we do not get a single basis state in the first register; instead we get a superposition in the first register with real coefficients $c_g = \cas(2\pi hg/N)$.
 However, note that $c_g$ is just some real number in $[-1,1]$ depending on $h$ and $g$.
@@
     \[
-      |\$\rangle = \frac{1}{\sqrt{N}} \sum_{x \in X} \Big(\frac{1}{\sqrt{N}}\sum_{g: g*x_0 = x} \cas\big(\frac{2\pi \langle h,g \rangle}{N}\big)\Big)\, |x\rangle.
+      |\$\rangle = \frac{1}{\sqrt{N}} \sum_{x \in X} \Big(\frac{1}{\sqrt{N}}\sum_{g: g*x_0 = x} \cas\big(\frac{2\pi  hg}{N}\big)\Big)\, |x\rangle.
     \] 
@@
 
-\section{Efficient Quantum Hartley Transform Implementation}
-Before moving on to the verification algorithm, we briefly discuss how we implement the quantum Hartley transform (QHT) efficiently, as this is an important practical aspect of our scheme.
+\section{Efficient Quantum Hartley Transform Implementation}\label{sec:efficient_qht}
+Before moving on to the verification algorithm, we briefly discuss how we implement the quantum Hartley transform ($\qht$) efficiently, as this is an important practical aspect of our scheme.
 The Fourier transform is well-known to have efficient circuits; for the Hartley transform, fewer results are available, so we contributed a new circuit construction.
 
-The QHT we need is over an abelian group, which for concreteness one can think of as $\mathbb{Z}_N$ (the general finite abelian group case can usually be reduced to a direct sum of cyclic groups, applying QHT on each cyclic component).
+The $\qht$ we need is over an abelian group, which for concreteness one can think of as $\mathbb{Z}_N$ (the general finite abelian group case can usually be reduced to a direct sum of cyclic groups, applying $\qht$ on each cyclic component).
 Classical Hartley transforms have a recursive structure similar to fast Fourier transforms.
@@
 
-Our algorithm for QHT works roughly as follows:
+Our algorithm for $\qht$ works roughly as follows:
 - If $N$ is even, we can express the length-$N$ Hartley transform in terms of two length-$N/2$ Hartley transforms plus a combination of cheap operations (additions, permutations of data, etc.).
@@
 The key idea is to leverage the recursive structure of \( \qht_N \), analogous to the strategy used for \( \qft_N \).
-To facilitate this, we begin by rewriting the summation in Equation~\eqref{eq:qht_def} to expose its recursive form.
+To facilitate this, we begin by rewriting the summation in Equation~\eqref{eq:qht-N} to expose its recursive form.
 Our approach is as follows:
@@
 \end{align*}
+Here, $\mathds{1} \otimes \qht_{N / 2} \otimes \mathds{1}$ is a unitary that applies the identity to the first and last qubits and applies $\qht_{N/2}$ to the rest of the qubits.
 Next, we apply a controlled negation operation, where the ancilla qubit is flipped if and only if the least significant bit \( b \) is equal to 1.
@@
     To implement the unitary \( U_R \), which requires constructing the conditional rotation operator \( R(y, b) \) for arbitrary \( y \) and \( b \), we make use of the two-qubit controlled rotations:
-    \[
-    R_j = \ket{0}\bra{0} \otimes \mathds{1} + \ket{1}\bra{1} \otimes
+    \[ R_j = \ket{0}\bra{0} \otimes \mathds{1} + \ket{1}\bra{1} \otimes
         \begin{bmatrix}
-    \cos\left(\frac{2\pi 2^j}{N}\right) & \sin\left(\frac{2\pi 2^j}{N}\right) \\
-    -\sin\left(\frac{2\pi 2^j}{N}\right) & \cos\left(\frac{2\pi 2^j}{N}\right)
+            \cos(2\pi 2^j / N) & \sin(2\pi 2^j / N) \\
+            -\sin(2\pi 2^j / N) & \cos(2\pi 2^j / N)
         \end{bmatrix},
@@
 
-The resulting complexity for an $N$-point QHT is $O(\log^2 N)$ basic quantum gates (up to polylog factors for precision), which is on par (up to constant factors) with the complexity of a QFT circuit.
+The resulting complexity for an $N$-point $\qht$ is $O(\log^2 N)$ basic quantum gates (up to polylog factors for precision), which is on par (up to constant factors) with the complexity of a $\qft$ circuit.
 We also derived explicit constants for small cases to show improvements over prior work.
@@
         \end{align*}
-        where the second equality follows from the identity in \eqref{eq:QHT_QFT}, and the last equality follows from the fact that $\lambda_h = \lambda_{-h}$.
+        where the second equality follows from the identity in \eqref{eq:ht-ft}, and the last equality follows from the fact that $\lambda_h = \lambda_{-h}$.
     \end{proof}

### 2025-04-13 draft.tex
draft updated

@@
 
+% \section{Mixing in Classical and Quantum Walks}
+
+% \paragraph{Classical Mixing Time}
+
+% The \emph{mixing time} of a random walk on a graph quantifies how quickly the probability distribution over vertices converges to the stationary distribution.
+Consider a continuous-time random walk on a graph \( G = (V, E) \) defined via the Laplacian matrix \( L \).
+The evolution of the probability vector \( p(t) \in \mathbb{R}^{|V|} \), which represents the probability of being at each vertex at time \( t \), is governed by the differential equation:
+% \[
+% \frac{dp(t)}{dt} = Lp(t).
+% \]
+% Let \( u := \frac{1}{|V|}(1,1,\dots,1) \) denote the uniform distribution over vertices.
+This vector is an eigenvector of \( L \) corresponding to eigenvalue zero.
+Assuming \( G \) is connected, this eigenvalue is unique.
+Let \( \{ v_\lambda \} \) be an orthonormal basis of eigenvectors of \( L \), where \( \lambda \neq 0 \), such that:
+% \[
+% L = \sum_{\lambda \neq 0} \lambda v_\lambda v_\lambda^\top.
+% \]
+% Then, the solution to the walk is:
+% \begin{align}
+% p(t) &= e^{Lt}p(0) \label{eq:classical1} \\
+%      &= \left( |V| uu^\top + \sum_{\lambda \neq 0} e^{\lambda t} v_\lambda v_\lambda^\top \right)p(0) \label{eq:classical2} \\
+%      &= \langle u, p(0) \rangle u + \sum_{\lambda \neq 0} e^{\lambda t} \langle v_\lambda, p(0) \rangle v_\lambda. \label{eq:classical3}
+% \end{align}
+% As \( t \to \infty \), each term involving \( \lambda < 0 \) decays exponentially, and \( p(t) \to u \).
+Hence, the walk asymptotically approaches the uniform distribution.
+The rate of convergence is governed by the \emph{spectral gap}, i.e., the magnitude of the smallest nonzero eigenvalue of \( L \).
+
+% \paragraph{Quantum Mixing: Time-Averaged Behavior}
+
+% In contrast to classical walks, a quantum walk is a unitary process.
+As such, it does not converge to a stationary quantum state over time.
+However, it is still meaningful to define a limiting distribution in the measurement statistics.
+Consider a quantum walk generated by a Hermitian operator \( H \) (e.g., the Laplacian or adjacency matrix), evolving under:
+% \[
+% \ket{\psi(t)} = e^{-iHt} \ket{a},
+% \]
+% where \( \ket{a} \) is the initial vertex state.
+Since unitary evolution is reversible and norm-preserving, convergence is not possible in the traditional sense.
+Nevertheless, one may define a time-averaged probability of observing vertex \( b \) after evolving for a randomly chosen time \( t \in [0, T] \):
+% \[
+% p_{a \to b}(T) = \frac{1}{T} \int_0^T |\langle b | e^{-iHt} | a \rangle|^2 \, dt.
+% \]
+% Assuming a non-degenerate spectral decomposition \( H = \sum_\lambda \lambda \ket{\lambda}\bra{\lambda} \), one finds:
+% \begin{align}
+% p_{a \to b}(T) &= \sum_\lambda |\langle a | \lambda \rangle|^2 |\langle b | \lambda \rangle|^2 \\
+% &\quad + \sum_{\lambda \neq \lambda'} \langle b | \lambda \rangle \langle \lambda | a \rangle \langle a | \lambda' \rangle \langle \lambda' | b \rangle \cdot \frac{1 - e^{-i(\lambda - \lambda')T}}{i(\lambda - \lambda')T}.
+% \end{align}
+% As \( T \to \infty \), the second term vanishes, and the limiting distribution becomes:
+% \[
+% p_{a \to b}(\infty) := \sum_\lambda |\langle a | \lambda \rangle|^2 |\langle b | \lambda \rangle|^2.
+% \]
+% This distribution does not depend on time and captures the long-time average behavior of the quantum walk.
+The convergence rate is now controlled by the minimum spectral gap between \emph{any pair} of distinct eigenvalues of \( H \), not just the smallest nonzero eigenvalue.
+\section{Mixing in Classical and Quantum Walks}
+
+\paragraph{Classical Mixing Time}
+
+The \emph{mixing time} of a random walk on a graph quantifies how quickly the probability distribution over vertices converges to the stationary distribution.
+Consider a continuous-time random walk on a graph \( G = (V, E) \) defined via the Laplacian matrix \( L \).
+The evolution of the probability vector \( p(t) \in \mathbb{R}^{|V|} \), which represents the probability of being at each vertex at time \( t \), is governed by the differential equation:
+\[
+\frac{dp(t)}{dt} = Lp(t).
+\]
+Let \( u := \frac{1}{|V|}(1,1,\dots,1) \) denote the uniform distribution over vertices.
+This vector is an eigenvector of \( L \) corresponding to eigenvalue zero.
+Assuming \( G \) is connected, this eigenvalue is unique.
+Let \( \{ v_\lambda \} \) be an orthonormal basis of eigenvectors of \( L \), where \( \lambda \neq 0 \), such that:
+\[
+L = \sum_{\lambda \neq 0} \lambda v_\lambda v_\lambda^\top.
+\]
+Then, the solution to the walk is:
+\begin{align}
+p(t) &= e^{Lt}p(0) \label{eq:classical1} \\
+     &= \left( |V| uu^\top + \sum_{\lambda \neq 0} e^{\lambda t} v_\lambda v_\lambda^\top \right)p(0) \label{eq:classical2} \\
+     &= \langle u, p(0) \rangle u + \sum_{\lambda \neq 0} e^{\lambda t} \langle v_\lambda, p(0) \rangle v_\lambda. \label{eq:classical3}
+\end{align}
+As \( t \to \infty \), each term involving \( \lambda < 0 \) decays exponentially, and \( p(t) \to u \).
+Hence, the walk asymptotically approaches the uniform distribution.
+The rate of convergence is governed by the \emph{spectral gap}, i.e., the magnitude of the smallest nonzero eigenvalue of \( L \)~\cite{childs2022quantum}.
+
+\paragraph{Quantum Mixing: Time-Averaged Behavior}
+
+In contrast to classical walks, a quantum walk is a unitary process.
+As such, it does not converge to a stationary quantum state over time.
+However, it is still meaningful to define a limiting distribution in the measurement statistics.
+Consider a quantum walk generated by a Hermitian operator \( H \) (e.g., the Laplacian or adjacency matrix), evolving under:
+\[
+\ket{\psi(t)} = e^{-iHt} \ket{a},
+\]
+where \( \ket{a} \) is the initial vertex state.
+Since unitary evolution is reversible and norm-preserving, convergence is not possible in the traditional sense.
+Nevertheless, one may define a time-averaged probability of observing vertex \( b \) after evolving for a randomly chosen time \( t \in [0, T] \):
+\[
+p_{a \to b}(T) = \frac{1}{T} \int_0^T |\langle b | e^{-iHt} | a \rangle|^2 \, dt.
+\]
+Assuming a non-degenerate spectral decomposition \( H = \sum_\lambda \lambda \ket{\lambda}\bra{\lambda} \), one finds:
+\begin{align}
+p_{a \to b}(T) &= \sum_\lambda |\langle a | \lambda \rangle|^2 |\langle b | \lambda \rangle|^2 \\
+&\quad + \sum_{\lambda \neq \lambda'} \langle b | \lambda \rangle \langle \lambda | a \rangle \langle a | \lambda' \rangle \langle \lambda' | b \rangle \cdot \frac{1 - e^{-i(\lambda - \lambda')T}}{i(\lambda - \lambda')T}.
+\end{align}
+As \( T \to \infty \), the second term vanishes, and the limiting distribution becomes:
+\[
+p_{a \to b}(\infty) := \sum_\lambda |\langle a | \lambda \rangle|^2 |\langle b | \lambda \rangle|^2.
+\]
+This distribution does not depend on time and captures the long-time average behavior of the quantum walk.
+The convergence rate is now controlled by the minimum spectral gap between \emph{any pair} of distinct eigenvalues of \( H \), not just the smallest nonzero eigenvalue~\cite{childs2022quantum}.
+
 \section{Comparing Continuous and Discrete-Time Quantum Walks}
@@
 Interestingly, there exist formal \textit{equivalences} between the two models.
-A coined DTQW can approximate a CTQW through small time-step evolution, as demonstrated by Childs et al., and conversely, CTQWs can often be embedded into DTQWs by carefully engineering the coin space to emulate continuous dynamics.
+A coined DTQW can approximate a CTQW through small time-step evolution, as demonstrated by Childs ~\cite{childs2010relationship}, and conversely, CTQWs can often be embedded into DTQWs by carefully engineering the coin space to emulate continuous dynamics.
 While both are computationally equivalent in power, each model has practical advantages in different settings.
@@
 
-% \[
-% A = \sum_{s \in S} P_s,
-% \]
-% where $P_s$ is the permutation matrix representing left multiplication by $s \in G$: $P_s \ket{g} = \ket{sg}$ for all $g \in G$.
-
-% If $S$ is symmetric (i.e., closed under inversion), then $A$ is Hermitian, and $P_s^\dagger = P_{s^{-1}}$.
-The eigenstates of $A$ are understood through group representation theory.
-In particular, the regular representation of $G$ on $\mathbb{C}^{|G|}$ decomposes into a direct sum of irreducible representations (irreps), and since each $P_s$ acts via the regular representation, the adjacency matrix $A$ is a sum of representation operators:
-% \[
-% A = \sum_{s \in S} \rho(s),
-% \]
-% where $\rho$ denotes the regular representation.
-
-% By Schur’s lemma, $A$ acts within each irreducible subspace as a matrix proportional to the representation of $S$.
-Hence, $A$ is block-diagonal (in a suitable basis), with blocks corresponding to irreps of $G$.
-If $\{\phi_\alpha\}$ are the irreps of $G$, then the eigenvalues of $A$ can be determined from the character values $\chi_\alpha(s)$:
-% \[
-% \lambda_\alpha = \sum_{s \in S} \chi_\alpha(s), \quad \text{(for abelian $G$, $\chi_\alpha$ is a character)}.
-% \]
-
-% In the case of abelian $G$, all irreps are one-dimensional, and the eigenstates of $A$ are the Fourier basis:
-% \[
-% \ket{\chi} = \frac{1}{\sqrt{|G|}} \sum_{g \in G} \chi(g) \ket{g}, \quad \lambda_\chi = \sum_{s \in S} \chi(s).
-% \]
-
-% \textbf{Example – Hypercube:} For $G = \mathbb{Z}_2^n$, characters are labeled by bitstrings $u \in \{0,1\}^n$, and $\chi_u(g) = (-1)^{u \cdot g}$. Then
-% \[
-% \lambda_u = \sum_{j=1}^n (-1)^{u_j},
-% \]
-% which gives the $n+1$ distinct eigenvalues $n, n-2, \dots, -n$ of the $n$-dimensional hypercube.
-
-% In the nonabelian case, similar principles apply but require using higher-dimensional irreps and the Great Orthogonality Theorem.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 This idea is also used in the analysis of the glued trees graph, where the walk remains uniform on each layer.
-
-% \paragraph{Hitting and Mixing Properties}
-
-% Quantum walks on Cayley graphs have been applied to study hitting and mixing times.
-In the classical case, random walks on many Cayley graphs are rapidly mixing (e.g., those based on nonabelian simple groups, which often form expanders).
-
-% In the quantum case, mixing is more subtle due to unitary evolution.
-One typically considers \emph{instantaneous} or \emph{time-averaged} mixing.
-Some Cayley graphs support perfect state transfer or periodicity in CTQWs.
-
-% \textbf{Examples:}
-% \begin{itemize}
-%     \item On the cycle graph $C_n$, a CTQW exhibits perfect revival at time $t = \pi$ if $n$ is even.
-%     \item On the hypercube, the CTQW exhibits approximate uniform mixing at specific times.
-% \end{itemize}
-
-% These properties are derived from the spectral structure, which is accessible via group characters.
-
-% \paragraph{Discrete-Time Walks and Symmetry}
-
-% Coined DTQWs also benefit from Cayley graph symmetry.
-If a symmetric coin (e.g., the Grover coin) is used at each vertex of a vertex-transitive graph, the walk respects the full symmetry.
-As a result:
-% \begin{itemize}
-%     \item Amplitudes often remain uniform on symmetry-equivalent vertices.
-%     \item The dynamics of the walk can often be simplified by restricting to a smaller symmetric subspace.
-%     \item In some cases, symmetry can lead to \emph{localization}, where amplitude becomes trapped due to spectral properties of the coin.
-% \end{itemize}
-
-% These effects can be mitigated or exploited through careful coin design or by using Szegedy's method, which naturally respects symmetry.
-
-% In summary, Cayley graphs provide a rich and algebraically structured setting for quantum walks.
-Their underlying group-theoretic properties enable powerful techniques such as spectral analysis through irreducible representations, dimensionality reduction via symmetries and invariant subspaces, and explicit calculations of probabilities, mixing behavior, and hitting times.
-These features make Cayley graphs especially amenable to efficient quantum walk algorithms, which often exploit such structures either explicitly or implicitly.
-In the sections that follow, we extend these ideas to more general settings where group actions go beyond the framework of simple Cayley graphs.
-
-\paragraph{Hitting and Mixing Properties}
-Quantum walks on Cayley graphs have been applied to study hitting and mixing times.
-In the classical case, random walks on many Cayley graphs are rapidly mixing (e.g., those based on nonabelian simple groups, which often form expanders).
-
-In the quantum case, mixing is more subtle due to unitary evolution.
-One typically considers instantaneous or time-averaged mixing.
-Some Cayley graphs support perfect state transfer or periodicity in CTQWs~\cite{Gerhardt2003}.
-Recent work has also established upper bounds on the mixing time for quantum walks on random graphs, showing polynomial-time convergence in certain regimes~\cite{Chakraborty2020}.
-
-Examples:
-\begin{itemize}
-    \item On the cycle graph $C_n$, a CTQW exhibits perfect revival at time $t = \pi$ if $n$ is even.
-    \item On the hypercube, the CTQW exhibits approximate uniform mixing at specific times.
-\end{itemize}
-These properties are derived from the spectral structure, which is accessible via group characters.
 
@@
 
-To see this, we have:
+Now, to see why we have the above equation, we have:
 
